### 2024-06-17 manuscript.tex
Initial commit

\documentclass[12pt,a4paper]{article}
\usepackage{fontspec}
\usepackage[margin=2cm]{geometry}
\usepackage[citecolor=black]{hyperref}
\usepackage[authoryear,round]{natbib}
\usepackage{doi}
\usepackage{titlesec}
\usepackage{caption}
\DeclareCaptionLabelSeparator{pipe}{ | }
\captionsetup{labelfont={bf,sf},labelsep=pipe}
\usepackage{graphicx}
\setsansfont{Source Sans Pro}
\setmainfont{Source Serif Pro}
\hypersetup{
	colorlinks=true,
	urlcolor=blue,
	pdftitle={Using ship observations to assess Southern Ocean clouds in a storm-resolving general circulation model ICON},
	pdfauthor={Peter Kuma, Frida A.-M. Bender, Adrian J. McDonald and Thorsten Mauritsen}
}
\bibliographystyle{abbrvnat}
\titleformat*{\section}{\large\bfseries\sffamily}
\titleformat*{\subsection}{\normalsize\bfseries\sffamily}
\titlespacing*{\section}{0pt}{12pt}{6pt}
\titlespacing*{\subsection}{0pt}{8pt}{4pt}
%\renewcommand{\bibsection}{\section*{Publications}}
\parskip=6pt
\parindent=0pt

\begin{document}

\begin{center} \Large \sffamily\textbf{Using ship observations to assess Southern Ocean clouds in a storm-resolving general circulation model ICON}\\[0.4cm]
\large Peter Kuma$^\mathsf{1,}$*, Frida A.-M. Bender$^\mathsf{1}$, Adrian J. McDonald$^\mathsf{2}$ and Thorsten Mauritsen$^\mathsf{1}$\\[0.4cm]
\small
$^\mathsf{1}$Department of Meteorology (MISU) and Bolin Centre for Climate Research, Stockholm University, Stockholm SE-106 91, Sweden\\[0.2cm]
$^\mathsf{2}$School of Physical and Chemical Sciences, University of Canterbury, Christchurch, New Zealand\\[0.2cm]
*Corresponding author: Peter Kuma (\href{mailto:peter.kuma@misu.su.se}{peter.kuma@misu.su.se})\\[0.4cm]
\large 11 June 2024\\[0.4cm]

\end{center}

\section*{Abstract}

Currently, a new generation of km-scale resolution global climate models are in development as the forthcoming phase of climate modelling. One such model is a 5-km version of the Icosahedral Nonhydrostatic Weather and Climate Model (ICON) developed jointly by Deutscher Wetterdienst (DWD) and the Max-Planck-Institute for Meteorology (MPI-M). Because of the high resolution, most parametrisations, such as that of convection and clouds, can be avoided.

Previous studies have identified substantial large-scale biases in model clouds over the Southern Ocean (SO), affecting sea surface temperature and the Earth's albedo overall. Our aim is to quantify how well the high-resolution ICON model is simulating clouds in this region, particularly in light of the fact that subgrid-scale clouds are not parametrised in this model. This region is mostly dominated by boundary layer clouds generated by shallow convection, and these are problematic to observe by spaceborne lidar and radars, which are affected by attenuation by overlapping and thick clouds and ground clutter, respectively. Therefore, we choose to use a large set of ship-based observations conducted with ceilometers and lidars on board of RV \textit{Polarstern} and other voyages. Altogether, we analyse over 2000 days (about 6 years) of data from 31 voyages and 1 sub-antarctic station covering diverse longitudes of the SO. To achieve a like-for-like comparison with the model, we use a ground-based lidar simulator called the Automatic Lidar and Ceilometer Framework (ALCF). We contrast the results with the ECMWF Reanalysis 5 (ERA5) and the Modern-Era Retrospective analysis for Research and Applications, Version 2 (MERRA-2).

We show that the model underestimates the total cloud fraction by about 10\%, with overestimation of cloud below 2 km, and underestimation of cloud above 2 km. The reanalyses also underestimate the total cloud fraction by about 20\%. ERA5 overestimates cloud below 1 km but underestimates near-surface cloud or fog. In addition to lidar data, we compare radiosonde profiles acquired on the RV \textit{Polarstern} voyages with ICON. Notably, the model exhibits smaller natural variability than observations, and its lifting condensation level tends to be higher. This might explain why cloud occurrence is peaking higher in the model (at 500 m) than in observations (at the surface).

The results imply that the SO cloud biases are still a significant issue in a km-scale resolution model, even though an improvement over the lower-resolution reanalyses is notable. More effort is needed to improve model cloud simulations in this fast-changing and understudied region. The advancement from convection and cloud parametrisation to cloud-resolving models might not solve this bias without an additional effort.

\section{Introduction}

Increasing climate model resolution is a common way of improving model
accuracy \citep{mauritsen2022}. This is of course limited by the available
computational power and a trade-off with increasing parametrisation complexity.
Current computational availability is progressing to enable km-scale Earth
system models (ESMs) and coupled atmophsere--ocean general circulation models
(AOGCMs) in research conditions today and operationally in the forthcoming
years. Therefore, it represents a natural advacement in climate modeling.
Representative of this efforts is the DYnamics of the Atmospheric general
circulation Modeled On Non-hydrostatic Domains (DYAMOND) project
\citep{stevens2019}, which is an intercomparison of global storm-resolving
models.

% Danker et al. (2022), Exploring relations between cloud morphology, cloud phase, and cloud radiative properties in Southern Ocean's stratocumulus clouds
% Possner et al. (2022), Resolution Dependence of Southern Ocean Mixed-Phase Clouds in ICON
% Wall et al. (2022), Observational Constraints on Southern Ocean Cloud-Phase Feedback
% Ramadoss et al. (2020), Simulating mixed-phase cloud properties with ICON around the CAPRICORN ﬁeld campaign at the kilometre scale [poster]
% Ramadoss et al. (2021), An evaluation of kilometre scale ICON simulations of mixed-phase stratocumulus over the Southern Ocean durin CAPRICORN [poster]
% Roh et al. (2021), Intercomparison of cloud properties in DYAMOND simulations over the Atlantic Ocean
% Caldwell et al. (2021), Convection-Permitting Simulations With the E3SM Global Atmosphere Model
% Mauritsen et al. (2022), Early Development and Tuning of a Global Coupled Cloud Resolving Model, and its Fast Response to Increasing CO2
% Heim et al. (2021), Inter-model Variability in Convection-Resolving Simulations of Subtropical Marine Low Clouds
% Zheng et al. (2024), Using Satellite and ARM Observations to Evaluate Cold Air Outbreak Cloud Transitions in E3SM Global Storm-Resolving Simulations
% Mooers et al. (2023), Comparing storm resolving models and climates via unsupervised machine learning
% Seiki and Roh (2020), Improvements in Supercooled Liquid Water Simulations of Low-Level Mixed-Phase Clouds over the Southern Ocean Using a Single-Column Model
% Takasuka et al. (2024), A protocol and analysis of year-long simulations of global storm-resolving models and beyond
% Grundner (2023), Data-Driven Cloud Cover Parameterizations for the ICON Earth System Model Using Deep Learning and Symbolic Regression
% Stevens et al. (2020), The added value of large-eddy and storm-resolving models for simulating clouds and precipitation
% Knight et al. (2024), Cloud properties and boundary layer stability above Southern Ocean sea ice and coastal Antarctica
% Atlas et al. (2020), How well do large‐eddy simulations and global climate models represent observed boundary layer structures and low clouds over the summertime Southern Ocean?
% Korn et al. (2020), ICON‐O: The Ocean Component of the ICON Earth System Model—Global Simulation Characteristics and Local Telescoping Capability
% Schmidt et al. (2024), Effects of vertical grid spacing on the climate simulated in the ICON-Sapphire global storm-resolving model
% Fons et al. (2024), Investigating the sign of stratocumulus adjustments to aerosols in the global storm-resolving model ICON
% Grundner et al. (2022), Deep learning based cloud cover parameterization for ICON
% Cesana et al. (2022), Southern Ocean Solar Reflection Biases in CMIP6 Models Linked to Cloud Phase and Vertical Structure Representations
% Vignesh et al. (2020), Assessment of CMIP6 Cloud Fraction and Comparison with Satellite Observations
% Miao et al. (2021), A Regime-based Investigation into the Errors of CMIP6 Simulated Cloud Radiative Effects Using Satellite Observations
% Chen et al. (2022), Evaluation of Simulated Cloud Diurnal Variation in CMIP6 Climate Models
% Zhang et al. (2023), Understanding models' global sea surface temperature bias in mean state: from CMIP5 to CMIP6
% Schuddeboom and McDonald (2021), The Southern Ocean Radiative Bias, Cloud Compensating Errors, and Equilibrium Climate Sensitivity in CMIP6 Models
% Zhao et al. (2022), Compensating Errors in Cloud Radiative and Physical Properties over the Southern Ocean in the CMIP6 Climate Models
% Jian et al. (2020), Evaluation of the CMIP6 planetary albedo climatology using satellite observations
% Konsta et al. (2022), Low-Level Marine Tropical Clouds in Six CMIP6 Models Are Too Few, Too Bright but Also Too Compact and Too Homogeneous
% Lin and Yu (2022), The potential impact of model horizontal resolution on the simulation of atmospheric cloud radiative effect in CMIP6 models
% Luo et al. (2023), Origins of Southern Ocean warm sea surface temperature bias in CMIP6 models
% Hyder et al. (2018), Critical Southern Ocean climate model biases traced to atmospheric model cloud errors
% Fiddes et al. (2022), Southern Ocean cloud and shortwave radiation biases in a nudged climate model simulation: does the model ever get it right?
% Fiddes et al. (2024), A machine learning approach for evaluating Southern Ocean cloud radiative biases in a global atmosphere model
% Sherriff-Tadano et al. (2023), Southern Ocean Surface Temperatures and Cloud Biases in Climate Models Connected to the Representation of Glacial Deep Ocean Circulation

The NextGEMS project is focused on the research and
development of high resolution (km-scale) global storm-resolving climate models
(GSRMs), which are planned to be the next generation of operational climate
models. Because of the high resolution, some previously parameterised physical
processes can be resolved on the model grid. Thus, such parameterisations and
related uncertainties can be eliminated.

The main aim of our research is to evaluate a high-resolution version of the
Icosahedral Nonhydrostatic Weather and Climate Model (ICON), developed by
NextGEMS jointly with Deutscher Wetterdienst (DWD) and the Max-Planck-Institute
for Meteorology (MPI-M). Previous studies have identified substantial
large-scale biases in climate model clouds over the Southern Ocean (SO), affecting
sea surface temperature and the Earth’s albedo overall. Our aim is to quantify
how well the high-resolution ICON model is simulating clouds in this region,
particularly in light of the fact that subgrid-scale clouds are not
parameterised in this model. This region is mostly dominated by boundary layer
clouds generated by shallow convection, and these are problematic to observe by
spaceborne lidar and radars, which are affected by attenuation by overlapping
and thick clouds and ground clutter, respectively. Therefore, we chose to use
a large set of ship-based observations conducted with ceilometers and lidars on
board of the RV \emph{Polarstern} and other voyages and stations.

Marine clouds have disproportionate effect on TOA shortwave radiation due to
the relatively low albedo of the sea surface. The longitudinal symmetry of the
SO means that model cloud biases tend to be similar across
longitudes.

Altogether, we analysed over 1500 days of data from 31 voyages and one
sub-Antarctic station covering diverse longitudes of the SO. To
achieve a like-for-like comparison with the model, we used a ground-based lidar
simulator called the Automatic Lidar and Ceilometer Framework (ALCF)
\citep{kuma2021}. We contrasted the results with the European Centre for
Medium-Range Weather Forecasts (ECMWF) Reanalysis 5 (ERA5) \citep{era5} and the
Modern-Era Retrospective analysis for Research and Applications, Version 2
(MERRA-2) \citep{gelaro2017}.

\begin{figure}
\centering
\includegraphics[width=0.65\textwidth]{img/map.png}
\caption{A map showing the tracks of 31 voyages of RV \emph{Polarstern}, RSV \emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B. Palmer} and HMNZS \emph{Wellington} and one sub-Antractic station (Macquarie Island) analysed here. The tracks cover Antarctic sectors south of South Americ, the Atlantic Ocean, Africa, Australia and New Zealand in the years 2010 to 2021.}
\label{fig:map}
\end{figure}

\section{Methods}
\label{sec:methods}

\subsection{Voyage and station data}

Together, we analysed data from 31 voyages of RV \emph{Polarstern}, RSV
\emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B. Palmer},
HMNZS \emph{Wellington} and one sub-Antarctic station (Macquarie Island) in the
SO south of 40°S between year 2010 and 2021 (Fig. \ref{fig:map} and
Table \ref{tab:voyages}). Altogether, the voyages and the station comprised
2421 days of data south of 40$^\circ$S, but the availability of ceilometer data
was smaller.

These data sources contained ceilometer (lidar) observations with the Vaisala
CL51 operating at 910 nm and the Lufft CHM-15k operating at 1064 nm. A
ceilometer is a low-power vertically pointing lidar with the purpose of
measuring the cloud base, but it also measures the full vertical structure of
clouds as long as the laser signal is not attenuated by thick clouds. A total
of about 1500 days of lidar observations were included in our analysis.

Apart from lidar observations, radiosondes were launched on weather balloons
at regular synoptic times on the RV \emph{Polarstern} voyages, and surface
meteorological quantities were measured continuously.

\subsection{ICON}

A coupled storm-resolving version of the ICON model is in development by the
NextGEMS project \citep{hohenegger2023}. NextGEMS has so far produced four
cycles of model runs. In our research, we used a Cycle 3 run ngc3028 produced
in 2023 \citep{nextgems2023a,nextgems2023b}. We could not use Cycle 4 due to unavailability of
the necessary variables. The horizontal resolution of ngc3028 is about 5 km.
Unlike current general circulation models (GCMs), the strom-resolving version
of ICON does not use convective and cloud parameterisation but relies on
explicit simulation of convection and clouds on the model grid. While this
makes the code development simpler without having to rely on uncertain
parameterisations, it can miss smaller-scale clouds below the grid resolution.
Turbulence and cloud microphysics are still parameterised in this model. In our
analysis, we used four years of coupled simulation output between years 2021
and 2024 (inclusive). Because the model is free-running, weather and climate
oscillations (such as the El Niño--Southern Oscillation) are not expected to be
equivalent to reality at the same time and place. To compare with observations
taken during different years (2010--2021), we compared the model output with
observations at the same time of year and geographical location.

\subsection{ALCF}

The Automatic Lidar and Ceilometer Framework (ALCF) is a ground-based lidar
simulator. It performs radiative transfer calculations to derive equivalent
lidar backscattered radiation in an atmospheric model, which can then
be compared with observed lidar backscatter \citep{kuma2021}. For this purpose,
it takes atmospheric fields of cloud fraction, liquid and ice mass mixing ratio,
temperature and pressure fields as an input and can be run offline (on the
model output rather than inside the model code). The lidar simulator in the
ALCF is based on the instrument simulator Cloud Feedback Model
Intercomparison Project (CFMIP) Observation Simulator Package (COSP)
\citep{bodas-salcedo2011}. After the backscattered radiation is calculated, a
cloud mask, cloud occurrence by height and the total cloud fraction are
determined.

ALCF has already been used by several research teams for model and reanalysis
evaluation
\citep{kuma2020,kremser2021,guyot2022,pei2023,whitehead2023,mcdonald2024}.

\subsection{Vaisala CL51}

The Vaisala CL51 is a ceilometer operating at a near-infrared wavelength of 910
nm. The maximum range 15.4 km, vertical resolution 10 m, and the number of
vertical levels is 1540. The wavelength is affected by water vapour absorption
of about 20\% in the mid-latitudes \citep{wiegner2015,wiegner2019}.  The
instrument data files containing uncalibrated backscatter were first converted
to NetCDF with cl2nc (\url{https://github.com/peterkuma/cl2nc}) and then
processed with the ALCF to produce a cloud mask and cloud occurrence by height
and the total cloud fraction.

% TODO: Describe absolute calibration.

\subsection{Lufft CHM 15k}

The Lufft CHM 15k is a ceilometer operating at a near-infrared wavelength of
1064 nm. The maximum range is 15.4 km, vertical resolution is 5 m in the near
range (up to 150 m) and 15 m above, the sampling rate is 2 s, and the number of
vertical levels is 1024.  NetCDF files containing uncalibrated backscatter
produced by the instrument were processed with the ALCF to produce a cloud mask
and cloud occurrence by height and the total cloud fraction.

% TODO: Describe absolute calibration.
% TODO: Check sampling rate.

\subsection{MERRA-2}

\subsection{ERA5}

ERA5 \citep{era5} is a reanalysis produced by the European Centre for
Medium-Range Weather Forecasts (ECMWF). It is based on a numerical weather
prediction (NWP) model Integrated Forecast System (IFS) version CY41R2.  The
horizontal resolution is 0.25$^\circ$ in latitude and longitude (about 28 km in
the North--South direction and 14 km in the East--West direction at
60$^\circ$S). The model uses 137 vertical levels.

\subsection{Cyclone tracking}

We used a cyclone tracking algorithm to identify extratropical and polar
cyclones (ECs and PCs) over the SO in the reanalysis and ICON data,
for the purpose of partitioning the cloud occurrence data into cyclonic and
non-cyclonic conditions. We used the open source package CyTRACK
\citep{perez-alarcon2024}. Generally, what constitutes an EC is considered
relatively arbitrary due to a very large variability of ECs \citep{neu2013}.
We used the mean sea level pressure field and horizontal wind speed fields
as input to the CyTRACK algorithm. The algorithm uses pressure and wind
speed thresholds as well as tracking across time steps to identify cyclone
centres and radii.

\subsection{Precipitation identification using machine learning}
\label{sec:ann}

It was not possible to include precipitation simulation in the ALCF due to the
absence of required fields in our model output and reanalysis data (liquid and
ice precipitation mass mixing ratios) because the required radiation
calculations are not implemented in the ALCF. At the same time, it is relatively
difficult to distinguish precipitation backscatter from cloud backscatter
in lidar observations, especially when only one wavelength channel and no
polarisation channel are available.

In order to get a fair comparison of observations and models, one needs to
exclude profiles with precipitation either manually or using an automated
method. In models, this can be accomplished relatively easily by excluding
profiles with an amount of surface precipitation flux exceeding a threshold.
In observations, this can be more complicated, especially on voyages, because
rain gauges are known to be unreliable on ships.

On the RV \emph{Polarstern} voyages, regular synoptic observations were
available.  These included precipitation observations by an observer. We
used this dataset to train a convolutional artiﬁcial neural network (ANN)
of the U-Net type \citep{ronneberger2015} to recognise precipitation in the
lidar data. Samples of short time intervals (10 min) of near-surface
backscatter (0–250 m) were classified as clear, rain, snow and fog, using the
synoptic observations as a training set. From these, a binary classification of
profiles as wet or dry was derived.

The ANN achieved 65\% sensitivity and 87\% speciﬁcity when the true positive
rate (26\%) was made to match observations. We considered these success rates
satisfactory for the purpose of filtering precipitation profiles.

\section{Results}
\label{sec:results}

\begin{table}
% TODO: Add sampling intervals.
\caption{List of voyages and stations. Start, end and days (UTC; inclusive) indicate the time period when the vessel was south of 40$^\circ$S. Abbreviations: ceilometer (ceil.), Australia (AU), New Zealand (NZ), South America (SA), Atlantic Ocean (AO) and Africa (AF). The number of days is rounded to the nearest integer.}
\label{tab:voyages}
\small
\begin{tabular}{llllllr}
Name & Vessel & Ceil. & Region & Start & End & Days\\
\hline
AA15-16  & RSV \emph{Aurora Australis}   & CL51    & AU       & 2015-10-22 & 2016-02-22 & 124\\
HMNZSW16 & HMNZS \emph{Wellington}       & CHM 15k & NZ       & 2016-11-23 & 2016-12-19 & 27 \\
MARCUS   & RSV \emph{Aurora Australis}   & CL51    & AU       & 2017-10-29 & 2018-03-26 & 149\\
MCQ16-18 & /                             & CL51    & AU/NZ    & 2016-04-03 & 2018-03-14 & 710\\
NBP1704  & RV \emph{Nathaniel B. Palmer} & CHM 15k & NZ       & 2017-04-14 & 2017-06-08 & 55 \\
PS77/2   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2010-12-01 & 2011-02-04 & 65 \\
PS77/3   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2011-02-07 & 2011-04-14 & 66 \\
PS79/2   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2011-12-06 & 2012-01-02 & 27 \\
PS79/3   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2012-01-10 & 2012-03-10 & 61 \\
PS79/4   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2012-03-14 & 2012-04-08 & 26 \\
PS81/2   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2012-12-02 & 2013-01-18 & 47 \\
PS81/3   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-01-22 & 2013-03-17 & 55 \\
PS81/4   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-03-18 & 2013-04-16 & 30 \\
PS81/5   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-04-20 & 2013-05-23 & 33 \\
PS81/6   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-06-10 & 2013-08-12 & 63 \\
PS81/7   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-08-15 & 2013-10-14 & 60 \\
PS81/8   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-11-12 & 2013-12-14 & 31 \\
PS81/9   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-12-21 & 2014-03-02 & 71 \\
PS89     & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2014-12-05 & 2015-01-30 & 56 \\
PS96     & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2015-12-08 & 2016-02-14 & 68 \\
PS97     & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2016-02-15 & 2016-04-06 & 52 \\
PS103    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2016-12-18 & 2017-02-02 & 46 \\
PS104    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2017-02-08 & 2017-03-18 & 39 \\
PS111    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2018-01-21 & 2018-03-14 & 52 \\
PS112    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2018-03-18 & 2018-05-05 & 49 \\
PS117    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2018-12-18 & 2019-02-07 & 51 \\
PS118    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2019-02-18 & 2019-04-08 & 50 \\
PS123    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2021-01-10 & 2021-01-31 & 21 \\
PS124    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2021-02-03 & 2021-03-30 & 55 \\
TAN1502  & RV \emph{Tangaroa}            & CL51    & NZ       & 2015-01-20 & 2015-03-12 & 51 \\
TAN1702  & RV \emph{Tangaroa}            & CHM 15k & NZ       & 2017-03-09 & 2017-03-31 & 23 \\
TAN1802  & RV \emph{Tangaroa}            & CHM 15k & NZ       & 2018-02-07 & 2018-03-20 & 41 \\
\hline
\textbf{Total} &                         &          &            &            &         & \textbf{2421}\\
\end{tabular}
\normalsize
\end{table}

\begin{figure}
\centerline{
\includegraphics[width=1.06\textwidth]{img/cloud_occurrence_panel.pdf}
}
\caption{Cloud occurrence by height for the 31 voyages and one sub-Antarctic
station (MCQ16-18) in observations (OBS), and simulated by the ALCF from the
ICON model, MERRA‐2 (M2) and ERA5 reanalysis data. The numbers in the legend
indicate the total cloud fraction and the number of days of data.}
\label{fig:cloud-occurrence-panel}
\end{figure}

\subsection{Cloud occurrence}

We used the ALCF to derive cloud occurrence by height and the total cloud
fraction from observations, ICON and two reanalyses MERRA-2 and ERA5 (Fig.
\ref{fig:cloud-occurrence-panel}). We aggregated the sources by calculating
the averages and percentiles of all individual profiles (Fig.
\ref{fig:cloud-occurrence}). The analysis shows that the total cloud fraction
(determined as the fraction of proﬁles with clouds at any height in the lidar
cloud mask) is underestimated in ICON and reanalyses by about 10\% and 20\%,
respectively.

In particular, ICON overestimates cloud occurrence below 1 km and
underestimates it above, MERRA-2 underestimates cloud occurrence at all heights,
especially near the surface, and ERA5 simulates cloud occurrence relatively well
above 1 km, but strongly underestimates it near the surface.
We note that fog or near-surface clouds are strongly lacking in the reanalyses.
As shown in Fig. \ref{fig:cloud-occurrence-panel}, the biases are relatively
consistent across voyages and longitudes. The ICON results are overall better
matching the observations than the reanalyses.

The ICON comparison is limited by the fact that the model is free-running.
Thus, the vertical proﬁles are not expected to represent the same weather
conditions as in observations, but long-term statistical comparison is still
possible. Only proﬁles with the same sea ice conditions (present or not) were
included to avoid comparing sea ice with open sea conditions.

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{img/cloud_occurrence.pdf}
\caption{Cloud occurrence by height aggregated from the 31 voyages and one station
for observations (OBS), the ICON mode, the MERRA-2 and ERA5 reanalyses. The
total cloud fraction (CF) is shown in the legend. The ranges are from the
16$^\mathrm{th}$ to the 84$^\mathrm{th}$ percentile.}
\label{fig:cloud-occurrence}
\end{figure}

\subsection{Thermodynamic proﬁles}

We compared about 2000 radiosonde proﬁles from 24 RV \emph{Polarstern}
voyages between the observations and the model. Proﬁles in the model were taken
at the same geographical location and time relative to the start of the year.
Only proﬁles for which the sea ice conditions (sea ice present or absent) are
the same in the observations and the model were included. We derived potential
temperature profiles, lifting condensation level (LCL), and aggregated the
profiles by sea ice conditions (Fig. \ref{fig:radiosonde}).

We found that the variability of potential temperature in the model to be
smaller than in the observations. This indicates that the model does not
represent the entire natural variability. The LCL peaks at the surface in the
observations, but the peak in the model is higher (about 200 m). This probably
relates to the greater occurrence of fog and the peak of cloud occurrence at
the surface in observations, whereas in the model the peak is higher.

\subsection{Cloud occurrence by cyclonic conditions}

\subsection{Cloud occurrence by stability}

We determine stability by calculating lower tropospheric stability (LTS)
as the difference between potential temperature at 700 hPa and the surface.
From a histogram of LTS in ERA5 and MERRA-2 calculated at all voyage tracks
and the station (Fig. S1), we determined a dividing threshold of 12 K for
relatively unstable (< 12 K) and relatively stable (>= 12 K) conditions.

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{img/radiosonde.pdf}
\caption{Radiosonde proﬁles of potential temperature and lifting condensation
level (LCL) on all RV \emph{Polarstern} voyages.}
\label{fig:radiosonde}
\end{figure}

\section{Discussion}

\section{Conclusions}

We show that the model underestimates the total cloud fraction by about 10\%,
with an overestimation of clouds below 2 km, and an underestimation of clouds
above 2 km. The reanalyses also underestimate the total cloud fraction by about
20\%.  ERA5 overestimates cloud below 1 km but underestimates near-surface
cloud or fog. In addition to lidar data, we compare radiosonde profiles
acquired on the RV \textit{Polarstern} voyages with ICON. Notably, the model
exhibits smaller natural variability than observations, and its lifting
condensation level tends to be higher. This might explain why cloud occurrence
is peaking higher in the model (at 500 m) than in observations (at the
surface).

We compared radiosonde proﬁles acquired on the RV \emph{Polarstern} voyages
with ICON.  The ICON model exhibits smaller internal variability than
observations, and its LCL level tends to be higher, which might explain why a
peak of cloud occurrence in observations is located at the surface, while in
ICON it is located higher, corresponding to the LCL.

The results imply that SO cloud biases are still a significant
issue in a km-scale resolution model, even though an improvement over the
lower-resolution reanalyses is notable. More effort is needed to improve model
cloud simulations in this fast-changing and understudied region. The
advancement from convection and cloud parameterisation to cloud-resolving models
might not solve this bias without additional effort.

Further analysis will focus on investigating the role of cyclones in the
identified biases by using cyclone tracking and the role of local thermodynamic
stability using lower tropospheric stability and estimated inversion strength.

\section*{Acknowledgements}

We acknowledge the RV Polarstern datasets provided by the Alfred Wegener
Institute, RSV Aurora Australis datasets provided by the Australian Antarctic
Program and the University of Canterbury (UC), RV Tangaroa datasets provided by
the National Institute of Water and Atmospheric Research and the UC, RV
Nathaniel B. Palmer dataset provided by the National Science Foundation,
Cooperative Institute for Research in Environmental Sciences, University of
Colorado and the UC, HMNZS Wellington dataset provided by the Royal New Zealand
Navy and the UC and a Macquarie Island dataset provided by the Atmospheric
Radiation Measurement and the UC. We thank the scientiﬁc staff, the crew and
everyone involved in collecting data on the voyages and Macquarie Island,
especially Kelly Schick, Peter Guest, John J. Cassano, Simon
Parsons, Graeme Plank, Sally Garrett, Jamie Halla, Sean Hartery, Mike J.
Harvey, Simon P. Alexander and Alex Schuddeboom. We acknowledge the reanalysis
dataset ERA5 provided by the Copernicus Climate Change Service and MERRA-2
provided by the Global Modeling and Assimilation Office. We also acknowledge the
AMSR Uniﬁed and SMMR and SSM/I-SSMIS datasets provided by the National Snow and
Ice Data Center.

\section*{Code availability}

The ALCF is open source and is available at \url{https://alcf.peterkuma.net}.
cl2nc is open source and is available at
\url{https://github.com/peterkuma/cl2nc}, Our processing a plotting code is
open source and available at
\url{https://github.com/peterkuma/icon-so-2024-code}.

\section*{Data availability}

The RV \emph{Polarstern} data are openly available from Pangaea
(\url{https://pangaea.de}). The MARCUS and Macquarie Island (MICRE) data are
openly available from the Atmospheric Radiation Measurement (ARM)
(\url{https://www.arm.gov}). The MERRA-2 data are openly available at from NASA
NASA Goddard Earth Sciences (GES) Data and Information Services Center (DISC)
(\url{https://disc.gsfc.nasa.gov/datasets?project=MERRA-2}).  The ERA5 data are
openly available from Copernicus Climate Data Store (CDS)
(\url{https://cds.climate.copernicus.eu}).  The other voyage and station data
are openly available on Zenodo (). Subsetted model and reanalysis data for the
voyage tracks and the station and data processed with the ALCF are openly
available on Zenodo ().

\footnotesize
\setlength{\bibsep}{0.0pt}
\bibliography{manuscript}

\end{document}

### 2024-06-20 manuscript.tex
Auto title date
Writing introduction

@@
+% Takasuka et al. (2024), A protocol and analysis of year-long simulations of global storm-resolving models and beyond
+% Knight et al. (2024), Cloud properties and boundary layer stability above Southern Ocean sea ice and coastal Antarctica
+% Zheng et al. (2024), Using Satellite and ARM Observations to Evaluate Cold Air Outbreak Cloud Transitions in E3SM Global Storm-Resolving Simulations
+% Schmidt et al. (2024), Effects of vertical grid spacing on the climate simulated in the ICON-Sapphire global storm-resolving model
+% Fons et al. (2024), Investigating the sign of stratocumulus adjustments to aerosols in the global storm-resolving model ICON
+% Fiddes et al. (2024), A machine learning approach for evaluating Southern Ocean cloud radiative biases in a global atmosphere model
+% Mooers et al. (2023), Comparing storm resolving models and climates via unsupervised machine learning
+% Zhang et al. (2023), Understanding models' global sea surface temperature bias in mean state: from CMIP5 to CMIP6
+% Grundner (2023), Data-Driven Cloud Cover Parameterizations for the ICON Earth System Model Using Deep Learning and Symbolic Regression [thesis]
+% Luo et al. (2023), Origins of Southern Ocean warm sea surface temperature bias in CMIP6 models
+% Sherriff-Tadano et al. (2023), Southern Ocean Surface Temperatures and Cloud Biases in Climate Models Connected to the Representation of Glacial Deep Ocean Circulation
+% Danker et al. (2022), Exploring relations between cloud morphology, cloud phase, and cloud radiative properties in Southern Ocean's stratocumulus clouds
+% Possner et al. (2022), Resolution Dependence of Southern Ocean Mixed-Phase Clouds in ICON
+% Mauritsen et al. (2022), Early Development and Tuning of a Global Coupled Cloud Resolving Model, and its Fast Response to Increasing CO2
+% Wall et al. (2022), Observational Constraints on Southern Ocean Cloud-Phase Feedback
+% Grundner et al. (2022), Deep learning based cloud cover parameterization for ICON
+% Cesana et al. (2022), Southern Ocean Solar Reflection Biases in CMIP6 Models Linked to Cloud Phase and Vertical Structure Representations
+% Fiddes et al. (2022), Southern Ocean cloud and shortwave radiation biases in a nudged climate model simulation: does the model ever get it right?
+% Zhao et al. (2022), Compensating Errors in Cloud Radiative and Physical Properties over the Southern Ocean in the CMIP6 Climate Models
+% Konsta et al. (2022), Low-Level Marine Tropical Clouds in Six CMIP6 Models Are Too Few, Too Bright but Also Too Compact and Too Homogeneous
+% Lin and Yu (2022), The potential impact of model horizontal resolution on the simulation of atmospheric cloud radiative effect in CMIP6 models
+% Ramadoss et al. (2021), An evaluation of kilometre scale ICON simulations of mixed-phase stratocumulus over the Southern Ocean durin CAPRICORN [poster]
+% Miao et al. (2021), A Regime-based Investigation into the Errors of CMIP6 Simulated Cloud Radiative Effects Using Satellite Observations
+% Roh et al. (2021), Intercomparison of cloud properties in DYAMOND simulations over the Atlantic Ocean
+% Caldwell et al. (2021), Convection-Permitting Simulations With the E3SM Global Atmosphere Model
+% Schuddeboom and McDonald (2021), The Southern Ocean Radiative Bias, Cloud Compensating Errors, and Equilibrium Climate Sensitivity in CMIP6 Models
+% Ramadoss et al. (2020), Simulating mixed-phase cloud properties with ICON around the CAPRICORN ﬁeld campaign at the kilometre scale [poster]
+% Heim et al. (2021), Inter-model Variability in Convection-Resolving Simulations of Subtropical Marine Low Clouds
+% Seiki and Roh (2020), Improvements in Supercooled Liquid Water Simulations of Low-Level Mixed-Phase Clouds over the Southern Ocean Using a Single-Column Model
+% Stevens et al. (2020), The added value of large-eddy and storm-resolving models for simulating clouds and precipitation
+% Atlas et al. (2020), How well do large‐eddy simulations and global climate models represent observed boundary layer structures and low clouds over the summertime Southern Ocean?
+% Korn et al. (2020), ICON‐O: The Ocean Component of the ICON Earth System Model—Global Simulation Characteristics and Local Telescoping Capability
+% Vignesh et al. (2020), Assessment of CMIP6 Cloud Fraction and Comparison with Satellite Observations
+% Chen et al. (2022), Evaluation of Simulated Cloud Diurnal Variation in CMIP6 Climate Models
+% Jian et al. (2020), Evaluation of the CMIP6 planetary albedo climatology using satellite observations
+% Satoh et al. (2019), Global Cloud-Resolving Models
+% Hyder et al. (2018), Critical Southern Ocean climate model biases traced to atmospheric model cloud errors
+
 \documentclass[12pt,a4paper]{article}
@@
 *Corresponding author: Peter Kuma (\href{mailto:peter.kuma@misu.su.se}{peter.kuma@misu.su.se})\\[0.4cm]
-\large 11 June 2024\\[0.4cm]
+\large \today\\[0.4cm]
 
@@
 
-Currently, a new generation of km-scale resolution global climate models are in development as the forthcoming phase of climate modelling.
-One such model is a 5-km version of the Icosahedral Nonhydrostatic Weather and Climate Model (ICON) developed jointly by Deutscher Wetterdienst (DWD) and the Max-Planck-Institute for Meteorology (MPI-M).
-Because of the high resolution, most parametrisations, such as that of convection and clouds, can be avoided.
+Currently, a new generation of km-scale (also called `k-scale') resolution
+global climate models are in development as the forthcoming phase of climate
+modelling. One such model is a 5-km version of the Icosahedral Nonhydrostatic
+Weather and Climate Model (ICON) developed jointly by Deutscher Wetterdienst
+(DWD) and the Max-Planck-Institute for Meteorology (MPI-M). Because of the high
+resolution, most parametrisations, such as that of convection and clouds, can
+be avoided.
 
-Previous studies have identified substantial large-scale biases in model clouds over the Southern Ocean (SO), affecting sea surface temperature and the Earth's albedo overall.
-Our aim is to quantify how well the high-resolution ICON model is simulating clouds in this region, particularly in light of the fact that subgrid-scale clouds are not parametrised in this model.
-This region is mostly dominated by boundary layer clouds generated by shallow convection, and these are problematic to observe by spaceborne lidar and radars, which are affected by attenuation by overlapping and thick clouds and ground clutter, respectively.
-Therefore, we choose to use a large set of ship-based observations conducted with ceilometers and lidars on board of RV \textit{Polarstern} and other voyages.
-Altogether, we analyse over 2000 days (about 6 years) of data from 31 voyages and 1 sub-antarctic station covering diverse longitudes of the SO.
-To achieve a like-for-like comparison with the model, we use a ground-based lidar simulator called the Automatic Lidar and Ceilometer Framework (ALCF).
-We contrast the results with the ECMWF Reanalysis 5 (ERA5) and the Modern-Era Retrospective analysis for Research and Applications, Version 2 (MERRA-2).
+Previous studies have identified substantial large-scale biases in model clouds
+over the Southern Ocean (SO), affecting sea surface temperature and the Earth's
+albedo overall. Our aim is to quantify how well the high-resolution ICON model
+is simulating clouds in this region, particularly in light of the fact that
+subgrid-scale clouds are not parametrised in this model. This region is mostly
+dominated by boundary layer clouds generated by shallow convection, and these
+are problematic to observe by spaceborne lidar and radars, which are affected
+by attenuation by overlapping and thick clouds and ground clutter,
+respectively. Therefore, we choose to use a large set of ship-based
+observations conducted with ceilometers and lidars on board of Research Vessel
+(RV) \textit{Polarstern} and other voyages. Altogether, we analyse over 2000
+days (about 6 years) of data from 31 voyages and 1 sub-antarctic station
+covering diverse longitudes of the SO. To achieve a like-for-like comparison
+with the model, we use a ground-based lidar simulator called the Automatic
+Lidar and Ceilometer Framework (ALCF). We contrast the results with the ECMWF
+Reanalysis 5 (ERA5) and the Modern-Era Retrospective analysis for Research and
+Applications, Version 2 (MERRA-2).
 
-We show that the model underestimates the total cloud fraction by about 10\%, with overestimation of cloud below 2 km, and underestimation of cloud above 2 km.
-The reanalyses also underestimate the total cloud fraction by about 20\%.
-ERA5 overestimates cloud below 1 km but underestimates near-surface cloud or fog.
-In addition to lidar data, we compare radiosonde profiles acquired on the RV \textit{Polarstern} voyages with ICON.
-Notably, the model exhibits smaller natural variability than observations, and its lifting condensation level tends to be higher.
-This might explain why cloud occurrence is peaking higher in the model (at 500 m) than in observations (at the surface).
+We show that the model underestimates the total cloud fraction by about 10\%,
+with overestimation of cloud below 2 km, and underestimation of cloud above 2
+km. The reanalyses also underestimate the total cloud fraction by about 20\%.
+ERA5 overestimates cloud below 1 km but underestimates near-surface cloud or
+fog. In addition to lidar data, we compare radiosonde profiles acquired on the
+RV \textit{Polarstern} voyages with ICON. Notably, the model exhibits smaller
+natural variability than observations, and its lifting condensation level tends
+to be higher. This might explain why cloud occurrence is peaking higher in the
+model (at 500 m) than in observations (at the surface).
 
-The results imply that the SO cloud biases are still a significant issue in a km-scale resolution model, even though an improvement over the lower-resolution reanalyses is notable.
-More effort is needed to improve model cloud simulations in this fast-changing and understudied region.
-The advancement from convection and cloud parametrisation to cloud-resolving models might not solve this bias without an additional effort.
+The results imply that the SO cloud biases are still a significant issue in a
+km-scale resolution model, even though an improvement over the lower-resolution
+reanalyses is notable. More effort is needed to improve model cloud simulations
+in this fast-changing and understudied region. The advancement from convection
+and cloud parametrisation to cloud-resolving models might not solve this bias
+without an additional effort.
 
@@
 
-Increasing climate model resolution is a common way of improving model
-accuracy \citep{mauritsen2022}. This is of course limited by the available
-computational power and a trade-off with increasing parametrisation complexity.
-Current computational availability is progressing to enable km-scale Earth
-system models (ESMs) and coupled atmophsere--ocean general circulation models
+Increasing climate model resolution is a common way of improving model accuracy
+\citep{mauritsen2022}. This is of course limited by the available computational
+power and a tradeoff with increasing parametrisation complexity.  Current
+computational availability and acceleration from general-purpose computing on
+graphics processing units (GPGPUs) is progressing to enable km-scale Earth
+system models (ESMs) and coupled atmosphsere--ocean general circulation models
 (AOGCMs) in research conditions today and operationally in the forthcoming
-years. Therefore, it represents a natural advacement in climate modeling.
-Representative of this efforts is the DYnamics of the Atmospheric general
-circulation Modeled On Non-hydrostatic Domains (DYAMOND) project
-\citep{stevens2019}, which is an intercomparison of global storm-resolving
-models.
+years. Therefore, it represents a natural advancement in climate modeling.
+Global strom-resolving models (GSRMs) are emerging as a new front in the
+development of high-resolution global climate models, with horizontal grid
+resolutions of about 2--8 km \citep{satoh2019,stevens2019}. This is enough to
+resolve mesoscale convective storms, but smaller-scale convective plumes and
+smaller-scale cloud structure remain unresolved. At a 5-km scale,
+non-hydrostatic processes also become important, and for this reason such
+models are generally non-hydrostatic. The terms global cloud-resolving models
+(GCRMs), or global convection-permitting/-resolving models (GCPMs) are also
+sometimes used interchangeably with GSRMs but imply that clouds or convection
+are resolved explicitly, which is not entirely true for GSRMs, as this would
+require an even higher horizontal resolution \citep{satoh2019}.  Representative
+of these efforts is the DYnamics of the Atmospheric general circulation Modeled
+On Non-hydrostatic Domains (DYAMOND) project \citep{stevens2019,dyamond}, which
+is an intercomparison of nine global storm-resolving models (GSRMs) on two
+40-day time periods in summer (1 August -- 10 September 2016) and winter (20
+January - 1 March 2020). A new one-year GSRM intercomparison is currently
+proposed by \cite{takasuka2024}, with the hope of also evaluating the seasonal
+cycle and large-scale circulation.  An alternative to using a
+computantionally costly GSRM is to train an artificial neural network on GSRM
+output and use it for subgrid-scale clouds, as done with the GSRM ICON by
+\cite{grundner2022}; \cite{grundner2023}.
 
-% Danker et al. (2022), Exploring relations between cloud morphology, cloud phase, and cloud radiative properties in Southern Ocean's stratocumulus clouds
-% Possner et al. (2022), Resolution Dependence of Southern Ocean Mixed-Phase Clouds in ICON
-% Wall et al. (2022), Observational Constraints on Southern Ocean Cloud-Phase Feedback
-% Ramadoss et al. (2020), Simulating mixed-phase cloud properties with ICON around the CAPRICORN ﬁeld campaign at the kilometre scale [poster]
-% Ramadoss et al. (2021), An evaluation of kilometre scale ICON simulations of mixed-phase stratocumulus over the Southern Ocean durin CAPRICORN [poster]
-% Roh et al. (2021), Intercomparison of cloud properties in DYAMOND simulations over the Atlantic Ocean
-% Caldwell et al. (2021), Convection-Permitting Simulations With the E3SM Global Atmosphere Model
-% Mauritsen et al. (2022), Early Development and Tuning of a Global Coupled Cloud Resolving Model, and its Fast Response to Increasing CO2
-% Heim et al. (2021), Inter-model Variability in Convection-Resolving Simulations of Subtropical Marine Low Clouds
-% Zheng et al. (2024), Using Satellite and ARM Observations to Evaluate Cold Air Outbreak Cloud Transitions in E3SM Global Storm-Resolving Simulations
-% Mooers et al. (2023), Comparing storm resolving models and climates via unsupervised machine learning
-% Seiki and Roh (2020), Improvements in Supercooled Liquid Water Simulations of Low-Level Mixed-Phase Clouds over the Southern Ocean Using a Single-Column Model
-% Takasuka et al. (2024), A protocol and analysis of year-long simulations of global storm-resolving models and beyond
-% Grundner (2023), Data-Driven Cloud Cover Parameterizations for the ICON Earth System Model Using Deep Learning and Symbolic Regression
-% Stevens et al. (2020), The added value of large-eddy and storm-resolving models for simulating clouds and precipitation
-% Knight et al. (2024), Cloud properties and boundary layer stability above Southern Ocean sea ice and coastal Antarctica
-% Atlas et al. (2020), How well do large‐eddy simulations and global climate models represent observed boundary layer structures and low clouds over the summertime Southern Ocean?
-% Korn et al. (2020), ICON‐O: The Ocean Component of the ICON Earth System Model—Global Simulation Characteristics and Local Telescoping Capability
-% Schmidt et al. (2024), Effects of vertical grid spacing on the climate simulated in the ICON-Sapphire global storm-resolving model
-% Fons et al. (2024), Investigating the sign of stratocumulus adjustments to aerosols in the global storm-resolving model ICON
-% Grundner et al. (2022), Deep learning based cloud cover parameterization for ICON
-% Cesana et al. (2022), Southern Ocean Solar Reflection Biases in CMIP6 Models Linked to Cloud Phase and Vertical Structure Representations
-% Vignesh et al. (2020), Assessment of CMIP6 Cloud Fraction and Comparison with Satellite Observations
-% Miao et al. (2021), A Regime-based Investigation into the Errors of CMIP6 Simulated Cloud Radiative Effects Using Satellite Observations
-% Chen et al. (2022), Evaluation of Simulated Cloud Diurnal Variation in CMIP6 Climate Models
-% Zhang et al. (2023), Understanding models' global sea surface temperature bias in mean state: from CMIP5 to CMIP6
-% Schuddeboom and McDonald (2021), The Southern Ocean Radiative Bias, Cloud Compensating Errors, and Equilibrium Climate Sensitivity in CMIP6 Models
-% Zhao et al. (2022), Compensating Errors in Cloud Radiative and Physical Properties over the Southern Ocean in the CMIP6 Climate Models
-% Jian et al. (2020), Evaluation of the CMIP6 planetary albedo climatology using satellite observations
-% Konsta et al. (2022), Low-Level Marine Tropical Clouds in Six CMIP6 Models Are Too Few, Too Bright but Also Too Compact and Too Homogeneous
-% Lin and Yu (2022), The potential impact of model horizontal resolution on the simulation of atmospheric cloud radiative effect in CMIP6 models
-% Luo et al. (2023), Origins of Southern Ocean warm sea surface temperature bias in CMIP6 models
-% Hyder et al. (2018), Critical Southern Ocean climate model biases traced to atmospheric model cloud errors
-% Fiddes et al. (2022), Southern Ocean cloud and shortwave radiation biases in a nudged climate model simulation: does the model ever get it right?
-% Fiddes et al. (2024), A machine learning approach for evaluating Southern Ocean cloud radiative biases in a global atmosphere model
-% Sherriff-Tadano et al. (2023), Southern Ocean Surface Temperatures and Cloud Biases in Climate Models Connected to the Representation of Glacial Deep Ocean Circulation
+nextGEMS is an EU-funded project \citep{nextgems} focused on the research and
+development of GSRMs at multiple modelling centres and universities in Europe.
+The project also develops GSRM versions of the Icosahedral Nonhydrostatic
+Weather and Climate Model (ICON), the Integrated Forecasting System (IFS), and
+their ocean components at eddy-resolving resolutions: ICON-O coupled with ICON
+and Finite-Element/volumE Sea ice-Ocean Model (FESOM) and Nucleus for European
+Modelling of the Ocean (NEMO) coupled with IFS.  The project has so far
+produced ICON and IFS simulations in three cycles (Cycle 1--3) and pre-final
+simulation, with a final production simulation planned by the end of the
+project. nextGEMS is not the only project developing GSRMs. Other GSRMs (or
+GSRM versions of climate models) currently in development include:
+Convection-Permitting Simulations With the E3SM Global Atmosphere Model
+[SCREAM; \cite{caldwell2021}], Atmospheric Model [NICAM; \cite{satoh2008}],
+Unified Model (UM), eXperimental System for High-resolution modeling for
+Earth-to-Local Domain [X-SHiELD; \cite{shield}], Action de Recherche Petite
+Echelle Grande Echelle-NonHydrostatic version [ARPEGE-NH;
+\cite{bubnova1995,voldoire2017}], Finite-Volume Dynamical Core on the Cubed
+Sphere [FV3, \cite{lin2004}], NASA Goddard Earth Observing System global
+atmospheric model version 5 [GEOS5; \cite{putman2011}], Model for Prediction
+Across Scales [MPAS; \cite{skamarock2012}], and System for Atmospheric Modeling
+[SAM; \cite{khairoutdinov2003}].
 
-The NextGEMS project is focused on the research and
-development of high resolution (km-scale) global storm-resolving climate models
-(GSRMs), which are planned to be the next generation of operational climate
-models. Because of the high resolution, some previously parameterised physical
-processes can be resolved on the model grid. Thus, such parameterisations and
-related uncertainties can be eliminated.
+Multiple cloud properties have an effect on the shortwave (SW) and longwave
+(LW) radiation. On the first order, it is the total cloud fraction, cloud phase,
+and the liquid and ice water path. These are influenced by the atmopheric
+thermodynamics, convection and circulation, and indirect and direct effects
+of aerosols. On smaller orders, it is the cloud droplet size distribution, ice
+crystal habit, cloud lifetime, and direct radiative interaction with aerosols.
+In the 6th phase of the Coupled Model Intercomparison Project [CMIP6;
+\citep{eyring2016}], the cloud feedback has increased relative to CMIP5
+\citep{zelinka2020}, also being one of the main reasons for the higher climate
+sensitivity of CMIP6 models.
 
-The main aim of our research is to evaluate a high-resolution version of the
-Icosahedral Nonhydrostatic Weather and Climate Model (ICON), developed by
-NextGEMS jointly with Deutscher Wetterdienst (DWD) and the Max-Planck-Institute
+The Southern Ocean (SO) is known to be a problematic region for climate model
+biases due to reasons such as a lack of surface and in situ observations and
+being a lower priority region for numerical weather prediction (NWP) and
+climate model development because it is far away from populated areas of
+interest.  Nevertheless, radiation biases and changes over an area of its size
+have a very significant influence on the global climate, and the SO is an
+important part of the global ocean conveyor belt.  Marine clouds have
+disproportionate effect on top of atmosphere (TOA) SW radiation due to the
+relatively low albedo of the sea surface.  The longitudinal symmetry of the SO
+means that model cloud biases tend to be similar across longitudes.  Here, we
+will conventionally refer to the SO as ocean regions south of 40$^\circ$S,
+low-latitude SO as 40--55$^\circ$S and high-latitude SO as south of
+55$^\circ$S.
+
+SO radiation biases have been relatively large and systematic compared to the
+rest of the globe since at least CMIP3 \citep{trenberth2010}, and the SO SW CRE
+bias is still positive in eight analysed CMIP6 models analysed by
+\cite{schuddeboom2021} over high-latitude SO, whereas over low-latitude SO it
+tends to be more neutral or negative in some models. Too much absorbed SW
+radiation over the SO was also identified in the GSRM SCREAM
+\cite{caldwell2021}. Compensating biases are possible, such as the `too few too
+bright' cloud bias, characterised by too small cloud fraction and too large
+cloud albedo \citep{wall2017,kuma2020}, previously described by
+\cite{webb2001}, \cite{weare2004}, \cite{zhang2005}, \cite{karlsson2008},
+\cite{nam2012}, \cite{klein2013}, and \cite{bender2017} in other regions and
+models. That is, a model maintains a resonable SW radiation balance by
+reflecting too much SW radiation by cloudy sky but has too little cloudy sky
+area overall. A study by \cite{konsta2022} showed that this type bias is still
+present in six analysed CMIP6 models in tropical marine clouds, using the
+GCM-Oriented Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observation
+(CALIPSO) Cloud Product [CALIPSO--GOCCP; \cite{chepfer2010}] and Polarization
+\& Anisotropy of Reflectances for Atmospheric Sciences coupled with
+Observations from a Lidar [PARASOL; \citep{lier2008}] as a reference. They
+suggest improper simulation of subgrid-scale cloud heterogeneity as a cause.
+Compensating cloud biases in the Australian Community Climate and Earth System
+Simulator (ACCESS) – Atmosphere-only model version 2 (AM2) over the SO were
+analysed by \cite{fiddes2022} and \cite{fiddes2024}.  \cite{possner2022} showed
+that over the SO, the DYAMOND GSRM ICON underestimates low-level cloud fraction
+on the order of 30\% [relative to the Moderate Resolution Imaging
+Spectroradiometer (MODIS)] and overestimates downwelling TOA SW radiation on
+the order of 10 Wm$^\mathrm{-2}$ in  [relative to the Clouds and the Earth’s
+Radiant Energy System (CERES)] in the highest model resolution run (2.5 km).
+\cite{zhao2022} reported a similar SW radiation bias in five analysed CMIP6
+models over high-latitude SO and total CF underestimation on the order of 10\%
+over the entire 40--60$^\circ$S SO.
+
+In general, SST biases in the SO can originate either in the atmosphere, caused
+by too much shortwave heating of the surface, too little longwave cooling of
+the surface, or in the ocean circulation.  Interactions of both are also
+possible, due to, for example SST affecting clouds and clouds affecting the
+surface radiation.  \cite{zhang2023} have shown that SST biases have improved
+in CMIP6 compared to CMIP5 (relative to ERA5), with SST overall increasing in
+the later CMIP phase. However, over the SO this resulted in an even higher
+positive bias, especially in the Atlantic Ocean (AO) sector of the SO,
+increasing by up to 1$^\circ$C.  \cite{luo2023} identified that the SO SST bias
+in an ensemble of 18 CMIP6 models originates not from the surface heat and
+radiation fluxes (using reanalyses as a reference), but from a warm bias in the
+Northern Atlantic Deep Water.
+
+The main aim of our research is to evaluate the GSRM version of ICON, developed
+jointly by nextGEMS, Deutscher Wetterdienst (DWD) and the Max-Planck-Institute
 for Meteorology (MPI-M). Previous studies have identified substantial
-large-scale biases in climate model clouds over the Southern Ocean (SO), affecting
-sea surface temperature and the Earth’s albedo overall. Our aim is to quantify
-how well the high-resolution ICON model is simulating clouds in this region,
-particularly in light of the fact that subgrid-scale clouds are not
+large-scale biases in climate model clouds over the Southern Ocean (SO),
+affecting sea surface temperature and the Earth’s albedo overall. Our aim is to
+quantify how well the high-resolution ICON model is simulating clouds in this
+region, particularly in light of the fact that subgrid-scale clouds are not
 parameterised in this model. This region is mostly dominated by boundary layer
@@
 spaceborne lidar and radars, which are affected by attenuation by overlapping
-and thick clouds and ground clutter, respectively. Therefore, we chose to use
-a large set of ship-based observations conducted with ceilometers and lidars on
-board of the RV \emph{Polarstern} and other voyages and stations.
-
-Marine clouds have disproportionate effect on TOA shortwave radiation due to
-the relatively low albedo of the sea surface. The longitudinal symmetry of the
-SO means that model cloud biases tend to be similar across
-longitudes.
+and thick clouds and ground clutter, respectively.  Specifically, the radar on
+CloudSat and lidar on CALIPSO are affected by the abovementioned issues,
+resulting in a strong underestimation of cloud occurrence below 2 km relative to
+ground-based lidar observations \citep{mcerlich2021}.  This, in turn, can lead to
+systematic biases in low clouds in climate models, which are frequently
+evaluated against CloudSat--CALIPSO products. Reanalyses can also suffer from
+cloud biases, as these are usually parametrised in their atmospheric component,
+and also in regions where input observations are sparse.  This makes them a
+problematic reference for clouds over the SO, and any biases relative to a
+reanalysis should be interpreted with caution. Instead, we chose to use a large
+set of ship-based observations conducted with ceilometers and lidars on board
+of the RV \emph{Polarstern} and other voyages and stations as a reference for
+the model evaluation.
 
@@
 \includegraphics[width=0.65\textwidth]{img/map.png}
-\caption{A map showing the tracks of 31 voyages of RV \emph{Polarstern}, RSV \emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B.
-Palmer} and HMNZS \emph{Wellington} and one sub-Antractic station (Macquarie Island) analysed here.
-The tracks cover Antarctic sectors south of South Americ, the Atlantic Ocean, Africa, Australia and New Zealand in the years 2010 to 2021.}
+\caption{
+A map showing the tracks of 31 voyages of RV \emph{Polarstern}, RSV
+\emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B. Palmer}, and
+HMNZS \emph{Wellington} and one sub-Antarctic station (Macquarie Island)
+analysed here. The tracks cover Antarctic sectors south of South America, the
+Atlantic Ocean, Africa, Australia, and New Zealand in the years 2010 to 2021.
+The dashed line at 40$^\circ$S delineates the Southern Ocean area of our
+analysis.
+}
 \label{fig:map}
@@
 Together, we analysed data from 31 voyages of RV \emph{Polarstern}, RSV
-\emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B. Palmer},
-HMNZS \emph{Wellington} and one sub-Antarctic station (Macquarie Island) in the
-SO south of 40°S between year 2010 and 2021 (Fig. \ref{fig:map} and
-Table \ref{tab:voyages}). Altogether, the voyages and the station comprised
-2421 days of data south of 40$^\circ$S, but the availability of ceilometer data
-was smaller.
+\emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B. Palmer}, Her
+Majesty's New Zealand Ship (HMNZS) \emph{Wellington} and one sub-Antarctic
+station (Macquarie Island) in the SO south of 40°S between year 2010 and 2021
+(Fig. \ref{fig:map} and Table \ref{tab:voyages}). Altogether, the voyages and
+the station comprised 2421 days of data south of 40$^\circ$S, but the
+availability of ceilometer data was smaller.
 
@@
 
-A coupled storm-resolving version of the ICON model is in development by the
-NextGEMS project \citep{hohenegger2023}. NextGEMS has so far produced four
-cycles of model runs. In our research, we used a Cycle 3 run ngc3028 produced
-in 2023 \citep{nextgems2023a,nextgems2023b}. We could not use Cycle 4 due to unavailability of
-the necessary variables. The horizontal resolution of ngc3028 is about 5 km.
-Unlike current general circulation models (GCMs), the strom-resolving version
-of ICON does not use convective and cloud parameterisation but relies on
-explicit simulation of convection and clouds on the model grid. While this
-makes the code development simpler without having to rely on uncertain
-parameterisations, it can miss smaller-scale clouds below the grid resolution.
-Turbulence and cloud microphysics are still parameterised in this model. In our
-analysis, we used four years of coupled simulation output between years 2021
-and 2024 (inclusive). Because the model is free-running, weather and climate
+A coupled (atmosphere--ocean) GSRM version of the ICON model is in development
+by the nextGEMS project \citep{hohenegger2023}. nextGEMS has so far produced
+four cycles of model runs. In our research, we used a Cycle 3 run
+\emph{ngc3028} produced in 2023 \citep{nextgems2023a,nextgems2023b}. We could
+not use Cycle 4 due to unavailability of the necessary variables. The
+horizontal resolution of ngc3028 is about 5 km.  Unlike current general
+circulation models (GCMs), the strom-resolving version of ICON does not use
+convective and cloud parameterisation but relies on explicit simulation of
+convection and clouds on the model grid. While this makes the code development
+simpler without having to rely on uncertain parameterisations, it can miss
+smaller-scale clouds below the grid resolution.  Turbulence and cloud
+microphysics are still parameterised in this model. In our analysis, we used
+four years of coupled simulation output between years 2021 and 2024
+(inclusive). Because the model is free-running, weather and climate
 oscillations (such as the El Niño--Southern Oscillation) are not expected to be
@@
 observations at the same time of year and geographical location.
+
+ICON is a very versatile model, allowing for simulations ranging from
+coarse-resolution ESM simulations, GSRM simulations, limited area model (LAM)
+simulations, to large eddy simulations (LES), for both weather prediction and
+climate projections.
+
+ICON uses the atmospheric component ICON-A \citep{giorgetta2018}, whose
+physics is derived from ECHAM6 \citep{stevens2013}, and the ocean component
+ICON-O \citep{korn2022}.
+
+Earlier runs of the GSRM ICON from DYAMOND were evaluated by
+\cite{mauritsen2022}.
 
@@
 
+Similar to our results \cite{cesana2022} showed that CMIP6 also tend to
+underestimate cloud occurrence above 2 km over the SO, although their analysis
+in this case was limited to liquid clouds.
+
 \section{Conclusions}

### 2024-06-20 manuscript.tex
Cloud occurrence figure

@@
 \centering
-\includegraphics[width=0.5\textwidth]{img/cloud_occurrence.pdf}
-\caption{Cloud occurrence by height aggregated from the 31 voyages and one station
-for observations (OBS), the ICON mode, the MERRA-2 and ERA5 reanalyses. The
+\includegraphics[width=0.8\textwidth]{img/cloud_occurrence_agg.pdf}
+\caption{
+Cloud occurrence by height aggregated from the 31 voyages and one station for
+observations (OBS), the ICON model, and the MERRA-2 and ERA5 reanalyses. The
 total cloud fraction (CF) is shown in the legend. The ranges are from the
-16$^\mathrm{th}$ to the 84$^\mathrm{th}$ percentile.}
+16$^\mathrm{th}$ to the 84$^\mathrm{th}$ percentile. \textbf{(a)} all conditions,
+\textbf{(b)}, \textbf{(c)} cyclonic and non-cyclonic conditions as identified
+by cyclone tracking, \textbf{(d)}, \textbf{(e)} stable and unstable conditions
+as divided by the lower tropospheric stability criterion.
+}
 \label{fig:cloud-occurrence}

### 2024-06-24 manuscript.tex
Add a figure with AVBC example
Add photos to the map figure

@@
 \centering
-\includegraphics[width=0.65\textwidth]{img/map.png}
+\includegraphics[width=\textwidth]{img/map-fig.png}
 \caption{
-A map showing the tracks of 31 voyages of RV \emph{Polarstern}, RSV
+\textbf{(a)} A map showing the tracks of 31 voyages of RV \emph{Polarstern}, RSV
 \emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B. Palmer}, and
@@
 The dashed line at 40$^\circ$S delineates the Southern Ocean area of our
-analysis.
+analysis. A photo of \textbf{(b)} RV \emph{Polarstern} (© Folke
+Mehrtens/Alfred-Wegener-Institut), \textbf{(c)} Lufft CHM 15k installed on RV
+\emph{Tangaroa} (© Peter Kuma), \textbf{(d)} Vaisala CL51 install at the
+Macquarie Island station (© Jeﬀ Aquilina, Bureau of Meteorology).
+% TODO: Ask for photo permission and info about license.
 }
 \label{fig:map}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{img/example.png}
+\caption{
+An example of attenuated volume backscattering coefficient (AVBC) measured by
+CL51 during 24 hours on the PS81/3 voyage and an equivalent AVBC simulated with
+the ALCF from ERA5 data during the same time period. Shown is also the cloud
+mask determined by the ALCF.
+}
+\label{fig:example}
 \end{figure}
@@
 
-Together, we analysed data from 31 voyages of RV \emph{Polarstern}, RSV
-\emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B. Palmer}, Her
-Majesty's New Zealand Ship (HMNZS) \emph{Wellington} and one sub-Antarctic
-station (Macquarie Island) in the SO south of 40°S between year 2010 and 2021
-(Fig. \ref{fig:map} and Table \ref{tab:voyages}). Altogether, the voyages and
-the station comprised 2421 days of data south of 40$^\circ$S, but the
-availability of ceilometer data was smaller.
+Together, we analysed data from 31 voyages of RV \emph{Polarstern}, resupply
+vessel (RSV) \emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B.
+Palmer}, Her Majesty's New Zealand Ship (HMNZS) \emph{Wellington} and one
+sub-Antarctic station (Macquarie Island) in the SO south of 40°S between year
+2010 and 2021 (Fig. \ref{fig:map} and Table \ref{tab:voyages}). Altogether, the
+voyages and the station comprised 2421 days of data south of 40$^\circ$S, but
+the availability of ceilometer data was smaller.
 

### 2024-06-24 manuscript.tex
Add LTS figure

@@
 mask determined by the ALCF.
+}
+\label{fig:example}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{img/lts-dist.pdf}
+\caption{
+Lower tropospheric stability (LTS) distribution in \textbf{(a)} ERA5 and
+\textbf{(b)} MERRA-2 calculated for the 31 voyage tracks and one station from
+the highest instantaneous temporal resolution data. Shown is also the chosen
+dividing threshold of 12 K for `stable' and `unstable' conditions.
 }

### 2024-06-24 manuscript.tex
Improve example figure

@@
 \caption{
-An example of attenuated volume backscattering coefficient (AVBC) measured by
-CL51 during 24 hours on the PS81/3 voyage and an equivalent AVBC simulated with
-the ALCF from ERA5 data during the same time period. Shown is also the cloud
-mask determined by the ALCF.
+An example of attenuated volume backscattering coefficient (AVBC) \textbf{(a)}
+measured by CL51 during 24 hours on the PS81/3 voyage and \textbf{(b)} an
+equivalent AVBC simulated with the ALCF from ERA5 data during the same time
+period. Shown is also the cloud mask determined by the ALCF.
 }

### 2024-08-05 manuscript.tex
Various changes and additions

@@
 
-\begin{center} \Large \sffamily\textbf{Using ship observations to assess Southern Ocean clouds in a storm-resolving general circulation model ICON}\\[0.4cm]
+\begin{center} \Large \sffamily\textbf{Using ship observations to assess Southern Ocean clouds in the storm-resolving general circulation model ICON}\\[0.4cm]
 \large Peter Kuma$^\mathsf{1,}$*, Frida A.-M. Bender$^\mathsf{1}$, Adrian J. McDonald$^\mathsf{2}$ and Thorsten Mauritsen$^\mathsf{1}$\\[0.4cm]
@@
 Currently, a new generation of km-scale (also called `k-scale') resolution
-global climate models are in development as the forthcoming phase of climate
+global climate models is in development as the forthcoming phase of climate
 modelling. One such model is a 5-km version of the Icosahedral Nonhydrostatic
-Weather and Climate Model (ICON) developed jointly by Deutscher Wetterdienst
-(DWD) and the Max-Planck-Institute for Meteorology (MPI-M). Because of the high
-resolution, most parametrisations, such as that of convection and clouds, can
-be avoided.
+Weather and Climate Model (ICON), developed jointly by the Deutscher
+Wetterdienst (DWD) and Max-Planck-Institute for Meteorology (MPI-M). Because of
+the high resolution, most parametrisations, such as those of convection and
+clouds, can be avoided.
 
@@
 respectively. Therefore, we choose to use a large set of ship-based
-observations conducted with ceilometers and lidars on board of Research Vessel
-(RV) \textit{Polarstern} and other voyages. Altogether, we analyse over 2000
-days (about 6 years) of data from 31 voyages and 1 sub-antarctic station
+observations conducted with ceilometers and lidars on board of the Research
+Vessel (RV) \textit{Polarstern} and other voyages. Altogether, we analyse over
+2000 days (about 6 years) of data from 31 voyages and 1 sub-antarctic station
 covering diverse longitudes of the SO. To achieve a like-for-like comparison
@@
 We show that the model underestimates the total cloud fraction by about 10\%,
-with overestimation of cloud below 2 km, and underestimation of cloud above 2
+with overestimation of cloud below 2 km and underestimation of cloud above 2
 km. The reanalyses also underestimate the total cloud fraction by about 20\%.
@@
 analysis. A photo of \textbf{(b)} RV \emph{Polarstern} (© Folke
-Mehrtens/Alfred-Wegener-Institut), \textbf{(c)} Lufft CHM 15k installed on RV
-\emph{Tangaroa} (© Peter Kuma), \textbf{(d)} Vaisala CL51 install at the
-Macquarie Island station (© Jeﬀ Aquilina, Bureau of Meteorology).
+Mehrtens, Alfred-Wegener-Institut), \textbf{(c)} Lufft CHM 15k installed on RV
+\emph{Tangaroa} (© Peter Kuma, University of Canterbury), \textbf{(d)} Vaisala
+CL51 installation at the Macquarie Island station (© Jeﬀ Aquilina, Bureau of
+Meteorology).
 % TODO: Ask for photo permission and info about license.
@@
 }
-\label{fig:example}
+\label{fig:lts-dist}
 \end{figure}
@@
 
+Missing days in the ceilometer data were HMNZSW16 (7 days): 24--27 November, 10
+December, 16--17 December 2016; MARCUS (3 days): 8, 10 November, 10 December;
+MCQ16-18 (9 days): 7--8, 29 June, 5, 16 July, 15 August, 17 October 2016, 11
+February, 21 March 2017; TAN1502 (1 day): 24 January.
+
 These data sources contained ceilometer (lidar) observations with the Vaisala
-CL51 operating at 910 nm and the Lufft CHM-15k operating at 1064 nm. A
+CL51 and CL31 operating at 910 nm and the Lufft CHM-15k operating at 1064 nm. A
 ceilometer is a low-power vertically pointing lidar with the purpose of
@@
 
-\subsection{Vaisala CL51}
+\subsection{Vaisala CL51 and CL31}
 
-The Vaisala CL51 is a ceilometer operating at a near-infrared wavelength of 910
-nm. The maximum range 15.4 km, vertical resolution 10 m, and the number of
-vertical levels is 1540. The wavelength is affected by water vapour absorption
-of about 20\% in the mid-latitudes \citep{wiegner2015,wiegner2019}.  The
-instrument data files containing uncalibrated backscatter were first converted
-to NetCDF with cl2nc (\url{https://github.com/peterkuma/cl2nc}) and then
-processed with the ALCF to produce a cloud mask and cloud occurrence by height
-and the total cloud fraction.
+The Vaisala CL51 and CL31 are ceilometers operating at a near-infrared
+wavelength of 910 nm. The maximum range 15.4 km (CL51), 7.7 km (CL31 with 5 m
+vertical resolution) and 7.550 (CL31 with 10 m vertical resolution).
+The vertical resolution is 10 m (5 m configurable). The wavelength is affected
+by water vapour absorption of about 20\% in the mid-latitudes
+\citep{wiegner2015,wiegner2019}.  The instrument data files containing
+uncalibrated backscatter were first converted to NetCDF with cl2nc
+(\url{https://github.com/peterkuma/cl2nc}) and then processed with the ALCF to
+produce a cloud mask and cloud occurrence by height and the total cloud
+fraction. CL51 can also be configured to emulate CL31.
+
+For the MARCUS voyage, Vaisala CL31 were made available by the Atmospheric
+Radiation Measurement (ARM) processed to a maximum range of 7.545 km, vertical
+resolution of 30 m and 252 vertical levels.
 
@@
 
+The Modern-Era Retrospective analysis for Research and Applications, Version 2
+(MERRA-2) is a reanalysis produced by the Global Modeling and Assimilation
+Office at the NASA Goddard Space Flight Center \citep{gelaro2017}.  It uses
+version 5.12.4 of the Goddard Earth Observing System (GEOS) atmospheric
+model \citep{rienecker2008,molod2015}. The reanalysis output analysed here is
+available at a spatial resolution of 0.5° in latitude and 0.625° in longitude,
+which is about 56 km in the North--South direction and 35 km in the East--West
+direction at 60°S. The number of vertical model levels is 72, which we
+interpolate to height levels as needed. In our analysis we use the following
+products: 1-hourly instantaneous 2D single-level diagnostics (M2I1NXASM) for
+2-m temperature and humidity; 3-hourly instantaneous 3D assimilated
+meteorological fields (M2I3NVASM) for cloud quantities, pressure and
+temperature; 1-hourly average 2D surface flux diagnostics (M2T1NXFLX) for
+precipitation and sea ice; and 1-hourly average 2D radiation diagnostics
+(M2T1NXRAD) for radiation quantities \citep{merra2}.
+
 \subsection{ERA5}
@@
 prediction (NWP) model Integrated Forecast System (IFS) version CY41R2.  The
-horizontal resolution is 0.25$^\circ$ in latitude and longitude (about 28 km in
-the North--South direction and 14 km in the East--West direction at
-60$^\circ$S). The model uses 137 vertical levels.
+horizontal resolution is 0.25$^\circ$ in latitude and longitude, which is about
+28 km in the North--South direction and 14 km in the East--West direction at
+60$^\circ$S. The model uses 137 vertical levels. In our analysis we use output
+at one hourly instantaeous time intervals, except for radiation quantities,
+which are accumulations (from these we calculate daily means).
+Vertically-resolved quantities are specified on pressure levels. We interpolate
+these quantities to height levels as needed.
 
@@
 Abbreviations: ceilometer (ceil.), Australia (AU), New Zealand (NZ), South America (SA), Atlantic Ocean (AO) and Africa (AF).
-The number of days is rounded to the nearest integer.}
+The number of days is rounded to the nearest integer.
+CL51/31 indicates CL51 configured to emulate CL31.}
 \label{tab:voyages}
@@
 HMNZSW16 & HMNZS \emph{Wellington}       & CHM 15k & NZ       & 2016-11-23 & 2016-12-19 & 27 \\
-MARCUS   & RSV \emph{Aurora Australis}   & CL51    & AU       & 2017-10-29 & 2018-03-26 & 149\\
+MARCUS   & RSV \emph{Aurora Australis}   & CL31    & AU       & 2017-10-29 & 2018-03-26 & 149\\
 MCQ16-18 & /                             & CL51    & AU/NZ    & 2016-04-03 & 2018-03-14 & 710\\
@@
 PS124    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2021-02-03 & 2021-03-30 & 55 \\
-TAN1502  & RV \emph{Tangaroa}            & CL51    & NZ       & 2015-01-20 & 2015-03-12 & 51 \\
+TAN1502  & RV \emph{Tangaroa}            & CL51/31 & NZ       & 2015-01-20 & 2015-03-12 & 51 \\
 TAN1702  & RV \emph{Tangaroa}            & CHM 15k & NZ       & 2017-03-09 & 2017-03-31 & 23 \\

### 2024-08-07 manuscript.tex
Multiple updates and additions

@@
 
+\subsection{CERES}
+
+TOA radiation quantities are taken from the Clouds and the Earth’s Radiant
+Energy System (CERES) instruments on board of the Terra and Aqua satellites
+\citep{wielicki1996,loeb2018}. In our analysis we use the adjusted all sky SW
+and LW upwelling fluxes at TOA from the synoptic TOA and surface fluxes and
+clouds 1 degree daily edition 4A product
+(CER\_SYN1deg-Day\_Terra-Aqua-MODIS\_Edition4A)
+\citep{doelling2013,doelling2016}.
+
 \subsection{Cyclone tracking}
@@
 satisfactory for the purpose of filtering precipitation profiles.
+
+\subsection{Data processing}
+
+The radiation calculations were done in such a way that they always represent
+averages of daily means. This is done in order to be consistent with the CERES
+SYN1deg data, which are expressed as daily means. Therefore, for every
+instantaneous profile in the simulated lidar data is assigned a daily mean
+radiation value corresonding to theo the day (in UTC). In turn, the average
+radiation during the entire voyage or station measurement is calculated as the
+average of the profile values. In the observed lidar data, the daily mean
+radiation value is taken from the spatially and temporally co-located CERES
+SYN1deg data for the day (in UTC). The voyage or station measurement average
+is calculated in the same way.
 
@@
 \label{fig:cloud-occurrence}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{img/clt_hist.pdf}
+\caption{
+Daily total cloud fraction histograms calculated as the average of all voyage
+and station histograms. The models and subsets are as in Fig.
+\ref{fig:cloud-occurrence}
+}
+\label{fig:clt-hist}
 \end{figure}
@@
 openly available from Copernicus Climate Data Store (CDS)
-(\url{https://cds.climate.copernicus.eu}).  The other voyage and station data
-are openly available on Zenodo (). Subsetted model and reanalysis data for the
-voyage tracks and the station and data processed with the ALCF are openly
+(\url{https://cds.climate.copernicus.eu}). The CERES products are available
+from the project website (\url{https://ceres.larc.nasa.gov}) and the NASA
+Atmospheric Science Data Centre
+(\url{https://asdc.larc.nasa.gov/project/CERES}).  The other voyage and station
+data are openly available on Zenodo (). Subsetted model and reanalysis data for
+the voyage tracks and the station and data processed with the ALCF are openly
 available on Zenodo ().

### 2024-08-07 manuscript.tex
Figure improvements

@@
 \centering
-\includegraphics[width=0.8\textwidth]{img/cloud_occurrence_agg.pdf}
+\includegraphics[width=0.75\textwidth]{img/cloud_occurrence_agg.pdf}
 \caption{
-Cloud occurrence by height aggregated from the 31 voyages and one station for
-observations (OBS), the ICON model, and the MERRA-2 and ERA5 reanalyses. The
-total cloud fraction (CF) is shown in the legend. The ranges are from the
-16$^\mathrm{th}$ to the 84$^\mathrm{th}$ percentile. \textbf{(a)} all conditions,
-\textbf{(b)}, \textbf{(c)} cyclonic and non-cyclonic conditions as identified
-by cyclone tracking, \textbf{(d)}, \textbf{(e)} stable and unstable conditions
-as divided by the lower tropospheric stability criterion.
-}
+Cloud occurrence by height calculated as the average of all voyages and stations
+for the observed (OBS) and simulated lidar cloud mask. The total cloud fraction
+(CF), average shortwave (SW) and longwave (LW) are shown in the legend. The
+bands span the 16$^\mathrm{th}$--84$^\mathrm{th}$ percentile calculated from
+the set of all voyages and stations. The subsets \textbf{(a--g)} are described
+in the text (Section \ref{sec:results}).}
 \label{fig:cloud-occurrence}
@@
 Daily total cloud fraction histograms calculated as the average of all voyage
-and station histograms. The models and subsets are as in Fig.
-\ref{fig:cloud-occurrence}
+and station histograms. The total cloud fraction of a day (UTC) is calculated
+as a fraction of cloudy (based on the cloud mask) observed (OBS) or simulated
+lidar profiles. The models and subsets are as in Fig.
+\ref{fig:cloud-occurrence}.
 }

### 2024-08-08 manuscript.tex
Rename figure file
Improve figure file names
Improve map figure and replace degree symbols

@@
 means that model cloud biases tend to be similar across longitudes.  Here, we
-will conventionally refer to the SO as ocean regions south of 40$^\circ$S,
-low-latitude SO as 40--55$^\circ$S and high-latitude SO as south of
-55$^\circ$S.
+will conventionally refer to the SO as ocean regions south of 40°S,
+low-latitude SO as 40--55°S and high-latitude SO as south of
+55°S.
 
@@
 models over high-latitude SO and total CF underestimation on the order of 10\%
-over the entire 40--60$^\circ$S SO.
+over the entire 40--60°S SO.
 
@@
 positive bias, especially in the Atlantic Ocean (AO) sector of the SO,
-increasing by up to 1$^\circ$C.  \cite{luo2023} identified that the SO SST bias
+increasing by up to 1°C.  \cite{luo2023} identified that the SO SST bias
 in an ensemble of 18 CMIP6 models originates not from the surface heat and
@@
 \centering
-\includegraphics[width=\textwidth]{img/map-fig.png}
+\includegraphics[width=\textwidth]{img/map_fig.png}
 \caption{
-\textbf{(a)} A map showing the tracks of 31 voyages of RV \emph{Polarstern}, RSV
-\emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B. Palmer}, and
-HMNZS \emph{Wellington} and one sub-Antarctic station (Macquarie Island)
+\textbf{(a)} A map showing the tracks of 31 voyages of RV \emph{Polarstern},
+RSV \emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B. Palmer},
+and HMNZS \emph{Wellington} and one sub-Antarctic station (Macquarie Island)
 analysed here. The tracks cover Antarctic sectors south of South America, the
 Atlantic Ocean, Africa, Australia, and New Zealand in the years 2010 to 2021.
-The dashed line at 40$^\circ$S delineates the Southern Ocean area of our
-analysis. A photo of \textbf{(b)} RV \emph{Polarstern} (© Folke
-Mehrtens, Alfred-Wegener-Institut), \textbf{(c)} Lufft CHM 15k installed on RV
+The dotted and dashed lines at 40°S and 55°S delineate the Southern
+Ocean area of our analysis and its partitioning into two subsets, respectively.
+A photo of \textbf{(b)} RV \emph{Polarstern} (© Folke Mehrtens,
+Alfred-Wegener-Institut), \textbf{(c)} Lufft CHM 15k installed on RV
 \emph{Tangaroa} (© Peter Kuma, University of Canterbury), \textbf{(d)} Vaisala
@@
 \centering
-\includegraphics[width=\textwidth]{img/lts-dist.pdf}
+\includegraphics[width=\textwidth]{img/lts_dist.pdf}
 \caption{
@@
 2010 and 2021 (Fig. \ref{fig:map} and Table \ref{tab:voyages}). Altogether, the
-voyages and the station comprised 2421 days of data south of 40$^\circ$S, but
+voyages and the station comprised 2421 days of data south of 40°S, but
 the availability of ceilometer data was smaller.
@@
 prediction (NWP) model Integrated Forecast System (IFS) version CY41R2.  The
-horizontal resolution is 0.25$^\circ$ in latitude and longitude, which is about
+horizontal resolution is 0.25° in latitude and longitude, which is about
 28 km in the North--South direction and 14 km in the East--West direction at
-60$^\circ$S. The model uses 137 vertical levels. In our analysis we use output
+60°S. The model uses 137 vertical levels. In our analysis we use output
 at one hourly instantaeous time intervals, except for radiation quantities,
@@
 \caption{List of voyages and stations.
-Start, end and days (UTC; inclusive) indicate the time period when the vessel was south of 40$^\circ$S.
+Start, end and days (UTC; inclusive) indicate the time period when the vessel was south of 40°S.
 Abbreviations: ceilometer (ceil.), Australia (AU), New Zealand (NZ), South America (SA), Atlantic Ocean (AO) and Africa (AF).
@@
 \centering
-\includegraphics[width=0.75\textwidth]{img/cloud_occurrence_agg.pdf}
+\includegraphics[width=0.75\textwidth]{img/cl_agg.pdf}
 \caption{

### 2024-08-14 manuscript.tex
Voyage references and small edits

@@
 December, 16--17 December 2016; MARCUS (3 days): 8, 10 November, 10 December;
-MCQ16-18 (9 days): 7--8, 29 June, 5, 16 July, 15 August, 17 October 2016, 11
+MICRE (9 days): 7--8, 29 June, 5, 16 July, 15 August, 17 October 2016, 11
 February, 21 March 2017; TAN1502 (1 day): 24 January.
@@
 28 km in the North--South direction and 14 km in the East--West direction at
-60°S. The model uses 137 vertical levels. In our analysis we use output
-at one hourly instantaeous time intervals, except for radiation quantities,
-which are accumulations (from these we calculate daily means).
-Vertically-resolved quantities are specified on pressure levels. We interpolate
-these quantities to height levels as needed.
+60°S. Internally, the model uses 137 vertical levels. In our analysis we use
+output at one hourly instantaeous time intervals, except for radiation
+quantities, which are accumulations (from these we calculate daily means).
+Vertically-resolved quantities are made available on 37 pressure levels. We
+interpolate these quantities to height levels as needed.
 
@@
 \hline
-AA15-16  & RSV \emph{Aurora Australis}   & CL51    & AU       & 2015-10-22 & 2016-02-22 & 124\\
+AA15-16  & RSV \emph{Aurora Australis}   & CL51    & AU       & 2015-10-22 & 2016-02-22 & 124 \\
 HMNZSW16 & HMNZS \emph{Wellington}       & CHM 15k & NZ       & 2016-11-23 & 2016-12-19 & 27 \\
-MARCUS   & RSV \emph{Aurora Australis}   & CL31    & AU       & 2017-10-29 & 2018-03-26 & 149\\
-MCQ16-18 & /                             & CL51    & AU/NZ    & 2016-04-03 & 2018-03-14 & 710\\
+MARCUS   & RSV \emph{Aurora Australis}   & CL31    & AU       & 2017-10-29 & 2018-03-26 & 149 \\
+MICRE    & [Macquarie Is. station]       & CL51    & AU/NZ    & 2016-04-03 & 2018-03-14 & 710 \\
 NBP1704  & RV \emph{Nathaniel B. Palmer} & CHM 15k & NZ       & 2017-04-14 & 2017-06-08 & 55 \\
@@
 
+\begin{table}
+\caption{List of voyages and station references.}
+\label{tab:voyage-references}
+\small
+\begin{tabular}{ll}
+Name & References\\
+\hline
+AA15-16  & \cite{klekociuk2020} \\
+MARCUS   & \cite{mcfarquhar2016,mcfarquhar2019} \\
+MICRE    & \cite{marchand2015,marchand2020} \\
+PS77/2   & \cite{kniglanglo2011a,kniglanglo2011b,kniglanglo2011c,kniglanglo2014a,fahrbach2011} \\
+PS77/3   & \cite{kniglanglo2011d,kniglanglo2011e,kniglanglo2012a,kniglanglo2014b,knust2011} \\
+PS79/2   & \cite{kniglanglo2012b,kniglanglo2012c,kniglanglo2012d,kniglanglo2014c,kattner2012} \\
+PS79/3   & \cite{kniglanglo2012e,kniglanglo2012f,kniglanglo2012g,kniglanglo2014d,wolfgladrow2012} \\
+PS79/4   & \cite{kniglanglo2012h,kniglanglo2012i,kniglanglo2012j,kniglanglo2014e,lucassen2012} \\
+PS81/2   & \cite{kniglanglo2013a,kniglanglo2013b,kniglanglo2013c,kniglanglo2014f,boebel2013} \\
+PS81/3   & \cite{kniglanglo2013d,kniglanglo2013e,kniglanglo2013f,kniglanglo2014g,gutt2013} \\
+PS81/4   & \cite{kniglanglo2013g,kniglanglo2013h,kniglanglo2013i,kniglanglo2014f,bohrmann2013} \\
+PS81/5   & \cite{kniglanglo2013j,kniglanglo2013k,kniglanglo2013l,kniglanglo2014g,jokat2013} \\
+PS81/6   & \cite{kniglanglo2013m,kniglanglo2013n,kniglanglo2013o,kniglanglo2014h,lemke2013} \\
+PS81/7   & \cite{kniglanglo2013p,kniglanglo2013q,kniglanglo2014i,kniglanglo2016a,meyer2013} \\
+PS81/8   & \cite{kniglanglo2013r,kniglanglo2014j,kniglanglo2014k,kniglanglo2014l,schlindwein2014} \\
+PS81/9   & \cite{kniglanglo2014m,kniglanglo2014n,kniglanglo2014o,kniglanglo2014p,knust2014} \\
+PS89     & \cite{kniglanglo2015a,kniglanglo2015b,kniglanglo2015c,kniglanglo2015d,boebel2016}\\
+PS96     & \cite{kniglanglo2016b,kniglanglo2016c,kniglanglo2016d,kniglanglo2016e,schrder2017} \\
+PS97     & \cite{kniglanglo2016f,kniglanglo2016g,kniglanglo2016h,kniglanglo2016i,lamy2017} \\
+PS103    & \cite{kniglanglo2017a,kniglanglo2017b,kniglanglo2017c,kniglanglo2017d,boebel2018} \\
+PS104    & \cite{kniglanglo2017e,kniglanglo2017f,kniglanglo2017g,gohl2018,schmithsen2021a} \\
+PS111    & \cite{schmithsen2019a,schmithsen2020a,schmithsen2021b,schmithsen2021c,schrder2018} \\
+PS112    & \cite{schmithsen2019b,schmithsen2020b,schmithsen2021d,schmithsen2021e,meyer2018} \\
+PS117    & \cite{schmithsen2019c,schmithsen2020c,schmithsen2021f,schmithsen2021g,boebel2019} \\
+PS118    & \cite{schmithsen2019d,schmithsen2020d,schmithsen2021h,schmithsen2021i,dorschel2019} \\
+PS123    & \cite{schmithsen2021j,schmithsen2021m,schmithsen2021n,schmithsen2021k,hoppmann2023} \\
+PS124    & \cite{schmithsen2021o,schmithsen2021q,schmithsen2021p,hoppmann2023} \\
+TAN1802  & \cite{kremser2021} \\
+\end{tabular}
+\end{table}
+
 \begin{figure}
@@
 \caption{Cloud occurrence by height for the 31 voyages and one sub-Antarctic
-station (MCQ16-18) in observations (OBS), and simulated by the ALCF from the
+station (MICRE) in observations (OBS), and simulated by the ALCF from the
 ICON model, MERRA‐2 (M2) and ERA5 reanalysis data. The numbers in the legend

### 2024-08-14 manuscript.tex
Voyage references

--- 2024-08-08 manuscript.tex
@@
 sub-Antarctic station (Macquarie Island) in the SO south of 40°S between year
-2010 and 2021 (Fig. \ref{fig:map} and Table \ref{tab:voyages}). Altogether, the
-voyages and the station comprised 2421 days of data south of 40°S, but
-the availability of ceilometer data was smaller.
+2010 and 2021 (Fig. \ref{fig:map}, Table \ref{tab:voyages} and
+\ref{tab:voyage-references}). Altogether, the voyages and the station comprised
+2421 days of data south of 40°S, but the availability of ceilometer data was
+smaller.
 
@@
 \begin{tabular}{llllllr}
-Name & Vessel & Ceil. & Region & Start & End & Days\\
+\textbf{Name} & \textbf{Vessel} & \textbf{Ceil.} & \textbf{Region} & \textbf{Start} & \textbf{End} & \textbf{Days}\\
 \hline
-AA15-16  & RSV \emph{Aurora Australis}   & CL51    & AU       & 2015-10-22 & 2016-02-22 & 124\\
+AA15-16  & RSV \emph{Aurora Australis}   & CL51    & AU       & 2015-10-22 & 2016-02-22 & 124 \\
 HMNZSW16 & HMNZS \emph{Wellington}       & CHM 15k & NZ       & 2016-11-23 & 2016-12-19 & 27 \\
-MARCUS   & RSV \emph{Aurora Australis}   & CL31    & AU       & 2017-10-29 & 2018-03-26 & 149\\
-MCQ16-18 & /                             & CL51    & AU/NZ    & 2016-04-03 & 2018-03-14 & 710\\
+MARCUS   & RSV \emph{Aurora Australis}   & CL31    & AU       & 2017-10-29 & 2018-03-26 & 149 \\
+MICRE    & [Macquarie Is. station]       & CL51    & AU/NZ    & 2016-04-03 & 2018-03-14 & 710 \\
 NBP1704  & RV \emph{Nathaniel B. Palmer} & CHM 15k & NZ       & 2017-04-14 & 2017-06-08 & 55 \\
@@
 
+\begin{table}
+\caption{List of voyage and station references.}
+\label{tab:voyage-references}
+\small
+\begin{tabular}{lp{13cm}}
+\textbf{Name} & \textbf{References}\\
+\hline
+AA15-16  & \cite{klekociuk2020} \\
+MARCUS   & \cite{mcfarquhar2016,mcfarquhar2019,zhang2017,keeler2017,walton2017,cromwell2017} \\
+MICRE    & \cite{marchand2015,marchand2020,zhang2016} \\
+PS77/2   & \cite{kniglanglo2011a,kniglanglo2011b,kniglanglo2011c,kniglanglo2014a,fahrbach2011} \\
+PS77/3   & \cite{kniglanglo2011d,kniglanglo2011e,kniglanglo2012a,kniglanglo2014b,knust2011} \\
+PS79/2   & \cite{kniglanglo2012b,kniglanglo2012c,kniglanglo2012d,kniglanglo2014c,kattner2012} \\
+PS79/3   & \cite{kniglanglo2012e,kniglanglo2012f,kniglanglo2012g,kniglanglo2014d,wolfgladrow2012} \\
+PS79/4   & \cite{kniglanglo2012h,kniglanglo2012i,kniglanglo2012j,kniglanglo2014e,lucassen2012} \\
+PS81/2   & \cite{kniglanglo2013a,kniglanglo2013b,kniglanglo2013c,kniglanglo2014f,boebel2013} \\
+PS81/3   & \cite{kniglanglo2013d,kniglanglo2013e,kniglanglo2013f,kniglanglo2014g,gutt2013} \\
+PS81/4   & \cite{kniglanglo2013g,kniglanglo2013h,kniglanglo2013i,kniglanglo2014f,bohrmann2013} \\
+PS81/5   & \cite{kniglanglo2013j,kniglanglo2013k,kniglanglo2013l,kniglanglo2014g,jokat2013} \\
+PS81/6   & \cite{kniglanglo2013m,kniglanglo2013n,kniglanglo2013o,kniglanglo2014h,lemke2013} \\
+PS81/7   & \cite{kniglanglo2013p,kniglanglo2013q,kniglanglo2014i,kniglanglo2016a,meyer2013} \\
+PS81/8   & \cite{kniglanglo2013r,kniglanglo2014j,kniglanglo2014k,kniglanglo2014l,schlindwein2014} \\
+PS81/9   & \cite{kniglanglo2014m,kniglanglo2014n,kniglanglo2014o,kniglanglo2014p,knust2014} \\
+PS89     & \cite{kniglanglo2015a,kniglanglo2015b,kniglanglo2015c,kniglanglo2015d,boebel2016}\\
+PS96     & \cite{kniglanglo2016b,kniglanglo2016c,kniglanglo2016d,kniglanglo2016e,schrder2017} \\
+PS97     & \cite{kniglanglo2016f,kniglanglo2016g,kniglanglo2016h,kniglanglo2016i,lamy2017} \\
+PS103    & \cite{kniglanglo2017a,kniglanglo2017b,kniglanglo2017c,kniglanglo2017d,boebel2018} \\
+PS104    & \cite{kniglanglo2017e,kniglanglo2017f,kniglanglo2017g,gohl2018,schmithsen2021a} \\
+PS111    & \cite{schmithsen2019a,schmithsen2020a,schmithsen2021b,schmithsen2021c,schrder2018} \\
+PS112    & \cite{schmithsen2019b,schmithsen2020b,schmithsen2021d,schmithsen2021e,meyer2018} \\
+PS117    & \cite{schmithsen2019c,schmithsen2020c,schmithsen2021f,schmithsen2021g,boebel2019} \\
+PS118    & \cite{schmithsen2019d,schmithsen2020d,schmithsen2021h,schmithsen2021i,dorschel2019} \\
+PS123    & \cite{schmithsen2021j,schmithsen2021m,schmithsen2021n,schmithsen2021k,hoppmann2023} \\
+PS124    & \cite{schmithsen2021o,schmithsen2021q,schmithsen2021p,hoppmann2023} \\
+TAN1802  & \cite{kremser2020,kremser2021} \\
+\end{tabular}
+\end{table}
+
 \begin{figure}

### 2024-08-14 manuscript.tex
More references

--- 2024-08-08 manuscript.tex
@@
 
+\begin{table}
+\caption{List of voyage and station references.}
+\label{tab:voyage-references}
+\small
+\begin{tabular}{lp{14.5cm}}
+\textbf{Name} & \textbf{References}\\
+\hline
+AA15-16  & \cite{klekociuk2020} \\
+MARCUS   & \cite{mcfarquhar2016,mcfarquhar2019,zhang2017,keeler2017,walton2017,cromwell2017,mcfarquhar2021} \\
+MICRE    & \cite{marchand2015,marchand2020,zhang2016,mcfarquhar2021} \\
+PS77/2   & \cite{kniglanglo2011a,kniglanglo2011b,kniglanglo2011c,kniglanglo2014a,fahrbach2011} \\
+PS77/3   & \cite{kniglanglo2011d,kniglanglo2011e,kniglanglo2012a,kniglanglo2014b,knust2011} \\
+PS79/2   & \cite{kniglanglo2012b,kniglanglo2012c,kniglanglo2012d,kniglanglo2014c,kattner2012} \\
+PS79/3   & \cite{kniglanglo2012e,kniglanglo2012f,kniglanglo2012g,kniglanglo2014d,wolfgladrow2012} \\
+PS79/4   & \cite{kniglanglo2012h,kniglanglo2012i,kniglanglo2012j,kniglanglo2014e,lucassen2012} \\
+PS81/2   & \cite{kniglanglo2013a,kniglanglo2013b,kniglanglo2013c,kniglanglo2014f,boebel2013} \\
+PS81/3   & \cite{kniglanglo2013d,kniglanglo2013e,kniglanglo2013f,kniglanglo2014g,gutt2013} \\
+PS81/4   & \cite{kniglanglo2013g,kniglanglo2013h,kniglanglo2013i,kniglanglo2014f,bohrmann2013} \\
+PS81/5   & \cite{kniglanglo2013j,kniglanglo2013k,kniglanglo2013l,kniglanglo2014g,jokat2013} \\
+PS81/6   & \cite{kniglanglo2013m,kniglanglo2013n,kniglanglo2013o,kniglanglo2014h,lemke2013} \\
+PS81/7   & \cite{kniglanglo2013p,kniglanglo2013q,kniglanglo2014i,kniglanglo2016a,meyer2013} \\
+PS81/8   & \cite{kniglanglo2013r,kniglanglo2014j,kniglanglo2014k,kniglanglo2014l,schlindwein2014} \\
+PS81/9   & \cite{kniglanglo2014m,kniglanglo2014n,kniglanglo2014o,kniglanglo2014p,knust2014} \\
+PS89     & \cite{kniglanglo2015a,kniglanglo2015b,kniglanglo2015c,kniglanglo2015d,boebel2016}\\
+PS96     & \cite{kniglanglo2016b,kniglanglo2016c,kniglanglo2016d,kniglanglo2016e,schrder2017} \\
+PS97     & \cite{kniglanglo2016f,kniglanglo2016g,kniglanglo2016h,kniglanglo2016i,lamy2017} \\
+PS103    & \cite{kniglanglo2017a,kniglanglo2017b,kniglanglo2017c,kniglanglo2017d,boebel2018} \\
+PS104    & \cite{kniglanglo2017e,kniglanglo2017f,kniglanglo2017g,gohl2018,schmithsen2021a} \\
+PS111    & \cite{schmithsen2019a,schmithsen2020a,schmithsen2021b,schmithsen2021c,schrder2018} \\
+PS112    & \cite{schmithsen2019b,schmithsen2020b,schmithsen2021d,schmithsen2021e,meyer2018} \\
+PS117    & \cite{schmithsen2019c,schmithsen2020c,schmithsen2021f,schmithsen2021g,boebel2019} \\
+PS118    & \cite{schmithsen2019d,schmithsen2020d,schmithsen2021h,schmithsen2021i,dorschel2019} \\
+PS123    & \cite{schmithsen2021j,schmithsen2021m,schmithsen2021n,schmithsen2021k,hoppmann2023} \\
+PS124    & \cite{schmithsen2021o,schmithsen2021q,schmithsen2021p,hoppmann2023} \\
+TAN1802  & \cite{kremser2020,kremser2021} \\
+\end{tabular}
+\end{table}
+
 \begin{figure}

### 2024-08-16 manuscript.tex
Figure improvements

@@
 	urlcolor=blue,
-	pdftitle={Using ship observations to assess Southern Ocean clouds in a storm-resolving general circulation model ICON},
+	pdftitle={Ship and ground-based lidar and radiosonde evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON and the ERA5 and MERRA-2 reanalyses},
 	pdfauthor={Peter Kuma, Frida A.-M. Bender, Adrian J. McDonald and Thorsten Mauritsen}
@@
 
-\begin{center} \Large \sffamily\textbf{Using ship observations to assess Southern Ocean clouds in the storm-resolving general circulation model ICON}\\[0.4cm]
+\begin{center} \Large \sffamily\textbf{Ship and ground-based lidar and radiosonde evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON and the ERA5 and MERRA-2 reanalyses}\\[0.4cm]
 \large Peter Kuma$^\mathsf{1,}$*, Frida A.-M. Bender$^\mathsf{1}$, Adrian J. McDonald$^\mathsf{2}$ and Thorsten Mauritsen$^\mathsf{1}$\\[0.4cm]
@@
 \centering
-\includegraphics[width=0.75\textwidth]{img/cl_agg.pdf}
+\includegraphics[width=\textwidth]{img/cl_agg_exp.pdf}
 \caption{
@@
 \centering
-\includegraphics[width=0.8\textwidth]{img/radiosonde.pdf}
-\caption{Radiosonde proﬁles of potential temperature and lifting condensation
-level (LCL) on all RV \emph{Polarstern} voyages.}
-\label{fig:radiosonde}
+\includegraphics[width=0.72\textwidth]{img/theta_hur.pdf}
+\caption{
+Virtual potential temperature ($\theta_v$) and relative humidity (RH)
+determined from radiosonde launches and co-located profiles in
+ICON, ERA5 and MERRA-2 in subsets as in Fig. \ref{fig:cloud-occurrence}.
+The solid lines are the average calculated from the averages of every
+individual voyage and station. The bands span the
+16$^\mathrm{th}$--84$^\mathrm{th}$ percentiles calculated from the distribution
+of the voyage and station averages.
+}
+\label{fig:theta-hur}
 \end{figure}

### 2024-08-16 manuscript.tex
Results description

@@
 
+The observations show cloud occurrence peaking at the surface, whereas models
+show higher peak (at about 500 m). The models underestimate total cloud
+fraction by 10--20\%, and show a strong decrease in cloud occurrence near the
+surface, but this is not happening in the observations. ICON and ERA5
+overestimate cloud occurrence at the peak (between 0--1 km). Above 1 km, ICON
+and MERRA-2 understimate cloud occurrence, but ERA5 is very accurate. The too
+high peak in models is partly supported by the LCL distribution, which peaks
+higher in the models then in the observations (at the surface), although this
+is not very pronounced. The northern zone shows stronger peak of cloud
+occurrence near the surface than the southern zone, and this could be because
+higher latitudes have more unstable atmospheric profiles. The northern and
+southern zones show similar biases in models as in the general case, but ERA5
+does not overestimate the peak in the northern zone (near-surface cloud
+occurrence is still strongly understimated). Cyclonic situations have a larger
+amount observed cloudiness, including the peak and total cloud fraction. In
+these situations, the models are doing a relatively good job of getting the
+vertical profile of cloud occurrence right, but still tend to underestimate
+cloud occurrence above 1 km and near the surface. Non-cyclonic situations are
+similar to the general case. In stable stituations cloud occurrence peaks
+strongly at the surface in observations, compared to unstable situations, where
+the peak is more more obtuse and spread across 0--1 km. In stable situations
+the models are doing a fairly good job, but overestimate cloud occurrence at
+the peak below 1 km, above 1 km the show similar biases as in the general case.
+In unstable situations the bias in ICON is very pronounced, with a much
+stronger peak at about 500 m, ERA5 is underestimating cloud occurrence below 1
+km (especially near the surface), and MERRA-2 even more strongly. In all
+situations, even when the models overestimate cloud occurrence at some
+altitudes, they always substantially underestimate the total cloud fraction.
+ICON can be generally characterised as substantially overestimating cloud
+occurrence below 1 km and underestimating above, underestimating the total
+cloud fraction, and showing greatest biases in unstable and non-cyclonic
+conditition. It also shows peak of cloud occurrence at higher altitude than obs
+(500 m vs. near the surface) and correspondingly its LCL tends to be also
+higher. MERRA-2 can be generally characterised as underestimating cloud
+occurrence at nearly all altitudes as well as the total cloud fraction, but
+mostly above and below 500 m (the peak at 500 m is well-represented). It
+struggles the most in the northern zone, and in unstable situations. ERA5 can
+be generally characterised as representing cloud occurrence correctly above
+about 1--1.5 km, overestimating below, but underestimating near-surface cloud
+occurrence (0--500 m). The total cloud fraction is strongly understimated in
+all situations. It has tendency towards understimation in the northern zone and
+unstable stiuations, and conversely overestimating in the southern zone and
+stable conditions.
+
 \begin{figure}

### 2024-08-26 manuscript.tex
Multiple updates

@@
 2421 days of data south of 40°S, but the availability of ceilometer data was
-smaller.
+smaller due to gaps in measurements. Missing days in the ceilometer data were
+HMNZSW16 (7 days): 24--27 November, 10 December, 16--17 December 2016; MARCUS
+(3 days): 8, 10 November, 10 December; MICRE (9 days): 7--8, 29 June, 5, 16
+July, 15 August, 17 October 2016, 11 February, 21 March 2017; TAN1502 (1 day):
+24 January.
 
-Missing days in the ceilometer data were HMNZSW16 (7 days): 24--27 November, 10
-December, 16--17 December 2016; MARCUS (3 days): 8, 10 November, 10 December;
-MICRE (9 days): 7--8, 29 June, 5, 16 July, 15 August, 17 October 2016, 11
-February, 21 March 2017; TAN1502 (1 day): 24 January.
+These data sources contained ceilometer observations with the Vaisala CL51 and
+CL31 operating at 910 nm and the Lufft CHM-15k operating at 1064 nm, described
+in detail below (Sections \ref{sec:cl51} and \ref{sec:chm15k}). A ceilometer is
+a low-power near-infrared vertically pointing lidar with the purpose of
+measuring the cloud base, but it also measures the full vertical structure of
+clouds as long as the laser signal is not attenuated by thick clouds.
 
-These data sources contained ceilometer (lidar) observations with the Vaisala
-CL51 and CL31 operating at 910 nm and the Lufft CHM-15k operating at 1064 nm. A
-ceilometer is a low-power vertically pointing lidar with the purpose of
-measuring the cloud base, but it also measures the full vertical structure of
-clouds as long as the laser signal is not attenuated by thick clouds. A total
-of about 1500 days of lidar observations were included in our analysis.
-
-Apart from lidar observations, radiosondes were launched on weather balloons
-at regular synoptic times on the RV \emph{Polarstern} voyages, and surface
-meteorological quantities were measured continuously.
+Apart from lidar observations, radiosondes were launched on weather balloons at
+regular synoptic times on the RV \emph{Polarstern}, MARCUS, NBP17024, TAN1702,
+and TAN1802 voyage, measuring pressure, temperature, relative humidity and
+global navigation satellite system coordinates. Derived thermodynamic (virtual
+potential temperature, lifting condensation level, \ldots) and dynamic
+quantities (wind speed and direction) for the measured vertical profiles were
+calculated with rstool \citep{rstool}. Surface meteorological quantities were
+measured continuously by an onboard automatic weather station or individual
+instruments.
 
@@
 \subsection{Vaisala CL51 and CL31}
+\label{sec:cl51}
 
@@
 \subsection{Lufft CHM 15k}
+\label{sec:chm15k}
 
@@
 
-It was not possible to include precipitation simulation in the ALCF due to the
-absence of required fields in our model output and reanalysis data (liquid and
-ice precipitation mass mixing ratios) because the required radiation
-calculations are not implemented in the ALCF. At the same time, it is relatively
-difficult to distinguish precipitation backscatter from cloud backscatter
-in lidar observations, especially when only one wavelength channel and no
-polarisation channel are available.
+Precipitation can cause strong enough lidar backscattering to be recognised as
+a cloud by the cloud detection method used in the ALCF. This is undesirable
+if equivalent precipitation backscatter is not included in the simulated lidar
+profiles. It was not possible to include precipitation simulation in the ALCF
+due to the absence of required fields in the ICON model output and the
+reanalysis data, the liquid and ice precipitation mass mixing ratios, and
+because the required radiation calculations for precipitation are not
+implemented in the ALCF. In this situation, in order to achieve a fair
+comparison of observations and models, one should exclude profiles with
+precipitation either manually or using an automated method. It is relatively
+difficult to distinguish precipitation backscatter from cloud backscatter in
+lidar observations, especially when only one wavelength channel and no
+polarisation channel are available. In models, the same can be accomplished
+relatively easily by excluding profiles with an amount of surface precipitation
+flux exceeding a given threshold. In the observations, using precipitation
+flux measurements can be very unreliable on ships due to ship movement and
+turbulence caused by nearby ship structures. Our analysis of rain gauge data
+from the RV \emph{Tangaroa} showed large discrepancies between the rain gauge
+time series and human-performed synoptic observations, as well as large
+inconsistencies in the rain gauge time series. Therefore, it is desirable to
+implement a method of detecting precipitation from observed backscatter
+profiles instead.
 
-In order to get a fair comparison of observations and models, one needs to
-exclude profiles with precipitation either manually or using an automated
-method. In models, this can be accomplished relatively easily by excluding
-profiles with an amount of surface precipitation flux exceeding a threshold.
-In observations, this can be more complicated, especially on voyages, because
-rain gauges are known to be unreliable on ships.
-
-On the RV \emph{Polarstern} voyages, regular synoptic observations were
-available.  These included precipitation observations by an observer. We
-used this dataset to train a convolutional artiﬁcial neural network (ANN)
-of the U-Net type \citep{ronneberger2015} to recognise precipitation in the
-lidar data. Samples of short time intervals (10 min) of near-surface
-backscatter (0–250 m) were classified as clear, rain, snow and fog, using the
-synoptic observations as a training set. From these, a binary classification of
-profiles as wet or dry was derived.
+On the RV \emph{Polarstern} voyages, regular human-performed synoptic
+observations were available and included precipitation presence and type. We
+used this dataset to train a convolutional artiﬁcial neural network (ANN) of
+the U-Net type \citep{ronneberger2015} to recognise profiles with precipitation
+from lidar backscatter. Samples of short time intervals (10 min) of
+near-surface backscatter (0–250 m) were classified as clear, rain, snow and
+fog, using the synoptic observations as a training dataset. From these, a
+binary classification of profiles as wet (rain or fog) and dry (clear or fog)
+was derived.
 
@@
 \centering
-\includegraphics[width=\textwidth]{img/cl_agg_exp.pdf}
+\includegraphics[width=\textwidth]{img/cl_agg.pdf}
 \caption{
@@
 
-We compared about 2000 radiosonde proﬁles from 24 RV \emph{Polarstern}
+We analysed about 2300 radiosonde proﬁles south of 40°S from the 24 RV
+\emph{Polarstern} voyages, MARCUS, NBP1704, TAN1702, and TAN1802.
+
 voyages between the observations and the model. Proﬁles in the model were taken

### 2024-08-26 manuscript.tex
Multiple updates

@@
 cloud mask, cloud occurrence by height and the total cloud fraction are
-determined.
-
-ALCF has already been used by several research teams for model and reanalysis
-evaluation
+determined. ALCF has already been used by several research teams for model and
+reanalysis evaluation
 \citep{kuma2020,kremser2021,guyot2022,pei2023,whitehead2023,mcdonald2024}.
+Absolute calibration of the observed backscatter was performed by comparing
+the measured clear-sky molecular backscatter statistically with simulated
+clear-sky molecular backscatter.
 
@@
 
-% TODO: Describe absolute calibration.
-
 \subsection{Lufft CHM 15k}
@@
 
-% TODO: Describe absolute calibration.
 % TODO: Check sampling rate.
@@
 
-We used a cyclone tracking algorithm to identify extratropical and polar
+We partitioned our data into subsets by cyclonic activity. For this purpose,
+we used a cyclone tracking algorithm to identify extratropical and polar
 cyclones (ECs and PCs) over the SO in the reanalysis and ICON data,
-for the purpose of partitioning the cloud occurrence data into cyclonic and
-non-cyclonic conditions. We used the open source package CyTRACK
+We used the open source cylone tracking package CyTRACK
 \citep{perez-alarcon2024}. Generally, what constitutes an EC is considered
 relatively arbitrary due to a very large variability of ECs \citep{neu2013}.
-We used the mean sea level pressure field and horizontal wind speed fields
-as input to the CyTRACK algorithm. The algorithm uses pressure and wind
-speed thresholds as well as tracking across time steps to identify cyclone
-centres and radii.
+We used the mean sea level pressure field and horizontal wind speed fields as
+input to the CyTRACK algorithm. The algorithm uses pressure and wind speed
+thresholds as well as tracking across time steps to identify cyclone centres
+and radii. From this information, we could classify geographical areas as
+either cyclonic or non-cyclonic. Due to a relatively small total area covered,
+we chose a circle of a double radius (relative to one identified by CyTRACK)
+centred at the cyclone centre as a cyclonic area for every time step and
+cyclone. All other areas were identified as non-cyclonic.  For identifying
+cyclones in the observations, ERA5 pressure and wind fields were used as the
+input to CyTRACK. This is justified by the fact that large-scale pressure and
+wind fields are likely sufficiently close to the reality in ERA5. For
+identifying cyclones in ICON, ERA5, MERRA-2, their own pressure and wind fields
+were used as the input to CyTRACK.
+
+\subsection{Cloud occurrence by stability}
+
+We determine stability by calculating lower tropospheric stability (LTS)
+as the difference between potential temperature at 700 hPa and the surface.
+From a histogram of LTS in ERA5 and MERRA-2 calculated at all voyage tracks
+and the station (Fig. S1), we determined a dividing threshold of 12 K for
+relatively unstable (< 12 K) and relatively stable (>= 12 K) conditions.
 
@@
 
-\subsection{Cloud occurrence}
+\subsection{Cloud occurrence by height}
 
@@
 }
-\label{fig:clt-hist}
+\label{fig:cloud-cover}
 \end{figure}
+
+\subsection{Cloud cover}
+
+We analysed daily cloud cover (total cloud fraction) distribution. This is a
+measure of cloudiness irrespective of height. A cloud detected at any height
+means that the lidar profile was classified as cloudy, otherwise it was
+classified as clear sky. When all profiles in a day are aggregated together,
+the cloud cover for the day is determied as the fraction of cloudy profiles in
+the total number of profiles, expressed in octas.
+
+In Fig.  \ref{fig:cloud-cover} we show the results for the same subsets as
+anlysed above. Observations show the greatest representation of high cloud
+cover (5--8 octas), peaking at 7 octas. This is not represented by ICON or the
+reanalyses.  While ICON is the closest, it tends to be 1 octa clearer the
+observations, peaking at 6 octas, and highly understimating days with 8 octas.
+Overall, the reanalyses show results similar to each other, underestimating
+cloud cover by about 2 octas, and strongly understimating days with 7 and 8
+octas. Of the two reanalyses, MERRA-2 shows slightly higher cloud cover and
+thus more consistent with observations.
+
+When analysed by subsets, the cyclonic subset show to highest cloud cover, with
+8 octas occurring on one half of such days (Fig. \ref{fig:cloud-cover}d).  This
+is not represented by ICON or the reanalyses at all. Interestingly, clear sky
+days (0 octas) also have a local maximum peaking at about 15\% in this subset.
+When we contrast the low and high latitude zones, we see that the high latitude
+zone tends to have greater cloud cover, peaking at 8 octas (Fig.
+\ref{cloud-cover}c). The high latitue also has almost no clear sky or small
+cloud cover cases (0--4 octas). ICON and the reanalyses represent at least this
+charactertic of the distribution well for 0--3 octas, but otherwise show bises
+similar to the general case. One of the greatest biases is present in ERA5 in
+the unstable subset, where it peaks at 3 octas, whereas the observations peak
+at 7 octas and show negligible cloud cover below 5 octas.
 
@@
 We analysed about 2300 radiosonde proﬁles south of 40°S from the 24 RV
-\emph{Polarstern} voyages, MARCUS, NBP1704, TAN1702, and TAN1802.
+\emph{Polarstern} voyages, MARCUS, NBP1704, TAN1702, and TAN1802. Spatially and
+temporaly colocated profiles were taken from ICON and the reanalyses. Because
+the time period of the ICON model output was different from the observations,
+model time was chosen to be the same as the radiosonde launch time relative to
+the start of the year. The profiles were partitioned into the same subsets as
+the lidar observations: all, 40--55°S, 55+°S, cyclonic, non-cyclonic, stable,
+and unstable. The groups 40--55°S and 55+°S, cyclonic and non-cyclonic, and
+stable and unstable were mutually exclusive in pairs. Apart from relative
+humidity, we focus on comparing virtual potential temperature ($\theta_v$) due
+to its role in low-level tropospheric stability, being one of the primary
+factors affecting shallow convection and the associated low-level cloud
+formation and dissipation. The observed and model profiles of virtual potential
+temperature are shown in Fig. \ref{fig:potential-temperature}.
 
-voyages between the observations and the model. Proﬁles in the model were taken
-at the same geographical location and time relative to the start of the year.
-Only proﬁles for which the sea ice conditions (sea ice present or absent) are
-the same in the observations and the model were included. We derived potential
-temperature profiles, lifting condensation level (LCL), and aggregated the
-profiles by sea ice conditions (Fig. \ref{fig:radiosonde}).
+Overall, the mean $\theta_v$ is relatively well represented in ICON and MERRA-2,
+being only slightly colder in the mid-to-high troposophere (less stable) in ICON
+than in observations (Fig. \ref{fig:potential-temperature}a). Large differences exist, however, exist in the 40--55°S
+zone, where ICON is colder in $\theta_v$ by up to about 5 K and more so
+at higher altitudes (Fig. \ref{fig:potential-temperature}b). In other subsets, the bias is relatively small. MERRA-2
+is very close to the observations, possibly due to a high accuracy of
+assimilation of this quantity. Notably, the variability of virtual potential
+temperature (as represented by the percentiles) is much smaller in ICON than in
+the observations. This indicates that the model's internal variability in the
+lower-tropospheric thermodynamic conditions in the SO is smaller then in the
+reality.
 
-We found that the variability of potential temperature in the model to be
-smaller than in the observations. This indicates that the model does not
-represent the entire natural variability. The LCL peaks at the surface in the
-observations, but the peak in the model is higher (about 200 m). This probably
-relates to the greater occurrence of fog and the peak of cloud occurrence at
-the surface in observations, whereas in the model the peak is higher.
-
-\subsection{Cloud occurrence by cyclonic conditions}
-
-\subsection{Cloud occurrence by stability}
-
-We determine stability by calculating lower tropospheric stability (LTS)
-as the difference between potential temperature at 700 hPa and the surface.
-From a histogram of LTS in ERA5 and MERRA-2 calculated at all voyage tracks
-and the station (Fig. S1), we determined a dividing threshold of 12 K for
-relatively unstable (< 12 K) and relatively stable (>= 12 K) conditions.
+Relative humidity displays much larger biases. In all subsets, ICON is too
+humid in the first 1 km, but very accorate above, except for the 40--55°S zone
+and unstable conditions (Fig. \ref{fig:potential-temperature}b, g),  where it
+is too dry between about 1 and 3 km. MERRA-2, on the other hand, is much more
+humid then observations at all altitudes and in all subsets, by up to about
+20\% at 5 km.
 
@@
 }
-\label{fig:theta-hur}
+\label{fig:potential-temperature}
 \end{figure}
 
-\section{Discussion}
-
-Similar to our results \cite{cesana2022} showed that CMIP6 also tend to
-underestimate cloud occurrence above 2 km over the SO, although their analysis
-in this case was limited to liquid clouds.
-
-\section{Conclusions}
+\section{Discussion and conclusions}
 
@@
 surface).
+
+Similar to our results \cite{cesana2022} showed that CMIP6 also tend to
+underestimate cloud occurrence above 2 km over the SO, although their analysis
+in this case was limited to liquid clouds.
 
@@
 
-The ALCF is open source and is available at \url{https://alcf.peterkuma.net}.
-cl2nc is open source and is available at
-\url{https://github.com/peterkuma/cl2nc}, Our processing a plotting code is
-open source and available at
-\url{https://github.com/peterkuma/icon-so-2024-code}.
+The ALCF, cl2nc, rstool, and our plotting code are open source and available at
+\url{https://alcf.peterkuma.net}, \url{https://github.com/peterkuma/cl2nc}, and
+\url{https://github.com/peterkuma/rstool}, and
+\url{https://github.com/peterkuma/icon-so-2024-code}, respectively. CyTRACK
+is available at \url{https://github.com/apalarcon/CyTRACK}.
 

### 2024-08-26 manuscript.tex
Various updates

@@
 \textbf{(b)} MERRA-2 calculated for the 31 voyage tracks and one station from
-the highest instantaneous temporal resolution data. Shown is also the chosen
-dividing threshold of 12 K for `stable' and `unstable' conditions.
+the highest instantaneous temporal resolution data available. Shown is also the
+chosen dividing threshold of 12 K for `stable' and `unstable' conditions.
 }
-\label{fig:lts-dist}
+\label{fig:lts}
 \end{figure}
@@
 
-We partitioned our data into subsets by cyclonic activity. For this purpose,
-we used a cyclone tracking algorithm to identify extratropical and polar
-cyclones (ECs and PCs) over the SO in the reanalysis and ICON data,
-We used the open source cylone tracking package CyTRACK
-\citep{perez-alarcon2024}. Generally, what constitutes an EC is considered
-relatively arbitrary due to a very large variability of ECs \citep{neu2013}.
-We used the mean sea level pressure field and horizontal wind speed fields as
-input to the CyTRACK algorithm. The algorithm uses pressure and wind speed
-thresholds as well as tracking across time steps to identify cyclone centres
-and radii. From this information, we could classify geographical areas as
-either cyclonic or non-cyclonic. Due to a relatively small total area covered,
-we chose a circle of a double radius (relative to one identified by CyTRACK)
-centred at the cyclone centre as a cyclonic area for every time step and
-cyclone. All other areas were identified as non-cyclonic.  For identifying
-cyclones in the observations, ERA5 pressure and wind fields were used as the
-input to CyTRACK. This is justified by the fact that large-scale pressure and
-wind fields are likely sufficiently close to the reality in ERA5. For
-identifying cyclones in ICON, ERA5, MERRA-2, their own pressure and wind fields
-were used as the input to CyTRACK.
+We partitioned our data into two subsets by cyclonic activity. For this
+purpose, we used a cyclone tracking algorithm to identify extratropical and
+polar cyclones (ECs and PCs) over the SO in the reanalysis and ICON data, We
+used the open source cylone tracking package CyTRACK \citep{perez-alarcon2024}.
+Generally, what constitutes an EC is considered relatively arbitrary due to a
+very large variability of ECs \citep{neu2013}.  We used the mean sea level
+pressure field and horizontal wind speed fields as input to the CyTRACK
+algorithm. The algorithm uses pressure and wind speed thresholds as well as
+tracking across time steps to identify cyclone centres and radii. From this
+information, we could classify geographical areas as either cyclonic or
+non-cyclonic. Due to a relatively small total area covered, we chose a circle
+of a double radius (relative to one identified by CyTRACK) centred at the
+cyclone centre as a cyclonic area for every time step and cyclone. All other
+areas were identified as non-cyclonic. For identifying cyclones in the
+observations and the reanalyses, ERA5 pressure and wind fields were used as the
+input to CyTRACK.  This is justified by the fact that the large-scale pressure
+and wind fields in ERA5 are likely sufficiently close to the reality. For
+identifying cyclones in ICON, its own pressure and wind fields were used as the
+input to CyTRACK, because the model is free-running, and thus the pressure and
+wind fields are different from reality.
 
@@
 
-We determine stability by calculating lower tropospheric stability (LTS)
-as the difference between potential temperature at 700 hPa and the surface.
-From a histogram of LTS in ERA5 and MERRA-2 calculated at all voyage tracks
-and the station (Fig. S1), we determined a dividing threshold of 12 K for
-relatively unstable (< 12 K) and relatively stable (>= 12 K) conditions.
+We partitioned our data into two subset by stability. We determined this by
+calculating lower tropospheric stability (LTS) as the difference between
+potential temperature at 700 hPa and the surface.  Based on a histogram of LTS
+in ERA5 and MERRA-2 calculated at all voyage tracks and stations (Fig.
+\ref{fig:lts}), we determined a dividing threshold of 12 K for relatively
+unstable (< 12 K) and relatively stable (>= 12 K) conditions.
 

### 2024-08-30 manuscript.tex
Flip map
Cyclonic days distribution

@@
 \centering
-\includegraphics[width=\textwidth]{img/map_fig.png}
+\includegraphics[width=\textwidth]{img/map_fig.pdf}
 \caption{
@@
 chosen dividing threshold of 12 K for `stable' and `unstable' conditions.
+}
+\label{fig:lts}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{img/cyc_dist.pdf}
+\caption{
+Geographical distribution of cyclonic days in \textbf{(a)} ERA5 in years
+2010--2013 and \textbf{(b)} ICON in model years 2021--2023 (free running) as
+identified by CyTRACK, expressed as a fraction of the number of days with
+cyclonic activity, defined as grid points located within a double radius of any
+cyclone on a given day (UTC).
 }
@@
 instantaneous profile in the simulated lidar data is assigned a daily mean
-radiation value corresonding to theo the day (in UTC). In turn, the average
-radiation during the entire voyage or station measurement is calculated as the
-average of the profile values. In the observed lidar data, the daily mean
-radiation value is taken from the spatially and temporally co-located CERES
-SYN1deg data for the day (in UTC). The voyage or station measurement average
-is calculated in the same way.
+radiation value corresonding to the day (in the Coordinated Universal Time;
+UTC). In turn, the average radiation during the entire voyage or station
+measurement is calculated as the average of the profile values. In the observed
+lidar data, the daily mean radiation value is taken from the spatially and
+temporally co-located CERES SYN1deg data for the day (in UTC). The voyage or
+station measurement average is calculated in the same way.
 

### 2024-09-02 manuscript.tex
Improve figure caption

@@
 \caption{
-Cloud occurrence by height calculated as the average of all voyages and stations
-for the observed (OBS) and simulated lidar cloud mask. The total cloud fraction
-(CF), average shortwave (SW) and longwave (LW) are shown in the legend. The
-bands span the 16$^\mathrm{th}$--84$^\mathrm{th}$ percentile calculated from
-the set of all voyages and stations. The subsets \textbf{(a--g)} are described
-in the text (Section \ref{sec:results}).}
+Cloud occurrence by height calculated as the average of all voyages and
+stations for the observed (OBS) and simulated lidar cloud mask. The total cloud
+fraction (CF), average shortwave (SW) and longwave (LW) are shown in the
+legend, and the relative frequency of occurrence (RFO) of the subset. The bands
+span the 16$^\mathrm{th}$--84$^\mathrm{th}$ percentile calculated from the set
+of all voyages and stations. The subsets \textbf{(a--g)} are described in the
+text (Section \ref{sec:results}).
+}
 \label{fig:cloud-occurrence}

### 2024-09-02 manuscript.tex
Inclusive years

@@
 analysed here. The tracks cover Antarctic sectors south of South America, the
-Atlantic Ocean, Africa, Australia, and New Zealand in the years 2010 to 2021.
-The dotted and dashed lines at 40°S and 55°S delineate the Southern
-Ocean area of our analysis and its partitioning into two subsets, respectively.
-A photo of \textbf{(b)} RV \emph{Polarstern} (© Folke Mehrtens,
+Atlantic Ocean, Africa, Australia, and New Zealand in the years 2010--2021
+(inclusive).  The dotted and dashed lines at 40°S and 55°S delineate the
+Southern Ocean area of our analysis and its partitioning into two subsets,
+respectively.  A photo of \textbf{(b)} RV \emph{Polarstern} (© Folke Mehrtens,
 Alfred-Wegener-Institut), \textbf{(c)} Lufft CHM 15k installed on RV
@@
 Geographical distribution of cyclonic days in \textbf{(a)} ERA5 in years
-2010--2013 and \textbf{(b)} ICON in model years 2021--2023 (free running) as
-identified by CyTRACK, expressed as a fraction of the number of days with
-cyclonic activity, defined as grid points located within a double radius of any
-cyclone on a given day (UTC).
+2010--2013 (inclusive) and \textbf{(b)} ICON in model years 2021--2023 (free
+running) as identified by CyTRACK, expressed as a fraction of the number of
+days with cyclonic activity, defined as grid points located within a double
+radius of any cyclone on a given day (UTC).
 }
@@
 equivalent to reality at the same time and place. To compare with observations
-taken during different years (2010--2021), we compared the model output with
-observations at the same time of year and geographical location.
+taken during different years (2010--2021, inclusive), we compared the model
+output with observations at the same time of year and geographical location.
 

### 2024-09-03 manuscript.tex
Add RFO to radiosonde plots
Add stable time steps plots

@@
 \centering
-\includegraphics[width=\textwidth]{img/cyc_dist.pdf}
+\includegraphics[width=\textwidth]{img/cyc_stab_dist.pdf}
 \caption{
-Geographical distribution of cyclonic days in \textbf{(a)} ERA5 in years
-2010--2013 (inclusive) and \textbf{(b)} ICON in model years 2021--2023 (free
-running) as identified by CyTRACK, expressed as a fraction of the number of
-days with cyclonic activity, defined as grid points located within a double
-radius of any cyclone on a given day (UTC).
+Geographical distribution of \textbf{(a, b)} cyclonic days and \textbf{(b, d)}
+relatively stable (LTS > 12 K) time steps in \textbf{(a, c)} ERA5 in years
+2010--2013 (inclusive) and \textbf{(b, d)} ICON in model years 2021--2023 (free
+running). Cyclonic days are expressed as a fraction of the number of days with
+cyclonic activity, defined as grid points located within a double radius of any
+cyclone on a given day (UTC), as identified by CyTRACK.
 }
@@
 16$^\mathrm{th}$--84$^\mathrm{th}$ percentiles calculated from the distribution
-of the voyage and station averages.
+of the voyage and station averages. Shown is also the relative frequency of
+occurrence and the number of profiles in each subset.
 }

### 2024-09-04 manuscript.tex
Improve code availability section

@@
 
-The ALCF, cl2nc, rstool, and our plotting code are open source and available at
+The ALCF, cl2nc, rstool, lidar precipitation detection code, and our data
+processing and plotting code are open source and available at
 \url{https://alcf.peterkuma.net}, \url{https://github.com/peterkuma/cl2nc}, and
 \url{https://github.com/peterkuma/rstool}, and
-\url{https://github.com/peterkuma/icon-so-2024-code}, respectively. CyTRACK
-is available at \url{https://github.com/apalarcon/CyTRACK}.
+\url{https://github.com/peterkuma/alcf-precip},
+\url{https://github.com/peterkuma/icon-so-2024}, respectively. CyTRACK is
+available at \url{https://github.com/apalarcon/CyTRACK}.
 

### 2024-09-06 manuscript.tex
Fix grammar

@@
 proposed by \cite{takasuka2024}, with the hope of also evaluating the seasonal
-cycle and large-scale circulation.  An alternative to using a
-computantionally costly GSRM is to train an artificial neural network on GSRM
-output and use it for subgrid-scale clouds, as done with the GSRM ICON by
-\cite{grundner2022}; \cite{grundner2023}.
+cycle and large-scale circulation.  An alternative to using a computantionally
+costly GSRM is to train an artificial neural network on GSRM output and use it
+for subgrid-scale clouds, as done with the GSRM ICON by \cite{grundner2022};
+\cite{grundner2023}.
 
@@
 Multiple cloud properties have an effect on the shortwave (SW) and longwave
-(LW) radiation. On the first order, it is the total cloud fraction, cloud phase,
-and the liquid and ice water path. These are influenced by the atmopheric
-thermodynamics, convection and circulation, and indirect and direct effects
-of aerosols. On smaller orders, it is the cloud droplet size distribution, ice
-crystal habit, cloud lifetime, and direct radiative interaction with aerosols.
-In the 6th phase of the Coupled Model Intercomparison Project [CMIP6;
-\citep{eyring2016}], the cloud feedback has increased relative to CMIP5
-\citep{zelinka2020}, also being one of the main reasons for the higher climate
-sensitivity of CMIP6 models.
+(LW) radiation. On the first order, it is the total cloud fraction, cloud
+phase, and the liquid and ice water path. These are influenced by the
+atmopheric thermodynamics, convection and circulation, and indirect and direct
+effects of aerosols. On smaller orders, it is the cloud droplet size
+distribution, ice crystal habit, cloud lifetime, and direct radiative
+interaction with aerosols.  In the 6th phase of the Coupled Model
+Intercomparison Project [CMIP6; \citep{eyring2016}], the cloud feedback has
+increased relative to CMIP5 \citep{zelinka2020}, also being one of the main
+reasons for the higher climate sensitivity of CMIP6 models.
 
@@
 will conventionally refer to the SO as ocean regions south of 40°S,
-low-latitude SO as 40--55°S and high-latitude SO as south of
-55°S.
+low-latitude SO as 40--55°S and high-latitude SO as south of 55°S.
 
@@
 positive bias, especially in the Atlantic Ocean (AO) sector of the SO,
-increasing by up to 1°C.  \cite{luo2023} identified that the SO SST bias
-in an ensemble of 18 CMIP6 models originates not from the surface heat and
-radiation fluxes (using reanalyses as a reference), but from a warm bias in the
-Northern Atlantic Deep Water.
+increasing by up to 1°C.  \cite{luo2023} identified that the SO SST bias in an
+ensemble of 18 CMIP6 models originates not from the surface heat and radiation
+fluxes (using reanalyses as a reference), but from a warm bias in the Northern
+Atlantic Deep Water.
 
@@
 CloudSat and lidar on CALIPSO are affected by the abovementioned issues,
-resulting in a strong underestimation of cloud occurrence below 2 km relative to
-ground-based lidar observations \citep{mcerlich2021}.  This, in turn, can lead to
-systematic biases in low clouds in climate models, which are frequently
+resulting in a strong underestimation of cloud occurrence below 2 km relative
+to ground-based lidar observations \citep{mcerlich2021}.  This, in turn, can
+lead to systematic biases in low clouds in climate models, which are frequently
 evaluated against CloudSat--CALIPSO products. Reanalyses can also suffer from
@@
 Altogether, we analysed over 1500 days of data from 31 voyages and one
-sub-Antarctic station covering diverse longitudes of the SO. To
-achieve a like-for-like comparison with the model, we used a ground-based lidar
-simulator called the Automatic Lidar and Ceilometer Framework (ALCF)
-\citep{kuma2021}. We contrasted the results with the European Centre for
-Medium-Range Weather Forecasts (ECMWF) Reanalysis 5 (ERA5) \citep{era5} and the
-Modern-Era Retrospective analysis for Research and Applications, Version 2
-(MERRA-2) \citep{gelaro2017}.
+sub-Antarctic station covering diverse longitudes of the SO. To achieve a
+like-for-like comparison with the model, we used a ground-based lidar simulator
+called the Automatic Lidar and Ceilometer Framework (ALCF) \citep{kuma2021}. We
+contrasted the results with the European Centre for Medium-Range Weather
+Forecasts (ECMWF) Reanalysis 5 (ERA5) \citep{era5} and the Modern-Era
+Retrospective analysis for Research and Applications, Version 2 (MERRA-2)
+\citep{gelaro2017}.
 
@@
 Palmer}, Her Majesty's New Zealand Ship (HMNZS) \emph{Wellington} and one
-sub-Antarctic station (Macquarie Island) in the SO south of 40°S between year
-2010 and 2021 (Fig. \ref{fig:map}, Table \ref{tab:voyages} and
+sub-Antarctic station (Macquarie Island) in the SO south of 40°S between 2010
+and 2021 (Fig. \ref{fig:map}, Table \ref{tab:voyages} and
 \ref{tab:voyage-references}). Altogether, the voyages and the station comprised
@@
 regular synoptic times on the RV \emph{Polarstern}, MARCUS, NBP17024, TAN1702,
-and TAN1802 voyage, measuring pressure, temperature, relative humidity and
+and TAN1802 voyages, measuring pressure, temperature, relative humidity, and
 global navigation satellite system coordinates. Derived thermodynamic (virtual
-potential temperature, lifting condensation level, \ldots) and dynamic
-quantities (wind speed and direction) for the measured vertical profiles were
-calculated with rstool \citep{rstool}. Surface meteorological quantities were
-measured continuously by an onboard automatic weather station or individual
-instruments.
+potential temperature, lifting condensation level, etc.) and dynamic quantities
+(wind speed and direction) for the measured vertical profiles were calculated
+with rstool \citep{rstool}. Surface meteorological quantities were measured
+continuously by an onboard automatic weather station or individual instruments.
 
@@
 \emph{ngc3028} produced in 2023 \citep{nextgems2023a,nextgems2023b}. We could
-not use Cycle 4 due to unavailability of the necessary variables. The
+not use Cycle 4 due to the unavailability of the necessary variables. The
 horizontal resolution of ngc3028 is about 5 km.  Unlike current general
@@
 
-ICON uses the atmospheric component ICON-A \citep{giorgetta2018}, whose
-physics is derived from ECHAM6 \citep{stevens2013}, and the ocean component
-ICON-O \citep{korn2022}.
+ICON uses the atmospheric component ICON-A \citep{giorgetta2018}, whose physics
+is derived from ECHAM6 \citep{stevens2013}, and the ocean component ICON-O
+\citep{korn2022}.
 
@@
 simulator. It performs radiative transfer calculations to derive equivalent
-lidar backscattered radiation in an atmospheric model, which can then
-be compared with observed lidar backscatter \citep{kuma2021}. For this purpose,
-it takes atmospheric fields of cloud fraction, liquid and ice mass mixing ratio,
-temperature and pressure fields as an input and can be run offline (on the
+lidar backscattered radiation in an atmospheric model, which can then be
+compared with observed lidar backscatter \citep{kuma2021}. For this purpose, it
+takes atmospheric fields of cloud fraction, liquid and ice mass mixing ratio,
+temperature, and pressure fields as an input and can be run offline (on the
 model output rather than inside the model code). The lidar simulator in the
-ALCF is based on the instrument simulator Cloud Feedback Model
-Intercomparison Project (CFMIP) Observation Simulator Package (COSP)
-\citep{bodas-salcedo2011}. After the backscattered radiation is calculated, a
-cloud mask, cloud occurrence by height and the total cloud fraction are
-determined. ALCF has already been used by several research teams for model and
-reanalysis evaluation
+ALCF is based on the instrument simulator Cloud Feedback Model Intercomparison
+Project (CFMIP) Observation Simulator Package (COSP) \citep{bodas-salcedo2011}.
+After the backscattered radiation is calculated, a cloud mask, cloud occurrence
+by height, and the total cloud fraction are determined. ALCF has already been
+used by several research teams for model and reanalysis evaluation
 \citep{kuma2020,kremser2021,guyot2022,pei2023,whitehead2023,mcdonald2024}.
-Absolute calibration of the observed backscatter was performed by comparing
-the measured clear-sky molecular backscatter statistically with simulated
-clear-sky molecular backscatter.
+Absolute calibration of the observed backscatter was performed by comparing the
+measured clear-sky molecular backscatter statistically with simulated clear-sky
+molecular backscatter.
 
@@
 
-The Vaisala CL51 and CL31 are ceilometers operating at a near-infrared
-wavelength of 910 nm. The maximum range 15.4 km (CL51), 7.7 km (CL31 with 5 m
-vertical resolution) and 7.550 (CL31 with 10 m vertical resolution).
-The vertical resolution is 10 m (5 m configurable). The wavelength is affected
-by water vapour absorption of about 20\% in the mid-latitudes
-\citep{wiegner2015,wiegner2019}.  The instrument data files containing
-uncalibrated backscatter were first converted to NetCDF with cl2nc
+The Vaisala CL51 (Fig. \ref{fig:map}d) and CL31 are ceilometers operating at a
+near-infrared wavelength of 910 nm. The maximum range is 15.4 km (CL51), 7.7 km
+(CL31 with 5 m vertical resolution), and 7.550 km (CL31 with 10 m vertical
+resolution).  The vertical resolution is 10 m (5 m configurable). The
+wavelength is affected by water vapour absorption of about 20\% in the
+mid-latitudes \citep{wiegner2015,wiegner2019}.  The instrument data files
+containing uncalibrated backscatter were first converted to NetCDF with cl2nc
 (\url{https://github.com/peterkuma/cl2nc}) and then processed with the ALCF to
@@
 
-For the MARCUS voyage, Vaisala CL31 were made available by the Atmospheric
-Radiation Measurement (ARM) processed to a maximum range of 7.545 km, vertical
-resolution of 30 m and 252 vertical levels.
+For the MARCUS voyage, Vaisala CL31 was made available by the Atmospheric
+Radiation Measurement (ARM) processed to a maximum range of 7.545 km, a
+vertical resolution of 30 m, and 252 vertical levels.
 
@@
 
-The Lufft CHM 15k is a ceilometer operating at a near-infrared wavelength of
-1064 nm. The maximum range is 15.4 km, vertical resolution is 5 m in the near
-range (up to 150 m) and 15 m above, the sampling rate is 2 s, and the number of
-vertical levels is 1024.  NetCDF files containing uncalibrated backscatter
-produced by the instrument were processed with the ALCF to produce a cloud mask
-and cloud occurrence by height and the total cloud fraction.
+The Lufft CHM 15k (Fig. \ref{fig:map}c) is a ceilometer operating at a
+near-infrared wavelength of 1064 nm. The maximum range is 15.4 km, the vertical
+resolution is 5 m in the near range (up to 150 m) and 15 m above, the sampling
+rate is 2 s, and the number of vertical levels is 1024.  NetCDF files
+containing uncalibrated backscatter produced by the instrument were processed
+with the ALCF to produce a cloud mask and cloud occurrence by height and the
+total cloud fraction.
 
@@
 Office at the NASA Goddard Space Flight Center \citep{gelaro2017}.  It uses
-version 5.12.4 of the Goddard Earth Observing System (GEOS) atmospheric
-model \citep{rienecker2008,molod2015}. The reanalysis output analysed here is
+version 5.12.4 of the Goddard Earth Observing System (GEOS) atmospheric model
+\citep{rienecker2008,molod2015}. The reanalysis output analysed here is
 available at a spatial resolution of 0.5° in latitude and 0.625° in longitude,
@@
 2-m temperature and humidity; 3-hourly instantaneous 3D assimilated
-meteorological fields (M2I3NVASM) for cloud quantities, pressure and
+meteorological fields (M2I3NVASM) for cloud quantities, pressure, and
 temperature; 1-hourly average 2D surface flux diagnostics (M2T1NXFLX) for
@@
 prediction (NWP) model Integrated Forecast System (IFS) version CY41R2.  The
-horizontal resolution is 0.25° in latitude and longitude, which is about
-28 km in the North--South direction and 14 km in the East--West direction at
-60°S. Internally, the model uses 137 vertical levels. In our analysis we use
-output at one hourly instantaeous time intervals, except for radiation
-quantities, which are accumulations (from these we calculate daily means).
+horizontal resolution is 0.25° in latitude and longitude, which is about 28 km
+in the North--South direction and 14 km in the East--West direction at 60°S.
+Internally, the model uses 137 vertical levels. In our analysis we use output
+at one hourly instantaeous time intervals, except for radiation quantities,
+which are accumulations (from these we calculate daily means).
 Vertically-resolved quantities are made available on 37 pressure levels. We
@@
 purpose, we used a cyclone tracking algorithm to identify extratropical and
-polar cyclones (ECs and PCs) over the SO in the reanalysis and ICON data, We
-used the open source cylone tracking package CyTRACK \citep{perez-alarcon2024}.
-Generally, what constitutes an EC is considered relatively arbitrary due to a
-very large variability of ECs \citep{neu2013}.  We used the mean sea level
-pressure field and horizontal wind speed fields as input to the CyTRACK
-algorithm. The algorithm uses pressure and wind speed thresholds as well as
-tracking across time steps to identify cyclone centres and radii. From this
-information, we could classify geographical areas as either cyclonic or
-non-cyclonic. Due to a relatively small total area covered, we chose a circle
-of a double radius (relative to one identified by CyTRACK) centred at the
-cyclone centre as a cyclonic area for every time step and cyclone. All other
-areas were identified as non-cyclonic. For identifying cyclones in the
-observations and the reanalyses, ERA5 pressure and wind fields were used as the
-input to CyTRACK.  This is justified by the fact that the large-scale pressure
-and wind fields in ERA5 are likely sufficiently close to the reality. For
-identifying cyclones in ICON, its own pressure and wind fields were used as the
-input to CyTRACK, because the model is free-running, and thus the pressure and
-wind fields are different from reality.
+polar cyclones (ECs and PCs) over the SO in the reanalysis and ICON data. We
+used the open source cyclone tracking package CyTRACK
+\citep{perez-alarcon2024}.  Generally, what constitutes an EC is considered
+relatively arbitrary due to the very large variability of ECs \citep{neu2013}.
+We used the mean sea level pressure field and horizontal wind speed fields as
+input to the CyTRACK algorithm. The algorithm uses pressure and wind speed
+thresholds as well as tracking across time steps to identify cyclone centres
+and radii. From this information, we could classify geographical areas as
+either cyclonic or non-cyclonic. Due to a relatively small total area covered,
+we chose a circle of a double radius (relative to one identified by CyTRACK)
+centred at the cyclone centre as a cyclonic area for every time step and
+cyclone. All other areas were identified as non-cyclonic. For identifying
+cyclones in the observations and the reanalyses, ERA5 pressure and wind fields
+were used as the input to CyTRACK.  This is justified by the fact that the
+large-scale pressure and wind fields in ERA5 are likely sufficiently close to
+reality. For identifying cyclones in ICON, its own pressure and wind fields
+were used as the input to CyTRACK, because the model is free-running, and thus
+the pressure and wind fields are different from reality.
 
@@
 
-We partitioned our data into two subset by stability. We determined this by
-calculating lower tropospheric stability (LTS) as the difference between
+We partitioned our data into two subsets by stability. We determined this by
+calculating lower tropospheric stability (LTS) as the difference between the
 potential temperature at 700 hPa and the surface.  Based on a histogram of LTS
@@
 Precipitation can cause strong enough lidar backscattering to be recognised as
-a cloud by the cloud detection method used in the ALCF. This is undesirable
-if equivalent precipitation backscatter is not included in the simulated lidar
+a cloud by the cloud detection method used in the ALCF. This is undesirable if
+equivalent precipitation backscatter is not included in the simulated lidar
 profiles. It was not possible to include precipitation simulation in the ALCF
@@
 relatively easily by excluding profiles with an amount of surface precipitation
-flux exceeding a given threshold. In the observations, using precipitation
-flux measurements can be very unreliable on ships due to ship movement and
+flux exceeding a given threshold. In the observations, using precipitation flux
+measurements can be very unreliable on ships due to ship movement and
 turbulence caused by nearby ship structures. Our analysis of rain gauge data
@@
 from lidar backscatter. Samples of short time intervals (10 min) of
-near-surface backscatter (0–250 m) were classified as clear, rain, snow and
+near-surface backscatter (0–250 m) were classified as clear, rain, snow, and
 fog, using the synoptic observations as a training dataset. From these, a
@@
 instantaneous profile in the simulated lidar data is assigned a daily mean
-radiation value corresonding to the day (in the Coordinated Universal Time;
+radiation value corresponding to the day (in the Coordinated Universal Time;
 UTC). In turn, the average radiation during the entire voyage or station
@@
 % TODO: Add sampling intervals.
-\caption{List of voyages and stations.
-Start, end and days (UTC; inclusive) indicate the time period when the vessel was south of 40°S.
-Abbreviations: ceilometer (ceil.), Australia (AU), New Zealand (NZ), South America (SA), Atlantic Ocean (AO) and Africa (AF).
-The number of days is rounded to the nearest integer.
-CL51/31 indicates CL51 configured to emulate CL31.}
+\caption{
+List of voyages and stations. Start, end, and days (UTC; inclusive)
+indicate the time period when the vessel was south of 40°S. Abbreviations:
+ceilometer (ceil.), Australia (AU), New Zealand (NZ), South America (SA),
+Atlantic Ocean (AO) and Africa (AF). The number of days is rounded to the
+nearest integer. CL51/31 indicates CL51 configured to emulate CL31.
+}
 \label{tab:voyages}
@@
 We used the ALCF to derive cloud occurrence by height and the total cloud
-fraction from observations, ICON and two reanalyses MERRA-2 and ERA5 (Fig.
-\ref{fig:cloud-occurrence-panel}). We aggregated the sources by calculating
-the averages and percentiles of all individual profiles (Fig.
+fraction from observations, ICON, and two reanalyses, MERRA-2 and ERA5 (Fig.
+\ref{fig:cloud-occurrence-panel}). We aggregated the sources by calculating the
+averages and percentiles of all individual profiles (Fig.
 \ref{fig:cloud-occurrence}). The analysis shows that the total cloud fraction
@@
 In particular, ICON overestimates cloud occurrence below 1 km and
-underestimates it above, MERRA-2 underestimates cloud occurrence at all heights,
-especially near the surface, and ERA5 simulates cloud occurrence relatively well
-above 1 km, but strongly underestimates it near the surface.
+underestimates it above, MERRA-2 underestimates cloud occurrence at all
+heights, especially near the surface, and ERA5 simulates cloud occurrence
+relatively well above 1 km, but strongly underestimates it near the surface.
 We note that fog or near-surface clouds are strongly lacking in the reanalyses.
@@
 The observations show cloud occurrence peaking at the surface, whereas models
-show higher peak (at about 500 m). The models underestimate total cloud
-fraction by 10--20\%, and show a strong decrease in cloud occurrence near the
+show a higher peak (at about 500 m). The models underestimate total cloud
+fraction by 10--20\% and show a strong decrease in cloud occurrence near the
 surface, but this is not happening in the observations. ICON and ERA5
@@
 high peak in models is partly supported by the LCL distribution, which peaks
-higher in the models then in the observations (at the surface), although this
-is not very pronounced. The northern zone shows stronger peak of cloud
+higher in the models than in the observations (at the surface), although this
+is not very pronounced. The northern zone shows a stronger peak of cloud
 occurrence near the surface than the southern zone, and this could be because
@@
 occurrence is still strongly understimated). Cyclonic situations have a larger
-amount observed cloudiness, including the peak and total cloud fraction. In
+amount of observed cloudiness, including the peak and total cloud fraction. In
 these situations, the models are doing a relatively good job of getting the
@@
 cloud occurrence above 1 km and near the surface. Non-cyclonic situations are
-similar to the general case. In stable stituations cloud occurrence peaks
+similar to the general case. In stable situations cloud occurrence peaks
 strongly at the surface in observations, compared to unstable situations, where
-the peak is more more obtuse and spread across 0--1 km. In stable situations
-the models are doing a fairly good job, but overestimate cloud occurrence at
-the peak below 1 km, above 1 km the show similar biases as in the general case.
+the peak is more obtuse and spread across 0--1 km. In stable situations, the
+models are doing a fairly good job, but overestimate cloud occurrence at the
+peak below 1 km; above 1 km, they show similar biases as in the general case.
 In unstable situations the bias in ICON is very pronounced, with a much
@@
 cloud fraction, and showing greatest biases in unstable and non-cyclonic
-conditition. It also shows peak of cloud occurrence at higher altitude than obs
-(500 m vs. near the surface) and correspondingly its LCL tends to be also
+condititions. It also shows a peak of cloud occurrence at higher altitude than
+obs (500 m vs. near the surface), and correspondingly, its LCL tends to be also
 higher. MERRA-2 can be generally characterised as underestimating cloud
@@
 mostly above and below 500 m (the peak at 500 m is well-represented). It
-struggles the most in the northern zone, and in unstable situations. ERA5 can
-be generally characterised as representing cloud occurrence correctly above
-about 1--1.5 km, overestimating below, but underestimating near-surface cloud
+struggles the most in the northern zone and in unstable situations. ERA5 can be
+generally characterised as representing cloud occurrence correctly above about
+1--1.5 km, overestimating below, but underestimating near-surface cloud
 occurrence (0--500 m). The total cloud fraction is strongly understimated in
-all situations. It has tendency towards understimation in the northern zone and
-unstable stiuations, and conversely overestimating in the southern zone and
+all situations. It has a tendency towards understimation in the northern zone
+and unstable situations, conversely, overestimating in the southern zone and
 stable conditions.
@@
 fraction (CF), average shortwave (SW) and longwave (LW) are shown in the
-legend, and the relative frequency of occurrence (RFO) of the subset. The bands
-span the 16$^\mathrm{th}$--84$^\mathrm{th}$ percentile calculated from the set
-of all voyages and stations. The subsets \textbf{(a--g)} are described in the
-text (Section \ref{sec:results}).
+legend, and the relative frequency of occurrence (RFO) of the subset is shown
+below.  The bands span the 16$^\mathrm{th}$--84$^\mathrm{th}$ percentile
+calculated from the set of all voyages and stations. The subsets
+\textbf{(a--g)} are described in the text (Section \ref{sec:results}).
 }
@@
 
-We analysed daily cloud cover (total cloud fraction) distribution. This is a
-measure of cloudiness irrespective of height. A cloud detected at any height
-means that the lidar profile was classified as cloudy, otherwise it was
-classified as clear sky. When all profiles in a day are aggregated together,
-the cloud cover for the day is determied as the fraction of cloudy profiles in
+We analysed the daily cloud cover (total cloud fraction) distribution. This is
+a measure of cloudiness, irrespective of height. A cloud detected at any height
+means that the lidar profile was classified as cloudy; otherwise, it was
+classified as a clear sky. When all profiles in a day are aggregated together,
+the cloud cover for the day is defined as the fraction of cloudy profiles in
 the total number of profiles, expressed in octas.
@@
 In Fig.  \ref{fig:cloud-cover} we show the results for the same subsets as
-anlysed above. Observations show the greatest representation of high cloud
+analysed above. Observations show the greatest representation of high cloud
 cover (5--8 octas), peaking at 7 octas. This is not represented by ICON or the
@@
 
-When analysed by subsets, the cyclonic subset show to highest cloud cover, with
-8 octas occurring on one half of such days (Fig. \ref{fig:cloud-cover}d).  This
-is not represented by ICON or the reanalyses at all. Interestingly, clear sky
-days (0 octas) also have a local maximum peaking at about 15\% in this subset.
-When we contrast the low and high latitude zones, we see that the high latitude
-zone tends to have greater cloud cover, peaking at 8 octas (Fig.
-\ref{cloud-cover}c). The high latitue also has almost no clear sky or small
+When analysed by subsets, the cyclonic subset shows the highest cloud cover,
+with 8 octas occurring on one half of such days (Fig. \ref{fig:cloud-cover}d).
+This is not represented by ICON or the reanalyses at all. Interestingly, clear
+sky days (0 octas) also have a local maximum peaking at about 15\% in this
+subset.  When we contrast the low and high latitude zones, we see that the high
+latitude zone tends to have greater cloud cover, peaking at 8 octas (Fig.
+\ref{cloud-cover}c). The high latitude also has almost no clear sky or small
 cloud cover cases (0--4 octas). ICON and the reanalyses represent at least this
-charactertic of the distribution well for 0--3 octas, but otherwise show bises
-similar to the general case. One of the greatest biases is present in ERA5 in
-the unstable subset, where it peaks at 3 octas, whereas the observations peak
-at 7 octas and show negligible cloud cover below 5 octas.
+characteristic of the distribution well for 0--3 octas, but otherwise show
+bises similar to the general case. One of the greatest biases is present in
+ERA5 in the unstable subset, where it peaks at 3 octas, whereas the
+observations peak at 7 octas and show negligible cloud cover below 5 octas.
 
@@
 \emph{Polarstern} voyages, MARCUS, NBP1704, TAN1702, and TAN1802. Spatially and
-temporaly colocated profiles were taken from ICON and the reanalyses. Because
+temporally colocated profiles were taken from ICON and the reanalyses. Because
 the time period of the ICON model output was different from the observations,
@@
 
-Overall, the mean $\theta_v$ is relatively well represented in ICON and MERRA-2,
-being only slightly colder in the mid-to-high troposophere (less stable) in ICON
-than in observations (Fig. \ref{fig:potential-temperature}a). Large differences exist, however, exist in the 40--55°S
-zone, where ICON is colder in $\theta_v$ by up to about 5 K and more so
-at higher altitudes (Fig. \ref{fig:potential-temperature}b). In other subsets, the bias is relatively small. MERRA-2
-is very close to the observations, possibly due to a high accuracy of
-assimilation of this quantity. Notably, the variability of virtual potential
-temperature (as represented by the percentiles) is much smaller in ICON than in
-the observations. This indicates that the model's internal variability in the
-lower-tropospheric thermodynamic conditions in the SO is smaller then in the
-reality.
+Overall, the mean $\theta_v$ is relatively well represented in ICON and
+MERRA-2, being only slightly colder in the mid-to-high troposophere (less
+stable) in ICON than in observations (Fig. \ref{fig:potential-temperature}a).
+Large differences exist, however, in the 40--55°S zone, where ICON is colder in
+$\theta_v$ by up to about 5 K and more so at higher altitudes (Fig.
+\ref{fig:potential-temperature}b). In other subsets, the bias is relatively
+small. MERRA-2 is very close to the observations, possibly due to a high
+accuracy of assimilation of this quantity. Notably, the variability of virtual
+potential temperature (as represented by the percentiles) is much smaller in
+ICON than in the observations. This indicates that the model's internal
+variability in the lower-tropospheric thermodynamic conditions in the SO is
+smaller than in reality.
 
@@
 is too dry between about 1 and 3 km. MERRA-2, on the other hand, is much more
-humid then observations at all altitudes and in all subsets, by up to about
+humid than observations at all altitudes and in all subsets, by up to about
 20\% at 5 km.
@@
 determined from radiosonde launches and co-located profiles in
-ICON, ERA5 and MERRA-2 in subsets as in Fig. \ref{fig:cloud-occurrence}.
+ICON, ERA5, and MERRA-2 in subsets as in Fig. \ref{fig:cloud-occurrence}.
 The solid lines are the average calculated from the averages of every
@@
 
-Similar to our results \cite{cesana2022} showed that CMIP6 also tend to
+Similar to our results, \cite{cesana2022} showed that CMIP6 also tends to
 underestimate cloud occurrence above 2 km over the SO, although their analysis
@@
 
-The results imply that SO cloud biases are still a significant
-issue in a km-scale resolution model, even though an improvement over the
-lower-resolution reanalyses is notable. More effort is needed to improve model
-cloud simulations in this fast-changing and understudied region. The
-advancement from convection and cloud parameterisation to cloud-resolving models
-might not solve this bias without additional effort.
+The results imply that SO cloud biases are still a significant issue in a
+km-scale resolution model, even though an improvement over the lower-resolution
+reanalyses is notable. More effort is needed to improve model cloud simulations
+in this fast-changing and understudied region. The advancement from convection
+and cloud parameterisation to cloud-resolving models might not solve this bias
+without additional effort.
 
@@
 Navy and the UC and a Macquarie Island dataset provided by the Atmospheric
-Radiation Measurement and the UC. We thank the scientiﬁc staff, the crew and
+Radiation Measurement and the UC. We thank the scientiﬁc staff, the crew, and
 everyone involved in collecting data on the voyages and Macquarie Island,
-especially Kelly Schick, Peter Guest, John J. Cassano, Simon
-Parsons, Graeme Plank, Sally Garrett, Jamie Halla, Sean Hartery, Mike J.
-Harvey, Simon P. Alexander and Alex Schuddeboom. We acknowledge the reanalysis
-dataset ERA5 provided by the Copernicus Climate Change Service and MERRA-2
-provided by the Global Modeling and Assimilation Office. We also acknowledge the
-AMSR Uniﬁed and SMMR and SSM/I-SSMIS datasets provided by the National Snow and
-Ice Data Center.
+especially Kelly Schick, Peter Guest, John J. Cassano, Simon Parsons, Graeme
+Plank, Sally Garrett, Jamie Halla, Sean Hartery, Mike J.  Harvey, Simon P.
+Alexander and Alex Schuddeboom. We acknowledge the reanalysis dataset ERA5
+provided by the Copernicus Climate Change Service and MERRA-2 provided by the
+Global Modeling and Assimilation Office. We also acknowledge the AMSR Uniﬁed
+and SMMR and SSM/I-SSMIS datasets provided by the National Snow and Ice Data
+Center.
 
@@
 openly available from the Atmospheric Radiation Measurement (ARM)
-(\url{https://www.arm.gov}). The MERRA-2 data are openly available at from NASA
-NASA Goddard Earth Sciences (GES) Data and Information Services Center (DISC)
-(\url{https://disc.gsfc.nasa.gov/datasets?project=MERRA-2}).  The ERA5 data are
-openly available from Copernicus Climate Data Store (CDS)
+(\url{https://www.arm.gov}). The MERRA-2 data are openly available from the
+NASA NASA Goddard Earth Sciences (GES) Data and Information Services Center
+(DISC) (\url{https://disc.gsfc.nasa.gov/datasets?project=MERRA-2}).  The ERA5
+data are openly available from the Copernicus Climate Data Store (CDS)
 (\url{https://cds.climate.copernicus.eu}). The CERES products are available

### 2024-09-23 manuscript.tex
ANN figure

@@
 \label{fig:example}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{img/ann.pdf}
+\caption{
+Artificial neural network (ANN) for prediction of precipitation in lidar
+backscatter. \textbf{(a)} Diagram showing the TensorFlow structure of the ANN,
+\textbf{(b)} randomly selected example samples of near-surface backscatter in
+four categories (clear, fog, rain and snow), as determined by coincident
+human-performed weather observations, \textbf{(c)} receiver operating
+characteristic diagram of the ANN, \textbf{(d)} examples of 10-day periods
+human-observed (`HUM') and predicted precipitation based on an ANN trained on
+all voyages (`ANN') and all voyages except for the shown voyage (`ANN2') during
+three randomly selected voyages with the available data. Here, by `randomly
+selected' we mean selected from the top of a permutation generated by a
+pseudo-random number generator to prevent authors' bias in the selection.
+}
+\label{fig:ann}
 \end{figure}

### 2024-09-23 manuscript.tex
Improve precip. detection section

--- 2024-09-06 manuscript.tex
@@
 \centering
+\includegraphics[width=\textwidth]{img/ann.pdf}
+\caption{
+Artificial neural network (ANN) for prediction of precipitation in lidar
+backscatter. \textbf{(a)} Diagram showing the TensorFlow structure of the ANN,
+\textbf{(b)} randomly selected example samples of near-surface backscatter in
+four categories (clear, fog, rain and snow), as determined by coincident
+human-performed weather observations, \textbf{(c)} receiver operating
+characteristic diagram of the ANN, \textbf{(d)} examples of 10-day time series
+of human-observed (`HUM') and predicted precipitation based on an ANN trained
+on all voyages (`ANN') and all voyages except for the shown voyage (`ANN2')
+during three randomly selected voyages with the available data. Here, by
+`randomly selected' we mean selected from the top of a permutation generated by
+a pseudo-random number generator to prevent authors' bias in the selection.
+}
+\label{fig:ann}
+\end{figure}
+
+\begin{figure}
+\centering
 \includegraphics[width=\textwidth]{img/lts_dist.pdf}
@@
 Precipitation can cause strong enough lidar backscattering to be recognised as
-a cloud by the cloud detection method used in the ALCF. This is undesirable if
-equivalent precipitation backscatter is not included in the simulated lidar
-profiles. It was not possible to include precipitation simulation in the ALCF
-due to the absence of required fields in the ICON model output and the
-reanalysis data, the liquid and ice precipitation mass mixing ratios, and
-because the required radiation calculations for precipitation are not
-implemented in the ALCF. In this situation, in order to achieve a fair
-comparison of observations and models, one should exclude profiles with
-precipitation either manually or using an automated method. It is relatively
-difficult to distinguish precipitation backscatter from cloud backscatter in
-lidar observations, especially when only one wavelength channel and no
-polarisation channel are available. In models, the same can be accomplished
-relatively easily by excluding profiles with an amount of surface precipitation
-flux exceeding a given threshold. In the observations, using precipitation flux
-measurements can be very unreliable on ships due to ship movement and
+a cloud by the threshold-based cloud detection method used in the ALCF. This is
+undesirable if equivalent precipitation backscatter is not included in the
+simulated lidar profiles. It was not possible to include precipitation
+simulation in the ALCF due to the absence of required fields in the ICON model
+output and the reanalysis data (the liquid and ice precipitation mass mixing
+ratios), and because the required radiation calculations for precipitation are
+currently not implemented in the ALCF. In order to achieve a fair comparison of
+observations with models, one should exclude observed and simulated lidar
+profiles with precipitation either manually or using an automated method. It is
+relatively difficult to distinguish precipitation backscatter from cloud
+backscatter in lidar observations, especially when only one wavelength channel
+and no polarised channel are available. In models, the same can be accomplished
+relatively easily by excluding profiles exceeding a certain amount of surface
+precipitation flux. In the observations, using precipitation flux measurements
+from rain gauges can be very unreliable on ships due to ship movement and
 turbulence caused by nearby ship structures. Our analysis of rain gauge data
@@
 time series and human-performed synoptic observations, as well as large
-inconsistencies in the rain gauge time series. Therefore, it is desirable to
-implement a method of detecting precipitation from observed backscatter
-profiles instead.
+inconsistencies in the rain gauge time series. Human-performed observations of
+precipitation presence or absence are expected to be reliable, but only cover a
+limited set of time instants. Therefore, it was desirable to implement a method
+of detecting precipitation from observed backscatter profiles alone.
 
 On the RV \emph{Polarstern} voyages, regular human-performed synoptic
-observations were available and included precipitation presence and type. We
-used this dataset to train a convolutional artiﬁcial neural network (ANN) of
-the U-Net type \citep{ronneberger2015} to recognise profiles with precipitation
-from lidar backscatter. Samples of short time intervals (10 min) of
-near-surface backscatter (0–250 m) were classified as clear, rain, snow, and
-fog, using the synoptic observations as a training dataset. From these, a
-binary classification of profiles as wet (rain or fog) and dry (clear or fog)
-was derived.
+observations were available and included precipitation presence or absence and
+type. We used this dataset to train a convolutional artiﬁcial neural network
+(ANN) of the U-Net type \citep{ronneberger2015} to recognise profiles with
+precipitation from lidar backscatter (Fig. \ref{fig:ann}a), implemented in the
+TensorFlow ANN framework \citep{tensorflow}. Samples of short time intervals
+(10 min) of near-surface lidar backscatter (0–250 m) were classified as clear,
+rain, snow, and fog, using the synoptic observations as a training dataset
+(Fig.  \ref{fig:ann}b). From these, a binary, mutually exclusive classification
+of profiles as precipitating (rain or snow) or dry (clear or fog) was derived.
+For detecting model and reanalysis precipitation, we used a fixed threshold for
+surface precipitation flux of 0.1 mm h$^{-1}$ (the ANN was not used).
 
 The ANN achieved 65\% sensitivity and 87\% speciﬁcity when the true positive
-rate (26\%) was made to match observations. We considered these success rates
-satisfactory for the purpose of filtering precipitation profiles.
+rate (26\%) was made to match observations. The receiver operating
+characteristic curve is shown in Fig. \ref{fig:ann}c. We considered these rates
+satisfactory for the purpose of filtering precipitation profiles. Fig.
+\ref{fig:ann}d shows examples of the predicted precipitation compared to
+human-performed observations.
 

### 2024-09-24 manuscript.tex
Improving the methods section

@@
 sub-Antarctic station (Macquarie Island) in the SO south of 40°S between 2010
-and 2021 (Fig. \ref{fig:map}, Table \ref{tab:voyages} and
-\ref{tab:voyage-references}). Altogether, the voyages and the station comprised
+and 2021. Fig. \ref{fig:map} shows a map of the voyages, Table \ref{tab:voyages}
+list the voyages and stations, and \ref{tab:voyage-references} lists references
+where available. Altogether, the voyages and station dataset comprised
 2421 days of data south of 40°S, but the availability of ceilometer data was
-smaller due to gaps in measurements. Missing days in the ceilometer data were
-HMNZSW16 (7 days): 24--27 November, 10 December, 16--17 December 2016; MARCUS
-(3 days): 8, 10 November, 10 December; MICRE (9 days): 7--8, 29 June, 5, 16
-July, 15 August, 17 October 2016, 11 February, 21 March 2017; TAN1502 (1 day):
-24 January.
+slightly smaller due to gaps in measurements.
 
-These data sources contained ceilometer observations with the Vaisala CL51 and
-CL31 operating at 910 nm and the Lufft CHM-15k operating at 1064 nm, described
-in detail below (Sections \ref{sec:cl51} and \ref{sec:chm15k}). A ceilometer is
-a low-power near-infrared vertically pointing lidar with the purpose of
-measuring the cloud base, but it also measures the full vertical structure of
-clouds as long as the laser signal is not attenuated by thick clouds.
+Missing days in the ceilometer data were HMNZSW16 (7 days): 24--27 November, 10
+December, 16--17 December 2016; MARCUS (3 days): 8, 10 November, 10 December;
+MICRE (9 days): 7--8, 29 June, 5, 16 July, 15 August, 17 October 2016, 11
+February, 21 March 2017; TAN1502 (1 day): 24 January.
+
+The data sources contained ceilometer observations captured by the Vaisala CL51
+and CL31 operating at a wavelenght of 910 nm and the Lufft CHM-15k operating at
+1064 nm, described in detail below (Sections \ref{sec:cl51} and
+\ref{sec:chm15k}). A ceilometer is a low-power near-infrared vertically
+pointing lidar with the purpose of measuring the cloud base, but it also
+measures the full vertical structure of clouds as long as the laser signal is
+not attenuated by thick clouds, which can be used to infer additional
+information such as a cloud mask and cloud occurrence by height.
 
@@
 global navigation satellite system coordinates. Derived thermodynamic (virtual
-potential temperature, lifting condensation level, etc.) and dynamic quantities
-(wind speed and direction) for the measured vertical profiles were calculated
-with rstool \citep{rstool}. Surface meteorological quantities were measured
-continuously by an onboard automatic weather station or individual instruments.
+potential temperature, lifting condensation level, etc.) and dynamic physical
+quantities (wind speed and direction) for the measured vertical profiles were
+calculated with rstool \citep{rstool}. Surface meteorological quantities were
+measured continuously by an onboard automatic weather station or individual
+instruments.
+
+\subsection{Vaisala CL51 and CL31}
+\label{sec:cl51}
+
+The Vaisala CL51 (photo in Fig. \ref{fig:map}d) and CL31 are ceilometers
+operating at a near-infrared wavelength of 910 nm. The maximum range is 15.4 km
+(CL51), 7.7 km (CL31 with 5 m vertical resolution), and 7.550 km (CL31 with 10
+m vertical resolution). The vertical resolution is 10 m (5 m configurable), and
+the sampling (temporal) resolution is 6 s (AA15‐16, MARCUS, and MICRE), 36 s (RV
+\emph{Polarstern}), and about 2.37 s (TAN1502). From the MARCUS voyage, unlike raw
+instrument data available for the other voyages and stations, the Vaisala CL31
+data were made available by the Atmospheric Radiation Measurement (ARM)
+processed to a maximum range of 7.545 km, a vertical resolution of 30 m, and
+sampling resolution of 16 s. The wavelength of 910 nm is affected by water
+vapour absorption of about 20\% in the mid-latitudes
+\citep{wiegner2015,wiegner2019}.  The instrument data files containing raw
+uncalibrated backscatter were first converted to NetCDF with cl2nc
+(\url{https://github.com/peterkuma/cl2nc}) and then processed with the ALCF
+(Section \ref{sec:alcf}) to produce absolutely calibrated attenuated volume
+backscattering coefficinet (AVBC), cloud mask, cloud occurrence by height and
+the total cloud fraction. CL51 can also be configured to emulate CL31. The
+Vaisala CL51 and CL31 instruments were used on most of the voyages and stations
+analysed here. Fig. \ref{fig:example}a shows an example of derived from the
+CL51 instrument.
+
+\subsection{Lufft CHM 15k}
+\label{sec:chm15k}
+
+The Lufft CHM 15k (photo in Fig. \ref{fig:map}c) is a ceilometer operating at a
+near-infrared wavelength of 1064 nm. The maximum range is 15.4 km, the vertical
+resolution is 5 m in the near range (up to 150 m) and 15 m above, the sampling
+(temporal) resolution is 2 s, and the number of vertical levels is 1024.
+NetCDF files containing uncalibrated backscatter produced by the instrument
+were processed with the ALCF (Section \ref{sec:alcf}) to produce AVBC, cloud
+mask, cloud occurrence by height and the total cloud fraction. The CHM 15k was
+used on a minority of voyages (HMNZSW16, TAN1702, TAN1802, and NBP1704).
+
+\subsection{ALCF}
+\label{sec:alcf}
+
+The Automatic Lidar and Ceilometer Framework (ALCF) is a ground-based lidar
+simulator and a tool for processing observed lidar data, supporting various
+instruments and models. It performs radiative transfer calculations to derive
+equivalent lidar AVBC in an atmospheric model, which can then be compared with
+observed AVBC \citep{kuma2021}. For this purpose, it takes atmospheric fields
+of cloud fraction, liquid and ice mass mixing ratio, temperature, and pressure
+fields as an input and can be run offline (on the model output rather than
+inside the model code). The lidar simulator in the ALCF is based on the
+instrument simulator Cloud Feedback Model Intercomparison Project (CFMIP)
+Observation Simulator Package (COSP) \citep{bodas-salcedo2011}.  After AVBC is
+calculated, a cloud mask, cloud occurrence by height, and the total cloud
+fraction are determined. The ALCF has already been used by several research
+teams for model and reanalysis evaluation
+\citep{kuma2020,kremser2021,guyot2022,pei2023,whitehead2023,mcdonald2024}.
+Absolute calibration of the observed backscatter was performed by comparing the
+measured clear-sky molecular backscatter statistically with simulated clear-sky
+molecular backscatter. AVBC is resampled to 5 min temporal resolution and 50 m
+vertical resolution to increase signal-to-noise ratio, while having enough
+resolution to detect small-scale cloud variability. Noise standard deviation is
+calculated from AVBC at the highest range, where no clouds are expected.  A
+cloud mask is calculated from AVBC using a fixed threshold of $\mathrm{2\times
+10^{-6} m^{-1}sr^{-1}}$ after subtracting 5 standard deviations of range-scale
+noise. Fig. \ref{fig:example}b shows an example of simulated Vaisala CL51
+backscatter from ERA5 data, corresponding to a day of measurements by the
+instrument on the PS81/3 voyage.
 
@@
 \cite{mauritsen2022}.
-
-\subsection{ALCF}
-
-The Automatic Lidar and Ceilometer Framework (ALCF) is a ground-based lidar
-simulator. It performs radiative transfer calculations to derive equivalent
-lidar backscattered radiation in an atmospheric model, which can then be
-compared with observed lidar backscatter \citep{kuma2021}. For this purpose, it
-takes atmospheric fields of cloud fraction, liquid and ice mass mixing ratio,
-temperature, and pressure fields as an input and can be run offline (on the
-model output rather than inside the model code). The lidar simulator in the
-ALCF is based on the instrument simulator Cloud Feedback Model Intercomparison
-Project (CFMIP) Observation Simulator Package (COSP) \citep{bodas-salcedo2011}.
-After the backscattered radiation is calculated, a cloud mask, cloud occurrence
-by height, and the total cloud fraction are determined. ALCF has already been
-used by several research teams for model and reanalysis evaluation
-\citep{kuma2020,kremser2021,guyot2022,pei2023,whitehead2023,mcdonald2024}.
-Absolute calibration of the observed backscatter was performed by comparing the
-measured clear-sky molecular backscatter statistically with simulated clear-sky
-molecular backscatter.
-
-\subsection{Vaisala CL51 and CL31}
-\label{sec:cl51}
-
-The Vaisala CL51 (Fig. \ref{fig:map}d) and CL31 are ceilometers operating at a
-near-infrared wavelength of 910 nm. The maximum range is 15.4 km (CL51), 7.7 km
-(CL31 with 5 m vertical resolution), and 7.550 km (CL31 with 10 m vertical
-resolution).  The vertical resolution is 10 m (5 m configurable). The
-wavelength is affected by water vapour absorption of about 20\% in the
-mid-latitudes \citep{wiegner2015,wiegner2019}.  The instrument data files
-containing uncalibrated backscatter were first converted to NetCDF with cl2nc
-(\url{https://github.com/peterkuma/cl2nc}) and then processed with the ALCF to
-produce a cloud mask and cloud occurrence by height and the total cloud
-fraction. CL51 can also be configured to emulate CL31.
-
-For the MARCUS voyage, Vaisala CL31 was made available by the Atmospheric
-Radiation Measurement (ARM) processed to a maximum range of 7.545 km, a
-vertical resolution of 30 m, and 252 vertical levels.
-
-\subsection{Lufft CHM 15k}
-\label{sec:chm15k}
-
-The Lufft CHM 15k (Fig. \ref{fig:map}c) is a ceilometer operating at a
-near-infrared wavelength of 1064 nm. The maximum range is 15.4 km, the vertical
-resolution is 5 m in the near range (up to 150 m) and 15 m above, the sampling
-rate is 2 s, and the number of vertical levels is 1024.  NetCDF files
-containing uncalibrated backscatter produced by the instrument were processed
-with the ALCF to produce a cloud mask and cloud occurrence by height and the
-total cloud fraction.
-
-% TODO: Check sampling rate.
 
@@
 \begin{tabular}{llllllr}
-\textbf{Name} & \textbf{Vessel} & \textbf{Ceil.} & \textbf{Region} & \textbf{Start} & \textbf{End} & \textbf{Days}\\
+\textbf{Name} & \textbf{Vessel or station} & \textbf{Ceil.} & \textbf{Region} & \textbf{Start} & \textbf{End} & \textbf{Days}\\
 \hline
@@
 MARCUS   & RSV \emph{Aurora Australis}   & CL31    & AU       & 2017-10-29 & 2018-03-26 & 149 \\
-MICRE    & [Macquarie Is. station]       & CL51    & AU/NZ    & 2016-04-03 & 2018-03-14 & 710 \\
+MICRE    & Macquarie Is. station         & CL51    & AU/NZ    & 2016-04-03 & 2018-03-14 & 710 \\
 NBP1704  & RV \emph{Nathaniel B. Palmer} & CHM 15k & NZ       & 2017-04-14 & 2017-06-08 & 55 \\

### 2024-09-25 manuscript.tex
Restructuring methods

@@
 \citep{kuma2020,kremser2021,guyot2022,pei2023,whitehead2023,mcdonald2024}.
+
 Absolute calibration of the observed backscatter was performed by comparing the
@@
 A coupled (atmosphere--ocean) GSRM version of the ICON model is in development
-by the nextGEMS project \citep{hohenegger2023}. nextGEMS has so far produced
-four cycles of model runs. In our research, we used a Cycle 3 run
-\emph{ngc3028} produced in 2023 \citep{nextgems2023a,nextgems2023b}. We could
-not use Cycle 4 due to the unavailability of the necessary variables. The
-horizontal resolution of ngc3028 is about 5 km.  Unlike current general
-circulation models (GCMs), the strom-resolving version of ICON does not use
-convective and cloud parameterisation but relies on explicit simulation of
+by the nextGEMS project \citep{hohenegger2023}. ICON is a very versatile model,
+allowing for simulations ranging from coarse-resolution ESM simulations, GSRM
+simulations, limited area model (LAM) simulations, to large eddy simulations
+(LES), for both weather prediction and climate projections. ICON uses the
+atmospheric component ICON-A \citep{giorgetta2018}, whose physics is derived
+from ECHAM6 \citep{stevens2013}, and the ocean component ICON-O
+\citep{korn2022}. Earlier runs of the GSRM ICON from DYAMOND were evaluated by
+\cite{mauritsen2022}.
+
+Here, we use a free running (i.e. \emph{not} nudged or using prescribed SST)
+coupled GSRM simulation made for the purpse of climate projection.  nextGEMS
+has so far produced four cycles of model runs. We used a Cycle 3 run
+\emph{ngc3028} produced in 2023 \citep{nextgems2023a,nextgems2023b} for a model
+time period of 20 January 2020 to 22 July 2025, of which we analysed the full
+years 2021--2024 (inclusive). While a Cycle 4 run was available, we could not
+use due it to the unavailability of the necessary variables. The horizontal
+resolution of ngc3028 is about 5 km.  The model output is available on 90
+vertical levels and 3-hourly instantaneous temporal resolution.  Unlike current
+general circulation models (GCMs), the strom-resolving version of ICON does not
+use convective and cloud parameterisation but relies on explicit simulation of
 convection and clouds on the model grid. While this makes the code development
@@
 smaller-scale clouds below the grid resolution.  Turbulence and cloud
-microphysics are still parameterised in this model. In our analysis, we used
-four years of coupled simulation output between years 2021 and 2024
-(inclusive). Because the model is free-running, weather and climate
-oscillations (such as the El Niño--Southern Oscillation) are not expected to be
-equivalent to reality at the same time and place. To compare with observations
-taken during different years (2010--2021, inclusive), we compared the model
-output with observations at the same time of year and geographical location.
+microphysics are still parameterised in this model.
 
-ICON is a very versatile model, allowing for simulations ranging from
-coarse-resolution ESM simulations, GSRM simulations, limited area model (LAM)
-simulations, to large eddy simulations (LES), for both weather prediction and
-climate projections.
-
-ICON uses the atmospheric component ICON-A \citep{giorgetta2018}, whose physics
-is derived from ECHAM6 \citep{stevens2013}, and the ocean component ICON-O
-\citep{korn2022}.
-
-Earlier runs of the GSRM ICON from DYAMOND were evaluated by
-\cite{mauritsen2022}.
+Because the model is free-running, weather and climate oscillations (such as
+the El Niño--Southern Oscillation) are not expected to be equivalent to reality
+at the same time and place. To compare with the observations collected on
+different years (2010--2021, inclusive), we compared the model output with
+observations at the same time of year and geographical location, as determined
+for each data point such as a lidar profile or a radiosonde launch.
 
@@
 \citep{rienecker2008,molod2015}. The reanalysis output analysed here is
-available at a spatial resolution of 0.5° in latitude and 0.625° in longitude,
+available at a spatial resolution of 0.5° of latitude and 0.625° of longitude,
 which is about 56 km in the North--South direction and 35 km in the East--West
-direction at 60°S. The number of vertical model levels is 72, which we
-interpolate to height levels as needed. In our analysis we use the following
-products: 1-hourly instantaneous 2D single-level diagnostics (M2I1NXASM) for
-2-m temperature and humidity; 3-hourly instantaneous 3D assimilated
-meteorological fields (M2I3NVASM) for cloud quantities, pressure, and
-temperature; 1-hourly average 2D surface flux diagnostics (M2T1NXFLX) for
+direction at 60°S. The number of vertical model levels is 72. Here, we use the
+following products: 1-hourly instantaneous 2D single-level diagnostics
+(M2I1NXASM) for 2-m temperature and humidity; 3-hourly instantaneous 3D
+assimilated meteorological fields (M2I3NVASM) for cloud quantities, pressure,
+and temperature; 1-hourly average 2D surface flux diagnostics (M2T1NXFLX) for
 precipitation and sea ice; and 1-hourly average 2D radiation diagnostics
@@
 in the North--South direction and 14 km in the East--West direction at 60°S.
-Internally, the model uses 137 vertical levels. In our analysis we use output
-at one hourly instantaeous time intervals, except for radiation quantities,
-which are accumulations (from these we calculate daily means).
-Vertically-resolved quantities are made available on 37 pressure levels. We
-interpolate these quantities to height levels as needed.
+Internally, the model uses 137 vertical levels. Here, we use output at 1-hourly
+instantaeous time intervals, except for radiation quantities, which are
+accumulations (from these we calculate daily means).  Vertically-resolved
+quantities are made available on 37 pressure levels.
 
@@
 
-\subsection{Cyclone tracking}
-
-We partitioned our data into two subsets by cyclonic activity. For this
-purpose, we used a cyclone tracking algorithm to identify extratropical and
-polar cyclones (ECs and PCs) over the SO in the reanalysis and ICON data. We
-used the open source cyclone tracking package CyTRACK
-\citep{perez-alarcon2024}.  Generally, what constitutes an EC is considered
-relatively arbitrary due to the very large variability of ECs \citep{neu2013}.
-We used the mean sea level pressure field and horizontal wind speed fields as
-input to the CyTRACK algorithm. The algorithm uses pressure and wind speed
-thresholds as well as tracking across time steps to identify cyclone centres
-and radii. From this information, we could classify geographical areas as
-either cyclonic or non-cyclonic. Due to a relatively small total area covered,
-we chose a circle of a double radius (relative to one identified by CyTRACK)
-centred at the cyclone centre as a cyclonic area for every time step and
-cyclone. All other areas were identified as non-cyclonic. For identifying
-cyclones in the observations and the reanalyses, ERA5 pressure and wind fields
-were used as the input to CyTRACK.  This is justified by the fact that the
-large-scale pressure and wind fields in ERA5 are likely sufficiently close to
-reality. For identifying cyclones in ICON, its own pressure and wind fields
-were used as the input to CyTRACK, because the model is free-running, and thus
-the pressure and wind fields are different from reality.
-
-\subsection{Cloud occurrence by stability}
-
-We partitioned our data into two subsets by stability. We determined this by
-calculating lower tropospheric stability (LTS) as the difference between the
-potential temperature at 700 hPa and the surface.  Based on a histogram of LTS
-in ERA5 and MERRA-2 calculated at all voyage tracks and stations (Fig.
-\ref{fig:lts}), we determined a dividing threshold of 12 K for relatively
-unstable (< 12 K) and relatively stable (>= 12 K) conditions.
+Radiation calculations presented in the results (Section \ref{sec:results})
+were done in such a way that they always represent averages of daily means.
+This is done in order to be consistent with the CERES SYN1deg data, which are
+available as daily means. Therefore, every instantaneous profile in the
+simulated lidar data is assigned a daily mean radiation value corresponding to
+the day (in the Coordinated Universal Time; UTC). In turn, the average
+radiation during the entire voyage or station observation period is calculated
+as the average of the profile values. In the observed lidar data, the daily
+mean radiation value is taken from the spatially and temporally co-located
+CERES SYN1deg data of the day (in UTC). The voyage or station average is
+calculated in the same way.
 
@@
 
-\subsection{Data processing}
+\subsection{Partitioning by cyclonic activity and stability}
 
-The radiation calculations were done in such a way that they always represent
-averages of daily means. This is done in order to be consistent with the CERES
-SYN1deg data, which are expressed as daily means. Therefore, for every
-instantaneous profile in the simulated lidar data is assigned a daily mean
-radiation value corresponding to the day (in the Coordinated Universal Time;
-UTC). In turn, the average radiation during the entire voyage or station
-measurement is calculated as the average of the profile values. In the observed
-lidar data, the daily mean radiation value is taken from the spatially and
-temporally co-located CERES SYN1deg data for the day (in UTC). The voyage or
-station measurement average is calculated in the same way.
+We partitioned our data into two subsets by cyclonic activity. For this
+purpose, we used a cyclone tracking algorithm to identify extratropical and
+polar cyclones (ECs and PCs) over the SO in the reanalysis and ICON data. We
+used the open source cyclone tracking package CyTRACK
+\citep{perez-alarcon2024}.  Generally, what constitutes an EC is considered
+relatively arbitrary due to the very large variability of ECs \citep{neu2013}.
+We used the mean sea level pressure field and horizontal wind speed fields as
+input to the CyTRACK algorithm. The algorithm uses pressure and wind speed
+thresholds as well as tracking across time steps to identify cyclone centres
+and radii. From this information, we could classify geographical areas as
+either cyclonic or non-cyclonic. Due to a relatively small total area covered,
+we chose a circle of a double radius (relative to one identified by CyTRACK)
+centred at the cyclone centre as a cyclonic area for every time step and
+cyclone. All other areas were identified as non-cyclonic. For identifying
+cyclones in the observations and the reanalyses, ERA5 pressure and wind fields
+were used as the input to CyTRACK.  This is justified by the fact that the
+large-scale pressure and wind fields in ERA5 are likely sufficiently close to
+reality. For identifying cyclones in ICON, its own pressure and wind fields
+were used as the input to CyTRACK, because the model is free-running, and thus
+the pressure and wind fields are different from reality.
+
+In addition to the above, we partitioned our data into two subsets by
+stability. We determined this by calculating lower tropospheric stability (LTS)
+as the difference between the potential temperature at 700 hPa and the surface.
+Based on a histogram of LTS in ERA5 and MERRA-2 calculated at all voyage tracks
+and stations (Fig.  \ref{fig:lts}), we determined a dividing threshold of 12 K
+for relatively unstable (< 12 K) and relatively stable (>= 12 K) conditions.
 

### 2024-09-25 manuscript.tex
Rearrange figures and tables

@@
 
-\begin{figure}
+\begin{figure}[b!]
 \centering
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{img/example.png}
-\caption{
-An example of attenuated volume backscattering coefficient (AVBC) \textbf{(a)}
-measured by CL51 during 24 hours on the PS81/3 voyage and \textbf{(b)} an
-equivalent AVBC simulated with the ALCF from ERA5 data during the same time
-period. Shown is also the cloud mask determined by the ALCF.
-}
-\label{fig:example}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{img/ann.pdf}
-\caption{
-Artificial neural network (ANN) for prediction of precipitation in lidar
-backscatter. \textbf{(a)} Diagram showing the TensorFlow structure of the ANN,
-\textbf{(b)} randomly selected example samples of near-surface backscatter in
-four categories (clear, fog, rain and snow), as determined by coincident
-human-performed weather observations, \textbf{(c)} receiver operating
-characteristic diagram of the ANN, \textbf{(d)} examples of 10-day time series
-of human-observed (`HUM') and predicted precipitation based on an ANN trained
-on all voyages (`ANN') and all voyages except for the shown voyage (`ANN2')
-during three randomly selected voyages with the available data. Here, by
-`randomly selected' we mean selected from the top of a permutation generated by
-a pseudo-random number generator to prevent authors' bias in the selection.
-}
-\label{fig:ann}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{img/lts_dist.pdf}
-\caption{
-Lower tropospheric stability (LTS) distribution in \textbf{(a)} ERA5 and
-\textbf{(b)} MERRA-2 calculated for the 31 voyage tracks and one station from
-the highest instantaneous temporal resolution data available. Shown is also the
-chosen dividing threshold of 12 K for `stable' and `unstable' conditions.
-}
-\label{fig:lts}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{img/cyc_stab_dist.pdf}
-\caption{
-Geographical distribution of \textbf{(a, b)} cyclonic days and \textbf{(b, d)}
-relatively stable (LTS > 12 K) time steps in \textbf{(a, c)} ERA5 in years
-2010--2013 (inclusive) and \textbf{(b, d)} ICON in model years 2021--2023 (free
-running). Cyclonic days are expressed as a fraction of the number of days with
-cyclonic activity, defined as grid points located within a double radius of any
-cyclone on a given day (UTC), as identified by CyTRACK.
-}
-\label{fig:lts}
-\end{figure}
-
 \section{Methods}
@@
 sub-Antarctic station (Macquarie Island) in the SO south of 40°S between 2010
-and 2021. Fig. \ref{fig:map} shows a map of the voyages, Table \ref{tab:voyages}
-list the voyages and stations, and \ref{tab:voyage-references} lists references
-where available. Altogether, the voyages and station dataset comprised
-2421 days of data south of 40°S, but the availability of ceilometer data was
-slightly smaller due to gaps in measurements.
+and 2021. Fig. \ref{fig:map} shows a map of the voyages, Table
+\ref{tab:voyages} list the voyages and stations, and Table
+\ref{tab:voyage-references} lists references where available. Altogether, the
+voyages and station dataset comprised 2421 days of data south of 40°S, but the
+availability of ceilometer data was slightly smaller due to gaps in
+measurements.
 
@@
 
-\subsection{Vaisala CL51 and CL31}
-\label{sec:cl51}
-
-The Vaisala CL51 (photo in Fig. \ref{fig:map}d) and CL31 are ceilometers
-operating at a near-infrared wavelength of 910 nm. The maximum range is 15.4 km
-(CL51), 7.7 km (CL31 with 5 m vertical resolution), and 7.550 km (CL31 with 10
-m vertical resolution). The vertical resolution is 10 m (5 m configurable), and
-the sampling (temporal) resolution is 6 s (AA15‐16, MARCUS, and MICRE), 36 s (RV
-\emph{Polarstern}), and about 2.37 s (TAN1502). From the MARCUS voyage, unlike raw
-instrument data available for the other voyages and stations, the Vaisala CL31
-data were made available by the Atmospheric Radiation Measurement (ARM)
-processed to a maximum range of 7.545 km, a vertical resolution of 30 m, and
-sampling resolution of 16 s. The wavelength of 910 nm is affected by water
-vapour absorption of about 20\% in the mid-latitudes
-\citep{wiegner2015,wiegner2019}.  The instrument data files containing raw
-uncalibrated backscatter were first converted to NetCDF with cl2nc
-(\url{https://github.com/peterkuma/cl2nc}) and then processed with the ALCF
-(Section \ref{sec:alcf}) to produce absolutely calibrated attenuated volume
-backscattering coefficinet (AVBC), cloud mask, cloud occurrence by height and
-the total cloud fraction. CL51 can also be configured to emulate CL31. The
-Vaisala CL51 and CL31 instruments were used on most of the voyages and stations
-analysed here. Fig. \ref{fig:example}a shows an example of derived from the
-CL51 instrument.
-
-\subsection{Lufft CHM 15k}
-\label{sec:chm15k}
-
-The Lufft CHM 15k (photo in Fig. \ref{fig:map}c) is a ceilometer operating at a
-near-infrared wavelength of 1064 nm. The maximum range is 15.4 km, the vertical
-resolution is 5 m in the near range (up to 150 m) and 15 m above, the sampling
-(temporal) resolution is 2 s, and the number of vertical levels is 1024.
-NetCDF files containing uncalibrated backscatter produced by the instrument
-were processed with the ALCF (Section \ref{sec:alcf}) to produce AVBC, cloud
-mask, cloud occurrence by height and the total cloud fraction. The CHM 15k was
-used on a minority of voyages (HMNZSW16, TAN1702, TAN1802, and NBP1704).
-
-\subsection{ALCF}
-\label{sec:alcf}
-
-The Automatic Lidar and Ceilometer Framework (ALCF) is a ground-based lidar
-simulator and a tool for processing observed lidar data, supporting various
-instruments and models. It performs radiative transfer calculations to derive
-equivalent lidar AVBC in an atmospheric model, which can then be compared with
-observed AVBC \citep{kuma2021}. For this purpose, it takes atmospheric fields
-of cloud fraction, liquid and ice mass mixing ratio, temperature, and pressure
-fields as an input and can be run offline (on the model output rather than
-inside the model code). The lidar simulator in the ALCF is based on the
-instrument simulator Cloud Feedback Model Intercomparison Project (CFMIP)
-Observation Simulator Package (COSP) \citep{bodas-salcedo2011}.  After AVBC is
-calculated, a cloud mask, cloud occurrence by height, and the total cloud
-fraction are determined. The ALCF has already been used by several research
-teams for model and reanalysis evaluation
-\citep{kuma2020,kremser2021,guyot2022,pei2023,whitehead2023,mcdonald2024}.
-
-Absolute calibration of the observed backscatter was performed by comparing the
-measured clear-sky molecular backscatter statistically with simulated clear-sky
-molecular backscatter. AVBC is resampled to 5 min temporal resolution and 50 m
-vertical resolution to increase signal-to-noise ratio, while having enough
-resolution to detect small-scale cloud variability. Noise standard deviation is
-calculated from AVBC at the highest range, where no clouds are expected.  A
-cloud mask is calculated from AVBC using a fixed threshold of $\mathrm{2\times
-10^{-6} m^{-1}sr^{-1}}$ after subtracting 5 standard deviations of range-scale
-noise. Fig. \ref{fig:example}b shows an example of simulated Vaisala CL51
-backscatter from ERA5 data, corresponding to a day of measurements by the
-instrument on the PS81/3 voyage.
-
-\subsection{ICON}
-
-A coupled (atmosphere--ocean) GSRM version of the ICON model is in development
-by the nextGEMS project \citep{hohenegger2023}. ICON is a very versatile model,
-allowing for simulations ranging from coarse-resolution ESM simulations, GSRM
-simulations, limited area model (LAM) simulations, to large eddy simulations
-(LES), for both weather prediction and climate projections. ICON uses the
-atmospheric component ICON-A \citep{giorgetta2018}, whose physics is derived
-from ECHAM6 \citep{stevens2013}, and the ocean component ICON-O
-\citep{korn2022}. Earlier runs of the GSRM ICON from DYAMOND were evaluated by
-\cite{mauritsen2022}.
-
-Here, we use a free running (i.e. \emph{not} nudged or using prescribed SST)
-coupled GSRM simulation made for the purpse of climate projection.  nextGEMS
-has so far produced four cycles of model runs. We used a Cycle 3 run
-\emph{ngc3028} produced in 2023 \citep{nextgems2023a,nextgems2023b} for a model
-time period of 20 January 2020 to 22 July 2025, of which we analysed the full
-years 2021--2024 (inclusive). While a Cycle 4 run was available, we could not
-use due it to the unavailability of the necessary variables. The horizontal
-resolution of ngc3028 is about 5 km.  The model output is available on 90
-vertical levels and 3-hourly instantaneous temporal resolution.  Unlike current
-general circulation models (GCMs), the strom-resolving version of ICON does not
-use convective and cloud parameterisation but relies on explicit simulation of
-convection and clouds on the model grid. While this makes the code development
-simpler without having to rely on uncertain parameterisations, it can miss
-smaller-scale clouds below the grid resolution.  Turbulence and cloud
-microphysics are still parameterised in this model.
-
-Because the model is free-running, weather and climate oscillations (such as
-the El Niño--Southern Oscillation) are not expected to be equivalent to reality
-at the same time and place. To compare with the observations collected on
-different years (2010--2021, inclusive), we compared the model output with
-observations at the same time of year and geographical location, as determined
-for each data point such as a lidar profile or a radiosonde launch.
-
-\subsection{MERRA-2}
-
-The Modern-Era Retrospective analysis for Research and Applications, Version 2
-(MERRA-2) is a reanalysis produced by the Global Modeling and Assimilation
-Office at the NASA Goddard Space Flight Center \citep{gelaro2017}.  It uses
-version 5.12.4 of the Goddard Earth Observing System (GEOS) atmospheric model
-\citep{rienecker2008,molod2015}. The reanalysis output analysed here is
-available at a spatial resolution of 0.5° of latitude and 0.625° of longitude,
-which is about 56 km in the North--South direction and 35 km in the East--West
-direction at 60°S. The number of vertical model levels is 72. Here, we use the
-following products: 1-hourly instantaneous 2D single-level diagnostics
-(M2I1NXASM) for 2-m temperature and humidity; 3-hourly instantaneous 3D
-assimilated meteorological fields (M2I3NVASM) for cloud quantities, pressure,
-and temperature; 1-hourly average 2D surface flux diagnostics (M2T1NXFLX) for
-precipitation and sea ice; and 1-hourly average 2D radiation diagnostics
-(M2T1NXRAD) for radiation quantities \citep{merra2}.
-
-\subsection{ERA5}
-
-ERA5 \citep{era5} is a reanalysis produced by the European Centre for
-Medium-Range Weather Forecasts (ECMWF). It is based on a numerical weather
-prediction (NWP) model Integrated Forecast System (IFS) version CY41R2.  The
-horizontal resolution is 0.25° in latitude and longitude, which is about 28 km
-in the North--South direction and 14 km in the East--West direction at 60°S.
-Internally, the model uses 137 vertical levels. Here, we use output at 1-hourly
-instantaeous time intervals, except for radiation quantities, which are
-accumulations (from these we calculate daily means).  Vertically-resolved
-quantities are made available on 37 pressure levels.
-
-\subsection{CERES}
-
-TOA radiation quantities are taken from the Clouds and the Earth’s Radiant
-Energy System (CERES) instruments on board of the Terra and Aqua satellites
-\citep{wielicki1996,loeb2018}. In our analysis we use the adjusted all sky SW
-and LW upwelling fluxes at TOA from the synoptic TOA and surface fluxes and
-clouds 1 degree daily edition 4A product
-(CER\_SYN1deg-Day\_Terra-Aqua-MODIS\_Edition4A)
-\citep{doelling2013,doelling2016}.
-
-Radiation calculations presented in the results (Section \ref{sec:results})
-were done in such a way that they always represent averages of daily means.
-This is done in order to be consistent with the CERES SYN1deg data, which are
-available as daily means. Therefore, every instantaneous profile in the
-simulated lidar data is assigned a daily mean radiation value corresponding to
-the day (in the Coordinated Universal Time; UTC). In turn, the average
-radiation during the entire voyage or station observation period is calculated
-as the average of the profile values. In the observed lidar data, the daily
-mean radiation value is taken from the spatially and temporally co-located
-CERES SYN1deg data of the day (in UTC). The voyage or station average is
-calculated in the same way.
-
-\subsection{Precipitation identification using machine learning}
-\label{sec:ann}
-
-Precipitation can cause strong enough lidar backscattering to be recognised as
-a cloud by the threshold-based cloud detection method used in the ALCF. This is
-undesirable if equivalent precipitation backscatter is not included in the
-simulated lidar profiles. It was not possible to include precipitation
-simulation in the ALCF due to the absence of required fields in the ICON model
-output and the reanalysis data (the liquid and ice precipitation mass mixing
-ratios), and because the required radiation calculations for precipitation are
-currently not implemented in the ALCF. In order to achieve a fair comparison of
-observations with models, one should exclude observed and simulated lidar
-profiles with precipitation either manually or using an automated method. It is
-relatively difficult to distinguish precipitation backscatter from cloud
-backscatter in lidar observations, especially when only one wavelength channel
-and no polarised channel are available. In models, the same can be accomplished
-relatively easily by excluding profiles exceeding a certain amount of surface
-precipitation flux. In the observations, using precipitation flux measurements
-from rain gauges can be very unreliable on ships due to ship movement and
-turbulence caused by nearby ship structures. Our analysis of rain gauge data
-from the RV \emph{Tangaroa} showed large discrepancies between the rain gauge
-time series and human-performed synoptic observations, as well as large
-inconsistencies in the rain gauge time series. Human-performed observations of
-precipitation presence or absence are expected to be reliable, but only cover a
-limited set of time instants. Therefore, it was desirable to implement a method
-of detecting precipitation from observed backscatter profiles alone.
-
-On the RV \emph{Polarstern} voyages, regular human-performed synoptic
-observations were available and included precipitation presence or absence and
-type. We used this dataset to train a convolutional artiﬁcial neural network
-(ANN) of the U-Net type \citep{ronneberger2015} to recognise profiles with
-precipitation from lidar backscatter (Fig. \ref{fig:ann}a), implemented in the
-TensorFlow ANN framework \citep{tensorflow}. Samples of short time intervals
-(10 min) of near-surface lidar backscatter (0–250 m) were classified as clear,
-rain, snow, and fog, using the synoptic observations as a training dataset
-(Fig.  \ref{fig:ann}b). From these, a binary, mutually exclusive classification
-of profiles as precipitating (rain or snow) or dry (clear or fog) was derived.
-For detecting model and reanalysis precipitation, we used a fixed threshold for
-surface precipitation flux of 0.1 mm h$^{-1}$ (the ANN was not used).
-
-The ANN achieved 65\% sensitivity and 87\% speciﬁcity when the true positive
-rate (26\%) was made to match observations. The receiver operating
-characteristic curve is shown in Fig. \ref{fig:ann}c. We considered these rates
-satisfactory for the purpose of filtering precipitation profiles. Fig.
-\ref{fig:ann}d shows examples of the predicted precipitation compared to
-human-performed observations.
-
-\subsection{Partitioning by cyclonic activity and stability}
-
-We partitioned our data into two subsets by cyclonic activity. For this
-purpose, we used a cyclone tracking algorithm to identify extratropical and
-polar cyclones (ECs and PCs) over the SO in the reanalysis and ICON data. We
-used the open source cyclone tracking package CyTRACK
-\citep{perez-alarcon2024}.  Generally, what constitutes an EC is considered
-relatively arbitrary due to the very large variability of ECs \citep{neu2013}.
-We used the mean sea level pressure field and horizontal wind speed fields as
-input to the CyTRACK algorithm. The algorithm uses pressure and wind speed
-thresholds as well as tracking across time steps to identify cyclone centres
-and radii. From this information, we could classify geographical areas as
-either cyclonic or non-cyclonic. Due to a relatively small total area covered,
-we chose a circle of a double radius (relative to one identified by CyTRACK)
-centred at the cyclone centre as a cyclonic area for every time step and
-cyclone. All other areas were identified as non-cyclonic. For identifying
-cyclones in the observations and the reanalyses, ERA5 pressure and wind fields
-were used as the input to CyTRACK.  This is justified by the fact that the
-large-scale pressure and wind fields in ERA5 are likely sufficiently close to
-reality. For identifying cyclones in ICON, its own pressure and wind fields
-were used as the input to CyTRACK, because the model is free-running, and thus
-the pressure and wind fields are different from reality.
-
-In addition to the above, we partitioned our data into two subsets by
-stability. We determined this by calculating lower tropospheric stability (LTS)
-as the difference between the potential temperature at 700 hPa and the surface.
-Based on a histogram of LTS in ERA5 and MERRA-2 calculated at all voyage tracks
-and stations (Fig.  \ref{fig:lts}), we determined a dividing threshold of 12 K
-for relatively unstable (< 12 K) and relatively stable (>= 12 K) conditions.
-
-\section{Results}
-\label{sec:results}
-
-\begin{table}
+\begin{table}[p!]
 % TODO: Add sampling intervals.
@@
 
-\begin{table}
+\begin{table}[t!]
 \caption{List of voyage and station references.}
@@
 
-\begin{figure}
+\subsection{Vaisala CL51 and CL31}
+\label{sec:cl51}
+
+The Vaisala CL51 (photo in Fig. \ref{fig:map}d) and CL31 are ceilometers
+operating at a near-infrared wavelength of 910 nm. The maximum range is 15.4 km
+(CL51), 7.7 km (CL31 with 5 m vertical resolution), and 7.550 km (CL31 with 10
+m vertical resolution). The vertical resolution is 10 m (5 m configurable), and
+the sampling (temporal) resolution is 6 s (AA15‐16, MARCUS, and MICRE), 36 s (RV
+\emph{Polarstern}), and about 2.37 s (TAN1502). From the MARCUS voyage, unlike raw
+instrument data available for the other voyages and stations, the Vaisala CL31
+data were made available by the Atmospheric Radiation Measurement (ARM)
+processed to a maximum range of 7.545 km, a vertical resolution of 30 m, and
+sampling resolution of 16 s. The wavelength of 910 nm is affected by water
+vapour absorption of about 20\% in the mid-latitudes
+\citep{wiegner2015,wiegner2019}.  The instrument data files containing raw
+uncalibrated backscatter were first converted to NetCDF with cl2nc
+(\url{https://github.com/peterkuma/cl2nc}) and then processed with the ALCF
+(Section \ref{sec:alcf}) to produce absolutely calibrated attenuated volume
+backscattering coefficinet (AVBC), cloud mask, cloud occurrence by height and
+the total cloud fraction. CL51 can also be configured to emulate CL31. The
+Vaisala CL51 and CL31 instruments were used on most of the voyages and stations
+analysed here. Fig. \ref{fig:example}a shows an example of derived from the
+CL51 instrument.
+
+\begin{figure}[b!]
+\centering
+\includegraphics[width=\textwidth]{img/example.png}
+\caption{
+An example of attenuated volume backscattering coefficient (AVBC) \textbf{(a)}
+measured by CL51 during 24 hours on the PS81/3 voyage and \textbf{(b)} an
+equivalent AVBC simulated with the ALCF from ERA5 data during the same time
+period. Shown is also the cloud mask determined by the ALCF.
+}
+\label{fig:example}
+\end{figure}
+
+\subsection{Lufft CHM 15k}
+\label{sec:chm15k}
+
+The Lufft CHM 15k (photo in Fig. \ref{fig:map}c) is a ceilometer operating at a
+near-infrared wavelength of 1064 nm. The maximum range is 15.4 km, the vertical
+resolution is 5 m in the near range (up to 150 m) and 15 m above, the sampling
+(temporal) resolution is 2 s, and the number of vertical levels is 1024.
+NetCDF files containing uncalibrated backscatter produced by the instrument
+were processed with the ALCF (Section \ref{sec:alcf}) to produce AVBC, cloud
+mask, cloud occurrence by height and the total cloud fraction. The CHM 15k was
+used on a minority of voyages (HMNZSW16, TAN1702, TAN1802, and NBP1704).
+
+\subsection{ALCF}
+\label{sec:alcf}
+
+The Automatic Lidar and Ceilometer Framework (ALCF) is a ground-based lidar
+simulator and a tool for processing observed lidar data, supporting various
+instruments and models. It performs radiative transfer calculations to derive
+equivalent lidar AVBC in an atmospheric model, which can then be compared with
+observed AVBC \citep{kuma2021}. For this purpose, it takes atmospheric fields
+of cloud fraction, liquid and ice mass mixing ratio, temperature, and pressure
+fields as an input and can be run offline (on the model output rather than
+inside the model code). The lidar simulator in the ALCF is based on the
+instrument simulator Cloud Feedback Model Intercomparison Project (CFMIP)
+Observation Simulator Package (COSP) \citep{bodas-salcedo2011}.  After AVBC is
+calculated, a cloud mask, cloud occurrence by height, and the total cloud
+fraction are determined. The ALCF has already been used by several research
+teams for model and reanalysis evaluation
+\citep{kuma2020,kremser2021,guyot2022,pei2023,whitehead2023,mcdonald2024}.
+
+Absolute calibration of the observed backscatter was performed by comparing the
+measured clear-sky molecular backscatter statistically with simulated clear-sky
+molecular backscatter. AVBC is resampled to 5 min temporal resolution and 50 m
+vertical resolution to increase signal-to-noise ratio, while having enough
+resolution to detect small-scale cloud variability. Noise standard deviation is
+calculated from AVBC at the highest range, where no clouds are expected.  A
+cloud mask is calculated from AVBC using a fixed threshold of $\mathrm{2\times
+10^{-6} m^{-1}sr^{-1}}$ after subtracting 5 standard deviations of range-scale
+noise. Fig. \ref{fig:example}b shows an example of simulated Vaisala CL51
+backscatter from ERA5 data, corresponding to a day of measurements by the
+instrument on the PS81/3 voyage.
+
+\subsection{ICON}
+
+A coupled (atmosphere--ocean) GSRM version of the ICON model is in development
+by the nextGEMS project \citep{hohenegger2023}. ICON is a very versatile model,
+allowing for simulations ranging from coarse-resolution ESM simulations, GSRM
+simulations, limited area model (LAM) simulations, to large eddy simulations
+(LES), for both weather prediction and climate projections. ICON uses the
+atmospheric component ICON-A \citep{giorgetta2018}, whose physics is derived
+from ECHAM6 \citep{stevens2013}, and the ocean component ICON-O
+\citep{korn2022}. Earlier runs of the GSRM ICON from DYAMOND were evaluated by
+\cite{mauritsen2022}.
+
+Here, we use a free running (i.e. \emph{not} nudged or using prescribed SST)
+coupled GSRM simulation made for the purpse of climate projection.  nextGEMS
+has so far produced four cycles of model runs. We used a Cycle 3 run
+\emph{ngc3028} produced in 2023 \citep{nextgems2023a,nextgems2023b} for a model
+time period of 20 January 2020 to 22 July 2025, of which we analysed the full
+years 2021--2024 (inclusive). While a Cycle 4 run was available, we could not
+use due it to the unavailability of the necessary variables. The horizontal
+resolution of ngc3028 is about 5 km.  The model output is available on 90
+vertical levels and 3-hourly instantaneous temporal resolution.  Unlike current
+general circulation models (GCMs), the strom-resolving version of ICON does not
+use convective and cloud parameterisation but relies on explicit simulation of
+convection and clouds on the model grid. While this makes the code development
+simpler without having to rely on uncertain parameterisations, it can miss
+smaller-scale clouds below the grid resolution.  Turbulence and cloud
+microphysics are still parameterised in this model.
+
+Because the model is free-running, weather and climate oscillations (such as
+the El Niño--Southern Oscillation) are not expected to be equivalent to reality
+at the same time and place. To compare with the observations collected on
+different years (2010--2021, inclusive), we compared the model output with
+observations at the same time of year and geographical location, as determined
+for each data point such as a lidar profile or a radiosonde launch.
+
+\subsection{MERRA-2}
+
+The Modern-Era Retrospective analysis for Research and Applications, Version 2
+(MERRA-2) is a reanalysis produced by the Global Modeling and Assimilation
+Office at the NASA Goddard Space Flight Center \citep{gelaro2017}.  It uses
+version 5.12.4 of the Goddard Earth Observing System (GEOS) atmospheric model
+\citep{rienecker2008,molod2015}. The reanalysis output analysed here is
+available at a spatial resolution of 0.5° of latitude and 0.625° of longitude,
+which is about 56 km in the North--South direction and 35 km in the East--West
+direction at 60°S. The number of vertical model levels is 72. Here, we use the
+following products: 1-hourly instantaneous 2D single-level diagnostics
+(M2I1NXASM) for 2-m temperature and humidity; 3-hourly instantaneous 3D
+assimilated meteorological fields (M2I3NVASM) for cloud quantities, pressure,
+and temperature; 1-hourly average 2D surface flux diagnostics (M2T1NXFLX) for
+precipitation and sea ice; and 1-hourly average 2D radiation diagnostics
+(M2T1NXRAD) for radiation quantities \citep{merra2}.
+
+\subsection{ERA5}
+
+ERA5 \citep{era5} is a reanalysis produced by the European Centre for
+Medium-Range Weather Forecasts (ECMWF). It is based on a numerical weather
+prediction (NWP) model Integrated Forecast System (IFS) version CY41R2.  The
+horizontal resolution is 0.25° in latitude and longitude, which is about 28 km
+in the North--South direction and 14 km in the East--West direction at 60°S.
+Internally, the model uses 137 vertical levels. Here, we use output at 1-hourly
+instantaeous time intervals, except for radiation quantities, which are
+accumulations (from these we calculate daily means).  Vertically-resolved
+quantities are made available on 37 pressure levels.
+
+\subsection{CERES}
+
+TOA radiation quantities are taken from the Clouds and the Earth’s Radiant
+Energy System (CERES) instruments on board of the Terra and Aqua satellites
+\citep{wielicki1996,loeb2018}. In our analysis we use the adjusted all sky SW
+and LW upwelling fluxes at TOA from the synoptic TOA and surface fluxes and
+clouds 1 degree daily edition 4A product
+(CER\_SYN1deg-Day\_Terra-Aqua-MODIS\_Edition4A)
+\citep{doelling2013,doelling2016}.
+
+Radiation calculations presented in the results (Section \ref{sec:results})
+were done in such a way that they always represent averages of daily means.
+This is done in order to be consistent with the CERES SYN1deg data, which are
+available as daily means. Therefore, every instantaneous profile in the
+simulated lidar data is assigned a daily mean radiation value corresponding to
+the day (in the Coordinated Universal Time; UTC). In turn, the average
+radiation during the entire voyage or station observation period is calculated
+as the average of the profile values. In the observed lidar data, the daily
+mean radiation value is taken from the spatially and temporally co-located
+CERES SYN1deg data of the day (in UTC). The voyage or station average is
+calculated in the same way.
+
+\begin{figure}[b!]
+\centering
+\includegraphics[width=\textwidth]{img/ann.pdf}
+\caption{
+Artificial neural network (ANN) for prediction of precipitation in lidar
+backscatter. \textbf{(a)} Diagram showing the TensorFlow structure of the ANN,
+\textbf{(b)} randomly selected example samples of near-surface backscatter in
+four categories (clear, fog, rain and snow), as determined by coincident
+human-performed weather observations, \textbf{(c)} receiver operating
+characteristic diagram of the ANN, \textbf{(d)} examples of 10-day time series
+of human-observed (`HUM') and predicted precipitation based on an ANN trained
+on all voyages (`ANN') and all voyages except for the shown voyage (`ANN2')
+during three randomly selected voyages with the available data. Here, by
+`randomly selected' we mean selected from the top of a permutation generated by
+a pseudo-random number generator to prevent authors' bias in the selection.
+}
+\label{fig:ann}
+\end{figure}
+
+\subsection{Precipitation identification using machine learning}
+\label{sec:ann}
+
+Precipitation can cause strong enough lidar backscattering to be recognised as
+a cloud by the threshold-based cloud detection method used in the ALCF. This is
+undesirable if equivalent precipitation backscatter is not included in the
+simulated lidar profiles. It was not possible to include precipitation
+simulation in the ALCF due to the absence of required fields in the ICON model
+output and the reanalysis data (the liquid and ice precipitation mass mixing
+ratios), and because the required radiation calculations for precipitation are
+currently not implemented in the ALCF. In order to achieve a fair comparison of
+observations with models, one should exclude observed and simulated lidar
+profiles with precipitation either manually or using an automated method. It is
+relatively difficult to distinguish precipitation backscatter from cloud
+backscatter in lidar observations, especially when only one wavelength channel
+and no polarised channel are available. In models, the same can be accomplished
+relatively easily by excluding profiles exceeding a certain amount of surface
+precipitation flux. In the observations, using precipitation flux measurements
+from rain gauges can be very unreliable on ships due to ship movement and
+turbulence caused by nearby ship structures. Our analysis of rain gauge data
+from the RV \emph{Tangaroa} showed large discrepancies between the rain gauge
+time series and human-performed synoptic observations, as well as large
+inconsistencies in the rain gauge time series. Human-performed observations of
+precipitation presence or absence are expected to be reliable, but only cover a
+limited set of time instants. Therefore, it was desirable to implement a method
+of detecting precipitation from observed backscatter profiles alone.
+
+On the RV \emph{Polarstern} voyages, regular human-performed synoptic
+observations were available and included precipitation presence or absence and
+type. We used this dataset to train a convolutional artiﬁcial neural network
+(ANN) of the U-Net type \citep{ronneberger2015} to recognise profiles with
+precipitation from lidar backscatter (Fig. \ref{fig:ann}a), implemented in the
+TensorFlow ANN framework \citep{tensorflow}. Samples of short time intervals
+(10 min) of near-surface lidar backscatter (0–250 m) were classified as clear,
+rain, snow, and fog, using the synoptic observations as a training dataset
+(Fig.  \ref{fig:ann}b). From these, a binary, mutually exclusive classification
+of profiles as precipitating (rain or snow) or dry (clear or fog) was derived.
+For detecting model and reanalysis precipitation, we used a fixed threshold for
+surface precipitation flux of 0.1 mm h$^{-1}$ (the ANN was not used).
+
+The ANN achieved 65\% sensitivity and 87\% speciﬁcity when the true positive
+rate (26\%) was made to match observations. The receiver operating
+characteristic curve is shown in Fig. \ref{fig:ann}c. We considered these rates
+satisfactory for the purpose of filtering precipitation profiles. Fig.
+\ref{fig:ann}d shows examples of the predicted precipitation compared to
+human-performed observations.
+
+\begin{figure}[b!]
+\centering
+\includegraphics[width=\textwidth]{img/lts_dist.pdf}
+\caption{
+Lower tropospheric stability (LTS) distribution in \textbf{(a)} ERA5 and
+\textbf{(b)} MERRA-2 calculated for the 31 voyage tracks and one station from
+the highest instantaneous temporal resolution data available. Shown is also the
+chosen dividing threshold of 12 K for `stable' and `unstable' conditions.
+}
+\label{fig:lts}
+\end{figure}
+
+\subsection{Partitioning by cyclonic activity and stability}
+
+We partitioned our data into two subsets by cyclonic activity. For this
+purpose, we used a cyclone tracking algorithm to identify extratropical and
+polar cyclones (ECs and PCs) over the SO in the reanalysis and ICON data. We
+used the open source cyclone tracking package CyTRACK
+\citep{perez-alarcon2024}.  Generally, what constitutes an EC is considered
+relatively arbitrary due to the very large variability of ECs \citep{neu2013}.
+We used the mean sea level pressure field and horizontal wind speed fields as
+input to the CyTRACK algorithm. The algorithm uses pressure and wind speed
+thresholds as well as tracking across time steps to identify cyclone centres
+and radii. From this information, we could classify geographical areas as
+either cyclonic or non-cyclonic. Due to a relatively small total area covered,
+we chose a circle of a double radius (relative to one identified by CyTRACK)
+centred at the cyclone centre as a cyclonic area for every time step and
+cyclone. All other areas were identified as non-cyclonic. For identifying
+cyclones in the observations and the reanalyses, ERA5 pressure and wind fields
+were used as the input to CyTRACK.  This is justified by the fact that the
+large-scale pressure and wind fields in ERA5 are likely sufficiently close to
+reality. For identifying cyclones in ICON, its own pressure and wind fields
+were used as the input to CyTRACK, because the model is free-running, and thus
+the pressure and wind fields are different from reality.
+
+In addition to the above, we partitioned our data into two subsets by
+stability. We determined this by calculating lower tropospheric stability (LTS)
+as the difference between the potential temperature at 700 hPa and the surface.
+Based on a histogram of LTS in ERA5 and MERRA-2 calculated at all voyage tracks
+and stations (Fig.  \ref{fig:lts}), we determined a dividing threshold of 12 K
+for relatively unstable (< 12 K) and relatively stable (>= 12 K) conditions.
+
+\section{Results}
+\label{sec:results}
+
+\begin{figure}[b!]
+\centering
+\includegraphics[width=\textwidth]{img/cyc_stab_dist.pdf}
+\caption{
+Geographical distribution of \textbf{(a, b)} cyclonic days and \textbf{(b, d)}
+relatively stable (LTS > 12 K) time steps in \textbf{(a, c)} ERA5 in years
+2010--2013 (inclusive) and \textbf{(b, d)} ICON in model years 2021--2023 (free
+running). Cyclonic days are expressed as a fraction of the number of days with
+cyclonic activity, defined as grid points located within a double radius of any
+cyclone on a given day (UTC), as identified by CyTRACK.
+}
+\label{fig:cyclone-stability}
+\end{figure}
+
+\subsection{Cyclonic activity and stability}
+
+Here, we briefly describe the results of the cyclonic activity and stability
+distribution, which is relavant for the subsequent analaysis, because these
+quantities are used for subsetting our dataset.  Fig.
+\ref{fig:cyclone-stability}a shows a geographical distribution of the fraction
+of cyclonic days as determined by the cyclone tracking algorithm applied on the
+ERA5 reanalysis and ICON data. As expected the strongest cyclonic activity is
+in the high-latitude SO zone, and it is relatively zonally symmetric at all
+latitudes.  While both reanalysis and the model agree relatively well,
+differences in the strength of the local extremes of occurrence are notable,
+especially over the Amundsen Sea, which is more cyclonic in the reanalysis, and
+around Cape Adere, which is more cyclonic in ICON. There differences might,
+however, stem from the relatively short time periods of comparison (4 year) and
+the fact that the model is free running.
+
+Fig. \ref{fig:cyclone-stability}b shows a geographical distribution of the LTS.
+
+\begin{figure}[p!]
 \centerline{
@@
 
-\begin{figure}
+\begin{figure}[p!]
 \centering
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{img/clt_hist.pdf}
-\caption{
-Daily total cloud fraction histograms calculated as the average of all voyage
-and station histograms. The total cloud fraction of a day (UTC) is calculated
-as a fraction of cloudy (based on the cloud mask) observed (OBS) or simulated
-lidar profiles. The models and subsets are as in Fig.
-\ref{fig:cloud-occurrence}.
-}
-\label{fig:cloud-cover}
-\end{figure}
-
 \subsection{Cloud cover}
@@
 observations peak at 7 octas and show negligible cloud cover below 5 octas.
+
+\begin{figure}[p!]
+\centering
+\includegraphics[width=\textwidth]{img/clt_hist.pdf}
+\caption{
+Daily total cloud fraction histograms calculated as the average of all voyage
+and station histograms. The total cloud fraction of a day (UTC) is calculated
+as a fraction of cloudy (based on the cloud mask) observed (OBS) or simulated
+lidar profiles. The models and subsets are as in Fig.
+\ref{fig:cloud-occurrence}.
+}
+\label{fig:cloud-cover}
+\end{figure}
+
+\begin{figure}[p!]
+\centering
+\includegraphics[width=0.72\textwidth]{img/theta_hur.pdf}
+\caption{
+Virtual potential temperature ($\theta_v$) and relative humidity (RH)
+determined from radiosonde launches and co-located profiles in
+ICON, ERA5, and MERRA-2 in subsets as in Fig. \ref{fig:cloud-occurrence}.
+The solid lines are the average calculated from the averages of every
+individual voyage and station. The bands span the
+16$^\mathrm{th}$--84$^\mathrm{th}$ percentiles calculated from the distribution
+of the voyage and station averages. Shown is also the relative frequency of
+occurrence and the number of profiles in each subset.
+}
+\label{fig:potential-temperature}
+\end{figure}
 
@@
 20\% at 5 km.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.72\textwidth]{img/theta_hur.pdf}
-\caption{
-Virtual potential temperature ($\theta_v$) and relative humidity (RH)
-determined from radiosonde launches and co-located profiles in
-ICON, ERA5, and MERRA-2 in subsets as in Fig. \ref{fig:cloud-occurrence}.
-The solid lines are the average calculated from the averages of every
-individual voyage and station. The bands span the
-16$^\mathrm{th}$--84$^\mathrm{th}$ percentiles calculated from the distribution
-of the voyage and station averages. Shown is also the relative frequency of
-occurrence and the number of profiles in each subset.
-}
-\label{fig:potential-temperature}
-\end{figure}
 

### 2024-09-25 manuscript.tex
Section on LTS results

@@
 
-Fig. \ref{fig:cyclone-stability}b shows a geographical distribution of the LTS.
+Fig. \ref{fig:cyclone-stability}b shows a geographical distribution of
+relatively stable and unstable conditions as determined by the LTS.  The
+relatively unstable conditions are prevalent in the mid SO (50--65°S), which
+might be explained by the relatively cold near-surface air overlying relatively
+warm sea surface. Relatively stable conditions are prevalent elsewhere over the
+SO. The distribution is also less zonally symmetric than the cyclonic activity.
+In the high-latitude SO, the presence of sea ice might have significant
+stabilising effect. The ERA5 renalysis is also substantially more stable than
+ICON across the whole region.
 

### 2024-09-25 manuscript.tex
Various improvements

@@
 and 2021. Fig. \ref{fig:map} shows a map of the voyages, Table
-\ref{tab:voyages} list the voyages and stations, and Table
+\ref{tab:voyages} list the voyages, campaigns and stations, and Table
 \ref{tab:voyage-references} lists references where available. Altogether, the
@@
 regular synoptic times on the RV \emph{Polarstern}, MARCUS, NBP17024, TAN1702,
-and TAN1802 voyages, measuring pressure, temperature, relative humidity, and
-global navigation satellite system coordinates. Derived thermodynamic (virtual
-potential temperature, lifting condensation level, etc.) and dynamic physical
-quantities (wind speed and direction) for the measured vertical profiles were
-calculated with rstool \citep{rstool}. Surface meteorological quantities were
-measured continuously by an onboard automatic weather station or individual
-instruments.
+and TAN1802 voyages and campaigns, measuring pressure, temperature, relative
+humidity, and global navigation satellite system coordinates. Derived
+thermodynamic (virtual potential temperature, lifting condensation level, etc.)
+and dynamic physical quantities (wind speed and direction) for the measured
+vertical profiles were calculated with rstool \citep{rstool}. Surface
+meteorological quantities were measured continuously by an onboard automatic
+weather station or individual instruments.
 
@@
 \caption{
-List of voyages and stations. Start, end, and days (UTC; inclusive)
-indicate the time period when the vessel was south of 40°S. Abbreviations:
-ceilometer (ceil.), Australia (AU), New Zealand (NZ), South America (SA),
-Atlantic Ocean (AO) and Africa (AF). The number of days is rounded to the
-nearest integer. CL51/31 indicates CL51 configured to emulate CL31.
+An overview of the analysed voyages, campaigns and stations. Start, end, and days
+(UTC; inclusive) indicate the time period when the vessel was south of 40°S.
+Abbreviations: ceilometer (ceil.), Australia (AU), New Zealand (NZ), South
+America (SA), Atlantic Ocean (AO) and Africa (AF). The number of days is
+rounded to the nearest integer. CL51/31 indicates CL51 configured to emulate
+CL31.
 }
@@
 \begin{table}[t!]
-\caption{List of voyage and station references.}
+\caption{Voyage, campaign and station publication references.}
 \label{tab:voyage-references}
@@
 the sampling (temporal) resolution is 6 s (AA15‐16, MARCUS, and MICRE), 36 s (RV
-\emph{Polarstern}), and about 2.37 s (TAN1502). From the MARCUS voyage, unlike raw
+\emph{Polarstern}), and about 2.37 s (TAN1502). From the MARCUS campaign, unlike raw
 instrument data available for the other voyages and stations, the Vaisala CL31

### 2024-09-25 manuscript.tex
Multiple additions

@@
 In the high-latitude SO, the presence of sea ice might have significant
-stabilising effect. The ERA5 renalysis is also substantially more stable than
-ICON across the whole region.
+stabilising effect \citep{knight2024}. The ERA5 renalysis is also substantially
+more stable than ICON across the whole region.
 
@@
 
+We analysed a total of about 2421 days of lidar and radiosonde data from 31
+voyages and campaigns and one subantarctic station data, covering the Atlantic,
+Australian and New Zealand sectors of the SO over the span of 10 years. This
+dataset, together with the use of the ALCF lidar simulator, provided a fairly
+comprehensive basis for evaluating SO cloud and thermodynamic profile biases in
+the GSRM ICON and the ERA5 and MERRA-2 reanalyses. This provides a unique
+evaluation perspective different from satellite observations, one which is
+more suitable for evaluating bounary layer clouds, which are predominant in
+this region. Furthermore, we subsetted our dataset by low and high latitude
+bands, cyclonic activity and stability, in order to identify how these
+conditions relate the the biases. Our main finding corroborates previous
+findings of large boundary layer cloud biases in models, and their subsequent
+effect on the radiative transfer. This also applies to the new ICON GSRM,
+but the biases are lower than in the reanalyses, despite the reanalyses having
+the advantage of assimilation of the observed meteorological conditions.
+
 We show that the model underestimates the total cloud fraction by about 10\%,

### 2024-09-25 manuscript.tex
Multiple additions

@@
 
+\section{Limitations}
+
+Limitations of our study are numerous. The spatial coverage of our dataset
+does not include most parts of the the Indian Ocean and Pacific Ocean sectors
+of the SO. Even though climatological features of the SO are typically
+relatively uniform zonally, variantions exist, such as those related to the
+Antarctic Peninsula and the southern of South America. The voyages were
+mostly undertaken in the Austral summer months, and only rarely in the winter
+months, due to the poor accesibility of this region during winter. Therefore,
+our results are mostly representative of summer, and to lesser extent spring
+and autumn conditions.
+
+The time period of ICON is relatively short with only four full years of
+simulation available. Moreover, the simulation was free running, which means
+that observations had to be temporally mapped to this time period (at the same
+time relative to the start of the year) for the comparison. For these reasons,
+one can expect the results to be slightly different due to reasons unrelated to
+model biases, such as different weather conditions and the phase of climatic
+oscillations such as the ENSO in the observations and the model.
+
+Ground-based lidar observations are affected by attenuation by thick cloud
+layers, and for this reason the results are mostly representative of BL clouds,
+while higher-level clouds are only occassionaly visible to the lidar when BL
+are not present. Ground-based lidar observations can be regarded as superior to
+satellite lidar observations for low-level clouds in this region, while mid-
+and high-level clouds are better represented in satellite observations
+\citep{mcerlich2021}.
+
+We attempted to remove lidar profiles with precipitation, which could not be
+properly simulated with the lidar simulator (Section \ref{sec:ann}). However,
+the approach was limited by relatively low sensitivity of the ANN (65\%), and
+the fact that we had to choose a fixed threshold for surface precipitation flux
+in the model and renalyses, which might not exactly correspond to detection by
+the ANN applied to obseravations. Also, we did not make an attempt to remove
+profiles with precipitation not reaching the surface. The above reasons can
+result in artificial bias in the comparison, even though we exect this to be
+much smaller than the identified model biases.
+
 \section{Discussion and conclusions}
@@
 the advantage of assimilation of the observed meteorological conditions.
+The GSRM has, on the other hand, the advange of a much higher spatial
+resolution and, to some extent, explicit calculation of traditionally
+subgrid-scale processes such as convection.
+
+The relationship between cloud biases and radiation has a number of notable
+features. Perhaps unsurprisingly, The reanalyses exhibit the too few,
+too bright type of bias previously identified in models. In our results,
+this is characterised by outgoing SW radiation similar to or higher
+than in satellite observations, while at the same time total cloud fraction
+is substantially underestimated relative to the ground-based lidar observation.
+This feature seems to be much more pronounced in ERA5 than in MERRA-2. On
+the other hand, this type of relationship is not present in ICON. This model
+mostly predicts smaller outgoing SW radiation and smaller total cloud fraction
+than observations, and the deficit of outgoing SW radiation is approximately
+proportial to the deficit of the total cloud fraction. While this might be a
+welcome feature and an improvement over previous models, it does mean that the
+outgoing SW radiation is overall underestimated, instead of being compensated
+by a higher cloud albedo. This can, of course, lead to undesirable secondary
+effects such as overestimated solar heating of the sea surface, but a
+combination of many factors have been found to be responsible for SO SST biases
+in climate models \citep{zhang2023,luo2023}.
 
@@
 (\url{https://www.arm.gov}). The MERRA-2 data are openly available from the
-NASA NASA Goddard Earth Sciences (GES) Data and Information Services Center
+NASA Goddard Earth Sciences (GES) Data and Information Services Center
 (DISC) (\url{https://disc.gsfc.nasa.gov/datasets?project=MERRA-2}).  The ERA5
 data are openly available from the Copernicus Climate Data Store (CDS)
-(\url{https://cds.climate.copernicus.eu}). The CERES products are available
-from the project website (\url{https://ceres.larc.nasa.gov}) and the NASA
-Atmospheric Science Data Centre
-(\url{https://asdc.larc.nasa.gov/project/CERES}).  The other voyage and station
-data are openly available on Zenodo (). Subsetted model and reanalysis data for
-the voyage tracks and the station and data processed with the ALCF are openly
-available on Zenodo ().
+(\url{https://cds.climate.copernicus.eu}). The ICON data are available on the
+Levante cluster of the Deutsches Klimarechenzentrum (DKRZ;
+\url{https://www.dkrz.de/en/systems/hpc/hlre-4-levante}) after registration at
+\url{https://luv.dkrz.de/register/}. The CERES products are available from the
+project website (\url{https://ceres.larc.nasa.gov}) and the NASA Atmospheric
+Science Data Centre (\url{https://asdc.larc.nasa.gov/project/CERES}). The other
+voyage and station data are openly available on Zenodo (). Subsetted model and
+reanalysis data for the voyage tracks and the station and data processed with
+the ALCF are openly available on Zenodo ().
 

### 2024-09-26 manuscript.tex
Improve style

@@
 % Schuddeboom and McDonald (2021), The Southern Ocean Radiative Bias, Cloud Compensating Errors, and Equilibrium Climate Sensitivity in CMIP6 Models
-% Ramadoss et al. (2020), Simulating mixed-phase cloud properties with ICON around the CAPRICORN ﬁeld campaign at the kilometre scale [poster]
+% Ramadoss et al. (2020), Simulating mixed-phase cloud properties with ICON around the CAPRICORN field campaign at the kilometre scale [poster]
 % Heim et al. (2021), Inter-model Variability in Convection-Resolving Simulations of Subtropical Marine Low Clouds
@@
 \usepackage{graphicx}
+\usepackage{lineno}
+\linenumbers
 \setsansfont{Source Sans Pro}
-\setmainfont{Source Serif Pro}
+\setmainfont{Crimson Text}
+\setmonofont[Scale=0.8]{Space Mono}
 \hypersetup{
@@
 	urlcolor=blue,
-	pdftitle={Ship and ground-based lidar and radiosonde evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON and the ERA5 and MERRA-2 reanalyses},
+	pdftitle={Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON, and the ERA5 and MERRA-2 reanalyses},
 	pdfauthor={Peter Kuma, Frida A.-M. Bender, Adrian J. McDonald and Thorsten Mauritsen}
@@
 \titlespacing*{\section}{0pt}{12pt}{6pt}
-\titlespacing*{\subsection}{0pt}{8pt}{4pt}
+\titlespacing*{\subsection}{0pt}{10pt}{4pt}
 %\renewcommand{\bibsection}{\section*{Publications}}
@@
 
-\begin{center} \Large \sffamily\textbf{Ship and ground-based lidar and radiosonde evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON and the ERA5 and MERRA-2 reanalyses}\\[0.4cm]
+\fontsize{13pt}{15pt}\selectfont
+
+\begin{center} \Large \sffamily\textbf{Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON and the ERA5 and MERRA-2 reanalyses}\\[0.4cm]
 \large Peter Kuma$^\mathsf{1,}$*, Frida A.-M. Bender$^\mathsf{1}$, Adrian J. McDonald$^\mathsf{2}$ and Thorsten Mauritsen$^\mathsf{1}$\\[0.4cm]
@@
 subgrid-scale clouds are not parametrised in this model. This region is mostly
-dominated by boundary layer clouds generated by shallow convection, and these
-are problematic to observe by spaceborne lidar and radars, which are affected
-by attenuation by overlapping and thick clouds and ground clutter,
+dominated by boundary layer (BL) clouds generated by shallow convection, and
+these are problematic to observe by spaceborne lidar and radars, which are
+affected by attenuation by overlapping and thick clouds and ground clutter,
 respectively. Therefore, we choose to use a large set of ship-based
@@
 region, particularly in light of the fact that subgrid-scale clouds are not
-parameterised in this model. This region is mostly dominated by boundary layer
-clouds generated by shallow convection, and these are problematic to observe by
+parameterised in this model. This region is mostly dominated by BL clouds
+generated by shallow convection, and these are problematic to observe by
 spaceborne lidar and radars, which are affected by attenuation by overlapping
@@
 \emph{Tangaroa} (© Peter Kuma, University of Canterbury), \textbf{(d)} Vaisala
-CL51 installation at the Macquarie Island station (© Jeﬀ Aquilina, Bureau of
+CL51 installation at the Macquarie Island station (© Jeff Aquilina, Bureau of
 Meteorology).
@@
 observations were available and included precipitation presence or absence and
-type. We used this dataset to train a convolutional artiﬁcial neural network
+type. We used this dataset to train a convolutional artificial neural network
 (ANN) of the U-Net type \citep{ronneberger2015} to recognise profiles with
@@
 
-The ANN achieved 65\% sensitivity and 87\% speciﬁcity when the true positive
+The ANN achieved 65\% sensitivity and 87\% specificity when the true positive
 rate (26\%) was made to match observations. The receiver operating
@@
 
-\begin{figure}[b!]
+\begin{figure}[p!]
 \centering
@@
 \ref{fig:cloud-occurrence}). The analysis shows that the total cloud fraction
-(determined as the fraction of proﬁles with clouds at any height in the lidar
+(determined as the fraction of profiles with clouds at any height in the lidar
 cloud mask) is underestimated in ICON and reanalyses by about 10\% and 20\%,
@@
 The ICON comparison is limited by the fact that the model is free-running.
-Thus, the vertical proﬁles are not expected to represent the same weather
+Thus, the vertical profiles are not expected to represent the same weather
 conditions as in observations, but long-term statistical comparison is still
-possible. Only proﬁles with the same sea ice conditions (present or not) were
+possible. Only profiles with the same sea ice conditions (present or not) were
 included to avoid comparing sea ice with open sea conditions.
@@
 the cloud cover for the day is defined as the fraction of cloudy profiles in
-the total number of profiles, expressed in octas.
+the total number of profiles, expressed in oktas.
 
@@
 analysed above. Observations show the greatest representation of high cloud
-cover (5--8 octas), peaking at 7 octas. This is not represented by ICON or the
-reanalyses.  While ICON is the closest, it tends to be 1 octa clearer the
-observations, peaking at 6 octas, and highly understimating days with 8 octas.
+cover (5--8 oktas), peaking at 7 oktas. This is not represented by ICON or the
+reanalyses.  While ICON is the closest, it tends to be 1 okta clearer the
+observations, peaking at 6 oktas, and highly understimating days with 8 oktas.
 Overall, the reanalyses show results similar to each other, underestimating
-cloud cover by about 2 octas, and strongly understimating days with 7 and 8
-octas. Of the two reanalyses, MERRA-2 shows slightly higher cloud cover and
+cloud cover by about 2 oktas, and strongly understimating days with 7 and 8
+oktas. Of the two reanalyses, MERRA-2 shows slightly higher cloud cover and
 thus more consistent with observations.
@@
 When analysed by subsets, the cyclonic subset shows the highest cloud cover,
-with 8 octas occurring on one half of such days (Fig. \ref{fig:cloud-cover}d).
+with 8 oktas occurring on one half of such days (Fig. \ref{fig:cloud-cover}d).
 This is not represented by ICON or the reanalyses at all. Interestingly, clear
-sky days (0 octas) also have a local maximum peaking at about 15\% in this
+sky days (0 oktas) also have a local maximum peaking at about 15\% in this
 subset.  When we contrast the low and high latitude zones, we see that the high
-latitude zone tends to have greater cloud cover, peaking at 8 octas (Fig.
-\ref{cloud-cover}c). The high latitude also has almost no clear sky or small
-cloud cover cases (0--4 octas). ICON and the reanalyses represent at least this
-characteristic of the distribution well for 0--3 octas, but otherwise show
-bises similar to the general case. One of the greatest biases is present in
-ERA5 in the unstable subset, where it peaks at 3 octas, whereas the
-observations peak at 7 octas and show negligible cloud cover below 5 octas.
+latitude zone tends to have greater cloud cover, peaking at 8 oktas (Fig.
+\ref{fig:cloud-cover}c). The high latitude also has almost no clear sky or
+small cloud cover cases (0--4 oktas). ICON and the reanalyses represent at
+least this characteristic of the distribution well for 0--3 oktas, but
+otherwise show bises similar to the general case. One of the greatest biases is
+present in ERA5 in the unstable subset, where it peaks at 3 oktas, whereas the
+observations peak at 7 oktas and show negligible cloud cover below 5 oktas.
 
@@
 
-\subsection{Thermodynamic proﬁles}
-
-We analysed about 2300 radiosonde proﬁles south of 40°S from the 24 RV
+\subsection{Thermodynamic profiles}
+
+We analysed about 2300 radiosonde profiles south of 40°S from the 24 RV
 \emph{Polarstern} voyages, MARCUS, NBP1704, TAN1702, and TAN1802. Spatially and
@@
 the GSRM ICON and the ERA5 and MERRA-2 reanalyses. This provides a unique
-evaluation perspective different from satellite observations, one which is
-more suitable for evaluating bounary layer clouds, which are predominant in
-this region. Furthermore, we subsetted our dataset by low and high latitude
-bands, cyclonic activity and stability, in order to identify how these
-conditions relate the the biases. Our main finding corroborates previous
-findings of large boundary layer cloud biases in models, and their subsequent
-effect on the radiative transfer. This also applies to the new ICON GSRM,
-but the biases are lower than in the reanalyses, despite the reanalyses having
-the advantage of assimilation of the observed meteorological conditions.
-The GSRM has, on the other hand, the advange of a much higher spatial
-resolution and, to some extent, explicit calculation of traditionally
-subgrid-scale processes such as convection.
+evaluation perspective different from satellite observations, one which is more
+suitable for evaluating bounary layer clouds, which are predominant in this
+region. Furthermore, we subsetted our dataset by low and high latitude bands,
+cyclonic activity and stability, in order to identify how these conditions
+relate the the biases. Our main finding corroborates previous findings of large
+BL cloud biases in models, and their subsequent effect on the radiative
+transfer. This also applies to the new ICON GSRM, but the biases are lower than
+in the reanalyses, despite the reanalyses having the advantage of assimilation
+of the observed meteorological conditions.  The GSRM has, on the other hand,
+the advange of a much higher spatial resolution and, to some extent, explicit
+calculation of traditionally subgrid-scale processes such as convection.
 
@@
 
-We compared radiosonde proﬁles acquired on the RV \emph{Polarstern} voyages
+We compared radiosonde profiles acquired on the RV \emph{Polarstern} voyages
 with ICON.  The ICON model exhibits smaller internal variability than
@@
 
+\fontsize{12pt}{14pt}\selectfont
 \section*{Acknowledgements}
@@
 Navy and the UC and a Macquarie Island dataset provided by the Atmospheric
-Radiation Measurement and the UC. We thank the scientiﬁc staff, the crew, and
+Radiation Measurement and the UC. We thank the scientific staff, the crew, and
 everyone involved in collecting data on the voyages and Macquarie Island,
@@
 provided by the Copernicus Climate Change Service and MERRA-2 provided by the
-Global Modeling and Assimilation Office. We also acknowledge the AMSR Uniﬁed
+Global Modeling and Assimilation Office. We also acknowledge the AMSR Unified
 and SMMR and SSM/I-SSMIS datasets provided by the National Snow and Ice Data
@@
 
-\footnotesize
+%\footnotesize
+\fontsize{11pt}{13pt}\selectfont
 \setlength{\bibsep}{0.0pt}

### 2024-09-26 manuscript.tex
Add font files
Add fonts

@@
 \setsansfont{Source Sans Pro}
-\setmainfont{Crimson Text}
-\setmonofont[Scale=0.8]{Space Mono}
+%\setmainfont{Crimson Text}
+\setmainfont{CrimsonText}[
+	Path=./fonts/,
+	Extension=.ttf,
+	UprightFont=*-Regular,
+	BoldFont=*-Bold,
+	ItalicFont=*-Italic,
+	BoldItalicFont=*-BoldItalic
+]
+%\setmonofont[Scale=0.8]{Space Mono}
+\setmonofont[Scale=0.8]{SpaceMono}[
+	Path=./fonts/,
+	Extension=.ttf,
+	UprightFont=*-Regular,
+	BoldFont=*-Bold,
+	ItalicFont=*-Italic,
+	BoldItalicFont=*-BoldItalic
+]
 \hypersetup{

### 2024-09-26 manuscript.tex
Multiple improvements

@@
 \titleformat*{\subsection}{\normalsize\bfseries\sffamily}
-\titlespacing*{\section}{0pt}{12pt}{6pt}
-\titlespacing*{\subsection}{0pt}{10pt}{4pt}
+\titlespacing*{\section}{0pt}{14pt}{6pt}
+\titlespacing*{\subsection}{0pt}{12pt}{4pt}
 %\renewcommand{\bibsection}{\section*{Publications}}
@@
 
-We show that the model underestimates the total cloud fraction by about 10\%,
+We show that the model underestimates the total cloud fraction (CF) by about 10\%,
 with overestimation of cloud below 2 km and underestimation of cloud above 2
-km. The reanalyses also underestimate the total cloud fraction by about 20\%.
+km. The reanalyses also underestimate the total CF by about 20\%.
 ERA5 overestimates cloud below 1 km but underestimates near-surface cloud or
@@
 \cite{zhao2022} reported a similar SW radiation bias in five analysed CMIP6
-models over high-latitude SO and total CF underestimation on the order of 10\%
-over the entire 40--60°S SO.
+models over high-latitude SO and the total cloud fraction underestimation on
+the order of 10\% over the entire 40--60°S SO.
 
@@
 and temperature; 1-hourly average 2D surface flux diagnostics (M2T1NXFLX) for
-precipitation and sea ice; and 1-hourly average 2D radiation diagnostics
+precipitation; and 1-hourly average 2D radiation diagnostics
 (M2T1NXRAD) for radiation quantities \citep{merra2}.
@@
 the highest instantaneous temporal resolution data available. Shown is also the
-chosen dividing threshold of 12 K for `stable' and `unstable' conditions.
+chosen dividing threshold of 12 K for the relatively stable and unstable
+conditions.
 }
@@
 \subsection{Partitioning by cyclonic activity and stability}
+\label{sec:cyclone-stability}
 
@@
 and stations (Fig.  \ref{fig:lts}), we determined a dividing threshold of 12 K
-for relatively unstable (< 12 K) and relatively stable (>= 12 K) conditions.
+for the relatively unstable (< 12 K) and the relatively stable (>= 12 K)
+conditions.
 
@@
 Geographical distribution of \textbf{(a, b)} cyclonic days and \textbf{(b, d)}
-relatively stable (LTS > 12 K) time steps in \textbf{(a, c)} ERA5 in years
+the relatively stable (LTS > 12 K) time steps in \textbf{(a, c)} ERA5 in years
 2010--2013 (inclusive) and \textbf{(b, d)} ICON in model years 2021--2023 (free
@@
 distribution, which is relavant for the subsequent analaysis, because these
-quantities are used for subsetting our dataset. Fig.
+conditions are used for subsetting our dataset. Fig.
 \ref{fig:cyclone-stability}a shows a geographical distribution of the fraction
 of cyclonic days as determined by the cyclone tracking algorithm applied on the
-ERA5 reanalysis and ICON data. As expected the strongest cyclonic activity is
-in the high-latitude SO zone, and it is relatively zonally symmetric at all
-latitudes.  While both reanalysis and the model agree relatively well,
-differences in the strength of the local extremes of occurrence are notable,
-especially over the Amundsen Sea, which is more cyclonic in the reanalysis, and
-around Cape Adere, which is more cyclonic in ICON. There differences might,
-however, stem from the relatively short time periods of comparison (4 year) and
-the fact that the model is free running.
-
-Fig. \ref{fig:cyclone-stability}b shows a geographical distribution of
-relatively stable and unstable conditions as determined by the LTS.  The
-relatively unstable conditions are prevalent in the mid SO (50--65°S), which
-might be explained by the relatively cold near-surface air overlying relatively
-warm sea surface. Relatively stable conditions are prevalent elsewhere over the
-SO. The distribution is also less zonally symmetric than the cyclonic activity.
-In the high-latitude SO, the presence of sea ice might have significant
-stabilising effect \citep{knight2024}. The ERA5 renalysis is also substantially
-more stable than ICON across the whole region.
+ERA5 reanalysis and ICON data (Section \ref{sec:cyclone-stability}). As
+expected, the strongest cyclonic activity is in the high-latitude SO zone, and
+it is relatively zonally symmetric at all latitudes.  While both reanalysis and
+the model agree relatively well, differences in the strength of the local
+extremes of occurrence are notable, especially over the Amundsen Sea, which is
+more cyclonic in the reanalysis, and around Cape Adere, which is more cyclonic
+in ICON. There differences might, however, stem from the relatively short time
+periods of comparison (4 year) and the fact that the model is free running.
+
+Fig. \ref{fig:cyclone-stability}b shows a geographical distribution of the
+relatively stable and unstable conditions as determined by the LTS (Section
+\ref{sec:cyclone-stability}).  The relatively unstable conditions are prevalent
+in the mid SO (50--65°S), which might be explained by the relatively cold
+near-surface air overlying relatively warm sea surface. The relatively stable
+conditions are prevalent elsewhere over the SO. The distribution is also less
+zonally symmetric than the cyclonic activity.  In the high-latitude SO, the
+presence of sea ice might have significant stabilising effect
+\citep{knight2024}. The ERA5 renalysis is also substantially more stable than
+ICON across the whole region.
 
@@
 We used the ALCF to derive cloud occurrence by height and the total cloud
-fraction from observations, ICON, and two reanalyses, MERRA-2 and ERA5 (Fig.
-\ref{fig:cloud-occurrence-panel}). We aggregated the sources by calculating the
-averages and percentiles of all individual profiles (Fig.
-\ref{fig:cloud-occurrence}). The analysis shows that the total cloud fraction
-(determined as the fraction of profiles with clouds at any height in the lidar
-cloud mask) is underestimated in ICON and reanalyses by about 10\% and 20\%,
-respectively.
-
-In particular, ICON overestimates cloud occurrence below 1 km and
-underestimates it above, MERRA-2 underestimates cloud occurrence at all
-heights, especially near the surface, and ERA5 simulates cloud occurrence
-relatively well above 1 km, but strongly underestimates it near the surface.
-We note that fog or near-surface clouds are strongly lacking in the reanalyses.
-As shown in Fig. \ref{fig:cloud-occurrence-panel}, the biases are relatively
-consistent across voyages and longitudes. The ICON results are overall better
-matching the observations than the reanalyses.
-
-The ICON comparison is limited by the fact that the model is free-running.
-Thus, the vertical profiles are not expected to represent the same weather
-conditions as in observations, but long-term statistical comparison is still
-possible. Only profiles with the same sea ice conditions (present or not) were
-included to avoid comparing sea ice with open sea conditions.
-
-The observations show cloud occurrence peaking at the surface, whereas models
-show a higher peak (at about 500 m). The models underestimate total cloud
-fraction by 10--20\% and show a strong decrease in cloud occurrence near the
-surface, but this is not happening in the observations. ICON and ERA5
-overestimate cloud occurrence at the peak (between 0--1 km). Above 1 km, ICON
-and MERRA-2 understimate cloud occurrence, but ERA5 is very accurate. The too
-high peak in models is partly supported by the LCL distribution, which peaks
-higher in the models than in the observations (at the surface), although this
-is not very pronounced. The northern zone shows a stronger peak of cloud
-occurrence near the surface than the southern zone, and this could be because
-higher latitudes have more unstable atmospheric profiles. The northern and
-southern zones show similar biases in models as in the general case, but ERA5
-does not overestimate the peak in the northern zone (near-surface cloud
-occurrence is still strongly understimated). Cyclonic situations have a larger
-amount of observed cloudiness, including the peak and total cloud fraction. In
-these situations, the models are doing a relatively good job of getting the
-vertical profile of cloud occurrence right, but still tend to underestimate
-cloud occurrence above 1 km and near the surface. Non-cyclonic situations are
-similar to the general case. In stable situations cloud occurrence peaks
-strongly at the surface in observations, compared to unstable situations, where
-the peak is more obtuse and spread across 0--1 km. In stable situations, the
-models are doing a fairly good job, but overestimate cloud occurrence at the
-peak below 1 km; above 1 km, they show similar biases as in the general case.
-In unstable situations the bias in ICON is very pronounced, with a much
+fraction from observations, ICON, and the two reanalyses, ERA5 and MERRA-2
+(Fig.  \ref{fig:cloud-occurrence-panel}). We aggregated the data sources
+(voyages, campaigns and stations) by calculating the averages and percentiles
+of all individual profiles (Fig.  \ref{fig:cloud-occurrence}). The analysis
+shows that the total cloud fraction (determined as the fraction of profiles
+with clouds at any height in the lidar cloud mask) is underestimated in ICON
+and reanalyses by about 10\% and 20\%, respectively. In particular, ICON
+overestimates cloud occurrence below 1 km and underestimates it above, MERRA-2
+underestimates cloud occurrence at all heights, especially near the surface,
+and ERA5 simulates cloud occurrence relatively well above 1 km, but strongly
+underestimates it near the surface.  We note that fog or near-surface clouds
+are strongly lacking in the reanalyses.  As shown in Fig.
+\ref{fig:cloud-occurrence-panel}, the biases are relatively consistent across
+the data sources and longitudes. The ICON results are overall better matching
+the observations than the reanalyses.
+
+In the general case (Fig. \ref{fig:cloud-occurrence}a), the observations show
+cloud occurrence peaking at the surface, whereas models show a higher peak (at
+about 500 m). The models underestimate the total cloud fraction by 10--20\% and
+show a strong drop in cloud occurrence near the surface, but this is not
+supported by the observations. ICON and ERA5 overestimate cloud occurrence at
+the peak (between 0--1 km). Above 1 km, ICON and MERRA-2 understimate cloud
+occurrence, but ERA5 is very accurate. The too high peak in models is partly
+supported by the LCL distribution, which peaks higher in the models than in the
+observations (at the surface), although this is not very pronounced.
+
+When subsetted by low- and high-latitude zones (Fig.
+\ref{fig:cloud-occurrence}b, c), we can see that the low-latitude SO zone shows
+a stronger peak of cloud occurrence near the surface than the high-latitude SO
+zone, and this could be because higher latitudes have more unstable atmospheric
+profiles. The low- and high-latitude SO zones show similar biases in models as
+in the general case, but ERA5 does not overestimate the peak in the
+low-latitude SO zone (near-surface cloud occurrence is still strongly
+understimated).
+
+When subsetted by cyclonic and non-cyclonic situations (Fig.
+\ref{fig:cloud-occurrence}d, e), we can see that the cyclonic situations have a
+larger amount of observed cloudiness, including the peak and total cloud
+fraction. In these situations, the models are doing a relatively good job of
+getting the vertical profile of cloud occurrence right, but still tend to
+underestimate cloud occurrence above 1 km and near the surface. Non-cyclonic
+situations are similar to the general case.
+
+When subsetted by the relatively stable and unstable conditions (Fig.
+\ref{fig:cloud-occurrence}f, g), as defined in Section
+\ref{sec:cyclone-stability}, we can see that in the relatively stable
+situations cloud occurrence peaks strongly at the surface in observations,
+compared to the relatively unstable situations, where the peak is more obtuse
+and spread across 0--1 km.  In the relatively stable situations, the models are
+doing a fairly good job, but overestimate cloud occurrence at the peak below 1
+km; above 1 km, they show similar biases as in the general case.  In the
+relatively unstable situations the bias in ICON is very pronounced, with a much
 stronger peak at about 500 m, ERA5 is underestimating cloud occurrence below 1
-km (especially near the surface), and MERRA-2 even more strongly. In all
-situations, even when the models overestimate cloud occurrence at some
+km (especially near the surface), and MERRA-2 even more strongly.
+
+In all situations, even when the models overestimate cloud occurrence at some
 altitudes, they always substantially underestimate the total cloud fraction.
@@
 occurrence below 1 km and underestimating above, underestimating the total
-cloud fraction, and showing greatest biases in unstable and non-cyclonic
-condititions. It also shows a peak of cloud occurrence at higher altitude than
-obs (500 m vs. near the surface), and correspondingly, its LCL tends to be also
-higher. MERRA-2 can be generally characterised as underestimating cloud
-occurrence at nearly all altitudes as well as the total cloud fraction, but
-mostly above and below 500 m (the peak at 500 m is well-represented). It
-struggles the most in the northern zone and in unstable situations. ERA5 can be
-generally characterised as representing cloud occurrence correctly above about
-1--1.5 km, overestimating below, but underestimating near-surface cloud
-occurrence (0--500 m). The total cloud fraction is strongly understimated in
-all situations. It has a tendency towards understimation in the northern zone
-and unstable situations, conversely, overestimating in the southern zone and
-stable conditions.
+cloud fraction, and showing greatest biases in the relatively unstable and
+non-cyclonic condititions. It also shows a peak of cloud occurrence at higher
+altitude than obs (500 m vs. near the surface), and correspondingly, its LCL
+tends to be also higher. MERRA-2 can be generally characterised as
+underestimating cloud occurrence at nearly all altitudes as well as the total
+cloud fraction, but mostly above and below 500 m (the peak at 500 m is
+well-represented). It struggles the most in the low-latitude SO zone and in the
+relatively unstable situations. ERA5 can be generally characterised as
+representing cloud occurrence correctly above about 1--1.5 km, overestimating
+below, but underestimating near-surface cloud occurrence (0--500 m). The total
+cloud fraction is strongly understimated in all situations. It has a tendency
+towards understimation in the low-latitude SO zone and the relatively unstable
+situations, conversely, overestimating in the high-latitude SO zone and the
+relatively stable conditions.
 
@@
 otherwise show bises similar to the general case. One of the greatest biases is
-present in ERA5 in the unstable subset, where it peaks at 3 oktas, whereas the
+present in ERA5 in the relatively unstable subset, where it peaks at 3 oktas, whereas the
 observations peak at 7 oktas and show negligible cloud cover below 5 oktas.

### 2024-09-26 manuscript.tex
Various improvements

@@
 subgrid-scale clouds are not parametrised in this model. This region is mostly
-dominated by boundary layer (BL) clouds generated by shallow convection, and
+dominated by boundary layer clouds generated by shallow convection, and
 these are problematic to observe by spaceborne lidar and radars, which are
@@
 region, particularly in light of the fact that subgrid-scale clouds are not
-parameterised in this model. This region is mostly dominated by BL clouds
-generated by shallow convection, and these are problematic to observe by
+parameterised in this model. This region is mostly dominated by boundary layer
+clouds generated by shallow convection, and these are problematic to observe by
 spaceborne lidar and radars, which are affected by attenuation by overlapping
@@
 \subsection{Cloud occurrence by height}
+\label{sec:cloud-occurrence}
 
@@
 When subsetted by low- and high-latitude zones (Fig.
-\ref{fig:cloud-occurrence}b, c), we can see that the low-latitude SO zone shows
+\ref{fig:cloud-occurrence}b, c), we see that the low-latitude SO zone shows
 a stronger peak of cloud occurrence near the surface than the high-latitude SO
@@
 When subsetted by cyclonic and non-cyclonic situations (Fig.
-\ref{fig:cloud-occurrence}d, e), we can see that the cyclonic situations have a
+\ref{fig:cloud-occurrence}d, e), we see that the cyclonic situations have a
 larger amount of observed cloudiness, including the peak and total cloud
@@
 \ref{fig:cloud-occurrence}f, g), as defined in Section
-\ref{sec:cyclone-stability}, we can see that in the relatively stable
+\ref{sec:cyclone-stability}, we see that in the relatively stable
 situations cloud occurrence peaks strongly at the surface in observations,
 compared to the relatively unstable situations, where the peak is more obtuse
-and spread across 0--1 km.  In the relatively stable situations, the models are
-doing a fairly good job, but overestimate cloud occurrence at the peak below 1
-km; above 1 km, they show similar biases as in the general case.  In the
-relatively unstable situations the bias in ICON is very pronounced, with a much
-stronger peak at about 500 m, ERA5 is underestimating cloud occurrence below 1
-km (especially near the surface), and MERRA-2 even more strongly.
+and spread across the altitudes of 0--1 km.  In the relatively stable
+situations, the models are doing a fairly good job, but overestimate cloud
+occurrence at the peak below 1 km; above 1 km, they show similar biases as in
+the general case.  In the relatively unstable situations, the bias in ICON is
+very pronounced, with a much stronger peak at about 500 m, ERA5 is
+underestimating cloud occurrence below 1 km (especially near the surface), and
+MERRA-2 is underestimating it even more strongly.
 
@@
 calculated from the set of all voyages and stations. The subsets
-\textbf{(a--g)} are described in the text (Section \ref{sec:results}).
+\textbf{(d--g)} are defined in Section \ref{sec:cyclone-stability}.
 }
@@
 We analysed the daily cloud cover (total cloud fraction) distribution. This is
-a measure of cloudiness, irrespective of height. A cloud detected at any height
-means that the lidar profile was classified as cloudy; otherwise, it was
-classified as a clear sky. When all profiles in a day are aggregated together,
-the cloud cover for the day is defined as the fraction of cloudy profiles in
-the total number of profiles, expressed in oktas.
-
-In Fig.  \ref{fig:cloud-cover} we show the results for the same subsets as
-analysed above. Observations show the greatest representation of high cloud
-cover (5--8 oktas), peaking at 7 oktas. This is not represented by ICON or the
-reanalyses.  While ICON is the closest, it tends to be 1 okta clearer the
-observations, peaking at 6 oktas, and highly understimating days with 8 oktas.
-Overall, the reanalyses show results similar to each other, underestimating
-cloud cover by about 2 oktas, and strongly understimating days with 7 and 8
-oktas. Of the two reanalyses, MERRA-2 shows slightly higher cloud cover and
-thus more consistent with observations.
+a measure of cloudiness, irrespective of height, calculated over the course of
+a day (UTC). A cloud detected at any height means that the lidar profile was
+classified as cloudy; otherwise, it was classified as a clear sky. When all
+profiles in a day are taken together, the cloud cover for the day is defined as
+the fraction of cloudy profiles in the total number of profiles, expressed in
+oktas (multiples of 1/8).
+
+In Fig.  \ref{fig:cloud-cover} we show the results for the same subsets of data
+as in the previous section. Observations show the greatest representation of
+high cloud cover (5--8 oktas), peaking at 7 oktas. This is not represented by
+ICON or the reanalyses.  While ICON is the closest, it tends to be 1 okta
+clearer the observations, peaking at 6 oktas, and highly understimating days
+with 8 oktas.  Overall, the reanalyses show results similar to each other,
+underestimating cloud cover by about 2 oktas, and strongly understimating days
+with 7 and 8 oktas. Of the two reanalyses, MERRA-2 shows slightly higher cloud
+cover and thus is more consistent with observations.
 
@@
 sky days (0 oktas) also have a local maximum peaking at about 15\% in this
-subset.  When we contrast the low and high latitude zones, we see that the high
-latitude zone tends to have greater cloud cover, peaking at 8 oktas (Fig.
-\ref{fig:cloud-cover}c). The high latitude also has almost no clear sky or
+subset.  When we contrast the low- and high-latitude zones, we see that the
+high-latitude zone tends to have greater cloud cover, peaking at 8 oktas (Fig.
+\ref{fig:cloud-cover}c). The high-latitude zone also has almost no clear sky or
 small cloud cover cases (0--4 oktas). ICON and the reanalyses represent at
@@
 otherwise show bises similar to the general case. One of the greatest biases is
-present in ERA5 in the relatively unstable subset, where it peaks at 3 oktas, whereas the
-observations peak at 7 oktas and show negligible cloud cover below 5 oktas.
+present in ERA5 in the relatively unstable subset, in which ERA5 peaks at 3
+oktas, whereas the observations peak at 7 oktas and show negligible cloud cover
+below 5 oktas.
 
@@
 
-Limitations of our study are numerous. The spatial coverage of our dataset
-does not include most parts of the the Indian Ocean and Pacific Ocean sectors
-of the SO. Even though climatological features of the SO are typically
-relatively uniform zonally, variantions exist, such as those related to the
-Antarctic Peninsula and the southern of South America. The voyages were
-mostly undertaken in the Austral summer months, and only rarely in the winter
-months, due to the poor accesibility of this region during winter. Therefore,
-our results are mostly representative of summer, and to lesser extent spring
-and autumn conditions.
+Let us consider the main limitations of the presented results. The spatial
+coverage of our dataset does not include most parts of the the Indian Ocean and
+Pacific Ocean sectors of the SO. Even though climatological features of the SO
+are typically relatively uniform zonally, variantions exist, such as those
+related to the Antarctic Peninsula and the southern of South America. The
+voyages were mostly undertaken in the Austral summer months, and only rarely in
+the winter months, due to the poor accesibility of this region during winter.
+Therefore, our results are mostly representative of summer, and to lesser
+extent spring and autumn conditions.
 
 The time period of ICON is relatively short with only four full years of
-simulation available. Moreover, the simulation was free running, which means
+simulation available. Moreover, the simulation is free-running, which means
 that observations had to be temporally mapped to this time period (at the same
@@
 one can expect the results to be slightly different due to reasons unrelated to
-model biases, such as different weather conditions and the phase of climatic
+model biases, such as different weather conditions and the phase of climate
 oscillations such as the ENSO in the observations and the model.
@@
 Ground-based lidar observations are affected by attenuation by thick cloud
-layers, and for this reason the results are mostly representative of BL clouds,
-while higher-level clouds are only occassionaly visible to the lidar when BL
-are not present. Ground-based lidar observations can be regarded as superior to
-satellite lidar observations for low-level clouds in this region, while mid-
-and high-level clouds are better represented in satellite observations
-\citep{mcerlich2021}.
+layers, and for this reason the results are mostly representative of boundary
+layer clouds, while higher-level clouds are only occassionaly visible to the
+lidar when boundary layer clouds are not present. Ground-based lidar
+observations can be regarded as superior to satellite lidar observations for
+low-level clouds in this region, while mid- and high-level clouds are better
+represented in satellite observations \citep{mcerlich2021}.
 
@@
 profiles with precipitation not reaching the surface. The above reasons can
-result in artificial bias in the comparison, even though we exect this to be
-much smaller than the identified model biases.
+result in an artificial bias in the comparison, even though we expect this to
+be much smaller than the identified model biases.
 
@@
 relate the the biases. Our main finding corroborates previous findings of large
-BL cloud biases in models, and their subsequent effect on the radiative
-transfer. This also applies to the new ICON GSRM, but the biases are lower than
-in the reanalyses, despite the reanalyses having the advantage of assimilation
-of the observed meteorological conditions.  The GSRM has, on the other hand,
-the advange of a much higher spatial resolution and, to some extent, explicit
-calculation of traditionally subgrid-scale processes such as convection.
+boundary layer cloud biases in models, and their subsequent effect on the
+radiative transfer. This also applies to the new ICON GSRM, but the biases are
+lower than in the reanalyses, despite the reanalyses having the advantage of
+assimilation of the observed meteorological conditions.  The GSRM has, on the
+other hand, the advange of a much higher spatial resolution and, to some
+extent, explicit calculation of traditionally subgrid-scale processes such as
+convection.
 
@@
 
-We acknowledge the RV Polarstern datasets provided by the Alfred Wegener
-Institute, RSV Aurora Australis datasets provided by the Australian Antarctic
-Program and the University of Canterbury (UC), RV Tangaroa datasets provided by
-the National Institute of Water and Atmospheric Research and the UC, RV
-Nathaniel B. Palmer dataset provided by the National Science Foundation,
-Cooperative Institute for Research in Environmental Sciences, University of
-Colorado and the UC, HMNZS Wellington dataset provided by the Royal New Zealand
-Navy and the UC and a Macquarie Island dataset provided by the Atmospheric
-Radiation Measurement and the UC. We thank the scientific staff, the crew, and
-everyone involved in collecting data on the voyages and Macquarie Island,
-especially Kelly Schick, Peter Guest, John J. Cassano, Simon Parsons, Graeme
-Plank, Sally Garrett, Jamie Halla, Sean Hartery, Mike J.  Harvey, Simon P.
-Alexander and Alex Schuddeboom. We acknowledge the reanalysis dataset ERA5
-provided by the Copernicus Climate Change Service and MERRA-2 provided by the
-Global Modeling and Assimilation Office. We also acknowledge the AMSR Unified
-and SMMR and SSM/I-SSMIS datasets provided by the National Snow and Ice Data
-Center.
+We acknowledge the RV \emph{Polarstern} datasets provided by the Alfred Wegener
+Institute and Pangaea, RSV \emph{Aurora Australis} datasets provided by the
+Australian Antarctic Program and the University of Canterbury (UC), RV
+\emph{Tangaroa} datasets provided by the National Institute of Water and
+Atmospheric Research and the UC, RV \emph{Nathaniel B. Palmer} dataset provided
+by the National Science Foundation, Cooperative Institute for Research in
+Environmental Sciences, University of Colorado and the UC, HMNZS
+\emph{Wellington} dataset provided by the Royal New Zealand Navy and the UC and
+the Macquarie Island station dataset provided by the Atmospheric Radiation
+Measurement and the UC.  We thank the scientific staff, the crew, and everyone
+involved in collecting data on the voyages and stations, especially Kelly
+Schick, Peter Guest, John J.  Cassano, Simon Parsons, Graeme Plank, Sally
+Garrett, Jamie Halla, Sean Hartery, Mike J.  Harvey, Simon P.  Alexander and
+Alex Schuddeboom. We acknowledge the ICON model output provided by the
+Deutsches Klimarechenzentrum (DKRZ), reanalysis dataset ERA5 provided by the
+Copernicus Climate Change Service and MERRA-2 provided by the Global Modeling
+and Assimilation Office.
 
@@
 (\url{https://www.arm.gov}). The MERRA-2 data are openly available from the
-NASA Goddard Earth Sciences (GES) Data and Information Services Center
-(DISC) (\url{https://disc.gsfc.nasa.gov/datasets?project=MERRA-2}).  The ERA5
-data are openly available from the Copernicus Climate Data Store (CDS)
+NASA Goddard Earth Sciences (GES) Data and Information Services Center (DISC)
+(\url{https://disc.gsfc.nasa.gov/datasets?project=MERRA-2}).  The ERA5 data are
+openly available from the Copernicus Climate Data Store (CDS)
 (\url{https://cds.climate.copernicus.eu}). The ICON data are available on the
-Levante cluster of the Deutsches Klimarechenzentrum (DKRZ;
-\url{https://www.dkrz.de/en/systems/hpc/hlre-4-levante}) after registration at
+Levante cluster of the DKRZ
+(\url{https://www.dkrz.de/en/systems/hpc/hlre-4-levante}) after registration at
 \url{https://luv.dkrz.de/register/}. The CERES products are available from the

### 2024-09-26 manuscript.tex
Various improvements

@@
 The relationship between cloud biases and radiation has a number of notable
-features. Perhaps unsurprisingly, The reanalyses exhibit the too few,
-too bright type of bias previously identified in models. In our results,
-this is characterised by outgoing SW radiation similar to or higher
-than in satellite observations, while at the same time total cloud fraction
-is substantially underestimated relative to the ground-based lidar observation.
-This feature seems to be much more pronounced in ERA5 than in MERRA-2. On
-the other hand, this type of relationship is not present in ICON. This model
-mostly predicts smaller outgoing SW radiation and smaller total cloud fraction
-than observations, and the deficit of outgoing SW radiation is approximately
-proportial to the deficit of the total cloud fraction. While this might be a
-welcome feature and an improvement over previous models, it does mean that the
-outgoing SW radiation is overall underestimated, instead of being compensated
-by a higher cloud albedo. This can, of course, lead to undesirable secondary
-effects such as overestimated solar heating of the sea surface, but a
-combination of many factors have been found to be responsible for SO SST biases
-in climate models \citep{zhang2023,luo2023}.
+features. Perhaps unsurprisingly, the reanalyses exhibit the too few, too
+bright bias previously identified in models. In our results, this is
+characterised by outgoing TOA SW radiation similar to or higher than in
+satellite observations, while at the same time total cloud fraction is
+substantially underestimated relative to the ground-based lidar observation.
+This feature seems to be much more pronounced in ERA5 than in MERRA-2. On the
+other hand, this type of relationship is not present in ICON. This model mostly
+predicts smaller outgoing TOA SW radiation and smaller total cloud fraction
+than observations, and the deficit of outgoing TOA SW radiation is
+approximately proportial to the deficit of the total cloud fraction. While this
+might be a welcome feature and an improvement over previous models, it does
+mean that the outgoing TOA SW radiation is overall underestimated, instead of
+being compensated by a higher cloud albedo. This can, of course, lead to
+undesirable secondary effects such as overestimated solar heating of the sea
+surface. Previously, a combination of many factors have been found to be
+responsible for SO SST biases in climate models \citep{zhang2023,luo2023}.
 
@@
 Schick, Peter Guest, John J.  Cassano, Simon Parsons, Graeme Plank, Sally
-Garrett, Jamie Halla, Sean Hartery, Mike J.  Harvey, Simon P.  Alexander and
-Alex Schuddeboom. We acknowledge the ICON model output provided by the
-Deutsches Klimarechenzentrum (DKRZ), reanalysis dataset ERA5 provided by the
-Copernicus Climate Change Service and MERRA-2 provided by the Global Modeling
-and Assimilation Office.
+Garrett, Jamie Halla, Sean Hartery, Mike J.  Harvey (†), Simon P.  Alexander and
+Alex Schuddeboom. We acknowledge the ICON model output provided by the nextGEMS
+project and the Deutsches Klimarechenzentrum (DKRZ), reanalysis dataset ERA5
+provided by the Copernicus Climate Change Service and MERRA-2 provided by the
+Global Modeling and Assimilation Office. We would like to dedicate this study
+to the memory of Mike J. Harvey, who very substantially contributed to
+obtaining atmospheric measurments on the RV \emph{Tangaroa} voyages used in
+this study.
 

### 2024-09-26 manuscript.tex
Various improvements

@@
 
+Cloud in some of the voyage and station data were previsouly analysed by other
+authors. \cite{pei2023} compared the Macquarie Ib
+
 Similar to our results, \cite{cesana2022} showed that CMIP6 also tends to
@@
 We acknowledge the RV \emph{Polarstern} datasets provided by the Alfred Wegener
-Institute and Pangaea, RSV \emph{Aurora Australis} datasets provided by the
-Australian Antarctic Program and the University of Canterbury (UC), RV
+Institute and Pangaea, AA15-16 dataset provided by the
+Australian Antarctic Division (AAD) and University of Canterbury (UC), RV
 \emph{Tangaroa} datasets provided by the National Institute of Water and
-Atmospheric Research and the UC, RV \emph{Nathaniel B. Palmer} dataset provided
+Atmospheric Research and UC, RV \emph{Nathaniel B. Palmer} dataset provided
 by the National Science Foundation, Cooperative Institute for Research in
-Environmental Sciences, University of Colorado and the UC, HMNZS
-\emph{Wellington} dataset provided by the Royal New Zealand Navy and the UC and
-the Macquarie Island station dataset provided by the Atmospheric Radiation
-Measurement and the UC.  We thank the scientific staff, the crew, and everyone
-involved in collecting data on the voyages and stations, especially Kelly
-Schick, Peter Guest, John J.  Cassano, Simon Parsons, Graeme Plank, Sally
-Garrett, Jamie Halla, Sean Hartery, Mike J.  Harvey (†), Simon P.  Alexander and
-Alex Schuddeboom. We acknowledge the ICON model output provided by the nextGEMS
-project and the Deutsches Klimarechenzentrum (DKRZ), reanalysis dataset ERA5
-provided by the Copernicus Climate Change Service and MERRA-2 provided by the
-Global Modeling and Assimilation Office. We would like to dedicate this study
-to the memory of Mike J. Harvey, who very substantially contributed to
-obtaining atmospheric measurments on the RV \emph{Tangaroa} voyages used in
-this study.
+Environmental Sciences, University of Colorado and UC, HMNZS \emph{Wellington}
+dataset provided by the Royal New Zealand Navy and UC, the MARCUS dataset was
+provided by the Atmospheric Radiation Measurement (ARM). The MICRE dataset was
+provided by ARM, the Australian Bureau of Meteorology, AAD and UC.  We thank
+the scientific staff, the crew, and everyone involved in collecting data on the
+voyages and stations, especially Kelly Schick, Peter Guest, John J.  Cassano,
+Simon Parsons, Graeme Plank, Sally Garrett, Jamie Halla, Sean Hartery, Mike J.
+Harvey (†), Simon P.  Alexander and Alex Schuddeboom. We acknowledge the ICON
+model output provided by the nextGEMS project and the Deutsches
+Klimarechenzentrum (DKRZ), reanalysis dataset ERA5 provided by the Copernicus
+Climate Change Service and MERRA-2 provided by the Global Modeling and
+Assimilation Office. We dedicate this study to the memory of Mike J. Harvey,
+who very substantially contributed to obtaining atmospheric measurments on the
+RV \emph{Tangaroa} voyages used in this study.
 
@@
 
-The RV \emph{Polarstern} data are openly available from Pangaea
-(\url{https://pangaea.de}). The MARCUS and Macquarie Island (MICRE) data are
-openly available from the Atmospheric Radiation Measurement (ARM)
-(\url{https://www.arm.gov}). The MERRA-2 data are openly available from the
-NASA Goddard Earth Sciences (GES) Data and Information Services Center (DISC)
-(\url{https://disc.gsfc.nasa.gov/datasets?project=MERRA-2}).  The ERA5 data are
-openly available from the Copernicus Climate Data Store (CDS)
+The RV \emph{Polarstern} datasets are openly available from Pangaea
+(\url{https://pangaea.de}). The MARCUS and MICRE datasets are openly available
+from ARM (\url{https://www.arm.gov}). The MERRA-2 data are openly available
+from the NASA Goddard Earth Sciences (GES) Data and Information Services Center
+(DISC) (\url{https://disc.gsfc.nasa.gov/datasets?project=MERRA-2}).  The ERA5
+data are openly available from the Copernicus Climate Data Store (CDS)
 (\url{https://cds.climate.copernicus.eu}). The ICON data are available on the
@@
 project website (\url{https://ceres.larc.nasa.gov}) and the NASA Atmospheric
-Science Data Centre (\url{https://asdc.larc.nasa.gov/project/CERES}). The other
-voyage and station data are openly available on Zenodo (). Subsetted model and
-reanalysis data for the voyage tracks and the station and data processed with
-the ALCF are openly available on Zenodo ().
+Science Data Centre (\url{https://asdc.larc.nasa.gov/project/CERES}).
+The TAN1802 data ara available on Zenodo
+(\url{https://doi.org/10.5281/zenodo.4060237}).  The other voyage and station
+data are openly available on Zenodo (). Subsetted model and reanalysis data for
+the voyage tracks and the station and data processed with the ALCF are openly
+available on Zenodo ().
+
+\section*{Author contributions}
+
+TODO
 

### 2024-09-26 manuscript.tex
Various improvements

@@
 The data sources contained ceilometer observations captured by the Vaisala CL51
-and CL31 operating at a wavelenght of 910 nm and the Lufft CHM-15k operating at
+operating at a wavelenght of 910 nm and the Lufft CHM-15k operating at
 1064 nm, described in detail below (Sections \ref{sec:cl51} and
@@
 HMNZSW16 & HMNZS \emph{Wellington}       & CHM 15k & NZ       & 2016-11-23 & 2016-12-19 & 27 \\
-MARCUS   & RSV \emph{Aurora Australis}   & CL31    & AU       & 2017-10-29 & 2018-03-26 & 149 \\
+MARCUS   & RSV \emph{Aurora Australis}   & CL51    & AU       & 2017-10-29 & 2018-03-26 & 149 \\
 MICRE    & Macquarie Is. station         & CL51    & AU/NZ    & 2016-04-03 & 2018-03-14 & 710 \\
@@
 
-\subsection{Vaisala CL51 and CL31}
+\subsection{Vaisala CL51}
 \label{sec:cl51}
 
-The Vaisala CL51 (photo in Fig. \ref{fig:map}d) and CL31 are ceilometers
-operating at a near-infrared wavelength of 910 nm. The maximum range is 15.4 km
-(CL51), 7.7 km (CL31 with 5 m vertical resolution), and 7.550 km (CL31 with 10
-m vertical resolution). The vertical resolution is 10 m (5 m configurable), and
-the sampling (temporal) resolution is 6 s (AA15‐16, MARCUS, and MICRE), 36 s (RV
-\emph{Polarstern}), and about 2.37 s (TAN1502). From the MARCUS campaign, unlike raw
-instrument data available for the other voyages and stations, the Vaisala CL31
-data were made available by the Atmospheric Radiation Measurement (ARM)
-processed to a maximum range of 7.545 km, a vertical resolution of 30 m, and
-sampling resolution of 16 s. The wavelength of 910 nm is affected by water
-vapour absorption of about 20\% in the mid-latitudes
-\citep{wiegner2015,wiegner2019}.  The instrument data files containing raw
-uncalibrated backscatter were first converted to NetCDF with cl2nc
-(\url{https://github.com/peterkuma/cl2nc}) and then processed with the ALCF
-(Section \ref{sec:alcf}) to produce absolutely calibrated attenuated volume
-backscattering coefficinet (AVBC), cloud mask, cloud occurrence by height and
-the total cloud fraction. CL51 can also be configured to emulate CL31. The
-Vaisala CL51 and CL31 instruments were used on most of the voyages and stations
-analysed here. Fig. \ref{fig:example}a shows an example of derived from the
-CL51 instrument.
+The Vaisala CL51 (photo in Fig. \ref{fig:map}d) is a ceilometer operating at a
+near-infrared wavelength of 910 nm. CL51 can also be configured to emulate the
+Vaisala CL31. The maximum range is 15.4 km (CL51), 7.7 km (CL31 emulation mode
+with 5 m vertical resolution), and 7.550 km (CL31 emulation mode with 10 m
+vertical resolution). The vertical resolution is 10 m (5 m configurable), and
+the sampling (temporal) resolution is 6 s (AA15‐16, MARCUS, and MICRE), 36 s
+(RV \emph{Polarstern}), and about 2.37 s (TAN1502). From the MARCUS and MICRE
+campaigns, unlike raw instrument data available for the other voyages and
+stations, the Vaisala CL51 data were made available by the Atmospheric
+Radiation Measurement (ARM) processed to a maximum range of 7.545 km, a
+vertical resolution of 30 m, and sampling resolution of 16 s. The wavelength of
+910 nm is affected by water vapour absorption of about 20\% in the
+mid-latitudes \citep{wiegner2015,wiegner2019}.  The instrument data files
+containing raw uncalibrated backscatter were first converted to NetCDF with
+cl2nc (\url{https://github.com/peterkuma/cl2nc}) and then processed with the
+ALCF (Section \ref{sec:alcf}) to produce absolutely calibrated attenuated
+volume backscattering coefficinet (AVBC), cloud mask, cloud occurrence by
+height and the total cloud fraction.  The Vaisala CL51 instruments were used on
+most of the voyages and stations analysed here. Fig. \ref{fig:example}a shows
+an example of derived from the CL51 instrument.
 
@@
 We acknowledge the RV \emph{Polarstern} datasets provided by the Alfred Wegener
-Institute and Pangaea, AA15-16 dataset provided by the
-Australian Antarctic Division (AAD) and University of Canterbury (UC), RV
-\emph{Tangaroa} datasets provided by the National Institute of Water and
-Atmospheric Research and UC, RV \emph{Nathaniel B. Palmer} dataset provided
-by the National Science Foundation, Cooperative Institute for Research in
-Environmental Sciences, University of Colorado and UC, HMNZS \emph{Wellington}
-dataset provided by the Royal New Zealand Navy and UC, the MARCUS dataset was
-provided by the Atmospheric Radiation Measurement (ARM). The MICRE dataset was
-provided by ARM, the Australian Bureau of Meteorology, AAD and UC.  We thank
-the scientific staff, the crew, and everyone involved in collecting data on the
-voyages and stations, especially Kelly Schick, Peter Guest, John J.  Cassano,
-Simon Parsons, Graeme Plank, Sally Garrett, Jamie Halla, Sean Hartery, Mike J.
-Harvey (†), Simon P.  Alexander and Alex Schuddeboom. We acknowledge the ICON
-model output provided by the nextGEMS project and the Deutsches
-Klimarechenzentrum (DKRZ), reanalysis dataset ERA5 provided by the Copernicus
-Climate Change Service and MERRA-2 provided by the Global Modeling and
-Assimilation Office. We dedicate this study to the memory of Mike J. Harvey,
-who very substantially contributed to obtaining atmospheric measurments on the
-RV \emph{Tangaroa} voyages used in this study.
+Institute and Pangaea, the AA15-16 dataset provided by the Australian Antarctic
+Division (AAD) and University of Canterbury (UC), RV \emph{Tangaroa} datasets
+provided by the National Institute of Water and Atmospheric Research and UC,
+the NBP1704 dataset provided by the National Science Foundation, Cooperative
+Institute for Research in Environmental Sciences, University of Colorado and
+UC, the HMNZSW16 dataset provided by the Royal New Zealand Navy and UC, the
+MARCUS dataset provided by the Atmospheric Radiation Measurement (ARM), AAD and
+UC, and the MICRE dataset provided by ARM, the Australian Bureau of
+Meteorology, AAD and UC. We thank the scientific staff, the crew, and everyone
+involved in collecting data on the voyages and stations, especially Kelly
+Schick, Peter Guest, John J.  Cassano, Simon Parsons, Graeme Plank, Sally
+Garrett, Jamie Halla, Sean Hartery, Mike J.  Harvey (†), Simon P.  Alexander
+and Alex Schuddeboom. We acknowledge the ICON model output provided by the
+nextGEMS project and the Deutsches Klimarechenzentrum (DKRZ), reanalysis
+dataset ERA5 provided by the Copernicus Climate Change Service and MERRA-2
+provided by the Global Modeling and Assimilation Office. We dedicate this study
+to the memory of Mike J. Harvey, who very substantially contributed to
+obtaining atmospheric measurments on the RV \emph{Tangaroa} voyages used in
+this study.
 
@@
 
-The RV \emph{Polarstern} datasets are openly available from Pangaea
+The RV \emph{Polarstern} datasets are openly available on Pangaea
 (\url{https://pangaea.de}). The MARCUS and MICRE datasets are openly available
@@
 project website (\url{https://ceres.larc.nasa.gov}) and the NASA Atmospheric
-Science Data Centre (\url{https://asdc.larc.nasa.gov/project/CERES}).
-The TAN1802 data ara available on Zenodo
+Science Data Centre (\url{https://asdc.larc.nasa.gov/project/CERES}).  The
+TAN1802 data ara available on Zenodo
 (\url{https://doi.org/10.5281/zenodo.4060237}).  The other voyage and station
-data are openly available on Zenodo (). Subsetted model and reanalysis data for
-the voyage tracks and the station and data processed with the ALCF are openly
-available on Zenodo ().
+data are openly available on Zenodo ([TODO]). Subsetted model and reanalysis data
+for the voyage tracks and the station and data processed with the ALCF are
+openly available on Zenodo ([TODO]).
 
@@
 
-TODO
+[TODO]
 

### 2024-09-26 manuscript.tex
Various additions

@@
 HMNZSW16 & HMNZS \emph{Wellington}       & CHM 15k & NZ       & 2016-11-23 & 2016-12-19 & 27 \\
-MARCUS   & RSV \emph{Aurora Australis}   & CL51    & AU       & 2017-10-29 & 2018-03-26 & 149 \\
-MICRE    & Macquarie Is. station         & CL51    & AU/NZ    & 2016-04-03 & 2018-03-14 & 710 \\
+MARCUS   & RSV \emph{Aurora Australis}   & CT25K   & AU       & 2017-10-29 & 2018-03-26 & 149 \\
+MICRE    & Macquarie Is. station         & CT25K   & AU/NZ    & 2016-04-03 & 2018-03-14 & 710 \\
 NBP1704  & RV \emph{Nathaniel B. Palmer} & CHM 15k & NZ       & 2017-04-14 & 2017-06-08 & 55 \\
@@
 
-\subsection{Vaisala CL51}
+\subsection{Vaisala CL51 and CT25K}
 \label{sec:cl51}
@@
 campaigns, unlike raw instrument data available for the other voyages and
-stations, the Vaisala CL51 data were made available by the Atmospheric
+stations, the Vaisala CT25K data were made available by the Atmospheric
 Radiation Measurement (ARM) processed to a maximum range of 7.545 km, a
@@
 UC, the HMNZSW16 dataset provided by the Royal New Zealand Navy and UC, the
-MARCUS dataset provided by the Atmospheric Radiation Measurement (ARM), AAD and
-UC, and the MICRE dataset provided by ARM, the Australian Bureau of
-Meteorology, AAD and UC. We thank the scientific staff, the crew, and everyone
-involved in collecting data on the voyages and stations, especially Kelly
-Schick, Peter Guest, John J.  Cassano, Simon Parsons, Graeme Plank, Sally
-Garrett, Jamie Halla, Sean Hartery, Mike J.  Harvey (†), Simon P.  Alexander
-and Alex Schuddeboom. We acknowledge the ICON model output provided by the
-nextGEMS project and the Deutsches Klimarechenzentrum (DKRZ), reanalysis
-dataset ERA5 provided by the Copernicus Climate Change Service and MERRA-2
-provided by the Global Modeling and Assimilation Office. We dedicate this study
-to the memory of Mike J. Harvey, who very substantially contributed to
-obtaining atmospheric measurments on the RV \emph{Tangaroa} voyages used in
-this study.
+MARCUS dataset provided by the Atmospheric Radiation Measurement (ARM) and AAD,
+and the MICRE dataset provided by ARM, the Australian Bureau of Meteorology,
+and AAD. We thank the scientific staff, the crew, and everyone involved in
+collecting data on the voyages and stations, especially Kelly Schick, Peter
+Guest, John J.  Cassano, Simon Parsons, Graeme Plank, Sally Garrett, Jamie
+Halla, Sean Hartery, Mike J.  Harvey (†), Simon P.  Alexander and Alex
+Schuddeboom. We acknowledge the ICON model output provided by the nextGEMS
+project and the Deutsches Klimarechenzentrum (DKRZ), reanalysis dataset ERA5
+provided by the Copernicus Climate Change Service and MERRA-2 provided by the
+Global Modeling and Assimilation Office. We dedicate this study to the memory
+of Mike J. Harvey, who very substantially contributed to obtaining the
+atmospheric measurments on the RV \emph{Tangaroa} voyages used in this study.
 

### 2024-10-21 manuscript.tex
Various improvements

@@
 \usepackage{fontspec}
+\usepackage{microtype}
 \usepackage[margin=2cm]{geometry}
@@
 \setsansfont{Source Sans Pro}
+\setmainfont{EB Garamond}
 %\setmainfont{Crimson Text}
-\setmainfont{CrimsonText}[
-	Path=./fonts/,
-	Extension=.ttf,
-	UprightFont=*-Regular,
-	BoldFont=*-Bold,
-	ItalicFont=*-Italic,
-	BoldItalicFont=*-BoldItalic
-]
+%\setmainfont{CrimsonText}[
+%	Path=./fonts/,
+%	Extension=.ttf,
+%	UprightFont=*-Regular,
+%	BoldFont=*-Bold,
+%	ItalicFont=*-Italic,
+%	BoldItalicFont=*-BoldItalic
+%]
 %\setmonofont[Scale=0.8]{Space Mono}
@@
 	pdftitle={Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON, and the ERA5 and MERRA-2 reanalyses},
-	pdfauthor={Peter Kuma, Frida A.-M. Bender, Adrian J. McDonald and Thorsten Mauritsen}
+	pdfauthor={Peter Kuma, Frida A.-M. Bender, …}
 }
@@
 \titlespacing*{\section}{0pt}{14pt}{6pt}
-\titlespacing*{\subsection}{0pt}{12pt}{4pt}
+\titlespacing*{\subsection}{0pt}{13pt}{4pt}
 %\renewcommand{\bibsection}{\section*{Publications}}
@@
 \begin{center} \Large \sffamily\textbf{Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON and the ERA5 and MERRA-2 reanalyses}\\[0.4cm]
-\large Peter Kuma$^\mathsf{1,}$*, Frida A.-M. Bender$^\mathsf{1}$, Adrian J. McDonald$^\mathsf{2}$ and Thorsten Mauritsen$^\mathsf{1}$\\[0.4cm]
+\large Peter Kuma$^\mathsf{1,}$*, Frida A.-M. Bender$^\mathsf{1}$, \ldots\\[0.4cm]
 \small
 $^\mathsf{1}$Department of Meteorology (MISU) and Bolin Centre for Climate Research, Stockholm University, Stockholm SE-106 91, Sweden\\[0.2cm]
-$^\mathsf{2}$School of Physical and Chemical Sciences, University of Canterbury, Christchurch, New Zealand\\[0.2cm]
 *Corresponding author: Peter Kuma (\href{mailto:peter.kuma@misu.su.se}{peter.kuma@misu.su.se})\\[0.4cm]
@@
 
-Currently, a new generation of km-scale (also called `k-scale') resolution
-global climate models is in development as the forthcoming phase of climate
-modelling. One such model is a 5-km version of the Icosahedral Nonhydrostatic
-Weather and Climate Model (ICON), developed jointly by the Deutscher
-Wetterdienst (DWD) and Max-Planck-Institute for Meteorology (MPI-M). Because of
-the high resolution, most parametrisations, such as those of convection and
-clouds, can be avoided.
-
-Previous studies have identified substantial large-scale biases in model clouds
-over the Southern Ocean (SO), affecting sea surface temperature and the Earth's
-albedo overall. Our aim is to quantify how well the high-resolution ICON model
-is simulating clouds in this region, particularly in light of the fact that
-subgrid-scale clouds are not parametrised in this model. This region is mostly
-dominated by boundary layer clouds generated by shallow convection, and
-these are problematic to observe by spaceborne lidar and radars, which are
-affected by attenuation by overlapping and thick clouds and ground clutter,
-respectively. Therefore, we choose to use a large set of ship-based
-observations conducted with ceilometers and lidars on board of the Research
-Vessel (RV) \textit{Polarstern} and other voyages. Altogether, we analyse over
-2000 days (about 6 years) of data from 31 voyages and 1 sub-antarctic station
-covering diverse longitudes of the SO. To achieve a like-for-like comparison
-with the model, we use a ground-based lidar simulator called the Automatic
-Lidar and Ceilometer Framework (ALCF). We contrast the results with the ECMWF
-Reanalysis 5 (ERA5) and the Modern-Era Retrospective analysis for Research and
-Applications, Version 2 (MERRA-2).
-
-We show that the model underestimates the total cloud fraction (CF) by about 10\%,
-with overestimation of cloud below 2 km and underestimation of cloud above 2
-km. The reanalyses also underestimate the total CF by about 20\%.
-ERA5 overestimates cloud below 1 km but underestimates near-surface cloud or
-fog. In addition to lidar data, we compare radiosonde profiles acquired on the
-RV \textit{Polarstern} voyages with ICON. Notably, the model exhibits smaller
-natural variability than observations, and its lifting condensation level tends
-to be higher. This might explain why cloud occurrence is peaking higher in the
-model (at 500 m) than in observations (at the surface).
-
-The results imply that the SO cloud biases are still a significant issue in a
-km-scale resolution model, even though an improvement over the lower-resolution
-reanalyses is notable. More effort is needed to improve model cloud simulations
-in this fast-changing and understudied region. The advancement from convection
-and cloud parametrisation to cloud-resolving models might not solve this bias
-without an additional effort.
+Global storm-resolving models (GSRMs) are developed as the forthcoming phase of
+climate modelling. Among them is a 5-km Icosahedral Nonhydrostatic Weather and
+Climate Model (ICON). Due to the resolution, parametrisations of convection and
+clouds are avoided. Standard-resolution models have substantial cloud biases
+over the Southern Ocean (SO), affecting radiation and sea surface temperature.
+We quantify how the GSRM ICON simulates clouds over the SO and contrast it with
+the ECMWF Reanalysis 5 (ERA5) and Modern-Era Retrospective analysis for
+Research and Applications, Version 2 (MERRA-2). The SO is dominated by boundary
+layer clouds, which often cannot be observed properly by speceborne instruments
+due to overlapping clouds, attenuation, and ground clutter. Instead, we use
+about 2400 days of ship-based lidar observations from 31 voyages and one
+subantarctic station. We use a ground-based lidar simulator for a like-for-like
+comparison. ICON underestimates the total cloud fraction (TCF) by about 10\%,
+with overestimation of clouds below 2 km and underestimation of clouds above 2
+km. The reanalyses underestimate TCF by about 20\%. ERA5 overestimates clouds
+below 1 km but underestimates near-surface clouds or fog. Compared to
+radiosonde observations, ICON exhibits smaller natural variability, and its
+lifting condensation level is higher, which might explain why cloud occurrence
+peaks higher in the model than in observations. SO cloud biases are still a
+substantial issue in a GSRM, even though an improvement over the
+lower-resolution reanalyses is notable. The transition from parametrisation to
+explicitly resolved convection and cloud processes might not be enough to
+address the model cloud biases.
 
 \section{Introduction}
+\label{sec:introduction}
 
@@
 computational availability and acceleration from general-purpose computing on
-graphics processing units (GPGPUs) is progressing to enable km-scale Earth
-system models (ESMs) and coupled atmosphsere--ocean general circulation models
-(AOGCMs) in research conditions today and operationally in the forthcoming
-years. Therefore, it represents a natural advancement in climate modeling.
-Global strom-resolving models (GSRMs) are emerging as a new front in the
-development of high-resolution global climate models, with horizontal grid
-resolutions of about 2--8 km \citep{satoh2019,stevens2019}. This is enough to
-resolve mesoscale convective storms, but smaller-scale convective plumes and
-smaller-scale cloud structure remain unresolved. At a 5-km scale,
-non-hydrostatic processes also become important, and for this reason such
-models are generally non-hydrostatic. The terms global cloud-resolving models
-(GCRMs), or global convection-permitting/-resolving models (GCPMs) are also
-sometimes used interchangeably with GSRMs but imply that clouds or convection
-are resolved explicitly, which is not entirely true for GSRMs, as this would
-require an even higher horizontal resolution \citep{satoh2019}.  Representative
-of these efforts is the DYnamics of the Atmospheric general circulation Modeled
-On Non-hydrostatic Domains (DYAMOND) project \citep{stevens2019,dyamond}, which
-is an intercomparison of nine global storm-resolving models (GSRMs) on two
-40-day time periods in summer (1 August -- 10 September 2016) and winter (20
-January - 1 March 2020). A new one-year GSRM intercomparison is currently
-proposed by \cite{takasuka2024}, with the hope of also evaluating the seasonal
-cycle and large-scale circulation.  An alternative to using a computantionally
-costly GSRM is to train an artificial neural network on GSRM output and use it
-for subgrid-scale clouds, as done with the GSRM ICON by \cite{grundner2022};
+graphics processing units (GPGPUs) is progressing to enable km-scale (also
+called k-scale) Earth system models (ESMs) and coupled atmosphsere--ocean
+general circulation models (AOGCMs) in research conditions today and
+operationally in the forthcoming years. Therefore, it represents a natural
+advancement in climate modeling.  Global strom-resolving models (GSRMs) are
+emerging as a new front in the development of high-resolution global climate
+models, with horizontal grid resolutions of about 2--8 km
+\citep{satoh2019,stevens2019}. This is enough to resolve mesoscale convective
+storms, but smaller-scale convective plumes and smaller-scale cloud structure
+remain unresolved. At a 5-km scale, non-hydrostatic processes also become
+important, and for this reason such models are generally non-hydrostatic. The
+terms global cloud-resolving models (GCRMs), or global
+convection-permitting/-resolving models (GCPMs) are also sometimes used
+interchangeably with GSRMs but imply that clouds or convection are resolved
+explicitly, which is not entirely true for GSRMs, as this would require an even
+higher horizontal resolution \citep{satoh2019}.  Representative of these
+efforts is the DYnamics of the Atmospheric general circulation Modeled On
+Non-hydrostatic Domains (DYAMOND) project \citep{stevens2019,dyamond}, which is
+an intercomparison of nine global storm-resolving models (GSRMs) on two 40-day
+time periods in summer (1 August -- 10 September 2016) and winter (20 January -
+1 March 2020). A new one-year GSRM intercomparison is currently proposed by
+\cite{takasuka2024}, with the hope of also evaluating the seasonal cycle and
+large-scale circulation.  An alternative to using a computantionally costly
+GSRM is to train an artificial neural network on GSRM output and use it for
+subgrid-scale clouds, as done with the GSRM ICON by \cite{grundner2022};
 \cite{grundner2023}.
 
-nextGEMS is an EU-funded project \citep{nextgems} focused on the research and
+nextGEMS is a European Union--funded project \citep{nextgems} focused on the research and
 development of GSRMs at multiple modelling centres and universities in Europe.
@@
 \cite{bubnova1995,voldoire2017}], Finite-Volume Dynamical Core on the Cubed
-Sphere [FV3, \cite{lin2004}], NASA Goddard Earth Observing System global
-atmospheric model version 5 [GEOS5; \cite{putman2011}], Model for Prediction
-Across Scales [MPAS; \cite{skamarock2012}], and System for Atmospheric Modeling
-[SAM; \cite{khairoutdinov2003}].
+Sphere [FV3, \cite{lin2004}], the National Aeronautics and Space Administration
+(NASA) Goddard Earth Observing System global atmospheric model version 5
+[GEOS5; \cite{putman2011}], Model for Prediction Across Scales [MPAS;
+\cite{skamarock2012}], and System for Atmospheric Modeling [SAM;
+\cite{khairoutdinov2003}].
 
@@
 distribution, ice crystal habit, cloud lifetime, and direct radiative
-interaction with aerosols.  In the 6th phase of the Coupled Model
+interaction with aerosols.  In the 6$^\mathrm{th}$ phase of the Coupled Model
 Intercomparison Project [CMIP6; \citep{eyring2016}], the cloud feedback has
@@
 interest.  Nevertheless, radiation biases and changes over an area of its size
-have a very significant influence on the global climate, and the SO is an
+have a very substantial influence on the global climate, and the SO is an
 important part of the global ocean conveyor belt.  Marine clouds have
 disproportionate effect on top of atmosphere (TOA) SW radiation due to the
-relatively low albedo of the sea surface.  The longitudinal symmetry of the SO
-means that model cloud biases tend to be similar across longitudes.  Here, we
-will conventionally refer to the SO as ocean regions south of 40°S,
+relatively low albedo of the sea surface.  The relative longitudinal symmetry
+of the SO means that model cloud biases tend to be similar across longitudes.
+Here, we conventionally refer to the SO as ocean regions south of 40°S,
 low-latitude SO as 40--55°S and high-latitude SO as south of 55°S.
@@
 models over high-latitude SO and the total cloud fraction underestimation on
-the order of 10\% over the entire 40--60°S SO.
+the order of 10\% over the entire 40--60°S SO. Recently, \cite{ramadoss2024}
+analysed 48 hours of km-scale ICON limited area model NWP simulation over a
+SO region adjacent to Tasmania agaist the Clouds, Aerosols, Precipitation,
+Radiation, and atmospherIc Composition Over the southeRn oceaN (CAPRICORN)
+voyage cloud and precipitation observations. They found the ICON cloud optical
+thickness underestimated relative to Himawari‐8 satellite observations, but also
+large differences in cloud top phase.
 
@@
 
-The main aim of our research is to evaluate the GSRM version of ICON, developed
-jointly by nextGEMS, Deutscher Wetterdienst (DWD) and the Max-Planck-Institute
-for Meteorology (MPI-M). Previous studies have identified substantial
-large-scale biases in climate model clouds over the Southern Ocean (SO),
-affecting sea surface temperature and the Earth’s albedo overall. Our aim is to
-quantify how well the high-resolution ICON model is simulating clouds in this
-region, particularly in light of the fact that subgrid-scale clouds are not
-parameterised in this model. This region is mostly dominated by boundary layer
-clouds generated by shallow convection, and these are problematic to observe by
-spaceborne lidar and radars, which are affected by attenuation by overlapping
-and thick clouds and ground clutter, respectively.  Specifically, the radar on
-CloudSat and lidar on CALIPSO are affected by the abovementioned issues,
-resulting in a strong underestimation of cloud occurrence below 2 km relative
-to ground-based lidar observations \citep{mcerlich2021}.  This, in turn, can
-lead to systematic biases in low clouds in climate models, which are frequently
-evaluated against CloudSat--CALIPSO products. Reanalyses can also suffer from
-cloud biases, as these are usually parametrised in their atmospheric component,
-and also in regions where input observations are sparse.  This makes them a
-problematic reference for clouds over the SO, and any biases relative to a
-reanalysis should be interpreted with caution. Instead, we chose to use a large
-set of ship-based observations conducted with ceilometers and lidars on board
-of the RV \emph{Polarstern} and other voyages and stations as a reference for
-the model evaluation.
-
-Altogether, we analysed over 1500 days of data from 31 voyages and one
-sub-Antarctic station covering diverse longitudes of the SO. To achieve a
-like-for-like comparison with the model, we used a ground-based lidar simulator
-called the Automatic Lidar and Ceilometer Framework (ALCF) \citep{kuma2021}. We
-contrasted the results with the European Centre for Medium-Range Weather
-Forecasts (ECMWF) Reanalysis 5 (ERA5) \citep{era5} and the Modern-Era
-Retrospective analysis for Research and Applications, Version 2 (MERRA-2)
-\citep{gelaro2017}.
+The main aim of this study is to evaluate the GSRM version of ICON, developed
+jointly by nextGEMS, Deutscher Wetterdienst (DWD), Max-Planck-Institute for
+Meteorology (MPI-M), Deutsches Klimarechenzentrum (DKRZ), Karlsruhe Institute
+of Technology (KIT), and the Center for Climate Systems Modeling (C2SM).
+Previous studies have identified substantial large-scale biases in climate
+model clouds over the SO, affecting sea surface temperature and the Earth’s
+albedo. Our aim is to quantify how well the GSRM ICON is simulating clouds in
+this region, particularly in light of the fact that subgrid-scale clouds and
+convection are not parameterised in this model. This region is mostly dominated
+by boundary layer clouds generated by shallow convection, and these are
+problematic to observe by spaceborne lidars and radars, which are affected by
+attenuation by overlapping and thick clouds and ground clutter, respectively.
+Specifically, the radar on CloudSat and lidar on CALIPSO (neither of them
+operational any more) are affected by the abovementioned issues, resulting in a
+strong underestimation of cloud occurrence below 2 km relative to ground-based
+lidar observations \citep{mcerlich2021}.  This, in turn, can lead to systematic
+biases in low clouds in climate models, which are frequently evaluated against
+CloudSat--CALIPSO products. Reanalyses can also suffer from cloud biases, as
+these are usually parametrised in their atmospheric component, and also in
+regions where input observations are sparse.  This makes them a problematic
+reference for clouds over the SO, and any biases relative to a reanalysis
+should be interpreted with caution. Instead, we chose to use a large set of
+ship-based observations conducted with ceilometers and lidars on board of the
+RV \emph{Polarstern} and other voyages and stations as a reference for the
+model evaluation.
+
+Altogether, we analysed about 2400 days of data from 31 voyages and one
+sub-Antarctic station covering diverse longitudes and latitudes of the SO. To
+achieve a like-for-like comparison with the model, we used a ground-based lidar
+simulator called the Automatic Lidar and Ceilometer Framework (ALCF)
+\citep{kuma2021}. We contrasted the results with the European Centre for
+Medium-Range Weather Forecasts (ECMWF) Reanalysis 5 (ERA5) \citep{era5} and the
+Modern-Era Retrospective analysis for Research and Applications, Version 2
+(MERRA-2) \citep{gelaro2017}.
 
@@
 The data sources contained ceilometer observations captured by the Vaisala CL51
-operating at a wavelenght of 910 nm and the Lufft CHM-15k operating at
-1064 nm, described in detail below (Sections \ref{sec:cl51} and
-\ref{sec:chm15k}). A ceilometer is a low-power near-infrared vertically
-pointing lidar with the purpose of measuring the cloud base, but it also
-measures the full vertical structure of clouds as long as the laser signal is
-not attenuated by thick clouds, which can be used to infer additional
+ perating at a wavelenght of 910 nm, Vaisala CT25K operating at 905 nm, and
+Lufft CHM 15k operating at 1064 nm, described in detail below (Sections
+\ref{sec:cl51} and \ref{sec:chm15k}). A ceilometer is a low-power near-infrared
+vertically pointing lidar with the purpose of measuring the cloud base, but it
+also measures the full vertical structure of clouds as long as the laser signal
+is not attenuated by thick clouds, which can be used to infer additional
 information such as a cloud mask and cloud occurrence by height.
@@
 and TAN1802 voyages and campaigns, measuring pressure, temperature, relative
-humidity, and global navigation satellite system coordinates. Derived
+humidity, and the global navigation satellite system coordinates. Derived
 thermodynamic (virtual potential temperature, lifting condensation level, etc.)
@@
 \caption{
-An overview of the analysed voyages, campaigns and stations. Start, end, and days
-(UTC; inclusive) indicate the time period when the vessel was south of 40°S.
-Abbreviations: ceilometer (ceil.), Australia (AU), New Zealand (NZ), South
-America (SA), Atlantic Ocean (AO) and Africa (AF). The number of days is
-rounded to the nearest integer. CL51/31 indicates CL51 configured to emulate
-CL31.
+An overview of the analysed voyages, campaigns and stations. Start, end, and
+the number of days (UTC; inclusive) refer to the time period when the vessel
+was south of 40°S.  Abbreviations: ceilometer (ceil.), Australia (AU), New
+Zealand (NZ), South America (SA), Atlantic Ocean (AO), and Africa (AF). The
+number of days is rounded to the nearest integer. CL51/31 indicates CL51
+configured to emulate CL31.
 }
@@
 
-The Vaisala CL51 (photo in Fig. \ref{fig:map}d) is a ceilometer operating at a
-near-infrared wavelength of 910 nm. CL51 can also be configured to emulate the
-Vaisala CL31. The maximum range is 15.4 km (CL51), 7.7 km (CL31 emulation mode
-with 5 m vertical resolution), and 7.550 km (CL31 emulation mode with 10 m
-vertical resolution). The vertical resolution is 10 m (5 m configurable), and
-the sampling (temporal) resolution is 6 s (AA15‐16, MARCUS, and MICRE), 36 s
-(RV \emph{Polarstern}), and about 2.37 s (TAN1502). From the MARCUS and MICRE
-campaigns, unlike raw instrument data available for the other voyages and
-stations, the Vaisala CT25K data were made available by the Atmospheric
-Radiation Measurement (ARM) processed to a maximum range of 7.545 km, a
-vertical resolution of 30 m, and sampling resolution of 16 s. The wavelength of
-910 nm is affected by water vapour absorption of about 20\% in the
-mid-latitudes \citep{wiegner2015,wiegner2019}.  The instrument data files
-containing raw uncalibrated backscatter were first converted to NetCDF with
-cl2nc (\url{https://github.com/peterkuma/cl2nc}) and then processed with the
-ALCF (Section \ref{sec:alcf}) to produce absolutely calibrated attenuated
-volume backscattering coefficinet (AVBC), cloud mask, cloud occurrence by
-height and the total cloud fraction.  The Vaisala CL51 instruments were used on
-most of the voyages and stations analysed here. Fig. \ref{fig:example}a shows
-an example of derived from the CL51 instrument.
+The Vaisala CL51 (photo in Fig. \ref{fig:map}d) and CT25K are ceilometers
+operating at a near-infrared wavelength of 910 nm and 905 nm, respectively.
+CL51 can also be configured to emulate the Vaisala CL31. The maximum range is
+15.4 km (CL51), 7.7 km (CL31 emulation mode with 5 m vertical resolution), and
+7.5 km (CT25K). The vertical resolution is 10 m (5 m configurable) in CL51 and
+30 m in CT25K. The sampling (temporal) resolution is configurable and in our
+datasets it is about 6 s for CL51 on AA15‐16, 16 s for CT25K on MARCUS and
+MICRE, 36 s for CL51 on RV \emph{Polarstern}, and about 2.37 s for CL51 with
+CL31 emulation on TAN1502. The wavelength of 910 nm is affected by water vapour
+absorption of about 20\% in the mid-latitudes \citep{wiegner2015,wiegner2019},
+but we do not expect this to be a significant issue as explained in
+\cite{kuma2021}.  The instrument data files containing raw uncalibrated
+backscatter were first converted to NetCDF with cl2nc
+(\url{https://github.com/peterkuma/cl2nc}) and then processed with the ALCF
+(Section \ref{sec:alcf}) to produce absolutely calibrated attenuated volume
+backscattering coefficinet (AVBC), cloud mask, cloud occurrence by height and
+the total cloud fraction. Because the CT25K uses a very similar wavelength to
+CL51, equivalent calculations as for CL51 were done assuming a wavelength of
+910 nm. The Vaisala CL51 and CT25K instruments were used on most of the voyages
+and stations analysed here. Fig.  \ref{fig:example}a shows an example of AVBC
+derived from the CL51 instrument data.
 
@@
 mask, cloud occurrence by height and the total cloud fraction. The CHM 15k was
-used on a minority of voyages (HMNZSW16, TAN1702, TAN1802, and NBP1704).
+used on four voyages (HMNZSW16, TAN1702, TAN1802, and NBP1704).
 
@@
 simulator and a tool for processing observed lidar data, supporting various
-instruments and models. It performs radiative transfer calculations to derive
-equivalent lidar AVBC in an atmospheric model, which can then be compared with
-observed AVBC \citep{kuma2021}. For this purpose, it takes atmospheric fields
-of cloud fraction, liquid and ice mass mixing ratio, temperature, and pressure
-fields as an input and can be run offline (on the model output rather than
+instruments and models \citep{kuma2021}. It performs radiative transfer
+calculations to derive equivalent lidar AVBC in an atmospheric model, which can
+then be compared with observed AVBC. For this purpose, it takes atmospheric
+fields of cloud fraction, liquid and ice mass mixing ratio, temperature, and
+pressure fields as an input and is run offline (on the model output rather than
 inside the model code). The lidar simulator in the ALCF is based on the
@@
 calculated, a cloud mask, cloud occurrence by height, and the total cloud
-fraction are determined. The ALCF has already been used by several research
-teams for model and reanalysis evaluation
+fraction are determined. The ALCF has been used by several research teams for
+model and reanalysis evaluation
 \citep{kuma2020,kremser2021,guyot2022,pei2023,whitehead2023,mcdonald2024}.
@@
 measured clear-sky molecular backscatter statistically with simulated clear-sky
-molecular backscatter. AVBC is resampled to 5 min temporal resolution and 50 m
+molecular backscatter. AVBC was resampled to 5 min temporal resolution and 50 m
 vertical resolution to increase signal-to-noise ratio, while having enough
-resolution to detect small-scale cloud variability. Noise standard deviation is
-calculated from AVBC at the highest range, where no clouds are expected.  A
-cloud mask is calculated from AVBC using a fixed threshold of $\mathrm{2\times
+resolution to detect small-scale cloud variability. Noise standard deviation
+was calculated from AVBC at the highest range, where no clouds are expected.  A
+cloud mask was calculated from AVBC using a fixed threshold of $\mathrm{2\times
 10^{-6} m^{-1}sr^{-1}}$ after subtracting 5 standard deviations of range-scale
@@
 A coupled (atmosphere--ocean) GSRM version of the ICON model is in development
-by the nextGEMS project \citep{hohenegger2023}. ICON is a very versatile model,
+at the nextGEMS project \citep{hohenegger2023}. ICON is a very versatile model,
 allowing for simulations ranging from coarse-resolution ESM simulations, GSRM
-simulations, limited area model (LAM) simulations, to large eddy simulations
-(LES), for both weather prediction and climate projections. ICON uses the
-atmospheric component ICON-A \citep{giorgetta2018}, whose physics is derived
-from ECHAM6 \citep{stevens2013}, and the ocean component ICON-O
-\citep{korn2022}. Earlier runs of the GSRM ICON from DYAMOND were evaluated by
-\cite{mauritsen2022}.
-
-Here, we use a free running (i.e. \emph{not} nudged or using prescribed SST)
+simulations, limited area model simulations, to large eddy simulations (LES),
+for both weather prediction and climate projections. ICON uses the atmospheric
+component ICON-A \citep{giorgetta2018}, whose physics is derived from ECHAM6
+\citep{stevens2013}, and the ocean component ICON-O \citep{korn2022}. Earlier
+runs of the GSRM ICON from DYAMOND were evaluated by \cite{mauritsen2022}.
+
+Here, we use a free-running (i.e. \emph{not} nudged or using prescribed SST)
 coupled GSRM simulation made for the purpse of climate projection.  nextGEMS
@@
 years 2021--2024 (inclusive). While a Cycle 4 run was available, we could not
-use due it to the unavailability of the necessary variables. The horizontal
+use it due it to the unavailability of the necessary variables. The horizontal
 resolution of ngc3028 is about 5 km.  The model output is available on 90
@@
 
-We partitioned our data into two subsets by cyclonic activity. For this
-purpose, we used a cyclone tracking algorithm to identify extratropical and
-polar cyclones (ECs and PCs) over the SO in the reanalysis and ICON data. We
-used the open source cyclone tracking package CyTRACK
+We partitioned our data into two mutually-exclusive subsets by cyclonic
+activity. For this purpose, we used a cyclone tracking algorithm to identify
+extratropical and polar cyclones (ECs and PCs) over the SO in the reanalysis
+and ICON data. We used the open source cyclone tracking package CyTRACK
 \citep{perez-alarcon2024}.  Generally, what constitutes an EC is considered
@@
 thresholds as well as tracking across time steps to identify cyclone centres
-and radii. From this information, we could classify geographical areas as
+and radii. With this information, we could classify geographical areas as
 either cyclonic or non-cyclonic. Due to a relatively small total area covered,
@@
 
-In addition to the above, we partitioned our data into two subsets by
-stability. We determined this by calculating lower tropospheric stability (LTS)
-as the difference between the potential temperature at 700 hPa and the surface.
-Based on a histogram of LTS in ERA5 and MERRA-2 calculated at all voyage tracks
-and stations (Fig.  \ref{fig:lts}), we determined a dividing threshold of 12 K
-for the relatively unstable (< 12 K) and the relatively stable (>= 12 K)
-conditions.
+In addition to the above, we partitioned our data into two mutually-exclusive
+subsets by stability. We determined this by calculating lower tropospheric
+stability (LTS) as the difference between the potential temperature at 700 hPa
+and the surface.  Based on a histogram of LTS in ERA5 and MERRA-2 calculated at
+all voyage tracks and stations (Fig.  \ref{fig:lts}), we determined a dividing
+threshold of 12 K for the relatively unstable (< 12 K) and the relatively
+stable (>= 12 K) conditions.
 
@@
 zonally symmetric than the cyclonic activity.  In the high-latitude SO, the
-presence of sea ice might have significant stabilising effect
+presence of sea ice might have substantial stabilising effect
 \citep{knight2024}. The ERA5 renalysis is also substantially more stable than
@@
 are typically relatively uniform zonally, variantions exist, such as those
-related to the Antarctic Peninsula and the southern of South America. The
+related to the Antarctic Peninsula and the southern tip of South America. The
 voyages were mostly undertaken in the Austral summer months, and only rarely in
@@
 the fact that we had to choose a fixed threshold for surface precipitation flux
-in the model and renalyses, which might not exactly correspond to detection by
+in the model and reanalyses, which might not exactly correspond to detection by
 the ANN applied to obseravations. Also, we did not make an attempt to remove
@@
 
-We analysed a total of about 2421 days of lidar and radiosonde data from 31
+We analysed a total of about 2400 days of lidar and radiosonde data from 31
 voyages and campaigns and one subantarctic station data, covering the Atlantic,
@@
 assimilation of the observed meteorological conditions.  The GSRM has, on the
-other hand, the advange of a much higher spatial resolution and, to some
+other hand, the advange of a much higher spatial resolution and, to a limited
 extent, explicit calculation of traditionally subgrid-scale processes such as
@@
 satellite observations, while at the same time total cloud fraction is
-substantially underestimated relative to the ground-based lidar observation.
+substantially underestimated relative to the ground-based lidar observations.
 This feature seems to be much more pronounced in ERA5 than in MERRA-2. On the
@@
 undesirable secondary effects such as overestimated solar heating of the sea
-surface. Previously, a combination of many factors have been found to be
-responsible for SO SST biases in climate models \citep{zhang2023,luo2023}.
-
-We show that the model underestimates the total cloud fraction by about 10\%,
-with an overestimation of clouds below 2 km, and an underestimation of clouds
-above 2 km. The reanalyses also underestimate the total cloud fraction by about
-20\%.  ERA5 overestimates cloud below 1 km but underestimates near-surface
-cloud or fog. In addition to lidar data, we compare radiosonde profiles
-acquired on the RV \textit{Polarstern} voyages with ICON. Notably, the model
-exhibits smaller natural variability than observations, and its lifting
-condensation level tends to be higher. This might explain why cloud occurrence
-is peaking higher in the model (at 500 m) than in observations (at the
-surface).
-
-Cloud in some of the voyage and station data were previsouly analysed by other
-authors. \cite{pei2023} compared the Macquarie Ib
-
-Similar to our results, \cite{cesana2022} showed that CMIP6 also tends to
-underestimate cloud occurrence above 2 km over the SO, although their analysis
-in this case was limited to liquid clouds.
-
-We compared radiosonde profiles acquired on the RV \emph{Polarstern} voyages
-with ICON.  The ICON model exhibits smaller internal variability than
-observations, and its LCL level tends to be higher, which might explain why a
-peak of cloud occurrence in observations is located at the surface, while in
-ICON it is located higher, corresponding to the LCL.
-
-The results imply that SO cloud biases are still a significant issue in a
-km-scale resolution model, even though an improvement over the lower-resolution
-reanalyses is notable. More effort is needed to improve model cloud simulations
-in this fast-changing and understudied region. The advancement from convection
-and cloud parameterisation to cloud-resolving models might not solve this bias
-without additional effort.
-
-Further analysis will focus on investigating the role of cyclones in the
-identified biases by using cyclone tracking and the role of local thermodynamic
-stability using lower tropospheric stability and estimated inversion strength.
+surface, among other factors responsible for SO SST biases in climate models
+\citep{zhang2023,luo2023}.
+
+We show that ICON underestimates the total cloud fraction by about 10\%, with
+an overestimation of clouds below 2 km, and an underestimation of clouds above
+2 km. The reanalyses also underestimate the total cloud fraction by about 20\%.
+ERA5 overestimates cloud below 1 km but underestimates near-surface cloud or
+fog. In addition to lidar data, we compare radiosonde profiles acquired on the
+RV \textit{Polarstern} voyages with ICON. Notably, the model exhibits smaller
+natural variability than observations, and its lifting condensation level tends
+to be higher. This might explain why cloud occurrence is peaking higher in the
+model (at 500 m) than in observations (at the surface). Similar to our results,
+\cite{cesana2022} showed that CMIP6 also tends to underestimate cloud
+occurrence above 2 km over the SO, although their analysis in this case was
+limited to liquid clouds.  We compared radiosonde profiles acquired on the RV
+\emph{Polarstern} voyages with ICON.  The ICON model exhibits smaller internal
+variability than observations, and its LCL level tends to be higher, which
+might explain why a peak of cloud occurrence in observations is located at the
+surface, while in ICON it is located higher, corresponding to the LCL.
+
+The results imply that SO cloud biases are still a substantial issue in the
+km-scale resolution ICON model, even though an improvement over the
+lower-resolution reanalyses is notable. More effort is needed to improve the
+model cloud simulations in this fast-changing and understudied region. The
+transition from models with parametrised convection and clouds to
+storm-resolving models might not solve this these biases without an additional
+effort. Evaluation of SO ocean--atmosphere heat, moisture and momentum fluxes
+against in situ observations and comparison of GSRM model simulations against
+large-eddy simulations are two potential avenues for future research which
+could elucidate the physical mechanisms behind the biases, in addition to the
+more common efforts in SO cloud microphysics and precipitation evaluation.
 
@@
 Schuddeboom. We acknowledge the ICON model output provided by the nextGEMS
-project and the Deutsches Klimarechenzentrum (DKRZ), reanalysis dataset ERA5
-provided by the Copernicus Climate Change Service and MERRA-2 provided by the
-Global Modeling and Assimilation Office. We dedicate this study to the memory
-of Mike J. Harvey, who very substantially contributed to obtaining the
-atmospheric measurments on the RV \emph{Tangaroa} voyages used in this study.
+project and the DKRZ, reanalysis dataset ERA5 provided by the Copernicus
+Climate Change Service and MERRA-2 provided by the Global Modeling and
+Assimilation Office. We acknowledge supercomputing resources provided by the
+DKRZ.  We dedicate this study to the memory of Mike J. Harvey, who very
+substantially contributed to obtaining the atmospheric observations on the RV
+\emph{Tangaroa} voyages used in this study.
 

### 2024-10-22 manuscript.tex
Various improvements

@@
+% Related publications:
+%
 % Takasuka et al. (2024), A protocol and analysis of year-long simulations of global storm-resolving models and beyond
@@
 \setmainfont{EB Garamond}
-%\setmainfont{Crimson Text}
-%\setmainfont{CrimsonText}[
-%	Path=./fonts/,
-%	Extension=.ttf,
-%	UprightFont=*-Regular,
-%	BoldFont=*-Bold,
-%	ItalicFont=*-Italic,
-%	BoldItalicFont=*-BoldItalic
-%]
-%\setmonofont[Scale=0.8]{Space Mono}
 \setmonofont[Scale=0.8]{SpaceMono}[
@@
 \titlespacing*{\subsection}{0pt}{13pt}{4pt}
-%\renewcommand{\bibsection}{\section*{Publications}}
 \parskip=6pt
@@
 Energy System (CERES) instruments on board of the Terra and Aqua satellites
-\citep{wielicki1996,loeb2018}. In our analysis we use the adjusted all sky SW
+\citep{wielicki1996,loeb2018}. In our analysis we used the adjusted all sky SW
 and LW upwelling fluxes at TOA from the synoptic TOA and surface fluxes and
@@
 were done in such a way that they always represent averages of daily means.
-This is done in order to be consistent with the CERES SYN1deg data, which are
+This was done in order to be consistent with the CERES SYN1deg data, which are
 available as daily means. Therefore, every instantaneous profile in the
-simulated lidar data is assigned a daily mean radiation value corresponding to
+simulated lidar data was assigned a daily mean radiation value corresponding to
 the day (in the Coordinated Universal Time; UTC). In turn, the average
-radiation during the entire voyage or station observation period is calculated
-as the average of the profile values. In the observed lidar data, the daily
-mean radiation value is taken from the spatially and temporally co-located
-CERES SYN1deg data of the day (in UTC). The voyage or station average is
-calculated in the same way.
+radiation during the entire voyage or station observation period were
+calculated as the average of the profile values. In the observed lidar data,
+the daily mean radiation value was taken from the spatially and temporally
+co-located CERES SYN1deg data of the day (in UTC). The voyage or station
+average was calculated in the same way.
 
@@
 Precipitation can cause strong enough lidar backscattering to be recognised as
-a cloud by the threshold-based cloud detection method used in the ALCF. This is
+clouds by the threshold-based cloud detection method used in the ALCF. This is
 undesirable if equivalent precipitation backscatter is not included in the
@@
 more cyclonic in the reanalysis, and around Cape Adere, which is more cyclonic
-in ICON. There differences might, however, stem from the relatively short time
-periods of comparison (4 year) and the fact that the model is free running.
+in ICON. These differences might, however, stem from the relatively short time
+periods of comparison (4 year) and the fact that the model is free-running.
 
@@
 \ref{sec:cyclone-stability}).  The relatively unstable conditions are prevalent
-in the mid SO (50--65°S), which might be explained by the relatively cold
+in the middle SO (50--65°S), which might be explained by the relatively cold
 near-surface air overlying relatively warm sea surface. The relatively stable
@@
 We used the ALCF to derive cloud occurrence by height and the total cloud
-fraction from observations, ICON, and the two reanalyses, ERA5 and MERRA-2
-(Fig.  \ref{fig:cloud-occurrence-panel}). We aggregated the data sources
-(voyages, campaigns and stations) by calculating the averages and percentiles
-of all individual profiles (Fig.  \ref{fig:cloud-occurrence}). The analysis
+fraction from observations, ICON, ERA5 and MERRA-2 (Fig.
+\ref{fig:cloud-occurrence-panel}). In addition, we aggregated the data sources
+(voyages and stations) by calculating the averages and percentiles of all
+individual profiles, presented in Fig. \ref{fig:cloud-occurrence}. The analysis
 shows that the total cloud fraction (determined as the fraction of profiles
 with clouds at any height in the lidar cloud mask) is underestimated in ICON
-and reanalyses by about 10\% and 20\%, respectively. In particular, ICON
-overestimates cloud occurrence below 1 km and underestimates it above, MERRA-2
-underestimates cloud occurrence at all heights, especially near the surface,
-and ERA5 simulates cloud occurrence relatively well above 1 km, but strongly
-underestimates it near the surface.  We note that fog or near-surface clouds
-are strongly lacking in the reanalyses.  As shown in Fig.
+and the reanalyses by about 10\% and 20\%, respectively. When analysed by
+height, ICON overestimates cloud occurrence below 1 km and underestimates it
+above, MERRA-2 underestimates cloud occurrence at all heights, especially near
+the surface, and ERA5 simulates cloud occurrence relatively well above 1 km,
+but strongly underestimates it near the surface.  We note that fog or
+near-surface clouds are strongly lacking in the reanalyses (fog and clouds are
+both included in the cloud occurrence).  As shown in Fig.
 \ref{fig:cloud-occurrence-panel}, the biases are relatively consistent across
-the data sources and longitudes. The ICON results are overall better matching
-the observations than the reanalyses.
+the data sources and longitudes. We conclude that the ICON results are overall
+better matching the observations than the reanalyses in this metric.
 
@@
 occurrence, but ERA5 is very accurate. The too high peak in models is partly
-supported by the LCL distribution, which peaks higher in the models than in the
-observations (at the surface), although this is not very pronounced.
+supported by the lifting condensation level (LCL) distribution, which peaks
+higher in the models than in the observations (at the surface), although this
+is not very pronounced.
 
@@
 non-cyclonic condititions. It also shows a peak of cloud occurrence at higher
-altitude than obs (500 m vs. near the surface), and correspondingly, its LCL
-tends to be also higher. MERRA-2 can be generally characterised as
+altitude than observations (500 m vs. near the surface), and correspondingly,
+its LCL tends to be also higher. MERRA-2 can be generally characterised as
 underestimating cloud occurrence at nearly all altitudes as well as the total
@@
 \subsection{Cloud cover}
+\label{sec:cloud-cover}
 
@@
 In Fig.  \ref{fig:cloud-cover} we show the results for the same subsets of data
-as in the previous section. Observations show the greatest representation of
+as in the previous section. Observations have the greatest representation of
 high cloud cover (5--8 oktas), peaking at 7 oktas. This is not represented by
@@
 
-When analysed by subsets, the cyclonic subset shows the highest cloud cover,
-with 8 oktas occurring on one half of such days (Fig. \ref{fig:cloud-cover}d).
-This is not represented by ICON or the reanalyses at all. Interestingly, clear
-sky days (0 oktas) also have a local maximum peaking at about 15\% in this
-subset.  When we contrast the low- and high-latitude zones, we see that the
-high-latitude zone tends to have greater cloud cover, peaking at 8 oktas (Fig.
-\ref{fig:cloud-cover}c). The high-latitude zone also has almost no clear sky or
-small cloud cover cases (0--4 oktas). ICON and the reanalyses represent at
-least this characteristic of the distribution well for 0--3 oktas, but
-otherwise show bises similar to the general case. One of the greatest biases is
-present in ERA5 in the relatively unstable subset, in which ERA5 peaks at 3
-oktas, whereas the observations peak at 7 oktas and show negligible cloud cover
-below 5 oktas.
+When analysed by subsets, observations in the cyclonic subset show the highest
+cloud cover, with 8 oktas occurring on one half of such days (Fig.
+\ref{fig:cloud-cover}d).  This is not represented by ICON or the reanalyses at
+all. Interestingly, clear sky days (0 oktas) also have a local maximum peaking
+at about 15\% in this subset.  When we contrast the low- and high-latitude
+zones, we see that the high-latitude zone tends to have greater cloud cover,
+peaking at 8 oktas (Fig.  \ref{fig:cloud-cover}c). The high-latitude zone also
+has almost no clear sky or small cloud cover cases (0--4 oktas). ICON and the
+reanalyses represent at least this characteristic of the distribution well for
+0--3 oktas, but otherwise show bises similar to the general case. One of the
+greatest biases is present in ERA5 in the relatively unstable subset, in which
+ERA5 peaks at 3 oktas, whereas the observations peak at 7 oktas and show
+negligible cloud cover below 5 oktas.
 
@@
 the start of the year. The profiles were partitioned into the same subsets as
-the lidar observations: all, 40--55°S, 55+°S, cyclonic, non-cyclonic, stable,
-and unstable. The groups 40--55°S and 55+°S, cyclonic and non-cyclonic, and
-stable and unstable were mutually exclusive in pairs. Apart from relative
-humidity, we focus on comparing virtual potential temperature ($\theta_v$) due
-to its role in low-level tropospheric stability, being one of the primary
-factors affecting shallow convection and the associated low-level cloud
-formation and dissipation. The observed and model profiles of virtual potential
-temperature are shown in Fig. \ref{fig:potential-temperature}.
+above (Sections \ref{sec:cloud-occurrence} and \ref{sec:cloud-cover}).  Apart
+from relative humidity, we focus on comparing virtual potential temperature
+($\theta_v$) due to its role in low-level tropospheric stability, being one of
+the primary factors affecting shallow convection and the associated low-level
+cloud formation and dissipation. The observed and model profiles of virtual
+potential temperature are shown in Fig. \ref{fig:potential-temperature}.
 
@@
 
-We acknowledge the RV \emph{Polarstern} datasets provided by the Alfred Wegener
-Institute and Pangaea, the AA15-16 dataset provided by the Australian Antarctic
-Division (AAD) and University of Canterbury (UC), RV \emph{Tangaroa} datasets
-provided by the National Institute of Water and Atmospheric Research and UC,
-the NBP1704 dataset provided by the National Science Foundation, Cooperative
-Institute for Research in Environmental Sciences, University of Colorado and
-UC, the HMNZSW16 dataset provided by the Royal New Zealand Navy and UC, the
-MARCUS dataset provided by the Atmospheric Radiation Measurement (ARM) and AAD,
-and the MICRE dataset provided by ARM, the Australian Bureau of Meteorology,
-and AAD. We thank the scientific staff, the crew, and everyone involved in
-collecting data on the voyages and stations, especially Kelly Schick, Peter
-Guest, John J.  Cassano, Simon Parsons, Graeme Plank, Sally Garrett, Jamie
-Halla, Sean Hartery, Mike J.  Harvey (†), Simon P.  Alexander and Alex
-Schuddeboom. We acknowledge the ICON model output provided by the nextGEMS
-project and the DKRZ, reanalysis dataset ERA5 provided by the Copernicus
-Climate Change Service and MERRA-2 provided by the Global Modeling and
-Assimilation Office. We acknowledge supercomputing resources provided by the
-DKRZ.  We dedicate this study to the memory of Mike J. Harvey, who very
-substantially contributed to obtaining the atmospheric observations on the RV
-\emph{Tangaroa} voyages used in this study.
+PK and FB received funding from the European Union’s Horizon 2020 research and
+innovation programme under a grant agreement no. 101003470 and supercomputing
+resources were provided by the DKRZ (project 1125 ICON-development) and the
+National Academic Infrastructure for Supercomputing in Sweden (allocation
+2023/22-202).  We acknowledge the RV \emph{Polarstern} datasets provided by the
+Alfred Wegener Institute and Pangaea, the AA15-16 dataset provided by the
+Australian Antarctic Division (AAD) and University of Canterbury (UC), RV
+\emph{Tangaroa} datasets provided by the National Institute of Water and
+Atmospheric Research and UC, the NBP1704 dataset provided by the National
+Science Foundation, Cooperative Institute for Research in Environmental
+Sciences, University of Colorado and UC, the HMNZSW16 dataset provided by the
+Royal New Zealand Navy and UC, the MARCUS dataset provided by the Atmospheric
+Radiation Measurement (ARM) and AAD, and the MICRE dataset provided by ARM, the
+Australian Bureau of Meteorology, and AAD. We thank the scientific staff, the
+crew, and everyone involved in collecting data on the voyages and stations,
+especially Kelly Schick, Peter Guest, John J.  Cassano, Simon Parsons, Graeme
+Plank, Sally Garrett, Jamie Halla, Sean Hartery, Mike J.  Harvey (†), Simon P.
+Alexander and Alex Schuddeboom. We acknowledge the ICON model output provided
+by the nextGEMS project and the DKRZ, reanalysis dataset ERA5 provided by the
+Copernicus Climate Change Service and MERRA-2 provided by the Global Modeling
+and Assimilation Office.  Last but not least, we acknowledge the use of open
+source software Python, Cython \citep{behnel2011}, TensorFlow
+\citep{abadi2016}, Devuan GNU+Linux, parallel \citep{tange2011}, NumPy
+\citep{harris2020}, SciPy \citep{virtanen2020}, Matplotlib \citep{hunter2007},
+cartopy \citep{cartopy}, pyproj, Inkscape, Bash, GNU Fortran, HDF
+\citep{folk1999}, and NetCDF \citep{rew1990}.  We dedicate this study to the
+memory of Mike J.  Harvey, who very substantially contributed to obtaining the
+atmospheric observations on the RV \emph{Tangaroa} voyages used in this study.
 

### 2024-10-22 manuscript.tex
Various improvements

@@
 important, and for this reason such models are generally non-hydrostatic. The
-terms global cloud-resolving models (GCRMs), or global
-convection-permitting/-resolving models (GCPMs) are also sometimes used
-interchangeably with GSRMs but imply that clouds or convection are resolved
-explicitly, which is not entirely true for GSRMs, as this would require an even
-higher horizontal resolution \citep{satoh2019}.  Representative of these
-efforts is the DYnamics of the Atmospheric general circulation Modeled On
-Non-hydrostatic Domains (DYAMOND) project \citep{stevens2019,dyamond}, which is
-an intercomparison of nine global storm-resolving models (GSRMs) on two 40-day
-time periods in summer (1 August -- 10 September 2016) and winter (20 January -
-1 March 2020). A new one-year GSRM intercomparison is currently proposed by
-\cite{takasuka2024}, with the hope of also evaluating the seasonal cycle and
-large-scale circulation.  An alternative to using a computantionally costly
-GSRM is to train an artificial neural network on GSRM output and use it for
-subgrid-scale clouds, as done with the GSRM ICON by \cite{grundner2022};
-\cite{grundner2023}.
+terms global cloud-resolving models, or global convection-permitting/-resolving
+models are also sometimes used interchangeably with GSRMs but imply that clouds
+or convection are resolved explicitly, which is not entirely true for GSRMs, as
+this would require an even higher horizontal resolution \citep{satoh2019}.
+Representative of these efforts is the DYnamics of the Atmospheric general
+circulation Modeled On Non-hydrostatic Domains (DYAMOND) project
+\citep{stevens2019,dyamond}, which is an intercomparison of nine global
+storm-resolving models (GSRMs) on two 40-day time periods in summer (1 August
+-- 10 September 2016) and winter (20 January - 1 March 2020). A new one-year
+GSRM intercomparison is currently proposed by \cite{takasuka2024}, with the
+hope of also evaluating the seasonal cycle and large-scale circulation.  An
+alternative to using a computantionally costly GSRM is to train an artificial
+neural network on GSRM output and use it for subgrid-scale clouds, as done with
+the GSRM ICON by \cite{grundner2022}; \cite{grundner2023}.
 
@@
 
-In general, SST biases in the SO can originate either in the atmosphere, caused
-by too much shortwave heating of the surface, too little longwave cooling of
-the surface, or in the ocean circulation.  Interactions of both are also
-possible, due to, for example SST affecting clouds and clouds affecting the
-surface radiation.  \cite{zhang2023} have shown that SST biases have improved
-in CMIP6 compared to CMIP5 (relative to ERA5), with SST overall increasing in
-the later CMIP phase. However, over the SO this resulted in an even higher
-positive bias, especially in the Atlantic Ocean (AO) sector of the SO,
-increasing by up to 1°C.  \cite{luo2023} identified that the SO SST bias in an
-ensemble of 18 CMIP6 models originates not from the surface heat and radiation
-fluxes (using reanalyses as a reference), but from a warm bias in the Northern
-Atlantic Deep Water.
+In general, sea surface temperature (SST) biases in the SO can originate either
+in the atmosphere, caused by too much shortwave heating of the surface, too
+little longwave cooling of the surface, or in the ocean circulation.
+Interactions of both are also possible, due to, for example SST affecting
+clouds and clouds affecting the surface radiation.  \cite{zhang2023} have shown
+that SST biases have improved in CMIP6 compared to CMIP5 (relative to ERA5),
+with SST overall increasing in the later CMIP phase. However, over the SO this
+resulted in an even higher positive bias, especially in the Atlantic Ocean (AO)
+sector of the SO, increasing by up to 1°C.  \cite{luo2023} identified that the
+SO SST bias in an ensemble of 18 CMIP6 models originates not from the surface
+heat and radiation fluxes (using reanalyses as a reference), but from a warm
+bias in the Northern Atlantic Deep Water.
 
 The main aim of this study is to evaluate the GSRM version of ICON, developed
-jointly by nextGEMS, Deutscher Wetterdienst (DWD), Max-Planck-Institute for
-Meteorology (MPI-M), Deutsches Klimarechenzentrum (DKRZ), Karlsruhe Institute
-of Technology (KIT), and the Center for Climate Systems Modeling (C2SM).
-Previous studies have identified substantial large-scale biases in climate
-model clouds over the SO, affecting sea surface temperature and the Earth’s
-albedo. Our aim is to quantify how well the GSRM ICON is simulating clouds in
-this region, particularly in light of the fact that subgrid-scale clouds and
-convection are not parameterised in this model. This region is mostly dominated
-by boundary layer clouds generated by shallow convection, and these are
-problematic to observe by spaceborne lidars and radars, which are affected by
-attenuation by overlapping and thick clouds and ground clutter, respectively.
-Specifically, the radar on CloudSat and lidar on CALIPSO (neither of them
-operational any more) are affected by the abovementioned issues, resulting in a
-strong underestimation of cloud occurrence below 2 km relative to ground-based
-lidar observations \citep{mcerlich2021}.  This, in turn, can lead to systematic
+jointly by nextGEMS, Deutscher Wetterdienst, Max-Planck-Institute for
+Meteorology, Deutsches Klimarechenzentrum (DKRZ), Karlsruhe Institute of
+Technology, and the Center for Climate Systems Modeling.  Previous studies have
+identified substantial large-scale biases in climate model clouds over the SO,
+affecting sea surface temperature and the Earth’s albedo. Our aim is to
+quantify how well the GSRM ICON is simulating clouds in this region,
+particularly in light of the fact that subgrid-scale clouds and convection are
+not parameterised in this model. This region is mostly dominated by boundary
+layer clouds generated by shallow convection, and these are problematic to
+observe by spaceborne lidars and radars, which are affected by attenuation by
+overlapping and thick clouds and ground clutter, respectively.  Specifically,
+the radar on CloudSat and lidar on CALIPSO (neither of them operational any
+more) are affected by the abovementioned issues, resulting in a strong
+underestimation of cloud occurrence below 2 km relative to ground-based lidar
+observations \citep{mcerlich2021}.  This, in turn, can lead to systematic
 biases in low clouds in climate models, which are frequently evaluated against
@@
 Missing days in the ceilometer data were HMNZSW16 (7 days): 24--27 November, 10
-December, 16--17 December 2016; MARCUS (3 days): 8, 10 November, 10 December;
-MICRE (9 days): 7--8, 29 June, 5, 16 July, 15 August, 17 October 2016, 11
-February, 21 March 2017; TAN1502 (1 day): 24 January.
+December, 16--17 December 2016; Measurements of Aerosols, Radiation, and CloUds
+over the Southern Ocean (MARCUS;  3 days): 8, 10 November, 10 December;
+Macquarie Island Cloud Radiation Experiment (MICRE; 9 days): 7--8, 29 June, 5,
+16 July, 15 August, 17 October 2016, 11 February, 21 March 2017; TAN1502 (1
+day): 24 January.
 
@@
 \cite{kuma2021}.  The instrument data files containing raw uncalibrated
-backscatter were first converted to NetCDF with cl2nc
-(\url{https://github.com/peterkuma/cl2nc}) and then processed with the ALCF
-(Section \ref{sec:alcf}) to produce absolutely calibrated attenuated volume
-backscattering coefficinet (AVBC), cloud mask, cloud occurrence by height and
-the total cloud fraction. Because the CT25K uses a very similar wavelength to
-CL51, equivalent calculations as for CL51 were done assuming a wavelength of
-910 nm. The Vaisala CL51 and CT25K instruments were used on most of the voyages
-and stations analysed here. Fig.  \ref{fig:example}a shows an example of AVBC
-derived from the CL51 instrument data.
+backscatter were first converted to Network Common Data Form (NetCDF) with
+cl2nc (\url{https://github.com/peterkuma/cl2nc}) and then processed with the
+ALCF (Section \ref{sec:alcf}) to produce absolutely calibrated attenuated
+volume backscattering coefficinet (AVBC), cloud mask, cloud occurrence by
+height and the total cloud fraction. Because the CT25K uses a very similar
+wavelength to CL51, equivalent calculations as for CL51 were done assuming a
+wavelength of 910 nm. The Vaisala CL51 and CT25K instruments were used on most
+of the voyages and stations analysed here. Fig.  \ref{fig:example}a shows an
+example of AVBC derived from the CL51 instrument data.
 
@@
 Medium-Range Weather Forecasts (ECMWF). It is based on a numerical weather
-prediction (NWP) model Integrated Forecast System (IFS) version CY41R2.  The
-horizontal resolution is 0.25° in latitude and longitude, which is about 28 km
-in the North--South direction and 14 km in the East--West direction at 60°S.
-Internally, the model uses 137 vertical levels. Here, we use output at 1-hourly
-instantaeous time intervals, except for radiation quantities, which are
-accumulations (from these we calculate daily means).  Vertically-resolved
-quantities are made available on 37 pressure levels.
+prediction model IFS version CY41R2.  The horizontal resolution is 0.25° in
+latitude and longitude, which is about 28 km in the North--South direction and
+14 km in the East--West direction at 60°S.  Internally, the model uses 137
+vertical levels. Here, we use output at 1-hourly instantaeous time intervals,
+except for radiation quantities, which are accumulations (from these we
+calculate daily means).  Vertically-resolved quantities are made available on
+37 pressure levels.
 
@@
 
-TOA radiation quantities are taken from the Clouds and the Earth’s Radiant
-Energy System (CERES) instruments on board of the Terra and Aqua satellites
-\citep{wielicki1996,loeb2018}. In our analysis we used the adjusted all sky SW
-and LW upwelling fluxes at TOA from the synoptic TOA and surface fluxes and
-clouds 1 degree daily edition 4A product
+TOA radiation quantities are taken from the CERES instruments on board of the
+Terra and Aqua satellites \citep{wielicki1996,loeb2018}. In our analysis we
+used the adjusted all sky SW and LW upwelling fluxes at TOA from the synoptic
+TOA and surface fluxes and clouds 1 degree daily edition 4A product
 (CER\_SYN1deg-Day\_Terra-Aqua-MODIS\_Edition4A)
@@
 extremes of occurrence are notable, especially over the Amundsen Sea, which is
-more cyclonic in the reanalysis, and around Cape Adere, which is more cyclonic
+more cyclonic in the reanalysis, and around Cape Adare, which is more cyclonic
 in ICON. These differences might, however, stem from the relatively short time

### 2024-10-22 manuscript.tex
Minor fixes

@@
 graphics processing units (GPGPUs) is progressing to enable km-scale (also
-called k-scale) Earth system models (ESMs) and coupled atmosphsere--ocean
+called k-scale) Earth system models (ESMs) and coupled atmosphere--ocean
 general circulation models (AOGCMs) in research conditions today and
@@
 storm-resolving models (GSRMs) on two 40-day time periods in summer (1 August
--- 10 September 2016) and winter (20 January - 1 March 2020). A new one-year
+-- 10 September 2016) and winter (20 January -- 1 March 2020). A new one-year
 GSRM intercomparison is currently proposed by \cite{takasuka2024}, with the
@@
 neural network on GSRM output and use it for subgrid-scale clouds, as done with
-the GSRM ICON by \cite{grundner2022}; \cite{grundner2023}.
+the GSRM ICON by \cite{grundner2022} and \cite{grundner2023}.
 
@@
 interaction with aerosols.  In the 6$^\mathrm{th}$ phase of the Coupled Model
-Intercomparison Project [CMIP6; \citep{eyring2016}], the cloud feedback has
+Intercomparison Project [CMIP6; \cite{eyring2016}], the cloud feedback has
 increased relative to CMIP5 \citep{zelinka2020}, also being one of the main
@@
 \& Anisotropy of Reflectances for Atmospheric Sciences coupled with
-Observations from a Lidar [PARASOL; \citep{lier2008}] as a reference. They
+Observations from a Lidar [PARASOL; \cite{lier2008}] as a reference. They
 suggest improper simulation of subgrid-scale cloud heterogeneity as a cause.
@@
 achieve a like-for-like comparison with the model, we used a ground-based lidar
-simulator called the Automatic Lidar and Ceilometer Framework (ALCF)
-\citep{kuma2021}. We contrasted the results with the European Centre for
-Medium-Range Weather Forecasts (ECMWF) Reanalysis 5 (ERA5) \citep{era5} and the
+simulator called the Automatic Lidar and Ceilometer Framework [ALCF;
+\cite{kuma2021}]. We contrasted the results with the European Centre for
+Medium-Range Weather Forecasts (ECMWF) Reanalysis 5 [ERA5; \cite{era5}] and the
 Modern-Era Retrospective analysis for Research and Applications, Version 2
-(MERRA-2) \citep{gelaro2017}.
+[MERRA-2; \cite{gelaro2017}].
 

### 2024-10-22 manuscript.tex
Fix grammar

@@
 important, and for this reason such models are generally non-hydrostatic. The
-terms global cloud-resolving models, or global convection-permitting/-resolving
+terms global cloud-resolving models or global convection-permitting/-resolving
 models are also sometimes used interchangeably with GSRMs but imply that clouds
@@
 hope of also evaluating the seasonal cycle and large-scale circulation.  An
-alternative to using a computantionally costly GSRM is to train an artificial
+alternative to using a computationally costly GSRM is to train an artificial
 neural network on GSRM output and use it for subgrid-scale clouds, as done with
@@
 important part of the global ocean conveyor belt.  Marine clouds have
-disproportionate effect on top of atmosphere (TOA) SW radiation due to the
+a disproportionate effect on top of atmosphere (TOA) SW radiation due to the
 relatively low albedo of the sea surface.  The relative longitudinal symmetry
@@
 particularly in light of the fact that subgrid-scale clouds and convection are
-not parameterised in this model. This region is mostly dominated by boundary
+not parameterized in this model. This region is mostly dominated by boundary
 layer clouds generated by shallow convection, and these are problematic to
@@
 
-Altogether, we analysed about 2400 days of data from 31 voyages and one
+Altogether, we analysed about 2400 days of data from 31 voyages, and one
 sub-Antarctic station covering diverse longitudes and latitudes of the SO. To
@@
 and 2021. Fig. \ref{fig:map} shows a map of the voyages, Table
-\ref{tab:voyages} list the voyages, campaigns and stations, and Table
+\ref{tab:voyages} list the voyages, campaigns, and stations, and Table
 \ref{tab:voyage-references} lists references where available. Altogether, the
@@
 The data sources contained ceilometer observations captured by the Vaisala CL51
- perating at a wavelenght of 910 nm, Vaisala CT25K operating at 905 nm, and
-Lufft CHM 15k operating at 1064 nm, described in detail below (Sections
+ perating at a wavelenght of 910 nm, the Vaisala CT25K operating at 905 nm, and
+the Lufft CHM 15k operating at 1064 nm, described in detail below (Sections
 \ref{sec:cl51} and \ref{sec:chm15k}). A ceilometer is a low-power near-infrared
@@
 \caption{
-An overview of the analysed voyages, campaigns and stations. Start, end, and
+An overview of the analysed voyages, campaigns, and stations. Start, end, and
 the number of days (UTC; inclusive) refer to the time period when the vessel
@@
 7.5 km (CT25K). The vertical resolution is 10 m (5 m configurable) in CL51 and
-30 m in CT25K. The sampling (temporal) resolution is configurable and in our
+30 m in CT25K. The sampling (temporal) resolution is configurable, and in our
 datasets it is about 6 s for CL51 on AA15‐16, 16 s for CT25K on MARCUS and
@@
 ALCF (Section \ref{sec:alcf}) to produce absolutely calibrated attenuated
-volume backscattering coefficinet (AVBC), cloud mask, cloud occurrence by
-height and the total cloud fraction. Because the CT25K uses a very similar
+volume backscattering coefficient (AVBC), cloud mask, cloud occurrence by
+height, and the total cloud fraction. Because the CT25K uses a very similar
 wavelength to CL51, equivalent calculations as for CL51 were done assuming a
@@
 were processed with the ALCF (Section \ref{sec:alcf}) to produce AVBC, cloud
-mask, cloud occurrence by height and the total cloud fraction. The CHM 15k was
+mask, cloud occurrence by height, and the total cloud fraction. The CHM 15k was
 used on four voyages (HMNZSW16, TAN1702, TAN1802, and NBP1704).
@@
 molecular backscatter. AVBC was resampled to 5 min temporal resolution and 50 m
-vertical resolution to increase signal-to-noise ratio, while having enough
-resolution to detect small-scale cloud variability. Noise standard deviation
-was calculated from AVBC at the highest range, where no clouds are expected.  A
-cloud mask was calculated from AVBC using a fixed threshold of $\mathrm{2\times
-10^{-6} m^{-1}sr^{-1}}$ after subtracting 5 standard deviations of range-scale
-noise. Fig. \ref{fig:example}b shows an example of simulated Vaisala CL51
-backscatter from ERA5 data, corresponding to a day of measurements by the
-instrument on the PS81/3 voyage.
+vertical resolution to increase signal-to-noise ratio while having enough
+resolution to detect small-scale cloud variability. The noise standard
+deviation was calculated from AVBC at the highest range, where no clouds are
+expected.  A cloud mask was calculated from AVBC using a fixed threshold of
+$\mathrm{2\times 10^{-6} m^{-1}sr^{-1}}$ after subtracting 5 standard
+deviations of range-scale noise. Fig. \ref{fig:example}b shows an example of
+simulated Vaisala CL51 backscatter from ERA5 data, corresponding to a day of
+measurements by the instrument on the PS81/3 voyage.
 
@@
 
-Here, we use a free-running (i.e. \emph{not} nudged or using prescribed SST)
-coupled GSRM simulation made for the purpse of climate projection.  nextGEMS
+Here, we use a free-running (i.e., \emph{not} nudged or using prescribed SST)
+coupled GSRM simulation made for the purpose of climate projection.  nextGEMS
 has so far produced four cycles of model runs. We used a Cycle 3 run
@@
 years 2021--2024 (inclusive). While a Cycle 4 run was available, we could not
-use it due it to the unavailability of the necessary variables. The horizontal
+use it due to the unavailability of the necessary variables. The horizontal
 resolution of ngc3028 is about 5 km.  The model output is available on 90
@@
 general circulation models (GCMs), the strom-resolving version of ICON does not
-use convective and cloud parameterisation but relies on explicit simulation of
+use convective and cloud parameterization but relies on explicit simulation of
 convection and clouds on the model grid. While this makes the code development
-simpler without having to rely on uncertain parameterisations, it can miss
+simpler without having to rely on uncertain parameterizations, it can miss
 smaller-scale clouds below the grid resolution.  Turbulence and cloud
-microphysics are still parameterised in this model.
+microphysics are still parameterized in this model.
 
@@
 except for radiation quantities, which are accumulations (from these we
-calculate daily means).  Vertically-resolved quantities are made available on
+calculate daily means).  Vertically resolved quantities are made available on
 37 pressure levels.
@@
 \textbf{(b)} randomly selected example samples of near-surface backscatter in
-four categories (clear, fog, rain and snow), as determined by coincident
+four categories (clear, fog, rain, and snow), as determined by coincident
 human-performed weather observations, \textbf{(c)} receiver operating
@@
 output and the reanalysis data (the liquid and ice precipitation mass mixing
-ratios), and because the required radiation calculations for precipitation are
+ratios) and because the required radiation calculations for precipitation are
 currently not implemented in the ALCF. In order to achieve a fair comparison of
@@
 inconsistencies in the rain gauge time series. Human-performed observations of
-precipitation presence or absence are expected to be reliable, but only cover a
+precipitation presence or absence are expected to be reliable but only cover a
 limited set of time instants. Therefore, it was desirable to implement a method
@@
 
-We partitioned our data into two mutually-exclusive subsets by cyclonic
+We partitioned our data into two mutually exclusive subsets by cyclonic
 activity. For this purpose, we used a cyclone tracking algorithm to identify
@@
 
-In addition to the above, we partitioned our data into two mutually-exclusive
+In addition to the above, we partitioned our data into two mutually exclusive
 subsets by stability. We determined this by calculating lower tropospheric
@@
 Here, we briefly describe the results of the cyclonic activity and stability
-distribution, which is relavant for the subsequent analaysis, because these
+distribution, which is relevant for the subsequent analysis, because these
 conditions are used for subsetting our dataset. Fig.
@@
 in ICON. These differences might, however, stem from the relatively short time
-periods of comparison (4 year) and the fact that the model is free-running.
+periods of comparison (4 years) and the fact that the model is free-running.
 
@@
 in the middle SO (50--65°S), which might be explained by the relatively cold
-near-surface air overlying relatively warm sea surface. The relatively stable
-conditions are prevalent elsewhere over the SO. The distribution is also less
-zonally symmetric than the cyclonic activity.  In the high-latitude SO, the
-presence of sea ice might have substantial stabilising effect
+near-surface air overlying the relatively warm sea surface. The relatively
+stable conditions are prevalent elsewhere over the SO. The distribution is also
+less zonally symmetric than the cyclonic activity.  In the high-latitude SO,
+the presence of sea ice might have substantial stabilising effect
 \citep{knight2024}. The ERA5 renalysis is also substantially more stable than
@@
 \caption{Cloud occurrence by height for the 31 voyages and one sub-Antarctic
-station (MICRE) in observations (OBS), and simulated by the ALCF from the
-ICON model, MERRA‐2 (M2) and ERA5 reanalysis data. The numbers in the legend
+station (MICRE) in observations (OBS) and simulated by the ALCF from the
+ICON model, MERRA‐2 (M2), and ERA5 reanalysis data. The numbers in the legend
 indicate the total cloud fraction and the number of days of data.}
@@
 cloud fraction, and showing greatest biases in the relatively unstable and
-non-cyclonic condititions. It also shows a peak of cloud occurrence at higher
+non-cyclonic conditions. It also shows a peak of cloud occurrence at higher
 altitude than observations (500 m vs. near the surface), and correspondingly,
@@
 towards understimation in the low-latitude SO zone and the relatively unstable
-situations, conversely, overestimating in the high-latitude SO zone and the
+situations; conversely, overestimating in the high-latitude SO zone and the
 relatively stable conditions.
@@
 stations for the observed (OBS) and simulated lidar cloud mask. The total cloud
-fraction (CF), average shortwave (SW) and longwave (LW) are shown in the
+fraction (CF), average shortwave (SW), and longwave (LW) are shown in the
 legend, and the relative frequency of occurrence (RFO) of the subset is shown
@@
 with 8 oktas.  Overall, the reanalyses show results similar to each other,
-underestimating cloud cover by about 2 oktas, and strongly understimating days
+underestimating cloud cover by about 2 oktas and strongly understimating days
 with 7 and 8 oktas. Of the two reanalyses, MERRA-2 shows slightly higher cloud
@@
 Relative humidity displays much larger biases. In all subsets, ICON is too
-humid in the first 1 km, but very accorate above, except for the 40--55°S zone
+humid in the first 1 km but very accurate above, except for the 40--55°S zone
 and unstable conditions (Fig. \ref{fig:potential-temperature}b, g),  where it
@@
 Let us consider the main limitations of the presented results. The spatial
-coverage of our dataset does not include most parts of the the Indian Ocean and
+coverage of our dataset does not include most parts of the Indian Ocean and
 Pacific Ocean sectors of the SO. Even though climatological features of the SO
@@
 related to the Antarctic Peninsula and the southern tip of South America. The
-voyages were mostly undertaken in the Austral summer months, and only rarely in
+voyages were mostly undertaken in the Austral summer months and only rarely in
 the winter months, due to the poor accesibility of this region during winter.
-Therefore, our results are mostly representative of summer, and to lesser
-extent spring and autumn conditions.
-
-The time period of ICON is relatively short with only four full years of
+Therefore, our results are mostly representative of summer and to a lesser
+extent, spring and autumn conditions.
+
+The time period of ICON is relatively short, with only four full years of
 simulation available. Moreover, the simulation is free-running, which means
@@
 layers, and for this reason the results are mostly representative of boundary
-layer clouds, while higher-level clouds are only occassionaly visible to the
+layer clouds, while higher-level clouds are only occasionally visible to the
 lidar when boundary layer clouds are not present. Ground-based lidar
@@
 properly simulated with the lidar simulator (Section \ref{sec:ann}). However,
-the approach was limited by relatively low sensitivity of the ANN (65\%), and
-the fact that we had to choose a fixed threshold for surface precipitation flux
-in the model and reanalyses, which might not exactly correspond to detection by
-the ANN applied to obseravations. Also, we did not make an attempt to remove
-profiles with precipitation not reaching the surface. The above reasons can
-result in an artificial bias in the comparison, even though we expect this to
-be much smaller than the identified model biases.
+the approach was limited by the relatively low sensitivity of the ANN (65\%)
+and the fact that we had to choose a fixed threshold for surface precipitation
+flux in the model and reanalyses, which might not exactly correspond to
+detection by the ANN applied to obseravations. Also, we did not make an attempt
+to remove profiles with precipitation not reaching the surface. The above
+reasons can result in an artificial bias in the comparison, even though we
+expect this to be much smaller than the identified model biases.
 
@@
 voyages and campaigns and one subantarctic station data, covering the Atlantic,
-Australian and New Zealand sectors of the SO over the span of 10 years. This
+Australian, and New Zealand sectors of the SO over the span of 10 years. This
 dataset, together with the use of the ALCF lidar simulator, provided a fairly
@@
 the GSRM ICON and the ERA5 and MERRA-2 reanalyses. This provides a unique
-evaluation perspective different from satellite observations, one which is more
+evaluation perspective different from satellite observations, one that is more
 suitable for evaluating bounary layer clouds, which are predominant in this
 region. Furthermore, we subsetted our dataset by low and high latitude bands,
-cyclonic activity and stability, in order to identify how these conditions
-relate the the biases. Our main finding corroborates previous findings of large
-boundary layer cloud biases in models, and their subsequent effect on the
+cyclonic activity, and stability in order to identify how these conditions
+relate to the biases. Our main finding corroborates previous findings of large
+boundary layer cloud biases in models and their subsequent effect on the
 radiative transfer. This also applies to the new ICON GSRM, but the biases are
@@
 assimilation of the observed meteorological conditions.  The GSRM has, on the
-other hand, the advange of a much higher spatial resolution and, to a limited
+other hand, the advantage of a much higher spatial resolution and, to a limited
 extent, explicit calculation of traditionally subgrid-scale processes such as
@@
 than observations, and the deficit of outgoing TOA SW radiation is
-approximately proportial to the deficit of the total cloud fraction. While this
+approximately proportional to the deficit of the total cloud fraction. While this
 might be a welcome feature and an improvement over previous models, it does
-mean that the outgoing TOA SW radiation is overall underestimated, instead of
+mean that the outgoing TOA SW radiation is overall underestimated instead of
 being compensated by a higher cloud albedo. This can, of course, lead to
@@
 We show that ICON underestimates the total cloud fraction by about 10\%, with
-an overestimation of clouds below 2 km, and an underestimation of clouds above
+an overestimation of clouds below 2 km and an underestimation of clouds above
 2 km. The reanalyses also underestimate the total cloud fraction by about 20\%.
@@
 transition from models with parametrised convection and clouds to
-storm-resolving models might not solve this these biases without an additional
-effort. Evaluation of SO ocean--atmosphere heat, moisture and momentum fluxes
+storm-resolving models might not solve these biases without additional
+effort. Evaluation of SO ocean--atmosphere heat, moisture, and momentum fluxes
 against in situ observations and comparison of GSRM model simulations against
-large-eddy simulations are two potential avenues for future research which
+large-eddy simulations are two potential avenues for future research that
 could elucidate the physical mechanisms behind the biases, in addition to the
@@
 PK and FB received funding from the European Union’s Horizon 2020 research and
-innovation programme under a grant agreement no. 101003470 and supercomputing
+innovation program under a grant agreement no. 101003470, and supercomputing
 resources were provided by the DKRZ (project 1125 ICON-development) and the
@@
 Plank, Sally Garrett, Jamie Halla, Sean Hartery, Mike J.  Harvey (†), Simon P.
-Alexander and Alex Schuddeboom. We acknowledge the ICON model output provided
+Alexander, and Alex Schuddeboom. We acknowledge the ICON model output provided
 by the nextGEMS project and the DKRZ, reanalysis dataset ERA5 provided by the
@@
 processing and plotting code are open source and available at
-\url{https://alcf.peterkuma.net}, \url{https://github.com/peterkuma/cl2nc}, and
+\url{https://alcf.peterkuma.net}, \url{https://github.com/peterkuma/cl2nc},
 \url{https://github.com/peterkuma/rstool}, and
@@
 Science Data Centre (\url{https://asdc.larc.nasa.gov/project/CERES}).  The
-TAN1802 data ara available on Zenodo
+TAN1802 data are available on Zenodo
 (\url{https://doi.org/10.5281/zenodo.4060237}).  The other voyage and station

### 2024-10-22 manuscript.tex
Various improvements

@@
 
-Global storm-resolving models (GSRMs) are developed as the forthcoming phase of
-climate modelling. Among them is a 5-km Icosahedral Nonhydrostatic Weather and
-Climate Model (ICON). Due to the resolution, parametrisations of convection and
-clouds are avoided. Standard-resolution models have substantial cloud biases
-over the Southern Ocean (SO), affecting radiation and sea surface temperature.
-We quantify how the GSRM ICON simulates clouds over the SO and contrast it with
-the ECMWF Reanalysis 5 (ERA5) and Modern-Era Retrospective analysis for
-Research and Applications, Version 2 (MERRA-2). The SO is dominated by boundary
-layer clouds, which often cannot be observed properly by speceborne instruments
-due to overlapping clouds, attenuation, and ground clutter. Instead, we use
-about 2400 days of ship-based lidar observations from 31 voyages and one
-subantarctic station. We use a ground-based lidar simulator for a like-for-like
-comparison. ICON underestimates the total cloud fraction (TCF) by about 10\%,
-with overestimation of clouds below 2 km and underestimation of clouds above 2
-km. The reanalyses underestimate TCF by about 20\%. ERA5 overestimates clouds
-below 1 km but underestimates near-surface clouds or fog. Compared to
-radiosonde observations, ICON exhibits smaller natural variability, and its
-lifting condensation level is higher, which might explain why cloud occurrence
-peaks higher in the model than in observations. SO cloud biases are still a
-substantial issue in a GSRM, even though an improvement over the
-lower-resolution reanalyses is notable. The transition from parametrisation to
-explicitly resolved convection and cloud processes might not be enough to
-address the model cloud biases.
+Global storm-resolving models (GSRMs) are the next avenue of climate modelling.
+Among them is a 5-km Icosahedral Nonhydrostatic Weather and Climate Model
+(ICON). Due to the resolution, parametrisations of convection and clouds are
+avoided. Standard-resolution models have substantial cloud biases over the
+Southern Ocean (SO), affecting radiation and sea surface temperature.  We
+evaluated SO clouds in ICON and the ERA5 and MERRA-2 reanalyses.  The SO is
+dominated by low clouds, which cannot be observed properly from space due to
+overlapping clouds, attenuation, and ground clutter.  Instead, we analysed
+about 2400 days of lidar observations from 31 voyages and a station using a
+ground-based lidar simulator.  ICON and the reanalyses underestimate the total
+cloud fraction by about 10 and 20\%, respectively. ICON and ERA5 overestimate
+the cloud occurrence peak at about 500 m, potentially explained by their
+lifting condensation level being too high.  The reanalyses strongly
+underestimate near-surface clouds or fog.  MERRA-2 tends to underestimate cloud
+occurrence at all heights. Unstable conditions are the most problematic for the
+models. In daily cloud cover, ICON and the reanalyses tend to be about 1 and 2
+oktas clearer, respectively. Compared to radiosondes, potential temperature is
+accurate in all, but ICON is too unstable over low-latitude SO and too
+moist near the surface. MERRA-2 is too humid at all heights. SO cloud biases
+are a substantial issue in the GSRM, but it is an improvement over the
+lower-resolution reanalyses. Explicitly resolved convection and cloud processes
+were not enough to address the model cloud biases.
 
@@
 
-We analysed a total of about 2400 days of lidar and radiosonde data from 31
-voyages and campaigns and one subantarctic station data, covering the Atlantic,
-Australian, and New Zealand sectors of the SO over the span of 10 years. This
-dataset, together with the use of the ALCF lidar simulator, provided a fairly
-comprehensive basis for evaluating SO cloud and thermodynamic profile biases in
-the GSRM ICON and the ERA5 and MERRA-2 reanalyses. This provides a unique
-evaluation perspective different from satellite observations, one that is more
-suitable for evaluating bounary layer clouds, which are predominant in this
-region. Furthermore, we subsetted our dataset by low and high latitude bands,
-cyclonic activity, and stability in order to identify how these conditions
-relate to the biases. Our main finding corroborates previous findings of large
-boundary layer cloud biases in models and their subsequent effect on the
-radiative transfer. This also applies to the new ICON GSRM, but the biases are
-lower than in the reanalyses, despite the reanalyses having the advantage of
-assimilation of the observed meteorological conditions.  The GSRM has, on the
-other hand, the advantage of a much higher spatial resolution and, to a limited
-extent, explicit calculation of traditionally subgrid-scale processes such as
+We analysed a total of about 2400 days of lidar and 2300 radiosonde
+observations from 31 voyages/campaigns and a subantarctic station, covering the
+Atlantic, Australian, and New Zealand sectors of the SO over the span of 10
+years. This dataset, together with the use of a ground-based lidar simulator,
+provided a fairly comprehensive basis for evaluating SO cloud and thermodynamic
+profile biases in the GSRM ICON and the ERA5 and MERRA-2 reanalyses. Our
+analysis provides a unique evaluation perspective different from satellite
+observations -- one that is more suitable for evaluating bounary layer clouds,
+which are predominant in this region. Furthermore, we subsetted our dataset by
+low and high latitude bands, cyclonic activity, and stability in order to
+identify how these conditions relate to the biases.
+
+Our main finding corroborates previous findings of large boundary layer cloud
+biases in models and their subsequent effect on the radiative transfer. This
+also applies to the new GSRM ICON, but the biases are lower than in the
+reanalyses, despite the reanalyses having the advantage of assimilation of the
+observed meteorological conditions.  The GSRM has, on the other hand, the
+advantage of a much higher spatial resolution and, to a limited extent,
+explicit calculation of traditionally subgrid-scale processes such as
 convection.
+
+We show that relative to ERA5, the distribution and strength of cyclonic
+activity over the SO is well represented in ICON, but it is substantially less
+stable in terms of LTS. The latter is also manifested in the radiosonde profile
+comparison, which shows that the virtual potential temperature profiles in ICON
+are more stable than in the observations over low-latitude SO.
+
+The 31 voyages and a station show fairly similar biases in cloud occurrence by
+height in the lidar comparison, which indicates that common underlying causes
+for the biases exist regardless of longitude and season. ICON underestimates
+the total cloud fraction by about 10\%, with an overestimation of clouds below
+2 km and an underestimation of clouds above 2 km. The reanalyses also
+underestimate the total cloud fraction by about 20\%.  ERA5 overestimates cloud
+below 1 km but underestimates near-surface cloud or fog. ICON strongly
+overestimates the peak of cloud occurrence at about 500 m, which might be
+explained by the radiosonde comparison, which shows that it is too moist at
+around this height.  Similar to our results, \cite{cesana2022} showed that
+CMIP6 models also tend to underestimate cloud occurrence above 2 km over the
+SO, although their analysis in this case was limited to liquid clouds.
+
+Compared to the lidar observations, the daily cloud cover tends to be about 1
+okta lower in ICON and 2 oktas lower in the reanalyses.  Unstable conditions
+are associated with some of the greatest biases, especially in ERA5.  The
+models also underestimate the cloud cover very strongly in cyclonic conditions,
+which are very cloudy in the observations (8 oktas), but much less so in the
+models.
+
+The radiosonde observations indicate that the LCL is too high in ICON and
+reanalyses, which is probably responsible for the higher peak of clouds in the
+models and the lack of near-surface clouds or fog. The radiosonde comparison,
+however, does not seem to explain cloud biases at higher altitudes.  MERRA-2 is
+too moist at all heights.  ICON also exhibits smaller internal variability than
+the radiosonde observations. Overall, the radiosonde comparison is only
+partially explaining the identified cloud biases, and other physical causes are
+likely contributing.  This warrants further investigation, especially of
+ocean--atmosphere fluxes, shallow convection, and boundary layer turbulence.
+The lack of parametrised subgrid-scale convection in ICON might be a
+substantial issue even at the 5-km resolution.
 
@@
 bright bias previously identified in models. In our results, this is
-characterised by outgoing TOA SW radiation similar to or higher than in
+characterised by outgoing TOA SW radiation similar to or higher than in the
 satellite observations, while at the same time total cloud fraction is
@@
 
-We show that ICON underestimates the total cloud fraction by about 10\%, with
-an overestimation of clouds below 2 km and an underestimation of clouds above
-2 km. The reanalyses also underestimate the total cloud fraction by about 20\%.
-ERA5 overestimates cloud below 1 km but underestimates near-surface cloud or
-fog. In addition to lidar data, we compare radiosonde profiles acquired on the
-RV \textit{Polarstern} voyages with ICON. Notably, the model exhibits smaller
-natural variability than observations, and its lifting condensation level tends
-to be higher. This might explain why cloud occurrence is peaking higher in the
-model (at 500 m) than in observations (at the surface). Similar to our results,
-\cite{cesana2022} showed that CMIP6 also tends to underestimate cloud
-occurrence above 2 km over the SO, although their analysis in this case was
-limited to liquid clouds.  We compared radiosonde profiles acquired on the RV
-\emph{Polarstern} voyages with ICON.  The ICON model exhibits smaller internal
-variability than observations, and its LCL level tends to be higher, which
-might explain why a peak of cloud occurrence in observations is located at the
-surface, while in ICON it is located higher, corresponding to the LCL.
-
 The results imply that SO cloud biases are still a substantial issue in the
@@
 PK and FB received funding from the European Union’s Horizon 2020 research and
-innovation program under a grant agreement no. 101003470, and supercomputing
+innovation program under a grant agreement no. 101003470. Supercomputing
 resources were provided by the DKRZ (project 1125 ICON-development) and the

### 2024-10-22 manuscript.tex
Minor improvements

@@
 \small
-$^\mathsf{1}$Department of Meteorology (MISU) and Bolin Centre for Climate Research, Stockholm University, Stockholm SE-106 91, Sweden\\[0.2cm]
+$^\mathsf{1}$Department of Meteorology (MISU) and the the Bolin Centre for Climate Research, Stockholm University, Stockholm SE-106 91, Sweden\\[0.2cm]
 *Corresponding author: Peter Kuma (\href{mailto:peter.kuma@misu.su.se}{peter.kuma@misu.su.se})\\[0.4cm]
@@
 oktas clearer, respectively. Compared to radiosondes, potential temperature is
-accurate in all, but ICON is too unstable over low-latitude SO and too
-moist near the surface. MERRA-2 is too humid at all heights. SO cloud biases
-are a substantial issue in the GSRM, but it is an improvement over the
+accurate in all, but ICON is too unstable over low-latitude SO and too humid in
+the boundary layer. MERRA-2 is too humid at all heights. SO cloud biases are a
+substantial issue in the GSRM, but it is an improvement over the
 lower-resolution reanalyses. Explicitly resolved convection and cloud processes

### 2024-10-22 manuscript.tex
Fix typo

@@
 \small
-$^\mathsf{1}$Department of Meteorology (MISU) and the the Bolin Centre for Climate Research, Stockholm University, Stockholm SE-106 91, Sweden\\[0.2cm]
+$^\mathsf{1}$Department of Meteorology (MISU) and the Bolin Centre for Climate Research, Stockholm University, Stockholm SE-106 91, Sweden\\[0.2cm]
 *Corresponding author: Peter Kuma (\href{mailto:peter.kuma@misu.su.se}{peter.kuma@misu.su.se})\\[0.4cm]

### 2024-10-22 manuscript.tex
Fix typo

@@
 The data sources contained ceilometer observations captured by the Vaisala CL51
- perating at a wavelenght of 910 nm, the Vaisala CT25K operating at 905 nm, and
+operating at a wavelenght of 910 nm, the Vaisala CT25K operating at 905 nm, and
 the Lufft CHM 15k operating at 1064 nm, described in detail below (Sections

### 2024-10-24 manuscript.tex
Minor edits

@@
 	pdftitle={Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON, and the ERA5 and MERRA-2 reanalyses},
-	pdfauthor={Peter Kuma, Frida A.-M. Bender, …}
+	pdfauthor={Peter Kuma, Frida A.-M. Bender, Adrian J. McDonald, …}
 }
@@
 \begin{center} \Large \sffamily\textbf{Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON and the ERA5 and MERRA-2 reanalyses}\\[0.4cm]
-\large Peter Kuma$^\mathsf{1,}$*, Frida A.-M. Bender$^\mathsf{1}$, \ldots\\[0.4cm]
+\large Peter Kuma$^\mathsf{1,}$*, Frida A.-M. Bender$^\mathsf{1}$, Adrian J. McDonald$^\mathsf{2}$, \ldots\\[0.4cm]
 \small
-$^\mathsf{1}$Department of Meteorology (MISU) and the Bolin Centre for Climate Research, Stockholm University, Stockholm SE-106 91, Sweden\\[0.2cm]
+$^\mathsf{1}$Department of Meteorology (MISU) and the Bolin Centre for Climate Research, Stockholm University, Stockholm SE-106 91, Sweden\\
+$^\mathsf{2}$School of Physical and Chemical Sciences, University of Canterbury, Christchurch, Aotearoa/New Zealand\\[0.2cm]
 *Corresponding author: Peter Kuma (\href{mailto:peter.kuma@misu.su.se}{peter.kuma@misu.su.se})\\[0.4cm]
@@
 circulation Modeled On Non-hydrostatic Domains (DYAMOND) project
-\citep{stevens2019,dyamond}, which is an intercomparison of nine global
-storm-resolving models (GSRMs) on two 40-day time periods in summer (1 August
--- 10 September 2016) and winter (20 January -- 1 March 2020). A new one-year
-GSRM intercomparison is currently proposed by \cite{takasuka2024}, with the
-hope of also evaluating the seasonal cycle and large-scale circulation.  An
-alternative to using a computationally costly GSRM is to train an artificial
-neural network on GSRM output and use it for subgrid-scale clouds, as done with
-the GSRM ICON by \cite{grundner2022} and \cite{grundner2023}.
+\citep{stevens2019,dyamond}, which is an intercomparison of nine global GSRMs
+on two 40-day time periods in summer (1 August -- 10 September 2016) and winter
+(20 January -- 1 March 2020). A new one-year GSRM intercomparison is currently
+proposed by \cite{takasuka2024}, with the hope of also evaluating the seasonal
+cycle and large-scale circulation.  An alternative to using a computationally
+costly GSRM is to train an artificial neural network on GSRM output and use it
+for subgrid-scale clouds, as done with the GSRM ICON by \cite{grundner2022} and
+\cite{grundner2023}.
 
@@
 
-[TODO]
+The authors have made the following contributions based on the CRediT taxonomy
+(\url{https://credit.niso.org}).  PK: conceptualization, data curation, formal
+analysis, investigation, methodology, software, writing – original draft; FB:
+conceptualization, funding acquisition, project administration, supervision,
+and writing – review \& editing; AM: data curation, investigation, resources,
+writing – review \& editing. [TODO]
 

### 2024-10-24 manuscript.tex
Minor edits

@@
 clouds and clouds affecting the surface radiation.  \cite{zhang2023} have shown
-that SST biases have improved in CMIP6 compared to CMIP5 (relative to ERA5),
+that SST biases have improved in CMIP6 compared to CMIP5 [relative to the
+European Centre for Medium-Range Weather Forecasts (ECMWF) Reanalysis 5; ERA5],
 with SST overall increasing in the later CMIP phase. However, over the SO this
@@
 simulator called the Automatic Lidar and Ceilometer Framework [ALCF;
-\cite{kuma2021}]. We contrasted the results with the European Centre for
-Medium-Range Weather Forecasts (ECMWF) Reanalysis 5 [ERA5; \cite{era5}] and the
+\cite{kuma2021}]. We contrasted the results with ERA5 \citep{era5} and the
 Modern-Era Retrospective analysis for Research and Applications, Version 2
@@
 
-ERA5 \citep{era5} is a reanalysis produced by the European Centre for
-Medium-Range Weather Forecasts (ECMWF). It is based on a numerical weather
-prediction model IFS version CY41R2.  The horizontal resolution is 0.25° in
-latitude and longitude, which is about 28 km in the North--South direction and
-14 km in the East--West direction at 60°S.  Internally, the model uses 137
-vertical levels. Here, we use output at 1-hourly instantaeous time intervals,
-except for radiation quantities, which are accumulations (from these we
-calculate daily means).  Vertically resolved quantities are made available on
-37 pressure levels.
+ERA5 \citep{era5} is a reanalysis produced by the ECMWF.  It is based on a
+numerical weather prediction model IFS version CY41R2.  The horizontal
+resolution is 0.25° in latitude and longitude, which is about 28 km in the
+North--South direction and 14 km in the East--West direction at 60°S.
+Internally, the model uses 137 vertical levels. Here, we use output at 1-hourly
+instantaeous time intervals, except for radiation quantities, which are
+accumulations (from these we calculate daily means).  Vertically resolved
+quantities are made available on 37 pressure levels.
 

### 2024-10-24 manuscript.tex
Minor edits

@@
 SO radiation biases have been relatively large and systematic compared to the
-rest of the globe since at least CMIP3 \citep{trenberth2010}, and the SO SW CRE
-bias is still positive in eight analysed CMIP6 models analysed by
-\cite{schuddeboom2021} over high-latitude SO, whereas over low-latitude SO it
-tends to be more neutral or negative in some models. Too much absorbed SW
-radiation over the SO was also identified in the GSRM SCREAM
+rest of the globe since at least CMIP3 \citep{trenberth2010}, and the SO SW
+cloud radiative effect (CRE) bias is still positive in eight analysed CMIP6
+models analysed by \cite{schuddeboom2021} over high-latitude SO, whereas over
+low-latitude SO it tends to be more neutral or negative in some models. Too
+much absorbed SW radiation over the SO was also identified in the GSRM SCREAM
 \cite{caldwell2021}. Compensating biases are possible, such as the `too few too
@@
 the order of 10\% over the entire 40--60°S SO. Recently, \cite{ramadoss2024}
-analysed 48 hours of km-scale ICON limited area model NWP simulation over a
-SO region adjacent to Tasmania agaist the Clouds, Aerosols, Precipitation,
+analysed 48 hours of km-scale ICON limited area model NWP simulation over a SO
+region adjacent to Tasmania agaist the Clouds, Aerosols, Precipitation,
 Radiation, and atmospherIc Composition Over the southeRn oceaN (CAPRICORN)
 voyage cloud and precipitation observations. They found the ICON cloud optical
-thickness underestimated relative to Himawari‐8 satellite observations, but also
-large differences in cloud top phase.
+thickness underestimated relative to Himawari‐8 satellite observations, but
+also large differences in cloud top phase.
 

### 2024-10-24 manuscript.tex
Minor edits

@@
 transition from models with parametrised convection and clouds to
-storm-resolving models might not solve these biases without additional
-effort. Evaluation of SO ocean--atmosphere heat, moisture, and momentum fluxes
-against in situ observations and comparison of GSRM model simulations against
-large-eddy simulations are two potential avenues for future research that
-could elucidate the physical mechanisms behind the biases, in addition to the
-more common efforts in SO cloud microphysics and precipitation evaluation.
+storm-resolving models might not solve these biases without additional effort.
+Evaluation of ocean--atmosphere heat, moisture, and momentum fluxes against in
+situ observations over the SO and comparison of GSRM simulations against
+large-eddy simulations are two potential avenues for future research that could
+elucidate the physical mechanisms behind the biases, in addition to the more
+common efforts in SO cloud microphysics and precipitation evaluation.
 

### 2024-10-24 manuscript.tex
Minor edits

@@
 National Academic Infrastructure for Supercomputing in Sweden (allocation
-2023/22-202).  We acknowledge the RV \emph{Polarstern} datasets provided by the
-Alfred Wegener Institute and Pangaea, the AA15-16 dataset provided by the
-Australian Antarctic Division (AAD) and University of Canterbury (UC), RV
-\emph{Tangaroa} datasets provided by the National Institute of Water and
-Atmospheric Research and UC, the NBP1704 dataset provided by the National
-Science Foundation, Cooperative Institute for Research in Environmental
-Sciences, University of Colorado and UC, the HMNZSW16 dataset provided by the
-Royal New Zealand Navy and UC, the MARCUS dataset provided by the Atmospheric
-Radiation Measurement (ARM) and AAD, and the MICRE dataset provided by ARM, the
-Australian Bureau of Meteorology, and AAD. We thank the scientific staff, the
-crew, and everyone involved in collecting data on the voyages and stations,
-especially Kelly Schick, Peter Guest, John J.  Cassano, Simon Parsons, Graeme
-Plank, Sally Garrett, Jamie Halla, Sean Hartery, Mike J.  Harvey (†), Simon P.
-Alexander, and Alex Schuddeboom. We acknowledge the ICON model output provided
-by the nextGEMS project and the DKRZ, reanalysis dataset ERA5 provided by the
-Copernicus Climate Change Service and MERRA-2 provided by the Global Modeling
-and Assimilation Office.  Last but not least, we acknowledge the use of open
-source software Python, Cython \citep{behnel2011}, TensorFlow
-\citep{abadi2016}, Devuan GNU+Linux, parallel \citep{tange2011}, NumPy
-\citep{harris2020}, SciPy \citep{virtanen2020}, Matplotlib \citep{hunter2007},
-cartopy \citep{cartopy}, pyproj, Inkscape, Bash, GNU Fortran, HDF
-\citep{folk1999}, and NetCDF \citep{rew1990}.  We dedicate this study to the
-memory of Mike J.  Harvey, who very substantially contributed to obtaining the
-atmospheric observations on the RV \emph{Tangaroa} voyages used in this study.
+2023/22-202). We acknowledge the contribution of Thorsten Mauritsen to funding
+acquisition and project management.  We acknowledge the RV \emph{Polarstern}
+datasets provided by the Alfred Wegener Institute and Pangaea, the AA15-16
+dataset provided by the Australian Antarctic Division (AAD) and University of
+Canterbury (UC), RV \emph{Tangaroa} datasets provided by the National Institute
+of Water and Atmospheric Research and UC, the NBP1704 dataset provided by the
+National Science Foundation, Cooperative Institute for Research in
+Environmental Sciences, University of Colorado and UC, the HMNZSW16 dataset
+provided by the Royal New Zealand Navy and UC, the MARCUS dataset provided by
+the Atmospheric Radiation Measurement (ARM) and AAD, and the MICRE dataset
+provided by ARM, the Australian Bureau of Meteorology, and AAD. We thank the
+scientific staff, the crew, and everyone involved in collecting data on the
+voyages and stations, especially Kelly Schick, Peter Guest, John J.  Cassano,
+Simon Parsons, Graeme Plank, Sally Garrett, Jamie Halla, Sean Hartery, Mike J.
+Harvey (†), Simon P.  Alexander, and Alex Schuddeboom. We acknowledge the ICON
+model output provided by the nextGEMS project and the DKRZ, reanalysis dataset
+ERA5 provided by the Copernicus Climate Change Service and MERRA-2 provided by
+the Global Modeling and Assimilation Office.  Last but not least, we
+acknowledge the use of open source software Python, Cython \citep{behnel2011},
+TensorFlow \citep{abadi2016}, Devuan GNU+Linux, parallel \citep{tange2011},
+NumPy \citep{harris2020}, SciPy \citep{virtanen2020}, Matplotlib
+\citep{hunter2007}, cartopy \citep{cartopy}, pyproj, Inkscape, Bash, GNU
+Fortran, HDF \citep{folk1999}, and NetCDF \citep{rew1990}.  We dedicate this
+study to the memory of Mike J.  Harvey, who very substantially contributed to
+obtaining the atmospheric observations on the RV \emph{Tangaroa} voyages used
+in this study.
 

### 2024-10-24 manuscript.tex
Add Graeme Plank to the list of authors

@@
 	pdftitle={Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON, and the ERA5 and MERRA-2 reanalyses},
-	pdfauthor={Peter Kuma, Frida A.-M. Bender, Adrian J. McDonald, …}
+	pdfauthor={Peter Kuma, Frida A.-M. Bender, Adrian J. McDonald, Graeme Plank, …}
 }
@@
 \begin{center} \Large \sffamily\textbf{Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON and the ERA5 and MERRA-2 reanalyses}\\[0.4cm]
-\large Peter Kuma$^\mathsf{1,}$*, Frida A.-M. Bender$^\mathsf{1}$, Adrian J. McDonald$^\mathsf{2}$, \ldots\\[0.4cm]
+\large Peter Kuma$^\mathsf{1,}$*, Frida A.-M. Bender$^\mathsf{1}$, Adrian J. McDonald$^\mathsf{2}$, Graeme Plank$^\mathsf{2}$, \ldots\\[0.4cm]
 \small
@@
 voyages and stations, especially Kelly Schick, Peter Guest, John J.  Cassano,
-Simon Parsons, Graeme Plank, Sally Garrett, Jamie Halla, Sean Hartery, Mike J.
-Harvey (†), Simon P.  Alexander, and Alex Schuddeboom. We acknowledge the ICON
-model output provided by the nextGEMS project and the DKRZ, reanalysis dataset
-ERA5 provided by the Copernicus Climate Change Service and MERRA-2 provided by
-the Global Modeling and Assimilation Office.  Last but not least, we
-acknowledge the use of open source software Python, Cython \citep{behnel2011},
-TensorFlow \citep{abadi2016}, Devuan GNU+Linux, parallel \citep{tange2011},
-NumPy \citep{harris2020}, SciPy \citep{virtanen2020}, Matplotlib
-\citep{hunter2007}, cartopy \citep{cartopy}, pyproj, Inkscape, Bash, GNU
-Fortran, HDF \citep{folk1999}, and NetCDF \citep{rew1990}.  We dedicate this
-study to the memory of Mike J.  Harvey, who very substantially contributed to
-obtaining the atmospheric observations on the RV \emph{Tangaroa} voyages used
-in this study.
+Simon Parsons, Sally Garrett, Jamie Halla, Sean Hartery, Mike J.  Harvey (†),
+Simon P.  Alexander, and Alex Schuddeboom. We acknowledge the ICON model output
+provided by the nextGEMS project and the DKRZ, reanalysis dataset ERA5 provided
+by the Copernicus Climate Change Service and MERRA-2 provided by the Global
+Modeling and Assimilation Office.  Last but not least, we acknowledge the use
+of open source software Python, Cython \citep{behnel2011}, TensorFlow
+\citep{abadi2016}, Devuan GNU+Linux, parallel \citep{tange2011}, NumPy
+\citep{harris2020}, SciPy \citep{virtanen2020}, Matplotlib \citep{hunter2007},
+cartopy \citep{cartopy}, pyproj, Inkscape, Bash, GNU Fortran, HDF
+\citep{folk1999}, and NetCDF \citep{rew1990}.  We dedicate this study to the
+memory of Mike J.  Harvey, who very substantially contributed to obtaining the
+atmospheric observations on the RV \emph{Tangaroa} voyages used in this study.
 

### 2024-10-25 manuscript.tex
Add more authors

@@
 \begin{center} \Large \sffamily\textbf{Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON and the ERA5 and MERRA-2 reanalyses}\\[0.4cm]
-\large Peter Kuma$^\mathsf{1,}$*, Frida A.-M. Bender$^\mathsf{1}$, Adrian J. McDonald$^\mathsf{2}$, Graeme Plank$^\mathsf{2}$, \ldots\\[0.4cm]
+\large Peter Kuma$^\mathsf{1,}$*, Frida A.-M.
+Bender$^\mathsf{1}$, Adrian J.
+McDonald$^\mathsf{2}$, Graeme Plank$^\mathsf{2}$, Sean Hartery$^\mathsf{3}$, Alex J.
+Schuddeboom$^\mathsf{2}$, \ldots\\[0.4cm]
 \small
@@
 $^\mathsf{2}$School of Physical and Chemical Sciences, University of Canterbury, Christchurch, Aotearoa/New Zealand\\[0.2cm]
+$^\mathsf{3}$Department of Physics \& Atmospheric Science, Dalhousie University, Halifax, Canada\\[0.2cm]
 *Corresponding author: Peter Kuma (\href{mailto:peter.kuma@misu.su.se}{peter.kuma@misu.su.se})\\[0.4cm]

### 2024-10-30 manuscript.tex
Add more co-authors

--- 2024-10-24 manuscript.tex
@@
 	pdftitle={Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON, and the ERA5 and MERRA-2 reanalyses},
-	pdfauthor={Peter Kuma, Frida A.-M. Bender, Adrian J. McDonald, …}
+	pdfauthor={Peter Kuma, Frida A.-M. Bender, Adrian J. McDonald, Graeme Plank, Sean Hartery, Simon Parsons, Simon P. Alexander, Alex J. Schuddeboom, …}
 }
@@
 \begin{center} \Large \sffamily\textbf{Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON and the ERA5 and MERRA-2 reanalyses}\\[0.4cm]
-\large Peter Kuma$^\mathsf{1,}$*, Frida A.-M. Bender$^\mathsf{1}$, Adrian J. McDonald$^\mathsf{2}$, \ldots\\[0.4cm]
+\large Peter Kuma$^\mathsf{1,}$*, Frida A.-M.
+Bender$^\mathsf{1}$, Adrian J.
+McDonald$^\mathsf{2}$, Graeme Plank$^\mathsf{2}$, Sean Hartery$^\mathsf{3}$, Simon Parsons$^\mathsf{4}$, Simon P.
+Alexander$^\mathsf{5}$, Alex J.
+Schuddeboom$^\mathsf{2}$, \ldots\\[0.4cm]
 \small
-$^\mathsf{1}$Department of Meteorology (MISU) and the Bolin Centre for Climate Research, Stockholm University, Stockholm SE-106 91, Sweden\\
-$^\mathsf{2}$School of Physical and Chemical Sciences, University of Canterbury, Christchurch, Aotearoa/New Zealand\\[0.2cm]
+$^\mathsf{1}$Department of Meteorology (MISU) and Bolin Centre for Climate Research, Stockholm University, Stockholm SE-106 91, Sweden\\
+$^\mathsf{2}$School of Physical and Chemical Sciences, University of Canterbury, Christchurch, Aotearoa/New Zealand\\
+$^\mathsf{3}$Department of Physics \& Atmospheric Science, Dalhousie University, Halifax, Canada\\
+$^\mathsf{4}$New South Wales Department of Planning and Environment, Sydney, New South Wales, Australia\\
+$^\mathsf{5}$Australian Antarctic Division, Kingston, Tasmania, Australia; Australian Antarctic Program Partnership, Institute for Marine and Antarctic Studies, University of Tasmania, Hobart, Tasmania, Australia\\[0.2cm]
 *Corresponding author: Peter Kuma (\href{mailto:peter.kuma@misu.su.se}{peter.kuma@misu.su.se})\\[0.4cm]
@@
 voyages and stations, especially Kelly Schick, Peter Guest, John J.  Cassano,
-Simon Parsons, Graeme Plank, Sally Garrett, Jamie Halla, Sean Hartery, Mike J.
-Harvey (†), Simon P.  Alexander, and Alex Schuddeboom. We acknowledge the ICON
+Sally Garrett, Jamie Halla, and Mike J.  Harvey (†). We acknowledge the ICON
 model output provided by the nextGEMS project and the DKRZ, reanalysis dataset

### 2024-10-31 manuscript.tex
Update on Overleaf.

@@
 Global storm-resolving models (GSRMs) are the next avenue of climate modelling.
-Among them is a 5-km Icosahedral Nonhydrostatic Weather and Climate Model
+Among them is the 5-km Icosahedral Nonhydrostatic Weather and Climate Model
 (ICON). Due to the resolution, parametrisations of convection and clouds are
@@
 evaluated SO clouds in ICON and the ERA5 and MERRA-2 reanalyses.  The SO is
-dominated by low clouds, which cannot be observed properly from space due to
+dominated by low clouds, which cannot be observed accurately from space due to
 overlapping clouds, attenuation, and ground clutter.  Instead, we analysed
@@
 the cloud occurrence peak at about 500 m, potentially explained by their
-lifting condensation level being too high.  The reanalyses strongly
+lifting condensation levels being too high.  The reanalyses strongly
 underestimate near-surface clouds or fog.  MERRA-2 tends to underestimate cloud
@@
 oktas clearer, respectively. Compared to radiosondes, potential temperature is
-accurate in all, but ICON is too unstable over low-latitude SO and too humid in
+accurate in all, but ICON is too unstable over the low-latitude SO and too humid in
 the boundary layer. MERRA-2 is too humid at all heights. SO cloud biases are a
-substantial issue in the GSRM, but it is an improvement over the
+substantial issue in the GSRM, but are an improvement over the
 lower-resolution reanalyses. Explicitly resolved convection and cloud processes
@@
 computational availability and acceleration from general-purpose computing on
-graphics processing units (GPGPUs) is progressing to enable km-scale (also
+graphics processing units (GPUs) is progressing to enable km-scale (also
 called k-scale) Earth system models (ESMs) and coupled atmosphere--ocean
@@
 operationally in the forthcoming years. Therefore, it represents a natural
-advancement in climate modeling.  Global strom-resolving models (GSRMs) are
+advance in climate modelling.  Global storm-resolving models (GSRMs) are
 emerging as a new front in the development of high-resolution global climate
@@
 \citep{stevens2019,dyamond}, which is an intercomparison of nine global GSRMs
-on two 40-day time periods in summer (1 August -- 10 September 2016) and winter
+over two 40-day time periods in summer (1 August -- 10 September 2016) and winter
 (20 January -- 1 March 2020). A new one-year GSRM intercomparison is currently
@@
 Multiple cloud properties have an effect on the shortwave (SW) and longwave
-(LW) radiation. On the first order, it is the total cloud fraction, cloud
-phase, and the liquid and ice water path. These are influenced by the
-atmopheric thermodynamics, convection and circulation, and indirect and direct
-effects of aerosols. On smaller orders, it is the cloud droplet size
+(LW) radiation. To first order, the total cloud fraction, cloud
+phase, and the liquid and ice water path are the most important cloud properties influencing SW and LW radiation. These properties are  in turn influenced by the
+atmospheric thermodynamics, convection and circulation, and indirect and direct
+effects of aerosols. Second order effects on SW and LW radiation are associated with the cloud droplet size
 distribution, ice crystal habit, cloud lifetime, and direct radiative
@@
 Intercomparison Project [CMIP6; \cite{eyring2016}], the cloud feedback has
-increased relative to CMIP5 \citep{zelinka2020}, also being one of the main
+increased relative to CMIP5 \citep{zelinka2020}, this being one of the main
 reasons for the higher climate sensitivity of CMIP6 models.
@@
 The Southern Ocean (SO) is known to be a problematic region for climate model
-biases due to reasons such as a lack of surface and in situ observations and
+biases due to a lack of surface and in situ observations and
 being a lower priority region for numerical weather prediction (NWP) and
-climate model development because it is far away from populated areas of
+climate model development because of its distance from populated areas of
 interest.  Nevertheless, radiation biases and changes over an area of its size
@@
 cloud radiative effect (CRE) bias is still positive in eight analysed CMIP6
-models analysed by \cite{schuddeboom2021} over high-latitude SO, whereas over
-low-latitude SO it tends to be more neutral or negative in some models. Too
+models analysed by \cite{schuddeboom2021} over the high-latitude SO, whereas over
+the low-latitude SO it tends to be more neutral or negative in some models. Too
 much absorbed SW radiation over the SO was also identified in the GSRM SCREAM
@@
 \cite{nam2012}, \cite{klein2013}, and \cite{bender2017} in other regions and
-models. That is, a model maintains a resonable SW radiation balance by
-reflecting too much SW radiation by cloudy sky but has too little cloudy sky
-area overall. A study by \cite{konsta2022} showed that this type bias is still
+models. That is, a model maintains a reasonable SW radiation balance by
+reflecting too much SW radiation from clouds, but has too little cloud
+area overall. A study by \cite{konsta2022} showed that this type of bias is still
 present in six analysed CMIP6 models in tropical marine clouds, using the
@@
 that over the SO, the DYAMOND GSRM ICON underestimates low-level cloud fraction
-on the order of 30\% [relative to the Moderate Resolution Imaging
-Spectroradiometer (MODIS)] and overestimates downwelling TOA SW radiation on
-the order of 10 Wm$^\mathrm{-2}$ in  [relative to the Clouds and the Earth’s
-Radiant Energy System (CERES)] in the highest model resolution run (2.5 km).
+on the order of 30\% [relative to Moderate Resolution Imaging
+Spectroradiometer (MODIS) data] and overestimates downwelling TOA SW radiation on
+by approximately 10 Wm$^\mathrm{-2}$ in  [relative to the Clouds and the Earth’s
+Radiant Energy System (CERES) data] in the highest model resolution run (2.5 km).
 \cite{zhao2022} reported a similar SW radiation bias in five analysed CMIP6
@@
 the order of 10\% over the entire 40--60°S SO. Recently, \cite{ramadoss2024}
-analysed 48 hours of km-scale ICON limited area model NWP simulation over a SO
-region adjacent to Tasmania agaist the Clouds, Aerosols, Precipitation,
+analysed 48 hours of km-scale ICON limited area model NWP simulations over a SO
+region adjacent to Tasmania against the Clouds, Aerosols, Precipitation,
 Radiation, and atmospherIc Composition Over the southeRn oceaN (CAPRICORN)
-voyage cloud and precipitation observations. They found the ICON cloud optical
-thickness underestimated relative to Himawari‐8 satellite observations, but
-also large differences in cloud top phase.
+voyage cloud and precipitation observations \cite{mcfarquhar2021}. They found the ICON cloud optical
+thickness was underestimated relative to Himawari‐8 satellite observations, but
+also identified large differences in cloud top phase.
 
@@
 Interactions of both are also possible, due to, for example SST affecting
-clouds and clouds affecting the surface radiation.  \cite{zhang2023} have shown
+clouds and clouds affecting the surface radiation. \cite{zhang2023} has shown
 that SST biases have improved in CMIP6 compared to CMIP5 [relative to the

### 2024-10-31 manuscript.tex
Add co-authors

--- 2024-10-30 manuscript.tex
@@
 	pdftitle={Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON, and the ERA5 and MERRA-2 reanalyses},
-	pdfauthor={Peter Kuma, Frida A.-M. Bender, Adrian J. McDonald, Graeme Plank, Sean Hartery, Simon Parsons, Simon P. Alexander, Alex J. Schuddeboom, …}
+	pdfauthor={Peter Kuma, Frida A.-M. Bender, Adrian J. McDonald, Graeme Plank, Sean Hartery, Simon Parsons, Simon P. Alexander, Greg M. McFarquhar, John J. Cassano, Alex J. Schuddeboom, …}
 }
@@
 \begin{center} \Large \sffamily\textbf{Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON and the ERA5 and MERRA-2 reanalyses}\\[0.4cm]
-\large Peter Kuma$^\mathsf{1,}$*, Frida A.-M.
-Bender$^\mathsf{1}$, Adrian J.
-McDonald$^\mathsf{2}$, Graeme Plank$^\mathsf{2}$, Sean Hartery$^\mathsf{3}$, Simon Parsons$^\mathsf{4}$, Simon P.
-Alexander$^\mathsf{5}$, Alex J.
-Schuddeboom$^\mathsf{2}$, \ldots\\[0.4cm]
+\large Peter Kuma$^\mathsf{1,2}$*, Frida A.-M.
+Bender$^\mathsf{1,2}$, Adrian J.
+McDonald$^\mathsf{3}$, Graeme Plank$^\mathsf{3}$, Sean Hartery$^\mathsf{4}$, Simon Parsons$^\mathsf{5}$, Simon P.
+Alexander$^\mathsf{6,7}$, Greg M.
+McFarquhar$^\mathsf{8}$, John J.
+Cassano$^\mathsf{9,10,11}$, Alex J.
+Schuddeboom$^\mathsf{3}$, \ldots\\[0.4cm]
 \small
-$^\mathsf{1}$Department of Meteorology (MISU) and Bolin Centre for Climate Research, Stockholm University, Stockholm SE-106 91, Sweden\\
-$^\mathsf{2}$School of Physical and Chemical Sciences, University of Canterbury, Christchurch, Aotearoa/New Zealand\\
-$^\mathsf{3}$Department of Physics \& Atmospheric Science, Dalhousie University, Halifax, Canada\\
-$^\mathsf{4}$New South Wales Department of Planning and Environment, Sydney, New South Wales, Australia\\
-$^\mathsf{5}$Australian Antarctic Division, Kingston, Tasmania, Australia; Australian Antarctic Program Partnership, Institute for Marine and Antarctic Studies, University of Tasmania, Hobart, Tasmania, Australia\\[0.2cm]
+$^\mathsf{1}$Department of Meteorology (MISU), Stockholm University, Stockholm,, Sweden\\
+$^\mathsf{2}$Bolin Centre for Climate Research, Stockholm University, Stockholm, Sweden\\
+$^\mathsf{3}$School of Physical and Chemical Sciences, University of Canterbury, Christchurch, Aotearoa/New Zealand\\
+$^\mathsf{4}$Department of Physics \& Atmospheric Science, Dalhousie University, Halifax, Canada\\
+$^\mathsf{5}$New South Wales Department of Planning and Environment, Sydney, New South Wales, Australia\\
+$^\mathsf{6}$Australian Antarctic Division, Kingston, Tasmania, Australia\\
+$^\mathsf{7}$Australian Antarctic Program Partnership, Institute for Marine and Antarctic Studies, University of Tasmania, Hobart, Tasmania, Australia\\
+$^\mathsf{8}$Cooperative Institute for Mesoscale Meteorological Studies, and School of Meteorology, University of Oklahoma, Norman, Oklahoma, USA\\
+$^\mathsf{9}$Department of Atmospheric and Oceanic Sciences, University of Colorado Boulder, Boulder, Colorado, USA\\
+$^\mathsf{10}$National Snow and Ice Data Center, University of Colorado Boulder, Boulder, Colorado, USA\\
+$^\mathsf{11}$Department of Atmospheric and Oceanic Sciences, University of Colorado Boulder, Boulder, Colorado, USA\\[0.2cm]
 *Corresponding author: Peter Kuma (\href{mailto:peter.kuma@misu.su.se}{peter.kuma@misu.su.se})\\[0.4cm]
@@
 conceptualization, funding acquisition, project administration, supervision,
-and writing – review \& editing; AM: data curation, investigation, resources,
-writing – review \& editing. [TODO]
+and writing – review \& editing; AM, GP, SH, SP, SA, GM, JC, and AS: data
+curation, investigation, resources, writing – review \& editing; [TODO]
 

### 2024-11-01 manuscript.tex
Update acknowledgments

@@
 scientific staff, the crew, and everyone involved in collecting data on the
-voyages and stations, especially Kelly Schick, Peter Guest, John J.  Cassano,
-Sally Garrett, Jamie Halla, and Mike J.  Harvey (†). We acknowledge the ICON
-model output provided by the nextGEMS project and the DKRZ, reanalysis dataset
-ERA5 provided by the Copernicus Climate Change Service and MERRA-2 provided by
-the Global Modeling and Assimilation Office.  Last but not least, we
-acknowledge the use of open source software Python, Cython \citep{behnel2011},
-TensorFlow \citep{abadi2016}, Devuan GNU+Linux, parallel \citep{tange2011},
-NumPy \citep{harris2020}, SciPy \citep{virtanen2020}, Matplotlib
-\citep{hunter2007}, cartopy \citep{cartopy}, pyproj, Inkscape, Bash, GNU
-Fortran, HDF \citep{folk1999}, and NetCDF \citep{rew1990}.  We dedicate this
-study to the memory of Mike J.  Harvey, who very substantially contributed to
-obtaining the atmospheric observations on the RV \emph{Tangaroa} voyages used
-in this study.
+voyages and stations, especially Gert König-Langlo, Holger Schmithüsen, Roger
+Marchand, Peter Guest, Kelly Schick, Sally Garrett, Jamie Halla, and Mike J.
+Harvey (†). We acknowledge the ICON model output provided by the nextGEMS
+project and the DKRZ, reanalysis dataset ERA5 provided by the Copernicus
+Climate Change Service and MERRA-2 provided by the Global Modeling and
+Assimilation Office.  Last but not least, we acknowledge the use of open source
+software Python, Cython \citep{behnel2011}, TensorFlow \citep{abadi2016},
+Devuan GNU+Linux, parallel \citep{tange2011}, NumPy \citep{harris2020}, SciPy
+\citep{virtanen2020}, Matplotlib \citep{hunter2007}, cartopy \citep{cartopy},
+pyproj, Inkscape, Bash, GNU Fortran, HDF \citep{folk1999}, and NetCDF
+\citep{rew1990}.  We dedicate this study to the memory of Mike J.  Harvey, who
+very substantially contributed to obtaining the atmospheric observations on the
+RV \emph{Tangaroa} voyages used in this study.
 

### 2024-11-01 manuscript.tex
Add PIPERS reference

@@
 MICRE    & \cite{marchand2015,marchand2020,zhang2016,mcfarquhar2021} \\
+NBP1704  & \cite{ackley2020} \\
 PS77/2   & \cite{kniglanglo2011a,kniglanglo2011b,kniglanglo2011c,kniglanglo2014a,fahrbach2011} \\

### 2024-11-02 manuscript.tex
Update on Overleaf.

@@
 overlapping and thick clouds and ground clutter, respectively.  Specifically,
-the radar on CloudSat and lidar on CALIPSO (neither of them operational any
-more) are affected by the abovementioned issues, resulting in a strong
+the radar on CloudSat and lidar on CALIPSO (neither of which are now operational) are affected by the abovementioned issues, resulting in a strong
 underestimation of cloud occurrence below 2 km relative to ground-based lidar
@@
 
-Together, we analysed data from 31 voyages of RV \emph{Polarstern}, resupply
+Together, we analysed data from 31 voyages of RV \emph{Polarstern}, the resupply
 vessel (RSV) \emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B.
@@
 \ref{sec:cl51} and \ref{sec:chm15k}). A ceilometer is a low-power near-infrared
-vertically pointing lidar with the purpose of measuring the cloud base, but it
-also measures the full vertical structure of clouds as long as the laser signal
+vertically pointing lidar principally designed to  measure cloud base, but they 
+also measure the full vertical structure of clouds as long as the laser signal
 is not attenuated by thick clouds, which can be used to infer additional
@@
 operating at a near-infrared wavelength of 910 nm and 905 nm, respectively.
-CL51 can also be configured to emulate the Vaisala CL31. The maximum range is
+The CL51 can also be configured to emulate the Vaisala CL31. The maximum range is
 15.4 km (CL51), 7.7 km (CL31 emulation mode with 5 m vertical resolution), and
 7.5 km (CT25K). The vertical resolution is 10 m (5 m configurable) in CL51 and
-30 m in CT25K. The sampling (temporal) resolution is configurable, and in our
-datasets it is about 6 s for CL51 on AA15‐16, 16 s for CT25K on MARCUS and
+30 m in CT25K observations. The sampling (temporal) resolution is configurable, and in our
+datasets is approximately 6 s for CL51 on AA15‐16, 16 s for CT25K on MARCUS and
 MICRE, 36 s for CL51 on RV \emph{Polarstern}, and about 2.37 s for CL51 with
@@
 equivalent AVBC simulated with the ALCF from ERA5 data during the same time
-period. Shown is also the cloud mask determined by the ALCF.
+period. The red line identifies the cloud mask determined by the ALCF.
 }
@@
 NetCDF files containing uncalibrated backscatter produced by the instrument
-were processed with the ALCF (Section \ref{sec:alcf}) to produce AVBC, cloud
+were processed with the ALCF (Section \ref{sec:alcf}) to again produce AVBC, cloud
 mask, cloud occurrence by height, and the total cloud fraction. The CHM 15k was
@@
 calculations to derive equivalent lidar AVBC in an atmospheric model, which can
-then be compared with observed AVBC. For this purpose, it takes atmospheric
-fields of cloud fraction, liquid and ice mass mixing ratio, temperature, and
-pressure fields as an input and is run offline (on the model output rather than
+then be compared with observed AVBC. For this purpose, it takes the cloud fraction, liquid and ice mass mixing ratio, temperature, and
+pressure model fields as an input and is run offline (on the model output rather than
 inside the model code). The lidar simulator in the ALCF is based on the

### 2024-11-05 manuscript.tex
Address comments from Graeme

@@
 Among them is the 5-km Icosahedral Nonhydrostatic Weather and Climate Model
-(ICON). Due to the resolution, parametrisations of convection and clouds are
-avoided. Standard-resolution models have substantial cloud biases over the
+(ICON). Due to the high resolution, parametrisations of convection and clouds
+are avoided. Standard-resolution models have substantial cloud biases over the
 Southern Ocean (SO), affecting radiation and sea surface temperature.  We
@@
 oktas clearer, respectively. Compared to radiosondes, potential temperature is
-accurate in all, but ICON is too unstable over the low-latitude SO and too humid in
-the boundary layer. MERRA-2 is too humid at all heights. SO cloud biases are a
-substantial issue in the GSRM, but are an improvement over the
+accurate in all, but ICON is too unstable over the low-latitude SO and too
+humid in the boundary layer. MERRA-2 is too humid at all heights. SO cloud
+biases are a substantial issue in the GSRM, but are an improvement over the
 lower-resolution reanalyses. Explicitly resolved convection and cloud processes
@@
 
-Multiple cloud properties have an effect on the shortwave (SW) and longwave
-(LW) radiation. To first order, the total cloud fraction, cloud
-phase, and the liquid and ice water path are the most important cloud properties influencing SW and LW radiation. These properties are  in turn influenced by the
+Multiple cloud properties have an effect on shortwave (SW) and longwave (LW)
+radiation. To first order, the total cloud fraction, cloud phase, and the
+liquid and ice water path are the most important cloud properties influencing
+SW and LW radiation. These properties are  in turn influenced by the
 atmospheric thermodynamics, convection and circulation, and indirect and direct
-effects of aerosols. Second order effects on SW and LW radiation are associated with the cloud droplet size
-distribution, ice crystal habit, cloud lifetime, and direct radiative
-interaction with aerosols.  In the 6$^\mathrm{th}$ phase of the Coupled Model
-Intercomparison Project [CMIP6; \cite{eyring2016}], the cloud feedback has
-increased relative to CMIP5 \citep{zelinka2020}, this being one of the main
-reasons for the higher climate sensitivity of CMIP6 models.
+effects of aerosols. Second order effects on SW and LW radiation are associated
+with the cloud droplet size distribution, ice crystal habit, cloud lifetime,
+and direct radiative interaction with aerosols.  In the 6$^\mathrm{th}$ phase
+of the Coupled Model Intercomparison Project [CMIP6; \cite{eyring2016}], the
+cloud feedback has increased relative to CMIP5 \citep{zelinka2020}, this being
+one of the main reasons for the higher climate sensitivity of CMIP6 models.
 
@@
 little longwave cooling of the surface, or in the ocean circulation.
-Interactions of both are also possible, due to, for example SST affecting
-clouds and clouds affecting the surface radiation. \cite{zhang2023} has shown
-that SST biases have improved in CMIP6 compared to CMIP5 [relative to the
-European Centre for Medium-Range Weather Forecasts (ECMWF) Reanalysis 5; ERA5],
-with SST overall increasing in the later CMIP phase. However, over the SO this
-resulted in an even higher positive bias, especially in the Atlantic Ocean (AO)
-sector of the SO, increasing by up to 1°C.  \cite{luo2023} identified that the
-SO SST bias in an ensemble of 18 CMIP6 models originates not from the surface
-heat and radiation fluxes (using reanalyses as a reference), but from a warm
-bias in the Northern Atlantic Deep Water.
+Interactions of both are also possible, for example SST affecting clouds and
+clouds affecting the surface radiation. \cite{zhang2023} has shown that SST
+biases have improved in CMIP6 compared to CMIP5 [relative to the European
+Centre for Medium-Range Weather Forecasts (ECMWF) Reanalysis 5; ERA5], with SST
+overall increasing in the later CMIP phase. However, over the SO this resulted
+in an even higher positive bias, especially in the Atlantic Ocean (AO) sector
+of the SO, increasing by up to 1°C.  \cite{luo2023} identified that the SO SST
+bias in an ensemble of 18 CMIP6 models originates not from the surface heat and
+radiation fluxes (using reanalyses as a reference), but from a warm bias in the
+Northern Atlantic Deep Water.
 
@@
 the highest instantaneous temporal resolution data available. Shown is also the
-chosen dividing threshold of 12 K for the relatively stable and unstable
+chosen dividing threshold of 12 K for relatively stable and unstable
 conditions.
@@
 all voyage tracks and stations (Fig.  \ref{fig:lts}), we determined a dividing
-threshold of 12 K for the relatively unstable (< 12 K) and the relatively
-stable (>= 12 K) conditions.
+threshold of 12 K for relatively unstable (< 12 K) and relatively stable (>= 12
+K) conditions.
 
@@
 Geographical distribution of \textbf{(a, b)} cyclonic days and \textbf{(b, d)}
-the relatively stable (LTS > 12 K) time steps in \textbf{(a, c)} ERA5 in years
+relatively stable (LTS > 12 K) time steps in \textbf{(a, c)} ERA5 in years
 2010--2013 (inclusive) and \textbf{(b, d)} ICON in model years 2021--2023 (free
@@
 relatively stable and unstable conditions as determined by the LTS (Section
-\ref{sec:cyclone-stability}).  The relatively unstable conditions are prevalent
+\ref{sec:cyclone-stability}). Relatively unstable conditions are prevalent
 in the middle SO (50--65°S), which might be explained by the relatively cold
-near-surface air overlying the relatively warm sea surface. The relatively
+near-surface air overlying the relatively warm sea surface. Relatively
 stable conditions are prevalent elsewhere over the SO. The distribution is also
@@
 supported by the observations. ICON and ERA5 overestimate cloud occurrence at
-the peak (between 0--1 km). Above 1 km, ICON and MERRA-2 understimate cloud
-occurrence, but ERA5 is very accurate. The too high peak in models is partly
+the peak (between 0--1 km). Above 1 km, ICON and MERRA-2 underestimate cloud
+occurrence, but ERA5 is very accurate. The exaggerated peak in models is partly
 supported by the lifting condensation level (LCL) distribution, which peaks
@@
 low-latitude SO zone (near-surface cloud occurrence is still strongly
-understimated).
+underestimated).
 
@@
 
-When subsetted by the relatively stable and unstable conditions (Fig.
+When subsetted by relatively stable and unstable conditions (Fig.
 \ref{fig:cloud-occurrence}f, g), as defined in Section
-\ref{sec:cyclone-stability}, we see that in the relatively stable
+\ref{sec:cyclone-stability}, we see that in relatively stable
 situations cloud occurrence peaks strongly at the surface in observations,
-compared to the relatively unstable situations, where the peak is more obtuse
-and spread across the altitudes of 0--1 km.  In the relatively stable
+compared to relatively unstable situations, where the peak is more obtuse
+and spread across the altitudes of 0--1 km.  In relatively stable
 situations, the models are doing a fairly good job, but overestimate cloud
 occurrence at the peak below 1 km; above 1 km, they show similar biases as in
-the general case.  In the relatively unstable situations, the bias in ICON is
+the general case.  In relatively unstable situations, the bias in ICON is
 very pronounced, with a much stronger peak at about 500 m, ERA5 is
@@
 occurrence below 1 km and underestimating above, underestimating the total
-cloud fraction, and showing greatest biases in the relatively unstable and
+cloud fraction, and showing greatest biases in relatively unstable and
 non-cyclonic conditions. It also shows a peak of cloud occurrence at higher
@@
 below, but underestimating near-surface cloud occurrence (0--500 m). The total
-cloud fraction is strongly understimated in all situations. It has a tendency
-towards understimation in the low-latitude SO zone and the relatively unstable
+cloud fraction is strongly underestimated in all situations. It has a tendency
+towards underestimation in the low-latitude SO zone and relatively unstable
 situations; conversely, overestimating in the high-latitude SO zone and the
@@
 ICON or the reanalyses.  While ICON is the closest, it tends to be 1 okta
-clearer the observations, peaking at 6 oktas, and highly understimating days
+clearer the observations, peaking at 6 oktas, and highly underestimating days
 with 8 oktas.  Overall, the reanalyses show results similar to each other,
-underestimating cloud cover by about 2 oktas and strongly understimating days
+underestimating cloud cover by about 2 oktas and strongly underestimating days
 with 7 and 8 oktas. Of the two reanalyses, MERRA-2 shows slightly higher cloud
@@
 reanalyses represent at least this characteristic of the distribution well for
-0--3 oktas, but otherwise show bises similar to the general case. One of the
+0--3 oktas, but otherwise show biases similar to the general case. One of the
 greatest biases is present in ERA5 in the relatively unstable subset, in which
@@
 Overall, the mean $\theta_v$ is relatively well represented in ICON and
-MERRA-2, being only slightly colder in the mid-to-high troposophere (less
+MERRA-2, being only slightly colder in the mid-to-high troposphere (less
 stable) in ICON than in observations (Fig. \ref{fig:potential-temperature}a).
@@
 Pacific Ocean sectors of the SO. Even though climatological features of the SO
-are typically relatively uniform zonally, variantions exist, such as those
+are typically relatively uniform zonally, variations exist, such as those
 related to the Antarctic Peninsula and the southern tip of South America. The
@@
 flux in the model and reanalyses, which might not exactly correspond to
-detection by the ANN applied to obseravations. Also, we did not make an attempt
+detection by the ANN applied to observations. Also, we did not make an attempt
 to remove profiles with precipitation not reaching the surface. The above
@@
 stable in terms of LTS. The latter is also manifested in the radiosonde profile
-comparison, which shows that the virtual potential temperature profiles in ICON
+comparison, showing that the virtual potential temperature profiles in ICON
 are more stable than in the observations over low-latitude SO.
@@
 overestimates the peak of cloud occurrence at about 500 m, which might be
-explained by the radiosonde comparison, which shows that it is too moist at
+explained by the radiosonde comparison, showing that it is too moist at
 around this height.  Similar to our results, \cite{cesana2022} showed that
@@
 
-Compared to the lidar observations, the daily cloud cover tends to be about 1
-okta lower in ICON and 2 oktas lower in the reanalyses.  Unstable conditions
-are associated with some of the greatest biases, especially in ERA5.  The
-models also underestimate the cloud cover very strongly in cyclonic conditions,
-which are very cloudy in the observations (8 oktas), but much less so in the
-models.
+Compared to lidar observations, the daily cloud cover tends to be about 1 okta
+lower in ICON and 2 oktas lower in the reanalyses.  Unstable conditions are
+associated with some of the greatest biases, especially in ERA5.  The models
+also underestimate the cloud cover very strongly in cyclonic conditions, which
+are very cloudy in the observations (8 oktas), but much less so in the models.
 

### 2024-11-05 manuscript.tex
Fix spelling

@@
 Among them is the 5-km Icosahedral Nonhydrostatic Weather and Climate Model
-(ICON). Due to the high resolution, parametrisations of convection and clouds
+(ICON). Due to the high resolution, parameterizations of convection and clouds
 are avoided. Standard-resolution models have substantial cloud biases over the
@@
 \citep{mauritsen2022}. This is of course limited by the available computational
-power and a tradeoff with increasing parametrisation complexity. Current
+power and a trade-off with increasing parameterization complexity. Current
 computational availability and acceleration from general-purpose computing on
@@
 The data sources contained ceilometer observations captured by the Vaisala CL51
-operating at a wavelenght of 910 nm, the Vaisala CT25K operating at 905 nm, and
+operating at a wavelength of 910 nm, the Vaisala CT25K operating at 905 nm, and
 the Lufft CHM 15k operating at 1064 nm, described in detail below (Sections
@@
 vertical levels and 3-hourly instantaneous temporal resolution.  Unlike current
-general circulation models (GCMs), the strom-resolving version of ICON does not
+general circulation models (GCMs), the storm-resolving version of ICON does not
 use convective and cloud parameterization but relies on explicit simulation of
@@
 Internally, the model uses 137 vertical levels. Here, we use output at 1-hourly
-instantaeous time intervals, except for radiation quantities, which are
+instantaneous time intervals, except for radiation quantities, which are
 accumulations (from these we calculate daily means).  Vertically resolved
@@
 the presence of sea ice might have substantial stabilising effect
-\citep{knight2024}. The ERA5 renalysis is also substantially more stable than
+\citep{knight2024}. The ERA5 reanalysis is also substantially more stable than
 ICON across the whole region.
@@
 voyages were mostly undertaken in the Austral summer months and only rarely in
-the winter months, due to the poor accesibility of this region during winter.
+the winter months, due to the poor accessibility of this region during winter.
 Therefore, our results are mostly representative of summer and to a lesser
@@
 analysis provides a unique evaluation perspective different from satellite
-observations -- one that is more suitable for evaluating bounary layer clouds,
+observations -- one that is more suitable for evaluating boundary layer clouds,
 which are predominant in this region. Furthermore, we subsetted our dataset by

### 2024-11-07 manuscript.tex
Improve acks and code availability

@@
 Harvey (†). We acknowledge the ICON model output provided by the nextGEMS
-project and the DKRZ, reanalysis dataset ERA5 provided by the Copernicus
-Climate Change Service and MERRA-2 provided by the Global Modeling and
-Assimilation Office.  Last but not least, we acknowledge the use of open source
-software Python, Cython \citep{behnel2011}, TensorFlow \citep{abadi2016},
-Devuan GNU+Linux, parallel \citep{tange2011}, NumPy \citep{harris2020}, SciPy
+project, Deutscher Wetterdienst, Max-Planck-Institute for Meteorology, DKRZ,
+Karlsruhe Institute of Technology, and Center for Climate Systems Modeling;
+reanalysis dataset ERA5 provided by the Copernicus Climate Change Service;
+MERRA-2 provided by the Global Modeling and Assimilation Office; CERES datasets
+provided by the NASA Langley Atmospheric Science Data Center Distributed Active
+Archive Center; and the Natural Earth dataset provided by naturalearthdata.com.
+Last but not least, we acknowledge the use of open source software Python,
+Cython \citep{behnel2011}, TensorFlow \citep{abadi2016}, Devuan GNU+Linux,
+parallel \citep{tange2011}, NumPy \citep{harris2020}, SciPy
 \citep{virtanen2020}, Matplotlib \citep{hunter2007}, cartopy \citep{cartopy},
@@
 \url{https://github.com/peterkuma/icon-so-2024}, respectively. CyTRACK is
-available at \url{https://github.com/apalarcon/CyTRACK}.
+available at \url{https://github.com/apalarcon/CyTRACK}. The ICON model is
+available at \url{https://gitlab.dkrz.de/icon/icon-mpim}.
 

### 2024-11-08 manuscript.tex
Add funding acks

@@
 
-PK and FB received funding from the European Union’s Horizon 2020 research and
-innovation program under a grant agreement no. 101003470. Supercomputing
-resources were provided by the DKRZ (project 1125 ICON-development) and the
-National Academic Infrastructure for Supercomputing in Sweden (allocation
-2023/22-202). We acknowledge the contribution of Thorsten Mauritsen to funding
+PK and FB, and the nextGEMS project received funding from the European Union’s
+Horizon 2020 research and innovation program under a grant agreement no.
+101003470. FB received funding from the Wenner-Gren foundation and the Swedish
+e-Science Research Centre. Supercomputing resources were provided by the DKRZ
+(project 1125 ICON-development) and the National Academic Infrastructure for
+Supercomputing in Sweden (allocation 2023/22-202). The data collection by the
+University of Canterbury was funded by the Deep South National Science
+Challenge Clouds and Aerosols project.  Data collection on the RSV \emph{Aurora
+Australis} was funded by the Australian Antarctic Science project (grant no.
+4292).  We acknowledge the contribution of Thorsten Mauritsen to funding
 acquisition and project management.  We acknowledge the RV \emph{Polarstern}
@@
 voyages and stations, especially Gert König-Langlo, Holger Schmithüsen, Roger
-Marchand, Peter Guest, Kelly Schick, Sally Garrett, Jamie Halla, and Mike J.
-Harvey (†). We acknowledge the ICON model output provided by the nextGEMS
-project, Deutscher Wetterdienst, Max-Planck-Institute for Meteorology, DKRZ,
-Karlsruhe Institute of Technology, and Center for Climate Systems Modeling;
-reanalysis dataset ERA5 provided by the Copernicus Climate Change Service;
-MERRA-2 provided by the Global Modeling and Assimilation Office; CERES datasets
-provided by the NASA Langley Atmospheric Science Data Center Distributed Active
-Archive Center; and the Natural Earth dataset provided by naturalearthdata.com.
-Last but not least, we acknowledge the use of open source software Python,
-Cython \citep{behnel2011}, TensorFlow \citep{abadi2016}, Devuan GNU+Linux,
-parallel \citep{tange2011}, NumPy \citep{harris2020}, SciPy
-\citep{virtanen2020}, Matplotlib \citep{hunter2007}, cartopy \citep{cartopy},
-pyproj, Inkscape, Bash, GNU Fortran, HDF \citep{folk1999}, and NetCDF
-\citep{rew1990}.  We dedicate this study to the memory of Mike J.  Harvey, who
-very substantially contributed to obtaining the atmospheric observations on the
-RV \emph{Tangaroa} voyages used in this study.
+Marchand, Peter Guest, Kelly Schick, Sally Garrett, Jamie Halla, Mike J.
+Harvey (†). We thank Loretta Preis for providing additional RV
+\emph{Polarstern} data.  We acknowledge the ICON model output provided by the
+nextGEMS project, Deutscher Wetterdienst, Max-Planck-Institute for Meteorology,
+DKRZ, Karlsruhe Institute of Technology, and Center for Climate Systems
+Modeling; reanalysis dataset ERA5 provided by the Copernicus Climate Change
+Service; MERRA-2 provided by the Global Modeling and Assimilation Office; CERES
+datasets provided by the NASA Langley Atmospheric Science Data Center
+Distributed Active Archive Center; and the Natural Earth dataset provided by
+naturalearthdata.com.  Last but not least, we acknowledge the use of open
+source software Python, Cython \citep{behnel2011}, TensorFlow
+\citep{abadi2016}, Devuan GNU+Linux, parallel \citep{tange2011}, NumPy
+\citep{harris2020}, SciPy \citep{virtanen2020}, Matplotlib \citep{hunter2007},
+cartopy \citep{cartopy}, pyproj, Inkscape, Bash, GNU Fortran, HDF
+\citep{folk1999}, and NetCDF \citep{rew1990}.  We dedicate this study to the
+memory of Mike J.  Harvey, who very substantially contributed to obtaining the
+atmospheric observations on the RV \emph{Tangaroa} voyages used in this study.
 

### 2024-11-11 manuscript.tex
Update co-authors list

@@
 	pdftitle={Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON, and the ERA5 and MERRA-2 reanalyses},
-	pdfauthor={Peter Kuma, Frida A.-M. Bender, Adrian J. McDonald, Graeme Plank, Sean Hartery, Simon Parsons, Simon P. Alexander, Greg M. McFarquhar, John J. Cassano, Alex J. Schuddeboom, …}
+	pdfauthor={Peter Kuma, Frida A.-M.
+Bender, Adrian J.
+McDonald, Simon P.
+Alexander, Greg M.
+McFarquhar, John J.
+Cassano, Graeme Plank, Sean Hartery, Simon Parsons, Sally Garrett, and Alex J.
+Schuddeboom}
 }
@@
 \begin{center} \Large \sffamily\textbf{Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON and the ERA5 and MERRA-2 reanalyses}\\[0.4cm]
-\large Peter Kuma$^\mathsf{1,2}$*, Frida A.-M.
+\normalsize Peter Kuma$^\mathsf{1,2,\star}$, Frida A.-M.
 Bender$^\mathsf{1,2}$, Adrian J.
-McDonald$^\mathsf{3}$, Graeme Plank$^\mathsf{3}$, Sean Hartery$^\mathsf{4}$, Simon Parsons$^\mathsf{5}$, Simon P.
-Alexander$^\mathsf{6,7}$, Greg M.
-McFarquhar$^\mathsf{8}$, John J.
-Cassano$^\mathsf{9,10,11}$, Alex J.
-Schuddeboom$^\mathsf{3}$, \ldots\\[0.4cm]
-\small
+McDonald$^\mathsf{3}$, Simon P.
+Alexander$^\mathsf{4,5}$, Greg M.
+McFarquhar$^\mathsf{6}$, John J.
+Cassano$^\mathsf{7,8,9}$, Graeme Plank$^\mathsf{3}$, Sean Hartery$^\mathsf{10}$, Simon Parsons$^\mathsf{11}$, Sally Garrett$^\mathsf{12}$, and Alex J.
+Schuddeboom$^\mathsf{3}$\\[0.4cm]
+\footnotesize
 $^\mathsf{1}$Department of Meteorology (MISU), Stockholm University, Stockholm,, Sweden\\
@@
 $^\mathsf{3}$School of Physical and Chemical Sciences, University of Canterbury, Christchurch, Aotearoa/New Zealand\\
-$^\mathsf{4}$Department of Physics \& Atmospheric Science, Dalhousie University, Halifax, Canada\\
-$^\mathsf{5}$New South Wales Department of Planning and Environment, Sydney, New South Wales, Australia\\
-$^\mathsf{6}$Australian Antarctic Division, Kingston, Tasmania, Australia\\
-$^\mathsf{7}$Australian Antarctic Program Partnership, Institute for Marine and Antarctic Studies, University of Tasmania, Hobart, Tasmania, Australia\\
-$^\mathsf{8}$Cooperative Institute for Mesoscale Meteorological Studies, and School of Meteorology, University of Oklahoma, Norman, Oklahoma, USA\\
-$^\mathsf{9}$Department of Atmospheric and Oceanic Sciences, University of Colorado Boulder, Boulder, Colorado, USA\\
-$^\mathsf{10}$National Snow and Ice Data Center, University of Colorado Boulder, Boulder, Colorado, USA\\
-$^\mathsf{11}$Department of Atmospheric and Oceanic Sciences, University of Colorado Boulder, Boulder, Colorado, USA\\[0.2cm]
-*Corresponding author: Peter Kuma (\href{mailto:peter.kuma@misu.su.se}{peter.kuma@misu.su.se})\\[0.4cm]
-\large \today\\[0.4cm]
+$^\mathsf{4}$Australian Antarctic Division, Kingston, Tasmania, Australia\\
+$^\mathsf{5}$Australian Antarctic Program Partnership, Institute for Marine and Antarctic Studies, University of Tasmania, Hobart, Tasmania, Australia\\
+$^\mathsf{6}$Cooperative Institute for Mesoscale Meteorological Studies, and School of Meteorology, University of Oklahoma, Norman, Oklahoma, USA\\
+$^\mathsf{7}$Department of Atmospheric and Oceanic Sciences, University of Colorado Boulder, Boulder, Colorado, USA\\
+$^\mathsf{8}$National Snow and Ice Data Center, University of Colorado Boulder, Boulder, Colorado, USA\\
+$^\mathsf{9}$Department of Atmospheric and Oceanic Sciences, University of Colorado Boulder, Boulder, Colorado, USA\\[0.2cm]
+$^\mathsf{10}$Department of Physics \& Atmospheric Science, Dalhousie University, Halifax, Canada\\
+$^\mathsf{11}$New South Wales Department of Planning and Environment, Sydney, New South Wales, Australia\\
+$^\mathsf{12}$New Zealand Defence Force, Wellington, New Zealand\\
+$^\star$Corresponding author: Peter Kuma (\href{mailto:peter.kuma@misu.su.se}{peter.kuma@misu.su.se})\\[0.4cm]
+\normalsize \today\\[0.4cm]
 
@@
 voyages and stations, especially Gert König-Langlo, Holger Schmithüsen, Roger
-Marchand, Peter Guest, Kelly Schick, Sally Garrett, Jamie Halla, Mike J.
-Harvey (†). We thank Loretta Preis for providing additional RV
-\emph{Polarstern} data.  We acknowledge the ICON model output provided by the
-nextGEMS project, Deutscher Wetterdienst, Max-Planck-Institute for Meteorology,
-DKRZ, Karlsruhe Institute of Technology, and Center for Climate Systems
-Modeling; reanalysis dataset ERA5 provided by the Copernicus Climate Change
-Service; MERRA-2 provided by the Global Modeling and Assimilation Office; CERES
-datasets provided by the NASA Langley Atmospheric Science Data Center
-Distributed Active Archive Center; and the Natural Earth dataset provided by
-naturalearthdata.com.  Last but not least, we acknowledge the use of open
-source software Python, Cython \citep{behnel2011}, TensorFlow
-\citep{abadi2016}, Devuan GNU+Linux, parallel \citep{tange2011}, NumPy
-\citep{harris2020}, SciPy \citep{virtanen2020}, Matplotlib \citep{hunter2007},
-cartopy \citep{cartopy}, pyproj, Inkscape, Bash, GNU Fortran, HDF
-\citep{folk1999}, and NetCDF \citep{rew1990}.  We dedicate this study to the
-memory of Mike J.  Harvey, who very substantially contributed to obtaining the
-atmospheric observations on the RV \emph{Tangaroa} voyages used in this study.
+Marchand, Peter Guest, Kelly Schick, Jamie Halla, Mike J.  Harvey (†). We thank
+Loretta Preis for providing additional RV \emph{Polarstern} data.  We
+acknowledge the ICON model output provided by the nextGEMS project, Deutscher
+Wetterdienst, Max-Planck-Institute for Meteorology, DKRZ, Karlsruhe Institute
+of Technology, and Center for Climate Systems Modeling; reanalysis dataset ERA5
+provided by the Copernicus Climate Change Service; MERRA-2 provided by the
+Global Modeling and Assimilation Office; CERES datasets provided by the NASA
+Langley Atmospheric Science Data Center Distributed Active Archive Center; and
+the Natural Earth dataset provided by naturalearthdata.com.  Last but not
+least, we acknowledge the use of open source software Python, Cython
+\citep{behnel2011}, TensorFlow \citep{abadi2016}, Devuan GNU+Linux, parallel
+\citep{tange2011}, NumPy \citep{harris2020}, SciPy \citep{virtanen2020},
+Matplotlib \citep{hunter2007}, cartopy \citep{cartopy}, pyproj, Inkscape, Bash,
+GNU Fortran, HDF \citep{folk1999}, and NetCDF \citep{rew1990}.  We dedicate
+this study to the memory of Mike J.  Harvey, who very substantially contributed
+to obtaining the atmospheric observations on the RV \emph{Tangaroa} voyages
+used in this study.
 
@@
 conceptualization, funding acquisition, project administration, supervision,
-and writing – review \& editing; AM, GP, SH, SP, SA, GM, JC, and AS: data
+and writing – review \& editing; AM, SA, GM, JC, GP, SH, SP, SG, and AS: data
 curation, investigation, resources, writing – review \& editing; [TODO]

### 2024-11-24 manuscript.tex
Update on Overleaf.

@@
 $\mathrm{2\times 10^{-6} m^{-1}sr^{-1}}$ after subtracting 5 standard
-deviations of range-scale noise. Fig. \ref{fig:example}b shows an example of
+deviations of range-scaled noise. Fig. \ref{fig:example}b shows an example of
 simulated Vaisala CL51 backscatter from ERA5 data, corresponding to a day of
@@
 \emph{ngc3028} produced in 2023 \citep{nextgems2023a,nextgems2023b} for a model
-time period of 20 January 2020 to 22 July 2025, of which we analysed the full
-years 2021--2024 (inclusive). While a Cycle 4 run was available, we could not
-use it due to the unavailability of the necessary variables. The horizontal
+time period of 20 January 2020 to 22 July 2025, of which we analysed the period 2021--2024 (inclusive). While a Cycle 4 run was available, we could not
+use it due to a lack of availability of the necessary variables. The horizontal
 resolution of ngc3028 is about 5 km.  The model output is available on 90

### 2024-11-28 manuscript.tex
Addressing comments

@@
 McFarquhar, John J.
-Cassano, Graeme Plank, Sean Hartery, Simon Parsons, Sally Garrett, and Alex J.
+Cassano, Graeme E.
+Plank, Sean Hartery, Simon Parsons, Sally Garrett, and Alex J.
 Schuddeboom}
@@
 Alexander$^\mathsf{4,5}$, Greg M.
-McFarquhar$^\mathsf{6}$, John J.
-Cassano$^\mathsf{7,8,9}$, Graeme Plank$^\mathsf{3}$, Sean Hartery$^\mathsf{10}$, Simon Parsons$^\mathsf{11}$, Sally Garrett$^\mathsf{12}$, and Alex J.
+McFarquhar$^\mathsf{6,7}$, John J.
+Cassano$^\mathsf{8,9,10}$, Graeme E.
+Plank$^\mathsf{3}$, Sean Hartery$^\mathsf{11}$, Simon Parsons$^\mathsf{12}$, Sally Garrett$^\mathsf{13}$, and Alex J.
 Schuddeboom$^\mathsf{3}$\\[0.4cm]
 \footnotesize
-$^\mathsf{1}$Department of Meteorology (MISU), Stockholm University, Stockholm,, Sweden\\
+$^\mathsf{1}$Department of Meteorology (MISU), Stockholm University, Stockholm, Sweden\\
 $^\mathsf{2}$Bolin Centre for Climate Research, Stockholm University, Stockholm, Sweden\\
@@
 $^\mathsf{5}$Australian Antarctic Program Partnership, Institute for Marine and Antarctic Studies, University of Tasmania, Hobart, Tasmania, Australia\\
-$^\mathsf{6}$Cooperative Institute for Mesoscale Meteorological Studies, and School of Meteorology, University of Oklahoma, Norman, Oklahoma, USA\\
-$^\mathsf{7}$Department of Atmospheric and Oceanic Sciences, University of Colorado Boulder, Boulder, Colorado, USA\\
-$^\mathsf{8}$National Snow and Ice Data Center, University of Colorado Boulder, Boulder, Colorado, USA\\
-$^\mathsf{9}$Department of Atmospheric and Oceanic Sciences, University of Colorado Boulder, Boulder, Colorado, USA\\[0.2cm]
-$^\mathsf{10}$Department of Physics \& Atmospheric Science, Dalhousie University, Halifax, Canada\\
-$^\mathsf{11}$New South Wales Department of Planning and Environment, Sydney, New South Wales, Australia\\
-$^\mathsf{12}$New Zealand Defence Force, Wellington, New Zealand\\
+$^\mathsf{6}$Cooperative Institute of Severe and High Impact Weather Research and Operations, University of Oklahoma, Norman, OK, USA\\
+$^\mathsf{7}$School of Meteorology, University of Oklahoma, Norman, OK, USA\\
+$^\mathsf{8}$Cooperative Institute for Research in Environmental Sciences, University of Colorado, Boulder, CO, USA\\
+$^\mathsf{9}$National Snow and Ice Data Center, University of Colorado, Boulder, CO, USA\\
+$^\mathsf{10}$Department of Atmospheric and Oceanic Sciences, University of Colorado, Boulder, CO, USA\\[0.2cm]
+$^\mathsf{11}$Department of Physics \& Atmospheric Science, Dalhousie University, Halifax, Canada\\
+$^\mathsf{12}$New South Wales Department of Planning and Environment, Sydney, New South Wales, Australia\\
+$^\mathsf{13}$New Zealand Defence Force, Wellington, New Zealand\\
 $^\star$Corresponding author: Peter Kuma (\href{mailto:peter.kuma@misu.su.se}{peter.kuma@misu.su.se})\\[0.4cm]
@@
 Among them is the 5-km Icosahedral Nonhydrostatic Weather and Climate Model
-(ICON). Due to the high resolution, parameterizations of convection and clouds
-are avoided. Standard-resolution models have substantial cloud biases over the
-Southern Ocean (SO), affecting radiation and sea surface temperature.  We
-evaluated SO clouds in ICON and the ERA5 and MERRA-2 reanalyses.  The SO is
+(ICON). The high resolution allows for parameterizations of convection and
+clouds to be avoided. Standard-resolution models have substantial cloud biases
+over the Southern Ocean (SO), affecting radiation and sea surface temperature.
+We evaluated SO clouds in ICON and the ERA5 and MERRA-2 reanalyses.  The SO is
 dominated by low clouds, which cannot be observed accurately from space due to
@@
 underestimate near-surface clouds or fog.  MERRA-2 tends to underestimate cloud
-occurrence at all heights. Unstable conditions are the most problematic for the
-models. In daily cloud cover, ICON and the reanalyses tend to be about 1 and 2
-oktas clearer, respectively. Compared to radiosondes, potential temperature is
-accurate in all, but ICON is too unstable over the low-latitude SO and too
-humid in the boundary layer. MERRA-2 is too humid at all heights. SO cloud
-biases are a substantial issue in the GSRM, but are an improvement over the
-lower-resolution reanalyses. Explicitly resolved convection and cloud processes
-were not enough to address the model cloud biases.
+occurrence at all heights. Less stable conditions are the most problematic for
+ICON and the reanalyses.  In daily cloud cover, ICON and the reanalyses tend to
+be about 1 and 2 oktas clearer, respectively. Compared to radiosondes,
+potential temperature is accurate in the reanalyses, but ICON underestimates
+stability over the low-latitude SO and too humid in the boundary layer. MERRA-2
+is too humid at all heights. SO cloud biases remain a substantial issue in the
+GSRM, but are an improvement over the lower-resolution reanalyses. Explicitly
+resolved convection and cloud processes were not enough to address the model
+cloud biases.
 
@@
 
-Increasing climate model resolution is a common way of improving model accuracy
-\citep{mauritsen2022}. This is of course limited by the available computational
-power and a trade-off with increasing parameterization complexity. Current
+Increasing climate model resolution is one way of improving model accuracy of
+representation of the climate system \citep{mauritsen2022}. It has been
+practiced since the advent of climate modelling as more computational power,
+memory, and storage capacity become available. It is, however, often not as
+easy as changing the grid size because of the complex interplay between model
+dynamics and physics, which necessitates adjusting and tuning all components
+together.  Increasing resolution is of course limited by the available
+computational power and a trade-off with increasing parameterization
+complexity, which is another way of improving model accuracy.  Current
 computational availability and acceleration from general-purpose computing on
-graphics processing units (GPUs) is progressing to enable km-scale (also
-called k-scale) Earth system models (ESMs) and coupled atmosphere--ocean
-general circulation models (AOGCMs) in research conditions today and
-operationally in the forthcoming years. Therefore, it represents a natural
-advance in climate modelling.  Global storm-resolving models (GSRMs) are
-emerging as a new front in the development of high-resolution global climate
-models, with horizontal grid resolutions of about 2--8 km
-\citep{satoh2019,stevens2019}. This is enough to resolve mesoscale convective
-storms, but smaller-scale convective plumes and smaller-scale cloud structure
-remain unresolved. At a 5-km scale, non-hydrostatic processes also become
-important, and for this reason such models are generally non-hydrostatic. The
-terms global cloud-resolving models or global convection-permitting/-resolving
-models are also sometimes used interchangeably with GSRMs but imply that clouds
-or convection are resolved explicitly, which is not entirely true for GSRMs, as
+graphics processing units (GPUs) is progressing to enable km-scale (also called
+k-scale) Earth system models (ESMs) and coupled atmosphere--ocean general
+circulation models (AOGCMs) in research conditions today and operationally in
+the forthcoming years.  Therefore, it represents a natural advance in climate
+modelling.  Global storm-resolving models (GSRMs) are emerging as a new front
+in the development of high-resolution global climate models, with horizontal
+grid resolutions of about 2--8 km \citep{satoh2019,stevens2019}. This is enough
+to resolve mesoscale convective storms, but smaller-scale convective plumes and
+cloud structure remain unresolved. At an approximately 5-km scale,
+non-hydrostatic processes also become important \citep{weisman1997}, and for
+this reason such models are generally non-hydrostatic. The terms global
+cloud-resolving models or global convection-permitting/-resolving models are
+also sometimes used interchangeably with GSRMs but imply that clouds or
+convection are resolved explicitly, which is not entirely true for GSRMs, as
 this would require an even higher horizontal resolution \citep{satoh2019}.
@@
 \citep{stevens2019,dyamond}, which is an intercomparison of nine global GSRMs
-over two 40-day time periods in summer (1 August -- 10 September 2016) and winter
-(20 January -- 1 March 2020). A new one-year GSRM intercomparison is currently
-proposed by \cite{takasuka2024}, with the hope of also evaluating the seasonal
-cycle and large-scale circulation.  An alternative to using a computationally
-costly GSRM is to train an artificial neural network on GSRM output and use it
-for subgrid-scale clouds, as done with the GSRM ICON by \cite{grundner2022} and
-\cite{grundner2023}.
-
-nextGEMS is a European Union--funded project \citep{nextgems} focused on the research and
-development of GSRMs at multiple modelling centres and universities in Europe.
-The project also develops GSRM versions of the Icosahedral Nonhydrostatic
-Weather and Climate Model (ICON), the Integrated Forecasting System (IFS), and
-their ocean components at eddy-resolving resolutions: ICON-O coupled with ICON
-and Finite-Element/volumE Sea ice-Ocean Model (FESOM) and Nucleus for European
-Modelling of the Ocean (NEMO) coupled with IFS.  The project has so far
-produced ICON and IFS simulations in three cycles (Cycle 1--3) and pre-final
-simulation, with a final production simulation planned by the end of the
-project. nextGEMS is not the only project developing GSRMs. Other GSRMs (or
-GSRM versions of climate models) currently in development include:
-Convection-Permitting Simulations With the E3SM Global Atmosphere Model
-[SCREAM; \cite{caldwell2021}], Atmospheric Model [NICAM; \cite{satoh2008}],
-Unified Model (UM), eXperimental System for High-resolution modeling for
-Earth-to-Local Domain [X-SHiELD; \cite{shield}], Action de Recherche Petite
-Echelle Grande Echelle-NonHydrostatic version [ARPEGE-NH;
+over two 40-day time periods in summer (1 August -- 10 September 2016) and
+winter (20 January -- 1 March 2020). A new one-year GSRM intercomparison is
+currently proposed by \cite{takasuka2024}, with the hope of also evaluating the
+seasonal cycle and large-scale circulation.  An alternative to using a
+computationally costly GSRM is to train an artificial neural network on GSRM
+output and use it for subgrid-scale clouds, as done with the GSRM ICON by
+\cite{grundner2022} and \cite{grundner2023}.
+
+nextGEMS is a European Union--funded project \citep{nextgems} focused on the
+research and development of GSRMs at multiple modelling centres and
+universities in Europe.  The project also develops GSRM versions of the
+Icosahedral Nonhydrostatic Weather and Climate Model (ICON), the Integrated
+Forecasting System (IFS), and their ocean components at eddy-resolving
+resolutions: ICON-O coupled with ICON and Finite-Element/volumE Sea ice-Ocean
+Model (FESOM) and Nucleus for European Modelling of the Ocean (NEMO) coupled
+with IFS.  The project has so far produced ICON and IFS simulations in three
+cycles (Cycle 1--3) and pre-final simulation, with a final production
+simulation planned by the end of the project. nextGEMS is not the only project
+developing GSRMs. Other GSRMs (or GSRM versions of climate models) currently in
+development include: Convection-Permitting Simulations With the E3SM Global
+Atmosphere Model [SCREAM; \cite{caldwell2021}], Atmospheric Model [NICAM;
+\cite{satoh2008}], Unified Model (UM), eXperimental System for High-resolution
+modeling for Earth-to-Local Domain [X-SHiELD; \cite{shield}], Action de
+Recherche Petite Echelle Grande Echelle-NonHydrostatic version [ARPEGE-NH;
 \cite{bubnova1995,voldoire2017}], Finite-Volume Dynamical Core on the Cubed
@@
 of the Coupled Model Intercomparison Project [CMIP6; \cite{eyring2016}], the
-cloud feedback has increased relative to CMIP5 \citep{zelinka2020}, this being
+cloud feedback has increased relative to CMIP5 \citep{zelinka2020}, which is
 one of the main reasons for the higher climate sensitivity of CMIP6 models.
@@
 The Southern Ocean (SO) is known to be a problematic region for climate model
-biases due to a lack of surface and in situ observations and
-being a lower priority region for numerical weather prediction (NWP) and
-climate model development because of its distance from populated areas of
-interest.  Nevertheless, radiation biases and changes over an area of its size
-have a very substantial influence on the global climate, and the SO is an
-important part of the global ocean conveyor belt.  Marine clouds have
-a disproportionate effect on top of atmosphere (TOA) SW radiation due to the
-relatively low albedo of the sea surface.  The relative longitudinal symmetry
-of the SO means that model cloud biases tend to be similar across longitudes.
-Here, we conventionally refer to the SO as ocean regions south of 40°S,
-low-latitude SO as 40--55°S and high-latitude SO as south of 55°S.
+biases due to a lack of surface and in situ observations and being a lower
+priority region for numerical weather prediction (NWP) and climate model
+development because of its distance from populated areas.  Nevertheless,
+radiation biases and changes over an area of its size have a substantial
+influence on the global climate, and the SO is an important part of the global
+ocean conveyor belt.  Marine clouds have a disproportionate effect on top of
+atmosphere (TOA) SW radiation due to the relatively low albedo of the sea
+surface.  The relative longitudinal symmetry of the SO means that model cloud
+biases tend to be similar across longitudes.  Here, we conventionally refer to
+the SO as ocean regions south of 40°S, low-latitude SO as 40--55°S and
+high-latitude SO as south of 55°S.
 
@@
 cloud radiative effect (CRE) bias is still positive in eight analysed CMIP6
-models analysed by \cite{schuddeboom2021} over the high-latitude SO, whereas over
-the low-latitude SO it tends to be more neutral or negative in some models. Too
-much absorbed SW radiation over the SO was also identified in the GSRM SCREAM
-\cite{caldwell2021}. Compensating biases are possible, such as the `too few too
-bright' cloud bias, characterised by too small cloud fraction and too large
-cloud albedo \citep{wall2017,kuma2020}, previously described by
+models analysed by \cite{schuddeboom2021} over the high-latitude SO, whereas
+over the low-latitude SO it tends to be more neutral or negative in some
+models. Too much absorbed SW radiation over the SO was also identified in the
+GSRM SCREAM \cite{caldwell2021}. Compensating biases are possible, such as the
+`too few too bright' cloud bias, characterised by too small cloud fraction and
+too large cloud albedo \citep{wall2017,kuma2020}, previously described by
 \cite{webb2001}, \cite{weare2004}, \cite{zhang2005}, \cite{karlsson2008},
@@
 models. That is, a model maintains a reasonable SW radiation balance by
-reflecting too much SW radiation from clouds, but has too little cloud
-area overall. A study by \cite{konsta2022} showed that this type of bias is still
+reflecting too much SW radiation from clouds, but has too little cloud area
+overall. A study by \cite{konsta2022} showed that this type of bias is still
 present in six analysed CMIP6 models in tropical marine clouds, using the
@@
 that over the SO, the DYAMOND GSRM ICON underestimates low-level cloud fraction
-on the order of 30\% [relative to Moderate Resolution Imaging
-Spectroradiometer (MODIS) data] and overestimates downwelling TOA SW radiation on
-by approximately 10 Wm$^\mathrm{-2}$ in  [relative to the Clouds and the Earth’s
-Radiant Energy System (CERES) data] in the highest model resolution run (2.5 km).
-\cite{zhao2022} reported a similar SW radiation bias in five analysed CMIP6
-models over high-latitude SO and the total cloud fraction underestimation on
-the order of 10\% over the entire 40--60°S SO. Recently, \cite{ramadoss2024}
+on the order of 30\% [relative to Moderate Resolution Imaging Spectroradiometer
+(MODIS) data] and overestimates downwelling TOA SW radiation on by
+approximately 10 Wm$^\mathrm{-2}$ [relative to the Clouds and the Earth’s
+Radiant Energy System (CERES) data] in the highest model resolution run (2.5
+km).  \cite{zhao2022} reported a similar SW radiation bias in five analysed
+CMIP6 models over high-latitude SO and the total cloud fraction underestimation
+on the order of 10\% over the entire 40--60°S SO. Recently, \cite{ramadoss2024}
 analysed 48 hours of km-scale ICON limited area model NWP simulations over a SO
@@
 Radiation, and atmospherIc Composition Over the southeRn oceaN (CAPRICORN)
-voyage cloud and precipitation observations \cite{mcfarquhar2021}. They found the ICON cloud optical
-thickness was underestimated relative to Himawari‐8 satellite observations, but
-also identified large differences in cloud top phase.
+voyage cloud and precipitation observations \cite{mcfarquhar2021}. They found
+the ICON cloud optical thickness was underestimated relative to Himawari‐8
+satellite observations, but also identified large differences in cloud top
+phase.
 
@@
 overlapping and thick clouds and ground clutter, respectively.  Specifically,
-the radar on CloudSat and lidar on CALIPSO (neither of which are now operational) are affected by the abovementioned issues, resulting in a strong
+the radar on CloudSat and lidar on CALIPSO (neither of which are now
+operational) are affected by the abovementioned issues, resulting in a strong
 underestimation of cloud occurrence below 2 km relative to ground-based lidar
@@
 \emph{Tangaroa} (© Peter Kuma, University of Canterbury), \textbf{(d)} Vaisala
-CL51 installation at the Macquarie Island station (© Jeff Aquilina, Bureau of
-Meteorology).
-% TODO: Ask for photo permission and info about license.
+CL51 (© Jeff Aquilina, Bureau of Meteorology).
 }
@@
 December, 16--17 December 2016; Measurements of Aerosols, Radiation, and CloUds
-over the Southern Ocean (MARCUS;  3 days): 8, 10 November, 10 December;
+over the Southern Ocean (MARCUS;  3 days): 8, 10 November, 10 December 2017;
 Macquarie Island Cloud Radiation Experiment (MICRE; 9 days): 7--8, 29 June, 5,
@@
 \begin{table}[p!]
-% TODO: Add sampling intervals.
 \caption{
@@
 AA15-16  & \cite{klekociuk2020} \\
-MARCUS   & \cite{mcfarquhar2016,mcfarquhar2019,zhang2017,keeler2017,walton2017,cromwell2017,mcfarquhar2021} \\
-MICRE    & \cite{marchand2015,marchand2020,zhang2016,mcfarquhar2021} \\
+MARCUS   & \cite{mcfarquhar2021,xia2024,niu2024} \\
+MICRE    & \cite{mcfarquhar2021} \\
 NBP1704  & \cite{ackley2020} \\
@@
 A coupled (atmosphere--ocean) GSRM version of the ICON model is in development
-at the nextGEMS project \citep{hohenegger2023}. ICON is a very versatile model,
-allowing for simulations ranging from coarse-resolution ESM simulations, GSRM
-simulations, limited area model simulations, to large eddy simulations (LES),
-for both weather prediction and climate projections. ICON uses the atmospheric
-component ICON-A \citep{giorgetta2018}, whose physics is derived from ECHAM6
-\citep{stevens2013}, and the ocean component ICON-O \citep{korn2022}. Earlier
-runs of the GSRM ICON from DYAMOND were evaluated by \cite{mauritsen2022}.
+at the nextGEMS project \citep{hohenegger2023}. ICON is an exceptionally
+versatile model, allowing for simulations ranging from coarse-resolution ESM
+simulations, GSRM simulations, limited area model simulations, to large eddy
+simulations (LES), for both weather prediction and climate projections. ICON
+uses the atmospheric component ICON-A \citep{giorgetta2018}, whose physics is
+derived from ECHAM6 \citep{stevens2013}, and the ocean component ICON-O
+\citep{korn2022}. Earlier runs of the GSRM ICON from DYAMOND were evaluated by
+\cite{mauritsen2022}.
 
@@
 the El Niño--Southern Oscillation) are not expected to be equivalent to reality
-at the same time and place. To compare with the observations collected on
+at the same time and place. To compare with the observations collected in
 different years (2010--2021, inclusive), we compared the model output with
@@
 
-TOA radiation quantities are taken from the CERES instruments on board of the
+TOA radiation quantities are taken from the CERES instruments on board the
 Terra and Aqua satellites \citep{wielicki1996,loeb2018}. In our analysis we
@@
 output and the reanalysis data (the liquid and ice precipitation mass mixing
-ratios) and because the required radiation calculations for precipitation are
-currently not implemented in the ALCF. In order to achieve a fair comparison of
-observations with models, one should exclude observed and simulated lidar
-profiles with precipitation either manually or using an automated method. It is
-relatively difficult to distinguish precipitation backscatter from cloud
-backscatter in lidar observations, especially when only one wavelength channel
-and no polarised channel are available. In models, the same can be accomplished
-relatively easily by excluding profiles exceeding a certain amount of surface
+ratios). The required radiation calculations for precipitation are also
+currently not implemented in the ALCF, even though this is a planned feature.
+In order to achieve a fair comparison of observations with models, one should
+exclude observed and simulated lidar profiles with precipitation either
+manually or using an automated method. It is relatively difficult to
+distinguish precipitation backscatter from cloud backscatter in lidar
+observations, especially when only one wavelength channel and no polarised
+channel are available. In models, the same can be accomplished relatively
+easily by excluding profiles exceeding a certain amount of surface
 precipitation flux. In the observations, using precipitation flux measurements
-from rain gauges can be very unreliable on ships due to ship movement and
-turbulence caused by nearby ship structures. Our analysis of rain gauge data
-from the RV \emph{Tangaroa} showed large discrepancies between the rain gauge
-time series and human-performed synoptic observations, as well as large
-inconsistencies in the rain gauge time series. Human-performed observations of
-precipitation presence or absence are expected to be reliable but only cover a
-limited set of time instants. Therefore, it was desirable to implement a method
-of detecting precipitation from observed backscatter profiles alone.
+from rain gauges can be very unreliable on ships due to ship movement,
+turbulence caused by nearby ship structures, and sea spray. Our analysis of
+rain gauge data from the RV \emph{Tangaroa} showed large discrepancies between
+the rain gauge time series and human-performed synoptic observations, as well
+as large inconsistencies in the rain gauge time series. Human-performed
+observations of precipitation presence or absence are expected to be reliable
+but only cover a limited set of time instants. Therefore, it was desirable to
+implement a method of detecting precipitation from observed backscatter
+profiles alone.
 
@@
 conditions are used for subsetting our dataset. Fig.
-\ref{fig:cyclone-stability}a shows a geographical distribution of the fraction
+\ref{fig:cyclone-stability}a, b show a geographical distribution of the fraction
 of cyclonic days as determined by the cyclone tracking algorithm applied on the
@@
 
-Fig. \ref{fig:cyclone-stability}b shows a geographical distribution of the
+Fig. \ref{fig:cyclone-stability}c, d show a geographical distribution of the
 relatively stable and unstable conditions as determined by the LTS (Section
@@
 Cloud occurrence by height calculated as the average of all voyages and
-stations for the observed (OBS) and simulated lidar cloud mask. The total cloud
-fraction (CF), average shortwave (SW), and longwave (LW) are shown in the
-legend, and the relative frequency of occurrence (RFO) of the subset is shown
-below.  The bands span the 16$^\mathrm{th}$--84$^\mathrm{th}$ percentile
-calculated from the set of all voyages and stations. The subsets
-\textbf{(d--g)} are defined in Section \ref{sec:cyclone-stability}.
+stations for the observed (OBS) and simulated lidar cloud mask, and lifting
+condensation level (LCL) distribution. The total cloud fraction (CF), average
+shortwave (SW), and longwave (LW) are shown in the legend, and the relative
+frequency of occurrence (RFO) of the subset is shown below.  The bands span the
+16$^\mathrm{th}$--84$^\mathrm{th}$ percentile calculated from the set of all
+voyages and stations. The subsets \textbf{(d--g)} are defined in Section
+\ref{sec:cyclone-stability}.
 }
@@
 ICON or the reanalyses.  While ICON is the closest, it tends to be 1 okta
-clearer the observations, peaking at 6 oktas, and highly underestimating days
-with 8 oktas.  Overall, the reanalyses show results similar to each other,
+clearer than the observations, peaking at 6 oktas, and highly underestimating
+days with 8 oktas.  Overall, the reanalyses show results similar to each other,
 underestimating cloud cover by about 2 oktas and strongly underestimating days
@@
 observations can be regarded as superior to satellite lidar observations for
-low-level clouds in this region, while mid- and high-level clouds are better
-represented in satellite observations \citep{mcerlich2021}.
+low-level clouds, which are predominant in this region, while mid- and
+high-level clouds are better represented in satellite observations
+\citep{mcerlich2021}.
 
@@
 years. This dataset, together with the use of a ground-based lidar simulator,
-provided a fairly comprehensive basis for evaluating SO cloud and thermodynamic
+provided a comprehensive basis for evaluating SO cloud and thermodynamic
 profile biases in the GSRM ICON and the ERA5 and MERRA-2 reanalyses. Our
@@
 comparison, showing that the virtual potential temperature profiles in ICON
-are more stable than in the observations over low-latitude SO.
+are less stable than in the observations over low-latitude SO.
 
@@
 Horizon 2020 research and innovation program under a grant agreement no.
-101003470. FB received funding from the Wenner-Gren foundation and the Swedish
-e-Science Research Centre. Supercomputing resources were provided by the DKRZ
-(project 1125 ICON-development) and the National Academic Infrastructure for
-Supercomputing in Sweden (allocation 2023/22-202). The data collection by the
-University of Canterbury was funded by the Deep South National Science
-Challenge Clouds and Aerosols project.  Data collection on the RSV \emph{Aurora
-Australis} was funded by the Australian Antarctic Science project (grant no.
-4292).  We acknowledge the contribution of Thorsten Mauritsen to funding
+101003470. FB received funding from the Wenner-Gren Foundation and the Swedish
+e-Science Research Centre.  The work of GM was supported by the United States
+(U.S.) Department of Energy Award DE-SC0021159.  Supercomputing resources were
+provided by the DKRZ (project 1125 ICON-development) and the National Academic
+Infrastructure for Supercomputing in Sweden (allocation 2023/22-202). The data
+collection by the University of Canterbury was funded by the Deep South
+National Science Challenge Clouds and Aerosols project.  Data collection on the
+AA15-16 voyages was funded by the Australian Antarctic Science project (grant
+no.  4292).  We acknowledge the contribution of Thorsten Mauritsen to funding
 acquisition and project management.  We acknowledge the RV \emph{Polarstern}
@@
 dataset provided by the Australian Antarctic Division (AAD) and University of
-Canterbury (UC), RV \emph{Tangaroa} datasets provided by the National Institute
+Canterbury (UC), the RV \emph{Tangaroa} datasets provided by the National Institute
 of Water and Atmospheric Research and UC, the NBP1704 dataset provided by the
@@
 the Atmospheric Radiation Measurement (ARM) and AAD, and the MICRE dataset
-provided by ARM, the Australian Bureau of Meteorology, and AAD. We thank the
+provided by ARM, the Australian Bureau of Meteorology, and AAD.  Technical,
+logistical, and ship support for MARCUS and MICRE were provided by the AAD
+through Australian Antarctic Science projects 4292 and 4387, and we thank
+Steven Whiteside, Lloyd Symonds, Rick van den Enden, Peter de Vries, Chris
+Young, Chris Richards, Andrew Klekociuk, John French, Terry Egan, Nick
+Cartwright, and Ken Barrett for all of their assistance.  We thank the
 scientific staff, the crew, and everyone involved in collecting data on the
 voyages and stations, especially Gert König-Langlo, Holger Schmithüsen, Roger
-Marchand, Peter Guest, Kelly Schick, Jamie Halla, Mike J.  Harvey (†). We thank
-Loretta Preis for providing additional RV \emph{Polarstern} data.  We
+Marchand, Peter Guest, Kelly Schick, Jamie Halla, and Mike J.  Harvey (†). We
+thank Loretta Preis for providing additional RV \emph{Polarstern} data.  We
 acknowledge the ICON model output provided by the nextGEMS project, Deutscher
@@
 TAN1802 data are available on Zenodo
-(\url{https://doi.org/10.5281/zenodo.4060237}).  The other voyage and station
-data are openly available on Zenodo ([TODO]). Subsetted model and reanalysis data
-for the voyage tracks and the station and data processed with the ALCF are
-openly available on Zenodo ([TODO]).
+(\url{https://doi.org/10.5281/zenodo.4060237}).
+
+% TODO: The other voyage and station data are openly available on Zenodo ().
+% Subsetted model and reanalysis data for the voyage tracks and the station and
+% data processed with the ALCF are openly available on Zenodo ().
 
@@
 (\url{https://credit.niso.org}).  PK: conceptualization, data curation, formal
-analysis, investigation, methodology, software, writing – original draft; FB:
+analysis, investigation, methodology, software, writing – original draft; FAMB:
 conceptualization, funding acquisition, project administration, supervision,
-and writing – review \& editing; AM, SA, GM, JC, GP, SH, SP, SG, and AS: data
-curation, investigation, resources, writing – review \& editing; [TODO]
+and writing – review \& editing; AJM, SPA, GMM, JJC, GEP, SH, SP, SG, and AJS:
+data curation, investigation, resources, writing – review \& editing.
 

### 2024-11-28 manuscript.tex
Fix issue in ANN description

@@
 type. We used this dataset to train a convolutional artificial neural network
-(ANN) of the U-Net type \citep{ronneberger2015} to recognise profiles with
-precipitation from lidar backscatter (Fig. \ref{fig:ann}a), implemented in the
-TensorFlow ANN framework \citep{tensorflow}. Samples of short time intervals
-(10 min) of near-surface lidar backscatter (0–250 m) were classified as clear,
-rain, snow, and fog, using the synoptic observations as a training dataset
-(Fig.  \ref{fig:ann}b). From these, a binary, mutually exclusive classification
-of profiles as precipitating (rain or snow) or dry (clear or fog) was derived.
-For detecting model and reanalysis precipitation, we used a fixed threshold for
-surface precipitation flux of 0.1 mm h$^{-1}$ (the ANN was not used).
+(ANN) to recognise profiles with precipitation from lidar backscatter (Fig.
+\ref{fig:ann}a), implemented in the TensorFlow ANN framework
+\citep{tensorflow}. Samples of short time intervals (10 min) of near-surface
+lidar backscatter (0–250 m) were classified as clear, rain, snow, and fog,
+using the synoptic observations as a training dataset (Fig.  \ref{fig:ann}b).
+From these, a binary, mutually exclusive classification of profiles as
+precipitating (rain or snow) or dry (clear or fog) was derived.  For detecting
+model and reanalysis precipitation, we used a fixed threshold for surface
+precipitation flux of 0.1 mm h$^{-1}$ (the ANN was not used).
 

### 2024-12-02 manuscript.tex
Update on Overleaf.

@@
 Global storm-resolving models (GSRMs) are the next avenue of climate modelling.
-Among them is the 5-km Icosahedral Nonhydrostatic Weather and Climate Model
+Among them is a 5-km version of the Icosahedral Nonhydrostatic Weather and Climate Model
 (ICON). The high resolution allows for parameterizations of convection and
@@
 models. That is, a model maintains a reasonable SW radiation balance by
-reflecting too much SW radiation from clouds, but has too little cloud area
+reflecting too much SW radiation from clouds, but has too little cloudarea
 overall. A study by \cite{konsta2022} showed that this type of bias is still
@@
 on the order of 30\% [relative to Moderate Resolution Imaging Spectroradiometer
-(MODIS) data] and overestimates downwelling TOA SW radiation on by
+(MODIS) data] and overestimates downwelling TOA SW radiation by
 approximately 10 Wm$^\mathrm{-2}$ [relative to the Clouds and the Earth’s
@@
 Interactions of both are also possible, for example SST affecting clouds and
-clouds affecting the surface radiation. \cite{zhang2023} has shown that SST
+clouds affecting the surface radiation. \cite{zhang2023} have shown that SST
 biases have improved in CMIP6 compared to CMIP5 [relative to the European
@@
 overlapping and thick clouds and ground clutter, respectively.  Specifically,
-the radar on CloudSat and lidar on CALIPSO (neither of which are now
-operational) are affected by the abovementioned issues, resulting in a strong
+the radar on CloudSat and lidar on CALIPSO (neither of which are nowoperational) are affected by the abovementioned issues, resulting in a strong
 underestimation of cloud occurrence below 2 km relative to ground-based lidar
@@
 
-TOA radiation quantities are taken from the CERES instruments on board the
+TOA radiation quantities are taken from the CERES instruments onboard the
 Terra and Aqua satellites \citep{wielicki1996,loeb2018}. In our analysis we
@@
 Radiation calculations presented in the results (Section \ref{sec:results})
-were done in such a way that they always represent averages of daily means.
-This was done in order to be consistent with the CERES SYN1deg data, which are
-available as daily means. Therefore, every instantaneous profile in the
+were completed such that they always represent daily means in order to be consistent with the CERES SYN1deg data. Therefore, every instantaneous profile in the
 simulated lidar data was assigned a daily mean radiation value corresponding to
@@
 the daily mean radiation value was taken from the spatially and temporally
-co-located CERES SYN1deg data of the day (in UTC). The voyage or station
+co-located CERES SYN1deg data for the day (in UTC). The voyage or station
 average was calculated in the same way.
@@
 ratios). The required radiation calculations for precipitation are also
-currently not implemented in the ALCF, even though this is a planned feature.
-In order to achieve a fair comparison of observations with models, one should
+currently not implemented in the ALCF, even though this is a planned future addition.
+In order to achieve a fair comparison of observations with model output, we
 exclude observed and simulated lidar profiles with precipitation either
@@
 channel are available. In models, the same can be accomplished relatively
-easily by excluding profiles exceeding a certain amount of surface
+easily by excluding profiles exceeding a certain surface
 precipitation flux. In the observations, using precipitation flux measurements
@@
 observations of precipitation presence or absence are expected to be reliable
-but only cover a limited set of time instants. Therefore, it was desirable to
+but only cover a limited set of times. Therefore, it was desirable to
 implement a method of detecting precipitation from observed backscatter
@@
 In addition to the above, we partitioned our data into two mutually exclusive
-subsets by stability. We determined this by calculating lower tropospheric
-stability (LTS) as the difference between the potential temperature at 700 hPa
+subsets based on lower tropospheric stability (LTS), which is derived as the difference between the potential temperature at 700 hPa
 and the surface.  Based on a histogram of LTS in ERA5 and MERRA-2 calculated at
@@
 \ref{fig:cyclone-stability}a, b show a geographical distribution of the fraction
-of cyclonic days as determined by the cyclone tracking algorithm applied on the
+of cyclonic days as determined by the cyclone tracking algorithm applied to the
 ERA5 reanalysis and ICON data (Section \ref{sec:cyclone-stability}). As
@@
 with clouds at any height in the lidar cloud mask) is underestimated in ICON
-and the reanalyses by about 10\% and 20\%, respectively. When analysed by
+by about 10\% and in the reanalyses by about 20\%. When analysed by
 height, ICON overestimates cloud occurrence below 1 km and underestimates it
@@
 but strongly underestimates it near the surface.  We note that fog or
-near-surface clouds are strongly lacking in the reanalyses (fog and clouds are
+near-surface clouds are strongly underestimated in the reanalyses (fog and clouds are
 both included in the cloud occurrence).  As shown in Fig.
 \ref{fig:cloud-occurrence-panel}, the biases are relatively consistent across
-the data sources and longitudes. We conclude that the ICON results are overall
-better matching the observations than the reanalyses in this metric.
-
-In the general case (Fig. \ref{fig:cloud-occurrence}a), the observations show
-cloud occurrence peaking at the surface, whereas models show a higher peak (at
-about 500 m). The models underestimate the total cloud fraction by 10--20\% and
-show a strong drop in cloud occurrence near the surface, but this is not
+the data sources and longitudes. We conclude that the ICON results ch the observations better than the reanalyses in this metric.
+
+For all observations considered (Fig. \ref{fig:cloud-occurrence}a), the data show
+cloud occurrence peaking at the surface, whereas the models show a higher peak (at
+about 500 m). The models generally underestimate the total cloud fraction by 10--20\% and show a strong reduction in cloud occurrence near the surface, which is not
 supported by the observations. ICON and ERA5 overestimate cloud occurrence at
-the peak (between 0--1 km). Above 1 km, ICON and MERRA-2 underestimate cloud
+their peak (between 0--1 km). Above 1 km, ICON and MERRA-2 underestimate cloud
 occurrence, but ERA5 is very accurate. The exaggerated peak in models is partly
@@
 
-When subsetted by low- and high-latitude zones (Fig.
-\ref{fig:cloud-occurrence}b, c), we see that the low-latitude SO zone shows
+When subsetted by low- and high-latitude SO zones (Fig.
+\ref{fig:cloud-occurrence}b, c), we see that the low-latitude SO zone displays
 a stronger peak of cloud occurrence near the surface than the high-latitude SO
@@
 \ref{fig:cloud-occurrence}d, e), we see that the cyclonic situations have a
-larger amount of observed cloudiness, including the peak and total cloud
-fraction. In these situations, the models are doing a relatively good job of
-getting the vertical profile of cloud occurrence right, but still tend to
+larger amount of observed cloudiness, including peak and total cloud
+fraction. In these situations, the model vertical profiles of cloud occurrence compare well with observations, but still tend to
 underestimate cloud occurrence above 1 km and near the surface. Non-cyclonic
@@
 and spread across the altitudes of 0--1 km.  In relatively stable
-situations, the models are doing a fairly good job, but overestimate cloud
+situations, the models do a fairly good job, but overestimate cloud
 occurrence at the peak below 1 km; above 1 km, they show similar biases as in
 the general case.  In relatively unstable situations, the bias in ICON is
-very pronounced, with a much stronger peak at about 500 m, ERA5 is
-underestimating cloud occurrence below 1 km (especially near the surface), and
-MERRA-2 is underestimating it even more strongly.
+very pronounced, with a much stronger peak at about 500 m, ERA5 underestimates cloud occurrence below 1 km (especially near the surface), and
+MERRA-2 underestimates cloud occurrence even more strongly.
 
@@
 altitude than observations (500 m vs. near the surface), and correspondingly,
-its LCL tends to be also higher. MERRA-2 can be generally characterised as
+its LCL tends to be higher. MERRA-2 can be generally characterised as
 underestimating cloud occurrence at nearly all altitudes as well as the total
 cloud fraction, but mostly above and below 500 m (the peak at 500 m is
-well-represented). It struggles the most in the low-latitude SO zone and in the
-relatively unstable situations. ERA5 can be generally characterised as
+well-represented). MERRA-2 displays the largest errors relative to observations in the low-latitude SO zone and in relatively unstable situations. ERA5 can be generally characterised as
 representing cloud occurrence correctly above about 1--1.5 km, overestimating
 below, but underestimating near-surface cloud occurrence (0--500 m). The total
-cloud fraction is strongly underestimated in all situations. It has a tendency
+cloud fraction is strongly underestimated in all situations. ERA5 has a tendency
 towards underestimation in the low-latitude SO zone and relatively unstable
-situations; conversely, overestimating in the high-latitude SO zone and the
-relatively stable conditions.
+situations; conversely, overestimating in the high-latitude SO zone and relatively stable conditions.
 
@@
 
-We analysed the daily cloud cover (total cloud fraction) distribution. This is
+We also analysed the daily cloud cover (total cloud fraction) distribution. This is
 a measure of cloudiness, irrespective of height, calculated over the course of
 a day (UTC). A cloud detected at any height means that the lidar profile was
-classified as cloudy; otherwise, it was classified as a clear sky. When all
+classified as cloudy; otherwise, it was classified as clear sky. When all
 profiles in a day are taken together, the cloud cover for the day is defined as
@@
 In Fig.  \ref{fig:cloud-cover} we show the results for the same subsets of data
-as in the previous section. Observations have the greatest representation of
-high cloud cover (5--8 oktas), peaking at 7 oktas. This is not represented by
-ICON or the reanalyses.  While ICON is the closest, it tends to be 1 okta
+as in Section \ref{sec:cloud-occurrence}. Observations display the highest proportion of
+high cloud cover values (5--8 oktas), peaking at 7 oktas. This pattern is not represented by
+ICON or either reanalyses.  While ICON is closest to matching the observed distribution, it tends to be 1 okta
 clearer than the observations, peaking at 6 oktas, and highly underestimating
@@
 cloud cover, with 8 oktas occurring on one half of such days (Fig.
-\ref{fig:cloud-cover}d).  This is not represented by ICON or the reanalyses at
-all. Interestingly, clear sky days (0 oktas) also have a local maximum peaking
+\ref{fig:cloud-cover}d).  This sensitivity to cyclonic conditions is not observed in ICON or the reanalyses. Interestingly, clear sky days (0 oktas) also have a local maximum peaking
 at about 15\% in this subset.  When we contrast the low- and high-latitude
@@
 has almost no clear sky or small cloud cover cases (0--4 oktas). ICON and the
-reanalyses represent at least this characteristic of the distribution well for
+reanalyses represent this characteristic of the distribution well for
 0--3 oktas, but otherwise show biases similar to the general case. One of the
 greatest biases is present in ERA5 in the relatively unstable subset, in which
-ERA5 peaks at 3 oktas, whereas the observations peak at 7 oktas and show
+ERA5 peaks at 3 oktas, while the observations peak at 7 oktas and show
 negligible cloud cover below 5 oktas.
@@
 
-Overall, the mean $\theta_v$ is relatively well represented in ICON and
+Overall, the mean $\theta_v$ is very well represented in ICON and
 MERRA-2, being only slightly colder in the mid-to-high troposphere (less
 stable) in ICON than in observations (Fig. \ref{fig:potential-temperature}a).
-Large differences exist, however, in the 40--55°S zone, where ICON is colder in
-$\theta_v$ by up to about 5 K and more so at higher altitudes (Fig.
+Larger differences exist, however, in the 40--55°S zone, where ICON is colder by about 5 K at higher altitudes (Fig.
 \ref{fig:potential-temperature}b). In other subsets, the bias is relatively
@@
 Relative humidity displays much larger biases. In all subsets, ICON is too
-humid in the first 1 km but very accurate above, except for the 40--55°S zone
+humid in the first 1 km by about 5\% but very accurate above, except for the 40--55°S zone
 and unstable conditions (Fig. \ref{fig:potential-temperature}b, g),  where it
@@
 
-\section{Limitations}
+\section{Limitations of this study}
 
@@
 the winter months, due to the poor accessibility of this region during winter.
-Therefore, our results are mostly representative of summer and to a lesser
+Therefore, our results are likely representative of summer and to a lesser
 extent, spring and autumn conditions.
@@
 Ground-based lidar observations are affected by attenuation by thick cloud
-layers, and for this reason the results are mostly representative of boundary
+layers, and for this reason the results are most representative of boundary
 layer clouds, while higher-level clouds are only occasionally visible to the
@@
 low-level clouds, which are predominant in this region, while mid- and
-high-level clouds are better represented in satellite observations
+high-level clouds are better sampled by satellite observations
 \citep{mcerlich2021}.
 
-We attempted to remove lidar profiles with precipitation, which could not be
+We have attempted to remove lidar profiles with precipitation, which could not be
 properly simulated with the lidar simulator (Section \ref{sec:ann}). However,
@@
 and the fact that we had to choose a fixed threshold for surface precipitation
-flux in the model and reanalyses, which might not exactly correspond to
-detection by the ANN applied to observations. Also, we did not make an attempt
+flux in the model and reanalyses, which might not correspond to
+detection by the ANN applied to observations. Also, we made no attempt
 to remove profiles with precipitation not reaching the surface. The above
-reasons can result in an artificial bias in the comparison, even though we
+reasons may result in an artificial bias in the comparison, even though we
 expect this to be much smaller than the identified model biases.
@@
 analysis provides a unique evaluation perspective different from satellite
-observations -- one that is more suitable for evaluating boundary layer clouds,
+observations -- one that we argue is more suitable for evaluating boundary layer clouds,
 which are predominant in this region. Furthermore, we subsetted our dataset by
 low and high latitude bands, cyclonic activity, and stability in order to
-identify how these conditions relate to the biases.
+identify how these conditions influence the biases.
 
@@
 biases in models and their subsequent effect on the radiative transfer. This
-also applies to the new GSRM ICON, but the biases are lower than in the
+also applies to the new GSRM ICON, but the biases are generally lower than in the
 reanalyses, despite the reanalyses having the advantage of assimilation of the
@@
 We show that relative to ERA5, the distribution and strength of cyclonic
-activity over the SO is well represented in ICON, but it is substantially less
-stable in terms of LTS. The latter is also manifested in the radiosonde profile
+activity over the SO is well represented in ICON, but it displays lower values of LTS. The latter is also manifested in the radiosonde profile
 comparison, showing that the virtual potential temperature profiles in ICON
@@
 
-The 31 voyages and a station show fairly similar biases in cloud occurrence by
+The 31 voyages and a station show remarkably similar biases in cloud occurrence by
 height in the lidar comparison, which indicates that common underlying causes
@@
 too moist at all heights.  ICON also exhibits smaller internal variability than
-the radiosonde observations. Overall, the radiosonde comparison is only
-partially explaining the identified cloud biases, and other physical causes are
+the radiosonde observations. Overall, the radiosonde comparison only
+partially explains the identified cloud biases, and other physical causes are
 likely contributing.  This warrants further investigation, especially of
 ocean--atmosphere fluxes, shallow convection, and boundary layer turbulence.
-The lack of parametrised subgrid-scale convection in ICON might be a
+The lack of parametrised subgrid-scale convection in ICON could be a
 substantial issue even at the 5-km resolution.
@@
 This feature seems to be much more pronounced in ERA5 than in MERRA-2. On the
-other hand, this type of relationship is not present in ICON. This model mostly
+other hand, this relationship is not present in ICON. This model generally
 predicts smaller outgoing TOA SW radiation and smaller total cloud fraction
@@
 
-The results imply that SO cloud biases are still a substantial issue in the
+The results imply that SO cloud biases are still a substantial issue even in the
 km-scale resolution ICON model, even though an improvement over the
 lower-resolution reanalyses is notable. More effort is needed to improve the
-model cloud simulations in this fast-changing and understudied region. The
+model cloud simulations in this fast-changing and understudied region. However, this analysis suggests that the
 transition from models with parametrised convection and clouds to
 storm-resolving models might not solve these biases without additional effort.
-Evaluation of ocean--atmosphere heat, moisture, and momentum fluxes against in
-situ observations over the SO and comparison of GSRM simulations against
+Evaluation of ocean--atmosphere heat, moisture, and momentum fluxes against in-situ observations over the SO and comparison of GSRM simulations against
 large-eddy simulations are two potential avenues for future research that could

### 2024-12-03 manuscript.tex
Addressing comments

@@
 Global storm-resolving models (GSRMs) are the next avenue of climate modelling.
-Among them is a 5-km version of the Icosahedral Nonhydrostatic Weather and Climate Model
-(ICON). The high resolution allows for parameterizations of convection and
-clouds to be avoided. Standard-resolution models have substantial cloud biases
-over the Southern Ocean (SO), affecting radiation and sea surface temperature.
-We evaluated SO clouds in ICON and the ERA5 and MERRA-2 reanalyses.  The SO is
+Among them is a 5-km version of the Icosahedral Nonhydrostatic Weather and
+Climate Model (ICON). The high resolution allows for parameterizations of
+convection and clouds to be avoided, relying instead on explicitly resolved
+processes.  Standard-resolution models have substantial cloud biases over the
+Southern Ocean (SO), affecting radiation and sea surface temperature.  We
+evaluated SO clouds in ICON and the ERA5 and MERRA-2 reanalyses.  The SO is
 dominated by low clouds, which cannot be observed accurately from space due to
 overlapping clouds, attenuation, and ground clutter.  Instead, we analysed
-about 2400 days of lidar observations from 31 voyages and a station using a
-ground-based lidar simulator.  ICON and the reanalyses underestimate the total
-cloud fraction by about 10 and 20\%, respectively. ICON and ERA5 overestimate
-the cloud occurrence peak at about 500 m, potentially explained by their
-lifting condensation levels being too high.  The reanalyses strongly
-underestimate near-surface clouds or fog.  MERRA-2 tends to underestimate cloud
-occurrence at all heights. Less stable conditions are the most problematic for
-ICON and the reanalyses.  In daily cloud cover, ICON and the reanalyses tend to
-be about 1 and 2 oktas clearer, respectively. Compared to radiosondes,
-potential temperature is accurate in the reanalyses, but ICON underestimates
-stability over the low-latitude SO and too humid in the boundary layer. MERRA-2
-is too humid at all heights. SO cloud biases remain a substantial issue in the
-GSRM, but are an improvement over the lower-resolution reanalyses. Explicitly
-resolved convection and cloud processes were not enough to address the model
-cloud biases.
+about 2400 days of lidar observations from 31 voyages and a station during
+2010--2021 using a ground-based lidar simulator.  ICON and the reanalyses
+underestimate the total cloud fraction by about 10 and 20\%, respectively. ICON
+and ERA5 overestimate the cloud occurrence peak at about 500 m, potentially
+explained by their lifting condensation levels being too high.  The reanalyses
+strongly underestimate near-surface clouds or fog.  MERRA-2 tends to
+underestimate cloud occurrence at all heights. Less stable conditions are the
+most problematic for ICON and the reanalyses.  In daily cloud cover, ICON and
+the reanalyses tend to be about 1 and 2 oktas clearer, respectively. Compared
+to radiosondes, potential temperature is accurate in the reanalyses, but ICON
+underestimates stability over the low-latitude SO and too humid in the boundary
+layer. MERRA-2 is too humid at all heights. SO cloud biases remain a
+substantial issue in the GSRM, but are an improvement over the lower-resolution
+reanalyses. Explicitly resolved convection and cloud processes were not enough
+to address the model cloud biases.
 
@@
 
-nextGEMS is a European Union--funded project \citep{nextgems} focused on the
+nextGEMS is a project \citep{nextgems} focused on the
 research and development of GSRMs at multiple modelling centres and
@@
 Model (FESOM) and Nucleus for European Modelling of the Ocean (NEMO) coupled
-with IFS.  The project has so far produced ICON and IFS simulations in three
-cycles (Cycle 1--3) and pre-final simulation, with a final production
-simulation planned by the end of the project. nextGEMS is not the only project
-developing GSRMs. Other GSRMs (or GSRM versions of climate models) currently in
+with IFS.  The project has so far produced ICON and IFS simulations with three
+development versions called Cycle 1--3 and a pre-final version, with a final production
+version planned by the end of the project. nextGEMS is not the only project
+developing GSRMs; other GSRMs (or GSRM versions of climate models) currently in
 development include: Convection-Permitting Simulations With the E3SM Global
@@
 SW and LW radiation. These properties are  in turn influenced by the
-atmospheric thermodynamics, convection and circulation, and indirect and direct
+atmospheric thermodynamics, convection and circulation, and both the indirect and direct
 effects of aerosols. Second order effects on SW and LW radiation are associated
@@
 \cite{nam2012}, \cite{klein2013}, and \cite{bender2017} in other regions and
-models. That is, a model maintains a reasonable SW radiation balance by
-reflecting too much SW radiation from clouds, but has too little cloudarea
-overall. A study by \cite{konsta2022} showed that this type of bias is still
+models, which means that a model can maintain a reasonable SW radiation balance by
+reflecting too much SW radiation from clouds, but these cover too small area.
+A study by \cite{konsta2022} showed that this type of bias is still
 present in six analysed CMIP6 models in tropical marine clouds, using the
@@
 \emph{Tangaroa} (© Peter Kuma, University of Canterbury), \textbf{(d)} Vaisala
-CL51 (© Jeff Aquilina, Bureau of Meteorology).
+CL51 (© Jeff Aquilina, Bureau of Meteorology), \textbf{(e)} Vaisala CT25K at
+Macquarie Island (© Simon P.\ Alexander, Australian Antarctic Division).
 }
@@
 vessel (RSV) \emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B.
-Palmer}, Her Majesty's New Zealand Ship (HMNZS) \emph{Wellington} and one
+Palmer}, Her (now His) Majesty's New Zealand Ship (HMNZS) \emph{Wellington} and one
 sub-Antarctic station (Macquarie Island) in the SO south of 40°S between 2010
@@
 voyages and station dataset comprised 2421 days of data south of 40°S, but the
-availability of ceilometer data was slightly smaller due to gaps in
+availability of ceilometer data was slightly shorter due to gaps in
 measurements.
@@
 The data sources contained ceilometer observations captured by the Vaisala CL51
-operating at a wavelength of 910 nm, the Vaisala CT25K operating at 905 nm, and
-the Lufft CHM 15k operating at 1064 nm, described in detail below (Sections
+and CT25K, and the Lufft CHM 15k, described in detail below (Sections
 \ref{sec:cl51} and \ref{sec:chm15k}). A ceilometer is a low-power near-infrared
@@
 is not attenuated by thick clouds, which can be used to infer additional
-information such as a cloud mask and cloud occurrence by height.
+information such as a cloud mask and cloud occurrence by height.  We note that
+during the MICRE campaign, the ceilometers Vaisala CT25K and CL51 were
+installed at the Macquarie Island station concurrently, but in our analysis we
+only used the CT25K data obtained from the Atmospheric Radiation Measurement
+(ARM) data archive.
 
@@
 
-The Vaisala CL51 (photo in Fig. \ref{fig:map}d) and CT25K are ceilometers
+The Vaisala CL51 and CT25K (photos in Fig. \ref{fig:map}d, e) are ceilometers
 operating at a near-infrared wavelength of 910 nm and 905 nm, respectively.
@@
 it is relatively zonally symmetric at all latitudes.  While both reanalysis and
-the model agree relatively well, differences in the strength of the local
-extremes of occurrence are notable, especially over the Amundsen Sea, which is
+the model agree relatively well, there are clear differences particularly in the highest occurence rate regions -- over the Amundsen Sea, which is
 more cyclonic in the reanalysis, and around Cape Adare, which is more cyclonic
@@
 \ref{fig:cloud-occurrence-panel}, the biases are relatively consistent across
-the data sources and longitudes. We conclude that the ICON results ch the observations better than the reanalyses in this metric.
+the data sources and longitudes. We conclude that the ICON results match the observations better than the reanalyses in this metric.
 
@@
 underestimate cloud occurrence above 1 km and near the surface. Non-cyclonic
-situations are similar to the general case.
+situations are similar to the general case, partially also because they form
+the majority of cases.
 
@@
 situations cloud occurrence peaks strongly at the surface in observations,
-compared to relatively unstable situations, where the peak is more obtuse
-and spread across the altitudes of 0--1 km.  In relatively stable
+compared to relatively unstable situations, where the peak is more diffuse
+between 0 and 1 km.  In relatively stable
 situations, the models do a fairly good job, but overestimate cloud
@@
 ICON or either reanalyses.  While ICON is closest to matching the observed distribution, it tends to be 1 okta
-clearer than the observations, peaking at 6 oktas, and highly underestimating
+clearer than the observations, peaking at 6 oktas, and substantially underestimating
 days with 8 oktas.  Overall, the reanalyses show results similar to each other,
@@
 \emph{Polarstern} voyages, MARCUS, NBP1704, TAN1702, and TAN1802. Spatially and
-temporally colocated profiles were taken from ICON and the reanalyses. Because
-the time period of the ICON model output was different from the observations,
-model time was chosen to be the same as the radiosonde launch time relative to
-the start of the year. The profiles were partitioned into the same subsets as
+temporally colocated profiles were taken from ICON and the reanalyses.
+Because the time period covered by the ICON model output (2021--2024) was
+different from the time period covered by the observations (2010--2021), when
+comparing with the model, we first had to remap the observation time to model
+time by taking the same time relative to the start of the year. Consequently,
+we also had four virtual/model profiles (one for each year of 2021--2024) for
+each observed profile.
+The profiles were partitioned into the same subsets as
 above (Sections \ref{sec:cloud-occurrence} and \ref{sec:cloud-cover}).  Apart
@@
 lower-resolution reanalyses is notable. More effort is needed to improve the
-model cloud simulations in this fast-changing and understudied region. However, this analysis suggests that the
+model cloud simulations in this understudied region. However, this analysis suggests that the
 transition from models with parametrised convection and clouds to
@@
 provided by the Royal New Zealand Navy and UC, the MARCUS dataset provided by
-the Atmospheric Radiation Measurement (ARM) and AAD, and the MICRE dataset
+ARM and AAD, and the MICRE dataset
 provided by ARM, the Australian Bureau of Meteorology, and AAD.  Technical,

### 2024-12-04 manuscript.tex
Update on Overleaf.

@@
 convection and clouds to be avoided, relying instead on explicitly resolved
-processes.  Standard-resolution models have substantial cloud biases over the
+processes, except for, among others, microphysics and turbulence.  Standard-resolution models have substantial cloud biases over the
 Southern Ocean (SO), affecting radiation and sea surface temperature.  We
@@
 strongly underestimate near-surface clouds or fog.  MERRA-2 tends to
-underestimate cloud occurrence at all heights. Less stable conditions are the
-most problematic for ICON and the reanalyses.  In daily cloud cover, ICON and
+underestimate cloud occurrence at all heights. Conditions of weak stability are associated with the largest errors in ICON and the reanalyses.  In daily cloud cover, ICON and
 the reanalyses tend to be about 1 and 2 oktas clearer, respectively. Compared
@@
 substantial issue in the GSRM, but are an improvement over the lower-resolution
-reanalyses. Explicitly resolved convection and cloud processes were not enough
+reanalyses. Explicitly resolved convection and cloud processes (except microphysics) were not enough
 to address the model cloud biases.
@@
 universities in Europe.  The project also develops GSRM versions of the
-Icosahedral Nonhydrostatic Weather and Climate Model (ICON), the Integrated
+Icosahedral Nonhydrostatic Weather and Climate Model (ICON; \cite{hohenegger2023}), the Integrated
 Forecasting System (IFS), and their ocean components at eddy-resolving
@@
 \ref{fig:cloud-occurrence-panel}, the biases are relatively consistent across
-the data sources and longitudes. We conclude that the ICON results match the observations better than the reanalyses in this metric.
+the data sources and longitudes. We conclude that the ICON results ch the observations better than the reanalyses in this metric.
 

### 2024-12-04 manuscript.tex
Fixing comments

@@
 Icosahedral Nonhydrostatic Weather and Climate Model (ICON; \cite{hohenegger2023}), the Integrated
-Forecasting System (IFS), and their ocean components at eddy-resolving
+Forecasting System [IFS; \cite{ifs2023}], and their ocean components at eddy-resolving
 resolutions: ICON-O coupled with ICON and Finite-Element/volumE Sea ice-Ocean

### 2024-12-04 manuscript.tex
Addressing comments

--- 2024-12-04 manuscript.tex
@@
 Icosahedral Nonhydrostatic Weather and Climate Model (ICON; \cite{hohenegger2023}), the Integrated
-Forecasting System (IFS), and their ocean components at eddy-resolving
-resolutions: ICON-O coupled with ICON and Finite-Element/volumE Sea ice-Ocean
-Model (FESOM) and Nucleus for European Modelling of the Ocean (NEMO) coupled
+Forecasting System [IFS; \cite{ifs2023}], and their ocean components at eddy-resolving
+resolutions: ICON-O \citep{korn2022} coupled with ICON and Finite-Element/volumE Sea ice-Ocean
+Model [FESOM; \cite{wang2014}] and Nucleus for European Modelling of the Ocean [NEMO; \cite{madec2023}] coupled
 with IFS.  The project has so far produced ICON and IFS simulations with three

### 2024-12-04 manuscript.tex
Update on Overleaf.

@@
 influence on the global climate, and the SO is an important part of the global
-ocean conveyor belt.  Marine clouds have a disproportionate effect on top of
+ocean conveyor belt. In general, marine clouds have a disproportionate effect on top of
 atmosphere (TOA) SW radiation due to the relatively low albedo of the sea
@@
 Interactions of both are also possible, for example SST affecting clouds and
-clouds affecting the surface radiation. \cite{zhang2023} have shown that SST
-biases have improved in CMIP6 compared to CMIP5 [relative to the European
-Centre for Medium-Range Weather Forecasts (ECMWF) Reanalysis 5; ERA5], with SST
+clouds affecting the surface radiation. Using the European
+Centre for Medium-Range Weather Forecasts (ECMWF) Reanalysis 5 (ERA5) as a reference, \cite{zhang2023} have shown that SST
+biases have improved in CMIP6 compared to CMIP5, with SST
 overall increasing in the later CMIP phase. However, over the SO this resulted
@@
 MICRE, 36 s for CL51 on RV \emph{Polarstern}, and about 2.37 s for CL51 with
-CL31 emulation on TAN1502. The wavelength of 910 nm is affected by water vapour
-absorption of about 20\% in the mid-latitudes \citep{wiegner2015,wiegner2019},
+CL31 emulation on TAN1502. The wavelengths of 905 and 910 nm are affected by water vapour
+absorption of about 20\% in the mid-latitudes \citep{wiegner2015,wiegner2019}, with 910 nm affected more strongly,
 but we do not expect this to be a significant issue as explained in
@@
 
-Here, we use a free-running (i.e., \emph{not} nudged or using prescribed SST)
+Here, we use a free-running (i.e., the weather situation in the model does not correspond to reality)
 coupled GSRM simulation made for the purpose of climate projection.  nextGEMS
@@
 version 5.12.4 of the Goddard Earth Observing System (GEOS) atmospheric model
-\citep{rienecker2008,molod2015}. The reanalysis output analysed here is
+\citep{rienecker2008,molod2015}.
+Non-convective clouds (condensation, autoconversion, and evaporation) are parametrised using a prognostic scheme \citep{bacmeister2006}, and sub-grid cloud fraction is determined using total water distribution and a critical relative humidity threshold.
+The reanalysis output analysed here is
 available at a spatial resolution of 0.5° of latitude and 0.625° of longitude,
@@
 \ref{fig:cloud-occurrence-panel}, the biases are relatively consistent across
-the data sources and longitudes. We conclude that the ICON results ch the observations better than the reanalyses in this metric.
+the data sources and longitudes. We conclude that the ICON results  the observations better than the reanalyses in this metric.
 

### 2024-12-04 manuscript.tex
Update on Overleaf.

@@
 ERA5 \citep{era5} is a reanalysis produced by the ECMWF.  It is based on a
-numerical weather prediction model IFS version CY41R2.  The horizontal
+numerical weather prediction model IFS version CY41R2.  It uses the \cite{tiedtke1993} prognostic cloud scheme and \cite{forbes2014} for mixed-phase clouds. The horizontal
 resolution is 0.25° in latitude and longitude, which is about 28 km in the
@@
 human-performed observations.
+The main ANN (`ANN` in Fig.
+\ref{fig:ann}) was trained on all data, and ancillary ANNs (`ANN2` in Fig \ref{fig:ann}) were trained on all data except for each voyage.
+These were used for testing the results relative to each voyage.
 
@@
 thresholds as well as tracking across time steps to identify cyclone centres
-and radii. With this information, we could classify geographical areas as
-either cyclonic or non-cyclonic. Due to a relatively small total area covered,
+and radii in each time step. With this information, we could classify geographical areas as
+either cyclonic or non-cyclonic. Due to a relatively small total area covered by cyclones (as identified by the cyclone centre and radius),
 we chose a circle of a double radius (relative to one identified by CyTRACK)
@@
 
-Here, we briefly describe the results of the cyclonic activity and stability
-distribution, which is relevant for the subsequent analysis, because these
-conditions are used for subsetting our dataset. Fig.
-\ref{fig:cyclone-stability}a, b show a geographical distribution of the fraction
+Fig. \ref{fig:cyclone-stability}a, b show a geographical distribution of the fraction
 of cyclonic days as determined by the cyclone tracking algorithm applied to the
@@
 it is relatively zonally symmetric at all latitudes.  While both reanalysis and
-the model agree relatively well, there are clear differences particularly in the highest occurence rate regions -- over the Amundsen Sea, which is
+the model agree relatively well, there are clear differences particularly in the highest occurrence rate regions -- over the Amundsen Sea, where the Amundsen Sea low is located \cite{turner2013} and which is
 more cyclonic in the reanalysis, and around Cape Adare, which is more cyclonic
@@
 \ref{sec:cyclone-stability}). Relatively unstable conditions are prevalent
-in the middle SO (50--65°S), which might be explained by the relatively cold
+in the mid-to-high SO (with respect to our SO partitioning; 50--65°S), which might be explained by the relatively cold
 near-surface air overlying the relatively warm sea surface. Relatively
@@
 
-We analysed about 2300 radiosonde profiles south of 40°S from the 24 RV
+In order to link the cloud biases to the local physical conditions, we analysed about 2300 radiosonde profiles south of 40°S from the 24 RV
 \emph{Polarstern} voyages, MARCUS, NBP1704, TAN1702, and TAN1802. Spatially and
@@
 one can expect the results to be slightly different due to reasons unrelated to
-model biases, such as different weather conditions and the phase of climate
+model biases, such as different weather conditions, partially accounted for by the cyclone and stability subsetting, and the phase of climate
 oscillations such as the ENSO in the observations and the model.

### 2024-12-04 manuscript.tex
Update on Overleaf.

@@
 underestimation of cloud occurrence below 2 km relative to ground-based lidar
-observations \citep{mcerlich2021}.  This, in turn, can lead to systematic
+observations \citep{mcerlich2021}.  We hypothesise that this, in turn, can lead to systematic
 biases in low clouds in climate models, which are frequently evaluated against
@@
 
-When subsetted by low- and high-latitude SO zones (Fig.
+When subsetted by latitude (Fig.
 \ref{fig:cloud-occurrence}b, c), we see that the low-latitude SO zone displays

### 2024-12-04 manuscript.tex
Update on Overleaf.

@@
 In general, sea surface temperature (SST) biases in the SO can originate either
-in the atmosphere, caused by too much shortwave heating of the surface, too
+in the atmosphere \citep{hyder2018}, caused by too much shortwave heating of the surface, too
 little longwave cooling of the surface, or in the ocean circulation.
@@
 expected, the strongest cyclonic activity is in the high-latitude SO zone, and
-it is relatively zonally symmetric at all latitudes.  While both reanalysis and
+it is relatively zonally symmetric at all latitudes.  The pattern matches reasonably well with \cite{hoskins2005}. While both reanalysis and
 the model agree relatively well, there are clear differences particularly in the highest occurrence rate regions -- over the Amundsen Sea, where the Amundsen Sea low is located \cite{turner2013} and which is
@@
 surface, among other factors responsible for SO SST biases in climate models
-\citep{zhang2023,luo2023}.
+\citep{zhang2023,luo2023,hyder2018}.
 

### 2024-12-04 manuscript.tex
Update on Overleaf.
Addressing comments

@@
 \subsection{ICON}
+\label{sec:icon}
 
@@
 resolution of ngc3028 is about 5 km.  The model output is available on 90
-vertical levels and 3-hourly instantaneous temporal resolution.  Unlike current
-general circulation models (GCMs), the storm-resolving version of ICON does not
-use convective and cloud parameterization but relies on explicit simulation of
-convection and clouds on the model grid. While this makes the code development
-simpler without having to rely on uncertain parameterizations, it can miss
-smaller-scale clouds below the grid resolution.  Turbulence and cloud
-microphysics are still parameterized in this model.
+vertical levels and 3-hourly instantaneous temporal resolution.
+
+Unlike current general circulation models (GCMs), the storm-resolving version
+of ICON does not use convective and cloud parameterization but relies on
+explicit simulation of convection and clouds on the model grid. While this
+makes the code development simpler without having to rely on uncertain
+parameterizations, it can miss smaller-scale clouds below the grid resolution.
+Turbulence and cloud microphysics are still parameterized in this model. To
+account for the radiative effects of subgrid-scale clouds, a cloud
+inhomogeneity factor is introduced in the model which scales down the cloud
+liquid water for radiative calculations. It ranges from 0.4 at lower
+tropospheric stability (LTS) of 0 K to 0.8 at 30 K. In addition, vertical
+mixing is enhanced in unstable and humid lower-tropospheric conditions, which
+reduces the amount of shallow clouds.
 
@@
 In addition to the above, we partitioned our data into two mutually exclusive
-subsets based on lower tropospheric stability (LTS), which is derived as the difference between the potential temperature at 700 hPa
+subsets based on LTS, which is derived as the difference between the potential temperature at 700 hPa
 and the surface.  Based on a histogram of LTS in ERA5 and MERRA-2 calculated at
@@
 than observations, and the deficit of outgoing TOA SW radiation is
-approximately proportional to the deficit of the total cloud fraction. While this
-might be a welcome feature and an improvement over previous models, it does
-mean that the outgoing TOA SW radiation is overall underestimated instead of
-being compensated by a higher cloud albedo. This can, of course, lead to
+approximately proportional to the deficit of the total cloud fraction. While
+this might be a welcome feature and an improvement over previous models, it
+does mean that the outgoing TOA SW radiation is overall underestimated instead
+of being compensated by a higher cloud albedo.  This can, of course, lead to
 undesirable secondary effects such as overestimated solar heating of the sea
 surface, among other factors responsible for SO SST biases in climate models
-\citep{zhang2023,luo2023,hyder2018}.
+\citep{zhang2023,luo2023,hyder2018}.  To some extent, the cloud albedo might be
+reduced in the model artifically by the application of an inhomogeneity factor
+to lower cloud liquid water in the radiative transfer calculations (Sec.
+\ref{sec:icon}).
 

### 2024-12-05 manuscript.tex
Addressing comments

@@
 
-The main aim of this study is to evaluate the GSRM version of ICON, developed
-jointly by nextGEMS, Deutscher Wetterdienst, Max-Planck-Institute for
+The main aim of this study is to evaluate the GSRM version of ICON. ICON developed and maintained
+jointly by Deutscher Wetterdienst, Max-Planck-Institute for
 Meteorology, Deutsches Klimarechenzentrum (DKRZ), Karlsruhe Institute of
@@
 of ICON does not use convective and cloud parameterization but relies on
-explicit simulation of convection and clouds on the model grid. While this
-makes the code development simpler without having to rely on uncertain
-parameterizations, it can miss smaller-scale clouds below the grid resolution.
-Turbulence and cloud microphysics are still parameterized in this model. To
-account for the radiative effects of subgrid-scale clouds, a cloud
+explicit simulation of convection and clouds on the model grid. Subgrid-scale
+clouds are not resolved, and the grid cell cloud fraction is always either 0 or
+100\%. While this makes the code development simpler without having to rely on
+uncertain parameterizations, it can miss smaller-scale clouds below the grid
+resolution.  Turbulence and cloud microphysics are still parameterized in this
+model. To account for the radiative effects of subgrid-scale clouds, a cloud
 inhomogeneity factor is introduced in the model which scales down the cloud
@@
 }
-\caption{Cloud occurrence by height for the 31 voyages and one sub-Antarctic
-station (MICRE) in observations (OBS) and simulated by the ALCF from the
-ICON model, MERRA‐2 (M2), and ERA5 reanalysis data. The numbers in the legend
-indicate the total cloud fraction and the number of days of data.}
+\caption{
+Cloud occurrence by height for the 31 voyages and one sub-Antarctic
+station (MICRE) in observations (O) and simulated by the ALCF from the ICON
+model (I), MERRA‐2 (M), and ERA5 reanalysis data (E). The numbers in the legend
+indicate the total cloud fraction and the number of days of data.
+}
 \label{fig:cloud-occurrence-panel}

### 2024-12-06 manuscript.tex
Addressing comments

@@
 Among them is a 5-km version of the Icosahedral Nonhydrostatic Weather and
-Climate Model (ICON). The high resolution allows for parameterizations of
-convection and clouds to be avoided, relying instead on explicitly resolved
-processes, except for, among others, microphysics and turbulence.  Standard-resolution models have substantial cloud biases over the
-Southern Ocean (SO), affecting radiation and sea surface temperature.  We
-evaluated SO clouds in ICON and the ERA5 and MERRA-2 reanalyses.  The SO is
-dominated by low clouds, which cannot be observed accurately from space due to
-overlapping clouds, attenuation, and ground clutter.  Instead, we analysed
-about 2400 days of lidar observations from 31 voyages and a station during
-2010--2021 using a ground-based lidar simulator.  ICON and the reanalyses
-underestimate the total cloud fraction by about 10 and 20\%, respectively. ICON
-and ERA5 overestimate the cloud occurrence peak at about 500 m, potentially
-explained by their lifting condensation levels being too high.  The reanalyses
-strongly underestimate near-surface clouds or fog.  MERRA-2 tends to
-underestimate cloud occurrence at all heights. Conditions of weak stability are associated with the largest errors in ICON and the reanalyses.  In daily cloud cover, ICON and
-the reanalyses tend to be about 1 and 2 oktas clearer, respectively. Compared
-to radiosondes, potential temperature is accurate in the reanalyses, but ICON
-underestimates stability over the low-latitude SO and too humid in the boundary
-layer. MERRA-2 is too humid at all heights. SO cloud biases remain a
-substantial issue in the GSRM, but are an improvement over the lower-resolution
-reanalyses. Explicitly resolved convection and cloud processes (except microphysics) were not enough
+Climate Model (ICON). The high resolution means that parameterizations of
+convection and clouds including subgrid-scale clouds are forgone, relying on
+explicit their simulation, but still using microphysics and turbulence
+parametrization.  Standard-resolution (10--100-km) models, which use
+subgrid-scale convection and cloud parametrization, have substantial cloud
+biases over the Southern Ocean (SO), affecting radiation and sea surface
+temperature.  We evaluated SO clouds in ICON and the ERA5 and MERRA-2
+reanalyses.  The SO is dominated by low clouds, which cannot be observed
+accurately from space due to overlapping clouds, attenuation, and ground
+clutter.  Instead, we analysed about 2400 days of lidar observations from 31
+voyages and a station during 2010--2021 using a ground-based lidar simulator.
+ICON and the reanalyses underestimate the total cloud fraction by about 10 and
+20\%, respectively. ICON and ERA5 overestimate the cloud occurrence peak at
+about 500 m, potentially explained by their lifting condensation levels being
+too high.  The reanalyses strongly underestimate near-surface clouds or fog.
+MERRA-2 tends to underestimate cloud occurrence at all heights.  In daily cloud
+cover, ICON and the reanalyses tend to be about 1 and 2 oktas clearer,
+respectively.  Conditions of weak stability are associated with the largest
+errors in ICON and the reanalyses.  Compared to radiosondes, potential
+temperature is accurate in the reanalyses, but ICON underestimates stability
+over the low-latitude SO and too humid in the boundary layer. MERRA-2 is too
+humid at all heights. SO cloud biases remain a substantial issue in the GSRM,
+but are an improvement over the lower-resolution reanalyses. Explicitly
+resolved convection and cloud processes (except microphysics) were not enough
 to address the model cloud biases.
@@
 
-nextGEMS is a project \citep{nextgems} focused on the
-research and development of GSRMs at multiple modelling centres and
-universities in Europe.  The project also develops GSRM versions of the
-Icosahedral Nonhydrostatic Weather and Climate Model (ICON; \cite{hohenegger2023}), the Integrated
-Forecasting System [IFS; \cite{ifs2023}], and their ocean components at eddy-resolving
-resolutions: ICON-O \citep{korn2022} coupled with ICON and Finite-Element/volumE Sea ice-Ocean
-Model [FESOM; \cite{wang2014}] and Nucleus for European Modelling of the Ocean [NEMO; \cite{madec2023}] coupled
-with IFS.  The project has so far produced ICON and IFS simulations with three
-development versions called Cycle 1--3 and a pre-final version, with a final production
+nextGEMS is a project \citep{nextgems} focused on the research and development
+of GSRMs at multiple modelling centres and universities in Europe.  The project
+also develops GSRM versions of the Icosahedral Nonhydrostatic Weather and
+Climate Model (ICON; \cite{hohenegger2023}), the Integrated Forecasting System
+[IFS; \cite{ifs2023}], and their ocean components at eddy-resolving
+resolutions: ICON-O \citep{korn2022} coupled with ICON and
+Finite-Element/volumE Sea ice-Ocean Model [FESOM; \cite{wang2014}] and Nucleus
+for European Modelling of the Ocean [NEMO; \cite{madec2023}] coupled with IFS.
+The project has so far produced ICON and IFS simulations with three development
+versions called Cycle 1--3 and a pre-final version, with a final production
 version planned by the end of the project. nextGEMS is not the only project
@@
 SW and LW radiation. These properties are  in turn influenced by the
-atmospheric thermodynamics, convection and circulation, and both the indirect and direct
-effects of aerosols. Second order effects on SW and LW radiation are associated
-with the cloud droplet size distribution, ice crystal habit, cloud lifetime,
-and direct radiative interaction with aerosols.  In the 6$^\mathrm{th}$ phase
-of the Coupled Model Intercomparison Project [CMIP6; \cite{eyring2016}], the
-cloud feedback has increased relative to CMIP5 \citep{zelinka2020}, which is
-one of the main reasons for the higher climate sensitivity of CMIP6 models.
+atmospheric thermodynamics, convection and circulation, and both the indirect
+and direct effects of aerosols. Second order effects on SW and LW radiation are
+associated with the cloud droplet size distribution, ice crystal habit, cloud
+lifetime, and direct radiative interaction with aerosols.  In the
+6$^\mathrm{th}$ phase of the Coupled Model Intercomparison Project [CMIP6;
+\cite{eyring2016}], the cloud feedback has increased relative to CMIP5
+\citep{zelinka2020}, which is one of the main reasons for the higher climate
+sensitivity of CMIP6 models.
 
@@
 radiation biases and changes over an area of its size have a substantial
-influence on the global climate, and the SO is an important part of the global
-ocean conveyor belt. In general, marine clouds have a disproportionate effect on top of
+influence on the global climate, such as affecting the Earth radiation balance
+and carbon cycle, and the SO is an important part of the global ocean conveyor
+belt. In general, marine clouds have a disproportionate effect on top of
 atmosphere (TOA) SW radiation due to the relatively low albedo of the sea
@@
 \cite{nam2012}, \cite{klein2013}, and \cite{bender2017} in other regions and
-models, which means that a model can maintain a reasonable SW radiation balance by
-reflecting too much SW radiation from clouds, but these cover too small area.
-A study by \cite{konsta2022} showed that this type of bias is still
+models, which means that a model can maintain a reasonable SW radiation balance
+by reflecting too much SW radiation from clouds, but these cover too small
+area.  A study by \cite{konsta2022} showed that this type of bias is still
 present in six analysed CMIP6 models in tropical marine clouds, using the
@@
 on the order of 30\% [relative to Moderate Resolution Imaging Spectroradiometer
-(MODIS) data] and overestimates downwelling TOA SW radiation by
-approximately 10 Wm$^\mathrm{-2}$ [relative to the Clouds and the Earth’s
-Radiant Energy System (CERES) data] in the highest model resolution run (2.5
-km).  \cite{zhao2022} reported a similar SW radiation bias in five analysed
-CMIP6 models over high-latitude SO and the total cloud fraction underestimation
-on the order of 10\% over the entire 40--60°S SO. Recently, \cite{ramadoss2024}
+(MODIS) data] and overestimates downwelling TOA SW radiation by approximately
+10 Wm$^\mathrm{-2}$ [relative to the Clouds and the Earth’s Radiant Energy
+System (CERES) data] in the highest model resolution run (2.5 km).
+\cite{zhao2022} reported a similar SW radiation bias in five analysed CMIP6
+models over high-latitude SO and the total cloud fraction underestimation on
+the order of 10\% over the entire 40--60°S SO. Recently, \cite{ramadoss2024}
 analysed 48 hours of km-scale ICON limited area model NWP simulations over a SO
@@
 In general, sea surface temperature (SST) biases in the SO can originate either
-in the atmosphere \citep{hyder2018}, caused by too much shortwave heating of the surface, too
-little longwave cooling of the surface, or in the ocean circulation.
-Interactions of both are also possible, for example SST affecting clouds and
-clouds affecting the surface radiation. Using the European
-Centre for Medium-Range Weather Forecasts (ECMWF) Reanalysis 5 (ERA5) as a reference, \cite{zhang2023} have shown that SST
-biases have improved in CMIP6 compared to CMIP5, with SST
-overall increasing in the later CMIP phase. However, over the SO this resulted
-in an even higher positive bias, especially in the Atlantic Ocean (AO) sector
-of the SO, increasing by up to 1°C.  \cite{luo2023} identified that the SO SST
-bias in an ensemble of 18 CMIP6 models originates not from the surface heat and
-radiation fluxes (using reanalyses as a reference), but from a warm bias in the
-Northern Atlantic Deep Water.
-
-The main aim of this study is to evaluate the GSRM version of ICON. ICON developed and maintained
-jointly by Deutscher Wetterdienst, Max-Planck-Institute for
-Meteorology, Deutsches Klimarechenzentrum (DKRZ), Karlsruhe Institute of
-Technology, and the Center for Climate Systems Modeling.  Previous studies have
-identified substantial large-scale biases in climate model clouds over the SO,
-affecting sea surface temperature and the Earth’s albedo. Our aim is to
-quantify how well the GSRM ICON is simulating clouds in this region,
-particularly in light of the fact that subgrid-scale clouds and convection are
-not parameterized in this model. This region is mostly dominated by boundary
-layer clouds generated by shallow convection, and these are problematic to
-observe by spaceborne lidars and radars, which are affected by attenuation by
-overlapping and thick clouds and ground clutter, respectively.  Specifically,
-the radar on CloudSat and lidar on CALIPSO (neither of which are nowoperational) are affected by the abovementioned issues, resulting in a strong
-underestimation of cloud occurrence below 2 km relative to ground-based lidar
-observations \citep{mcerlich2021}.  We hypothesise that this, in turn, can lead to systematic
-biases in low clouds in climate models, which are frequently evaluated against
-CloudSat--CALIPSO products. Reanalyses can also suffer from cloud biases, as
-these are usually parametrised in their atmospheric component, and also in
-regions where input observations are sparse.  This makes them a problematic
-reference for clouds over the SO, and any biases relative to a reanalysis
-should be interpreted with caution. Instead, we chose to use a large set of
-ship-based observations conducted with ceilometers and lidars on board of the
-RV \emph{Polarstern} and other voyages and stations as a reference for the
-model evaluation.
+in the atmosphere \citep{hyder2018}, caused by too much shortwave heating of
+the surface, too little longwave cooling of the surface, or in the ocean
+circulation.  Interactions of both are also possible, for example SST affecting
+clouds and clouds affecting the surface radiation. Using the European Centre
+for Medium-Range Weather Forecasts (ECMWF) Reanalysis 5 (ERA5) as a reference,
+\cite{zhang2023} have shown that SST biases have improved in CMIP6 compared to
+CMIP5, with SST overall increasing in the later CMIP phase. However, over the
+SO this resulted in an even higher positive bias, especially in the Atlantic
+Ocean (AO) sector of the SO, increasing by up to 1°C.  \cite{luo2023}
+identified that the SO SST bias in an ensemble of 18 CMIP6 models originates
+not from the surface heat and radiation fluxes (using reanalyses as a
+reference), but from a warm bias in the Northern Atlantic Deep Water.
+
+The main aim of this study is to evaluate the GSRM version of ICON. ICON
+developed and maintained jointly by Deutscher Wetterdienst,
+Max-Planck-Institute for Meteorology, Deutsches Klimarechenzentrum (DKRZ),
+Karlsruhe Institute of Technology, and the Center for Climate Systems Modeling.
+Previous studies have identified substantial large-scale biases in climate
+model clouds over the SO, affecting sea surface temperature and the Earth’s
+albedo. Our aim is to quantify how well the GSRM ICON is simulating clouds in
+this region, particularly in light of the fact that subgrid-scale clouds and
+convection are not parameterized in this model. This region is mostly dominated
+by boundary layer clouds generated by shallow convection, and these are
+problematic to observe by spaceborne lidars and radars, which are affected by
+attenuation by overlapping and thick clouds and ground clutter, respectively.
+Specifically, the radar on CloudSat and lidar on CALIPSO (neither of which are
+nowoperational) are affected by the abovementioned issues, resulting in a
+strong underestimation of cloud occurrence below 2 km relative to ground-based
+lidar observations \citep{mcerlich2021}.  We hypothesise that this, in turn,
+can lead to systematic biases in low clouds in climate models, which are
+frequently evaluated against CloudSat--CALIPSO products. Reanalyses can also
+suffer from cloud biases, as these are usually parametrised in their
+atmospheric component, and also in regions where input observations are sparse.
+This makes them a problematic reference for clouds over the SO, and any biases
+relative to a reanalysis should be interpreted with caution. Instead, we chose
+to use a large set of ship-based observations conducted with ceilometers and
+lidars on board of the RV \emph{Polarstern} and other voyages and stations as a
+reference for the model evaluation.
 
@@
 
-Together, we analysed data from 31 voyages of RV \emph{Polarstern}, the resupply
-vessel (RSV) \emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B.
-Palmer}, Her (now His) Majesty's New Zealand Ship (HMNZS) \emph{Wellington} and one
-sub-Antarctic station (Macquarie Island) in the SO south of 40°S between 2010
-and 2021. Fig. \ref{fig:map} shows a map of the voyages, Table
-\ref{tab:voyages} list the voyages, campaigns, and stations, and Table
-\ref{tab:voyage-references} lists references where available. Altogether, the
-voyages and station dataset comprised 2421 days of data south of 40°S, but the
-availability of ceilometer data was slightly shorter due to gaps in
+Together, we analysed data from 31 voyages of RV \emph{Polarstern}, the
+resupply vessel (RSV) \emph{Aurora Australis}, RV \emph{Tangaroa}, RV
+\emph{Nathaniel B.  Palmer}, Her (now His) Majesty's New Zealand Ship (HMNZS)
+\emph{Wellington} and one sub-Antarctic station (Macquarie Island) in the SO
+south of 40°S between 2010 and 2021. Fig. \ref{fig:map} shows a map of the
+voyages, Table \ref{tab:voyages} list the voyages, campaigns, and stations, and
+Table \ref{tab:voyage-references} lists references where available. Altogether,
+the voyages and station dataset comprised 2421 days of data south of 40°S, but
+the availability of ceilometer data was slightly shorter due to gaps in
 measurements.
@@
 operating at a near-infrared wavelength of 910 nm and 905 nm, respectively.
-The CL51 can also be configured to emulate the Vaisala CL31. The maximum range is
-15.4 km (CL51), 7.7 km (CL31 emulation mode with 5 m vertical resolution), and
-7.5 km (CT25K). The vertical resolution is 10 m (5 m configurable) in CL51 and
-30 m in CT25K observations. The sampling (temporal) resolution is configurable, and in our
-datasets is approximately 6 s for CL51 on AA15‐16, 16 s for CT25K on MARCUS and
-MICRE, 36 s for CL51 on RV \emph{Polarstern}, and about 2.37 s for CL51 with
-CL31 emulation on TAN1502. The wavelengths of 905 and 910 nm are affected by water vapour
-absorption of about 20\% in the mid-latitudes \citep{wiegner2015,wiegner2019}, with 910 nm affected more strongly,
-but we do not expect this to be a significant issue as explained in
+The CL51 can also be configured to emulate the Vaisala CL31. The maximum range
+is 15.4 km (CL51), 7.7 km (CL31 emulation mode with 5 m vertical resolution),
+and 7.5 km (CT25K). The vertical resolution is 10 m (5 m configurable) in CL51
+and 30 m in CT25K observations. The sampling (temporal) resolution is
+configurable, and in our datasets is approximately 6 s for CL51 on AA15‐16, 16
+s for CT25K on MARCUS and MICRE, 36 s for CL51 on RV \emph{Polarstern}, and
+about 2.37 s for CL51 with CL31 emulation on TAN1502. The wavelengths of 905
+and 910 nm are affected by water vapour absorption of about 20\% in the
+mid-latitudes \citep{wiegner2015,wiegner2019}, with 910 nm affected more
+strongly, but we do not expect this to be a significant issue as explained in
 \cite{kuma2021}.  The instrument data files containing raw uncalibrated
@@
 NetCDF files containing uncalibrated backscatter produced by the instrument
-were processed with the ALCF (Section \ref{sec:alcf}) to again produce AVBC, cloud
-mask, cloud occurrence by height, and the total cloud fraction. The CHM 15k was
-used on four voyages (HMNZSW16, TAN1702, TAN1802, and NBP1704).
+were processed with the ALCF (Section \ref{sec:alcf}) to again produce AVBC,
+cloud mask, cloud occurrence by height, and the total cloud fraction. The CHM
+15k was used on four voyages (HMNZSW16, TAN1702, TAN1802, and NBP1704).
 
@@
 calculations to derive equivalent lidar AVBC in an atmospheric model, which can
-then be compared with observed AVBC. For this purpose, it takes the cloud fraction, liquid and ice mass mixing ratio, temperature, and
-pressure model fields as an input and is run offline (on the model output rather than
-inside the model code). The lidar simulator in the ALCF is based on the
-instrument simulator Cloud Feedback Model Intercomparison Project (CFMIP)
-Observation Simulator Package (COSP) \citep{bodas-salcedo2011}.  After AVBC is
-calculated, a cloud mask, cloud occurrence by height, and the total cloud
-fraction are determined. The ALCF has been used by several research teams for
-model and reanalysis evaluation
+then be compared with observed AVBC. For this purpose, it takes the cloud
+fraction, liquid and ice mass mixing ratio, temperature, and pressure model
+fields as an input and is run offline (on the model output rather than inside
+the model code). The lidar simulator in the ALCF is based on the instrument
+simulator Cloud Feedback Model Intercomparison Project (CFMIP) Observation
+Simulator Package (COSP) \citep{bodas-salcedo2011}.  After AVBC is calculated,
+a cloud mask, cloud occurrence by height, and the total cloud fraction are
+determined. The ALCF has been used by several research teams for model and
+reanalysis evaluation
 \citep{kuma2020,kremser2021,guyot2022,pei2023,whitehead2023,mcdonald2024}.
@@
 
-Here, we use a free-running (i.e., the weather situation in the model does not correspond to reality)
-coupled GSRM simulation made for the purpose of climate projection.  nextGEMS
-has so far produced four cycles of model runs. We used a Cycle 3 run
-\emph{ngc3028} produced in 2023 \citep{nextgems2023a,nextgems2023b} for a model
-time period of 20 January 2020 to 22 July 2025, of which we analysed the period 2021--2024 (inclusive). While a Cycle 4 run was available, we could not
-use it due to a lack of availability of the necessary variables. The horizontal
-resolution of ngc3028 is about 5 km.  The model output is available on 90
-vertical levels and 3-hourly instantaneous temporal resolution.
+Here, we use a free-running (i.e., the weather situation in the model does not
+correspond to reality) coupled GSRM simulation made for the purpose of climate
+projection.  nextGEMS has so far produced four cycles of model runs. We used a
+Cycle 3 run \emph{ngc3028} produced in 2023 \citep{nextgems2023a,nextgems2023b}
+for a model time period of 20 January 2020 to 22 July 2025, of which we
+analysed the period 2021--2024 (inclusive). While a Cycle 4 run was available,
+we could not use it due to a lack of availability of the necessary variables.
+The horizontal resolution of ngc3028 is about 5 km.  The model output is
+available on 90 vertical levels and 3-hourly instantaneous temporal resolution.
 
@@
 version 5.12.4 of the Goddard Earth Observing System (GEOS) atmospheric model
-\citep{rienecker2008,molod2015}.
-Non-convective clouds (condensation, autoconversion, and evaporation) are parametrised using a prognostic scheme \citep{bacmeister2006}, and sub-grid cloud fraction is determined using total water distribution and a critical relative humidity threshold.
-The reanalysis output analysed here is
-available at a spatial resolution of 0.5° of latitude and 0.625° of longitude,
-which is about 56 km in the North--South direction and 35 km in the East--West
-direction at 60°S. The number of vertical model levels is 72. Here, we use the
-following products: 1-hourly instantaneous 2D single-level diagnostics
-(M2I1NXASM) for 2-m temperature and humidity; 3-hourly instantaneous 3D
-assimilated meteorological fields (M2I3NVASM) for cloud quantities, pressure,
-and temperature; 1-hourly average 2D surface flux diagnostics (M2T1NXFLX) for
-precipitation; and 1-hourly average 2D radiation diagnostics
-(M2T1NXRAD) for radiation quantities \citep{merra2}.
+\citep{rienecker2008,molod2015}. Non-convective clouds (condensation,
+autoconversion, and evaporation) are parametrised using a prognostic scheme
+\citep{bacmeister2006}, and sub-grid cloud fraction is determined using total
+water distribution and a critical relative humidity threshold. The reanalysis
+output analysed here is available at a spatial resolution of 0.5° of latitude
+and 0.625° of longitude, which is about 56 km in the North--South direction and
+35 km in the East--West direction at 60°S. The number of vertical model levels
+is 72. Here, we use the following products: 1-hourly instantaneous 2D
+single-level diagnostics (M2I1NXASM) for 2-m temperature and humidity; 3-hourly
+instantaneous 3D assimilated meteorological fields (M2I3NVASM) for cloud
+quantities, pressure, and temperature; 1-hourly average 2D surface flux
+diagnostics (M2T1NXFLX) for precipitation; and 1-hourly average 2D radiation
+diagnostics (M2T1NXRAD) for radiation quantities \citep{merra2}.
 
@@
 ERA5 \citep{era5} is a reanalysis produced by the ECMWF.  It is based on a
-numerical weather prediction model IFS version CY41R2.  It uses the \cite{tiedtke1993} prognostic cloud scheme and \cite{forbes2014} for mixed-phase clouds. The horizontal
-resolution is 0.25° in latitude and longitude, which is about 28 km in the
-North--South direction and 14 km in the East--West direction at 60°S.
-Internally, the model uses 137 vertical levels. Here, we use output at 1-hourly
-instantaneous time intervals, except for radiation quantities, which are
-accumulations (from these we calculate daily means).  Vertically resolved
-quantities are made available on 37 pressure levels.
+numerical weather prediction model IFS version CY41R2.  It uses the
+\cite{tiedtke1993} prognostic cloud scheme and \cite{forbes2014} for
+mixed-phase clouds. The horizontal resolution is 0.25° in latitude and
+longitude, which is about 28 km in the North--South direction and 14 km in the
+East--West direction at 60°S.  Internally, the model uses 137 vertical levels.
+Here, we use output at 1-hourly instantaneous time intervals, except for
+radiation quantities, which are accumulations (from these we calculate daily
+means).  Vertically resolved quantities are made available on 37 pressure
+levels.
 
@@
 
-TOA radiation quantities are taken from the CERES instruments onboard the
-Terra and Aqua satellites \citep{wielicki1996,loeb2018}. In our analysis we
-used the adjusted all sky SW and LW upwelling fluxes at TOA from the synoptic
-TOA and surface fluxes and clouds 1 degree daily edition 4A product
+TOA radiation quantities are taken from the CERES instruments onboard the Terra
+and Aqua satellites \citep{wielicki1996,loeb2018}. In our analysis we used the
+adjusted all sky SW and LW upwelling fluxes at TOA from the synoptic TOA and
+surface fluxes and clouds 1 degree daily edition 4A product
 (CER\_SYN1deg-Day\_Terra-Aqua-MODIS\_Edition4A)
@@
 Radiation calculations presented in the results (Section \ref{sec:results})
-were completed such that they always represent daily means in order to be consistent with the CERES SYN1deg data. Therefore, every instantaneous profile in the
-simulated lidar data was assigned a daily mean radiation value corresponding to
-the day (in the Coordinated Universal Time; UTC). In turn, the average
-radiation during the entire voyage or station observation period were
+were completed such that they always represent daily means in order to be
+consistent with the CERES SYN1deg data. Therefore, every instantaneous profile
+in the simulated lidar data was assigned a daily mean radiation value
+corresponding to the day (in the Coordinated Universal Time; UTC). In turn, the
+average radiation during the entire voyage or station observation period were
 calculated as the average of the profile values. In the observed lidar data,
@@
 ratios). The required radiation calculations for precipitation are also
-currently not implemented in the ALCF, even though this is a planned future addition.
-In order to achieve a fair comparison of observations with model output, we
-exclude observed and simulated lidar profiles with precipitation either
-manually or using an automated method. It is relatively difficult to
+currently not implemented in the ALCF, even though this is a planned future
+addition.  In order to achieve a fair comparison of observations with model
+output, we exclude observed and simulated lidar profiles with precipitation
+either manually or using an automated method. It is relatively difficult to
 distinguish precipitation backscatter from cloud backscatter in lidar
@@
 channel are available. In models, the same can be accomplished relatively
-easily by excluding profiles exceeding a certain surface
-precipitation flux. In the observations, using precipitation flux measurements
-from rain gauges can be very unreliable on ships due to ship movement,
-turbulence caused by nearby ship structures, and sea spray. Our analysis of
-rain gauge data from the RV \emph{Tangaroa} showed large discrepancies between
-the rain gauge time series and human-performed synoptic observations, as well
-as large inconsistencies in the rain gauge time series. Human-performed
-observations of precipitation presence or absence are expected to be reliable
-but only cover a limited set of times. Therefore, it was desirable to
-implement a method of detecting precipitation from observed backscatter
-profiles alone.
+easily by excluding profiles exceeding a certain surface precipitation flux. In
+the observations, using precipitation flux measurements from rain gauges can be
+very unreliable on ships due to ship movement, turbulence caused by nearby ship
+structures, and sea spray. Our analysis of rain gauge data from the RV
+\emph{Tangaroa} showed large discrepancies between the rain gauge time series
+and human-performed synoptic observations, as well as large inconsistencies in
+the rain gauge time series. Human-performed observations of precipitation
+presence or absence are expected to be reliable but only cover a limited set of
+times. Therefore, it was desirable to implement a method of detecting
+precipitation from observed backscatter profiles alone.
 
@@
 \ref{fig:ann}d shows examples of the predicted precipitation compared to
-human-performed observations.
-The main ANN (`ANN` in Fig.
-\ref{fig:ann}) was trained on all data, and ancillary ANNs (`ANN2` in Fig \ref{fig:ann}) were trained on all data except for each voyage.
-These were used for testing the results relative to each voyage.
+human-performed observations. The main ANN (`ANN` in Fig. \ref{fig:ann}) was
+trained on all data, and ancillary ANNs (`ANN2` in Fig \ref{fig:ann}) were
+trained on all data except for each voyage. These were used for testing the
+results relative to each voyage.
 
@@
 the highest instantaneous temporal resolution data available. Shown is also the
-chosen dividing threshold of 12 K for relatively stable and unstable
-conditions.
+chosen dividing threshold of 12 K for conditions weak and strong stability.
 }
@@
 thresholds as well as tracking across time steps to identify cyclone centres
-and radii in each time step. With this information, we could classify geographical areas as
-either cyclonic or non-cyclonic. Due to a relatively small total area covered by cyclones (as identified by the cyclone centre and radius),
-we chose a circle of a double radius (relative to one identified by CyTRACK)
-centred at the cyclone centre as a cyclonic area for every time step and
-cyclone. All other areas were identified as non-cyclonic. For identifying
+and radii in each time step. With this information, we could classify
+geographical areas as either cyclonic or non-cyclonic. Due to a relatively
+small total area covered by cyclones (as identified by the cyclone centre and
+radius), we chose a circle of a double radius (relative to one identified by
+CyTRACK) centred at the cyclone centre as a cyclonic area for every time step
+and cyclone. All other areas were identified as non-cyclonic. For identifying
 cyclones in the observations and the reanalyses, ERA5 pressure and wind fields
@@
 were used as the input to CyTRACK, because the model is free-running, and thus
-the pressure and wind fields are different from reality.
+the pressure and wind fields are different from reality. Subsetting by
+proximity to cyclones is a relatively crude measure because it does not take
+into account the different sectors of cyclones, which are commonly associated
+with different weather situations. However, this was a choice made for
+simplicity of the analysis, given the amount of data.
 
 In addition to the above, we partitioned our data into two mutually exclusive
-subsets based on LTS, which is derived as the difference between the potential temperature at 700 hPa
-and the surface.  Based on a histogram of LTS in ERA5 and MERRA-2 calculated at
-all voyage tracks and stations (Fig.  \ref{fig:lts}), we determined a dividing
-threshold of 12 K for relatively unstable (< 12 K) and relatively stable (>= 12
-K) conditions.
+subsets based on LTS, which is derived as the difference between the potential
+temperature at 700 hPa and the surface.  Based on a histogram of LTS in ERA5
+and MERRA-2 calculated at all voyage tracks and stations (Fig.  \ref{fig:lts}),
+we determined a statistically-based dividing threshold of 12 K for weak
+stability (< 12 K) and strong stability (>= 12 K) conditions.
 
@@
 Geographical distribution of \textbf{(a, b)} cyclonic days and \textbf{(b, d)}
-relatively stable (LTS > 12 K) time steps in \textbf{(a, c)} ERA5 in years
+strong stability (LTS > 12 K) time steps in \textbf{(a, c)} ERA5 in years
 2010--2013 (inclusive) and \textbf{(b, d)} ICON in model years 2021--2023 (free
@@
 
-Fig. \ref{fig:cyclone-stability}a, b show a geographical distribution of the fraction
-of cyclonic days as determined by the cyclone tracking algorithm applied to the
-ERA5 reanalysis and ICON data (Section \ref{sec:cyclone-stability}). As
-expected, the strongest cyclonic activity is in the high-latitude SO zone, and
-it is relatively zonally symmetric at all latitudes.  The pattern matches reasonably well with \cite{hoskins2005}. While both reanalysis and
-the model agree relatively well, there are clear differences particularly in the highest occurrence rate regions -- over the Amundsen Sea, where the Amundsen Sea low is located \cite{turner2013} and which is
-more cyclonic in the reanalysis, and around Cape Adare, which is more cyclonic
-in ICON. These differences might, however, stem from the relatively short time
-periods of comparison (4 years) and the fact that the model is free-running.
+Fig. \ref{fig:cyclone-stability}a, b show a geographical distribution of the
+fraction of cyclonic days as determined by the cyclone tracking algorithm
+applied to the ERA5 reanalysis and ICON data (Section
+\ref{sec:cyclone-stability}). As expected, the strongest cyclonic activity is
+in the high-latitude SO zone, and it is relatively zonally symmetric at all
+latitudes.  The pattern matches reasonably well with \cite{hoskins2005}. While
+both reanalysis and the model agree relatively well, there are clear
+differences particularly in the highest occurrence rate regions -- over the
+Amundsen Sea, where the Amundsen Sea low is located \cite{turner2013} and which
+is more cyclonic in the reanalysis, and around Cape Adare, which is more
+cyclonic in ICON. These differences might, however, stem from the relatively
+short time periods of comparison (4 years) and the fact that the model is
+free-running.
 
 Fig. \ref{fig:cyclone-stability}c, d show a geographical distribution of the
-relatively stable and unstable conditions as determined by the LTS (Section
-\ref{sec:cyclone-stability}). Relatively unstable conditions are prevalent
-in the mid-to-high SO (with respect to our SO partitioning; 50--65°S), which might be explained by the relatively cold
-near-surface air overlying the relatively warm sea surface. Relatively
-stable conditions are prevalent elsewhere over the SO. The distribution is also
-less zonally symmetric than the cyclonic activity.  In the high-latitude SO,
-the presence of sea ice might have substantial stabilising effect
-\citep{knight2024}. The ERA5 reanalysis is also substantially more stable than
-ICON across the whole region.
+conditions of weak and strong stability as determined by the LTS (Section
+\ref{sec:cyclone-stability}). Conditions of weak stability are prevalent in the
+mid-to-high SO (with respect to our SO partitioning; 50--65°S), which might be
+explained by the relatively cold near-surface air overlying the relatively warm
+sea surface. Conditions of strong stability are prevalent elsewhere over the
+SO. The distribution is also less zonally symmetric than the cyclonic activity.
+In the high-latitude SO, the presence of sea ice might have substantial
+stabilising effect \citep{knight2024}. The ERA5 reanalysis is also
+substantially more stable than ICON across the whole region.
 
@@
 model (I), MERRA‐2 (M), and ERA5 reanalysis data (E). The numbers in the legend
-indicate the total cloud fraction and the number of days of data.
+indicate the total cloud fraction and the number of days of data. Multiple lines
+of ICON profiles are for each of the four years of model data available.
 }
@@
 shows that the total cloud fraction (determined as the fraction of profiles
-with clouds at any height in the lidar cloud mask) is underestimated in ICON
-by about 10\% and in the reanalyses by about 20\%. When analysed by
-height, ICON overestimates cloud occurrence below 1 km and underestimates it
-above, MERRA-2 underestimates cloud occurrence at all heights, especially near
-the surface, and ERA5 simulates cloud occurrence relatively well above 1 km,
-but strongly underestimates it near the surface.  We note that fog or
-near-surface clouds are strongly underestimated in the reanalyses (fog and clouds are
-both included in the cloud occurrence).  As shown in Fig.
-\ref{fig:cloud-occurrence-panel}, the biases are relatively consistent across
-the data sources and longitudes. We conclude that the ICON results  the observations better than the reanalyses in this metric.
-
-For all observations considered (Fig. \ref{fig:cloud-occurrence}a), the data show
-cloud occurrence peaking at the surface, whereas the models show a higher peak (at
-about 500 m). The models generally underestimate the total cloud fraction by 10--20\% and show a strong reduction in cloud occurrence near the surface, which is not
-supported by the observations. ICON and ERA5 overestimate cloud occurrence at
-their peak (between 0--1 km). Above 1 km, ICON and MERRA-2 underestimate cloud
-occurrence, but ERA5 is very accurate. The exaggerated peak in models is partly
-supported by the lifting condensation level (LCL) distribution, which peaks
-higher in the models than in the observations (at the surface), although this
-is not very pronounced.
-
-When subsetted by latitude (Fig.
-\ref{fig:cloud-occurrence}b, c), we see that the low-latitude SO zone displays
-a stronger peak of cloud occurrence near the surface than the high-latitude SO
-zone, and this could be because higher latitudes have more unstable atmospheric
-profiles. The low- and high-latitude SO zones show similar biases in models as
-in the general case, but ERA5 does not overestimate the peak in the
-low-latitude SO zone (near-surface cloud occurrence is still strongly
-underestimated).
+with clouds at any height in the lidar cloud mask) is underestimated in ICON by
+about 10\% and in the reanalyses by about 20\%. When analysed by height, ICON
+overestimates cloud occurrence below 1 km and underestimates it above, MERRA-2
+underestimates cloud occurrence at all heights, especially near the surface,
+and ERA5 simulates cloud occurrence relatively well above 1 km, but strongly
+underestimates it near the surface.  We note that fog or near-surface clouds
+are strongly underestimated in the reanalyses (fog and clouds are both included
+in the cloud occurrence).  As shown in Fig.  \ref{fig:cloud-occurrence-panel},
+the biases are relatively consistent across the data sources and longitudes. We
+conclude that the ICON results  the observations better than the reanalyses in
+this metric.
+
+For all observations considered (Fig. \ref{fig:cloud-occurrence}a), the data
+show cloud occurrence peaking at the surface, whereas the models show a higher
+peak (at about 500 m). The models generally underestimate the total cloud
+fraction by 10--20\% and show a strong reduction in cloud occurrence near the
+surface, which is not supported by the observations. ICON and ERA5 overestimate
+cloud occurrence at their peak (between 0--1 km). Above 1 km, ICON and MERRA-2
+underestimate cloud occurrence, but ERA5 is very accurate. The exaggerated peak
+in models is partly supported by the lifting condensation level (LCL)
+distribution, which peaks higher in the models than in the observations (at the
+surface), although this is not very pronounced. This is indicative of
+near-surface relatively humidity being often close to saturation in the
+observations but not in the models.
+
+When subsetted by latitude (Fig.  \ref{fig:cloud-occurrence}b, c), we see that
+the low-latitude SO zone displays a stronger peak of cloud occurrence near the
+surface than the high-latitude SO zone, and this could be because higher
+latitudes have less stable atmospheric profiles. The low- and high-latitude SO
+zones show similar biases in models as in the general case, but ERA5 does not
+overestimate the peak in the low-latitude SO zone (near-surface cloud
+occurrence is still strongly underestimated).
 
@@
 \ref{fig:cloud-occurrence}d, e), we see that the cyclonic situations have a
-larger amount of observed cloudiness, including peak and total cloud
-fraction. In these situations, the model vertical profiles of cloud occurrence compare well with observations, but still tend to
-underestimate cloud occurrence above 1 km and near the surface. Non-cyclonic
-situations are similar to the general case, partially also because they form
-the majority of cases.
-
-When subsetted by relatively stable and unstable conditions (Fig.
+larger amount of observed cloudiness, including peak and total cloud fraction.
+In these situations, the model vertical profiles of cloud occurrence compare
+well with observations, but still tend to underestimate cloud occurrence above
+1 km and near the surface. Non-cyclonic situations are similar to the general
+case, partially also because they form the majority of cases.
+
+When subsetted by conditions of weak and strong stability (Fig.
 \ref{fig:cloud-occurrence}f, g), as defined in Section
-\ref{sec:cyclone-stability}, we see that in relatively stable
-situations cloud occurrence peaks strongly at the surface in observations,
-compared to relatively unstable situations, where the peak is more diffuse
-between 0 and 1 km.  In relatively stable
-situations, the models do a fairly good job, but overestimate cloud
-occurrence at the peak below 1 km; above 1 km, they show similar biases as in
-the general case.  In relatively unstable situations, the bias in ICON is
-very pronounced, with a much stronger peak at about 500 m, ERA5 underestimates cloud occurrence below 1 km (especially near the surface), and
+\ref{sec:cyclone-stability}, we see that in situations of strong stability
+cloud occurrence peaks strongly at the surface in observations, compared to
+situations of weak stability, where the peak is more diffuse between 0 and 1
+km.  It is work mentioning that conditions of strong stability might be
+associated with the formation of advection fog, such as in situation of warm
+air advection from the north over colder sea surface, thus inducing fog
+formation by cooling of the warm and humid air by the cold surface.  In
+situations of strong stability, the models do a fairly good job, but
+overestimate cloud occurrence at the peak below 1 km; above 1 km, they show
+similar biases as in the general case.  In situations of weak stability, the
+bias in ICON is very pronounced, with a much stronger peak at about 500 m, ERA5
+underestimates cloud occurrence below 1 km (especially near the surface), and
 MERRA-2 underestimates cloud occurrence even more strongly.
@@
 occurrence below 1 km and underestimating above, underestimating the total
-cloud fraction, and showing greatest biases in relatively unstable and
+cloud fraction, and showing greatest biases in conditions of weak stability and
 non-cyclonic conditions. It also shows a peak of cloud occurrence at higher
@@
 cloud fraction, but mostly above and below 500 m (the peak at 500 m is
-well-represented). MERRA-2 displays the largest errors relative to observations in the low-latitude SO zone and in relatively unstable situations. ERA5 can be generally characterised as
-representing cloud occurrence correctly above about 1--1.5 km, overestimating
-below, but underestimating near-surface cloud occurrence (0--500 m). The total
-cloud fraction is strongly underestimated in all situations. ERA5 has a tendency
-towards underestimation in the low-latitude SO zone and relatively unstable
-situations; conversely, overestimating in the high-latitude SO zone and relatively stable conditions.
+well-represented). MERRA-2 displays the largest errors relative to observations
+in the low-latitude SO zone and in situations of weak stability. ERA5 can be
+generally characterised as representing cloud occurrence correctly above about
+1--1.5 km, overestimating below, but underestimating near-surface cloud
+occurrence (0--500 m). The total cloud fraction is strongly underestimated in
+all situations. ERA5 has a tendency towards underestimation in the low-latitude
+SO zone and situations of weak stability; conversely, overestimating in the
+high-latitude SO zone and conditions of strong stability.
 
@@
 Cloud occurrence by height calculated as the average of all voyages and
-stations for the observed (OBS) and simulated lidar cloud mask, and lifting
-condensation level (LCL) distribution. The total cloud fraction (CF), average
-shortwave (SW), and longwave (LW) are shown in the legend, and the relative
-frequency of occurrence (RFO) of the subset is shown below.  The bands span the
-16$^\mathrm{th}$--84$^\mathrm{th}$ percentile calculated from the set of all
-voyages and stations. The subsets \textbf{(d--g)} are defined in Section
-\ref{sec:cyclone-stability}.
+stations and lifting condensation level (LCL) distribution. The LCL is derived
+from radiosonde profiles and equivalent model profiles, which were not
+available for all voyages and times. The total cloud fraction (CF), average
+shortwave (SW), and longwave (LW) and the relative frequency of occurrence
+(RFO) are shown. The bands are the 16$^\mathrm{th}$--84$^\mathrm{th}$
+percentile calculated from the set of all voyages and stations.
 }
@@
 
-We also analysed the daily cloud cover (total cloud fraction) distribution. This is
-a measure of cloudiness, irrespective of height, calculated over the course of
-a day (UTC). A cloud detected at any height means that the lidar profile was
-classified as cloudy; otherwise, it was classified as clear sky. When all
-profiles in a day are taken together, the cloud cover for the day is defined as
-the fraction of cloudy profiles in the total number of profiles, expressed in
-oktas (multiples of 1/8).
+We also analysed the daily cloud cover (total cloud fraction) distribution.
+This is a measure of cloudiness, irrespective of height, calculated over the
+course of a day (UTC). A cloud detected at any height means that the lidar
+profile was classified as cloudy; otherwise, it was classified as clear sky.
+When all profiles in a day are taken together, the cloud cover for the day is
+defined as the fraction of cloudy profiles in the total number of profiles,
+expressed in oktas (multiples of 1/8).
 
 In Fig.  \ref{fig:cloud-cover} we show the results for the same subsets of data
-as in Section \ref{sec:cloud-occurrence}. Observations display the highest proportion of
-high cloud cover values (5--8 oktas), peaking at 7 oktas. This pattern is not represented by
-ICON or either reanalyses.  While ICON is closest to matching the observed distribution, it tends to be 1 okta
-clearer than the observations, peaking at 6 oktas, and substantially underestimating
-days with 8 oktas.  Overall, the reanalyses show results similar to each other,
+as in Section \ref{sec:cloud-occurrence}. Observations display the highest
+proportion of high cloud cover values (5--8 oktas), peaking at 7 oktas. This
+pattern is not represented by ICON or either reanalyses.  While ICON is closest
+to matching the observed distribution, it tends to be 1 okta clearer than the
+observations, peaking at 6 oktas, and substantially underestimating days with 8
+oktas.  Overall, the reanalyses show results similar to each other,
 underestimating cloud cover by about 2 oktas and strongly underestimating days
@@
 cloud cover, with 8 oktas occurring on one half of such days (Fig.
-\ref{fig:cloud-cover}d).  This sensitivity to cyclonic conditions is not observed in ICON or the reanalyses. Interestingly, clear sky days (0 oktas) also have a local maximum peaking
-at about 15\% in this subset.  When we contrast the low- and high-latitude
-zones, we see that the high-latitude zone tends to have greater cloud cover,
-peaking at 8 oktas (Fig.  \ref{fig:cloud-cover}c). The high-latitude zone also
-has almost no clear sky or small cloud cover cases (0--4 oktas). ICON and the
-reanalyses represent this characteristic of the distribution well for
-0--3 oktas, but otherwise show biases similar to the general case. One of the
-greatest biases is present in ERA5 in the relatively unstable subset, in which
-ERA5 peaks at 3 oktas, while the observations peak at 7 oktas and show
-negligible cloud cover below 5 oktas.
+\ref{fig:cloud-cover}d).  This sensitivity to cyclonic conditions is not
+observed in ICON or the reanalyses. Interestingly, clear sky days (0 oktas)
+also have a local maximum peaking at about 15\% in this subset.  When we
+contrast the low- and high-latitude zones, we see that the high-latitude zone
+tends to have greater cloud cover, peaking at 8 oktas (Fig.
+\ref{fig:cloud-cover}c). The high-latitude zone also has almost no clear sky or
+small cloud cover cases (0--4 oktas). ICON and the reanalyses represent this
+characteristic of the distribution well for 0--3 oktas, but otherwise show
+biases similar to the general case. One of the greatest biases is present in
+ERA5 in the subset of weak stability, in which ERA5 peaks at 3 oktas, while the
+observations peak at 7 oktas and show negligible cloud cover below 5 oktas.
 
@@
 Virtual potential temperature ($\theta_v$) and relative humidity (RH)
-determined from radiosonde launches and co-located profiles in
-ICON, ERA5, and MERRA-2 in subsets as in Fig. \ref{fig:cloud-occurrence}.
-The solid lines are the average calculated from the averages of every
-individual voyage and station. The bands span the
-16$^\mathrm{th}$--84$^\mathrm{th}$ percentiles calculated from the distribution
-of the voyage and station averages. Shown is also the relative frequency of
-occurrence and the number of profiles in each subset.
+determined from radiosonde launches and co-located profiles in ICON, ERA5, and
+MERRA-2 in subsets as in Fig. \ref{fig:cloud-occurrence}.  The solid lines are
+the average calculated from the averages of every individual voyage and
+station. The bands span the 16$^\mathrm{th}$--84$^\mathrm{th}$ percentiles
+calculated from the distribution of the voyage and station averages. Shown is
+also the relative frequency of occurrence and the number of profiles in each
+subset.
 }
@@
 
-In order to link the cloud biases to the local physical conditions, we analysed about 2300 radiosonde profiles south of 40°S from the 24 RV
-\emph{Polarstern} voyages, MARCUS, NBP1704, TAN1702, and TAN1802. Spatially and
-temporally colocated profiles were taken from ICON and the reanalyses.
-Because the time period covered by the ICON model output (2021--2024) was
-different from the time period covered by the observations (2010--2021), when
-comparing with the model, we first had to remap the observation time to model
-time by taking the same time relative to the start of the year. Consequently,
-we also had four virtual/model profiles (one for each year of 2021--2024) for
-each observed profile.
-The profiles were partitioned into the same subsets as
-above (Sections \ref{sec:cloud-occurrence} and \ref{sec:cloud-cover}).  Apart
-from relative humidity, we focus on comparing virtual potential temperature
+In order to link the cloud biases to the local physical conditions, we analysed
+about 2300 radiosonde profiles south of 40°S from the 24 RV \emph{Polarstern}
+voyages, MARCUS, NBP1704, TAN1702, and TAN1802. Spatially and temporally
+colocated profiles were taken from ICON and the reanalyses.  Because the time
+period covered by the ICON model output (2021--2024) was different from the
+time period covered by the observations (2010--2021), when comparing with the
+model, we first had to remap the observation time to model time by taking the
+same time relative to the start of the year. Consequently, we also had four
+virtual/model profiles (one for each year of 2021--2024) for each observed
+profile.  The profiles were partitioned into the same subsets as above
+(Sections \ref{sec:cloud-occurrence} and \ref{sec:cloud-cover}).  Apart from
+relative humidity, we focus on comparing virtual potential temperature
 ($\theta_v$) due to its role in low-level tropospheric stability, being one of
@@
 
-Overall, the mean $\theta_v$ is very well represented in ICON and
-MERRA-2, being only slightly colder in the mid-to-high troposphere (less
-stable) in ICON than in observations (Fig. \ref{fig:potential-temperature}a).
-Larger differences exist, however, in the 40--55°S zone, where ICON is colder by about 5 K at higher altitudes (Fig.
-\ref{fig:potential-temperature}b). In other subsets, the bias is relatively
-small. MERRA-2 is very close to the observations, possibly due to a high
-accuracy of assimilation of this quantity. Notably, the variability of virtual
-potential temperature (as represented by the percentiles) is much smaller in
-ICON than in the observations. This indicates that the model's internal
-variability in the lower-tropospheric thermodynamic conditions in the SO is
-smaller than in reality.
+Overall, the mean $\theta_v$ is very well represented in ICON and MERRA-2,
+being only slightly colder in the mid-to-high troposphere (less stable) in ICON
+than in observations (Fig. \ref{fig:potential-temperature}a).  Larger
+differences exist, however, in the 40--55°S zone, where ICON is colder by about
+5 K at higher altitudes (Fig.  \ref{fig:potential-temperature}b). In other
+subsets, the bias is relatively small. MERRA-2 is very close to the
+observations, possibly due to a high accuracy of assimilation of this quantity.
+Notably, the variability of virtual potential temperature (as represented by
+the percentiles) is much smaller in ICON than in the observations. This
+indicates that the model's internal variability in the lower-tropospheric
+thermodynamic conditions in the SO is smaller than in reality.
 
 Relative humidity displays much larger biases. In all subsets, ICON is too
-humid in the first 1 km by about 5\% but very accurate above, except for the 40--55°S zone
-and unstable conditions (Fig. \ref{fig:potential-temperature}b, g),  where it
-is too dry between about 1 and 3 km. MERRA-2, on the other hand, is much more
-humid than observations at all altitudes and in all subsets, by up to about
-20\% at 5 km.
+humid in the first 1 km by about 5\% but very accurate above, except for the
+40--55°S zone and conditions of weak stability (Fig.
+\ref{fig:potential-temperature}b, g),  where it is too dry between about 1 and
+3 km. MERRA-2, on the other hand, is more humid than observations at all
+altitudes and in all subsets, by up to about 20\% at 5 km. Even though the mean
+near-surface relative humidity is similar to the observations (Fig.
+\ref{potential-temperature}), the distribution in observation is more spread
+out across both high and low values, and thus observations have a greater
+prevalence of relative humidity close to 100\% and thus LCL located at the
+surface (Fig. \ref{cloud-occurrence}a). In our calculations, LCL is a exclusive
+function of near-surface temperature, near-surface relative humidity and
+surface pressure.
 
@@
 one can expect the results to be slightly different due to reasons unrelated to
-model biases, such as different weather conditions, partially accounted for by the cyclone and stability subsetting, and the phase of climate
-oscillations such as the ENSO in the observations and the model.
+model biases, such as different weather conditions, partially accounted for by
+the cyclone and stability subsetting, and the phase of climate oscillations
+such as the ENSO in the observations and the model.
 
@@
 
-We have attempted to remove lidar profiles with precipitation, which could not be
-properly simulated with the lidar simulator (Section \ref{sec:ann}). However,
-the approach was limited by the relatively low sensitivity of the ANN (65\%)
-and the fact that we had to choose a fixed threshold for surface precipitation
-flux in the model and reanalyses, which might not correspond to
-detection by the ANN applied to observations. Also, we made no attempt
-to remove profiles with precipitation not reaching the surface. The above
-reasons may result in an artificial bias in the comparison, even though we
-expect this to be much smaller than the identified model biases.
+We have attempted to remove lidar profiles with precipitation, which could not
+be properly simulated with the lidar simulator (Section \ref{sec:ann}).
+However, the approach was limited by the relatively low sensitivity of the ANN
+(65\%) and the fact that we had to choose a fixed threshold for surface
+precipitation flux in the model and reanalyses, which might not correspond to
+detection by the ANN applied to observations. Also, we made no attempt to
+remove profiles with precipitation not reaching the surface. The above reasons
+may result in an artificial bias in the comparison, even though we expect this
+to be much smaller than the identified model biases.
 
@@
 analysis provides a unique evaluation perspective different from satellite
-observations -- one that we argue is more suitable for evaluating boundary layer clouds,
-which are predominant in this region. Furthermore, we subsetted our dataset by
-low and high latitude bands, cyclonic activity, and stability in order to
-identify how these conditions influence the biases.
+observations -- one that we argue is more suitable for evaluating boundary
+layer clouds, which are predominant in this region. Furthermore, we subsetted
+our dataset by low and high latitude bands, cyclonic activity, and stability in
+order to identify how these conditions influence the biases.
 
@@
 biases in models and their subsequent effect on the radiative transfer. This
-also applies to the new GSRM ICON, but the biases are generally lower than in the
-reanalyses, despite the reanalyses having the advantage of assimilation of the
-observed meteorological conditions.  The GSRM has, on the other hand, the
+also applies to the new GSRM ICON, but the biases are generally lower than in
+the reanalyses, despite the reanalyses having the advantage of assimilation of
+the observed meteorological conditions.  The GSRM has, on the other hand, the
 advantage of a much higher spatial resolution and, to a limited extent,
@@
 We show that relative to ERA5, the distribution and strength of cyclonic
-activity over the SO is well represented in ICON, but it displays lower values of LTS. The latter is also manifested in the radiosonde profile
-comparison, showing that the virtual potential temperature profiles in ICON
-are less stable than in the observations over low-latitude SO.
-
-The 31 voyages and a station show remarkably similar biases in cloud occurrence by
-height in the lidar comparison, which indicates that common underlying causes
-for the biases exist regardless of longitude and season. ICON underestimates
-the total cloud fraction by about 10\%, with an overestimation of clouds below
-2 km and an underestimation of clouds above 2 km. The reanalyses also
-underestimate the total cloud fraction by about 20\%.  ERA5 overestimates cloud
-below 1 km but underestimates near-surface cloud or fog. ICON strongly
-overestimates the peak of cloud occurrence at about 500 m, which might be
-explained by the radiosonde comparison, showing that it is too moist at
-around this height.  Similar to our results, \cite{cesana2022} showed that
+activity over the SO is well represented in ICON, but it displays lower values
+of LTS. The latter is also manifested in the radiosonde profile comparison,
+showing that the virtual potential temperature profiles in ICON are less stable
+than in the observations over low-latitude SO.
+
+The 31 voyages and a station show remarkably similar biases in cloud occurrence
+by height in the lidar comparison, which indicates that common underlying
+causes for the biases exist regardless of longitude and season. ICON
+underestimates the total cloud fraction by about 10\%, with an overestimation
+of clouds below 2 km and an underestimation of clouds above 2 km. The
+reanalyses also underestimate the total cloud fraction by about 20\%.  ERA5
+overestimates cloud below 1 km but underestimates near-surface cloud or fog.
+ICON strongly overestimates the peak of cloud occurrence at about 500 m, which
+might be explained by the radiosonde comparison, showing that it is too moist
+at around this height.  Similar to our results, \cite{cesana2022} showed that
 CMIP6 models also tend to underestimate cloud occurrence above 2 km over the
@@
 Compared to lidar observations, the daily cloud cover tends to be about 1 okta
-lower in ICON and 2 oktas lower in the reanalyses.  Unstable conditions are
-associated with some of the greatest biases, especially in ERA5.  The models
-also underestimate the cloud cover very strongly in cyclonic conditions, which
-are very cloudy in the observations (8 oktas), but much less so in the models.
+lower in ICON and 2 oktas lower in the reanalyses.  Conditions of weak
+stability are associated with some of the greatest biases, especially in ERA5.
+The models also underestimate the cloud cover very strongly in cyclonic
+conditions, which are very cloudy in the observations (8 oktas), but much less
+so in the models.
 
@@
 too moist at all heights.  ICON also exhibits smaller internal variability than
-the radiosonde observations. Overall, the radiosonde comparison only
-partially explains the identified cloud biases, and other physical causes are
-likely contributing.  This warrants further investigation, especially of
+the radiosonde observations. Overall, the radiosonde comparison only partially
+explains the identified cloud biases, and other physical causes are likely
+contributing.  This warrants further investigation, especially of
 ocean--atmosphere fluxes, shallow convection, and boundary layer turbulence.
@@
 
-The results imply that SO cloud biases are still a substantial issue even in the
-km-scale resolution ICON model, even though an improvement over the
+The results imply that SO cloud biases are still a substantial issue even in
+the km-scale resolution ICON model, even though an improvement over the
 lower-resolution reanalyses is notable. More effort is needed to improve the
-model cloud simulations in this understudied region. However, this analysis suggests that the
-transition from models with parametrised convection and clouds to
-storm-resolving models might not solve these biases without additional effort.
-Evaluation of ocean--atmosphere heat, moisture, and momentum fluxes against in-situ observations over the SO and comparison of GSRM simulations against
-large-eddy simulations are two potential avenues for future research that could
-elucidate the physical mechanisms behind the biases, in addition to the more
-common efforts in SO cloud microphysics and precipitation evaluation.
+model cloud simulations in this understudied region. However, this analysis
+suggests that the transition from models with parametrised convection and
+clouds to storm-resolving models might not solve these biases without
+additional effort.  Evaluation of ocean--atmosphere heat, moisture, and
+momentum fluxes against in-situ observations over the SO and comparison of GSRM
+simulations against large-eddy simulations are two potential avenues for future
+research that could elucidate the physical mechanisms behind the biases, in
+addition to the more common efforts in SO cloud microphysics and precipitation
+evaluation.
 
@@
 dataset provided by the Australian Antarctic Division (AAD) and University of
-Canterbury (UC), the RV \emph{Tangaroa} datasets provided by the National Institute
-of Water and Atmospheric Research and UC, the NBP1704 dataset provided by the
-National Science Foundation, Cooperative Institute for Research in
-Environmental Sciences, University of Colorado and UC, the HMNZSW16 dataset
+Canterbury (UC), the RV \emph{Tangaroa} datasets provided by the National
+Institute of Water and Atmospheric Research and UC, the NBP1704 dataset
+provided by the National Science Foundation, Cooperative Institute for Research
+in Environmental Sciences, University of Colorado and UC, the HMNZSW16 dataset
 provided by the Royal New Zealand Navy and UC, the MARCUS dataset provided by
-ARM and AAD, and the MICRE dataset
-provided by ARM, the Australian Bureau of Meteorology, and AAD.  Technical,
-logistical, and ship support for MARCUS and MICRE were provided by the AAD
-through Australian Antarctic Science projects 4292 and 4387, and we thank
-Steven Whiteside, Lloyd Symonds, Rick van den Enden, Peter de Vries, Chris
-Young, Chris Richards, Andrew Klekociuk, John French, Terry Egan, Nick
-Cartwright, and Ken Barrett for all of their assistance.  We thank the
-scientific staff, the crew, and everyone involved in collecting data on the
-voyages and stations, especially Gert König-Langlo, Holger Schmithüsen, Roger
-Marchand, Peter Guest, Kelly Schick, Jamie Halla, and Mike J.  Harvey (†). We
-thank Loretta Preis for providing additional RV \emph{Polarstern} data.  We
-acknowledge the ICON model output provided by the nextGEMS project, Deutscher
-Wetterdienst, Max-Planck-Institute for Meteorology, DKRZ, Karlsruhe Institute
-of Technology, and Center for Climate Systems Modeling; reanalysis dataset ERA5
-provided by the Copernicus Climate Change Service; MERRA-2 provided by the
-Global Modeling and Assimilation Office; CERES datasets provided by the NASA
-Langley Atmospheric Science Data Center Distributed Active Archive Center; and
-the Natural Earth dataset provided by naturalearthdata.com.  Last but not
-least, we acknowledge the use of open source software Python, Cython
-\citep{behnel2011}, TensorFlow \citep{abadi2016}, Devuan GNU+Linux, parallel
-\citep{tange2011}, NumPy \citep{harris2020}, SciPy \citep{virtanen2020},
-Matplotlib \citep{hunter2007}, cartopy \citep{cartopy}, pyproj, Inkscape, Bash,
-GNU Fortran, HDF \citep{folk1999}, and NetCDF \citep{rew1990}.  We dedicate
-this study to the memory of Mike J.  Harvey, who very substantially contributed
-to obtaining the atmospheric observations on the RV \emph{Tangaroa} voyages
-used in this study.
+ARM and AAD, and the MICRE dataset provided by ARM, the Australian Bureau of
+Meteorology, and AAD.  Technical, logistical, and ship support for MARCUS and
+MICRE were provided by the AAD through Australian Antarctic Science projects
+4292 and 4387, and we thank Steven Whiteside, Lloyd Symonds, Rick van den
+Enden, Peter de Vries, Chris Young, Chris Richards, Andrew Klekociuk, John
+French, Terry Egan, Nick Cartwright, and Ken Barrett for all of their
+assistance.  We thank the scientific staff, the crew, and everyone involved in
+collecting data on the voyages and stations, especially Gert König-Langlo,
+Holger Schmithüsen, Roger Marchand, Peter Guest, Kelly Schick, Jamie Halla, and
+Mike J.  Harvey (†). We thank Loretta Preis for providing additional RV
+\emph{Polarstern} data.  We acknowledge the ICON model output provided by the
+nextGEMS project, Deutscher Wetterdienst, Max-Planck-Institute for Meteorology,
+DKRZ, Karlsruhe Institute of Technology, and Center for Climate Systems
+Modeling; reanalysis dataset ERA5 provided by the Copernicus Climate Change
+Service; MERRA-2 provided by the Global Modeling and Assimilation Office; CERES
+datasets provided by the NASA Langley Atmospheric Science Data Center
+Distributed Active Archive Center; and the Natural Earth dataset provided by
+naturalearthdata.com.  Last but not least, we acknowledge the use of open
+source software Python, Cython \citep{behnel2011}, TensorFlow
+\citep{abadi2016}, Devuan GNU+Linux, parallel \citep{tange2011}, NumPy
+\citep{harris2020}, SciPy \citep{virtanen2020}, Matplotlib \citep{hunter2007},
+cartopy \citep{cartopy}, pyproj, Inkscape, Bash, GNU Fortran, HDF
+\citep{folk1999}, and NetCDF \citep{rew1990}.  We dedicate this study to the
+memory of Mike J.  Harvey, who very substantially contributed to obtaining the
+atmospheric observations on the RV \emph{Tangaroa} voyages used in this study.
 

### 2024-12-09 manuscript.tex
Addressing comments

@@
 errors in ICON and the reanalyses.  Compared to radiosondes, potential
-temperature is accurate in the reanalyses, but ICON underestimates stability
-over the low-latitude SO and too humid in the boundary layer. MERRA-2 is too
-humid at all heights. SO cloud biases remain a substantial issue in the GSRM,
-but are an improvement over the lower-resolution reanalyses. Explicitly
-resolved convection and cloud processes (except microphysics) were not enough
-to address the model cloud biases.
+temperature is accurate in the reanalyses to about 0.5 K, but ICON
+underestimates stability over the low-latitude SO and too humid in the boundary
+layer. MERRA-2 is too humid at all heights. SO cloud biases remain a
+substantial issue in the GSRM, but are an improvement over the lower-resolution
+reanalyses. Explicitly resolved convection and cloud processes (except
+microphysics) were not enough to address the model cloud biases.
 
@@
 the SO as ocean regions south of 40°S, low-latitude SO as 40--55°S and
-high-latitude SO as south of 55°S.
+high-latitude SO as south of 55°S. The reason for this dividing latitude
+is to split the SO into about two equal zones, as well as the results by
+\cite{schuddeboom2021} (Fig. 2b), showing a contrast in CMIP model radiation
+biases, \citep{schuddeboom2019} (Fig. 2) and \cite{kuma2020} (Fig. 3) showing
+contrasting radiation biases in the Hadley Centre Global Environmental Model
+between these two zones. The findings of \cite{niu2024}, however, support a
+different dividing line of 62º based on cloud condensation nuclei
+concentration.
 
@@
 overestimates cloud occurrence below 1 km and underestimates it above, MERRA-2
-underestimates cloud occurrence at all heights, especially near the surface,
-and ERA5 simulates cloud occurrence relatively well above 1 km, but strongly
-underestimates it near the surface.  We note that fog or near-surface clouds
-are strongly underestimated in the reanalyses (fog and clouds are both included
-in the cloud occurrence).  As shown in Fig.  \ref{fig:cloud-occurrence-panel},
-the biases are relatively consistent across the data sources and longitudes. We
-conclude that the ICON results  the observations better than the reanalyses in
-this metric.
+underestimates cloud occurrence at all heights by up to about 10\%, especially
+near the surface, and ERA5 simulates cloud occurrence relatively well above 1
+km, but strongly underestimates it near the surface.  We note that fog or
+near-surface clouds are strongly underestimated in the reanalyses (fog and
+clouds are both included in the cloud occurrence).  As shown in Fig.
+\ref{fig:cloud-occurrence-panel}, the biases are relatively consistent across
+the data sources and longitudes. We conclude that the ICON results  the
+observations better than the reanalyses in this metric.
 
@@
 cloud occurrence at their peak (between 0--1 km). Above 1 km, ICON and MERRA-2
-underestimate cloud occurrence, but ERA5 is very accurate. The exaggerated peak
-in models is partly supported by the lifting condensation level (LCL)
-distribution, which peaks higher in the models than in the observations (at the
-surface), although this is not very pronounced. This is indicative of
-near-surface relatively humidity being often close to saturation in the
-observations but not in the models.
+underestimate cloud occurrence, but ERA5 is accurate to about 3\% or less. The
+exaggerated peak in models is partly supported by the lifting condensation
+level (LCL) distribution, which peaks higher by about 200 m in the models than
+in the observations (at the surface), although this is not very pronounced.
+This is indicative of near-surface relatively humidity being often close to
+saturation in the observations but not in the models.
 
@@
 \ref{fig:cloud-occurrence}d, e), we see that the cyclonic situations have a
-larger amount of observed cloudiness, including peak and total cloud fraction.
-In these situations, the model vertical profiles of cloud occurrence compare
-well with observations, but still tend to underestimate cloud occurrence above
-1 km and near the surface. Non-cyclonic situations are similar to the general
-case, partially also because they form the majority of cases.
+larger amount of observed cloudiness, including peak and total cloud fraction,
+both by about 7\%.  In the cyclonic situations, the model vertical profiles of
+cloud occurrence compare well with observations, but they peak higher by about
+200 m and stronger by about 8\%. The reanalyses still tend to underestimate
+cloud occurrence above 1 km by about 5\% and near the surface by about 14\%.
+Non-cyclonic situations are similar to the general case, partially also because
+they form the majority of cases.
 
@@
 formation by cooling of the warm and humid air by the cold surface.  In
-situations of strong stability, the models do a fairly good job, but
-overestimate cloud occurrence at the peak below 1 km; above 1 km, they show
-similar biases as in the general case.  In situations of weak stability, the
-bias in ICON is very pronounced, with a much stronger peak at about 500 m, ERA5
-underestimates cloud occurrence below 1 km (especially near the surface), and
-MERRA-2 underestimates cloud occurrence even more strongly.
+situations of strong stability, the models have smaller biases than in weak
+stability, with overestimated peak by up to 12\%, underestimated cloud
+occurrence above 1 km by up to 5\% and underestimated cloud occurrence near the
+surface by about 11\%.  In situations of weak stability, the bias in ICON is
+very pronounced, with a much stronger peak at about 500 m, ERA5 underestimates
+cloud occurrence below 1 km (especially near the surface), and MERRA-2
+underestimates cloud occurrence even more strongly.
 
@@
 underestimating cloud cover by about 2 oktas and strongly underestimating days
-with 7 and 8 oktas. Of the two reanalyses, MERRA-2 shows slightly higher cloud
-cover and thus is more consistent with observations.
+with 7 and 8 oktas. Of the two reanalyses, MERRA-2 has slightly higher cloud
+cover then ERA5, by about 6\% at 6 octas, which makes it more consistent with
+observations.
 
@@
 
-Overall, the mean $\theta_v$ is very well represented in ICON and MERRA-2,
-being only slightly colder in the mid-to-high troposphere (less stable) in ICON
-than in observations (Fig. \ref{fig:potential-temperature}a).  Larger
+Overall, the mean $\theta_v$ is accurate less than 0.5 K in ICON and MERRA-2,
+being only colder by up to 2 K in the mid-to-high troposphere (less stable) in
+ICON than in observations (Fig. \ref{fig:potential-temperature}a).  Larger
 differences exist, however, in the 40--55°S zone, where ICON is colder by about

### 2024-12-09 manuscript.tex
Addressing comments

@@
 The Southern Ocean (SO) is known to be a problematic region for climate model
-biases due to a lack of surface and in situ observations and being a lower
-priority region for numerical weather prediction (NWP) and climate model
-development because of its distance from populated areas.  Nevertheless,
-radiation biases and changes over an area of its size have a substantial
-influence on the global climate, such as affecting the Earth radiation balance
-and carbon cycle, and the SO is an important part of the global ocean conveyor
-belt. In general, marine clouds have a disproportionate effect on top of
-atmosphere (TOA) SW radiation due to the relatively low albedo of the sea
-surface.  The relative longitudinal symmetry of the SO means that model cloud
-biases tend to be similar across longitudes.  Here, we conventionally refer to
-the SO as ocean regions south of 40°S, low-latitude SO as 40--55°S and
-high-latitude SO as south of 55°S. The reason for this dividing latitude
-is to split the SO into about two equal zones, as well as the results by
-\cite{schuddeboom2021} (Fig. 2b), showing a contrast in CMIP model radiation
-biases, \citep{schuddeboom2019} (Fig. 2) and \cite{kuma2020} (Fig. 3) showing
-contrasting radiation biases in the Hadley Centre Global Environmental Model
-between these two zones. The findings of \cite{niu2024}, however, support a
-different dividing line of 62º based on cloud condensation nuclei
-concentration.
+biases \citep{schuddeboom2021,hyder2018,cesana2022,zhao2022} due to a lack of
+surface and in situ observations and being a lower priority region for
+numerical weather prediction (NWP) and climate model development because of its
+distance from populated areas.  Nevertheless, radiation biases and changes over
+an area of its size have a substantial influence on the global climate
+\citep{rintoul2011}, such as affecting the Earth radiation balance, ocean heat
+and carbon uptake \citep{williams2023}, and the SO is an important part of the
+global ocean conveyor belt \citep{wang2014}. In general, marine clouds have a
+disproportionate effect on top of atmosphere (TOA) SW radiation due to the
+relatively low albedo of the sea surface.  The relative longitudinal symmetry
+of the SO means that model cloud biases tend to be similar across longitudes.
+
+Here, we conventionally refer to the SO as ocean regions south of 40°S,
+low-latitude SO as 40--55°S and high-latitude SO as south of 55°S. The reason
+for this dividing latitude is to split the SO into about two equal zones, as
+well as the results by \cite{schuddeboom2021} (Fig. 2b), showing a contrast in
+CMIP model radiation biases, \cite{schuddeboom2019} (Fig. 2) and
+\cite{kuma2020} (Fig. 3) showing contrasting radiation biases in the Hadley
+Centre Global Environmental Model, and \cite{cesana2022} showing contrasting
+cloud biases due to the 0°C isotherm reaching the surface at 55°S. The findings
+of \cite{niu2024}, however, support a different dividing line of 62°S based on
+cloud condensation nuclei concentration.
 
@@
 problematic to observe by spaceborne lidars and radars, which are affected by
-attenuation by overlapping and thick clouds and ground clutter, respectively.
-Specifically, the radar on CloudSat and lidar on CALIPSO (neither of which are
-nowoperational) are affected by the abovementioned issues, resulting in a
-strong underestimation of cloud occurrence below 2 km relative to ground-based
-lidar observations \citep{mcerlich2021}.  We hypothesise that this, in turn,
-can lead to systematic biases in low clouds in climate models, which are
-frequently evaluated against CloudSat--CALIPSO products. Reanalyses can also
-suffer from cloud biases, as these are usually parametrised in their
-atmospheric component, and also in regions where input observations are sparse.
-This makes them a problematic reference for clouds over the SO, and any biases
-relative to a reanalysis should be interpreted with caution. Instead, we chose
-to use a large set of ship-based observations conducted with ceilometers and
-lidars on board of the RV \emph{Polarstern} and other voyages and stations as a
-reference for the model evaluation.
+attenuation by overlapping and thick clouds \citep{mace2009,medeiros2010} and
+ground clutter \citep{marchand2008}, respectively.  Specifically, the radar on
+CloudSat and lidar on CALIPSO (neither of which are nowoperational) are
+affected by the abovementioned issues, resulting in a strong underestimation of
+cloud occurrence below 2 km relative to ground-based lidar observations
+\citep{mcerlich2021}.  We hypothesise that this, in turn, can lead to
+systematic biases in low clouds in climate models, which are frequently
+evaluated against CloudSat--CALIPSO products. Reanalyses can also suffer from
+cloud biases, as these are usually parametrised in their atmospheric component,
+and also in regions where input observations are sparse.  This makes them a
+problematic reference for clouds over the SO, and any biases relative to a
+reanalysis should be interpreted with caution. Instead, we chose to use a large
+set of ship-based observations conducted with ceilometers and lidars on board
+of the RV \emph{Polarstern} and other voyages and stations as a reference for
+the model evaluation.
 
@@
 The time period of ICON is relatively short, with only four full years of
-simulation available. Moreover, the simulation is free-running, which means
-that observations had to be temporally mapped to this time period (at the same
-time relative to the start of the year) for the comparison. For these reasons,
-one can expect the results to be slightly different due to reasons unrelated to
-model biases, such as different weather conditions, partially accounted for by
-the cyclone and stability subsetting, and the phase of climate oscillations
-such as the ENSO in the observations and the model.
+simulation available. Moreover, the simulation is free-running and
+ocean-coupled, which means that observations had to be temporally mapped to
+this time period (at the same time relative to the start of the year) for the
+comparison. For these reasons, one can expect the results to be slightly
+different due to reasons unrelated to model biases, such as different weather
+conditions, partially accounted for by the cyclone and stability subsetting,
+and the phase of climate oscillations such as the ENSO in the observations and
+the model.
 

### 2024-12-09 manuscript_agu.tex
AGU template

--- 2024-12-09 manuscript.tex
@@
-% Related publications:
-%
-% Takasuka et al. (2024), A protocol and analysis of year-long simulations of global storm-resolving models and beyond
-% Knight et al. (2024), Cloud properties and boundary layer stability above Southern Ocean sea ice and coastal Antarctica
-% Zheng et al. (2024), Using Satellite and ARM Observations to Evaluate Cold Air Outbreak Cloud Transitions in E3SM Global Storm-Resolving Simulations
-% Schmidt et al. (2024), Effects of vertical grid spacing on the climate simulated in the ICON-Sapphire global storm-resolving model
-% Fons et al. (2024), Investigating the sign of stratocumulus adjustments to aerosols in the global storm-resolving model ICON
-% Fiddes et al. (2024), A machine learning approach for evaluating Southern Ocean cloud radiative biases in a global atmosphere model
-% Mooers et al. (2023), Comparing storm resolving models and climates via unsupervised machine learning
-% Zhang et al. (2023), Understanding models' global sea surface temperature bias in mean state: from CMIP5 to CMIP6
-% Grundner (2023), Data-Driven Cloud Cover Parameterizations for the ICON Earth System Model Using Deep Learning and Symbolic Regression [thesis]
-% Luo et al. (2023), Origins of Southern Ocean warm sea surface temperature bias in CMIP6 models
-% Sherriff-Tadano et al. (2023), Southern Ocean Surface Temperatures and Cloud Biases in Climate Models Connected to the Representation of Glacial Deep Ocean Circulation
-% Danker et al. (2022), Exploring relations between cloud morphology, cloud phase, and cloud radiative properties in Southern Ocean's stratocumulus clouds
-% Possner et al. (2022), Resolution Dependence of Southern Ocean Mixed-Phase Clouds in ICON
-% Mauritsen et al. (2022), Early Development and Tuning of a Global Coupled Cloud Resolving Model, and its Fast Response to Increasing CO2
-% Wall et al. (2022), Observational Constraints on Southern Ocean Cloud-Phase Feedback
-% Grundner et al. (2022), Deep learning based cloud cover parameterization for ICON
-% Cesana et al. (2022), Southern Ocean Solar Reflection Biases in CMIP6 Models Linked to Cloud Phase and Vertical Structure Representations
-% Fiddes et al. (2022), Southern Ocean cloud and shortwave radiation biases in a nudged climate model simulation: does the model ever get it right?
-% Zhao et al. (2022), Compensating Errors in Cloud Radiative and Physical Properties over the Southern Ocean in the CMIP6 Climate Models
-% Konsta et al. (2022), Low-Level Marine Tropical Clouds in Six CMIP6 Models Are Too Few, Too Bright but Also Too Compact and Too Homogeneous
-% Lin and Yu (2022), The potential impact of model horizontal resolution on the simulation of atmospheric cloud radiative effect in CMIP6 models
-% Ramadoss et al. (2021), An evaluation of kilometre scale ICON simulations of mixed-phase stratocumulus over the Southern Ocean durin CAPRICORN [poster]
-% Miao et al. (2021), A Regime-based Investigation into the Errors of CMIP6 Simulated Cloud Radiative Effects Using Satellite Observations
-% Roh et al. (2021), Intercomparison of cloud properties in DYAMOND simulations over the Atlantic Ocean
-% Caldwell et al. (2021), Convection-Permitting Simulations With the E3SM Global Atmosphere Model
-% Schuddeboom and McDonald (2021), The Southern Ocean Radiative Bias, Cloud Compensating Errors, and Equilibrium Climate Sensitivity in CMIP6 Models
-% Ramadoss et al. (2020), Simulating mixed-phase cloud properties with ICON around the CAPRICORN field campaign at the kilometre scale [poster]
-% Heim et al. (2021), Inter-model Variability in Convection-Resolving Simulations of Subtropical Marine Low Clouds
-% Seiki and Roh (2020), Improvements in Supercooled Liquid Water Simulations of Low-Level Mixed-Phase Clouds over the Southern Ocean Using a Single-Column Model
-% Stevens et al. (2020), The added value of large-eddy and storm-resolving models for simulating clouds and precipitation
-% Atlas et al. (2020), How well do large‐eddy simulations and global climate models represent observed boundary layer structures and low clouds over the summertime Southern Ocean?
-% Korn et al. (2020), ICON‐O: The Ocean Component of the ICON Earth System Model—Global Simulation Characteristics and Local Telescoping Capability
-% Vignesh et al. (2020), Assessment of CMIP6 Cloud Fraction and Comparison with Satellite Observations
-% Chen et al. (2022), Evaluation of Simulated Cloud Diurnal Variation in CMIP6 Climate Models
-% Jian et al. (2020), Evaluation of the CMIP6 planetary albedo climatology using satellite observations
-% Satoh et al. (2019), Global Cloud-Resolving Models
-% Hyder et al. (2018), Critical Southern Ocean climate model biases traced to atmospheric model cloud errors
-
-\documentclass[12pt,a4paper]{article}
-\usepackage{fontspec}
-\usepackage{microtype}
-\usepackage[margin=2cm]{geometry}
-\usepackage[citecolor=black]{hyperref}
-\usepackage[authoryear,round]{natbib}
-\usepackage{doi}
-\usepackage{titlesec}
-\usepackage{caption}
-\DeclareCaptionLabelSeparator{pipe}{ | }
-\captionsetup{labelfont={bf,sf},labelsep=pipe}
-\usepackage{graphicx}
+\documentclass[draft]{agujournal2019}
+\usepackage{url} %this package should fix any errors with URLs in refs.
 \usepackage{lineno}
+%\usepackage[inline]{trackchanges} %for better track changes. finalnew option will compile document with changes incorporated.
+\usepackage{soul}
 \linenumbers
-\setsansfont{Source Sans Pro}
-\setmainfont{EB Garamond}
-\setmonofont[Scale=0.8]{SpaceMono}[
-	Path=./fonts/,
-	Extension=.ttf,
-	UprightFont=*-Regular,
-	BoldFont=*-Bold,
-	ItalicFont=*-Italic,
-	BoldItalicFont=*-BoldItalic
-]
-\hypersetup{
-	colorlinks=true,
-	urlcolor=blue,
-	pdftitle={Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON, and the ERA5 and MERRA-2 reanalyses},
-	pdfauthor={Peter Kuma, Frida A.-M.
-Bender, Adrian J.
-McDonald, Simon P.
-Alexander, Greg M.
-McFarquhar, John J.
-Cassano, Graeme E.
-Plank, Sean Hartery, Simon Parsons, Sally Garrett, and Alex J.
-Schuddeboom}
-}
-\bibliographystyle{abbrvnat}
-\titleformat*{\section}{\large\bfseries\sffamily}
-\titleformat*{\subsection}{\normalsize\bfseries\sffamily}
-\titlespacing*{\section}{0pt}{14pt}{6pt}
-\titlespacing*{\subsection}{0pt}{13pt}{4pt}
-\parskip=6pt
-\parindent=0pt
+
+\draftfalse
+
+\journalname{JGR: Atmospheres}
 
@@
 
-\fontsize{13pt}{15pt}\selectfont
-
-\begin{center} \Large \sffamily\textbf{Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON and the ERA5 and MERRA-2 reanalyses}\\[0.4cm]
-\normalsize Peter Kuma$^\mathsf{1,2,\star}$, Frida A.-M.
-Bender$^\mathsf{1,2}$, Adrian J.
-McDonald$^\mathsf{3}$, Simon P.
-Alexander$^\mathsf{4,5}$, Greg M.
-McFarquhar$^\mathsf{6,7}$, John J.
-Cassano$^\mathsf{8,9,10}$, Graeme E.
-Plank$^\mathsf{3}$, Sean Hartery$^\mathsf{11}$, Simon Parsons$^\mathsf{12}$, Sally Garrett$^\mathsf{13}$, and Alex J.
-Schuddeboom$^\mathsf{3}$\\[0.4cm]
-\footnotesize
-$^\mathsf{1}$Department of Meteorology (MISU), Stockholm University, Stockholm, Sweden\\
-$^\mathsf{2}$Bolin Centre for Climate Research, Stockholm University, Stockholm, Sweden\\
-$^\mathsf{3}$School of Physical and Chemical Sciences, University of Canterbury, Christchurch, Aotearoa/New Zealand\\
-$^\mathsf{4}$Australian Antarctic Division, Kingston, Tasmania, Australia\\
-$^\mathsf{5}$Australian Antarctic Program Partnership, Institute for Marine and Antarctic Studies, University of Tasmania, Hobart, Tasmania, Australia\\
-$^\mathsf{6}$Cooperative Institute of Severe and High Impact Weather Research and Operations, University of Oklahoma, Norman, OK, USA\\
-$^\mathsf{7}$School of Meteorology, University of Oklahoma, Norman, OK, USA\\
-$^\mathsf{8}$Cooperative Institute for Research in Environmental Sciences, University of Colorado, Boulder, CO, USA\\
-$^\mathsf{9}$National Snow and Ice Data Center, University of Colorado, Boulder, CO, USA\\
-$^\mathsf{10}$Department of Atmospheric and Oceanic Sciences, University of Colorado, Boulder, CO, USA\\[0.2cm]
-$^\mathsf{11}$Department of Physics \& Atmospheric Science, Dalhousie University, Halifax, Canada\\
-$^\mathsf{12}$New South Wales Department of Planning and Environment, Sydney, New South Wales, Australia\\
-$^\mathsf{13}$New Zealand Defence Force, Wellington, New Zealand\\
-$^\star$Corresponding author: Peter Kuma (\href{mailto:peter.kuma@misu.su.se}{peter.kuma@misu.su.se})\\[0.4cm]
-\normalsize \today\\[0.4cm]
-
-\end{center}
-
-\section*{Abstract}
-
+\title{Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON, and the ERA5 and MERRA-2 reanalyses}
+
+\authors{Peter Kuma\affil{1,2}\thanks{}, Frida A.-M.
+Bender\affil{1,2}, Adrian J.
+McDonald\affil{3}, Simon P.
+Alexander\affil{4,5}, Greg M.
+McFarquhar\affil{6,7}, John J.
+Cassano\affil{8,9,10}, Graeme E.
+Plank\affil{3}, Sean Hartery\affil{11}, Simon Parsons\affil{12}, Sally Garrett\affil{13}, and Alex J.
+Schuddeboom\affil{3}}
+
+\affiliation{1}{Department of Meteorology (MISU), Stockholm University, Stockholm, Sweden}
+\affiliation{2}{Bolin Centre for Climate Research, Stockholm University, Stockholm, Sweden}
+\affiliation{3}{School of Physical and Chemical Sciences, University of Canterbury, Christchurch, Aotearoa/New Zealand}
+\affiliation{4}{Australian Antarctic Division, Kingston, Tasmania, Australia}
+\affiliation{5}{Australian Antarctic Program Partnership, Institute for Marine and Antarctic Studies, University of Tasmania, Hobart, Tasmania, Australia}
+\affiliation{6}{Cooperative Institute of Severe and High Impact Weather Research and Operations, University of Oklahoma, Norman, OK, USA}
+\affiliation{7}{School of Meteorology, University of Oklahoma, Norman, OK, USA}
+\affiliation{8}{Cooperative Institute for Research in Environmental Sciences, University of Colorado, Boulder, CO, USA}
+\affiliation{9}{National Snow and Ice Data Center, University of Colorado, Boulder, CO, USA}
+\affiliation{10}{Department of Atmospheric and Oceanic Sciences, University of Colorado, Boulder, CO, USA}
+\affiliation{11}{Department of Physics \& Atmospheric Science, Dalhousie University, Halifax, Canada}
+\affiliation{12}{New South Wales Department of Planning and Environment, Sydney, New South Wales, Australia}
+\affiliation{13}{New Zealand Defence Force, Wellington, Aotearoa/New Zealand}
+
+\correspondingauthor{Peter Kuma}{peter@peterkuma.net}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% KEY POINTS
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%  List up to three key points (at least one is required)
+%  Key Points summarize the main points and conclusions of the article
+%  Each must be 140 characters or fewer with no special characters or punctuation and must be complete sentences
+
+% Example:
+% \begin{keypoints}
+% \item	List up to three key points (at least one is required)
+% \item	Key Points summarize the main points and conclusions of the article
+% \item	Each must be 140 characters or fewer with no special characters or punctuation and must be complete sentences
+% \end{keypoints}
+
+\begin{keypoints}
+\item enter point 1 here
+\item enter point 2 here
+\item enter point 3 here
+\end{keypoints}
+
+\begin{abstract}
 Global storm-resolving models (GSRMs) are the next avenue of climate modelling.
@@
 microphysics) were not enough to address the model cloud biases.
+\end{abstract}
 
@@
 Increasing climate model resolution is one way of improving model accuracy of
-representation of the climate system \citep{mauritsen2022}. It has been
+representation of the climate system \citeA{mauritsen2022}. It has been
 practiced since the advent of climate modelling as more computational power,
@@
 in the development of high-resolution global climate models, with horizontal
-grid resolutions of about 2--8 km \citep{satoh2019,stevens2019}. This is enough
+grid resolutions of about 2--8 km \citeA{satoh2019,stevens2019}. This is enough
 to resolve mesoscale convective storms, but smaller-scale convective plumes and
 cloud structure remain unresolved. At an approximately 5-km scale,
-non-hydrostatic processes also become important \citep{weisman1997}, and for
+non-hydrostatic processes also become important \citeA{weisman1997}, and for
 this reason such models are generally non-hydrostatic. The terms global
@@
 convection are resolved explicitly, which is not entirely true for GSRMs, as
-this would require an even higher horizontal resolution \citep{satoh2019}.
+this would require an even higher horizontal resolution \citeA{satoh2019}.
 Representative of these efforts is the DYnamics of the Atmospheric general
 circulation Modeled On Non-hydrostatic Domains (DYAMOND) project
-\citep{stevens2019,dyamond}, which is an intercomparison of nine global GSRMs
+\citeA{stevens2019,dyamond}, which is an intercomparison of nine global GSRMs
 over two 40-day time periods in summer (1 August -- 10 September 2016) and
 winter (20 January -- 1 March 2020). A new one-year GSRM intercomparison is
-currently proposed by \cite{takasuka2024}, with the hope of also evaluating the
+currently proposed by \citeA{takasuka2024}, with the hope of also evaluating the
 seasonal cycle and large-scale circulation.  An alternative to using a
@@
 output and use it for subgrid-scale clouds, as done with the GSRM ICON by
-\cite{grundner2022} and \cite{grundner2023}.
-
-nextGEMS is a project \citep{nextgems} focused on the research and development
+\citeA{grundner2022} and \citeA{grundner2023}.
+
+nextGEMS is a project \citeA{nextgems} focused on the research and development
 of GSRMs at multiple modelling centres and universities in Europe.  The project
 also develops GSRM versions of the Icosahedral Nonhydrostatic Weather and
-Climate Model (ICON; \cite{hohenegger2023}), the Integrated Forecasting System
-[IFS; \cite{ifs2023}], and their ocean components at eddy-resolving
-resolutions: ICON-O \citep{korn2022} coupled with ICON and
-Finite-Element/volumE Sea ice-Ocean Model [FESOM; \cite{wang2014}] and Nucleus
-for European Modelling of the Ocean [NEMO; \cite{madec2023}] coupled with IFS.
+Climate Model (ICON; \citeA{hohenegger2023}), the Integrated Forecasting System
+[IFS; \citeA{ifs2023}], and their ocean components at eddy-resolving
+resolutions: ICON-O \citeA{korn2022} coupled with ICON and
+Finite-Element/volumE Sea ice-Ocean Model [FESOM; \citeA{wang2014}] and Nucleus
+for European Modelling of the Ocean [NEMO; \citeA{madec2023}] coupled with IFS.
 The project has so far produced ICON and IFS simulations with three development
@@
 development include: Convection-Permitting Simulations With the E3SM Global
-Atmosphere Model [SCREAM; \cite{caldwell2021}], Atmospheric Model [NICAM;
-\cite{satoh2008}], Unified Model (UM), eXperimental System for High-resolution
-modeling for Earth-to-Local Domain [X-SHiELD; \cite{shield}], Action de
+Atmosphere Model [SCREAM; \citeA{caldwell2021}], Atmospheric Model [NICAM;
+\citeA{satoh2008}], Unified Model (UM), eXperimental System for High-resolution
+modeling for Earth-to-Local Domain [X-SHiELD; \citeA{shield}], Action de
 Recherche Petite Echelle Grande Echelle-NonHydrostatic version [ARPEGE-NH;
-\cite{bubnova1995,voldoire2017}], Finite-Volume Dynamical Core on the Cubed
-Sphere [FV3, \cite{lin2004}], the National Aeronautics and Space Administration
+\citeA{bubnova1995,voldoire2017}], Finite-Volume Dynamical Core on the Cubed
+Sphere [FV3, \citeA{lin2004}], the National Aeronautics and Space Administration
 (NASA) Goddard Earth Observing System global atmospheric model version 5
-[GEOS5; \cite{putman2011}], Model for Prediction Across Scales [MPAS;
-\cite{skamarock2012}], and System for Atmospheric Modeling [SAM;
-\cite{khairoutdinov2003}].
+[GEOS5; \citeA{putman2011}], Model for Prediction Across Scales [MPAS;
+\citeA{skamarock2012}], and System for Atmospheric Modeling [SAM;
+\citeA{khairoutdinov2003}].
 
@@
 6$^\mathrm{th}$ phase of the Coupled Model Intercomparison Project [CMIP6;
-\cite{eyring2016}], the cloud feedback has increased relative to CMIP5
-\citep{zelinka2020}, which is one of the main reasons for the higher climate
+\citeA{eyring2016}], the cloud feedback has increased relative to CMIP5
+\citeA{zelinka2020}, which is one of the main reasons for the higher climate
 sensitivity of CMIP6 models.
@@
 The Southern Ocean (SO) is known to be a problematic region for climate model
-biases \citep{schuddeboom2021,hyder2018,cesana2022,zhao2022} due to a lack of
+biases \citeA{schuddeboom2021,hyder2018,cesana2022,zhao2022} due to a lack of
 surface and in situ observations and being a lower priority region for
@@
 an area of its size have a substantial influence on the global climate
-\citep{rintoul2011}, such as affecting the Earth radiation balance, ocean heat
-and carbon uptake \citep{williams2023}, and the SO is an important part of the
-global ocean conveyor belt \citep{wang2014}. In general, marine clouds have a
+\citeA{rintoul2011}, such as affecting the Earth radiation balance, ocean heat
+and carbon uptake \citeA{williams2023}, and the SO is an important part of the
+global ocean conveyor belt \citeA{wang2014}. In general, marine clouds have a
 disproportionate effect on top of atmosphere (TOA) SW radiation due to the
@@
 for this dividing latitude is to split the SO into about two equal zones, as
-well as the results by \cite{schuddeboom2021} (Fig. 2b), showing a contrast in
-CMIP model radiation biases, \cite{schuddeboom2019} (Fig. 2) and
-\cite{kuma2020} (Fig. 3) showing contrasting radiation biases in the Hadley
-Centre Global Environmental Model, and \cite{cesana2022} showing contrasting
+well as the results by \citeA{schuddeboom2021} (Fig. 2b), showing a contrast in
+CMIP model radiation biases, \citeA{schuddeboom2019} (Fig. 2) and
+\citeA{kuma2020} (Fig. 3) showing contrasting radiation biases in the Hadley
+Centre Global Environmental Model, and \citeA{cesana2022} showing contrasting
 cloud biases due to the 0°C isotherm reaching the surface at 55°S. The findings
-of \cite{niu2024}, however, support a different dividing line of 62°S based on
+of \citeA{niu2024}, however, support a different dividing line of 62°S based on
 cloud condensation nuclei concentration.
@@
 SO radiation biases have been relatively large and systematic compared to the
-rest of the globe since at least CMIP3 \citep{trenberth2010}, and the SO SW
+rest of the globe since at least CMIP3 \citeA{trenberth2010}, and the SO SW
 cloud radiative effect (CRE) bias is still positive in eight analysed CMIP6
-models analysed by \cite{schuddeboom2021} over the high-latitude SO, whereas
+models analysed by \citeA{schuddeboom2021} over the high-latitude SO, whereas
 over the low-latitude SO it tends to be more neutral or negative in some
 models. Too much absorbed SW radiation over the SO was also identified in the
-GSRM SCREAM \cite{caldwell2021}. Compensating biases are possible, such as the
+GSRM SCREAM \citeA{caldwell2021}. Compensating biases are possible, such as the
 `too few too bright' cloud bias, characterised by too small cloud fraction and
-too large cloud albedo \citep{wall2017,kuma2020}, previously described by
-\cite{webb2001}, \cite{weare2004}, \cite{zhang2005}, \cite{karlsson2008},
-\cite{nam2012}, \cite{klein2013}, and \cite{bender2017} in other regions and
+too large cloud albedo \citeA{wall2017,kuma2020}, previously described by
+\citeA{webb2001}, \citeA{weare2004}, \citeA{zhang2005}, \citeA{karlsson2008},
+\citeA{nam2012}, \citeA{klein2013}, and \citeA{bender2017} in other regions and
 models, which means that a model can maintain a reasonable SW radiation balance
 by reflecting too much SW radiation from clouds, but these cover too small
-area.  A study by \cite{konsta2022} showed that this type of bias is still
+area.  A study by \citeA{konsta2022} showed that this type of bias is still
 present in six analysed CMIP6 models in tropical marine clouds, using the
 GCM-Oriented Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observation
-(CALIPSO) Cloud Product [CALIPSO--GOCCP; \cite{chepfer2010}] and Polarization
+(CALIPSO) Cloud Product [CALIPSO--GOCCP; \citeA{chepfer2010}] and Polarization
 \& Anisotropy of Reflectances for Atmospheric Sciences coupled with
-Observations from a Lidar [PARASOL; \cite{lier2008}] as a reference. They
+Observations from a Lidar [PARASOL; \citeA{lier2008}] as a reference. They
 suggest improper simulation of subgrid-scale cloud heterogeneity as a cause.
@@
 Simulator (ACCESS) – Atmosphere-only model version 2 (AM2) over the SO were
-analysed by \cite{fiddes2022} and \cite{fiddes2024}.  \cite{possner2022} showed
+analysed by \citeA{fiddes2022} and \citeA{fiddes2024}.  \citeA{possner2022} showed
 that over the SO, the DYAMOND GSRM ICON underestimates low-level cloud fraction
@@
 System (CERES) data] in the highest model resolution run (2.5 km).
-\cite{zhao2022} reported a similar SW radiation bias in five analysed CMIP6
+\citeA{zhao2022} reported a similar SW radiation bias in five analysed CMIP6
 models over high-latitude SO and the total cloud fraction underestimation on
-the order of 10\% over the entire 40--60°S SO. Recently, \cite{ramadoss2024}
+the order of 10\% over the entire 40--60°S SO. Recently, \citeA{ramadoss2024}
 analysed 48 hours of km-scale ICON limited area model NWP simulations over a SO
@@
 Radiation, and atmospherIc Composition Over the southeRn oceaN (CAPRICORN)
-voyage cloud and precipitation observations \cite{mcfarquhar2021}. They found
+voyage cloud and precipitation observations \citeA{mcfarquhar2021}. They found
 the ICON cloud optical thickness was underestimated relative to Himawari‐8
@@
 In general, sea surface temperature (SST) biases in the SO can originate either
-in the atmosphere \citep{hyder2018}, caused by too much shortwave heating of
+in the atmosphere \citeA{hyder2018}, caused by too much shortwave heating of
 the surface, too little longwave cooling of the surface, or in the ocean
@@
 for Medium-Range Weather Forecasts (ECMWF) Reanalysis 5 (ERA5) as a reference,
-\cite{zhang2023} have shown that SST biases have improved in CMIP6 compared to
+\citeA{zhang2023} have shown that SST biases have improved in CMIP6 compared to
 CMIP5, with SST overall increasing in the later CMIP phase. However, over the
 SO this resulted in an even higher positive bias, especially in the Atlantic
-Ocean (AO) sector of the SO, increasing by up to 1°C.  \cite{luo2023}
+Ocean (AO) sector of the SO, increasing by up to 1°C.  \citeA{luo2023}
 identified that the SO SST bias in an ensemble of 18 CMIP6 models originates
@@
 problematic to observe by spaceborne lidars and radars, which are affected by
-attenuation by overlapping and thick clouds \citep{mace2009,medeiros2010} and
-ground clutter \citep{marchand2008}, respectively.  Specifically, the radar on
+attenuation by overlapping and thick clouds \citeA{mace2009,medeiros2010} and
+ground clutter \citeA{marchand2008}, respectively.  Specifically, the radar on
 CloudSat and lidar on CALIPSO (neither of which are nowoperational) are
@@
 cloud occurrence below 2 km relative to ground-based lidar observations
-\citep{mcerlich2021}.  We hypothesise that this, in turn, can lead to
+\citeA{mcerlich2021}.  We hypothesise that this, in turn, can lead to
 systematic biases in low clouds in climate models, which are frequently
@@
 simulator called the Automatic Lidar and Ceilometer Framework [ALCF;
-\cite{kuma2021}]. We contrasted the results with ERA5 \citep{era5} and the
+\citeA{kuma2021}]. We contrasted the results with ERA5 \citeA{era5} and the
 Modern-Era Retrospective analysis for Research and Applications, Version 2
-[MERRA-2; \cite{gelaro2017}].
+[MERRA-2; \citeA{gelaro2017}].
 
@@
 and dynamic physical quantities (wind speed and direction) for the measured
-vertical profiles were calculated with rstool \citep{rstool}. Surface
+vertical profiles were calculated with rstool \citeA{rstool}. Surface
 meteorological quantities were measured continuously by an onboard automatic
@@
 \label{tab:voyages}
+\centering
 \small
@@
 \textbf{Total} &                         &         &          &            &            & \textbf{2421}\\
+\hline
 \end{tabular}
@@
 \label{tab:voyage-references}
+\centering
 \small
@@
 \hline
-AA15-16  & \cite{klekociuk2020} \\
-MARCUS   & \cite{mcfarquhar2021,xia2024,niu2024} \\
-MICRE    & \cite{mcfarquhar2021} \\
-NBP1704  & \cite{ackley2020} \\
-PS77/2   & \cite{kniglanglo2011a,kniglanglo2011b,kniglanglo2011c,kniglanglo2014a,fahrbach2011} \\
-PS77/3   & \cite{kniglanglo2011d,kniglanglo2011e,kniglanglo2012a,kniglanglo2014b,knust2011} \\
-PS79/2   & \cite{kniglanglo2012b,kniglanglo2012c,kniglanglo2012d,kniglanglo2014c,kattner2012} \\
-PS79/3   & \cite{kniglanglo2012e,kniglanglo2012f,kniglanglo2012g,kniglanglo2014d,wolfgladrow2012} \\
-PS79/4   & \cite{kniglanglo2012h,kniglanglo2012i,kniglanglo2012j,kniglanglo2014e,lucassen2012} \\
-PS81/2   & \cite{kniglanglo2013a,kniglanglo2013b,kniglanglo2013c,kniglanglo2014f,boebel2013} \\
-PS81/3   & \cite{kniglanglo2013d,kniglanglo2013e,kniglanglo2013f,kniglanglo2014g,gutt2013} \\
-PS81/4   & \cite{kniglanglo2013g,kniglanglo2013h,kniglanglo2013i,kniglanglo2014f,bohrmann2013} \\
-PS81/5   & \cite{kniglanglo2013j,kniglanglo2013k,kniglanglo2013l,kniglanglo2014g,jokat2013} \\
-PS81/6   & \cite{kniglanglo2013m,kniglanglo2013n,kniglanglo2013o,kniglanglo2014h,lemke2013} \\
-PS81/7   & \cite{kniglanglo2013p,kniglanglo2013q,kniglanglo2014i,kniglanglo2016a,meyer2013} \\
-PS81/8   & \cite{kniglanglo2013r,kniglanglo2014j,kniglanglo2014k,kniglanglo2014l,schlindwein2014} \\
-PS81/9   & \cite{kniglanglo2014m,kniglanglo2014n,kniglanglo2014o,kniglanglo2014p,knust2014} \\
-PS89     & \cite{kniglanglo2015a,kniglanglo2015b,kniglanglo2015c,kniglanglo2015d,boebel2016}\\
-PS96     & \cite{kniglanglo2016b,kniglanglo2016c,kniglanglo2016d,kniglanglo2016e,schrder2017} \\
-PS97     & \cite{kniglanglo2016f,kniglanglo2016g,kniglanglo2016h,kniglanglo2016i,lamy2017} \\
-PS103    & \cite{kniglanglo2017a,kniglanglo2017b,kniglanglo2017c,kniglanglo2017d,boebel2018} \\
-PS104    & \cite{kniglanglo2017e,kniglanglo2017f,kniglanglo2017g,gohl2018,schmithsen2021a} \\
-PS111    & \cite{schmithsen2019a,schmithsen2020a,schmithsen2021b,schmithsen2021c,schrder2018} \\
-PS112    & \cite{schmithsen2019b,schmithsen2020b,schmithsen2021d,schmithsen2021e,meyer2018} \\
-PS117    & \cite{schmithsen2019c,schmithsen2020c,schmithsen2021f,schmithsen2021g,boebel2019} \\
-PS118    & \cite{schmithsen2019d,schmithsen2020d,schmithsen2021h,schmithsen2021i,dorschel2019} \\
-PS123    & \cite{schmithsen2021j,schmithsen2021m,schmithsen2021n,schmithsen2021k,hoppmann2023} \\
-PS124    & \cite{schmithsen2021o,schmithsen2021q,schmithsen2021p,hoppmann2023} \\
-TAN1802  & \cite{kremser2020,kremser2021} \\
+AA15-16  & \citeA{klekociuk2020} \\
+MARCUS   & \citeA{mcfarquhar2021,xia2024,niu2024} \\
+MICRE    & \citeA{mcfarquhar2021} \\
+NBP1704  & \citeA{ackley2020} \\
+PS77/2   & \citeA{kniglanglo2011a,kniglanglo2011b,kniglanglo2011c,kniglanglo2014a,fahrbach2011} \\
+PS77/3   & \citeA{kniglanglo2011d,kniglanglo2011e,kniglanglo2012a,kniglanglo2014b,knust2011} \\
+PS79/2   & \citeA{kniglanglo2012b,kniglanglo2012c,kniglanglo2012d,kniglanglo2014c,kattner2012} \\
+PS79/3   & \citeA{kniglanglo2012e,kniglanglo2012f,kniglanglo2012g,kniglanglo2014d,wolfgladrow2012} \\
+PS79/4   & \citeA{kniglanglo2012h,kniglanglo2012i,kniglanglo2012j,kniglanglo2014e,lucassen2012} \\
+PS81/2   & \citeA{kniglanglo2013a,kniglanglo2013b,kniglanglo2013c,kniglanglo2014f,boebel2013} \\
+PS81/3   & \citeA{kniglanglo2013d,kniglanglo2013e,kniglanglo2013f,kniglanglo2014g,gutt2013} \\
+PS81/4   & \citeA{kniglanglo2013g,kniglanglo2013h,kniglanglo2013i,kniglanglo2014f,bohrmann2013} \\
+PS81/5   & \citeA{kniglanglo2013j,kniglanglo2013k,kniglanglo2013l,kniglanglo2014g,jokat2013} \\
+PS81/6   & \citeA{kniglanglo2013m,kniglanglo2013n,kniglanglo2013o,kniglanglo2014h,lemke2013} \\
+PS81/7   & \citeA{kniglanglo2013p,kniglanglo2013q,kniglanglo2014i,kniglanglo2016a,meyer2013} \\
+PS81/8   & \citeA{kniglanglo2013r,kniglanglo2014j,kniglanglo2014k,kniglanglo2014l,schlindwein2014} \\
+PS81/9   & \citeA{kniglanglo2014m,kniglanglo2014n,kniglanglo2014o,kniglanglo2014p,knust2014} \\
+PS89     & \citeA{kniglanglo2015a,kniglanglo2015b,kniglanglo2015c,kniglanglo2015d,boebel2016}\\
+PS96     & \citeA{kniglanglo2016b,kniglanglo2016c,kniglanglo2016d,kniglanglo2016e,schrder2017} \\
+PS97     & \citeA{kniglanglo2016f,kniglanglo2016g,kniglanglo2016h,kniglanglo2016i,lamy2017} \\
+PS103    & \citeA{kniglanglo2017a,kniglanglo2017b,kniglanglo2017c,kniglanglo2017d,boebel2018} \\
+PS104    & \citeA{kniglanglo2017e,kniglanglo2017f,kniglanglo2017g,gohl2018,schmithsen2021a} \\
+PS111    & \citeA{schmithsen2019a,schmithsen2020a,schmithsen2021b,schmithsen2021c,schrder2018} \\
+PS112    & \citeA{schmithsen2019b,schmithsen2020b,schmithsen2021d,schmithsen2021e,meyer2018} \\
+PS117    & \citeA{schmithsen2019c,schmithsen2020c,schmithsen2021f,schmithsen2021g,boebel2019} \\
+PS118    & \citeA{schmithsen2019d,schmithsen2020d,schmithsen2021h,schmithsen2021i,dorschel2019} \\
+PS123    & \citeA{schmithsen2021j,schmithsen2021m,schmithsen2021n,schmithsen2021k,hoppmann2023} \\
+PS124    & \citeA{schmithsen2021o,schmithsen2021q,schmithsen2021p,hoppmann2023} \\
+TAN1802  & \citeA{kremser2020,kremser2021} \\
+\hline
 \end{tabular}
@@
 and 910 nm are affected by water vapour absorption of about 20\% in the
-mid-latitudes \citep{wiegner2015,wiegner2019}, with 910 nm affected more
+mid-latitudes \citeA{wiegner2015,wiegner2019}, with 910 nm affected more
 strongly, but we do not expect this to be a significant issue as explained in
-\cite{kuma2021}.  The instrument data files containing raw uncalibrated
+\citeA{kuma2021}.  The instrument data files containing raw uncalibrated
 backscatter were first converted to Network Common Data Form (NetCDF) with
@@
 simulator and a tool for processing observed lidar data, supporting various
-instruments and models \citep{kuma2021}. It performs radiative transfer
+instruments and models \citeA{kuma2021}. It performs radiative transfer
 calculations to derive equivalent lidar AVBC in an atmospheric model, which can
@@
 simulator Cloud Feedback Model Intercomparison Project (CFMIP) Observation
-Simulator Package (COSP) \citep{bodas-salcedo2011}.  After AVBC is calculated,
+Simulator Package (COSP) \citeA{bodas-salcedo2011}.  After AVBC is calculated,
 a cloud mask, cloud occurrence by height, and the total cloud fraction are
@@
 reanalysis evaluation
-\citep{kuma2020,kremser2021,guyot2022,pei2023,whitehead2023,mcdonald2024}.
+\citeA{kuma2020,kremser2021,guyot2022,pei2023,whitehead2023,mcdonald2024}.
 
@@
 A coupled (atmosphere--ocean) GSRM version of the ICON model is in development
-at the nextGEMS project \citep{hohenegger2023}. ICON is an exceptionally
+at the nextGEMS project \citeA{hohenegger2023}. ICON is an exceptionally
 versatile model, allowing for simulations ranging from coarse-resolution ESM
@@
 simulations (LES), for both weather prediction and climate projections. ICON
-uses the atmospheric component ICON-A \citep{giorgetta2018}, whose physics is
-derived from ECHAM6 \citep{stevens2013}, and the ocean component ICON-O
-\citep{korn2022}. Earlier runs of the GSRM ICON from DYAMOND were evaluated by
-\cite{mauritsen2022}.
+uses the atmospheric component ICON-A \citeA{giorgetta2018}, whose physics is
+derived from ECHAM6 \citeA{stevens2013}, and the ocean component ICON-O
+\citeA{korn2022}. Earlier runs of the GSRM ICON from DYAMOND were evaluated by
+\citeA{mauritsen2022}.
 
@@
 projection.  nextGEMS has so far produced four cycles of model runs. We used a
-Cycle 3 run \emph{ngc3028} produced in 2023 \citep{nextgems2023a,nextgems2023b}
+Cycle 3 run \emph{ngc3028} produced in 2023 \citeA{nextgems2023a,nextgems2023b}
 for a model time period of 20 January 2020 to 22 July 2025, of which we
@@
 (MERRA-2) is a reanalysis produced by the Global Modeling and Assimilation
-Office at the NASA Goddard Space Flight Center \citep{gelaro2017}.  It uses
+Office at the NASA Goddard Space Flight Center \citeA{gelaro2017}.  It uses
 version 5.12.4 of the Goddard Earth Observing System (GEOS) atmospheric model
-\citep{rienecker2008,molod2015}. Non-convective clouds (condensation,
+\citeA{rienecker2008,molod2015}. Non-convective clouds (condensation,
 autoconversion, and evaporation) are parametrised using a prognostic scheme
-\citep{bacmeister2006}, and sub-grid cloud fraction is determined using total
+\citeA{bacmeister2006}, and sub-grid cloud fraction is determined using total
 water distribution and a critical relative humidity threshold. The reanalysis
@@
 diagnostics (M2T1NXFLX) for precipitation; and 1-hourly average 2D radiation
-diagnostics (M2T1NXRAD) for radiation quantities \citep{merra2}.
+diagnostics (M2T1NXRAD) for radiation quantities \citeA{merra2}.
 
@@
 
-ERA5 \citep{era5} is a reanalysis produced by the ECMWF.  It is based on a
+ERA5 \citeA{era5} is a reanalysis produced by the ECMWF.  It is based on a
 numerical weather prediction model IFS version CY41R2.  It uses the
-\cite{tiedtke1993} prognostic cloud scheme and \cite{forbes2014} for
+\citeA{tiedtke1993} prognostic cloud scheme and \citeA{forbes2014} for
 mixed-phase clouds. The horizontal resolution is 0.25° in latitude and
@@
 TOA radiation quantities are taken from the CERES instruments onboard the Terra
-and Aqua satellites \citep{wielicki1996,loeb2018}. In our analysis we used the
+and Aqua satellites \citeA{wielicki1996,loeb2018}. In our analysis we used the
 adjusted all sky SW and LW upwelling fluxes at TOA from the synoptic TOA and
@@
 (CER\_SYN1deg-Day\_Terra-Aqua-MODIS\_Edition4A)
-\citep{doelling2013,doelling2016}.
+\citeA{doelling2013,doelling2016}.
 
@@
 \ref{fig:ann}a), implemented in the TensorFlow ANN framework
-\citep{tensorflow}. Samples of short time intervals (10 min) of near-surface
+\citeA{tensorflow}. Samples of short time intervals (10 min) of near-surface
 lidar backscatter (0–250 m) were classified as clear, rain, snow, and fog,
@@
 and ICON data. We used the open source cyclone tracking package CyTRACK
-\citep{perez-alarcon2024}.  Generally, what constitutes an EC is considered
-relatively arbitrary due to the very large variability of ECs \citep{neu2013}.
+\citeA{perez-alarcon2024}.  Generally, what constitutes an EC is considered
+relatively arbitrary due to the very large variability of ECs \citeA{neu2013}.
 We used the mean sea level pressure field and horizontal wind speed fields as
@@
 in the high-latitude SO zone, and it is relatively zonally symmetric at all
-latitudes.  The pattern matches reasonably well with \cite{hoskins2005}. While
+latitudes.  The pattern matches reasonably well with \citeA{hoskins2005}. While
 both reanalysis and the model agree relatively well, there are clear
 differences particularly in the highest occurrence rate regions -- over the
-Amundsen Sea, where the Amundsen Sea low is located \cite{turner2013} and which
+Amundsen Sea, where the Amundsen Sea low is located \citeA{turner2013} and which
 is more cyclonic in the reanalysis, and around Cape Adare, which is more
@@
 In the high-latitude SO, the presence of sea ice might have substantial
-stabilising effect \citep{knight2024}. The ERA5 reanalysis is also
+stabilising effect \citeA{knight2024}. The ERA5 reanalysis is also
 substantially more stable than ICON across the whole region.
@@
 near-surface relative humidity is similar to the observations (Fig.
-\ref{potential-temperature}), the distribution in observation is more spread
+\ref{fig:potential-temperature}), the distribution in observation is more spread
 out across both high and low values, and thus observations have a greater
 prevalence of relative humidity close to 100\% and thus LCL located at the
-surface (Fig. \ref{cloud-occurrence}a). In our calculations, LCL is a exclusive
+surface (Fig. \ref{fig:cloud-occurrence}a). In our calculations, LCL is a exclusive
 function of near-surface temperature, near-surface relative humidity and
@@
 high-level clouds are better sampled by satellite observations
-\citep{mcerlich2021}.
+\citeA{mcerlich2021}.
 
@@
 might be explained by the radiosonde comparison, showing that it is too moist
-at around this height.  Similar to our results, \cite{cesana2022} showed that
+at around this height.  Similar to our results, \citeA{cesana2022} showed that
 CMIP6 models also tend to underestimate cloud occurrence above 2 km over the
@@
 surface, among other factors responsible for SO SST biases in climate models
-\citep{zhang2023,luo2023,hyder2018}.  To some extent, the cloud albedo might be
+\citeA{zhang2023,luo2023,hyder2018}.  To some extent, the cloud albedo might be
 reduced in the model artifically by the application of an inhomogeneity factor
@@
 
-\fontsize{12pt}{14pt}\selectfont
-\section*{Acknowledgements}
+\section*{Open Research Section}
+
+The RV \emph{Polarstern} datasets are openly available on Pangaea
+(\url{https://pangaea.de}). The MARCUS and MICRE datasets are openly available
+from ARM (\url{https://www.arm.gov}). The MERRA-2 data are openly available
+from the NASA Goddard Earth Sciences (GES) Data and Information Services Center
+(DISC) (\url{https://disc.gsfc.nasa.gov/datasets?project=MERRA-2}).  The ERA5
+data are openly available from the Copernicus Climate Data Store (CDS)
+(\url{https://cds.climate.copernicus.eu}). The ICON data are available on the
+Levante cluster of the DKRZ
+(\url{https://www.dkrz.de/en/systems/hpc/hlre-4-levante}) after registration at
+\url{https://luv.dkrz.de/register/}. The CERES products are available from the
+project website (\url{https://ceres.larc.nasa.gov}) and the NASA Atmospheric
+Science Data Centre (\url{https://asdc.larc.nasa.gov/project/CERES}).  The
+TAN1802 data are available on Zenodo
+(\url{https://doi.org/10.5281/zenodo.4060237}).
+
+% TODO: The other voyage and station data are openly available on Zenodo ().
+% Subsetted model and reanalysis data for the voyage tracks and the station and
+% data processed with the ALCF are openly available on Zenodo ().
+
+\acknowledgments
 
@@
 naturalearthdata.com.  Last but not least, we acknowledge the use of open
-source software Python, Cython \citep{behnel2011}, TensorFlow
-\citep{abadi2016}, Devuan GNU+Linux, parallel \citep{tange2011}, NumPy
-\citep{harris2020}, SciPy \citep{virtanen2020}, Matplotlib \citep{hunter2007},
-cartopy \citep{cartopy}, pyproj, Inkscape, Bash, GNU Fortran, HDF
-\citep{folk1999}, and NetCDF \citep{rew1990}.  We dedicate this study to the
+source software Python, Cython \cite{behnel2011}, TensorFlow
+\cite{abadi2016}, Devuan GNU+Linux, parallel \cite{tange2011}, NumPy
+\cite{harris2020}, SciPy \cite{virtanen2020}, Matplotlib \cite{hunter2007},
+cartopy \cite{cartopy}, pyproj, Inkscape, Bash, GNU Fortran, HDF
+\cite{folk1999}, and NetCDF \cite{rew1990}.  We dedicate this study to the
 memory of Mike J.  Harvey, who very substantially contributed to obtaining the
@@
 
-\section*{Code availability}
-
-The ALCF, cl2nc, rstool, lidar precipitation detection code, and our data
-processing and plotting code are open source and available at
-\url{https://alcf.peterkuma.net}, \url{https://github.com/peterkuma/cl2nc},
-\url{https://github.com/peterkuma/rstool}, and
-\url{https://github.com/peterkuma/alcf-precip},
-\url{https://github.com/peterkuma/icon-so-2024}, respectively. CyTRACK is
-available at \url{https://github.com/apalarcon/CyTRACK}. The ICON model is
-available at \url{https://gitlab.dkrz.de/icon/icon-mpim}.
-
-\section*{Data availability}
-
-The RV \emph{Polarstern} datasets are openly available on Pangaea
-(\url{https://pangaea.de}). The MARCUS and MICRE datasets are openly available
-from ARM (\url{https://www.arm.gov}). The MERRA-2 data are openly available
-from the NASA Goddard Earth Sciences (GES) Data and Information Services Center
-(DISC) (\url{https://disc.gsfc.nasa.gov/datasets?project=MERRA-2}).  The ERA5
-data are openly available from the Copernicus Climate Data Store (CDS)
-(\url{https://cds.climate.copernicus.eu}). The ICON data are available on the
-Levante cluster of the DKRZ
-(\url{https://www.dkrz.de/en/systems/hpc/hlre-4-levante}) after registration at
-\url{https://luv.dkrz.de/register/}. The CERES products are available from the
-project website (\url{https://ceres.larc.nasa.gov}) and the NASA Atmospheric
-Science Data Centre (\url{https://asdc.larc.nasa.gov/project/CERES}).  The
-TAN1802 data are available on Zenodo
-(\url{https://doi.org/10.5281/zenodo.4060237}).
-
-% TODO: The other voyage and station data are openly available on Zenodo ().
-% Subsetted model and reanalysis data for the voyage tracks and the station and
-% data processed with the ALCF are openly available on Zenodo ().
-
-\section*{Author contributions}
-
-The authors have made the following contributions based on the CRediT taxonomy
-(\url{https://credit.niso.org}).  PK: conceptualization, data curation, formal
-analysis, investigation, methodology, software, writing – original draft; FAMB:
-conceptualization, funding acquisition, project administration, supervision,
-and writing – review \& editing; AJM, SPA, GMM, JJC, GEP, SH, SP, SG, and AJS:
-data curation, investigation, resources, writing – review \& editing.
-
-%\footnotesize
-\fontsize{11pt}{13pt}\selectfont
-\setlength{\bibsep}{0.0pt}
 \bibliography{manuscript}

### 2024-12-09 manuscript_agu.tex
Reformat text

@@
 Global storm-resolving models (GSRMs) are the next avenue of climate modelling.
-Among them is a 5-km version of the Icosahedral Nonhydrostatic Weather and
-Climate Model (ICON). The high resolution means that parameterizations of
-convection and clouds including subgrid-scale clouds are forgone, relying on
-explicit their simulation, but still using microphysics and turbulence
-parametrization.  Standard-resolution (10--100-km) models, which use
-subgrid-scale convection and cloud parametrization, have substantial cloud
-biases over the Southern Ocean (SO), affecting radiation and sea surface
-temperature.  We evaluated SO clouds in ICON and the ERA5 and MERRA-2
-reanalyses.  The SO is dominated by low clouds, which cannot be observed
-accurately from space due to overlapping clouds, attenuation, and ground
-clutter.  Instead, we analysed about 2400 days of lidar observations from 31
-voyages and a station during 2010--2021 using a ground-based lidar simulator.
-ICON and the reanalyses underestimate the total cloud fraction by about 10 and
-20\%, respectively. ICON and ERA5 overestimate the cloud occurrence peak at
-about 500 m, potentially explained by their lifting condensation levels being
-too high.  The reanalyses strongly underestimate near-surface clouds or fog.
-MERRA-2 tends to underestimate cloud occurrence at all heights.  In daily cloud
-cover, ICON and the reanalyses tend to be about 1 and 2 oktas clearer,
-respectively.  Conditions of weak stability are associated with the largest
-errors in ICON and the reanalyses.  Compared to radiosondes, potential
-temperature is accurate in the reanalyses to about 0.5 K, but ICON
-underestimates stability over the low-latitude SO and too humid in the boundary
-layer. MERRA-2 is too humid at all heights. SO cloud biases remain a
-substantial issue in the GSRM, but are an improvement over the lower-resolution
-reanalyses. Explicitly resolved convection and cloud processes (except
-microphysics) were not enough to address the model cloud biases.
+Among them is a 5-km version of the Icosahedral Nonhydrostatic Weather and Climate Model (ICON).
+The high resolution means that parameterizations of convection and clouds including subgrid-scale clouds are forgone, relying on explicit their simulation, but still using microphysics and turbulence parametrization.
+Standard-resolution (10--100-km) models, which use subgrid-scale convection and cloud parametrization, have substantial cloud biases over the Southern Ocean (SO), affecting radiation and sea surface temperature.
+We evaluated SO clouds in ICON and the ERA5 and MERRA-2 reanalyses.
+The SO is dominated by low clouds, which cannot be observed accurately from space due to overlapping clouds, attenuation, and ground clutter.
+Instead, we analysed about 2400 days of lidar observations from 31 voyages and a station during 2010--2021 using a ground-based lidar simulator.
+ICON and the reanalyses underestimate the total cloud fraction by about 10 and 20\%, respectively.
+ICON and ERA5 overestimate the cloud occurrence peak at about 500 m, potentially explained by their lifting condensation levels being too high.
+The reanalyses strongly underestimate near-surface clouds or fog.
+MERRA-2 tends to underestimate cloud occurrence at all heights.
+In daily cloud cover, ICON and the reanalyses tend to be about 1 and 2 oktas clearer, respectively.
+Conditions of weak stability are associated with the largest errors in ICON and the reanalyses.
+Compared to radiosondes, potential temperature is accurate in the reanalyses to about 0.5 K, but ICON underestimates stability over the low-latitude SO and too humid in the boundary layer.
+MERRA-2 is too humid at all heights.
+SO cloud biases remain a substantial issue in the GSRM, but are an improvement over the lower-resolution reanalyses.
+Explicitly resolved convection and cloud processes (except microphysics) were not enough to address the model cloud biases.
 \end{abstract}
+
+\section*{Plain Language Summary}
+Enter your Plain Language Summary here or delete this section.
+Here are instructions on writing a Plain Language Summary:
+https://www.agu.org/Share-and-Advocate/Share/Community/Plain-language-summary
 
@@
 
-Increasing climate model resolution is one way of improving model accuracy of
-representation of the climate system \citeA{mauritsen2022}. It has been
-practiced since the advent of climate modelling as more computational power,
-memory, and storage capacity become available. It is, however, often not as
-easy as changing the grid size because of the complex interplay between model
-dynamics and physics, which necessitates adjusting and tuning all components
-together.  Increasing resolution is of course limited by the available
-computational power and a trade-off with increasing parameterization
-complexity, which is another way of improving model accuracy.  Current
-computational availability and acceleration from general-purpose computing on
-graphics processing units (GPUs) is progressing to enable km-scale (also called
-k-scale) Earth system models (ESMs) and coupled atmosphere--ocean general
-circulation models (AOGCMs) in research conditions today and operationally in
-the forthcoming years.  Therefore, it represents a natural advance in climate
-modelling.  Global storm-resolving models (GSRMs) are emerging as a new front
-in the development of high-resolution global climate models, with horizontal
-grid resolutions of about 2--8 km \citeA{satoh2019,stevens2019}. This is enough
-to resolve mesoscale convective storms, but smaller-scale convective plumes and
-cloud structure remain unresolved. At an approximately 5-km scale,
-non-hydrostatic processes also become important \citeA{weisman1997}, and for
-this reason such models are generally non-hydrostatic. The terms global
-cloud-resolving models or global convection-permitting/-resolving models are
-also sometimes used interchangeably with GSRMs but imply that clouds or
-convection are resolved explicitly, which is not entirely true for GSRMs, as
-this would require an even higher horizontal resolution \citeA{satoh2019}.
-Representative of these efforts is the DYnamics of the Atmospheric general
-circulation Modeled On Non-hydrostatic Domains (DYAMOND) project
-\citeA{stevens2019,dyamond}, which is an intercomparison of nine global GSRMs
-over two 40-day time periods in summer (1 August -- 10 September 2016) and
-winter (20 January -- 1 March 2020). A new one-year GSRM intercomparison is
-currently proposed by \citeA{takasuka2024}, with the hope of also evaluating the
-seasonal cycle and large-scale circulation.  An alternative to using a
-computationally costly GSRM is to train an artificial neural network on GSRM
-output and use it for subgrid-scale clouds, as done with the GSRM ICON by
-\citeA{grundner2022} and \citeA{grundner2023}.
+Increasing climate model resolution is one way of improving model accuracy of representation of the climate system \citeA{mauritsen2022}.
+It has been practiced since the advent of climate modelling as more computational power, memory, and storage capacity become available.
+It is, however, often not as easy as changing the grid size because of the complex interplay between model dynamics and physics, which necessitates adjusting and tuning all components together.
+Increasing resolution is of course limited by the available computational power and a trade-off with increasing parameterization complexity, which is another way of improving model accuracy.
+Current computational availability and acceleration from general-purpose computing on graphics processing units (GPUs) is progressing to enable km-scale (also called k-scale) Earth system models (ESMs) and coupled atmosphere--ocean general circulation models (AOGCMs) in research conditions today and operationally in the forthcoming years.
+Therefore, it represents a natural advance in climate modelling.
+Global storm-resolving models (GSRMs) are emerging as a new front in the development of high-resolution global climate models, with horizontal grid resolutions of about 2--8 km \citeA{satoh2019,stevens2019}.
+This is enough to resolve mesoscale convective storms, but smaller-scale convective plumes and cloud structure remain unresolved.
+At an approximately 5-km scale, non-hydrostatic processes also become important \citeA{weisman1997}, and for this reason such models are generally non-hydrostatic.
+The terms global cloud-resolving models or global convection-permitting/-resolving models are also sometimes used interchangeably with GSRMs but imply that clouds or convection are resolved explicitly, which is not entirely true for GSRMs, as this would require an even higher horizontal resolution \citeA{satoh2019}.
+Representative of these efforts is the DYnamics of the Atmospheric general circulation Modeled On Non-hydrostatic Domains (DYAMOND) project \citeA{stevens2019,dyamond}, which is an intercomparison of nine global GSRMs over two 40-day time periods in summer (1 August -- 10 September 2016) and winter (20 January -- 1 March 2020).
+A new one-year GSRM intercomparison is currently proposed by \citeA{takasuka2024}, with the hope of also evaluating the seasonal cycle and large-scale circulation.
+An alternative to using a computationally costly GSRM is to train an artificial neural network on GSRM output and use it for subgrid-scale clouds, as done with the GSRM ICON by \citeA{grundner2022} and \citeA{grundner2023}.
 
-nextGEMS is a project \citeA{nextgems} focused on the research and development
-of GSRMs at multiple modelling centres and universities in Europe.  The project
-also develops GSRM versions of the Icosahedral Nonhydrostatic Weather and
-Climate Model (ICON; \citeA{hohenegger2023}), the Integrated Forecasting System
-[IFS; \citeA{ifs2023}], and their ocean components at eddy-resolving
-resolutions: ICON-O \citeA{korn2022} coupled with ICON and
-Finite-Element/volumE Sea ice-Ocean Model [FESOM; \citeA{wang2014}] and Nucleus
-for European Modelling of the Ocean [NEMO; \citeA{madec2023}] coupled with IFS.
-The project has so far produced ICON and IFS simulations with three development
-versions called Cycle 1--3 and a pre-final version, with a final production
-version planned by the end of the project. nextGEMS is not the only project
-developing GSRMs; other GSRMs (or GSRM versions of climate models) currently in
-development include: Convection-Permitting Simulations With the E3SM Global
-Atmosphere Model [SCREAM; \citeA{caldwell2021}], Atmospheric Model [NICAM;
-\citeA{satoh2008}], Unified Model (UM), eXperimental System for High-resolution
-modeling for Earth-to-Local Domain [X-SHiELD; \citeA{shield}], Action de
-Recherche Petite Echelle Grande Echelle-NonHydrostatic version [ARPEGE-NH;
-\citeA{bubnova1995,voldoire2017}], Finite-Volume Dynamical Core on the Cubed
-Sphere [FV3, \citeA{lin2004}], the National Aeronautics and Space Administration
-(NASA) Goddard Earth Observing System global atmospheric model version 5
-[GEOS5; \citeA{putman2011}], Model for Prediction Across Scales [MPAS;
-\citeA{skamarock2012}], and System for Atmospheric Modeling [SAM;
-\citeA{khairoutdinov2003}].
+nextGEMS is a project \citeA{nextgems} focused on the research and development of GSRMs at multiple modelling centres and universities in Europe.
+The project also develops GSRM versions of the Icosahedral Nonhydrostatic Weather and Climate Model (ICON; \citeA{hohenegger2023}), the Integrated Forecasting System [IFS; \citeA{ifs2023}], and their ocean components at eddy-resolving resolutions: ICON-O \citeA{korn2022} coupled with ICON and Finite-Element/volumE Sea ice-Ocean Model [FESOM; \citeA{wang2014}] and Nucleus for European Modelling of the Ocean [NEMO; \citeA{madec2023}] coupled with IFS.
+The project has so far produced ICON and IFS simulations with three development versions called Cycle 1--3 and a pre-final version, with a final production version planned by the end of the project.
+nextGEMS is not the only project developing GSRMs; other GSRMs (or GSRM versions of climate models) currently in development include: Convection-Permitting Simulations With the E3SM Global Atmosphere Model [SCREAM; \citeA{caldwell2021}], Atmospheric Model [NICAM; \citeA{satoh2008}], Unified Model (UM), eXperimental System for High-resolution modeling for Earth-to-Local Domain [X-SHiELD; \citeA{shield}], Action de Recherche Petite Echelle Grande Echelle-NonHydrostatic version [ARPEGE-NH; \citeA{bubnova1995,voldoire2017}], Finite-Volume Dynamical Core on the Cubed Sphere [FV3, \citeA{lin2004}], the National Aeronautics and Space Administration (NASA) Goddard Earth Observing System global atmospheric model version 5 [GEOS5; \citeA{putman2011}], Model for Prediction Across Scales [MPAS; \citeA{skamarock2012}], and System for Atmospheric Modeling [SAM; \citeA{khairoutdinov2003}].
 
-Multiple cloud properties have an effect on shortwave (SW) and longwave (LW)
-radiation. To first order, the total cloud fraction, cloud phase, and the
-liquid and ice water path are the most important cloud properties influencing
-SW and LW radiation. These properties are  in turn influenced by the
-atmospheric thermodynamics, convection and circulation, and both the indirect
-and direct effects of aerosols. Second order effects on SW and LW radiation are
-associated with the cloud droplet size distribution, ice crystal habit, cloud
-lifetime, and direct radiative interaction with aerosols.  In the
-6$^\mathrm{th}$ phase of the Coupled Model Intercomparison Project [CMIP6;
-\citeA{eyring2016}], the cloud feedback has increased relative to CMIP5
-\citeA{zelinka2020}, which is one of the main reasons for the higher climate
-sensitivity of CMIP6 models.
+Multiple cloud properties have an effect on shortwave (SW) and longwave (LW) radiation.
+To first order, the total cloud fraction, cloud phase, and the liquid and ice water path are the most important cloud properties influencing SW and LW radiation.
+These properties are in turn influenced by the atmospheric thermodynamics, convection and circulation, and both the indirect and direct effects of aerosols.
+Second order effects on SW and LW radiation are associated with the cloud droplet size distribution, ice crystal habit, cloud lifetime, and direct radiative interaction with aerosols.
+In the 6$^\mathrm{th}$ phase of the Coupled Model Intercomparison Project [CMIP6; \citeA{eyring2016}], the cloud feedback has increased relative to CMIP5 \citeA{zelinka2020}, which is one of the main reasons for the higher climate sensitivity of CMIP6 models.
 
-The Southern Ocean (SO) is known to be a problematic region for climate model
-biases \citeA{schuddeboom2021,hyder2018,cesana2022,zhao2022} due to a lack of
-surface and in situ observations and being a lower priority region for
-numerical weather prediction (NWP) and climate model development because of its
-distance from populated areas.  Nevertheless, radiation biases and changes over
-an area of its size have a substantial influence on the global climate
-\citeA{rintoul2011}, such as affecting the Earth radiation balance, ocean heat
-and carbon uptake \citeA{williams2023}, and the SO is an important part of the
-global ocean conveyor belt \citeA{wang2014}. In general, marine clouds have a
-disproportionate effect on top of atmosphere (TOA) SW radiation due to the
-relatively low albedo of the sea surface.  The relative longitudinal symmetry
-of the SO means that model cloud biases tend to be similar across longitudes.
+The Southern Ocean (SO) is known to be a problematic region for climate model biases \citeA{schuddeboom2021,hyder2018,cesana2022,zhao2022} due to a lack of surface and in situ observations and being a lower priority region for numerical weather prediction (NWP) and climate model development because of its distance from populated areas.
+Nevertheless, radiation biases and changes over an area of its size have a substantial influence on the global climate \citeA{rintoul2011}, such as affecting the Earth radiation balance, ocean heat and carbon uptake \citeA{williams2023}, and the SO is an important part of the global ocean conveyor belt \citeA{wang2014}.
+In general, marine clouds have a disproportionate effect on top of atmosphere (TOA) SW radiation due to the relatively low albedo of the sea surface.
+The relative longitudinal symmetry of the SO means that model cloud biases tend to be similar across longitudes.
 
-Here, we conventionally refer to the SO as ocean regions south of 40°S,
-low-latitude SO as 40--55°S and high-latitude SO as south of 55°S. The reason
-for this dividing latitude is to split the SO into about two equal zones, as
-well as the results by \citeA{schuddeboom2021} (Fig. 2b), showing a contrast in
-CMIP model radiation biases, \citeA{schuddeboom2019} (Fig. 2) and
-\citeA{kuma2020} (Fig. 3) showing contrasting radiation biases in the Hadley
-Centre Global Environmental Model, and \citeA{cesana2022} showing contrasting
-cloud biases due to the 0°C isotherm reaching the surface at 55°S. The findings
-of \citeA{niu2024}, however, support a different dividing line of 62°S based on
-cloud condensation nuclei concentration.
+Here, we conventionally refer to the SO as ocean regions south of 40°S, low-latitude SO as 40--55°S and high-latitude SO as south of 55°S.
+The reason for this dividing latitude is to split the SO into about two equal zones, as well as the results by \citeA{schuddeboom2021} (Fig.
+2b), showing a contrast in CMIP model radiation biases, \citeA{schuddeboom2019} (Fig.
+2) and \citeA{kuma2020} (Fig.
+3) showing contrasting radiation biases in the Hadley Centre Global Environmental Model, and \citeA{cesana2022} showing contrasting cloud biases due to the 0°C isotherm reaching the surface at 55°S.
+The findings of \citeA{niu2024}, however, support a different dividing line of 62°S based on cloud condensation nuclei concentration.
 
-SO radiation biases have been relatively large and systematic compared to the
-rest of the globe since at least CMIP3 \citeA{trenberth2010}, and the SO SW
-cloud radiative effect (CRE) bias is still positive in eight analysed CMIP6
-models analysed by \citeA{schuddeboom2021} over the high-latitude SO, whereas
-over the low-latitude SO it tends to be more neutral or negative in some
-models. Too much absorbed SW radiation over the SO was also identified in the
-GSRM SCREAM \citeA{caldwell2021}. Compensating biases are possible, such as the
-`too few too bright' cloud bias, characterised by too small cloud fraction and
-too large cloud albedo \citeA{wall2017,kuma2020}, previously described by
-\citeA{webb2001}, \citeA{weare2004}, \citeA{zhang2005}, \citeA{karlsson2008},
-\citeA{nam2012}, \citeA{klein2013}, and \citeA{bender2017} in other regions and
-models, which means that a model can maintain a reasonable SW radiation balance
-by reflecting too much SW radiation from clouds, but these cover too small
-area.  A study by \citeA{konsta2022} showed that this type of bias is still
-present in six analysed CMIP6 models in tropical marine clouds, using the
-GCM-Oriented Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observation
-(CALIPSO) Cloud Product [CALIPSO--GOCCP; \citeA{chepfer2010}] and Polarization
-\& Anisotropy of Reflectances for Atmospheric Sciences coupled with
-Observations from a Lidar [PARASOL; \citeA{lier2008}] as a reference. They
-suggest improper simulation of subgrid-scale cloud heterogeneity as a cause.
-Compensating cloud biases in the Australian Community Climate and Earth System
-Simulator (ACCESS) – Atmosphere-only model version 2 (AM2) over the SO were
-analysed by \citeA{fiddes2022} and \citeA{fiddes2024}.  \citeA{possner2022} showed
-that over the SO, the DYAMOND GSRM ICON underestimates low-level cloud fraction
-on the order of 30\% [relative to Moderate Resolution Imaging Spectroradiometer
-(MODIS) data] and overestimates downwelling TOA SW radiation by approximately
-10 Wm$^\mathrm{-2}$ [relative to the Clouds and the Earth’s Radiant Energy
-System (CERES) data] in the highest model resolution run (2.5 km).
-\citeA{zhao2022} reported a similar SW radiation bias in five analysed CMIP6
-models over high-latitude SO and the total cloud fraction underestimation on
-the order of 10\% over the entire 40--60°S SO. Recently, \citeA{ramadoss2024}
-analysed 48 hours of km-scale ICON limited area model NWP simulations over a SO
-region adjacent to Tasmania against the Clouds, Aerosols, Precipitation,
-Radiation, and atmospherIc Composition Over the southeRn oceaN (CAPRICORN)
-voyage cloud and precipitation observations \citeA{mcfarquhar2021}. They found
-the ICON cloud optical thickness was underestimated relative to Himawari‐8
-satellite observations, but also identified large differences in cloud top
-phase.
+SO radiation biases have been relatively large and systematic compared to the rest of the globe since at least CMIP3 \citeA{trenberth2010}, and the SO SW cloud radiative effect (CRE) bias is still positive in eight analysed CMIP6 models analysed by \citeA{schuddeboom2021} over the high-latitude SO, whereas over the low-latitude SO it tends to be more neutral or negative in some models.
+Too much absorbed SW radiation over the SO was also identified in the GSRM SCREAM \citeA{caldwell2021}.
+Compensating biases are possible, such as the `too few too bright' cloud bias, characterised by too small cloud fraction and too large cloud albedo \citeA{wall2017,kuma2020}, previously described by \citeA{webb2001}, \citeA{weare2004}, \citeA{zhang2005}, \citeA{karlsson2008}, \citeA{nam2012}, \citeA{klein2013}, and \citeA{bender2017} in other regions and models, which means that a model can maintain a reasonable SW radiation balance by reflecting too much SW radiation from clouds, but these cover too small area.
+A study by \citeA{konsta2022} showed that this type of bias is still present in six analysed CMIP6 models in tropical marine clouds, using the GCM-Oriented Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observation (CALIPSO) Cloud Product [CALIPSO--GOCCP; \citeA{chepfer2010}] and Polarization \& Anisotropy of Reflectances for Atmospheric Sciences coupled with Observations from a Lidar [PARASOL; \citeA{lier2008}] as a reference.
+They suggest improper simulation of subgrid-scale cloud heterogeneity as a cause.
+Compensating cloud biases in the Australian Community Climate and Earth System Simulator (ACCESS) – Atmosphere-only model version 2 (AM2) over the SO were analysed by \citeA{fiddes2022} and \citeA{fiddes2024}.
+\citeA{possner2022} showed that over the SO, the DYAMOND GSRM ICON underestimates low-level cloud fraction on the order of 30\% [relative to Moderate Resolution Imaging Spectroradiometer (MODIS) data] and overestimates downwelling TOA SW radiation by approximately 10 Wm$^\mathrm{-2}$ [relative to the Clouds and the Earth’s Radiant Energy System (CERES) data] in the highest model resolution run (2.5 km).
+\citeA{zhao2022} reported a similar SW radiation bias in five analysed CMIP6 models over high-latitude SO and the total cloud fraction underestimation on the order of 10\% over the entire 40--60°S SO.
+Recently, \citeA{ramadoss2024} analysed 48 hours of km-scale ICON limited area model NWP simulations over a SO region adjacent to Tasmania against the Clouds, Aerosols, Precipitation, Radiation, and atmospherIc Composition Over the southeRn oceaN (CAPRICORN) voyage cloud and precipitation observations \citeA{mcfarquhar2021}.
+They found the ICON cloud optical thickness was underestimated relative to Himawari‐8 satellite observations, but also identified large differences in cloud top phase.
 
-In general, sea surface temperature (SST) biases in the SO can originate either
-in the atmosphere \citeA{hyder2018}, caused by too much shortwave heating of
-the surface, too little longwave cooling of the surface, or in the ocean
-circulation.  Interactions of both are also possible, for example SST affecting
-clouds and clouds affecting the surface radiation. Using the European Centre
-for Medium-Range Weather Forecasts (ECMWF) Reanalysis 5 (ERA5) as a reference,
-\citeA{zhang2023} have shown that SST biases have improved in CMIP6 compared to
-CMIP5, with SST overall increasing in the later CMIP phase. However, over the
-SO this resulted in an even higher positive bias, especially in the Atlantic
-Ocean (AO) sector of the SO, increasing by up to 1°C.  \citeA{luo2023}
-identified that the SO SST bias in an ensemble of 18 CMIP6 models originates
-not from the surface heat and radiation fluxes (using reanalyses as a
-reference), but from a warm bias in the Northern Atlantic Deep Water.
+In general, sea surface temperature (SST) biases in the SO can originate either in the atmosphere \citeA{hyder2018}, caused by too much shortwave heating of the surface, too little longwave cooling of the surface, or in the ocean circulation.
+Interactions of both are also possible, for example SST affecting clouds and clouds affecting the surface radiation.
+Using the European Centre for Medium-Range Weather Forecasts (ECMWF) Reanalysis 5 (ERA5) as a reference, \citeA{zhang2023} have shown that SST biases have improved in CMIP6 compared to CMIP5, with SST overall increasing in the later CMIP phase.
+However, over the SO this resulted in an even higher positive bias, especially in the Atlantic Ocean (AO) sector of the SO, increasing by up to 1°C.
+\citeA{luo2023} identified that the SO SST bias in an ensemble of 18 CMIP6 models originates not from the surface heat and radiation fluxes (using reanalyses as a reference), but from a warm bias in the Northern Atlantic Deep Water.
 
-The main aim of this study is to evaluate the GSRM version of ICON. ICON
-developed and maintained jointly by Deutscher Wetterdienst,
-Max-Planck-Institute for Meteorology, Deutsches Klimarechenzentrum (DKRZ),
-Karlsruhe Institute of Technology, and the Center for Climate Systems Modeling.
-Previous studies have identified substantial large-scale biases in climate
-model clouds over the SO, affecting sea surface temperature and the Earth’s
-albedo. Our aim is to quantify how well the GSRM ICON is simulating clouds in
-this region, particularly in light of the fact that subgrid-scale clouds and
-convection are not parameterized in this model. This region is mostly dominated
-by boundary layer clouds generated by shallow convection, and these are
-problematic to observe by spaceborne lidars and radars, which are affected by
-attenuation by overlapping and thick clouds \citeA{mace2009,medeiros2010} and
-ground clutter \citeA{marchand2008}, respectively.  Specifically, the radar on
-CloudSat and lidar on CALIPSO (neither of which are nowoperational) are
-affected by the abovementioned issues, resulting in a strong underestimation of
-cloud occurrence below 2 km relative to ground-based lidar observations
-\citeA{mcerlich2021}.  We hypothesise that this, in turn, can lead to
-systematic biases in low clouds in climate models, which are frequently
-evaluated against CloudSat--CALIPSO products. Reanalyses can also suffer from
-cloud biases, as these are usually parametrised in their atmospheric component,
-and also in regions where input observations are sparse.  This makes them a
-problematic reference for clouds over the SO, and any biases relative to a
-reanalysis should be interpreted with caution. Instead, we chose to use a large
-set of ship-based observations conducted with ceilometers and lidars on board
-of the RV \emph{Polarstern} and other voyages and stations as a reference for
+The main aim of this study is to evaluate the GSRM version of ICON.
+ICON developed and maintained jointly by Deutscher Wetterdienst, Max-Planck-Institute for Meteorology, Deutsches Klimarechenzentrum (DKRZ), Karlsruhe Institute of Technology, and the Center for Climate Systems Modeling.
+Previous studies have identified substantial large-scale biases in climate model clouds over the SO, affecting sea surface temperature and the Earth’s albedo.
+Our aim is to quantify how well the GSRM ICON is simulating clouds in this region, particularly in light of the fact that subgrid-scale clouds and convection are not parameterized in this model.
+This region is mostly dominated by boundary layer clouds generated by shallow convection, and these are problematic to observe by spaceborne lidars and radars, which are affected by attenuation by overlapping and thick clouds \citeA{mace2009,medeiros2010} and ground clutter \citeA{marchand2008}, respectively.
+Specifically, the radar on CloudSat and lidar on CALIPSO (neither of which are nowoperational) are affected by the abovementioned issues, resulting in a strong underestimation of cloud occurrence below 2 km relative to ground-based lidar observations \citeA{mcerlich2021}.
+We hypothesise that this, in turn, can lead to systematic biases in low clouds in climate models, which are frequently evaluated against CloudSat--CALIPSO products.
+Reanalyses can also suffer from cloud biases, as these are usually parametrised in their atmospheric component, and also in regions where input observations are sparse.
+This makes them a problematic reference for clouds over the SO, and any biases relative to a reanalysis should be interpreted with caution.
+Instead, we chose to use a large set of ship-based observations conducted with ceilometers and lidars on board of the RV \emph{Polarstern} and other voyages and stations as a reference for
 the model evaluation.
 
-Altogether, we analysed about 2400 days of data from 31 voyages, and one
-sub-Antarctic station covering diverse longitudes and latitudes of the SO. To
-achieve a like-for-like comparison with the model, we used a ground-based lidar
-simulator called the Automatic Lidar and Ceilometer Framework [ALCF;
-\citeA{kuma2021}]. We contrasted the results with ERA5 \citeA{era5} and the
-Modern-Era Retrospective analysis for Research and Applications, Version 2
-[MERRA-2; \citeA{gelaro2017}].
+Altogether, we analysed about 2400 days of data from 31 voyages, and one sub-Antarctic station covering diverse longitudes and latitudes of the SO.
+To achieve a like-for-like comparison with the model, we used a ground-based lidar simulator called the Automatic Lidar and Ceilometer Framework [ALCF; \citeA{kuma2021}].
+We contrasted the results with ERA5 \citeA{era5} and the Modern-Era Retrospective analysis for Research and Applications, Version 2 [MERRA-2; \citeA{gelaro2017}].
 
@@
 \caption{
-\textbf{(a)} A map showing the tracks of 31 voyages of RV \emph{Polarstern},
-RSV \emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B. Palmer},
-and HMNZS \emph{Wellington} and one sub-Antarctic station (Macquarie Island)
-analysed here. The tracks cover Antarctic sectors south of South America, the
-Atlantic Ocean, Africa, Australia, and New Zealand in the years 2010--2021
-(inclusive).  The dotted and dashed lines at 40°S and 55°S delineate the
-Southern Ocean area of our analysis and its partitioning into two subsets,
-respectively.  A photo of \textbf{(b)} RV \emph{Polarstern} (© Folke Mehrtens,
-Alfred-Wegener-Institut), \textbf{(c)} Lufft CHM 15k installed on RV
-\emph{Tangaroa} (© Peter Kuma, University of Canterbury), \textbf{(d)} Vaisala
-CL51 (© Jeff Aquilina, Bureau of Meteorology), \textbf{(e)} Vaisala CT25K at
-Macquarie Island (© Simon P.\ Alexander, Australian Antarctic Division).
+\textbf{(a)} A map showing the tracks of 31 voyages of RV \emph{Polarstern}, RSV \emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B.
+Palmer}, and HMNZS \emph{Wellington} and one sub-Antarctic station (Macquarie Island) analysed here.
+The tracks cover Antarctic sectors south of South America, the Atlantic Ocean, Africa, Australia, and New Zealand in the years 2010--2021 (inclusive).
+The dotted and dashed lines at 40°S and 55°S delineate the Southern Ocean area of our analysis and its partitioning into two subsets, respectively.
+A photo of \textbf{(b)} RV \emph{Polarstern} (© Folke Mehrtens, Alfred-Wegener-Institut), \textbf{(c)} Lufft CHM 15k installed on RV \emph{Tangaroa} (© Peter Kuma, University of Canterbury), \textbf{(d)} Vaisala CL51 (© Jeff Aquilina, Bureau of Meteorology), \textbf{(e)} Vaisala CT25K at Macquarie Island (© Simon P.\ Alexander, Australian Antarctic Division).
 }
@@
 
-Together, we analysed data from 31 voyages of RV \emph{Polarstern}, the
-resupply vessel (RSV) \emph{Aurora Australis}, RV \emph{Tangaroa}, RV
-\emph{Nathaniel B.  Palmer}, Her (now His) Majesty's New Zealand Ship (HMNZS)
-\emph{Wellington} and one sub-Antarctic station (Macquarie Island) in the SO
-south of 40°S between 2010 and 2021. Fig. \ref{fig:map} shows a map of the
-voyages, Table \ref{tab:voyages} list the voyages, campaigns, and stations, and
-Table \ref{tab:voyage-references} lists references where available. Altogether,
-the voyages and station dataset comprised 2421 days of data south of 40°S, but
-the availability of ceilometer data was slightly shorter due to gaps in
-measurements.
+Together, we analysed data from 31 voyages of RV \emph{Polarstern}, the resupply vessel (RSV) \emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B.
+Palmer}, Her (now His) Majesty's New Zealand Ship (HMNZS) \emph{Wellington} and one sub-Antarctic station (Macquarie Island) in the SO south of 40°S between 2010 and 2021.
+Fig.
+\ref{fig:map} shows a map of the voyages, Table \ref{tab:voyages} list the voyages, campaigns, and stations, and Table \ref{tab:voyage-references} lists references where available.
+Altogether, the voyages and station dataset comprised 2421 days of data south of 40°S, but the availability of ceilometer data was slightly shorter due to gaps in measurements.
 
-Missing days in the ceilometer data were HMNZSW16 (7 days): 24--27 November, 10
-December, 16--17 December 2016; Measurements of Aerosols, Radiation, and CloUds
-over the Southern Ocean (MARCUS;  3 days): 8, 10 November, 10 December 2017;
-Macquarie Island Cloud Radiation Experiment (MICRE; 9 days): 7--8, 29 June, 5,
-16 July, 15 August, 17 October 2016, 11 February, 21 March 2017; TAN1502 (1
-day): 24 January.
+Missing days in the ceilometer data were HMNZSW16 (7 days): 24--27 November, 10 December, 16--17 December 2016; Measurements of Aerosols, Radiation, and CloUds over the Southern Ocean (MARCUS; 3 days): 8, 10 November, 10 December 2017; Macquarie Island Cloud Radiation Experiment (MICRE; 9 days): 7--8, 29 June, 5, 16 July, 15 August, 17 October 2016, 11 February, 21 March 2017; TAN1502 (1 day): 24 January.
 
-The data sources contained ceilometer observations captured by the Vaisala CL51
-and CT25K, and the Lufft CHM 15k, described in detail below (Sections
-\ref{sec:cl51} and \ref{sec:chm15k}). A ceilometer is a low-power near-infrared
-vertically pointing lidar principally designed to  measure cloud base, but they
-also measure the full vertical structure of clouds as long as the laser signal
-is not attenuated by thick clouds, which can be used to infer additional
-information such as a cloud mask and cloud occurrence by height.  We note that
-during the MICRE campaign, the ceilometers Vaisala CT25K and CL51 were
-installed at the Macquarie Island station concurrently, but in our analysis we
-only used the CT25K data obtained from the Atmospheric Radiation Measurement
-(ARM) data archive.
+The data sources contained ceilometer observations captured by the Vaisala CL51 and CT25K, and the Lufft CHM 15k, described in detail below (Sections \ref{sec:cl51} and \ref{sec:chm15k}).
+A ceilometer is a low-power near-infrared vertically pointing lidar principally designed to measure cloud base, but they also measure the full vertical structure of clouds as long as the laser signal is not attenuated by thick clouds, which can be used to infer additional information such as a cloud mask and cloud occurrence by height.
+We note that during the MICRE campaign, the ceilometers Vaisala CT25K and CL51 were installed at the Macquarie Island station concurrently, but in our analysis we only used the CT25K data obtained from the Atmospheric Radiation Measurement (ARM) data archive.
 
-Apart from lidar observations, radiosondes were launched on weather balloons at
-regular synoptic times on the RV \emph{Polarstern}, MARCUS, NBP17024, TAN1702,
-and TAN1802 voyages and campaigns, measuring pressure, temperature, relative
-humidity, and the global navigation satellite system coordinates. Derived
-thermodynamic (virtual potential temperature, lifting condensation level, etc.)
-and dynamic physical quantities (wind speed and direction) for the measured
-vertical profiles were calculated with rstool \citeA{rstool}. Surface
-meteorological quantities were measured continuously by an onboard automatic
-weather station or individual instruments.
+Apart from lidar observations, radiosondes were launched on weather balloons at regular synoptic times on the RV \emph{Polarstern}, MARCUS, NBP17024, TAN1702, and TAN1802 voyages and campaigns, measuring pressure, temperature, relative humidity, and the global navigation satellite system coordinates.
+Derived thermodynamic (virtual potential temperature, lifting condensation level, etc.) and dynamic physical quantities (wind speed and direction) for the measured vertical profiles were calculated with rstool \citeA{rstool}.
+Surface meteorological quantities were measured continuously by an onboard automatic weather station or individual instruments.
 
@@
 \caption{
-An overview of the analysed voyages, campaigns, and stations. Start, end, and
-the number of days (UTC; inclusive) refer to the time period when the vessel
-was south of 40°S.  Abbreviations: ceilometer (ceil.), Australia (AU), New
-Zealand (NZ), South America (SA), Atlantic Ocean (AO), and Africa (AF). The
-number of days is rounded to the nearest integer. CL51/31 indicates CL51
-configured to emulate CL31.
+An overview of the analysed voyages, campaigns, and stations.
+Start, end, and the number of days (UTC; inclusive) refer to the time period when the vessel was south of 40°S.
+Abbreviations: ceilometer (ceil.), Australia (AU), New Zealand (NZ), South America (SA), Atlantic Ocean (AO), and Africa (AF).
+The number of days is rounded to the nearest integer.
+CL51/31 indicates CL51 configured to emulate CL31.
 }
@@
 
-The Vaisala CL51 and CT25K (photos in Fig. \ref{fig:map}d, e) are ceilometers
-operating at a near-infrared wavelength of 910 nm and 905 nm, respectively.
-The CL51 can also be configured to emulate the Vaisala CL31. The maximum range
-is 15.4 km (CL51), 7.7 km (CL31 emulation mode with 5 m vertical resolution),
-and 7.5 km (CT25K). The vertical resolution is 10 m (5 m configurable) in CL51
-and 30 m in CT25K observations. The sampling (temporal) resolution is
-configurable, and in our datasets is approximately 6 s for CL51 on AA15‐16, 16
-s for CT25K on MARCUS and MICRE, 36 s for CL51 on RV \emph{Polarstern}, and
-about 2.37 s for CL51 with CL31 emulation on TAN1502. The wavelengths of 905
-and 910 nm are affected by water vapour absorption of about 20\% in the
-mid-latitudes \citeA{wiegner2015,wiegner2019}, with 910 nm affected more
-strongly, but we do not expect this to be a significant issue as explained in
-\citeA{kuma2021}.  The instrument data files containing raw uncalibrated
-backscatter were first converted to Network Common Data Form (NetCDF) with
-cl2nc (\url{https://github.com/peterkuma/cl2nc}) and then processed with the
-ALCF (Section \ref{sec:alcf}) to produce absolutely calibrated attenuated
-volume backscattering coefficient (AVBC), cloud mask, cloud occurrence by
-height, and the total cloud fraction. Because the CT25K uses a very similar
-wavelength to CL51, equivalent calculations as for CL51 were done assuming a
-wavelength of 910 nm. The Vaisala CL51 and CT25K instruments were used on most
-of the voyages and stations analysed here. Fig.  \ref{fig:example}a shows an
-example of AVBC derived from the CL51 instrument data.
+The Vaisala CL51 and CT25K (photos in Fig.
+\ref{fig:map}d, e) are ceilometers operating at a near-infrared wavelength of 910 nm and 905 nm, respectively.
+The CL51 can also be configured to emulate the Vaisala CL31.
+The maximum range is 15.4 km (CL51), 7.7 km (CL31 emulation mode with 5 m vertical resolution), and 7.5 km (CT25K).
+The vertical resolution is 10 m (5 m configurable) in CL51 and 30 m in CT25K observations.
+The sampling (temporal) resolution is configurable, and in our datasets is approximately 6 s for CL51 on AA15‐16, 16 s for CT25K on MARCUS and MICRE, 36 s for CL51 on RV \emph{Polarstern}, and about 2.37 s for CL51 with CL31 emulation on TAN1502.
+The wavelengths of 905 and 910 nm are affected by water vapour absorption of about 20\% in the mid-latitudes \citeA{wiegner2015,wiegner2019}, with 910 nm affected more strongly, but we do not expect this to be a significant issue as explained in \citeA{kuma2021}.
+The instrument data files containing raw uncalibrated backscatter were first converted to Network Common Data Form (NetCDF) with cl2nc (\url{https://github.com/peterkuma/cl2nc}) and then processed with the ALCF (Section \ref{sec:alcf}) to produce absolutely calibrated attenuated volume backscattering coefficient (AVBC), cloud mask, cloud occurrence by height, and the total cloud fraction.
+Because the CT25K uses a very similar wavelength to CL51, equivalent calculations as for CL51 were done assuming a wavelength of 910 nm.
+The Vaisala CL51 and CT25K instruments were used on most of the voyages and stations analysed here.
+Fig.
+\ref{fig:example}a shows an example of AVBC derived from the CL51 instrument data.
 
@@
 \caption{
-An example of attenuated volume backscattering coefficient (AVBC) \textbf{(a)}
-measured by CL51 during 24 hours on the PS81/3 voyage and \textbf{(b)} an
-equivalent AVBC simulated with the ALCF from ERA5 data during the same time
-period. The red line identifies the cloud mask determined by the ALCF.
+An example of attenuated volume backscattering coefficient (AVBC) \textbf{(a)} measured by CL51 during 24 hours on the PS81/3 voyage and \textbf{(b)} an equivalent AVBC simulated with the ALCF from ERA5 data during the same time period.
+The red line identifies the cloud mask determined by the ALCF.
 }
@@
 
-The Lufft CHM 15k (photo in Fig. \ref{fig:map}c) is a ceilometer operating at a
-near-infrared wavelength of 1064 nm. The maximum range is 15.4 km, the vertical
-resolution is 5 m in the near range (up to 150 m) and 15 m above, the sampling
-(temporal) resolution is 2 s, and the number of vertical levels is 1024.
-NetCDF files containing uncalibrated backscatter produced by the instrument
-were processed with the ALCF (Section \ref{sec:alcf}) to again produce AVBC,
-cloud mask, cloud occurrence by height, and the total cloud fraction. The CHM
-15k was used on four voyages (HMNZSW16, TAN1702, TAN1802, and NBP1704).
+The Lufft CHM 15k (photo in Fig.
+\ref{fig:map}c) is a ceilometer operating at a near-infrared wavelength of 1064 nm.
+The maximum range is 15.4 km, the vertical resolution is 5 m in the near range (up to 150 m) and 15 m above, the sampling (temporal) resolution is 2 s, and the number of vertical levels is 1024.
+NetCDF files containing uncalibrated backscatter produced by the instrument were processed with the ALCF (Section \ref{sec:alcf}) to again produce AVBC, cloud mask, cloud occurrence by height, and the total cloud fraction.
+The CHM 15k was used on four voyages (HMNZSW16, TAN1702, TAN1802, and NBP1704).
 
@@
 
-The Automatic Lidar and Ceilometer Framework (ALCF) is a ground-based lidar
-simulator and a tool for processing observed lidar data, supporting various
-instruments and models \citeA{kuma2021}. It performs radiative transfer
-calculations to derive equivalent lidar AVBC in an atmospheric model, which can
-then be compared with observed AVBC. For this purpose, it takes the cloud
-fraction, liquid and ice mass mixing ratio, temperature, and pressure model
-fields as an input and is run offline (on the model output rather than inside
-the model code). The lidar simulator in the ALCF is based on the instrument
-simulator Cloud Feedback Model Intercomparison Project (CFMIP) Observation
-Simulator Package (COSP) \citeA{bodas-salcedo2011}.  After AVBC is calculated,
-a cloud mask, cloud occurrence by height, and the total cloud fraction are
-determined. The ALCF has been used by several research teams for model and
-reanalysis evaluation
-\citeA{kuma2020,kremser2021,guyot2022,pei2023,whitehead2023,mcdonald2024}.
+The Automatic Lidar and Ceilometer Framework (ALCF) is a ground-based lidar simulator and a tool for processing observed lidar data, supporting various instruments and models \citeA{kuma2021}.
+It performs radiative transfer calculations to derive equivalent lidar AVBC in an atmospheric model, which can then be compared with observed AVBC.
+For this purpose, it takes the cloud fraction, liquid and ice mass mixing ratio, temperature, and pressure model fields as an input and is run offline (on the model output rather than inside the model code).
+The lidar simulator in the ALCF is based on the instrument simulator Cloud Feedback Model Intercomparison Project (CFMIP) Observation Simulator Package (COSP) \citeA{bodas-salcedo2011}.
+After AVBC is calculated, a cloud mask, cloud occurrence by height, and the total cloud fraction are determined.
+The ALCF has been used by several research teams for model and reanalysis evaluation \citeA{kuma2020,kremser2021,guyot2022,pei2023,whitehead2023,mcdonald2024}.
 
-Absolute calibration of the observed backscatter was performed by comparing the
-measured clear-sky molecular backscatter statistically with simulated clear-sky
-molecular backscatter. AVBC was resampled to 5 min temporal resolution and 50 m
-vertical resolution to increase signal-to-noise ratio while having enough
-resolution to detect small-scale cloud variability. The noise standard
-deviation was calculated from AVBC at the highest range, where no clouds are
-expected.  A cloud mask was calculated from AVBC using a fixed threshold of
-$\mathrm{2\times 10^{-6} m^{-1}sr^{-1}}$ after subtracting 5 standard
-deviations of range-scaled noise. Fig. \ref{fig:example}b shows an example of
-simulated Vaisala CL51 backscatter from ERA5 data, corresponding to a day of
-measurements by the instrument on the PS81/3 voyage.
+Absolute calibration of the observed backscatter was performed by comparing the measured clear-sky molecular backscatter statistically with simulated clear-sky molecular backscatter.
+AVBC was resampled to 5 min temporal resolution and 50 m vertical resolution to increase signal-to-noise ratio while having enough resolution to detect small-scale cloud variability.
+The noise standard deviation was calculated from AVBC at the highest range, where no clouds are expected.
+A cloud mask was calculated from AVBC using a fixed threshold of $\mathrm{2\times 10^{-6} m^{-1}sr^{-1}}$ after subtracting 5 standard deviations of range-scaled noise.
+Fig.
+\ref{fig:example}b shows an example of simulated Vaisala CL51 backscatter from ERA5 data, corresponding to a day of measurements by the instrument on the PS81/3 voyage.
 
@@
 
-A coupled (atmosphere--ocean) GSRM version of the ICON model is in development
-at the nextGEMS project \citeA{hohenegger2023}. ICON is an exceptionally
-versatile model, allowing for simulations ranging from coarse-resolution ESM
-simulations, GSRM simulations, limited area model simulations, to large eddy
-simulations (LES), for both weather prediction and climate projections. ICON
-uses the atmospheric component ICON-A \citeA{giorgetta2018}, whose physics is
-derived from ECHAM6 \citeA{stevens2013}, and the ocean component ICON-O
-\citeA{korn2022}. Earlier runs of the GSRM ICON from DYAMOND were evaluated by
-\citeA{mauritsen2022}.
+A coupled (atmosphere--ocean) GSRM version of the ICON model is in development at the nextGEMS project \citeA{hohenegger2023}.
+ICON is an exceptionally versatile model, allowing for simulations ranging from coarse-resolution ESM simulations, GSRM simulations, limited area model simulations, to large eddy simulations (LES), for both weather prediction and climate projections.
+ICON uses the atmospheric component ICON-A \citeA{giorgetta2018}, whose physics is derived from ECHAM6 \citeA{stevens2013}, and the ocean component ICON-O \citeA{korn2022}.
+Earlier runs of the GSRM ICON from DYAMOND were evaluated by \citeA{mauritsen2022}.
 
-Here, we use a free-running (i.e., the weather situation in the model does not
-correspond to reality) coupled GSRM simulation made for the purpose of climate
-projection.  nextGEMS has so far produced four cycles of model runs. We used a
-Cycle 3 run \emph{ngc3028} produced in 2023 \citeA{nextgems2023a,nextgems2023b}
-for a model time period of 20 January 2020 to 22 July 2025, of which we
-analysed the period 2021--2024 (inclusive). While a Cycle 4 run was available,
-we could not use it due to a lack of availability of the necessary variables.
-The horizontal resolution of ngc3028 is about 5 km.  The model output is
-available on 90 vertical levels and 3-hourly instantaneous temporal resolution.
+Here, we use a free-running (i.e., the weather situation in the model does not correspond to reality) coupled GSRM simulation made for the purpose of climate projection.
+nextGEMS has so far produced four cycles of model runs.
+We used a Cycle 3 run \emph{ngc3028} produced in 2023 \citeA{nextgems2023a,nextgems2023b} for a model time period of 20 January 2020 to 22 July 2025, of which we analysed the period 2021--2024 (inclusive).
+While a Cycle 4 run was available, we could not use it due to a lack of availability of the necessary variables.
+The horizontal resolution of ngc3028 is about 5 km.
+The model output is available on 90 vertical levels and 3-hourly instantaneous temporal resolution.
 
-Unlike current general circulation models (GCMs), the storm-resolving version
-of ICON does not use convective and cloud parameterization but relies on
-explicit simulation of convection and clouds on the model grid. Subgrid-scale
-clouds are not resolved, and the grid cell cloud fraction is always either 0 or
-100\%. While this makes the code development simpler without having to rely on
-uncertain parameterizations, it can miss smaller-scale clouds below the grid
-resolution.  Turbulence and cloud microphysics are still parameterized in this
-model. To account for the radiative effects of subgrid-scale clouds, a cloud
-inhomogeneity factor is introduced in the model which scales down the cloud
-liquid water for radiative calculations. It ranges from 0.4 at lower
-tropospheric stability (LTS) of 0 K to 0.8 at 30 K. In addition, vertical
-mixing is enhanced in unstable and humid lower-tropospheric conditions, which
-reduces the amount of shallow clouds.
+Unlike current general circulation models (GCMs), the storm-resolving version of ICON does not use convective and cloud parameterization but relies on explicit simulation of convection and clouds on the model grid.
+Subgrid-scale clouds are not resolved, and the grid cell cloud fraction is always either 0 or 100\%.
+While this makes the code development simpler without having to rely on uncertain parameterizations, it can miss smaller-scale clouds below the grid resolution.
+Turbulence and cloud microphysics are still parameterized in this model.
+To account for the radiative effects of subgrid-scale clouds, a cloud inhomogeneity factor is introduced in the model which scales down the cloud liquid water for radiative calculations.
+It ranges from 0.4 at lower tropospheric stability (LTS) of 0 K to 0.8 at 30 K.
+In addition, vertical mixing is enhanced in unstable and humid lower-tropospheric conditions, which reduces the amount of shallow clouds.
 
-Because the model is free-running, weather and climate oscillations (such as
-the El Niño--Southern Oscillation) are not expected to be equivalent to reality
-at the same time and place. To compare with the observations collected in
-different years (2010--2021, inclusive), we compared the model output with
-observations at the same time of year and geographical location, as determined
-for each data point such as a lidar profile or a radiosonde launch.
+Because the model is free-running, weather and climate oscillations (such as the El Niño--Southern Oscillation) are not expected to be equivalent to reality at the same time and place.
+To compare with the observations collected in different years (2010--2021, inclusive), we compared the model output with observations at the same time of year and geographical location, as determined for each data point such as a lidar profile or a radiosonde launch.
 
@@
 
-The Modern-Era Retrospective analysis for Research and Applications, Version 2
-(MERRA-2) is a reanalysis produced by the Global Modeling and Assimilation
-Office at the NASA Goddard Space Flight Center \citeA{gelaro2017}.  It uses
-version 5.12.4 of the Goddard Earth Observing System (GEOS) atmospheric model
-\citeA{rienecker2008,molod2015}. Non-convective clouds (condensation,
-autoconversion, and evaporation) are parametrised using a prognostic scheme
-\citeA{bacmeister2006}, and sub-grid cloud fraction is determined using total
-water distribution and a critical relative humidity threshold. The reanalysis
-output analysed here is available at a spatial resolution of 0.5° of latitude
-and 0.625° of longitude, which is about 56 km in the North--South direction and
-35 km in the East--West direction at 60°S. The number of vertical model levels
-is 72. Here, we use the following products: 1-hourly instantaneous 2D
-single-level diagnostics (M2I1NXASM) for 2-m temperature and humidity; 3-hourly
-instantaneous 3D assimilated meteorological fields (M2I3NVASM) for cloud
-quantities, pressure, and temperature; 1-hourly average 2D surface flux
-diagnostics (M2T1NXFLX) for precipitation; and 1-hourly average 2D radiation
-diagnostics (M2T1NXRAD) for radiation quantities \citeA{merra2}.
+The Modern-Era Retrospective analysis for Research and Applications, Version 2 (MERRA-2) is a reanalysis produced by the Global Modeling and Assimilation Office at the NASA Goddard Space Flight Center \citeA{gelaro2017}.
+It uses version 5.12.4 of the Goddard Earth Observing System (GEOS) atmospheric model \citeA{rienecker2008,molod2015}.
+Non-convective clouds (condensation, autoconversion, and evaporation) are parametrised using a prognostic scheme \citeA{bacmeister2006}, and sub-grid cloud fraction is determined using total water distribution and a critical relative humidity threshold.
+The reanalysis output analysed here is available at a spatial resolution of 0.5° of latitude and 0.625° of longitude, which is about 56 km in the North--South direction and 35 km in the East--West direction at 60°S.
+The number of vertical model levels is 72.
+Here, we use the following products: 1-hourly instantaneous 2D single-level diagnostics (M2I1NXASM) for 2-m temperature and humidity; 3-hourly instantaneous 3D assimilated meteorological fields (M2I3NVASM) for cloud quantities, pressure, and temperature; 1-hourly average 2D surface flux diagnostics (M2T1NXFLX) for precipitation; and 1-hourly average 2D radiation diagnostics (M2T1NXRAD) for radiation quantities \citeA{merra2}.
 
@@
 
-ERA5 \citeA{era5} is a reanalysis produced by the ECMWF.  It is based on a
-numerical weather prediction model IFS version CY41R2.  It uses the
-\citeA{tiedtke1993} prognostic cloud scheme and \citeA{forbes2014} for
-mixed-phase clouds. The horizontal resolution is 0.25° in latitude and
-longitude, which is about 28 km in the North--South direction and 14 km in the
-East--West direction at 60°S.  Internally, the model uses 137 vertical levels.
-Here, we use output at 1-hourly instantaneous time intervals, except for
-radiation quantities, which are accumulations (from these we calculate daily
-means).  Vertically resolved quantities are made available on 37 pressure
-levels.
+ERA5 \citeA{era5} is a reanalysis produced by the ECMWF.
+It is based on a numerical weather prediction model IFS version CY41R2.
+It uses the \citeA{tiedtke1993} prognostic cloud scheme and \citeA{forbes2014} for mixed-phase clouds.
+The horizontal resolution is 0.25° in latitude and longitude, which is about 28 km in the North--South direction and 14 km in the East--West direction at 60°S.
+Internally, the model uses 137 vertical levels.
+Here, we use output at 1-hourly instantaneous time intervals, except for radiation quantities, which are accumulations (from these we calculate daily means).
+Vertically resolved quantities are made available on 37 pressure levels.
 
@@
 
-TOA radiation quantities are taken from the CERES instruments onboard the Terra
-and Aqua satellites \citeA{wielicki1996,loeb2018}. In our analysis we used the
-adjusted all sky SW and LW upwelling fluxes at TOA from the synoptic TOA and
-surface fluxes and clouds 1 degree daily edition 4A product
-(CER\_SYN1deg-Day\_Terra-Aqua-MODIS\_Edition4A)
-\citeA{doelling2013,doelling2016}.
+TOA radiation quantities are taken from the CERES instruments onboard the Terra and Aqua satellites \citeA{wielicki1996,loeb2018}.
+In our analysis we used the adjusted all sky SW and LW upwelling fluxes at TOA from the synoptic TOA and surface fluxes and clouds 1 degree daily edition 4A product (CER\_SYN1deg-Day\_Terra-Aqua-MODIS\_Edition4A) \citeA{doelling2013,doelling2016}.
 
-Radiation calculations presented in the results (Section \ref{sec:results})
-were completed such that they always represent daily means in order to be
-consistent with the CERES SYN1deg data. Therefore, every instantaneous profile
-in the simulated lidar data was assigned a daily mean radiation value
-corresponding to the day (in the Coordinated Universal Time; UTC). In turn, the
-average radiation during the entire voyage or station observation period were
-calculated as the average of the profile values. In the observed lidar data,
-the daily mean radiation value was taken from the spatially and temporally
-co-located CERES SYN1deg data for the day (in UTC). The voyage or station
-average was calculated in the same way.
+Radiation calculations presented in the results (Section \ref{sec:results}) were completed such that they always represent daily means in order to be consistent with the CERES SYN1deg data.
+Therefore, every instantaneous profile in the simulated lidar data was assigned a daily mean radiation value corresponding to the day (in the Coordinated Universal Time; UTC).
+In turn, the average radiation during the entire voyage or station observation period were calculated as the average of the profile values.
+In the observed lidar data, the daily mean radiation value was taken from the spatially and temporally co-located CERES SYN1deg data for the day (in UTC).
+The voyage or station average was calculated in the same way.
 
@@
 \caption{
-Artificial neural network (ANN) for prediction of precipitation in lidar
-backscatter. \textbf{(a)} Diagram showing the TensorFlow structure of the ANN,
-\textbf{(b)} randomly selected example samples of near-surface backscatter in
-four categories (clear, fog, rain, and snow), as determined by coincident
-human-performed weather observations, \textbf{(c)} receiver operating
-characteristic diagram of the ANN, \textbf{(d)} examples of 10-day time series
-of human-observed (`HUM') and predicted precipitation based on an ANN trained
-on all voyages (`ANN') and all voyages except for the shown voyage (`ANN2')
-during three randomly selected voyages with the available data. Here, by
-`randomly selected' we mean selected from the top of a permutation generated by
-a pseudo-random number generator to prevent authors' bias in the selection.
+Artificial neural network (ANN) for prediction of precipitation in lidar backscatter.
+\textbf{(a)} Diagram showing the TensorFlow structure of the ANN, \textbf{(b)} randomly selected example samples of near-surface backscatter in four categories (clear, fog, rain, and snow), as determined by coincident human-performed weather observations, \textbf{(c)} receiver operating characteristic diagram of the ANN, \textbf{(d)} examples of 10-day time series of human-observed (`HUM') and predicted precipitation based on an ANN trained on all voyages (`ANN') and all voyages except for the shown voyage (`ANN2') during three randomly selected voyages with the available data.
+Here, by `randomly selected' we mean selected from the top of a permutation generated by a pseudo-random number generator to prevent authors' bias in the selection.
 }
@@
 
-Precipitation can cause strong enough lidar backscattering to be recognised as
-clouds by the threshold-based cloud detection method used in the ALCF. This is
-undesirable if equivalent precipitation backscatter is not included in the
-simulated lidar profiles. It was not possible to include precipitation
-simulation in the ALCF due to the absence of required fields in the ICON model
-output and the reanalysis data (the liquid and ice precipitation mass mixing
-ratios). The required radiation calculations for precipitation are also
-currently not implemented in the ALCF, even though this is a planned future
-addition.  In order to achieve a fair comparison of observations with model
-output, we exclude observed and simulated lidar profiles with precipitation
-either manually or using an automated method. It is relatively difficult to
-distinguish precipitation backscatter from cloud backscatter in lidar
-observations, especially when only one wavelength channel and no polarised
-channel are available. In models, the same can be accomplished relatively
-easily by excluding profiles exceeding a certain surface precipitation flux. In
-the observations, using precipitation flux measurements from rain gauges can be
-very unreliable on ships due to ship movement, turbulence caused by nearby ship
-structures, and sea spray. Our analysis of rain gauge data from the RV
-\emph{Tangaroa} showed large discrepancies between the rain gauge time series
-and human-performed synoptic observations, as well as large inconsistencies in
-the rain gauge time series. Human-performed observations of precipitation
-presence or absence are expected to be reliable but only cover a limited set of
-times. Therefore, it was desirable to implement a method of detecting
-precipitation from observed backscatter profiles alone.
+Precipitation can cause strong enough lidar backscattering to be recognised as clouds by the threshold-based cloud detection method used in the ALCF.
+This is undesirable if equivalent precipitation backscatter is not included in the simulated lidar profiles.
+It was not possible to include precipitation simulation in the ALCF due to the absence of required fields in the ICON model output and the reanalysis data (the liquid and ice precipitation mass mixing ratios).
+The required radiation calculations for precipitation are also currently not implemented in the ALCF, even though this is a planned future addition.
+In order to achieve a fair comparison of observations with model output, we exclude observed and simulated lidar profiles with precipitation either manually or using an automated method.
+It is relatively difficult to distinguish precipitation backscatter from cloud backscatter in lidar observations, especially when only one wavelength channel and no polarised channel are available.
+In models, the same can be accomplished relatively easily by excluding profiles exceeding a certain surface precipitation flux.
+In the observations, using precipitation flux measurements from rain gauges can be very unreliable on ships due to ship movement, turbulence caused by nearby ship structures, and sea spray.
+Our analysis of rain gauge data from the RV \emph{Tangaroa} showed large discrepancies between the rain gauge time series and human-performed synoptic observations, as well as large inconsistencies in the rain gauge time series.
+Human-performed observations of precipitation presence or absence are expected to be reliable but only cover a limited set of times.
+Therefore, it was desirable to implement a method of detecting precipitation from observed backscatter profiles alone.
 
-On the RV \emph{Polarstern} voyages, regular human-performed synoptic
-observations were available and included precipitation presence or absence and
-type. We used this dataset to train a convolutional artificial neural network
-(ANN) to recognise profiles with precipitation from lidar backscatter (Fig.
-\ref{fig:ann}a), implemented in the TensorFlow ANN framework
-\citeA{tensorflow}. Samples of short time intervals (10 min) of near-surface
-lidar backscatter (0–250 m) were classified as clear, rain, snow, and fog,
-using the synoptic observations as a training dataset (Fig.  \ref{fig:ann}b).
-From these, a binary, mutually exclusive classification of profiles as
-precipitating (rain or snow) or dry (clear or fog) was derived.  For detecting
-model and reanalysis precipitation, we used a fixed threshold for surface
-precipitation flux of 0.1 mm h$^{-1}$ (the ANN was not used).
+On the RV \emph{Polarstern} voyages, regular human-performed synoptic observations were available and included precipitation presence or absence and type.
+We used this dataset to train a convolutional artificial neural network (ANN) to recognise profiles with precipitation from lidar backscatter (Fig.
+\ref{fig:ann}a), implemented in the TensorFlow ANN framework \citeA{tensorflow}.
+Samples of short time intervals (10 min) of near-surface lidar backscatter (0–250 m) were classified as clear, rain, snow, and fog, using the synoptic observations as a training dataset (Fig.
+\ref{fig:ann}b).
+From these, a binary, mutually exclusive classification of profiles as precipitating (rain or snow) or dry (clear or fog) was derived.
+For detecting model and reanalysis precipitation, we used a fixed threshold for surface precipitation flux of 0.1 mm h$^{-1}$ (the ANN was not used).
 
-The ANN achieved 65\% sensitivity and 87\% specificity when the true positive
-rate (26\%) was made to match observations. The receiver operating
-characteristic curve is shown in Fig. \ref{fig:ann}c. We considered these rates
-satisfactory for the purpose of filtering precipitation profiles. Fig.
-\ref{fig:ann}d shows examples of the predicted precipitation compared to
-human-performed observations. The main ANN (`ANN` in Fig. \ref{fig:ann}) was
-trained on all data, and ancillary ANNs (`ANN2` in Fig \ref{fig:ann}) were
-trained on all data except for each voyage. These were used for testing the
-results relative to each voyage.
+The ANN achieved 65\% sensitivity and 87\% specificity when the true positive rate (26\%) was made to match observations.
+The receiver operating characteristic curve is shown in Fig.
+\ref{fig:ann}c.
+We considered these rates satisfactory for the purpose of filtering precipitation profiles.
+Fig.
+\ref{fig:ann}d shows examples of the predicted precipitation compared to human-performed observations.
+The main ANN (`ANN` in Fig.
+\ref{fig:ann}) was trained on all data, and ancillary ANNs (`ANN2` in Fig \ref{fig:ann}) were trained on all data except for each voyage.
+These were used for testing the results relative to each voyage.
 
@@
 \caption{
-Lower tropospheric stability (LTS) distribution in \textbf{(a)} ERA5 and
-\textbf{(b)} MERRA-2 calculated for the 31 voyage tracks and one station from
-the highest instantaneous temporal resolution data available. Shown is also the
-chosen dividing threshold of 12 K for conditions weak and strong stability.
+Lower tropospheric stability (LTS) distribution in \textbf{(a)} ERA5 and \textbf{(b)} MERRA-2 calculated for the 31 voyage tracks and one station from the highest instantaneous temporal resolution data available.
+Shown is also the chosen dividing threshold of 12 K for conditions weak and strong stability.
 }
@@
 
-We partitioned our data into two mutually exclusive subsets by cyclonic
-activity. For this purpose, we used a cyclone tracking algorithm to identify
-extratropical and polar cyclones (ECs and PCs) over the SO in the reanalysis
-and ICON data. We used the open source cyclone tracking package CyTRACK
-\citeA{perez-alarcon2024}.  Generally, what constitutes an EC is considered
-relatively arbitrary due to the very large variability of ECs \citeA{neu2013}.
-We used the mean sea level pressure field and horizontal wind speed fields as
-input to the CyTRACK algorithm. The algorithm uses pressure and wind speed
-thresholds as well as tracking across time steps to identify cyclone centres
-and radii in each time step. With this information, we could classify
-geographical areas as either cyclonic or non-cyclonic. Due to a relatively
-small total area covered by cyclones (as identified by the cyclone centre and
-radius), we chose a circle of a double radius (relative to one identified by
-CyTRACK) centred at the cyclone centre as a cyclonic area for every time step
-and cyclone. All other areas were identified as non-cyclonic. For identifying
-cyclones in the observations and the reanalyses, ERA5 pressure and wind fields
-were used as the input to CyTRACK.  This is justified by the fact that the
-large-scale pressure and wind fields in ERA5 are likely sufficiently close to
-reality. For identifying cyclones in ICON, its own pressure and wind fields
-were used as the input to CyTRACK, because the model is free-running, and thus
-the pressure and wind fields are different from reality. Subsetting by
-proximity to cyclones is a relatively crude measure because it does not take
-into account the different sectors of cyclones, which are commonly associated
-with different weather situations. However, this was a choice made for
-simplicity of the analysis, given the amount of data.
+We partitioned our data into two mutually exclusive subsets by cyclonic activity.
+For this purpose, we used a cyclone tracking algorithm to identify extratropical and polar cyclones (ECs and PCs) over the SO in the reanalysis and ICON data.
+We used the open source cyclone tracking package CyTRACK \citeA{perez-alarcon2024}.
+Generally, what constitutes an EC is considered relatively arbitrary due to the very large variability of ECs \citeA{neu2013}.
+We used the mean sea level pressure field and horizontal wind speed fields as input to the CyTRACK algorithm.
+The algorithm uses pressure and wind speed thresholds as well as tracking across time steps to identify cyclone centres and radii in each time step.
+With this information, we could classify geographical areas as either cyclonic or non-cyclonic.
+Due to a relatively small total area covered by cyclones (as identified by the cyclone centre and radius), we chose a circle of a double radius (relative to one identified by CyTRACK) centred at the cyclone centre as a cyclonic area for every time step and cyclone.
+All other areas were identified as non-cyclonic.
+For identifying cyclones in the observations and the reanalyses, ERA5 pressure and wind fields were used as the input to CyTRACK.
+This is justified by the fact that the large-scale pressure and wind fields in ERA5 are likely sufficiently close to reality.
+For identifying cyclones in ICON, its own pressure and wind fields were used as the input to CyTRACK, because the model is free-running, and thus the pressure and wind fields are different from reality.
+Subsetting by proximity to cyclones is a relatively crude measure because it does not take into account the different sectors of cyclones, which are commonly associated with different weather situations.
+However, this was a choice made for simplicity of the analysis, given the amount of data.
 
-In addition to the above, we partitioned our data into two mutually exclusive
-subsets based on LTS, which is derived as the difference between the potential
-temperature at 700 hPa and the surface.  Based on a histogram of LTS in ERA5
-and MERRA-2 calculated at all voyage tracks and stations (Fig.  \ref{fig:lts}),
-we determined a statistically-based dividing threshold of 12 K for weak
-stability (< 12 K) and strong stability (>= 12 K) conditions.
+In addition to the above, we partitioned our data into two mutually exclusive subsets based on LTS, which is derived as the difference between the potential temperature at 700 hPa and the surface.
+Based on a histogram of LTS in ERA5 and MERRA-2 calculated at all voyage tracks and stations (Fig.
+\ref{fig:lts}), we determined a statistically-based dividing threshold of 12 K for weak stability (< 12 K) and strong stability (>= 12 K) conditions.
 
@@
 \caption{
-Geographical distribution of \textbf{(a, b)} cyclonic days and \textbf{(b, d)}
-strong stability (LTS > 12 K) time steps in \textbf{(a, c)} ERA5 in years
-2010--2013 (inclusive) and \textbf{(b, d)} ICON in model years 2021--2023 (free
-running). Cyclonic days are expressed as a fraction of the number of days with
-cyclonic activity, defined as grid points located within a double radius of any
-cyclone on a given day (UTC), as identified by CyTRACK.
+Geographical distribution of \textbf{(a, b)} cyclonic days and \textbf{(b, d)} strong stability (LTS > 12 K) time steps in \textbf{(a, c)} ERA5 in years 2010--2013 (inclusive) and \textbf{(b, d)} ICON in model years 2021--2023 (free running).
+Cyclonic days are expressed as a fraction of the number of days with cyclonic activity, defined as grid points located within a double radius of any cyclone on a given day (UTC), as identified by CyTRACK.
 }
@@
 
-Fig. \ref{fig:cyclone-stability}a, b show a geographical distribution of the
-fraction of cyclonic days as determined by the cyclone tracking algorithm
-applied to the ERA5 reanalysis and ICON data (Section
-\ref{sec:cyclone-stability}). As expected, the strongest cyclonic activity is
-in the high-latitude SO zone, and it is relatively zonally symmetric at all
-latitudes.  The pattern matches reasonably well with \citeA{hoskins2005}. While
-both reanalysis and the model agree relatively well, there are clear
-differences particularly in the highest occurrence rate regions -- over the
-Amundsen Sea, where the Amundsen Sea low is located \citeA{turner2013} and which
-is more cyclonic in the reanalysis, and around Cape Adare, which is more
-cyclonic in ICON. These differences might, however, stem from the relatively
-short time periods of comparison (4 years) and the fact that the model is
-free-running.
+Fig.
+\ref{fig:cyclone-stability}a, b show a geographical distribution of the fraction of cyclonic days as determined by the cyclone tracking algorithm applied to the ERA5 reanalysis and ICON data (Section \ref{sec:cyclone-stability}).
+As expected, the strongest cyclonic activity is in the high-latitude SO zone, and it is relatively zonally symmetric at all latitudes.
+The pattern matches reasonably well with \citeA{hoskins2005}.
+While both reanalysis and the model agree relatively well, there are clear differences particularly in the highest occurrence rate regions -- over the Amundsen Sea, where the Amundsen Sea low is located \citeA{turner2013} and which is more cyclonic in the reanalysis, and around Cape Adare, which is more cyclonic in ICON.
+These differences might, however, stem from the relatively short time periods of comparison (4 years) and the fact that the model is free-running.
 
-Fig. \ref{fig:cyclone-stability}c, d show a geographical distribution of the
-conditions of weak and strong stability as determined by the LTS (Section
-\ref{sec:cyclone-stability}). Conditions of weak stability are prevalent in the
-mid-to-high SO (with respect to our SO partitioning; 50--65°S), which might be
-explained by the relatively cold near-surface air overlying the relatively warm
-sea surface. Conditions of strong stability are prevalent elsewhere over the
-SO. The distribution is also less zonally symmetric than the cyclonic activity.
-In the high-latitude SO, the presence of sea ice might have substantial
-stabilising effect \citeA{knight2024}. The ERA5 reanalysis is also
-substantially more stable than ICON across the whole region.
+Fig.
+\ref{fig:cyclone-stability}c, d show a geographical distribution of the conditions of weak and strong stability as determined by the LTS (Section \ref{sec:cyclone-stability}).
+Conditions of weak stability are prevalent in the mid-to-high SO (with respect to our SO partitioning; 50--65°S), which might be explained by the relatively cold near-surface air overlying the relatively warm sea surface.
+Conditions of strong stability are prevalent elsewhere over the SO.
+The distribution is also less zonally symmetric than the cyclonic activity.
+In the high-latitude SO, the presence of sea ice might have substantial stabilising effect \citeA{knight2024}.
+The ERA5 reanalysis is also substantially more stable than ICON across the whole region.
 
@@
 \caption{
-Cloud occurrence by height for the 31 voyages and one sub-Antarctic
-station (MICRE) in observations (O) and simulated by the ALCF from the ICON
-model (I), MERRA‐2 (M), and ERA5 reanalysis data (E). The numbers in the legend
-indicate the total cloud fraction and the number of days of data. Multiple lines
-of ICON profiles are for each of the four years of model data available.
+Cloud occurrence by height for the 31 voyages and one sub-Antarctic station (MICRE) in observations (O) and simulated by the ALCF from the ICON model (I), MERRA‐2 (M), and ERA5 reanalysis data (E).
+The numbers in the legend indicate the total cloud fraction and the number of days of data.
+Multiple lines of ICON profiles are for each of the four years of model data available.
 }
@@
 
-We used the ALCF to derive cloud occurrence by height and the total cloud
-fraction from observations, ICON, ERA5 and MERRA-2 (Fig.
-\ref{fig:cloud-occurrence-panel}). In addition, we aggregated the data sources
-(voyages and stations) by calculating the averages and percentiles of all
-individual profiles, presented in Fig. \ref{fig:cloud-occurrence}. The analysis
-shows that the total cloud fraction (determined as the fraction of profiles
-with clouds at any height in the lidar cloud mask) is underestimated in ICON by
-about 10\% and in the reanalyses by about 20\%. When analysed by height, ICON
-overestimates cloud occurrence below 1 km and underestimates it above, MERRA-2
-underestimates cloud occurrence at all heights by up to about 10\%, especially
-near the surface, and ERA5 simulates cloud occurrence relatively well above 1
-km, but strongly underestimates it near the surface.  We note that fog or
-near-surface clouds are strongly underestimated in the reanalyses (fog and
-clouds are both included in the cloud occurrence).  As shown in Fig.
-\ref{fig:cloud-occurrence-panel}, the biases are relatively consistent across
-the data sources and longitudes. We conclude that the ICON results  the
-observations better than the reanalyses in this metric.
+We used the ALCF to derive cloud occurrence by height and the total cloud fraction from observations, ICON, ERA5 and MERRA-2 (Fig.
+\ref{fig:cloud-occurrence-panel}).
+In addition, we aggregated the data sources (voyages and stations) by calculating the averages and percentiles of all individual profiles, presented in Fig.
+\ref{fig:cloud-occurrence}.
+The analysis shows that the total cloud fraction (determined as the fraction of profiles with clouds at any height in the lidar cloud mask) is underestimated in ICON by about 10\% and in the reanalyses by about 20\%.
+When analysed by height, ICON overestimates cloud occurrence below 1 km and underestimates it above, MERRA-2 underestimates cloud occurrence at all heights by up to about 10\%, especially near the surface, and ERA5 simulates cloud occurrence relatively well above 1 km, but strongly underestimates it near the surface.
+We note that fog or near-surface clouds are strongly underestimated in the reanalyses (fog and clouds are both included in the cloud occurrence).
+As shown in Fig.
+\ref{fig:cloud-occurrence-panel}, the biases are relatively consistent across the data sources and longitudes.
+We conclude that the ICON results the observations better than the reanalyses in this metric.
 
-For all observations considered (Fig. \ref{fig:cloud-occurrence}a), the data
-show cloud occurrence peaking at the surface, whereas the models show a higher
-peak (at about 500 m). The models generally underestimate the total cloud
-fraction by 10--20\% and show a strong reduction in cloud occurrence near the
-surface, which is not supported by the observations. ICON and ERA5 overestimate
-cloud occurrence at their peak (between 0--1 km). Above 1 km, ICON and MERRA-2
-underestimate cloud occurrence, but ERA5 is accurate to about 3\% or less. The
-exaggerated peak in models is partly supported by the lifting condensation
-level (LCL) distribution, which peaks higher by about 200 m in the models than
-in the observations (at the surface), although this is not very pronounced.
-This is indicative of near-surface relatively humidity being often close to
-saturation in the observations but not in the models.
+For all observations considered (Fig.
+\ref{fig:cloud-occurrence}a), the data show cloud occurrence peaking at the surface, whereas the models show a higher peak (at about 500 m).
+The models generally underestimate the total cloud fraction by 10--20\% and show a strong reduction in cloud occurrence near the surface, which is not supported by the observations.
+ICON and ERA5 overestimate cloud occurrence at their peak (between 0--1 km).
+Above 1 km, ICON and MERRA-2 underestimate cloud occurrence, but ERA5 is accurate to about 3\% or less.
+The exaggerated peak in models is partly supported by the lifting condensation level (LCL) distribution, which peaks higher by about 200 m in the models than in the observations (at the surface), although this is not very pronounced.
+This is indicative of near-surface relatively humidity being often close to saturation in the observations but not in the models.
 
-When subsetted by latitude (Fig.  \ref{fig:cloud-occurrence}b, c), we see that
-the low-latitude SO zone displays a stronger peak of cloud occurrence near the
-surface than the high-latitude SO zone, and this could be because higher
-latitudes have less stable atmospheric profiles. The low- and high-latitude SO
-zones show similar biases in models as in the general case, but ERA5 does not
-overestimate the peak in the low-latitude SO zone (near-surface cloud
-occurrence is still strongly underestimated).
+When subsetted by latitude (Fig.
+\ref{fig:cloud-occurrence}b, c), we see that the low-latitude SO zone displays a stronger peak of cloud occurrence near the surface than the high-latitude SO zone, and this could be because higher latitudes have less stable atmospheric profiles.
+The low- and high-latitude SO zones show similar biases in models as in the general case, but ERA5 does not overestimate the peak in the low-latitude SO zone (near-surface cloud occurrence is still strongly underestimated).
 
 When subsetted by cyclonic and non-cyclonic situations (Fig.
-\ref{fig:cloud-occurrence}d, e), we see that the cyclonic situations have a
-larger amount of observed cloudiness, including peak and total cloud fraction,
-both by about 7\%.  In the cyclonic situations, the model vertical profiles of
-cloud occurrence compare well with observations, but they peak higher by about
-200 m and stronger by about 8\%. The reanalyses still tend to underestimate
-cloud occurrence above 1 km by about 5\% and near the surface by about 14\%.
-Non-cyclonic situations are similar to the general case, partially also because
-they form the majority of cases.
+\ref{fig:cloud-occurrence}d, e), we see that the cyclonic situations have a larger amount of observed cloudiness, including peak and total cloud fraction, both by about 7\%.
+In the cyclonic situations, the model vertical profiles of cloud occurrence compare well with observations, but they peak higher by about 200 m and stronger by about 8\%.
+The reanalyses still tend to underestimate cloud occurrence above 1 km by about 5\% and near the surface by about 14\%.
+Non-cyclonic situations are similar to the general case, partially also because they form the majority of cases.
 
 When subsetted by conditions of weak and strong stability (Fig.
-\ref{fig:cloud-occurrence}f, g), as defined in Section
-\ref{sec:cyclone-stability}, we see that in situations of strong stability
-cloud occurrence peaks strongly at the surface in observations, compared to
-situations of weak stability, where the peak is more diffuse between 0 and 1
-km.  It is work mentioning that conditions of strong stability might be
-associated with the formation of advection fog, such as in situation of warm
-air advection from the north over colder sea surface, thus inducing fog
-formation by cooling of the warm and humid air by the cold surface.  In
-situations of strong stability, the models have smaller biases than in weak
-stability, with overestimated peak by up to 12\%, underestimated cloud
-occurrence above 1 km by up to 5\% and underestimated cloud occurrence near the
-surface by about 11\%.  In situations of weak stability, the bias in ICON is
-very pronounced, with a much stronger peak at about 500 m, ERA5 underestimates
-cloud occurrence below 1 km (especially near the surface), and MERRA-2
-underestimates cloud occurrence even more strongly.
+\ref{fig:cloud-occurrence}f, g), as defined in Section \ref{sec:cyclone-stability}, we see that in situations of strong stability cloud occurrence peaks strongly at the surface in observations, compared to situations of weak stability, where the peak is more diffuse between 0 and 1 km.
+It is work mentioning that conditions of strong stability might be associated with the formation of advection fog, such as in situation of warm air advection from the north over colder sea surface, thus inducing fog formation by cooling of the warm and humid air by the cold surface.
+In situations of strong stability, the models have smaller biases than in weak stability, with overestimated peak by up to 12\%, underestimated cloud occurrence above 1 km by up to 5\% and underestimated cloud occurrence near the surface by about 11\%.
+In situations of weak stability, the bias in ICON is very pronounced, with a much stronger peak at about 500 m, ERA5 underestimates cloud occurrence below 1 km (especially near the surface), and MERRA-2 underestimates cloud occurrence even more strongly.
 
-In all situations, even when the models overestimate cloud occurrence at some
-altitudes, they always substantially underestimate the total cloud fraction.
-ICON can be generally characterised as substantially overestimating cloud
-occurrence below 1 km and underestimating above, underestimating the total
-cloud fraction, and showing greatest biases in conditions of weak stability and
-non-cyclonic conditions. It also shows a peak of cloud occurrence at higher
-altitude than observations (500 m vs. near the surface), and correspondingly,
-its LCL tends to be higher. MERRA-2 can be generally characterised as
-underestimating cloud occurrence at nearly all altitudes as well as the total
-cloud fraction, but mostly above and below 500 m (the peak at 500 m is
-well-represented). MERRA-2 displays the largest errors relative to observations
-in the low-latitude SO zone and in situations of weak stability. ERA5 can be
-generally characterised as representing cloud occurrence correctly above about
-1--1.5 km, overestimating below, but underestimating near-surface cloud
-occurrence (0--500 m). The total cloud fraction is strongly underestimated in
-all situations. ERA5 has a tendency towards underestimation in the low-latitude
-SO zone and situations of weak stability; conversely, overestimating in the
-high-latitude SO zone and conditions of strong stability.
+In all situations, even when the models overestimate cloud occurrence at some altitudes, they always substantially underestimate the total cloud fraction.
+ICON can be generally characterised as substantially overestimating cloud occurrence below 1 km and underestimating above, underestimating the total cloud fraction, and showing greatest biases in conditions of weak stability and non-cyclonic conditions.
+It also shows a peak of cloud occurrence at higher altitude than observations (500 m vs.
+near the surface), and correspondingly, its LCL tends to be higher.
+MERRA-2 can be generally characterised as underestimating cloud occurrence at nearly all altitudes as well as the total cloud fraction, but mostly above and below 500 m (the peak at 500 m is well-represented).
+MERRA-2 displays the largest errors relative to observations in the low-latitude SO zone and in situations of weak stability.
+ERA5 can be generally characterised as representing cloud occurrence correctly above about 1--1.5 km, overestimating below, but underestimating near-surface cloud occurrence (0--500 m).
+The total cloud fraction is strongly underestimated in all situations.
+ERA5 has a tendency towards underestimation in the low-latitude SO zone and situations of weak stability; conversely, overestimating in the high-latitude SO zone and conditions of strong stability.
 
@@
 \caption{
-Cloud occurrence by height calculated as the average of all voyages and
-stations and lifting condensation level (LCL) distribution. The LCL is derived
-from radiosonde profiles and equivalent model profiles, which were not
-available for all voyages and times. The total cloud fraction (CF), average
-shortwave (SW), and longwave (LW) and the relative frequency of occurrence
-(RFO) are shown. The bands are the 16$^\mathrm{th}$--84$^\mathrm{th}$
-percentile calculated from the set of all voyages and stations.
+Cloud occurrence by height calculated as the average of all voyages and stations and lifting condensation level (LCL) distribution.
+The LCL is derived from radiosonde profiles and equivalent model profiles, which were not available for all voyages and times.
+The total cloud fraction (CF), average shortwave (SW), and longwave (LW) and the relative frequency of occurrence (RFO) are shown.
+The bands are the 16$^\mathrm{th}$--84$^\mathrm{th}$ percentile calculated from the set of all voyages and stations.
 }
@@
 We also analysed the daily cloud cover (total cloud fraction) distribution.
-This is a measure of cloudiness, irrespective of height, calculated over the
-course of a day (UTC). A cloud detected at any height means that the lidar
-profile was classified as cloudy; otherwise, it was classified as clear sky.
-When all profiles in a day are taken together, the cloud cover for the day is
-defined as the fraction of cloudy profiles in the total number of profiles,
-expressed in oktas (multiples of 1/8).
+This is a measure of cloudiness, irrespective of height, calculated over the course of a day (UTC).
+A cloud detected at any height means that the lidar profile was classified as cloudy; otherwise, it was classified as clear sky.
+When all profiles in a day are taken together, the cloud cover for the day is defined as the fraction of cloudy profiles in the total number of profiles, expressed in oktas (multiples of 1/8).
 
-In Fig.  \ref{fig:cloud-cover} we show the results for the same subsets of data
-as in Section \ref{sec:cloud-occurrence}. Observations display the highest
-proportion of high cloud cover values (5--8 oktas), peaking at 7 oktas. This
-pattern is not represented by ICON or either reanalyses.  While ICON is closest
-to matching the observed distribution, it tends to be 1 okta clearer than the
-observations, peaking at 6 oktas, and substantially underestimating days with 8
-oktas.  Overall, the reanalyses show results similar to each other,
-underestimating cloud cover by about 2 oktas and strongly underestimating days
-with 7 and 8 oktas. Of the two reanalyses, MERRA-2 has slightly higher cloud
-cover then ERA5, by about 6\% at 6 octas, which makes it more consistent with
-observations.
+In Fig.
+\ref{fig:cloud-cover} we show the results for the same subsets of data as in Section \ref{sec:cloud-occurrence}.
+Observations display the highest proportion of high cloud cover values (5--8 oktas), peaking at 7 oktas.
+This pattern is not represented by ICON or either reanalyses.
+While ICON is closest to matching the observed distribution, it tends to be 1 okta clearer than the observations, peaking at 6 oktas, and substantially underestimating days with 8 oktas.
+Overall, the reanalyses show results similar to each other, underestimating cloud cover by about 2 oktas and strongly underestimating days with 7 and 8 oktas.
+Of the two reanalyses, MERRA-2 has slightly higher cloud cover then ERA5, by about 6\% at 6 octas, which makes it more consistent with observations.
 
-When analysed by subsets, observations in the cyclonic subset show the highest
-cloud cover, with 8 oktas occurring on one half of such days (Fig.
-\ref{fig:cloud-cover}d).  This sensitivity to cyclonic conditions is not
-observed in ICON or the reanalyses. Interestingly, clear sky days (0 oktas)
-also have a local maximum peaking at about 15\% in this subset.  When we
-contrast the low- and high-latitude zones, we see that the high-latitude zone
-tends to have greater cloud cover, peaking at 8 oktas (Fig.
-\ref{fig:cloud-cover}c). The high-latitude zone also has almost no clear sky or
-small cloud cover cases (0--4 oktas). ICON and the reanalyses represent this
-characteristic of the distribution well for 0--3 oktas, but otherwise show
-biases similar to the general case. One of the greatest biases is present in
-ERA5 in the subset of weak stability, in which ERA5 peaks at 3 oktas, while the
-observations peak at 7 oktas and show negligible cloud cover below 5 oktas.
+When analysed by subsets, observations in the cyclonic subset show the highest cloud cover, with 8 oktas occurring on one half of such days (Fig.
+\ref{fig:cloud-cover}d).
+This sensitivity to cyclonic conditions is not observed in ICON or the reanalyses.
+Interestingly, clear sky days (0 oktas) also have a local maximum peaking at about 15\% in this subset.
+When we contrast the low- and high-latitude zones, we see that the high-latitude zone tends to have greater cloud cover, peaking at 8 oktas (Fig.
+\ref{fig:cloud-cover}c).
+The high-latitude zone also has almost no clear sky or small cloud cover cases (0--4 oktas).
+ICON and the reanalyses represent this characteristic of the distribution well for 0--3 oktas, but otherwise show biases similar to the general case.
+One of the greatest biases is present in ERA5 in the subset of weak stability, in which ERA5 peaks at 3 oktas, while the observations peak at 7 oktas and show negligible cloud cover below 5 oktas.
 
@@
 \caption{
-Daily total cloud fraction histograms calculated as the average of all voyage
-and station histograms. The total cloud fraction of a day (UTC) is calculated
-as a fraction of cloudy (based on the cloud mask) observed (OBS) or simulated
-lidar profiles. The models and subsets are as in Fig.
+Daily total cloud fraction histograms calculated as the average of all voyage and station histograms.
+The total cloud fraction of a day (UTC) is calculated as a fraction of cloudy (based on the cloud mask) observed (OBS) or simulated lidar profiles.
+The models and subsets are as in Fig.
 \ref{fig:cloud-occurrence}.
@@
 \caption{
-Virtual potential temperature ($\theta_v$) and relative humidity (RH)
-determined from radiosonde launches and co-located profiles in ICON, ERA5, and
-MERRA-2 in subsets as in Fig. \ref{fig:cloud-occurrence}.  The solid lines are
-the average calculated from the averages of every individual voyage and
-station. The bands span the 16$^\mathrm{th}$--84$^\mathrm{th}$ percentiles
-calculated from the distribution of the voyage and station averages. Shown is
-also the relative frequency of occurrence and the number of profiles in each
-subset.
+Virtual potential temperature ($\theta_v$) and relative humidity (RH) determined from radiosonde launches and co-located profiles in ICON, ERA5, and MERRA-2 in subsets as in Fig.
+\ref{fig:cloud-occurrence}.
+The solid lines are the average calculated from the averages of every individual voyage and station.
+The bands span the 16$^\mathrm{th}$--84$^\mathrm{th}$ percentiles calculated from the distribution of the voyage and station averages.
+Shown is also the relative frequency of occurrence and the number of profiles in each subset.
 }
@@
 
-In order to link the cloud biases to the local physical conditions, we analysed
-about 2300 radiosonde profiles south of 40°S from the 24 RV \emph{Polarstern}
-voyages, MARCUS, NBP1704, TAN1702, and TAN1802. Spatially and temporally
-colocated profiles were taken from ICON and the reanalyses.  Because the time
-period covered by the ICON model output (2021--2024) was different from the
-time period covered by the observations (2010--2021), when comparing with the
-model, we first had to remap the observation time to model time by taking the
-same time relative to the start of the year. Consequently, we also had four
-virtual/model profiles (one for each year of 2021--2024) for each observed
-profile.  The profiles were partitioned into the same subsets as above
-(Sections \ref{sec:cloud-occurrence} and \ref{sec:cloud-cover}).  Apart from
-relative humidity, we focus on comparing virtual potential temperature
-($\theta_v$) due to its role in low-level tropospheric stability, being one of
-the primary factors affecting shallow convection and the associated low-level
-cloud formation and dissipation. The observed and model profiles of virtual
-potential temperature are shown in Fig. \ref{fig:potential-temperature}.
+In order to link the cloud biases to the local physical conditions, we analysed about 2300 radiosonde profiles south of 40°S from the 24 RV \emph{Polarstern} voyages, MARCUS, NBP1704, TAN1702, and TAN1802.
+Spatially and temporally colocated profiles were taken from ICON and the reanalyses.
+Because the time period covered by the ICON model output (2021--2024) was different from the time period covered by the observations (2010--2021), when comparing with the model, we first had to remap the observation time to model time by taking the same time relative to the start of the year.
+Consequently, we also had four virtual/model profiles (one for each year of 2021--2024) for each observed profile.
+The profiles were partitioned into the same subsets as above (Sections \ref{sec:cloud-occurrence} and \ref{sec:cloud-cover}).
+Apart from relative humidity, we focus on comparing virtual potential temperature ($\theta_v$) due to its role in low-level tropospheric stability, being one of the primary factors affecting shallow convection and the associated low-level cloud formation and dissipation.
+The observed and model profiles of virtual potential temperature are shown in Fig.
+\ref{fig:potential-temperature}.
 
-Overall, the mean $\theta_v$ is accurate less than 0.5 K in ICON and MERRA-2,
-being only colder by up to 2 K in the mid-to-high troposphere (less stable) in
-ICON than in observations (Fig. \ref{fig:potential-temperature}a).  Larger
-differences exist, however, in the 40--55°S zone, where ICON is colder by about
-5 K at higher altitudes (Fig.  \ref{fig:potential-temperature}b). In other
-subsets, the bias is relatively small. MERRA-2 is very close to the
-observations, possibly due to a high accuracy of assimilation of this quantity.
-Notably, the variability of virtual potential temperature (as represented by
-the percentiles) is much smaller in ICON than in the observations. This
-indicates that the model's internal variability in the lower-tropospheric
-thermodynamic conditions in the SO is smaller than in reality.
+Overall, the mean $\theta_v$ is accurate less than 0.5 K in ICON and MERRA-2, being only colder by up to 2 K in the mid-to-high troposphere (less stable) in ICON than in observations (Fig.
+\ref{fig:potential-temperature}a).
+Larger differences exist, however, in the 40--55°S zone, where ICON is colder by about 5 K at higher altitudes (Fig.
+\ref{fig:potential-temperature}b).
+In other subsets, the bias is relatively small.
+MERRA-2 is very close to the observations, possibly due to a high accuracy of assimilation of this quantity.
+Notably, the variability of virtual potential temperature (as represented by the percentiles) is much smaller in ICON than in the observations.
+This indicates that the model's internal variability in the lower-tropospheric thermodynamic conditions in the SO is smaller than in reality.
 
-Relative humidity displays much larger biases. In all subsets, ICON is too
-humid in the first 1 km by about 5\% but very accurate above, except for the
-40--55°S zone and conditions of weak stability (Fig.
-\ref{fig:potential-temperature}b, g),  where it is too dry between about 1 and
-3 km. MERRA-2, on the other hand, is more humid than observations at all
-altitudes and in all subsets, by up to about 20\% at 5 km. Even though the mean
-near-surface relative humidity is similar to the observations (Fig.
-\ref{fig:potential-temperature}), the distribution in observation is more spread
-out across both high and low values, and thus observations have a greater
-prevalence of relative humidity close to 100\% and thus LCL located at the
-surface (Fig. \ref{fig:cloud-occurrence}a). In our calculations, LCL is a exclusive
-function of near-surface temperature, near-surface relative humidity and
-surface pressure.
+Relative humidity displays much larger biases.
+In all subsets, ICON is too humid in the first 1 km by about 5\% but very accurate above, except for the 40--55°S zone and conditions of weak stability (Fig.
+\ref{fig:potential-temperature}b, g), where it is too dry between about 1 and 3 km.
+MERRA-2, on the other hand, is more humid than observations at all altitudes and in all subsets, by up to about 20\% at 5 km.
+Even though the mean near-surface relative humidity is similar to the observations (Fig.
+\ref{fig:potential-temperature}), the distribution in observation is more spread out across both high and low values, and thus observations have a greater prevalence of relative humidity close to 100\% and thus LCL located at the surface (Fig.
+\ref{fig:cloud-occurrence}a).
+In our calculations, LCL is a exclusive function of near-surface temperature, near-surface relative humidity and surface pressure.
 
@@
 
-Let us consider the main limitations of the presented results. The spatial
-coverage of our dataset does not include most parts of the Indian Ocean and
-Pacific Ocean sectors of the SO. Even though climatological features of the SO
-are typically relatively uniform zonally, variations exist, such as those
-related to the Antarctic Peninsula and the southern tip of South America. The
-voyages were mostly undertaken in the Austral summer months and only rarely in
-the winter months, due to the poor accessibility of this region during winter.
-Therefore, our results are likely representative of summer and to a lesser
-extent, spring and autumn conditions.
+Let us consider the main limitations of the presented results.
+The spatial coverage of our dataset does not include most parts of the Indian Ocean and Pacific Ocean sectors of the SO.
+Even though climatological features of the SO are typically relatively uniform zonally, variations exist, such as those related to the Antarctic Peninsula and the southern tip of South America.
+The voyages were mostly undertaken in the Austral summer months and only rarely in the winter months, due to the poor accessibility of this region during winter.
+Therefore, our results are likely representative of summer and to a lesser extent, spring and autumn conditions.
 
-The time period of ICON is relatively short, with only four full years of
-simulation available. Moreover, the simulation is free-running and
-ocean-coupled, which means that observations had to be temporally mapped to
-this time period (at the same time relative to the start of the year) for the
-comparison. For these reasons, one can expect the results to be slightly
-different due to reasons unrelated to model biases, such as different weather
-conditions, partially accounted for by the cyclone and stability subsetting,
-and the phase of climate oscillations such as the ENSO in the observations and
-the model.
+The time period of ICON is relatively short, with only four full years of simulation available.
+Moreover, the simulation is free-running and ocean-coupled, which means that observations had to be temporally mapped to this time period (at the same time relative to the start of the year) for the comparison.
+For these reasons, one can expect the results to be slightly different due to reasons unrelated to model biases, such as different weather conditions, partially accounted for by the cyclone and stability subsetting, and the phase of climate oscillations such as the ENSO in the observations and the model.
 
-Ground-based lidar observations are affected by attenuation by thick cloud
-layers, and for this reason the results are most representative of boundary
-layer clouds, while higher-level clouds are only occasionally visible to the
-lidar when boundary layer clouds are not present. Ground-based lidar
-observations can be regarded as superior to satellite lidar observations for
-low-level clouds, which are predominant in this region, while mid- and
-high-level clouds are better sampled by satellite observations
-\citeA{mcerlich2021}.
+Ground-based lidar observations are affected by attenuation by thick cloud layers, and for this reason the results are most representative of boundary layer clouds, while higher-level clouds are only occasionally visible to the lidar when boundary layer clouds are not present.
+Ground-based lidar observations can be regarded as superior to satellite lidar observations for low-level clouds, which are predominant in this region, while mid- and high-level clouds are better sampled by satellite observations \citeA{mcerlich2021}.
 
-We have attempted to remove lidar profiles with precipitation, which could not
-be properly simulated with the lidar simulator (Section \ref{sec:ann}).
-However, the approach was limited by the relatively low sensitivity of the ANN
-(65\%) and the fact that we had to choose a fixed threshold for surface
-precipitation flux in the model and reanalyses, which might not correspond to
-detection by the ANN applied to observations. Also, we made no attempt to
-remove profiles with precipitation not reaching the surface. The above reasons
-may result in an artificial bias in the comparison, even though we expect this
-to be much smaller than the identified model biases.
+We have attempted to remove lidar profiles with precipitation, which could not be properly simulated with the lidar simulator (Section \ref{sec:ann}).
+However, the approach was limited by the relatively low sensitivity of the ANN (65\%) and the fact that we had to choose a fixed threshold for surface precipitation flux in the model and reanalyses, which might not correspond to detection by the ANN applied to observations.
+Also, we made no attempt to remove profiles with precipitation not reaching the surface.
+The above reasons may result in an artificial bias in the comparison, even though we expect this to be much smaller than the identified model biases.
 
@@
 
-We analysed a total of about 2400 days of lidar and 2300 radiosonde
-observations from 31 voyages/campaigns and a subantarctic station, covering the
-Atlantic, Australian, and New Zealand sectors of the SO over the span of 10
-years. This dataset, together with the use of a ground-based lidar simulator,
-provided a comprehensive basis for evaluating SO cloud and thermodynamic
-profile biases in the GSRM ICON and the ERA5 and MERRA-2 reanalyses. Our
-analysis provides a unique evaluation perspective different from satellite
-observations -- one that we argue is more suitable for evaluating boundary
-layer clouds, which are predominant in this region. Furthermore, we subsetted
-our dataset by low and high latitude bands, cyclonic activity, and stability in
-order to identify how these conditions influence the biases.
+We analysed a total of about 2400 days of lidar and 2300 radiosonde observations from 31 voyages/campaigns and a subantarctic station, covering the Atlantic, Australian, and New Zealand sectors of the SO over the span of 10 years.
+This dataset, together with the use of a ground-based lidar simulator, provided a comprehensive basis for evaluating SO cloud and thermodynamic profile biases in the GSRM ICON and the ERA5 and MERRA-2 reanalyses.
+Our analysis provides a unique evaluation perspective different from satellite observations -- one that we argue is more suitable for evaluating boundary layer clouds, which are predominant in this region.
+Furthermore, we subsetted our dataset by low and high latitude bands, cyclonic activity, and stability in order to identify how these conditions influence the biases.
 
-Our main finding corroborates previous findings of large boundary layer cloud
-biases in models and their subsequent effect on the radiative transfer. This
-also applies to the new GSRM ICON, but the biases are generally lower than in
-the reanalyses, despite the reanalyses having the advantage of assimilation of
-the observed meteorological conditions.  The GSRM has, on the other hand, the
-advantage of a much higher spatial resolution and, to a limited extent,
-explicit calculation of traditionally subgrid-scale processes such as
-convection.
+Our main finding corroborates previous findings of large boundary layer cloud biases in models and their subsequent effect on the radiative transfer.
+This also applies to the new GSRM ICON, but the biases are generally lower than in the reanalyses, despite the reanalyses having the advantage of assimilation of the observed meteorological conditions.
+The GSRM has, on the other hand, the advantage of a much higher spatial resolution and, to a limited extent, explicit calculation of traditionally subgrid-scale processes such as convection.
 
-We show that relative to ERA5, the distribution and strength of cyclonic
-activity over the SO is well represented in ICON, but it displays lower values
-of LTS. The latter is also manifested in the radiosonde profile comparison,
-showing that the virtual potential temperature profiles in ICON are less stable
-than in the observations over low-latitude SO.
+We show that relative to ERA5, the distribution and strength of cyclonic activity over the SO is well represented in ICON, but it displays lower values of LTS.
+The latter is also manifested in the radiosonde profile comparison, showing that the virtual potential temperature profiles in ICON are less stable than in the observations over low-latitude SO.
 
-The 31 voyages and a station show remarkably similar biases in cloud occurrence
-by height in the lidar comparison, which indicates that common underlying
-causes for the biases exist regardless of longitude and season. ICON
-underestimates the total cloud fraction by about 10\%, with an overestimation
-of clouds below 2 km and an underestimation of clouds above 2 km. The
-reanalyses also underestimate the total cloud fraction by about 20\%.  ERA5
-overestimates cloud below 1 km but underestimates near-surface cloud or fog.
-ICON strongly overestimates the peak of cloud occurrence at about 500 m, which
-might be explained by the radiosonde comparison, showing that it is too moist
-at around this height.  Similar to our results, \citeA{cesana2022} showed that
-CMIP6 models also tend to underestimate cloud occurrence above 2 km over the
-SO, although their analysis in this case was limited to liquid clouds.
+The 31 voyages and a station show remarkably similar biases in cloud occurrence by height in the lidar comparison, which indicates that common underlying causes for the biases exist regardless of longitude and season.
+ICON underestimates the total cloud fraction by about 10\%, with an overestimation of clouds below 2 km and an underestimation of clouds above 2 km.
+The reanalyses also underestimate the total cloud fraction by about 20\%.
+ERA5 overestimates cloud below 1 km but underestimates near-surface cloud or fog.
+ICON strongly overestimates the peak of cloud occurrence at about 500 m, which might be explained by the radiosonde comparison, showing that it is too moist at around this height.
+Similar to our results, \citeA{cesana2022} showed that CMIP6 models also tend to underestimate cloud occurrence above 2 km over the SO, although their analysis in this case was limited to liquid clouds.
 
-Compared to lidar observations, the daily cloud cover tends to be about 1 okta
-lower in ICON and 2 oktas lower in the reanalyses.  Conditions of weak
-stability are associated with some of the greatest biases, especially in ERA5.
-The models also underestimate the cloud cover very strongly in cyclonic
-conditions, which are very cloudy in the observations (8 oktas), but much less
-so in the models.
+Compared to lidar observations, the daily cloud cover tends to be about 1 okta lower in ICON and 2 oktas lower in the reanalyses.
+Conditions of weak stability are associated with some of the greatest biases, especially in ERA5.
+The models also underestimate the cloud cover very strongly in cyclonic conditions, which are very cloudy in the observations (8 oktas), but much less so in the models.
 
-The radiosonde observations indicate that the LCL is too high in ICON and
-reanalyses, which is probably responsible for the higher peak of clouds in the
-models and the lack of near-surface clouds or fog. The radiosonde comparison,
-however, does not seem to explain cloud biases at higher altitudes.  MERRA-2 is
-too moist at all heights.  ICON also exhibits smaller internal variability than
-the radiosonde observations. Overall, the radiosonde comparison only partially
-explains the identified cloud biases, and other physical causes are likely
-contributing.  This warrants further investigation, especially of
-ocean--atmosphere fluxes, shallow convection, and boundary layer turbulence.
-The lack of parametrised subgrid-scale convection in ICON could be a
-substantial issue even at the 5-km resolution.
+The radiosonde observations indicate that the LCL is too high in ICON and reanalyses, which is probably responsible for the higher peak of clouds in the models and the lack of near-surface clouds or fog.
+The radiosonde comparison, however, does not seem to explain cloud biases at higher altitudes.
+MERRA-2 is too moist at all heights.
+ICON also exhibits smaller internal variability than the radiosonde observations.
+Overall, the radiosonde comparison only partially explains the identified cloud biases, and other physical causes are likely contributing.
+This warrants further investigation, especially of ocean--atmosphere fluxes, shallow convection, and boundary layer turbulence.
+The lack of parametrised subgrid-scale convection in ICON could be a substantial issue even at the 5-km resolution.
 
-The relationship between cloud biases and radiation has a number of notable
-features. Perhaps unsurprisingly, the reanalyses exhibit the too few, too
-bright bias previously identified in models. In our results, this is
-characterised by outgoing TOA SW radiation similar to or higher than in the
-satellite observations, while at the same time total cloud fraction is
-substantially underestimated relative to the ground-based lidar observations.
-This feature seems to be much more pronounced in ERA5 than in MERRA-2. On the
-other hand, this relationship is not present in ICON. This model generally
-predicts smaller outgoing TOA SW radiation and smaller total cloud fraction
-than observations, and the deficit of outgoing TOA SW radiation is
-approximately proportional to the deficit of the total cloud fraction. While
-this might be a welcome feature and an improvement over previous models, it
-does mean that the outgoing TOA SW radiation is overall underestimated instead
-of being compensated by a higher cloud albedo.  This can, of course, lead to
-undesirable secondary effects such as overestimated solar heating of the sea
-surface, among other factors responsible for SO SST biases in climate models
-\citeA{zhang2023,luo2023,hyder2018}.  To some extent, the cloud albedo might be
-reduced in the model artifically by the application of an inhomogeneity factor
-to lower cloud liquid water in the radiative transfer calculations (Sec.
+The relationship between cloud biases and radiation has a number of notable features.
+Perhaps unsurprisingly, the reanalyses exhibit the too few, too bright bias previously identified in models.
+In our results, this is characterised by outgoing TOA SW radiation similar to or higher than in the satellite observations, while at the same time total cloud fraction is substantially underestimated relative to the ground-based lidar observations.
+This feature seems to be much more pronounced in ERA5 than in MERRA-2.
+On the other hand, this relationship is not present in ICON.
+This model generally predicts smaller outgoing TOA SW radiation and smaller total cloud fraction than observations, and the deficit of outgoing TOA SW radiation is approximately proportional to the deficit of the total cloud fraction.
+While this might be a welcome feature and an improvement over previous models, it does mean that the outgoing TOA SW radiation is overall underestimated instead of being compensated by a higher cloud albedo.
+This can, of course, lead to undesirable secondary effects such as overestimated solar heating of the sea surface, among other factors responsible for SO SST biases in climate models \citeA{zhang2023,luo2023,hyder2018}.
+To some extent, the cloud albedo might be reduced in the model artifically by the application of an inhomogeneity factor to lower cloud liquid water in the radiative transfer calculations (Sec.
 \ref{sec:icon}).
 
-The results imply that SO cloud biases are still a substantial issue even in
-the km-scale resolution ICON model, even though an improvement over the
-lower-resolution reanalyses is notable. More effort is needed to improve the
-model cloud simulations in this understudied region. However, this analysis
-suggests that the transition from models with parametrised convection and
-clouds to storm-resolving models might not solve these biases without
-additional effort.  Evaluation of ocean--atmosphere heat, moisture, and
-momentum fluxes against in-situ observations over the SO and comparison of GSRM
-simulations against large-eddy simulations are two potential avenues for future
-research that could elucidate the physical mechanisms behind the biases, in
-addition to the more common efforts in SO cloud microphysics and precipitation
-evaluation.
+The results imply that SO cloud biases are still a substantial issue even in the km-scale resolution ICON model, even though an improvement over the lower-resolution reanalyses is notable.
+More effort is needed to improve the model cloud simulations in this understudied region.
+However, this analysis suggests that the transition from models with parametrised convection and clouds to storm-resolving models might not solve these biases without additional effort.
+Evaluation of ocean--atmosphere heat, moisture, and momentum fluxes against in-situ observations over the SO and comparison of GSRM simulations against large-eddy simulations are two potential avenues for future research that could elucidate the physical mechanisms behind the biases, in addition to the more common efforts in SO cloud microphysics and precipitation evaluation.
 
@@
 
-The RV \emph{Polarstern} datasets are openly available on Pangaea
-(\url{https://pangaea.de}). The MARCUS and MICRE datasets are openly available
-from ARM (\url{https://www.arm.gov}). The MERRA-2 data are openly available
-from the NASA Goddard Earth Sciences (GES) Data and Information Services Center
-(DISC) (\url{https://disc.gsfc.nasa.gov/datasets?project=MERRA-2}).  The ERA5
-data are openly available from the Copernicus Climate Data Store (CDS)
-(\url{https://cds.climate.copernicus.eu}). The ICON data are available on the
-Levante cluster of the DKRZ
-(\url{https://www.dkrz.de/en/systems/hpc/hlre-4-levante}) after registration at
-\url{https://luv.dkrz.de/register/}. The CERES products are available from the
-project website (\url{https://ceres.larc.nasa.gov}) and the NASA Atmospheric
-Science Data Centre (\url{https://asdc.larc.nasa.gov/project/CERES}).  The
-TAN1802 data are available on Zenodo
-(\url{https://doi.org/10.5281/zenodo.4060237}).
+The RV \emph{Polarstern} datasets are openly available on Pangaea (\url{https://pangaea.de}).
+The MARCUS and MICRE datasets are openly available from ARM (\url{https://www.arm.gov}).
+The MERRA-2 data are openly available from the NASA Goddard Earth Sciences (GES) Data and Information Services Center (DISC) (\url{https://disc.gsfc.nasa.gov/datasets?project=MERRA-2}).
+The ERA5 data are openly available from the Copernicus Climate Data Store (CDS) (\url{https://cds.climate.copernicus.eu}).
+The ICON data are available on the Levante cluster of the DKRZ (\url{https://www.dkrz.de/en/systems/hpc/hlre-4-levante}) after registration at \url{https://luv.dkrz.de/register/}.
+The CERES products are available from the project website (\url{https://ceres.larc.nasa.gov}) and the NASA Atmospheric Science Data Centre (\url{https://asdc.larc.nasa.gov/project/CERES}).
+The TAN1802 data are available on Zenodo (\url{https://doi.org/10.5281/zenodo.4060237}).
 
@@
 
-PK and FB, and the nextGEMS project received funding from the European Union’s
-Horizon 2020 research and innovation program under a grant agreement no.
-101003470. FB received funding from the Wenner-Gren Foundation and the Swedish
-e-Science Research Centre.  The work of GM was supported by the United States
-(U.S.) Department of Energy Award DE-SC0021159.  Supercomputing resources were
-provided by the DKRZ (project 1125 ICON-development) and the National Academic
-Infrastructure for Supercomputing in Sweden (allocation 2023/22-202). The data
-collection by the University of Canterbury was funded by the Deep South
-National Science Challenge Clouds and Aerosols project.  Data collection on the
-AA15-16 voyages was funded by the Australian Antarctic Science project (grant
-no.  4292).  We acknowledge the contribution of Thorsten Mauritsen to funding
-acquisition and project management.  We acknowledge the RV \emph{Polarstern}
-datasets provided by the Alfred Wegener Institute and Pangaea, the AA15-16
-dataset provided by the Australian Antarctic Division (AAD) and University of
-Canterbury (UC), the RV \emph{Tangaroa} datasets provided by the National
-Institute of Water and Atmospheric Research and UC, the NBP1704 dataset
-provided by the National Science Foundation, Cooperative Institute for Research
-in Environmental Sciences, University of Colorado and UC, the HMNZSW16 dataset
-provided by the Royal New Zealand Navy and UC, the MARCUS dataset provided by
-ARM and AAD, and the MICRE dataset provided by ARM, the Australian Bureau of
-Meteorology, and AAD.  Technical, logistical, and ship support for MARCUS and
-MICRE were provided by the AAD through Australian Antarctic Science projects
-4292 and 4387, and we thank Steven Whiteside, Lloyd Symonds, Rick van den
-Enden, Peter de Vries, Chris Young, Chris Richards, Andrew Klekociuk, John
-French, Terry Egan, Nick Cartwright, and Ken Barrett for all of their
-assistance.  We thank the scientific staff, the crew, and everyone involved in
-collecting data on the voyages and stations, especially Gert König-Langlo,
-Holger Schmithüsen, Roger Marchand, Peter Guest, Kelly Schick, Jamie Halla, and
-Mike J.  Harvey (†). We thank Loretta Preis for providing additional RV
-\emph{Polarstern} data.  We acknowledge the ICON model output provided by the
-nextGEMS project, Deutscher Wetterdienst, Max-Planck-Institute for Meteorology,
-DKRZ, Karlsruhe Institute of Technology, and Center for Climate Systems
-Modeling; reanalysis dataset ERA5 provided by the Copernicus Climate Change
-Service; MERRA-2 provided by the Global Modeling and Assimilation Office; CERES
-datasets provided by the NASA Langley Atmospheric Science Data Center
-Distributed Active Archive Center; and the Natural Earth dataset provided by
-naturalearthdata.com.  Last but not least, we acknowledge the use of open
-source software Python, Cython \cite{behnel2011}, TensorFlow
-\cite{abadi2016}, Devuan GNU+Linux, parallel \cite{tange2011}, NumPy
-\cite{harris2020}, SciPy \cite{virtanen2020}, Matplotlib \cite{hunter2007},
-cartopy \cite{cartopy}, pyproj, Inkscape, Bash, GNU Fortran, HDF
-\cite{folk1999}, and NetCDF \cite{rew1990}.  We dedicate this study to the
-memory of Mike J.  Harvey, who very substantially contributed to obtaining the
-atmospheric observations on the RV \emph{Tangaroa} voyages used in this study.
+PK and FB, and the nextGEMS project received funding from the European Union’s Horizon 2020 research and innovation program under a grant agreement no.
+101003470.
+FB received funding from the Wenner-Gren Foundation and the Swedish e-Science Research Centre.
+The work of GM was supported by the United States (U.S.) Department of Energy Award DE-SC0021159.
+Supercomputing resources were provided by the DKRZ (project 1125 ICON-development) and the National Academic Infrastructure for Supercomputing in Sweden (allocation 2023/22-202).
+The data collection by the University of Canterbury was funded by the Deep South National Science Challenge Clouds and Aerosols project.
+Data collection on the AA15-16 voyages was funded by the Australian Antarctic Science project (grant no.
+4292).
+We acknowledge the contribution of Thorsten Mauritsen to funding acquisition and project management.
+We acknowledge the RV \emph{Polarstern} datasets provided by the Alfred Wegener Institute and Pangaea, the AA15-16 dataset provided by the Australian Antarctic Division (AAD) and University of Canterbury (UC), the RV \emph{Tangaroa} datasets provided by the National Institute of Water and Atmospheric Research and UC, the NBP1704 dataset provided by the National Science Foundation, Cooperative Institute for Research in Environmental Sciences, University of Colorado and UC, the HMNZSW16 dataset provided by the Royal New Zealand Navy and UC, the MARCUS dataset provided by ARM and AAD, and the MICRE dataset provided by ARM, the Australian Bureau of Meteorology, and AAD.
+Technical, logistical, and ship support for MARCUS and MICRE were provided by the AAD through Australian Antarctic Science projects 4292 and 4387, and we thank Steven Whiteside, Lloyd Symonds, Rick van den Enden, Peter de Vries, Chris Young, Chris Richards, Andrew Klekociuk, John French, Terry Egan, Nick Cartwright, and Ken Barrett for all of their assistance.
+We thank the scientific staff, the crew, and everyone involved in collecting data on the voyages and stations, especially Gert König-Langlo, Holger Schmithüsen, Roger Marchand, Peter Guest, Kelly Schick, Jamie Halla, and Mike J.
+Harvey (†).
+We thank Loretta Preis for providing additional RV \emph{Polarstern} data.
+We acknowledge the ICON model output provided by the nextGEMS project, Deutscher Wetterdienst, Max-Planck-Institute for Meteorology, DKRZ, Karlsruhe Institute of Technology, and Center for Climate Systems Modeling; reanalysis dataset ERA5 provided by the Copernicus Climate Change Service; MERRA-2 provided by the Global Modeling and Assimilation Office; CERES datasets provided by the NASA Langley Atmospheric Science Data Center Distributed Active Archive Center; and the Natural Earth dataset provided by naturalearthdata.com.
+Last but not least, we acknowledge the use of open source software Python, Cython \cite{behnel2011}, TensorFlow \cite{abadi2016}, Devuan GNU+Linux, parallel \cite{tange2011}, NumPy \cite{harris2020}, SciPy \cite{virtanen2020}, Matplotlib \cite{hunter2007}, cartopy \cite{cartopy}, pyproj, Inkscape, Bash, GNU Fortran, HDF \cite{folk1999}, and NetCDF \cite{rew1990}.
+We dedicate this study to the memory of Mike J.
+Harvey, who very substantially contributed to obtaining the atmospheric observations on the RV \emph{Tangaroa} voyages used in this study.
 

### 2024-12-09 manuscript_agu.tex
Fix grammar

@@
 \begin{abstract}
-Global storm-resolving models (GSRMs) are the next avenue of climate modelling.
+Global storm-resolving models (GSRMs) are the next avenue of climate modeling.
 Among them is a 5-km version of the Icosahedral Nonhydrostatic Weather and Climate Model (ICON).
-The high resolution means that parameterizations of convection and clouds including subgrid-scale clouds are forgone, relying on explicit their simulation, but still using microphysics and turbulence parametrization.
+The high resolution means that parameterizations of convection and clouds, including subgrid-scale clouds, are forgone, relying on explicit simulation, but still using microphysics and turbulence parametrization.
 Standard-resolution (10--100-km) models, which use subgrid-scale convection and cloud parametrization, have substantial cloud biases over the Southern Ocean (SO), affecting radiation and sea surface temperature.
@@
 The SO is dominated by low clouds, which cannot be observed accurately from space due to overlapping clouds, attenuation, and ground clutter.
-Instead, we analysed about 2400 days of lidar observations from 31 voyages and a station during 2010--2021 using a ground-based lidar simulator.
+Instead, we analyzed about 2400 days of lidar observations from 31 voyages and a station during 2010--2021 using a ground-based lidar simulator.
 ICON and the reanalyses underestimate the total cloud fraction by about 10 and 20\%, respectively.
@@
 Conditions of weak stability are associated with the largest errors in ICON and the reanalyses.
-Compared to radiosondes, potential temperature is accurate in the reanalyses to about 0.5 K, but ICON underestimates stability over the low-latitude SO and too humid in the boundary layer.
+Compared to radiosondes, potential temperature is accurate in the reanalyses to about 0.5 K, but ICON underestimates stability over the low-latitude SO and is too humid in the boundary layer.
 MERRA-2 is too humid at all heights.
-SO cloud biases remain a substantial issue in the GSRM, but are an improvement over the lower-resolution reanalyses.
+SO cloud biases remain a substantial issue in the GSRM but are an improvement over the lower-resolution reanalyses.
 Explicitly resolved convection and cloud processes (except microphysics) were not enough to address the model cloud biases.
@@
 Increasing climate model resolution is one way of improving model accuracy of representation of the climate system \citeA{mauritsen2022}.
-It has been practiced since the advent of climate modelling as more computational power, memory, and storage capacity become available.
+It has been practiced since the advent of climate modeling as more computational power, memory, and storage capacity become available.
 It is, however, often not as easy as changing the grid size because of the complex interplay between model dynamics and physics, which necessitates adjusting and tuning all components together.
-Increasing resolution is of course limited by the available computational power and a trade-off with increasing parameterization complexity, which is another way of improving model accuracy.
+Increasing resolution, is of course, limited by the available computational power and a trade-off with increasing parameterization complexity, which is another way of improving model accuracy.
 Current computational availability and acceleration from general-purpose computing on graphics processing units (GPUs) is progressing to enable km-scale (also called k-scale) Earth system models (ESMs) and coupled atmosphere--ocean general circulation models (AOGCMs) in research conditions today and operationally in the forthcoming years.
-Therefore, it represents a natural advance in climate modelling.
+Therefore, it represents a natural advance in climate modeling.
 Global storm-resolving models (GSRMs) are emerging as a new front in the development of high-resolution global climate models, with horizontal grid resolutions of about 2--8 km \citeA{satoh2019,stevens2019}.
@@
 
-nextGEMS is a project \citeA{nextgems} focused on the research and development of GSRMs at multiple modelling centres and universities in Europe.
-The project also develops GSRM versions of the Icosahedral Nonhydrostatic Weather and Climate Model (ICON; \citeA{hohenegger2023}), the Integrated Forecasting System [IFS; \citeA{ifs2023}], and their ocean components at eddy-resolving resolutions: ICON-O \citeA{korn2022} coupled with ICON and Finite-Element/volumE Sea ice-Ocean Model [FESOM; \citeA{wang2014}] and Nucleus for European Modelling of the Ocean [NEMO; \citeA{madec2023}] coupled with IFS.
+nextGEMS is a project \citeA{nextgems} focused on the research and development of GSRMs at multiple modeling centers and universities in Europe.
+The project also develops GSRM versions of the Icosahedral Nonhydrostatic Weather and Climate Model (ICON; \citeA{hohenegger2023}), the Integrated Forecasting System [IFS; \citeA{ifs2023}], and their ocean components at eddy-resolving resolutions: ICON-O \citeA{korn2022} coupled with ICON and Finite-Element/volumE Sea ice-Ocean Model [FESOM; \citeA{wang2014}] and Nucleus for European modeling of the Ocean [NEMO; \citeA{madec2023}] coupled with IFS.
 The project has so far produced ICON and IFS simulations with three development versions called Cycle 1--3 and a pre-final version, with a final production version planned by the end of the project.
@@
 These properties are in turn influenced by the atmospheric thermodynamics, convection and circulation, and both the indirect and direct effects of aerosols.
-Second order effects on SW and LW radiation are associated with the cloud droplet size distribution, ice crystal habit, cloud lifetime, and direct radiative interaction with aerosols.
+Second-order effects on SW and LW radiation are associated with the cloud droplet size distribution, ice crystal habit, cloud lifetime, and direct radiative interaction with aerosols.
 In the 6$^\mathrm{th}$ phase of the Coupled Model Intercomparison Project [CMIP6; \citeA{eyring2016}], the cloud feedback has increased relative to CMIP5 \citeA{zelinka2020}, which is one of the main reasons for the higher climate sensitivity of CMIP6 models.
@@
 The Southern Ocean (SO) is known to be a problematic region for climate model biases \citeA{schuddeboom2021,hyder2018,cesana2022,zhao2022} due to a lack of surface and in situ observations and being a lower priority region for numerical weather prediction (NWP) and climate model development because of its distance from populated areas.
-Nevertheless, radiation biases and changes over an area of its size have a substantial influence on the global climate \citeA{rintoul2011}, such as affecting the Earth radiation balance, ocean heat and carbon uptake \citeA{williams2023}, and the SO is an important part of the global ocean conveyor belt \citeA{wang2014}.
+Nevertheless, radiation biases and changes over an area of its size have a substantial influence on the global climate \citeA{rintoul2011}, such as affecting the Earth radiation balance, ocean heat, and carbon uptake \citeA{williams2023}, and the SO is an important part of the global ocean conveyor belt \citeA{wang2014}.
 In general, marine clouds have a disproportionate effect on top of atmosphere (TOA) SW radiation due to the relatively low albedo of the sea surface.
@@
 
-SO radiation biases have been relatively large and systematic compared to the rest of the globe since at least CMIP3 \citeA{trenberth2010}, and the SO SW cloud radiative effect (CRE) bias is still positive in eight analysed CMIP6 models analysed by \citeA{schuddeboom2021} over the high-latitude SO, whereas over the low-latitude SO it tends to be more neutral or negative in some models.
+SO radiation biases have been relatively large and systematic compared to the rest of the globe since at least CMIP3 \citeA{trenberth2010}, and the SO SW cloud radiative effect (CRE) bias is still positive in eight analyzed CMIP6 models analyzed by \citeA{schuddeboom2021} over the high-latitude SO, whereas over the low-latitude SO it tends to be more neutral or negative in some models.
 Too much absorbed SW radiation over the SO was also identified in the GSRM SCREAM \citeA{caldwell2021}.
-Compensating biases are possible, such as the `too few too bright' cloud bias, characterised by too small cloud fraction and too large cloud albedo \citeA{wall2017,kuma2020}, previously described by \citeA{webb2001}, \citeA{weare2004}, \citeA{zhang2005}, \citeA{karlsson2008}, \citeA{nam2012}, \citeA{klein2013}, and \citeA{bender2017} in other regions and models, which means that a model can maintain a reasonable SW radiation balance by reflecting too much SW radiation from clouds, but these cover too small area.
-A study by \citeA{konsta2022} showed that this type of bias is still present in six analysed CMIP6 models in tropical marine clouds, using the GCM-Oriented Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observation (CALIPSO) Cloud Product [CALIPSO--GOCCP; \citeA{chepfer2010}] and Polarization \& Anisotropy of Reflectances for Atmospheric Sciences coupled with Observations from a Lidar [PARASOL; \citeA{lier2008}] as a reference.
+Compensating biases are possible, such as the `too few too bright' cloud bias, characterized by too small cloud fraction and too large cloud albedo \citeA{wall2017,kuma2020}, previously described by \citeA{webb2001}, \citeA{weare2004}, \citeA{zhang2005}, \citeA{karlsson2008}, \citeA{nam2012}, \citeA{klein2013}, and \citeA{bender2017} in other regions and models, which means that a model can maintain a reasonable SW radiation balance by reflecting too much SW radiation from clouds, but these cover too small an area.
+A study by \citeA{konsta2022} showed that this type of bias is still present in six analyzed CMIP6 models in tropical marine clouds, using the GCM-Oriented Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observation (CALIPSO) Cloud Product [CALIPSO--GOCCP; \citeA{chepfer2010}] and Polarization \& Anisotropy of Reflectances for Atmospheric Sciences coupled with Observations from a Lidar [PARASOL; \citeA{lier2008}] as a reference.
 They suggest improper simulation of subgrid-scale cloud heterogeneity as a cause.
-Compensating cloud biases in the Australian Community Climate and Earth System Simulator (ACCESS) – Atmosphere-only model version 2 (AM2) over the SO were analysed by \citeA{fiddes2022} and \citeA{fiddes2024}.
+Compensating cloud biases in the Australian Community Climate and Earth System Simulator (ACCESS) – Atmosphere-only model version 2 (AM2) over the SO were analyzed by \citeA{fiddes2022} and \citeA{fiddes2024}.
 \citeA{possner2022} showed that over the SO, the DYAMOND GSRM ICON underestimates low-level cloud fraction on the order of 30\% [relative to Moderate Resolution Imaging Spectroradiometer (MODIS) data] and overestimates downwelling TOA SW radiation by approximately 10 Wm$^\mathrm{-2}$ [relative to the Clouds and the Earth’s Radiant Energy System (CERES) data] in the highest model resolution run (2.5 km).
-\citeA{zhao2022} reported a similar SW radiation bias in five analysed CMIP6 models over high-latitude SO and the total cloud fraction underestimation on the order of 10\% over the entire 40--60°S SO.
-Recently, \citeA{ramadoss2024} analysed 48 hours of km-scale ICON limited area model NWP simulations over a SO region adjacent to Tasmania against the Clouds, Aerosols, Precipitation, Radiation, and atmospherIc Composition Over the southeRn oceaN (CAPRICORN) voyage cloud and precipitation observations \citeA{mcfarquhar2021}.
-They found the ICON cloud optical thickness was underestimated relative to Himawari‐8 satellite observations, but also identified large differences in cloud top phase.
+\citeA{zhao2022} reported a similar SW radiation bias in five analyzed CMIP6 models over high-latitude SO and the total cloud fraction underestimation on the order of 10\% over the entire 40--60°S SO.
+Recently, \citeA{ramadoss2024} analyzed 48 hours of km-scale ICON limited-area model NWP simulations over a SO region adjacent to Tasmania against the Clouds, Aerosols, Precipitation, Radiation, and atmospherIc Composition Over the southeRn oceaN (CAPRICORN) voyage cloud and precipitation observations \citeA{mcfarquhar2021}.
+They found the ICON cloud optical thickness was underestimated relative to Himawari‐8 satellite observations but also identified large differences in cloud top phase.
 
 In general, sea surface temperature (SST) biases in the SO can originate either in the atmosphere \citeA{hyder2018}, caused by too much shortwave heating of the surface, too little longwave cooling of the surface, or in the ocean circulation.
-Interactions of both are also possible, for example SST affecting clouds and clouds affecting the surface radiation.
+Interactions of both are also possible, for example, SST affecting clouds and clouds affecting the surface radiation.
 Using the European Centre for Medium-Range Weather Forecasts (ECMWF) Reanalysis 5 (ERA5) as a reference, \citeA{zhang2023} have shown that SST biases have improved in CMIP6 compared to CMIP5, with SST overall increasing in the later CMIP phase.
@@
 The main aim of this study is to evaluate the GSRM version of ICON.
-ICON developed and maintained jointly by Deutscher Wetterdienst, Max-Planck-Institute for Meteorology, Deutsches Klimarechenzentrum (DKRZ), Karlsruhe Institute of Technology, and the Center for Climate Systems Modeling.
+ICON is developed and maintained jointly by Deutscher Wetterdienst, Max-Planck-Institute for Meteorology, Deutsches Klimarechenzentrum (DKRZ), Karlsruhe Institute of Technology, and the Center for Climate Systems Modeling.
 Previous studies have identified substantial large-scale biases in climate model clouds over the SO, affecting sea surface temperature and the Earth’s albedo.
@@
 This region is mostly dominated by boundary layer clouds generated by shallow convection, and these are problematic to observe by spaceborne lidars and radars, which are affected by attenuation by overlapping and thick clouds \citeA{mace2009,medeiros2010} and ground clutter \citeA{marchand2008}, respectively.
-Specifically, the radar on CloudSat and lidar on CALIPSO (neither of which are nowoperational) are affected by the abovementioned issues, resulting in a strong underestimation of cloud occurrence below 2 km relative to ground-based lidar observations \citeA{mcerlich2021}.
-We hypothesise that this, in turn, can lead to systematic biases in low clouds in climate models, which are frequently evaluated against CloudSat--CALIPSO products.
-Reanalyses can also suffer from cloud biases, as these are usually parametrised in their atmospheric component, and also in regions where input observations are sparse.
+Specifically, the radar on CloudSat and lidar on CALIPSO (neither of which are now operational) are affected by the abovementioned issues, resulting in a strong underestimation of cloud occurrence below 2 km relative to ground-based lidar observations \citeA{mcerlich2021}.
+We hypothesize that this, in turn, can lead to systematic biases in low clouds in climate models, which are frequently evaluated against CloudSat--CALIPSO products.
+Reanalyses can also suffer from cloud biases, as these are usually parametrized in their atmospheric component and also in regions where input observations are sparse.
 This makes them a problematic reference for clouds over the SO, and any biases relative to a reanalysis should be interpreted with caution.
-Instead, we chose to use a large set of ship-based observations conducted with ceilometers and lidars on board of the RV \emph{Polarstern} and other voyages and stations as a reference for
-the model evaluation.
+Instead, we chose to use a large set of ship-based observations conducted with ceilometers and lidars on board the RV \emph{Polarstern} and other voyages and stations as a reference for the model evaluation.
 
-Altogether, we analysed about 2400 days of data from 31 voyages, and one sub-Antarctic station covering diverse longitudes and latitudes of the SO.
+Altogether, we analyzed about 2400 days of data from 31 voyages and one sub-Antarctic station covering diverse longitudes and latitudes of the SO.
 To achieve a like-for-like comparison with the model, we used a ground-based lidar simulator called the Automatic Lidar and Ceilometer Framework [ALCF; \citeA{kuma2021}].
@@
 \textbf{(a)} A map showing the tracks of 31 voyages of RV \emph{Polarstern}, RSV \emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B.
-Palmer}, and HMNZS \emph{Wellington} and one sub-Antarctic station (Macquarie Island) analysed here.
+Palmer}, and HMNZS \emph{Wellington} and one sub-Antarctic station (Macquarie Island) analyzed here.
 The tracks cover Antarctic sectors south of South America, the Atlantic Ocean, Africa, Australia, and New Zealand in the years 2010--2021 (inclusive).
@@
 
-Together, we analysed data from 31 voyages of RV \emph{Polarstern}, the resupply vessel (RSV) \emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B.
+Together, we analyzed data from 31 voyages of RV \emph{Polarstern}, the resupply vessel (RSV) \emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B.
 Palmer}, Her (now His) Majesty's New Zealand Ship (HMNZS) \emph{Wellington} and one sub-Antarctic station (Macquarie Island) in the SO south of 40°S between 2010 and 2021.
 Fig.
-\ref{fig:map} shows a map of the voyages, Table \ref{tab:voyages} list the voyages, campaigns, and stations, and Table \ref{tab:voyage-references} lists references where available.
+\ref{fig:map} shows a map of the voyages, Table \ref{tab:voyages} lists the voyages, campaigns, and stations, and Table \ref{tab:voyage-references} lists references where available.
 Altogether, the voyages and station dataset comprised 2421 days of data south of 40°S, but the availability of ceilometer data was slightly shorter due to gaps in measurements.
@@
 The data sources contained ceilometer observations captured by the Vaisala CL51 and CT25K, and the Lufft CHM 15k, described in detail below (Sections \ref{sec:cl51} and \ref{sec:chm15k}).
-A ceilometer is a low-power near-infrared vertically pointing lidar principally designed to measure cloud base, but they also measure the full vertical structure of clouds as long as the laser signal is not attenuated by thick clouds, which can be used to infer additional information such as a cloud mask and cloud occurrence by height.
+A ceilometer is a low-power, near-infrared vertically pointing lidar principally designed to measure cloud base, but they also measure the full vertical structure of clouds as long as the laser signal is not attenuated by thick clouds, which can be used to infer additional information such as a cloud mask and cloud occurrence by height.
 We note that during the MICRE campaign, the ceilometers Vaisala CT25K and CL51 were installed at the Macquarie Island station concurrently, but in our analysis we only used the CT25K data obtained from the Atmospheric Radiation Measurement (ARM) data archive.
@@
 \caption{
-An overview of the analysed voyages, campaigns, and stations.
+An overview of the analyzed voyages, campaigns, and stations.
 Start, end, and the number of days (UTC; inclusive) refer to the time period when the vessel was south of 40°S.
@@
 The Vaisala CL51 and CT25K (photos in Fig.
-\ref{fig:map}d, e) are ceilometers operating at a near-infrared wavelength of 910 nm and 905 nm, respectively.
+\ref{fig:map}d, e) are ceilometers operating at near-infrared wavelengths of 910 nm and 905 nm, respectively.
 The CL51 can also be configured to emulate the Vaisala CL31.
@@
 The vertical resolution is 10 m (5 m configurable) in CL51 and 30 m in CT25K observations.
-The sampling (temporal) resolution is configurable, and in our datasets is approximately 6 s for CL51 on AA15‐16, 16 s for CT25K on MARCUS and MICRE, 36 s for CL51 on RV \emph{Polarstern}, and about 2.37 s for CL51 with CL31 emulation on TAN1502.
-The wavelengths of 905 and 910 nm are affected by water vapour absorption of about 20\% in the mid-latitudes \citeA{wiegner2015,wiegner2019}, with 910 nm affected more strongly, but we do not expect this to be a significant issue as explained in \citeA{kuma2021}.
+The sampling (temporal) resolution is configurable, and in our datasets, it is approximately 6 s for CL51 on AA15‐16, 16 s for CT25K on MARCUS and MICRE, 36 s for CL51 on RV \emph{Polarstern}, and about 2.37 s for CL51 with CL31 emulation on TAN1502.
+The wavelengths of 905 and 910 nm are affected by water vapor absorption of about 20\% in the mid-latitudes \citeA{wiegner2015,wiegner2019}, with 910 nm affected more strongly, but we do not expect this to be a significant issue as explained in \citeA{kuma2021}.
 The instrument data files containing raw uncalibrated backscatter were first converted to Network Common Data Form (NetCDF) with cl2nc (\url{https://github.com/peterkuma/cl2nc}) and then processed with the ALCF (Section \ref{sec:alcf}) to produce absolutely calibrated attenuated volume backscattering coefficient (AVBC), cloud mask, cloud occurrence by height, and the total cloud fraction.
 Because the CT25K uses a very similar wavelength to CL51, equivalent calculations as for CL51 were done assuming a wavelength of 910 nm.
-The Vaisala CL51 and CT25K instruments were used on most of the voyages and stations analysed here.
+The Vaisala CL51 and CT25K instruments were used on most of the voyages and stations analyzed here.
 Fig.
@@
 \caption{
-An example of attenuated volume backscattering coefficient (AVBC) \textbf{(a)} measured by CL51 during 24 hours on the PS81/3 voyage and \textbf{(b)} an equivalent AVBC simulated with the ALCF from ERA5 data during the same time period.
+An example of the attenuated volume backscattering coefficient (AVBC) \textbf{(a)} measured by CL51 during 24 hours on the PS81/3 voyage and \textbf{(b)} an equivalent AVBC simulated with the ALCF from ERA5 data during the same time period.
 The red line identifies the cloud mask determined by the ALCF.
@@
 \ref{fig:map}c) is a ceilometer operating at a near-infrared wavelength of 1064 nm.
-The maximum range is 15.4 km, the vertical resolution is 5 m in the near range (up to 150 m) and 15 m above, the sampling (temporal) resolution is 2 s, and the number of vertical levels is 1024.
+The maximum range is 15.4 km; the vertical resolution is 5 m in the near range (up to 150 m) and 15 m above; the sampling (temporal) resolution is 2 s; and the number of vertical levels is 1024.
 NetCDF files containing uncalibrated backscatter produced by the instrument were processed with the ALCF (Section \ref{sec:alcf}) to again produce AVBC, cloud mask, cloud occurrence by height, and the total cloud fraction.
@@
 Absolute calibration of the observed backscatter was performed by comparing the measured clear-sky molecular backscatter statistically with simulated clear-sky molecular backscatter.
-AVBC was resampled to 5 min temporal resolution and 50 m vertical resolution to increase signal-to-noise ratio while having enough resolution to detect small-scale cloud variability.
+AVBC was resampled to 5 min temporal resolution and 50 m vertical resolution to increase the signal-to-noise ratio while having enough resolution to detect small-scale cloud variability.
 The noise standard deviation was calculated from AVBC at the highest range, where no clouds are expected.
@@
 nextGEMS has so far produced four cycles of model runs.
-We used a Cycle 3 run \emph{ngc3028} produced in 2023 \citeA{nextgems2023a,nextgems2023b} for a model time period of 20 January 2020 to 22 July 2025, of which we analysed the period 2021--2024 (inclusive).
+We used a Cycle 3 run \emph{ngc3028} produced in 2023 \citeA{nextgems2023a,nextgems2023b} for a model time period of 20 January 2020 to 22 July 2025, of which we analyzed the period 2021--2024 (inclusive).
 While a Cycle 4 run was available, we could not use it due to a lack of availability of the necessary variables.
@@
 Turbulence and cloud microphysics are still parameterized in this model.
-To account for the radiative effects of subgrid-scale clouds, a cloud inhomogeneity factor is introduced in the model which scales down the cloud liquid water for radiative calculations.
+To account for the radiative effects of subgrid-scale clouds, a cloud inhomogeneity factor is introduced in the model, which scales down the cloud liquid water for radiative calculations.
 It ranges from 0.4 at lower tropospheric stability (LTS) of 0 K to 0.8 at 30 K.
@@
 Because the model is free-running, weather and climate oscillations (such as the El Niño--Southern Oscillation) are not expected to be equivalent to reality at the same time and place.
-To compare with the observations collected in different years (2010--2021, inclusive), we compared the model output with observations at the same time of year and geographical location, as determined for each data point such as a lidar profile or a radiosonde launch.
+To compare with the observations collected in different years (2010--2021, inclusive), we compared the model output with observations at the same time of year and geographical location, as determined for each data point, such as a lidar profile or a radiosonde launch.
 
@@
 It uses version 5.12.4 of the Goddard Earth Observing System (GEOS) atmospheric model \citeA{rienecker2008,molod2015}.
-Non-convective clouds (condensation, autoconversion, and evaporation) are parametrised using a prognostic scheme \citeA{bacmeister2006}, and sub-grid cloud fraction is determined using total water distribution and a critical relative humidity threshold.
-The reanalysis output analysed here is available at a spatial resolution of 0.5° of latitude and 0.625° of longitude, which is about 56 km in the North--South direction and 35 km in the East--West direction at 60°S.
+Non-convective clouds (condensation, autoconversion, and evaporation) are parametrized using a prognostic scheme \citeA{bacmeister2006}, and sub-grid cloud fraction is determined using total water distribution and a critical relative humidity threshold.
+The reanalysis output analyzed here is available at a spatial resolution of 0.5° of latitude and 0.625° of longitude, which is about 56 km in the North--South direction and 35 km in the East--West direction at 60°S.
 The number of vertical model levels is 72.
@@
 TOA radiation quantities are taken from the CERES instruments onboard the Terra and Aqua satellites \citeA{wielicki1996,loeb2018}.
-In our analysis we used the adjusted all sky SW and LW upwelling fluxes at TOA from the synoptic TOA and surface fluxes and clouds 1 degree daily edition 4A product (CER\_SYN1deg-Day\_Terra-Aqua-MODIS\_Edition4A) \citeA{doelling2013,doelling2016}.
+In our analysis we used the adjusted all-sky SW and LW upwelling fluxes at TOA from the synoptic TOA and surface fluxes and clouds 1-degree daily edition 4A product (CER\_SYN1deg-Day\_Terra-Aqua-MODIS\_Edition4A) \citeA{doelling2013,doelling2016}.
 
@@
 Therefore, every instantaneous profile in the simulated lidar data was assigned a daily mean radiation value corresponding to the day (in the Coordinated Universal Time; UTC).
-In turn, the average radiation during the entire voyage or station observation period were calculated as the average of the profile values.
+In turn, the average radiation during the entire voyage or station observation period was calculated as the average of the profile values.
 In the observed lidar data, the daily mean radiation value was taken from the spatially and temporally co-located CERES SYN1deg data for the day (in UTC).
@@
 \textbf{(a)} Diagram showing the TensorFlow structure of the ANN, \textbf{(b)} randomly selected example samples of near-surface backscatter in four categories (clear, fog, rain, and snow), as determined by coincident human-performed weather observations, \textbf{(c)} receiver operating characteristic diagram of the ANN, \textbf{(d)} examples of 10-day time series of human-observed (`HUM') and predicted precipitation based on an ANN trained on all voyages (`ANN') and all voyages except for the shown voyage (`ANN2') during three randomly selected voyages with the available data.
-Here, by `randomly selected' we mean selected from the top of a permutation generated by a pseudo-random number generator to prevent authors' bias in the selection.
+Here, by `randomly selected', we mean selected from the top of a permutation generated by a pseudo-random number generator to prevent authors' bias in the selection.
 }
@@
 
-Precipitation can cause strong enough lidar backscattering to be recognised as clouds by the threshold-based cloud detection method used in the ALCF.
+Precipitation can cause strong enough lidar backscattering to be recognized as clouds by the threshold-based cloud detection method used in the ALCF.
 This is undesirable if equivalent precipitation backscatter is not included in the simulated lidar profiles.
@@
 In order to achieve a fair comparison of observations with model output, we exclude observed and simulated lidar profiles with precipitation either manually or using an automated method.
-It is relatively difficult to distinguish precipitation backscatter from cloud backscatter in lidar observations, especially when only one wavelength channel and no polarised channel are available.
+It is relatively difficult to distinguish precipitation backscatter from cloud backscatter in lidar observations, especially when only one wavelength channel and no polarized channel are available.
 In models, the same can be accomplished relatively easily by excluding profiles exceeding a certain surface precipitation flux.
@@
 On the RV \emph{Polarstern} voyages, regular human-performed synoptic observations were available and included precipitation presence or absence and type.
-We used this dataset to train a convolutional artificial neural network (ANN) to recognise profiles with precipitation from lidar backscatter (Fig.
+We used this dataset to train a convolutional artificial neural network (ANN) to recognize profiles with precipitation from lidar backscatter (Fig.
 \ref{fig:ann}a), implemented in the TensorFlow ANN framework \citeA{tensorflow}.
@@
 The main ANN (`ANN` in Fig.
-\ref{fig:ann}) was trained on all data, and ancillary ANNs (`ANN2` in Fig \ref{fig:ann}) were trained on all data except for each voyage.
+\ref{fig:ann}) was trained on all data, and ancillary ANNs (`ANN2` in Fig.
+\ref{fig:ann}) were trained on all data except for each voyage.
 These were used for testing the results relative to each voyage.
@@
 Lower tropospheric stability (LTS) distribution in \textbf{(a)} ERA5 and \textbf{(b)} MERRA-2 calculated for the 31 voyage tracks and one station from the highest instantaneous temporal resolution data available.
-Shown is also the chosen dividing threshold of 12 K for conditions weak and strong stability.
+Shown is also the chosen dividing threshold of 12 K for conditions of weak and strong stability.
 }
@@
 For this purpose, we used a cyclone tracking algorithm to identify extratropical and polar cyclones (ECs and PCs) over the SO in the reanalysis and ICON data.
-We used the open source cyclone tracking package CyTRACK \citeA{perez-alarcon2024}.
+We used the open-source cyclone tracking package CyTRACK \citeA{perez-alarcon2024}.
 Generally, what constitutes an EC is considered relatively arbitrary due to the very large variability of ECs \citeA{neu2013}.
 We used the mean sea level pressure field and horizontal wind speed fields as input to the CyTRACK algorithm.
-The algorithm uses pressure and wind speed thresholds as well as tracking across time steps to identify cyclone centres and radii in each time step.
+The algorithm uses pressure and wind speed thresholds as well as tracking across time steps to identify cyclone centers and radii in each time step.
 With this information, we could classify geographical areas as either cyclonic or non-cyclonic.
-Due to a relatively small total area covered by cyclones (as identified by the cyclone centre and radius), we chose a circle of a double radius (relative to one identified by CyTRACK) centred at the cyclone centre as a cyclonic area for every time step and cyclone.
+Due to a relatively small total area covered by cyclones (as identified by the cyclone center and radius), we chose a circle of a double radius (relative to one identified by CyTRACK) centered at the cyclone center as a cyclonic area for every time step and cyclone.
 All other areas were identified as non-cyclonic.
@@
 The pattern matches reasonably well with \citeA{hoskins2005}.
-While both reanalysis and the model agree relatively well, there are clear differences particularly in the highest occurrence rate regions -- over the Amundsen Sea, where the Amundsen Sea low is located \citeA{turner2013} and which is more cyclonic in the reanalysis, and around Cape Adare, which is more cyclonic in ICON.
+While both reanalysis and the model agree relatively well, there are clear differences, particularly in the highest occurrence rate regions -- over the Amundsen Sea, where the Amundsen Sea low is located \citeA{turner2013}, and which is more cyclonic in the reanalysis, and around Cape Adare, which is more cyclonic in ICON.
 These differences might, however, stem from the relatively short time periods of comparison (4 years) and the fact that the model is free-running.
@@
 The distribution is also less zonally symmetric than the cyclonic activity.
-In the high-latitude SO, the presence of sea ice might have substantial stabilising effect \citeA{knight2024}.
+In the high-latitude SO, the presence of sea ice might have a substantial stabilising effect \citeA{knight2024}.
 The ERA5 reanalysis is also substantially more stable than ICON across the whole region.
@@
 
-We used the ALCF to derive cloud occurrence by height and the total cloud fraction from observations, ICON, ERA5 and MERRA-2 (Fig.
+We used the ALCF to derive cloud occurrence by height and the total cloud fraction from observations, ICON, ERA5, and MERRA-2 (Fig.
 \ref{fig:cloud-occurrence-panel}).
@@
 The analysis shows that the total cloud fraction (determined as the fraction of profiles with clouds at any height in the lidar cloud mask) is underestimated in ICON by about 10\% and in the reanalyses by about 20\%.
-When analysed by height, ICON overestimates cloud occurrence below 1 km and underestimates it above, MERRA-2 underestimates cloud occurrence at all heights by up to about 10\%, especially near the surface, and ERA5 simulates cloud occurrence relatively well above 1 km, but strongly underestimates it near the surface.
+When analyzed by height, ICON overestimates cloud occurrence below 1 km and underestimates it above; MERRA-2 underestimates cloud occurrence at all heights by up to about 10\%, especially near the surface; and ERA5 simulates cloud occurrence relatively well above 1 km but strongly underestimates it near the surface.
 We note that fog or near-surface clouds are strongly underestimated in the reanalyses (fog and clouds are both included in the cloud occurrence).
@@
 The exaggerated peak in models is partly supported by the lifting condensation level (LCL) distribution, which peaks higher by about 200 m in the models than in the observations (at the surface), although this is not very pronounced.
-This is indicative of near-surface relatively humidity being often close to saturation in the observations but not in the models.
+This is indicative of near-surface relative humidity being often close to saturation in the observations but not in the models.
 
@@
 When subsetted by conditions of weak and strong stability (Fig.
-\ref{fig:cloud-occurrence}f, g), as defined in Section \ref{sec:cyclone-stability}, we see that in situations of strong stability cloud occurrence peaks strongly at the surface in observations, compared to situations of weak stability, where the peak is more diffuse between 0 and 1 km.
-It is work mentioning that conditions of strong stability might be associated with the formation of advection fog, such as in situation of warm air advection from the north over colder sea surface, thus inducing fog formation by cooling of the warm and humid air by the cold surface.
-In situations of strong stability, the models have smaller biases than in weak stability, with overestimated peak by up to 12\%, underestimated cloud occurrence above 1 km by up to 5\% and underestimated cloud occurrence near the surface by about 11\%.
-In situations of weak stability, the bias in ICON is very pronounced, with a much stronger peak at about 500 m, ERA5 underestimates cloud occurrence below 1 km (especially near the surface), and MERRA-2 underestimates cloud occurrence even more strongly.
+\ref{fig:cloud-occurrence}f, g), as defined in Section \ref{sec:cyclone-stability}, we see that in situations of strong stability, cloud occurrence peaks strongly at the surface in observations, compared to situations of weak stability, where the peak is more diffuse between 0 and 1 km.
+It is worth mentioning that conditions of strong stability might be associated with the formation of advection fog, such as in situations of warm air advection from the north over colder sea surface thus inducing fog formation by cooling of the warm and humid air by the cold surface.
+In situations of strong stability, the models have smaller biases than in weak stability, with an overestimated peak by up to 12\%, underestimated cloud occurrence above 1 km by up to 5\%, and underestimated cloud occurrence near the surface by about 11\%.
+In situations of weak stability, the bias in ICON is very pronounced, with a much stronger peak at about 500 m; ERA5 underestimates cloud occurrence below 1 km (especially near the surface); and MERRA-2 underestimates cloud occurrence even more strongly.
 
 In all situations, even when the models overestimate cloud occurrence at some altitudes, they always substantially underestimate the total cloud fraction.
-ICON can be generally characterised as substantially overestimating cloud occurrence below 1 km and underestimating above, underestimating the total cloud fraction, and showing greatest biases in conditions of weak stability and non-cyclonic conditions.
-It also shows a peak of cloud occurrence at higher altitude than observations (500 m vs.
+ICON can be generally characterized as substantially overestimating cloud occurrence below 1 km and underestimating above, underestimating the total cloud fraction, and showing the greatest biases in conditions of weak stability and non-cyclonic conditions.
+It also shows a peak of cloud occurrence at higher altitudes than observations (500 m vs.
 near the surface), and correspondingly, its LCL tends to be higher.
-MERRA-2 can be generally characterised as underestimating cloud occurrence at nearly all altitudes as well as the total cloud fraction, but mostly above and below 500 m (the peak at 500 m is well-represented).
+MERRA-2 can be generally characterized as underestimating cloud occurrence at nearly all altitudes as well as the total cloud fraction, but mostly above and below 500 m (the peak at 500 m is well represented).
 MERRA-2 displays the largest errors relative to observations in the low-latitude SO zone and in situations of weak stability.
-ERA5 can be generally characterised as representing cloud occurrence correctly above about 1--1.5 km, overestimating below, but underestimating near-surface cloud occurrence (0--500 m).
+ERA5 can be generally characterized as representing cloud occurrence correctly above about 1--1.5 km, overestimating below, but underestimating near-surface cloud occurrence (0--500 m).
 The total cloud fraction is strongly underestimated in all situations.
-ERA5 has a tendency towards underestimation in the low-latitude SO zone and situations of weak stability; conversely, overestimating in the high-latitude SO zone and conditions of strong stability.
+ERA5 has a tendency towards underestimation in the low-latitude SO zone and situations of weak stability; conversely, it overestimates in the high-latitude SO zone and conditions of strong stability.
 
@@
 
-We also analysed the daily cloud cover (total cloud fraction) distribution.
+We also analyzed the daily cloud cover (total cloud fraction) distribution.
 This is a measure of cloudiness, irrespective of height, calculated over the course of a day (UTC).
-A cloud detected at any height means that the lidar profile was classified as cloudy; otherwise, it was classified as clear sky.
+A cloud detected at any height means that the lidar profile was classified as cloudy; otherwise, it was classified as a clear sky.
 When all profiles in a day are taken together, the cloud cover for the day is defined as the fraction of cloudy profiles in the total number of profiles, expressed in oktas (multiples of 1/8).
@@
 Observations display the highest proportion of high cloud cover values (5--8 oktas), peaking at 7 oktas.
-This pattern is not represented by ICON or either reanalyses.
+This pattern is not represented by ICON or either reanalysis.
 While ICON is closest to matching the observed distribution, it tends to be 1 okta clearer than the observations, peaking at 6 oktas, and substantially underestimating days with 8 oktas.
 Overall, the reanalyses show results similar to each other, underestimating cloud cover by about 2 oktas and strongly underestimating days with 7 and 8 oktas.
-Of the two reanalyses, MERRA-2 has slightly higher cloud cover then ERA5, by about 6\% at 6 octas, which makes it more consistent with observations.
+Of the two reanalyses, MERRA-2 has slightly higher cloud cover than ERA5, by about 6\% at 6 octas, which makes it more consistent with observations.
 
-When analysed by subsets, observations in the cyclonic subset show the highest cloud cover, with 8 oktas occurring on one half of such days (Fig.
+When analyzed by subsets, observations in the cyclonic subset show the highest cloud cover, with 8 oktas occurring on one half of such days (Fig.
 \ref{fig:cloud-cover}d).
@@
 
-In order to link the cloud biases to the local physical conditions, we analysed about 2300 radiosonde profiles south of 40°S from the 24 RV \emph{Polarstern} voyages, MARCUS, NBP1704, TAN1702, and TAN1802.
+In order to link the cloud biases to the local physical conditions, we analyzed about 2300 radiosonde profiles south of 40°S from the 24 RV \emph{Polarstern} voyages, MARCUS, NBP1704, TAN1702, and TAN1802.
 Spatially and temporally colocated profiles were taken from ICON and the reanalyses.
@@
 
-Overall, the mean $\theta_v$ is accurate less than 0.5 K in ICON and MERRA-2, being only colder by up to 2 K in the mid-to-high troposphere (less stable) in ICON than in observations (Fig.
+Overall, the mean $\theta_v$ is accurate to less than 0.5 K in ICON and MERRA-2, being only colder by up to 2 K in the mid-to-high troposphere (less stable) in ICON than in observations (Fig.
 \ref{fig:potential-temperature}a).
@@
 \ref{fig:cloud-occurrence}a).
-In our calculations, LCL is a exclusive function of near-surface temperature, near-surface relative humidity and surface pressure.
+In our calculations, LCL is an exclusive function of near-surface temperature, near-surface relative humidity, and surface pressure.
 
@@
 The voyages were mostly undertaken in the Austral summer months and only rarely in the winter months, due to the poor accessibility of this region during winter.
-Therefore, our results are likely representative of summer and to a lesser extent, spring and autumn conditions.
+Therefore, our results are likely representative of summer and, to a lesser extent, spring and autumn conditions.
 
@@
 
-We analysed a total of about 2400 days of lidar and 2300 radiosonde observations from 31 voyages/campaigns and a subantarctic station, covering the Atlantic, Australian, and New Zealand sectors of the SO over the span of 10 years.
+We analyzed a total of about 2400 days of lidar and 2300 radiosonde observations from 31 voyages/campaigns and a subantarctic station, covering the Atlantic, Australian, and New Zealand sectors of the SO over the span of 10 years.
 This dataset, together with the use of a ground-based lidar simulator, provided a comprehensive basis for evaluating SO cloud and thermodynamic profile biases in the GSRM ICON and the ERA5 and MERRA-2 reanalyses.
@@
 This warrants further investigation, especially of ocean--atmosphere fluxes, shallow convection, and boundary layer turbulence.
-The lack of parametrised subgrid-scale convection in ICON could be a substantial issue even at the 5-km resolution.
+The lack of parametrized subgrid-scale convection in ICON could be a substantial issue even at the 5-km resolution.
 
@@
 Perhaps unsurprisingly, the reanalyses exhibit the too few, too bright bias previously identified in models.
-In our results, this is characterised by outgoing TOA SW radiation similar to or higher than in the satellite observations, while at the same time total cloud fraction is substantially underestimated relative to the ground-based lidar observations.
+In our results, this is characterized by outgoing TOA SW radiation similar to or higher than in the satellite observations, while at the same time total cloud fraction is substantially underestimated relative to the ground-based lidar observations.
 This feature seems to be much more pronounced in ERA5 than in MERRA-2.
@@
 This can, of course, lead to undesirable secondary effects such as overestimated solar heating of the sea surface, among other factors responsible for SO SST biases in climate models \citeA{zhang2023,luo2023,hyder2018}.
-To some extent, the cloud albedo might be reduced in the model artifically by the application of an inhomogeneity factor to lower cloud liquid water in the radiative transfer calculations (Sec.
+To some extent, the cloud albedo might be reduced in the model artificially by the application of an inhomogeneity factor to lower cloud liquid water in the radiative transfer calculations (Sec.
 \ref{sec:icon}).
@@
 More effort is needed to improve the model cloud simulations in this understudied region.
-However, this analysis suggests that the transition from models with parametrised convection and clouds to storm-resolving models might not solve these biases without additional effort.
+However, this analysis suggests that the transition from models with parametrized convection and clouds to storm-resolving models might not solve these biases without additional effort.
 Evaluation of ocean--atmosphere heat, moisture, and momentum fluxes against in-situ observations over the SO and comparison of GSRM simulations against large-eddy simulations are two potential avenues for future research that could elucidate the physical mechanisms behind the biases, in addition to the more common efforts in SO cloud microphysics and precipitation evaluation.
@@
 We thank Loretta Preis for providing additional RV \emph{Polarstern} data.
-We acknowledge the ICON model output provided by the nextGEMS project, Deutscher Wetterdienst, Max-Planck-Institute for Meteorology, DKRZ, Karlsruhe Institute of Technology, and Center for Climate Systems Modeling; reanalysis dataset ERA5 provided by the Copernicus Climate Change Service; MERRA-2 provided by the Global Modeling and Assimilation Office; CERES datasets provided by the NASA Langley Atmospheric Science Data Center Distributed Active Archive Center; and the Natural Earth dataset provided by naturalearthdata.com.
-Last but not least, we acknowledge the use of open source software Python, Cython \cite{behnel2011}, TensorFlow \cite{abadi2016}, Devuan GNU+Linux, parallel \cite{tange2011}, NumPy \cite{harris2020}, SciPy \cite{virtanen2020}, Matplotlib \cite{hunter2007}, cartopy \cite{cartopy}, pyproj, Inkscape, Bash, GNU Fortran, HDF \cite{folk1999}, and NetCDF \cite{rew1990}.
+We acknowledge the ICON model output provided by the nextGEMS project, Deutscher Wetterdienst, Max-Planck-Institute for Meteorology, DKRZ, Karlsruhe Institute of Technology, and Center for Climate Systems Modeling; the reanalysis dataset ERA5 provided by the Copernicus Climate Change Service; MERRA-2 provided by the Global Modeling and Assimilation Office; CERES datasets provided by the NASA Langley Atmospheric Science Data Center Distributed Active Archive Center; and the Natural Earth dataset provided by naturalearthdata.com.
+Last but not least, we acknowledge the use of open-source software: Python, Cython \cite{behnel2011}, TensorFlow \cite{abadi2016}, Devuan GNU+Linux, parallel \cite{tange2011}, NumPy \cite{harris2020}, SciPy \cite{virtanen2020}, Matplotlib \cite{hunter2007}, cartopy \cite{cartopy}, pyproj, Inkscape, Bash, GNU Fortran, HDF \cite{folk1999}, and NetCDF \cite{rew1990}.
 We dedicate this study to the memory of Mike J.

### 2024-12-10 manuscript_agu.tex
Fix references

@@
 nextGEMS is a project \citeA{nextgems} focused on the research and development of GSRMs at multiple modeling centers and universities in Europe.
-The project also develops GSRM versions of the Icosahedral Nonhydrostatic Weather and Climate Model (ICON; \citeA{hohenegger2023}), the Integrated Forecasting System [IFS; \citeA{ifs2023}], and their ocean components at eddy-resolving resolutions: ICON-O \citeA{korn2022} coupled with ICON and Finite-Element/volumE Sea ice-Ocean Model [FESOM; \citeA{wang2014}] and Nucleus for European modeling of the Ocean [NEMO; \citeA{madec2023}] coupled with IFS.
+The project also develops GSRM versions of the Icosahedral Nonhydrostatic Weather and Climate Model (ICON; \citeA{hohenegger2023}), the Integrated Forecasting System [IFS; \citeA{ifs2023}], and their ocean components at eddy-resolving resolutions: ICON-O \citeA{korn2022} coupled with ICON and Finite-Element/volumE Sea ice-Ocean Model [FESOM; \citeA{wang2014a}] and Nucleus for European modeling of the Ocean [NEMO; \citeA{madec2023}] coupled with IFS.
 The project has so far produced ICON and IFS simulations with three development versions called Cycle 1--3 and a pre-final version, with a final production version planned by the end of the project.
@@
 The Southern Ocean (SO) is known to be a problematic region for climate model biases \citeA{schuddeboom2021,hyder2018,cesana2022,zhao2022} due to a lack of surface and in situ observations and being a lower priority region for numerical weather prediction (NWP) and climate model development because of its distance from populated areas.
-Nevertheless, radiation biases and changes over an area of its size have a substantial influence on the global climate \citeA{rintoul2011}, such as affecting the Earth radiation balance, ocean heat, and carbon uptake \citeA{williams2023}, and the SO is an important part of the global ocean conveyor belt \citeA{wang2014}.
+Nevertheless, radiation biases and changes over an area of its size have a substantial influence on the global climate \citeA{rintoul2011}, such as affecting the Earth radiation balance, ocean heat, and carbon uptake \citeA{williams2023}, and the SO is an important part of the global ocean conveyor belt \citeA{wang2014b}.
 In general, marine clouds have a disproportionate effect on top of atmosphere (TOA) SW radiation due to the relatively low albedo of the sea surface.
@@
 PS81/3   & \citeA{kniglanglo2013d,kniglanglo2013e,kniglanglo2013f,kniglanglo2014g,gutt2013} \\
-PS81/4   & \citeA{kniglanglo2013g,kniglanglo2013h,kniglanglo2013i,kniglanglo2014f,bohrmann2013} \\
-PS81/5   & \citeA{kniglanglo2013j,kniglanglo2013k,kniglanglo2013l,kniglanglo2014g,jokat2013} \\
+PS81/4   & \citeA{kniglanglo2013g,kniglanglo2013h,kniglanglo2013i,kniglanglo2014q,bohrmann2013} \\
+PS81/5   & \citeA{kniglanglo2013j,kniglanglo2013k,kniglanglo2013l,kniglanglo2014r,jokat2013} \\
 PS81/6   & \citeA{kniglanglo2013m,kniglanglo2013n,kniglanglo2013o,kniglanglo2014h,lemke2013} \\
@@
 PS118    & \citeA{schmithsen2019d,schmithsen2020d,schmithsen2021h,schmithsen2021i,dorschel2019} \\
-PS123    & \citeA{schmithsen2021j,schmithsen2021m,schmithsen2021n,schmithsen2021k,hoppmann2023} \\
-PS124    & \citeA{schmithsen2021o,schmithsen2021q,schmithsen2021p,hoppmann2023} \\
+PS123    & \citeA{schmithsen2021j,schmithsen2021m,schmithsen2021n,schmithsen2021k,hoppmann2023a} \\
+PS124    & \citeA{schmithsen2021o,schmithsen2021q,schmithsen2021p,hoppmann2023b} \\
 TAN1802  & \citeA{kremser2020,kremser2021} \\

### 2024-12-10 manuscript_agu.tex
Add key points

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% KEY POINTS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%  List up to three key points (at least one is required)
-%  Key Points summarize the main points and conclusions of the article
-%  Each must be 140 characters or fewer with no special characters or punctuation and must be complete sentences
-
-% Example:
-% \begin{keypoints}
-% \item	List up to three key points (at least one is required)
-% \item	Key Points summarize the main points and conclusions of the article
-% \item	Each must be 140 characters or fewer with no special characters or punctuation and must be complete sentences
-% \end{keypoints}
-
 \begin{keypoints}
-\item enter point 1 here
-\item enter point 2 here
-\item enter point 3 here
+\item Ground-based lidar evaluation of a km-scale global climate model and reanalyses reveals substantial cloud biases over the Southern Ocean.
+\item Fog or low cloud is underestimated in the reanalyses. In all models a cloud occurrence peak at 500 m tends to be overestimated and too high.
+\item A "too few, too bright" problem of underestimated cloud fraction, compensated by overestimated cloud albedo is present in the reanalyses.
 \end{keypoints}

### 2024-12-10 manuscript_agu.tex
Fixing stuff

@@
 \item Ground-based lidar evaluation of a km-scale global climate model and reanalyses reveals substantial cloud biases over the Southern Ocean.
-\item Fog or low cloud is underestimated in the reanalyses. In all models a cloud occurrence peak at 500 m tends to be overestimated and too high.
-\item A "too few, too bright" problem of underestimated cloud fraction, compensated by overestimated cloud albedo is present in the reanalyses.
+\item Fog or low cloud is underestimated in the reanalyses. In all models, a cloud peak at 500 m tends to be overestimated and too high.
+\item A ``too few, too bright'' problem of underestimated cloud fraction, compensated by overestimated cloud albedo, is present in the reanalyses.
 \end{keypoints}
@@
 Too much absorbed SW radiation over the SO was also identified in the GSRM SCREAM \citeA{caldwell2021}.
-Compensating biases are possible, such as the `too few too bright' cloud bias, characterized by too small cloud fraction and too large cloud albedo \citeA{wall2017,kuma2020}, previously described by \citeA{webb2001}, \citeA{weare2004}, \citeA{zhang2005}, \citeA{karlsson2008}, \citeA{nam2012}, \citeA{klein2013}, and \citeA{bender2017} in other regions and models, which means that a model can maintain a reasonable SW radiation balance by reflecting too much SW radiation from clouds, but these cover too small an area.
+Compensating biases are possible, such as the ``too few too bright'' cloud bias, characterized by too small cloud fraction and too large cloud albedo \citeA{wall2017,kuma2020}, previously described by \citeA{webb2001}, \citeA{weare2004}, \citeA{zhang2005}, \citeA{karlsson2008}, \citeA{nam2012}, \citeA{klein2013}, and \citeA{bender2017} in other regions and models, which means that a model can maintain a reasonable SW radiation balance by reflecting too much SW radiation from clouds, but these cover too small an area.
 A study by \citeA{konsta2022} showed that this type of bias is still present in six analyzed CMIP6 models in tropical marine clouds, using the GCM-Oriented Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observation (CALIPSO) Cloud Product [CALIPSO--GOCCP; \citeA{chepfer2010}] and Polarization \& Anisotropy of Reflectances for Atmospheric Sciences coupled with Observations from a Lidar [PARASOL; \citeA{lier2008}] as a reference.
@@
 Artificial neural network (ANN) for prediction of precipitation in lidar backscatter.
-\textbf{(a)} Diagram showing the TensorFlow structure of the ANN, \textbf{(b)} randomly selected example samples of near-surface backscatter in four categories (clear, fog, rain, and snow), as determined by coincident human-performed weather observations, \textbf{(c)} receiver operating characteristic diagram of the ANN, \textbf{(d)} examples of 10-day time series of human-observed (`HUM') and predicted precipitation based on an ANN trained on all voyages (`ANN') and all voyages except for the shown voyage (`ANN2') during three randomly selected voyages with the available data.
-Here, by `randomly selected', we mean selected from the top of a permutation generated by a pseudo-random number generator to prevent authors' bias in the selection.
+\textbf{(a)} Diagram showing the TensorFlow structure of the ANN, \textbf{(b)} randomly selected example samples of near-surface backscatter in four categories (clear, fog, rain, and snow), as determined by coincident human-performed weather observations, \textbf{(c)} receiver operating characteristic diagram of the ANN, \textbf{(d)} examples of 10-day time series of human-observed (``HUM'') and predicted precipitation based on an ANN trained on all voyages (``ANN'') and all voyages except for the shown voyage (``ANN2'') during three randomly selected voyages with the available data.
+Here, by ``randomly selected'', we mean selected from the top of a permutation generated by a pseudo-random number generator to prevent authors' bias in the selection.
 }

### 2024-12-10 manuscript_agu.tex
Addressing comments

@@
 While this makes the code development simpler without having to rely on uncertain parameterizations, it can miss smaller-scale clouds below the grid resolution.
-Turbulence and cloud microphysics are still parameterized in this model.
+Turbulence and cloud microphysics are still parameterized in this model, and aerosols are taken from a climatology.
 To account for the radiative effects of subgrid-scale clouds, a cloud inhomogeneity factor is introduced in the model, which scales down the cloud liquid water for radiative calculations.
@@
 This is justified by the fact that the large-scale pressure and wind fields in ERA5 are likely sufficiently close to reality.
+\citeA{mcerlich2023} have shown that wind is simulated well in ERA5 relative to the WindSat polarimetric microwave radiometer measurements \cite{meissner2009}.
 For identifying cyclones in ICON, its own pressure and wind fields were used as the input to CyTRACK, because the model is free-running, and thus the pressure and wind fields are different from reality.
@@
 Based on a histogram of LTS in ERA5 and MERRA-2 calculated at all voyage tracks and stations (Fig.
-\ref{fig:lts}), we determined a statistically-based dividing threshold of 12 K for weak stability (< 12 K) and strong stability (>= 12 K) conditions.
+\ref{fig:lts}), we determined a statistically-based dividing threshold of 12 K for weak stability ($<$ 12 K) and strong stability ($\geq$ 12 K) conditions.
 
@@
 \caption{
-Geographical distribution of \textbf{(a, b)} cyclonic days and \textbf{(b, d)} strong stability (LTS > 12 K) time steps in \textbf{(a, c)} ERA5 in years 2010--2013 (inclusive) and \textbf{(b, d)} ICON in model years 2021--2023 (free running).
+Geographical distribution of \textbf{(a, b)} cyclonic days and \textbf{(b, d)} strong stability (LTS $\geq$ 12 K) time steps in \textbf{(a, c)} ERA5 in years 2010--2013 (inclusive) and \textbf{(b, d)} ICON in model years 2021--2023 (free running).
 Cyclonic days are expressed as a fraction of the number of days with cyclonic activity, defined as grid points located within a double radius of any cyclone on a given day (UTC), as identified by CyTRACK.
@@
 When all profiles in a day are taken together, the cloud cover for the day is defined as the fraction of cloudy profiles in the total number of profiles, expressed in oktas (multiples of 1/8).
+The same calculation is done the lidar observations as for the simulated lidar profiles.
+We use the term ``okta'' independently of its use in instantaneous synoptic observations, and here it simply means 1/8 (0.125\%) of the daily cloud cover.
 

### 2024-12-10 manuscript_agu.tex
Plain language summary

@@
 \section*{Plain Language Summary}
-Enter your Plain Language Summary here or delete this section.
-Here are instructions on writing a Plain Language Summary:
-https://www.agu.org/Share-and-Advocate/Share/Community/Plain-language-summary
+
+Global storm-resolving models are climate models with km-scale horizontal resolution, which are currently in development.
+Reanalyses are the best estimates of past meteorological conditions based on an underlying global model and observations.
+We evaluated clouds and thermodynamic profiles over the Southern Ocean in one such model, as well as two reanalyses, based on 2400 days of ship and station observations.
+Thanks to the high resolution, the model relies entirely on explicit simulation of clouds, instead of subgrid-scale parametrizations.
+For the evaluation, we used ceilometer and radiosonde observations and a lidar simulator, which enables a fair comparison with the model and reanalyses.
+We subsetted our results by cyclonic activity and stability.
+We found that the model and reanalyses underestimate a lidar-derived cloud fraction, and the reanalyses do so more strongly.
+Fog or near-surface clouds are especially underestimated in the reanalyses.
+However, the model and one of the reanalyses also tend to overestimate the peak of cloud occurrence at 500 m above the ground, and it tends to be higher.
+This is linked to thermodynamic profiles, which show a higher lifting condensation level.
+Southern Ocean biases are still an important problem in the model, but an improvement over the reanalyses is notable.
 
@@
 The models also underestimate the cloud cover very strongly in cyclonic conditions, which are very cloudy in the observations (8 oktas), but much less so in the models.
+Similarly, \citeA{mcerlich2023} found a 40\% underestimation of cloud liquid water in cyclones over the SO in ERA5, despite total column water vapor simulated much more accurately (5\% underestimation).
 

### 2024-12-11 manuscript_agu.tex
Addressing comments

@@
 
-Increasing climate model resolution is one way of improving model accuracy of representation of the climate system \citeA{mauritsen2022}.
+Increasing climate model resolution is one way of improving model accuracy of representation of the climate system \cite{mauritsen2022}.
 It has been practiced since the advent of climate modeling as more computational power, memory, and storage capacity become available.
@@
 Therefore, it represents a natural advance in climate modeling.
-Global storm-resolving models (GSRMs) are emerging as a new front in the development of high-resolution global climate models, with horizontal grid resolutions of about 2--8 km \citeA{satoh2019,stevens2019}.
+Global storm-resolving models (GSRMs) are emerging as a new front in the development of high-resolution global climate models, with horizontal grid resolutions of about 2--8 km \cite{satoh2019,stevens2019}.
 This is enough to resolve mesoscale convective storms, but smaller-scale convective plumes and cloud structure remain unresolved.
-At an approximately 5-km scale, non-hydrostatic processes also become important \citeA{weisman1997}, and for this reason such models are generally non-hydrostatic.
-The terms global cloud-resolving models or global convection-permitting/-resolving models are also sometimes used interchangeably with GSRMs but imply that clouds or convection are resolved explicitly, which is not entirely true for GSRMs, as this would require an even higher horizontal resolution \citeA{satoh2019}.
-Representative of these efforts is the DYnamics of the Atmospheric general circulation Modeled On Non-hydrostatic Domains (DYAMOND) project \citeA{stevens2019,dyamond}, which is an intercomparison of nine global GSRMs over two 40-day time periods in summer (1 August -- 10 September 2016) and winter (20 January -- 1 March 2020).
+At an approximately 5-km scale, non-hydrostatic processes also become important \cite{weisman1997}, and for this reason such models are generally non-hydrostatic.
+The terms global cloud-resolving models or global convection-permitting/-resolving models are also sometimes used interchangeably with GSRMs but imply that clouds or convection are resolved explicitly, which is not entirely true for GSRMs, as this would require an even higher horizontal resolution \cite{satoh2019}.
+Representative of these efforts is the DYnamics of the Atmospheric general circulation Modeled On Non-hydrostatic Domains (DYAMOND) project \cite{stevens2019,dyamond}, which is an intercomparison of nine global GSRMs over two 40-day time periods in summer (1 August -- 10 September 2016) and winter (20 January -- 1 March 2020).
 A new one-year GSRM intercomparison is currently proposed by \citeA{takasuka2024}, with the hope of also evaluating the seasonal cycle and large-scale circulation.
@@
 
-nextGEMS is a project \citeA{nextgems} focused on the research and development of GSRMs at multiple modeling centers and universities in Europe.
-The project also develops GSRM versions of the Icosahedral Nonhydrostatic Weather and Climate Model (ICON; \citeA{hohenegger2023}), the Integrated Forecasting System [IFS; \citeA{ifs2023}], and their ocean components at eddy-resolving resolutions: ICON-O \citeA{korn2022} coupled with ICON and Finite-Element/volumE Sea ice-Ocean Model [FESOM; \citeA{wang2014a}] and Nucleus for European modeling of the Ocean [NEMO; \citeA{madec2023}] coupled with IFS.
+nextGEMS is a project \cite{nextgems} focused on the research and development of GSRMs at multiple modeling centers and universities in Europe.
+The project also develops GSRM versions of the Icosahedral Nonhydrostatic Weather and Climate Model (ICON; \citeA{hohenegger2023}), the Integrated Forecasting System [IFS; \citeA{ifs2023}], and their ocean components at eddy-resolving resolutions: ICON-O \cite{korn2022} coupled with ICON and Finite-Element/volumE Sea ice-Ocean Model [FESOM; \citeA{wang2014a}] and Nucleus for European modeling of the Ocean [NEMO; \citeA{madec2023}] coupled with IFS.
 The project has so far produced ICON and IFS simulations with three development versions called Cycle 1--3 and a pre-final version, with a final production version planned by the end of the project.
@@
 Second-order effects on SW and LW radiation are associated with the cloud droplet size distribution, ice crystal habit, cloud lifetime, and direct radiative interaction with aerosols.
-In the 6$^\mathrm{th}$ phase of the Coupled Model Intercomparison Project [CMIP6; \citeA{eyring2016}], the cloud feedback has increased relative to CMIP5 \citeA{zelinka2020}, which is one of the main reasons for the higher climate sensitivity of CMIP6 models.
+In the 6$^\mathrm{th}$ phase of the Coupled Model Intercomparison Project [CMIP6; \citeA{eyring2016}], the cloud feedback has increased relative to CMIP5 \cite{zelinka2020}, which is one of the main reasons for the higher climate sensitivity of CMIP6 models.
 
-The Southern Ocean (SO) is known to be a problematic region for climate model biases \citeA{schuddeboom2021,hyder2018,cesana2022,zhao2022} due to a lack of surface and in situ observations and being a lower priority region for numerical weather prediction (NWP) and climate model development because of its distance from populated areas.
-Nevertheless, radiation biases and changes over an area of its size have a substantial influence on the global climate \citeA{rintoul2011}, such as affecting the Earth radiation balance, ocean heat, and carbon uptake \citeA{williams2023}, and the SO is an important part of the global ocean conveyor belt \citeA{wang2014b}.
+The Southern Ocean (SO) is known to be a problematic region for climate model biases \cite{schuddeboom2021,hyder2018,cesana2022,zhao2022} due to a lack of surface and in situ observations and being a lower priority region for numerical weather prediction (NWP) and climate model development because of its distance from populated areas.
+Nevertheless, radiation biases and changes over an area of its size have a substantial influence on the global climate \cite{rintoul2011}, such as affecting the Earth radiation balance, ocean heat, and carbon uptake \cite{williams2023}, and the SO is an important part of the global ocean conveyor belt \cite{wang2014b}.
 In general, marine clouds have a disproportionate effect on top of atmosphere (TOA) SW radiation due to the relatively low albedo of the sea surface.
@@
 
-SO radiation biases have been relatively large and systematic compared to the rest of the globe since at least CMIP3 \citeA{trenberth2010}, and the SO SW cloud radiative effect (CRE) bias is still positive in eight analyzed CMIP6 models analyzed by \citeA{schuddeboom2021} over the high-latitude SO, whereas over the low-latitude SO it tends to be more neutral or negative in some models.
-Too much absorbed SW radiation over the SO was also identified in the GSRM SCREAM \citeA{caldwell2021}.
-Compensating biases are possible, such as the ``too few too bright'' cloud bias, characterized by too small cloud fraction and too large cloud albedo \citeA{wall2017,kuma2020}, previously described by \citeA{webb2001}, \citeA{weare2004}, \citeA{zhang2005}, \citeA{karlsson2008}, \citeA{nam2012}, \citeA{klein2013}, and \citeA{bender2017} in other regions and models, which means that a model can maintain a reasonable SW radiation balance by reflecting too much SW radiation from clouds, but these cover too small an area.
+SO radiation biases have been relatively large and systematic compared to the rest of the globe since at least CMIP3 \cite{trenberth2010}, and the SO SW cloud radiative effect (CRE) bias is still positive in eight analyzed CMIP6 models analyzed by \citeA{schuddeboom2021} over the high-latitude SO, whereas over the low-latitude SO it tends to be more neutral or negative in some models.
+Too much absorbed SW radiation over the SO was also identified in the GSRM SCREAM \cite{caldwell2021}.
+Compensating biases are possible, such as the ``too few too bright'' cloud bias, characterized by too small cloud fraction and too large cloud albedo \cite{wall2017,kuma2020}, previously described by \citeA{webb2001}, \citeA{weare2004}, \citeA{zhang2005}, \citeA{karlsson2008}, \citeA{nam2012}, \citeA{klein2013}, and \citeA{bender2017} in other regions and models, which means that a model can maintain a reasonable SW radiation balance by reflecting too much SW radiation from clouds, but these cover too small an area.
 A study by \citeA{konsta2022} showed that this type of bias is still present in six analyzed CMIP6 models in tropical marine clouds, using the GCM-Oriented Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observation (CALIPSO) Cloud Product [CALIPSO--GOCCP; \citeA{chepfer2010}] and Polarization \& Anisotropy of Reflectances for Atmospheric Sciences coupled with Observations from a Lidar [PARASOL; \citeA{lier2008}] as a reference.
@@
 Compensating cloud biases in the Australian Community Climate and Earth System Simulator (ACCESS) – Atmosphere-only model version 2 (AM2) over the SO were analyzed by \citeA{fiddes2022} and \citeA{fiddes2024}.
-\citeA{possner2022} showed that over the SO, the DYAMOND GSRM ICON underestimates low-level cloud fraction on the order of 30\% [relative to Moderate Resolution Imaging Spectroradiometer (MODIS) data] and overestimates downwelling TOA SW radiation by approximately 10 Wm$^\mathrm{-2}$ [relative to the Clouds and the Earth’s Radiant Energy System (CERES) data] in the highest model resolution run (2.5 km).
+\citeA{possner2022} showed that over the SO, the DYAMOND GSRM ICON underestimates low-level cloud fraction on the order of 30\% and overestimates net dowward TOA SW radiation by approximately 10 Wm$^\mathrm{-2}$ in the highest model resolution run (2.5 km).
 \citeA{zhao2022} reported a similar SW radiation bias in five analyzed CMIP6 models over high-latitude SO and the total cloud fraction underestimation on the order of 10\% over the entire 40--60°S SO.
-Recently, \citeA{ramadoss2024} analyzed 48 hours of km-scale ICON limited-area model NWP simulations over a SO region adjacent to Tasmania against the Clouds, Aerosols, Precipitation, Radiation, and atmospherIc Composition Over the southeRn oceaN (CAPRICORN) voyage cloud and precipitation observations \citeA{mcfarquhar2021}.
+Recently, \citeA{ramadoss2024} analyzed 48 hours of km-scale ICON limited-area model NWP simulations over a SO region adjacent to Tasmania against the Clouds, Aerosols, Precipitation, Radiation, and atmospherIc Composition Over the southeRn oceaN (CAPRICORN) voyage cloud and precipitation observations \cite{mcfarquhar2021}.
 They found the ICON cloud optical thickness was underestimated relative to Himawari‐8 satellite observations but also identified large differences in cloud top phase.
 
-In general, sea surface temperature (SST) biases in the SO can originate either in the atmosphere \citeA{hyder2018}, caused by too much shortwave heating of the surface, too little longwave cooling of the surface, or in the ocean circulation.
+In general, sea surface temperature (SST) biases in the SO can originate either in the atmosphere \cite{hyder2018}, caused by too much shortwave heating of the surface, too little longwave cooling of the surface, or in the ocean circulation.
 Interactions of both are also possible, for example, SST affecting clouds and clouds affecting the surface radiation.
@@
 Our aim is to quantify how well the GSRM ICON is simulating clouds in this region, particularly in light of the fact that subgrid-scale clouds and convection are not parameterized in this model.
-This region is mostly dominated by boundary layer clouds generated by shallow convection, and these are problematic to observe by spaceborne lidars and radars, which are affected by attenuation by overlapping and thick clouds \citeA{mace2009,medeiros2010} and ground clutter \citeA{marchand2008}, respectively.
-Specifically, the radar on CloudSat and lidar on CALIPSO (neither of which are now operational) are affected by the abovementioned issues, resulting in a strong underestimation of cloud occurrence below 2 km relative to ground-based lidar observations \citeA{mcerlich2021}.
+This region is mostly dominated by boundary layer clouds generated by shallow convection, and these are problematic to observe by spaceborne lidars and radars, which are affected by attenuation by overlapping and thick clouds \cite{mace2009,medeiros2010} and ground clutter \cite{marchand2008}, respectively.
+Specifically, the radar on CloudSat and lidar on CALIPSO (neither of which are now operational) are affected by the abovementioned issues, resulting in a strong underestimation of cloud occurrence below 2 km relative to ground-based lidar observations \cite{mcerlich2021}.
 We hypothesize that this, in turn, can lead to systematic biases in low clouds in climate models, which are frequently evaluated against CloudSat--CALIPSO products.
@@
 To achieve a like-for-like comparison with the model, we used a ground-based lidar simulator called the Automatic Lidar and Ceilometer Framework [ALCF; \citeA{kuma2021}].
-We contrasted the results with ERA5 \citeA{era5} and the Modern-Era Retrospective analysis for Research and Applications, Version 2 [MERRA-2; \citeA{gelaro2017}].
+We contrasted the results with ERA5 \cite{era5} and the Modern-Era Retrospective analysis for Research and Applications, Version 2 [MERRA-2; \citeA{gelaro2017}].
 
@@
 Fig.
-\ref{fig:map} shows a map of the voyages, Table \ref{tab:voyages} lists the voyages, campaigns, and stations, and Table \ref{tab:voyage-references} lists references where available.
-Altogether, the voyages and station dataset comprised 2421 days of data south of 40°S, but the availability of ceilometer data was slightly shorter due to gaps in measurements.
+\ref{fig:map} shows a map of the campaigns, Table \ref{tab:voyages} lists the campaigns, and Table \ref{tab:voyage-references} lists references where available.
+Altogether, the analyzed dataset comprised 2421 days of data south of 40°S, but the availability of ceilometer data was slightly shorter due to gaps in measurements.
 
-Missing days in the ceilometer data were HMNZSW16 (7 days): 24--27 November, 10 December, 16--17 December 2016; Measurements of Aerosols, Radiation, and CloUds over the Southern Ocean (MARCUS; 3 days): 8, 10 November, 10 December 2017; Macquarie Island Cloud Radiation Experiment (MICRE; 9 days): 7--8, 29 June, 5, 16 July, 15 August, 17 October 2016, 11 February, 21 March 2017; TAN1502 (1 day): 24 January.
-
-The data sources contained ceilometer observations captured by the Vaisala CL51 and CT25K, and the Lufft CHM 15k, described in detail below (Sections \ref{sec:cl51} and \ref{sec:chm15k}).
+The campaigns contained ceilometer observations captured by the Vaisala CL51 and CT25K, and the Lufft CHM 15k, described in detail below (Sections \ref{sec:cl51} and \ref{sec:chm15k}).
 A ceilometer is a low-power, near-infrared vertically pointing lidar principally designed to measure cloud base, but they also measure the full vertical structure of clouds as long as the laser signal is not attenuated by thick clouds, which can be used to infer additional information such as a cloud mask and cloud occurrence by height.
@@
 
-Apart from lidar observations, radiosondes were launched on weather balloons at regular synoptic times on the RV \emph{Polarstern}, MARCUS, NBP17024, TAN1702, and TAN1802 voyages and campaigns, measuring pressure, temperature, relative humidity, and the global navigation satellite system coordinates.
-Derived thermodynamic (virtual potential temperature, lifting condensation level, etc.) and dynamic physical quantities (wind speed and direction) for the measured vertical profiles were calculated with rstool \citeA{rstool}.
+Apart from lidar observations, radiosondes were launched on weather balloons at regular synoptic times on the RV \emph{Polarstern}, MARCUS, NBP17024, TAN1702, and TAN1802 campaigns, measuring pressure, temperature, relative humidity, and the global navigation satellite system coordinates.
+Derived thermodynamic (virtual potential temperature, lifting condensation level, etc.) and dynamic physical quantities (wind speed and direction) for the measured vertical profiles were calculated with rstool \cite{rstool}.
 Surface meteorological quantities were measured continuously by an onboard automatic weather station or individual instruments.
@@
 \caption{
-An overview of the analyzed voyages, campaigns, and stations.
+An overview of the analyzed campaigns (voyages and stations).
 Start, end, and the number of days (UTC; inclusive) refer to the time period when the vessel was south of 40°S.
@@
 CL51/31 indicates CL51 configured to emulate CL31.
+Missing days in the ceilometer data were HMNZSW16 (7 days): 24--27 November, 10 December, 16--17 December 2016; MARCUS (3 days): 8, 10 November, 10 December 2017; MICRE (9 days): 7--8, 29 June, 5, 16 July, 15 August, 17 October 2016, 11 February, 21 March 2017; TAN1502 (1 day): 24 January.
 }
@@
 \begin{table}[t!]
-\caption{Voyage, campaign and station publication references.}
+\caption{Campaign publication references.}
 \label{tab:voyage-references}
@@
 The sampling (temporal) resolution is configurable, and in our datasets, it is approximately 6 s for CL51 on AA15‐16, 16 s for CT25K on MARCUS and MICRE, 36 s for CL51 on RV \emph{Polarstern}, and about 2.37 s for CL51 with CL31 emulation on TAN1502.
-The wavelengths of 905 and 910 nm are affected by water vapor absorption of about 20\% in the mid-latitudes \citeA{wiegner2015,wiegner2019}, with 910 nm affected more strongly, but we do not expect this to be a significant issue as explained in \citeA{kuma2021}.
+The wavelengths of 905 and 910 nm are affected by water vapor absorption of about 20\% in the mid-latitudes \cite{wiegner2015,wiegner2019}, with 910 nm affected more strongly, but we do not expect this to be a significant issue as explained in \citeA{kuma2021}.
 The instrument data files containing raw uncalibrated backscatter were first converted to Network Common Data Form (NetCDF) with cl2nc (\url{https://github.com/peterkuma/cl2nc}) and then processed with the ALCF (Section \ref{sec:alcf}) to produce absolutely calibrated attenuated volume backscattering coefficient (AVBC), cloud mask, cloud occurrence by height, and the total cloud fraction.
@@
 
-The Automatic Lidar and Ceilometer Framework (ALCF) is a ground-based lidar simulator and a tool for processing observed lidar data, supporting various instruments and models \citeA{kuma2021}.
+The Automatic Lidar and Ceilometer Framework (ALCF) is a ground-based lidar simulator and a tool for processing observed lidar data, supporting various instruments and models \cite{kuma2021}.
 It performs radiative transfer calculations to derive equivalent lidar AVBC in an atmospheric model, which can then be compared with observed AVBC.
 For this purpose, it takes the cloud fraction, liquid and ice mass mixing ratio, temperature, and pressure model fields as an input and is run offline (on the model output rather than inside the model code).
-The lidar simulator in the ALCF is based on the instrument simulator Cloud Feedback Model Intercomparison Project (CFMIP) Observation Simulator Package (COSP) \citeA{bodas-salcedo2011}.
+The lidar simulator in the ALCF is based on the instrument simulator Cloud Feedback Model Intercomparison Project (CFMIP) Observation Simulator Package (COSP) \cite{bodas-salcedo2011}.
 After AVBC is calculated, a cloud mask, cloud occurrence by height, and the total cloud fraction are determined.
-The ALCF has been used by several research teams for model and reanalysis evaluation \citeA{kuma2020,kremser2021,guyot2022,pei2023,whitehead2023,mcdonald2024}.
+The ALCF has been used by several research teams for model and reanalysis evaluation \cite{kuma2020,kremser2021,guyot2022,pei2023,whitehead2023,mcdonald2024}.
 
@@
 
-A coupled (atmosphere--ocean) GSRM version of the ICON model is in development at the nextGEMS project \citeA{hohenegger2023}.
+A coupled (atmosphere--ocean) GSRM version of the ICON model is in development at the nextGEMS project \cite{hohenegger2023}.
 ICON is an exceptionally versatile model, allowing for simulations ranging from coarse-resolution ESM simulations, GSRM simulations, limited area model simulations, to large eddy simulations (LES), for both weather prediction and climate projections.
-ICON uses the atmospheric component ICON-A \citeA{giorgetta2018}, whose physics is derived from ECHAM6 \citeA{stevens2013}, and the ocean component ICON-O \citeA{korn2022}.
+ICON uses the atmospheric component ICON-A \cite{giorgetta2018}, whose physics is derived from ECHAM6 \cite{stevens2013}, and the ocean component ICON-O \cite{korn2022}.
 Earlier runs of the GSRM ICON from DYAMOND were evaluated by \citeA{mauritsen2022}.
@@
 nextGEMS has so far produced four cycles of model runs.
-We used a Cycle 3 run \emph{ngc3028} produced in 2023 \citeA{nextgems2023a,nextgems2023b} for a model time period of 20 January 2020 to 22 July 2025, of which we analyzed the period 2021--2024 (inclusive).
+We used a Cycle 3 run \emph{ngc3028} produced in 2023 \cite{nextgems2023a,nextgems2023b} for a model time period of 20 January 2020 to 22 July 2025, of which we analyzed the period 2021--2024 (inclusive).
 While a Cycle 4 run was available, we could not use it due to a lack of availability of the necessary variables.
@@
 
-Because the model is free-running, weather and climate oscillations (such as the El Niño--Southern Oscillation) are not expected to be equivalent to reality at the same time and place.
-To compare with the observations collected in different years (2010--2021, inclusive), we compared the model output with observations at the same time of year and geographical location, as determined for each data point, such as a lidar profile or a radiosonde launch.
+Because the analyzed ICON simulation was free-running (years 2021--2024, inclusive), weather and climate oscillations (such as the El Niño--Southern Oscillation) are not expected to be equivalent to reality at the same time and place.
+To compare with the observations collected during a different time period (years 2010--2021, inclusive), we compared the model output with observations at the same time of year and geographical location, as determined for each data point, such as a lidar profile or a radiosonde launch.
+In the ALCF, this was done using the \emph{override\_year} option (\url{https://alcf.peterkuma.net/documentation/cli/cmd_model.html}).
+For radiosonde profiles, the same mapping of time from was done.
+That is, when selecting an equivalent profile from the model, the time of the profile was changed so that the time relative to the start of the year was preserved, but the year was changed to one of the four years available in the model data.
+Thus, for every radiosonde launch, there were four equivalent model profiles.
+The geographical location was kept the same.
 
@@
 
-The Modern-Era Retrospective analysis for Research and Applications, Version 2 (MERRA-2) is a reanalysis produced by the Global Modeling and Assimilation Office at the NASA Goddard Space Flight Center \citeA{gelaro2017}.
-It uses version 5.12.4 of the Goddard Earth Observing System (GEOS) atmospheric model \citeA{rienecker2008,molod2015}.
-Non-convective clouds (condensation, autoconversion, and evaporation) are parametrized using a prognostic scheme \citeA{bacmeister2006}, and sub-grid cloud fraction is determined using total water distribution and a critical relative humidity threshold.
+The Modern-Era Retrospective analysis for Research and Applications, Version 2 (MERRA-2) is a reanalysis produced by the Global Modeling and Assimilation Office at the NASA Goddard Space Flight Center \cite{gelaro2017}.
+It uses version 5.12.4 of the Goddard Earth Observing System (GEOS) atmospheric model \cite{rienecker2008,molod2015}.
+Non-convective clouds (condensation, autoconversion, and evaporation) are parametrized using a prognostic scheme \cite{bacmeister2006}, and sub-grid cloud fraction is determined using total water distribution and a critical relative humidity threshold.
 The reanalysis output analyzed here is available at a spatial resolution of 0.5° of latitude and 0.625° of longitude, which is about 56 km in the North--South direction and 35 km in the East--West direction at 60°S.
 The number of vertical model levels is 72.
-Here, we use the following products: 1-hourly instantaneous 2D single-level diagnostics (M2I1NXASM) for 2-m temperature and humidity; 3-hourly instantaneous 3D assimilated meteorological fields (M2I3NVASM) for cloud quantities, pressure, and temperature; 1-hourly average 2D surface flux diagnostics (M2T1NXFLX) for precipitation; and 1-hourly average 2D radiation diagnostics (M2T1NXRAD) for radiation quantities \citeA{merra2}.
+Here, we use the following products: 1-hourly instantaneous 2D single-level diagnostics (M2I1NXASM) for 2-m temperature and humidity; 3-hourly instantaneous 3D assimilated meteorological fields (M2I3NVASM) for cloud quantities, pressure, and temperature; 1-hourly average 2D surface flux diagnostics (M2T1NXFLX) for precipitation; and 1-hourly average 2D radiation diagnostics (M2T1NXRAD) for radiation quantities \cite{merra2}.
 
@@
 
-ERA5 \citeA{era5} is a reanalysis produced by the ECMWF.
+ERA5 \cite{era5} is a reanalysis produced by the ECMWF.
 It is based on a numerical weather prediction model IFS version CY41R2.
@@
 
-TOA radiation quantities are taken from the CERES instruments onboard the Terra and Aqua satellites \citeA{wielicki1996,loeb2018}.
-In our analysis we used the adjusted all-sky SW and LW upwelling fluxes at TOA from the synoptic TOA and surface fluxes and clouds 1-degree daily edition 4A product (CER\_SYN1deg-Day\_Terra-Aqua-MODIS\_Edition4A) \citeA{doelling2013,doelling2016}.
+TOA radiation quantities are taken from the CERES instruments onboard the Terra and Aqua satellites \cite{wielicki1996,loeb2018}.
+In our analysis we used the adjusted all-sky SW and LW upwelling fluxes at TOA from the synoptic TOA and surface fluxes and clouds 1-degree daily edition 4A product (CER\_SYN1deg-Day\_Terra-Aqua-MODIS\_Edition4A) \cite{doelling2013,doelling2016}.
 
@@
 We used this dataset to train a convolutional artificial neural network (ANN) to recognize profiles with precipitation from lidar backscatter (Fig.
-\ref{fig:ann}a), implemented in the TensorFlow ANN framework \citeA{tensorflow}.
+\ref{fig:ann}a), implemented in the TensorFlow ANN framework \cite{tensorflow}.
 Samples of short time intervals (10 min) of near-surface lidar backscatter (0–250 m) were classified as clear, rain, snow, and fog, using the synoptic observations as a training dataset (Fig.
@@
 For this purpose, we used a cyclone tracking algorithm to identify extratropical and polar cyclones (ECs and PCs) over the SO in the reanalysis and ICON data.
-We used the open-source cyclone tracking package CyTRACK \citeA{perez-alarcon2024}.
-Generally, what constitutes an EC is considered relatively arbitrary due to the very large variability of ECs \citeA{neu2013}.
+We used the open-source cyclone tracking package CyTRACK \cite{perez-alarcon2024}.
+Generally, what constitutes an EC is considered relatively arbitrary due to the very large variability of ECs \cite{neu2013}.
 We used the mean sea level pressure field and horizontal wind speed fields as input to the CyTRACK algorithm.
@@
 The pattern matches reasonably well with \citeA{hoskins2005}.
-While both reanalysis and the model agree relatively well, there are clear differences, particularly in the highest occurrence rate regions -- over the Amundsen Sea, where the Amundsen Sea low is located \citeA{turner2013}, and which is more cyclonic in the reanalysis, and around Cape Adare, which is more cyclonic in ICON.
+While both reanalysis and the model agree relatively well, there are clear differences, particularly in the highest occurrence rate regions -- over the Amundsen Sea, where the Amundsen Sea low is located \cite{turner2013}, and which is more cyclonic in the reanalysis, and around Cape Adare, which is more cyclonic in ICON.
 These differences might, however, stem from the relatively short time periods of comparison (4 years) and the fact that the model is free-running.
@@
 The distribution is also less zonally symmetric than the cyclonic activity.
-In the high-latitude SO, the presence of sea ice might have a substantial stabilising effect \citeA{knight2024}.
+In the high-latitude SO, the presence of sea ice might have a substantial stabilising effect \cite{knight2024}.
 The ERA5 reanalysis is also substantially more stable than ICON across the whole region.
@@
 
-We used the ALCF to derive cloud occurrence by height and the total cloud fraction from observations, ICON, ERA5, and MERRA-2 (Fig.
-\ref{fig:cloud-occurrence-panel}).
-In addition, we aggregated the data sources (voyages and stations) by calculating the averages and percentiles of all individual profiles, presented in Fig.
+We used the ALCF to derive cloud occurrence by height and the total cloud fraction from observations, ICON, ERA5, and MERRA-2.
+The results for all campaigns individually are shown in Fig.
+\ref{fig:cloud-occurrence-panel}.
+In addition, we aggregated the campaigns by calculating the averages and percentiles of all individual profiles, presented in Fig.
 \ref{fig:cloud-occurrence}.
@@
 As shown in Fig.
-\ref{fig:cloud-occurrence-panel}, the biases are relatively consistent across the data sources and longitudes.
+\ref{fig:cloud-occurrence-panel}, the biases are relatively consistent across the campaigns and longitudes.
 We conclude that the ICON results the observations better than the reanalyses in this metric.
@@
 For all observations considered (Fig.
-\ref{fig:cloud-occurrence}a), the data show cloud occurrence peaking at the surface, whereas the models show a higher peak (at about 500 m).
+\ref{fig:cloud-occurrence}a), the data show cloud occurrence peaking nearly at the surface, whereas the models show a higher peak (at about 500 m).
 The models generally underestimate the total cloud fraction by 10--20\% and show a strong reduction in cloud occurrence near the surface, which is not supported by the observations.
@@
 Above 1 km, ICON and MERRA-2 underestimate cloud occurrence, but ERA5 is accurate to about 3\% or less.
-The exaggerated peak in models is partly supported by the lifting condensation level (LCL) distribution, which peaks higher by about 200 m in the models than in the observations (at the surface), although this is not very pronounced.
+The exaggerated peak in models is partly supported by the lifting condensation level (LCL) distribution, which peaks higher by about 200 m in the models than in the observations (nearly at the surface), although this is not very pronounced.
 This is indicative of near-surface relative humidity being often close to saturation in the observations but not in the models.
@@
 When subsetted by conditions of weak and strong stability (Fig.
-\ref{fig:cloud-occurrence}f, g), as defined in Section \ref{sec:cyclone-stability}, we see that in situations of strong stability, cloud occurrence peaks strongly at the surface in observations, compared to situations of weak stability, where the peak is more diffuse between 0 and 1 km.
+\ref{fig:cloud-occurrence}f, g), as defined in Section \ref{sec:cyclone-stability}, we see that in situations of strong stability, cloud occurrence peaks strongly nearly at the surface in observations, compared to situations of weak stability, where the peak is more diffuse between 0 and 1 km.
 It is worth mentioning that conditions of strong stability might be associated with the formation of advection fog, such as in situations of warm air advection from the north over colder sea surface thus inducing fog formation by cooling of the warm and humid air by the cold surface.
@@
 Ground-based lidar observations are affected by attenuation by thick cloud layers, and for this reason the results are most representative of boundary layer clouds, while higher-level clouds are only occasionally visible to the lidar when boundary layer clouds are not present.
-Ground-based lidar observations can be regarded as superior to satellite lidar observations for low-level clouds, which are predominant in this region, while mid- and high-level clouds are better sampled by satellite observations \citeA{mcerlich2021}.
+Ground-based lidar observations can be regarded as superior to satellite lidar observations for low-level clouds, which are predominant in this region, while mid- and high-level clouds are better sampled by satellite observations \cite{mcerlich2021}.
+Near-surface lidar retrievals (~100 m) are affected by uncertainties related to incomplete overlap, signal saturation (dead time), and after-pulse effect corrections \cite{kuma2021}.
 
@@
 While this might be a welcome feature and an improvement over previous models, it does mean that the outgoing TOA SW radiation is overall underestimated instead of being compensated by a higher cloud albedo.
-This can, of course, lead to undesirable secondary effects such as overestimated solar heating of the sea surface, among other factors responsible for SO SST biases in climate models \citeA{zhang2023,luo2023,hyder2018}.
+This can, of course, lead to undesirable secondary effects such as overestimated solar heating of the sea surface, among other factors responsible for SO SST biases in climate models \cite{zhang2023,luo2023,hyder2018}.
 To some extent, the cloud albedo might be reduced in the model artificially by the application of an inhomogeneity factor to lower cloud liquid water in the radiative transfer calculations (Sec.
@@
 The ICON data are available on the Levante cluster of the DKRZ (\url{https://www.dkrz.de/en/systems/hpc/hlre-4-levante}) after registration at \url{https://luv.dkrz.de/register/}.
-The CERES products are available from the project website (\url{https://ceres.larc.nasa.gov}) and the NASA Atmospheric Science Data Centre (\url{https://asdc.larc.nasa.gov/project/CERES}).
-The TAN1802 data are available on Zenodo (\url{https://doi.org/10.5281/zenodo.4060237}).
-
-% TODO: The other voyage and station data are openly available on Zenodo ().
-% Subsetted model and reanalysis data for the voyage tracks and the station and
-% data processed with the ALCF are openly available on Zenodo ().
+The CERES products are openly available from the project website (\url{https://ceres.larc.nasa.gov}) and the NASA Atmospheric Science Data Centre (\url{https://asdc.larc.nasa.gov/project/CERES}).
+The TAN1802 data are openly available on Zenodo (\url{https://doi.org/10.5281/zenodo.4060237}).
+The code for performing the presented analysis and precipitation detection is open-source and available at \url{https://github.com/peterkuma/icon-so-2024} and \url{https://github.com/peterkuma/alcf-precip}, respectively.
+The remaining voyage data are openly available on Zenodo (\url{https://doi.org/}).
 

### 2024-12-11 manuscript_agu.tex
Addressing comments

@@
 Here, we conventionally refer to the SO as ocean regions south of 40°S, low-latitude SO as 40--55°S and high-latitude SO as south of 55°S.
-The reason for this dividing latitude is to split the SO into about two equal zones, as well as the results by \citeA{schuddeboom2021} (Fig.
-2b), showing a contrast in CMIP model radiation biases, \citeA{schuddeboom2019} (Fig.
-2) and \citeA{kuma2020} (Fig.
-3) showing contrasting radiation biases in the Hadley Centre Global Environmental Model, and \citeA{cesana2022} showing contrasting cloud biases due to the 0°C isotherm reaching the surface at 55°S.
+The reason for this dividing latitude is to split the SO into about two equal zones, as well as the results by \citeA{schuddeboom2021} (Fig.\ 2b), showing a contrast in CMIP model radiation biases, \citeA{schuddeboom2019} (Fig.\ 2) and \citeA{kuma2020} (Fig.\ 3) showing contrasting radiation biases in the Hadley Centre Global Environmental Model, and \citeA{cesana2022} showing contrasting cloud biases due to the 0°C isotherm reaching the surface at 55°S.
 The findings of \citeA{niu2024}, however, support a different dividing line of 62°S based on cloud condensation nuclei concentration.
@@
 Palmer}, Her (now His) Majesty's New Zealand Ship (HMNZS) \emph{Wellington} and one sub-Antarctic station (Macquarie Island) in the SO south of 40°S between 2010 and 2021.
-Fig.
-\ref{fig:map} shows a map of the campaigns, Table \ref{tab:voyages} lists the campaigns, and Table \ref{tab:voyage-references} lists references where available.
+Fig.\ \ref{fig:map} shows a map of the campaigns, Table \ref{tab:voyages} lists the campaigns, and Table \ref{tab:voyage-references} lists references where available.
 Altogether, the analyzed dataset comprised 2421 days of data south of 40°S, but the availability of ceilometer data was slightly shorter due to gaps in measurements.
@@
 
-The Vaisala CL51 and CT25K (photos in Fig.
-\ref{fig:map}d, e) are ceilometers operating at near-infrared wavelengths of 910 nm and 905 nm, respectively.
+The Vaisala CL51 and CT25K (photos in Fig.\ \ref{fig:map}d, e) are ceilometers operating at near-infrared wavelengths of 910 nm and 905 nm, respectively.
 The CL51 can also be configured to emulate the Vaisala CL31.
@@
 The Vaisala CL51 and CT25K instruments were used on most of the voyages and stations analyzed here.
-Fig.
-\ref{fig:example}a shows an example of AVBC derived from the CL51 instrument data.
+Fig.\ \ref{fig:example}a shows an example of AVBC derived from the CL51 instrument data.
 
@@
 
-The Lufft CHM 15k (photo in Fig.
-\ref{fig:map}c) is a ceilometer operating at a near-infrared wavelength of 1064 nm.
+The Lufft CHM 15k (photo in Fig.\ \ref{fig:map}c) is a ceilometer operating at a near-infrared wavelength of 1064 nm.
 The maximum range is 15.4 km; the vertical resolution is 5 m in the near range (up to 150 m) and 15 m above; the sampling (temporal) resolution is 2 s; and the number of vertical levels is 1024.
@@
 A cloud mask was calculated from AVBC using a fixed threshold of $\mathrm{2\times 10^{-6} m^{-1}sr^{-1}}$ after subtracting 5 standard deviations of range-scaled noise.
-Fig.
-\ref{fig:example}b shows an example of simulated Vaisala CL51 backscatter from ERA5 data, corresponding to a day of measurements by the instrument on the PS81/3 voyage.
+Fig.\ \ref{fig:example}b shows an example of simulated Vaisala CL51 backscatter from ERA5 data, corresponding to a day of measurements by the instrument on the PS81/3 voyage.
 
@@
 On the RV \emph{Polarstern} voyages, regular human-performed synoptic observations were available and included precipitation presence or absence and type.
-We used this dataset to train a convolutional artificial neural network (ANN) to recognize profiles with precipitation from lidar backscatter (Fig.
-\ref{fig:ann}a), implemented in the TensorFlow ANN framework \cite{tensorflow}.
-Samples of short time intervals (10 min) of near-surface lidar backscatter (0–250 m) were classified as clear, rain, snow, and fog, using the synoptic observations as a training dataset (Fig.
-\ref{fig:ann}b).
+We used this dataset to train a convolutional artificial neural network (ANN) to recognize profiles with precipitation from lidar backscatter (Fig.\ \ref{fig:ann}a), implemented in the TensorFlow ANN framework \cite{tensorflow}.
+Samples of short time intervals (10 min) of near-surface lidar backscatter (0–250 m) were classified as clear, rain, snow, and fog, using the synoptic observations as a training dataset (Fig.\ \ref{fig:ann}b).
 From these, a binary, mutually exclusive classification of profiles as precipitating (rain or snow) or dry (clear or fog) was derived.
@@
 The ANN achieved 65\% sensitivity and 87\% specificity when the true positive rate (26\%) was made to match observations.
-The receiver operating characteristic curve is shown in Fig.
-\ref{fig:ann}c.
+The receiver operating characteristic curve is shown in Fig.\ \ref{fig:ann}c.
 We considered these rates satisfactory for the purpose of filtering precipitation profiles.
-Fig.
-\ref{fig:ann}d shows examples of the predicted precipitation compared to human-performed observations.
-The main ANN (`ANN` in Fig.
-\ref{fig:ann}) was trained on all data, and ancillary ANNs (`ANN2` in Fig.
-\ref{fig:ann}) were trained on all data except for each voyage.
+Fig.\ \ref{fig:ann}d shows examples of the predicted precipitation compared to human-performed observations.
+The main ANN (`ANN` in Fig.\ \ref{fig:ann}) was trained on all data, and ancillary ANNs (`ANN2` in Fig.\ \ref{fig:ann}) were trained on all data except for each voyage.
 These were used for testing the results relative to each voyage.
@@
 In addition to the above, we partitioned our data into two mutually exclusive subsets based on LTS, which is derived as the difference between the potential temperature at 700 hPa and the surface.
-Based on a histogram of LTS in ERA5 and MERRA-2 calculated at all voyage tracks and stations (Fig.
-\ref{fig:lts}), we determined a statistically-based dividing threshold of 12 K for weak stability ($<$ 12 K) and strong stability ($\geq$ 12 K) conditions.
+Based on a histogram of LTS in ERA5 and MERRA-2 calculated at all voyage tracks and stations (Fig.\ \ref{fig:lts}), we determined a statistically-based dividing threshold of 12 K for weak stability ($<$ 12 K) and strong stability ($\geq$ 12 K) conditions.
 
@@
 
-Fig.
-\ref{fig:cyclone-stability}a, b show a geographical distribution of the fraction of cyclonic days as determined by the cyclone tracking algorithm applied to the ERA5 reanalysis and ICON data (Section \ref{sec:cyclone-stability}).
+Fig.\ \ref{fig:cyclone-stability}a, b show a geographical distribution of the fraction of cyclonic days as determined by the cyclone tracking algorithm applied to the ERA5 reanalysis and ICON data (Section \ref{sec:cyclone-stability}).
 As expected, the strongest cyclonic activity is in the high-latitude SO zone, and it is relatively zonally symmetric at all latitudes.
@@
 
-Fig.
-\ref{fig:cyclone-stability}c, d show a geographical distribution of the conditions of weak and strong stability as determined by the LTS (Section \ref{sec:cyclone-stability}).
+Fig.\ \ref{fig:cyclone-stability}c, d show a geographical distribution of the conditions of weak and strong stability as determined by the LTS (Section \ref{sec:cyclone-stability}).
 Conditions of weak stability are prevalent in the mid-to-high SO (with respect to our SO partitioning; 50--65°S), which might be explained by the relatively cold near-surface air overlying the relatively warm sea surface.
@@
 We used the ALCF to derive cloud occurrence by height and the total cloud fraction from observations, ICON, ERA5, and MERRA-2.
-The results for all campaigns individually are shown in Fig.
-\ref{fig:cloud-occurrence-panel}.
-In addition, we aggregated the campaigns by calculating the averages and percentiles of all individual profiles, presented in Fig.
-\ref{fig:cloud-occurrence}.
+The results for all campaigns individually are shown in Fig.\ \ref{fig:cloud-occurrence-panel}.
+In addition, we aggregated the campaigns by calculating the averages and percentiles of all individual profiles, presented in Fig.\ \ref{fig:cloud-occurrence}.
 The analysis shows that the total cloud fraction (determined as the fraction of profiles with clouds at any height in the lidar cloud mask) is underestimated in ICON by about 10\% and in the reanalyses by about 20\%.
@@
 We note that fog or near-surface clouds are strongly underestimated in the reanalyses (fog and clouds are both included in the cloud occurrence).
-As shown in Fig.
-\ref{fig:cloud-occurrence-panel}, the biases are relatively consistent across the campaigns and longitudes.
+As shown in Fig.\ \ref{fig:cloud-occurrence-panel}, the biases are relatively consistent across the campaigns and longitudes.
 We conclude that the ICON results the observations better than the reanalyses in this metric.
 
-For all observations considered (Fig.
-\ref{fig:cloud-occurrence}a), the data show cloud occurrence peaking nearly at the surface, whereas the models show a higher peak (at about 500 m).
+For all observations considered (Fig.\ \ref{fig:cloud-occurrence}a), the data show cloud occurrence peaking nearly at the surface, whereas the models show a higher peak (at about 500 m).
 The models generally underestimate the total cloud fraction by 10--20\% and show a strong reduction in cloud occurrence near the surface, which is not supported by the observations.
@@
 
-When subsetted by latitude (Fig.
-\ref{fig:cloud-occurrence}b, c), we see that the low-latitude SO zone displays a stronger peak of cloud occurrence near the surface than the high-latitude SO zone, and this could be because higher latitudes have less stable atmospheric profiles.
+When subsetted by latitude (Fig.\ \ref{fig:cloud-occurrence}b, c), we see that the low-latitude SO zone displays a stronger peak of cloud occurrence near the surface than the high-latitude SO zone, and this could be because higher latitudes have less stable atmospheric profiles.
 The low- and high-latitude SO zones show similar biases in models as in the general case, but ERA5 does not overestimate the peak in the low-latitude SO zone (near-surface cloud occurrence is still strongly underestimated).
 
-When subsetted by cyclonic and non-cyclonic situations (Fig.
-\ref{fig:cloud-occurrence}d, e), we see that the cyclonic situations have a larger amount of observed cloudiness, including peak and total cloud fraction, both by about 7\%.
+When subsetted by cyclonic and non-cyclonic situations (Fig.\ \ref{fig:cloud-occurrence}d, e), we see that the cyclonic situations have a larger amount of observed cloudiness, including peak and total cloud fraction, both by about 7\%.
 In the cyclonic situations, the model vertical profiles of cloud occurrence compare well with observations, but they peak higher by about 200 m and stronger by about 8\%.
@@
 
-When subsetted by conditions of weak and strong stability (Fig.
-\ref{fig:cloud-occurrence}f, g), as defined in Section \ref{sec:cyclone-stability}, we see that in situations of strong stability, cloud occurrence peaks strongly nearly at the surface in observations, compared to situations of weak stability, where the peak is more diffuse between 0 and 1 km.
+When subsetted by conditions of weak and strong stability (Fig.\ \ref{fig:cloud-occurrence}f, g), as defined in Section \ref{sec:cyclone-stability}, we see that in situations of strong stability, cloud occurrence peaks strongly nearly at the surface in observations, compared to situations of weak stability, where the peak is more diffuse between 0 and 1 km.
 It is worth mentioning that conditions of strong stability might be associated with the formation of advection fog, such as in situations of warm air advection from the north over colder sea surface thus inducing fog formation by cooling of the warm and humid air by the cold surface.
@@
 
-In Fig.
-\ref{fig:cloud-cover} we show the results for the same subsets of data as in Section \ref{sec:cloud-occurrence}.
+In Fig.\ \ref{fig:cloud-cover} we show the results for the same subsets of data as in Section \ref{sec:cloud-occurrence}.
 Observations display the highest proportion of high cloud cover values (5--8 oktas), peaking at 7 oktas.
@@
 
-When analyzed by subsets, observations in the cyclonic subset show the highest cloud cover, with 8 oktas occurring on one half of such days (Fig.
-\ref{fig:cloud-cover}d).
+When analyzed by subsets, observations in the cyclonic subset show the highest cloud cover, with 8 oktas occurring on one half of such days (Fig.\ \ref{fig:cloud-cover}d).
 This sensitivity to cyclonic conditions is not observed in ICON or the reanalyses.
 Interestingly, clear sky days (0 oktas) also have a local maximum peaking at about 15\% in this subset.
-When we contrast the low- and high-latitude zones, we see that the high-latitude zone tends to have greater cloud cover, peaking at 8 oktas (Fig.
-\ref{fig:cloud-cover}c).
+When we contrast the low- and high-latitude zones, we see that the high-latitude zone tends to have greater cloud cover, peaking at 8 oktas (Fig.\ \ref{fig:cloud-cover}c).
 The high-latitude zone also has almost no clear sky or small cloud cover cases (0--4 oktas).
@@
 The total cloud fraction of a day (UTC) is calculated as a fraction of cloudy (based on the cloud mask) observed (OBS) or simulated lidar profiles.
-The models and subsets are as in Fig.
-\ref{fig:cloud-occurrence}.
+The models and subsets are as in Fig.\ \ref{fig:cloud-occurrence}.
 }
@@
 \caption{
-Virtual potential temperature ($\theta_v$) and relative humidity (RH) determined from radiosonde launches and co-located profiles in ICON, ERA5, and MERRA-2 in subsets as in Fig.
-\ref{fig:cloud-occurrence}.
+Virtual potential temperature (virt.\ pot.\ temp.; $\theta_v$) and relative humidity (RH) determined from radiosonde launches and co-located profiles in ICON, ERA5, and MERRA-2 in subsets as in Fig.\ \ref{fig:cloud-occurrence}.
 The solid lines are the average calculated from the averages of every individual voyage and station.
@@
 Apart from relative humidity, we focus on comparing virtual potential temperature ($\theta_v$) due to its role in low-level tropospheric stability, being one of the primary factors affecting shallow convection and the associated low-level cloud formation and dissipation.
-The observed and model profiles of virtual potential temperature are shown in Fig.
-\ref{fig:potential-temperature}.
+The observed and model profiles of virtual potential temperature are shown in Fig.\ \ref{fig:potential-temperature}.
 
-Overall, the mean $\theta_v$ is accurate to less than 0.5 K in ICON and MERRA-2, being only colder by up to 2 K in the mid-to-high troposphere (less stable) in ICON than in observations (Fig.
-\ref{fig:potential-temperature}a).
-Larger differences exist, however, in the 40--55°S zone, where ICON is colder by about 5 K at higher altitudes (Fig.
-\ref{fig:potential-temperature}b).
+Overall, the mean $\theta_v$ is accurate to less than 0.5 K in ICON and MERRA-2, except for ICON being colder by up to 2.5 K in the mid-to-high troposphere (less stable) (Fig.\ \ref{fig:potential-temperature}a).
+Larger differences exist, however, in the 40--55°S zone, where ICON is colder by about 5 K at higher altitudes (Fig.\ \ref{fig:potential-temperature}b).
 In other subsets, the bias is relatively small.
@@
 Relative humidity displays much larger biases.
-In all subsets, ICON is too humid in the first 1 km by about 5\% but very accurate above, except for the 40--55°S zone and conditions of weak stability (Fig.
-\ref{fig:potential-temperature}b, g), where it is too dry between about 1 and 3 km.
+In all subsets, ICON is too humid in the first 1 km by about 5\% but very accurate above, except for the 40--55°S zone and conditions of weak stability (Fig.\ \ref{fig:potential-temperature}b, g), where it is too dry between about 1 and 3 km.
 MERRA-2, on the other hand, is more humid than observations at all altitudes and in all subsets, by up to about 20\% at 5 km.
-Even though the mean near-surface relative humidity is similar to the observations (Fig.
-\ref{fig:potential-temperature}), the distribution in observation is more spread out across both high and low values, and thus observations have a greater prevalence of relative humidity close to 100\% and thus LCL located at the surface (Fig.
-\ref{fig:cloud-occurrence}a).
+Even though the mean near-surface relative humidity is similar to the observations (Fig.\ \ref{fig:potential-temperature}), the distribution in observation is more spread out across both high and low values, and thus observations have a greater prevalence of relative humidity close to 100\% and thus LCL located at the surface (Fig.\ \ref{fig:cloud-occurrence}a).
 In our calculations, LCL is an exclusive function of near-surface temperature, near-surface relative humidity, and surface pressure.

### 2024-12-12 manuscript_agu.tex
Addressing comments

@@
 
-The campaigns contained ceilometer observations captured by the Vaisala CL51 and CT25K, and the Lufft CHM 15k, described in detail below (Sections \ref{sec:cl51} and \ref{sec:chm15k}).
+The campaigns contained ceilometer observations captured by the Vaisala CL51 and CT25K, and the Lufft CHM 15k, described in detail below (Sections\ \ref{sec:cl51} and \ref{sec:chm15k}).
 A ceilometer is a low-power, near-infrared vertically pointing lidar principally designed to measure cloud base, but they also measure the full vertical structure of clouds as long as the laser signal is not attenuated by thick clouds, which can be used to infer additional information such as a cloud mask and cloud occurrence by height.
@@
 The wavelengths of 905 and 910 nm are affected by water vapor absorption of about 20\% in the mid-latitudes \cite{wiegner2015,wiegner2019}, with 910 nm affected more strongly, but we do not expect this to be a significant issue as explained in \citeA{kuma2021}.
-The instrument data files containing raw uncalibrated backscatter were first converted to Network Common Data Form (NetCDF) with cl2nc (\url{https://github.com/peterkuma/cl2nc}) and then processed with the ALCF (Section \ref{sec:alcf}) to produce absolutely calibrated attenuated volume backscattering coefficient (AVBC), cloud mask, cloud occurrence by height, and the total cloud fraction.
+The instrument data files containing raw uncalibrated backscatter were first converted to Network Common Data Form (NetCDF) with cl2nc (\url{https://github.com/peterkuma/cl2nc}) and then processed with the ALCF (Section\ \ref{sec:alcf}) to produce absolutely calibrated attenuated volume backscattering coefficient (AVBC), cloud mask, cloud occurrence by height, and the total cloud fraction.
 Because the CT25K uses a very similar wavelength to CL51, equivalent calculations as for CL51 were done assuming a wavelength of 910 nm.
@@
 The maximum range is 15.4 km; the vertical resolution is 5 m in the near range (up to 150 m) and 15 m above; the sampling (temporal) resolution is 2 s; and the number of vertical levels is 1024.
-NetCDF files containing uncalibrated backscatter produced by the instrument were processed with the ALCF (Section \ref{sec:alcf}) to again produce AVBC, cloud mask, cloud occurrence by height, and the total cloud fraction.
+NetCDF files containing uncalibrated backscatter produced by the instrument were processed with the ALCF (Section\ \ref{sec:alcf}) to again produce AVBC, cloud mask, cloud occurrence by height, and the total cloud fraction.
 The CHM 15k was used on four voyages (HMNZSW16, TAN1702, TAN1802, and NBP1704).
@@
 The geographical location was kept the same.
+We discuss briefly the implications of comparing the observations with a free-running model in Section\ \ref{sec:limitations}.
 
@@
 
-Radiation calculations presented in the results (Section \ref{sec:results}) were completed such that they always represent daily means in order to be consistent with the CERES SYN1deg data.
+Radiation calculations presented in the results (Section\ \ref{sec:results}) were completed such that they always represent daily means in order to be consistent with the CERES SYN1deg data.
 Therefore, every instantaneous profile in the simulated lidar data was assigned a daily mean radiation value corresponding to the day (in the Coordinated Universal Time; UTC).
@@
 
-Fig.\ \ref{fig:cyclone-stability}a, b show a geographical distribution of the fraction of cyclonic days as determined by the cyclone tracking algorithm applied to the ERA5 reanalysis and ICON data (Section \ref{sec:cyclone-stability}).
+Fig.\ \ref{fig:cyclone-stability}a, b show a geographical distribution of the fraction of cyclonic days as determined by the cyclone tracking algorithm applied to the ERA5 reanalysis and ICON data (Section\ \ref{sec:cyclone-stability}).
 As expected, the strongest cyclonic activity is in the high-latitude SO zone, and it is relatively zonally symmetric at all latitudes.
 The pattern matches reasonably well with \citeA{hoskins2005}.
-While both reanalysis and the model agree relatively well, there are clear differences, particularly in the highest occurrence rate regions -- over the Amundsen Sea, where the Amundsen Sea low is located \cite{turner2013}, and which is more cyclonic in the reanalysis, and around Cape Adare, which is more cyclonic in ICON.
+While both reanalysis and the model agree within about 8\% in most areas, ICON is prevailingly more cyclonic by about 4\%.
+There are clear differences particularly in the highest occurrence rate regions such as around Cape Adare, which is by up to 20\% more cyclonic in ICON, and Weddel and Bellingshausen Sea, where ICON is less cyclonic by up to 10\%.
 These differences might, however, stem from the relatively short time periods of comparison (4 years) and the fact that the model is free-running.
 
-Fig.\ \ref{fig:cyclone-stability}c, d show a geographical distribution of the conditions of weak and strong stability as determined by the LTS (Section \ref{sec:cyclone-stability}).
+Fig.\ \ref{fig:cyclone-stability}c, d show a geographical distribution of the conditions of weak and strong stability as determined by the LTS (Section\ \ref{sec:cyclone-stability}).
 Conditions of weak stability are prevalent in the mid-to-high SO (with respect to our SO partitioning; 50--65°S), which might be explained by the relatively cold near-surface air overlying the relatively warm sea surface.
@@
 
-When subsetted by conditions of weak and strong stability (Fig.\ \ref{fig:cloud-occurrence}f, g), as defined in Section \ref{sec:cyclone-stability}, we see that in situations of strong stability, cloud occurrence peaks strongly nearly at the surface in observations, compared to situations of weak stability, where the peak is more diffuse between 0 and 1 km.
+When subsetted by conditions of weak and strong stability (Fig.\ \ref{fig:cloud-occurrence}f, g), as defined in Section\ \ref{sec:cyclone-stability}, we see that in situations of strong stability, cloud occurrence peaks strongly nearly at the surface in observations, compared to situations of weak stability, where the peak is more diffuse between 0 and 1 km.
 It is worth mentioning that conditions of strong stability might be associated with the formation of advection fog, such as in situations of warm air advection from the north over colder sea surface thus inducing fog formation by cooling of the warm and humid air by the cold surface.
@@
 
-In Fig.\ \ref{fig:cloud-cover} we show the results for the same subsets of data as in Section \ref{sec:cloud-occurrence}.
+In Fig.\ \ref{fig:cloud-cover} we show the results for the same subsets of data as in Section\ \ref{sec:cloud-occurrence}.
 Observations display the highest proportion of high cloud cover values (5--8 oktas), peaking at 7 oktas.
@@
 Consequently, we also had four virtual/model profiles (one for each year of 2021--2024) for each observed profile.
-The profiles were partitioned into the same subsets as above (Sections \ref{sec:cloud-occurrence} and \ref{sec:cloud-cover}).
+The profiles were partitioned into the same subsets as above (Sections\ \ref{sec:cloud-occurrence} and \ref{sec:cloud-cover}).
 Apart from relative humidity, we focus on comparing virtual potential temperature ($\theta_v$) due to its role in low-level tropospheric stability, being one of the primary factors affecting shallow convection and the associated low-level cloud formation and dissipation.
@@
 \section{Limitations of this study}
+\label{sec:limitations}
 
@@
 For these reasons, one can expect the results to be slightly different due to reasons unrelated to model biases, such as different weather conditions, partially accounted for by the cyclone and stability subsetting, and the phase of climate oscillations such as the ENSO in the observations and the model.
+The interannual variability in cloud occurrence in ICON can be seen in Fig.\ \ref{fig:cloud-occurrence-panel}, where each year in ICON is represented by a separate line.
+The interannual variability tends to be substantially smaller than the biases, and thus is unlikely to have a stong impact on the main findings.
 
@@
 
-We have attempted to remove lidar profiles with precipitation, which could not be properly simulated with the lidar simulator (Section \ref{sec:ann}).
+We have attempted to remove lidar profiles with precipitation, which could not be properly simulated with the lidar simulator (Section\ \ref{sec:ann}).
 However, the approach was limited by the relatively low sensitivity of the ANN (65\%) and the fact that we had to choose a fixed threshold for surface precipitation flux in the model and reanalyses, which might not correspond to detection by the ANN applied to observations.

### 2024-12-12 manuscript_agu.tex
Addressing comments

@@
 \begin{abstract}
-Global storm-resolving models (GSRMs) are the next avenue of climate modeling.
-Among them is a 5-km version of the Icosahedral Nonhydrostatic Weather and Climate Model (ICON).
-The high resolution means that parameterizations of convection and clouds, including subgrid-scale clouds, are forgone, relying on explicit simulation, but still using microphysics and turbulence parametrization.
-Standard-resolution (10--100-km) models, which use subgrid-scale convection and cloud parametrization, have substantial cloud biases over the Southern Ocean (SO), affecting radiation and sea surface temperature.
-We evaluated SO clouds in ICON and the ERA5 and MERRA-2 reanalyses.
+Global storm-resolving models (GSRMs) are the upcoming global climate models.
+One of them is a 5-km Icosahedral Nonhydrostatic Weather and Climate Model (ICON).
+The high resolution means that parameterizations of convection and clouds, including subgrid-scale clouds, are omitted, relying on explicit simulation but still utilizing microphysics and turbulence parameterizations.
+Standard-resolution (10--100 km) models, which use convection and cloud parameterizations, have substantial cloud biases over the Southern Ocean (SO), affecting radiation and sea surface temperature.
 The SO is dominated by low clouds, which cannot be observed accurately from space due to overlapping clouds, attenuation, and ground clutter.
-Instead, we analyzed about 2400 days of lidar observations from 31 voyages and a station during 2010--2021 using a ground-based lidar simulator.
-ICON and the reanalyses underestimate the total cloud fraction by about 10 and 20\%, respectively.
+We evaluated SO clouds in ICON and the ERA5 and MERRA-2 reanalyses using about 2400 days of lidar observations and 2300 radiosonde profiles from 31 voyages and a station during 2010--2021, compared with the models using a ground-based lidar simulator.
+We found that ICON and the reanalyses underestimate the total cloud fraction by about 10 and 20\%, respectively.
 ICON and ERA5 overestimate the cloud occurrence peak at about 500 m, potentially explained by their lifting condensation levels being too high.
-The reanalyses strongly underestimate near-surface clouds or fog.
-MERRA-2 tends to underestimate cloud occurrence at all heights.
-In daily cloud cover, ICON and the reanalyses tend to be about 1 and 2 oktas clearer, respectively.
-Conditions of weak stability are associated with the largest errors in ICON and the reanalyses.
-Compared to radiosondes, potential temperature is accurate in the reanalyses to about 0.5 K, but ICON underestimates stability over the low-latitude SO and is too humid in the boundary layer.
-MERRA-2 is too humid at all heights.
-SO cloud biases remain a substantial issue in the GSRM but are an improvement over the lower-resolution reanalyses.
-Explicitly resolved convection and cloud processes (except microphysics) were not enough to address the model cloud biases.
+The reanalyses strongly underestimate fog or near-surface clouds and MERRA-2 underestimates cloud occurrence at almost all heights.
+Outgoing shortwave radiation is overestimated in the reanalyses, implying a ``too few, too bright'' cloud problem.
+Thermodynamic conditions are relatively well represented, but ICON is less stable than observations and MERRA-2 is too humid.
+SO cloud biases are a substantial issue in the GSRM, but it matches the observations better than the lower-resolution reanalyses.
 \end{abstract}
@@
 We evaluated clouds and thermodynamic profiles over the Southern Ocean in one such model, as well as two reanalyses, based on 2400 days of ship and station observations.
-Thanks to the high resolution, the model relies entirely on explicit simulation of clouds, instead of subgrid-scale parametrizations.
+Thanks to the high resolution, the model relies entirely on explicit simulation of clouds, instead of subgrid-scale parameterizations.
 For the evaluation, we used ceilometer and radiosonde observations and a lidar simulator, which enables a fair comparison with the model and reanalyses.
@@
 We hypothesize that this, in turn, can lead to systematic biases in low clouds in climate models, which are frequently evaluated against CloudSat--CALIPSO products.
-Reanalyses can also suffer from cloud biases, as these are usually parametrized in their atmospheric component and also in regions where input observations are sparse.
+Reanalyses can also suffer from cloud biases, as these are usually parameterized in their atmospheric component and also in regions where input observations are sparse.
 This makes them a problematic reference for clouds over the SO, and any biases relative to a reanalysis should be interpreted with caution.
@@
 
-\subsection{Voyage and station data}
+\subsection{Voyage and Station Data}
 
@@
 It uses version 5.12.4 of the Goddard Earth Observing System (GEOS) atmospheric model \cite{rienecker2008,molod2015}.
-Non-convective clouds (condensation, autoconversion, and evaporation) are parametrized using a prognostic scheme \cite{bacmeister2006}, and sub-grid cloud fraction is determined using total water distribution and a critical relative humidity threshold.
+Non-convective clouds (condensation, autoconversion, and evaporation) are parameterized using a prognostic scheme \cite{bacmeister2006}, and sub-grid cloud fraction is determined using total water distribution and a critical relative humidity threshold.
 The reanalysis output analyzed here is available at a spatial resolution of 0.5° of latitude and 0.625° of longitude, which is about 56 km in the North--South direction and 35 km in the East--West direction at 60°S.
@@
 
-\subsection{Precipitation identification using machine learning}
+\subsection{Precipitation Identification Using Machine Learning}
 \label{sec:ann}
@@
 
-\subsection{Partitioning by cyclonic activity and stability}
+\subsection{Partitioning by Cyclonic Activity and Stability}
 \label{sec:cyclone-stability}
@@
 
-\subsection{Cyclonic activity and stability}
+\subsection{Cyclonic Activity and Stability}
 
@@
 
-\subsection{Cloud occurrence by height}
+\subsection{Cloud Occurrence by Height}
 \label{sec:cloud-occurrence}
@@
 
-\subsection{Cloud cover}
+\subsection{Top of Atmosphere Radiation}
+
+In Fig.\ \ref{fig:cloud-occurrence}, we also show outgoing shortwave and longwave top of atmosphere radiation.
+In observations, these come from daily mean CERES measurements averaged over the voyage tracks or a station location, whereas in the models they come from daily means of TOA radiation in the model output averaged over the same location and time periods.
+In the free-running ICON model, the time period is mapped onto the available years, as explained in Section\ \ref{sec:icon}.
+
+In the general case (Fig.\ \ref{fig:cloud-occurrence}a), ICON underestimates the outgoing SW radiation by 26 Wm$^{-2}$ and the reanalyses MERRA-2 and ERA5 are much closer, but overestimate it by 6 and 14 Wm$^{-2}$, respectively.
+While in ICON, this is in line with the underestimated total cloud fraction by 10\%, in the reanalyses this is the opposite result as expected from the underestimated total cloud fraction by about 20\%.
+The likely explanation is an overestimated cloud albedo, compensating for the lack of cloud area.
+
+In contrast, LW radiation if affected by much smaller biases than SW radiation, which is expected due to the prevailing low-level clouds having similar temperature as the surface.
+In ICON, the outgoing LW radiation is overestimates by 8\%, which could be caused by understimated total cloud fraction exposing a larger area sea surface are to cooling to space, which is typically warmer than the atmospheric temperature at 0--2 km, where most of the clouds are located.
+In the MERRA-2 and ERA5 reanalyses, the LW biases are also slighly positive by 4 and 7 Wm$^{-2}$.
+This is again in line with the underestimated total cloud fraction by about 20\%.
+However, if the clouds are too thick, as expected from the SW results, this might also provide a compensating effect where too small cloud area is counteracted by greater thermal emissivity, thus reducing the ougoing LW radiation more relative to thinner clouds.
+For thin clouds, the outgoing TOA LW radiation originates both from the warmer surface (partly blocked by the clouds) and the clouds, whereas for thick clouds, the outgoing TOA LW radiation originates mostly from the colder-than-surface clouds.
+
+In all of the subsets (Fig.\ \ref{fig:cloud-occurrence}b--g), the same type of bias is present as in the general case -- the outgoing SW radiation is underestimated in ICON and overestimated in MERRA-2 and ERA5, and the outgoing LW radiation is overestimated in all of the models.
+Even though the total cloud fraction is lower by 7\% over the high-latitude SO than the low-latitude SO, the outgoing SW radiation is much greater by 41 Wm$^{-2}$, implying a much greater cloud albedo over the high-latitude SO.
+ICON has the same contrast between these two regions in the total cloud fraction and SW radiation, but the outgoing SW radiation difference between the regions is much smaller (16 Wm$^{-2}$).
+The reanalyses do not show this type of contrast between the regions.
+The physical reason for this might be that the prevalence of fog or low-level clouds over the low-latitude SO and their relative lack over the high-latitude SO in obserations is not reproduced in the models (Fig.\ \ref{fig:cloud-occurrence}b--c).
+
+\subsection{Cloud Cover}
 \label{sec:cloud-cover}
@@
 
-\subsection{Thermodynamic profiles}
+\subsection{Thermodynamic Profiles}
 
@@
 
-\section{Limitations of this study}
+\section{Limitations of this Study}
 \label{sec:limitations}
@@
 
-\section{Discussion and conclusions}
+\section{Discussion and Conclusions}
 
@@
 This warrants further investigation, especially of ocean--atmosphere fluxes, shallow convection, and boundary layer turbulence.
-The lack of parametrized subgrid-scale convection in ICON could be a substantial issue even at the 5-km resolution.
+The lack of parameterized subgrid-scale convection in ICON could be a substantial issue even at the 5-km resolution.
 
@@
 More effort is needed to improve the model cloud simulations in this understudied region.
-However, this analysis suggests that the transition from models with parametrized convection and clouds to storm-resolving models might not solve these biases without additional effort.
+However, this analysis suggests that the transition from models with parameterized convection and clouds to storm-resolving models might not solve these biases without additional effort.
 Evaluation of ocean--atmosphere heat, moisture, and momentum fluxes against in-situ observations over the SO and comparison of GSRM simulations against large-eddy simulations are two potential avenues for future research that could elucidate the physical mechanisms behind the biases, in addition to the more common efforts in SO cloud microphysics and precipitation evaluation.

### 2024-12-12 manuscript_agu.tex
Grammar corrections

@@
 ICON and ERA5 overestimate the cloud occurrence peak at about 500 m, potentially explained by their lifting condensation levels being too high.
-The reanalyses strongly underestimate fog or near-surface clouds and MERRA-2 underestimates cloud occurrence at almost all heights.
+The reanalyses strongly underestimate fog or near-surface clouds, and MERRA-2 underestimates cloud occurrence at almost all heights.
 Outgoing shortwave radiation is overestimated in the reanalyses, implying a ``too few, too bright'' cloud problem.
@@
 It is, however, often not as easy as changing the grid size because of the complex interplay between model dynamics and physics, which necessitates adjusting and tuning all components together.
-Increasing resolution, is of course, limited by the available computational power and a trade-off with increasing parameterization complexity, which is another way of improving model accuracy.
+Increasing resolution is, of course, limited by the available computational power and a trade-off with increasing parameterization complexity, which is another way of improving model accuracy.
 Current computational availability and acceleration from general-purpose computing on graphics processing units (GPUs) is progressing to enable km-scale (also called k-scale) Earth system models (ESMs) and coupled atmosphere--ocean general circulation models (AOGCMs) in research conditions today and operationally in the forthcoming years.
@@
 Compensating cloud biases in the Australian Community Climate and Earth System Simulator (ACCESS) – Atmosphere-only model version 2 (AM2) over the SO were analyzed by \citeA{fiddes2022} and \citeA{fiddes2024}.
-\citeA{possner2022} showed that over the SO, the DYAMOND GSRM ICON underestimates low-level cloud fraction on the order of 30\% and overestimates net dowward TOA SW radiation by approximately 10 Wm$^\mathrm{-2}$ in the highest model resolution run (2.5 km).
+\citeA{possner2022} showed that over the SO, the DYAMOND GSRM ICON underestimates low-level cloud fraction on the order of 30\% and overestimates net downward TOA SW radiation by approximately 10 Wm$^\mathrm{-2}$ in the highest model resolution run (2.5 km).
 \citeA{zhao2022} reported a similar SW radiation bias in five analyzed CMIP6 models over high-latitude SO and the total cloud fraction underestimation on the order of 10\% over the entire 40--60°S SO.
@@
 The campaigns contained ceilometer observations captured by the Vaisala CL51 and CT25K, and the Lufft CHM 15k, described in detail below (Sections\ \ref{sec:cl51} and \ref{sec:chm15k}).
-A ceilometer is a low-power, near-infrared vertically pointing lidar principally designed to measure cloud base, but they also measure the full vertical structure of clouds as long as the laser signal is not attenuated by thick clouds, which can be used to infer additional information such as a cloud mask and cloud occurrence by height.
+A ceilometer is a low-power, near-infrared, vertically pointing lidar principally designed to measure cloud base, but they also measure the full vertical structure of clouds as long as the laser signal is not attenuated by thick clouds, which can be used to infer additional information such as a cloud mask and cloud occurrence by height.
 We note that during the MICRE campaign, the ceilometers Vaisala CT25K and CL51 were installed at the Macquarie Island station concurrently, but in our analysis we only used the CT25K data obtained from the Atmospheric Radiation Measurement (ARM) data archive.
@@
 TOA radiation quantities are taken from the CERES instruments onboard the Terra and Aqua satellites \cite{wielicki1996,loeb2018}.
-In our analysis we used the adjusted all-sky SW and LW upwelling fluxes at TOA from the synoptic TOA and surface fluxes and clouds 1-degree daily edition 4A product (CER\_SYN1deg-Day\_Terra-Aqua-MODIS\_Edition4A) \cite{doelling2013,doelling2016}.
+In our analysis, we used the adjusted all-sky SW and LW upwelling fluxes at TOA from the synoptic TOA and surface fluxes and clouds 1-degree daily edition 4A product (CER\_SYN1deg-Day\_Terra-Aqua-MODIS\_Edition4A) \cite{doelling2013,doelling2016}.
 
@@
 \textbf{(a)} Diagram showing the TensorFlow structure of the ANN, \textbf{(b)} randomly selected example samples of near-surface backscatter in four categories (clear, fog, rain, and snow), as determined by coincident human-performed weather observations, \textbf{(c)} receiver operating characteristic diagram of the ANN, \textbf{(d)} examples of 10-day time series of human-observed (``HUM'') and predicted precipitation based on an ANN trained on all voyages (``ANN'') and all voyages except for the shown voyage (``ANN2'') during three randomly selected voyages with the available data.
-Here, by ``randomly selected'', we mean selected from the top of a permutation generated by a pseudo-random number generator to prevent authors' bias in the selection.
+Here, by ``randomly selected,'' we mean selected from the top of a permutation generated by a pseudo-random number generator to prevent authors' bias in the selection.
 }
@@
 The required radiation calculations for precipitation are also currently not implemented in the ALCF, even though this is a planned future addition.
-In order to achieve a fair comparison of observations with model output, we exclude observed and simulated lidar profiles with precipitation either manually or using an automated method.
+In order to achieve a fair comparison of observations with model output, we exclude observed and simulated lidar profiles with precipitation, either manually or using an automated method.
 It is relatively difficult to distinguish precipitation backscatter from cloud backscatter in lidar observations, especially when only one wavelength channel and no polarized channel are available.
@@
 While both reanalysis and the model agree within about 8\% in most areas, ICON is prevailingly more cyclonic by about 4\%.
-There are clear differences particularly in the highest occurrence rate regions such as around Cape Adare, which is by up to 20\% more cyclonic in ICON, and Weddel and Bellingshausen Sea, where ICON is less cyclonic by up to 10\%.
+There are clear differences, particularly in the highest occurrence rate regions, such as around Cape Adare, which is by up to 20\% more cyclonic in ICON, and the Weddell and Bellingshausen Seas, where ICON is less cyclonic by up to 10\%.
 These differences might, however, stem from the relatively short time periods of comparison (4 years) and the fact that the model is free-running.
@@
 The distribution is also less zonally symmetric than the cyclonic activity.
-In the high-latitude SO, the presence of sea ice might have a substantial stabilising effect \cite{knight2024}.
+In the high-latitude SO, the presence of sea ice might have a substantial stabilizing effect \cite{knight2024}.
 The ERA5 reanalysis is also substantially more stable than ICON across the whole region.
@@
 When subsetted by conditions of weak and strong stability (Fig.\ \ref{fig:cloud-occurrence}f, g), as defined in Section\ \ref{sec:cyclone-stability}, we see that in situations of strong stability, cloud occurrence peaks strongly nearly at the surface in observations, compared to situations of weak stability, where the peak is more diffuse between 0 and 1 km.
-It is worth mentioning that conditions of strong stability might be associated with the formation of advection fog, such as in situations of warm air advection from the north over colder sea surface thus inducing fog formation by cooling of the warm and humid air by the cold surface.
+It is worth mentioning that conditions of strong stability might be associated with the formation of advection fog, such as in situations of warm air advection from the north over a colder sea surface, thus inducing fog formation by cooling of the warm and humid air by the cold surface.
 In situations of strong stability, the models have smaller biases than in weak stability, with an overestimated peak by up to 12\%, underestimated cloud occurrence above 1 km by up to 5\%, and underestimated cloud occurrence near the surface by about 11\%.
@@
 The total cloud fraction (CF), average shortwave (SW), and longwave (LW) and the relative frequency of occurrence (RFO) are shown.
-The bands are the 16$^\mathrm{th}$--84$^\mathrm{th}$ percentile calculated from the set of all voyages and stations.
+The bands are the 16$^\mathrm{th}$--84$^\mathrm{th}$ percentile, calculated from the set of all voyages and stations.
 }
@@
 
-In the general case (Fig.\ \ref{fig:cloud-occurrence}a), ICON underestimates the outgoing SW radiation by 26 Wm$^{-2}$ and the reanalyses MERRA-2 and ERA5 are much closer, but overestimate it by 6 and 14 Wm$^{-2}$, respectively.
+In the general case (Fig.\ \ref{fig:cloud-occurrence}a), ICON underestimates the outgoing SW radiation by 26 Wm$^{-2}$ and the reanalyses MERRA-2 and ERA5 are much closer but overestimate it by 6 and 14 Wm$^{-2}$, respectively.
 While in ICON, this is in line with the underestimated total cloud fraction by 10\%, in the reanalyses this is the opposite result as expected from the underestimated total cloud fraction by about 20\%.
@@
 
-In contrast, LW radiation if affected by much smaller biases than SW radiation, which is expected due to the prevailing low-level clouds having similar temperature as the surface.
-In ICON, the outgoing LW radiation is overestimates by 8\%, which could be caused by understimated total cloud fraction exposing a larger area sea surface are to cooling to space, which is typically warmer than the atmospheric temperature at 0--2 km, where most of the clouds are located.
-In the MERRA-2 and ERA5 reanalyses, the LW biases are also slighly positive by 4 and 7 Wm$^{-2}$.
+In contrast, LW radiation is affected by much smaller biases than SW radiation, which is expected due to the prevailing low-level clouds having similar temperature as the surface.
+In ICON, the outgoing LW radiation is overestimated by 8\%, which could be caused by an underestimated total cloud fraction exposing a larger sea surface area to cooling to space, which is typically warmer than the atmospheric temperature at 0--2 km, where most of the clouds are located.
+In the MERRA-2 and ERA5 reanalyses, the LW biases are also slightly positive by 4 and 7 Wm$^{-2}$.
 This is again in line with the underestimated total cloud fraction by about 20\%.
-However, if the clouds are too thick, as expected from the SW results, this might also provide a compensating effect where too small cloud area is counteracted by greater thermal emissivity, thus reducing the ougoing LW radiation more relative to thinner clouds.
+However, if the clouds are too thick, as expected from the SW results, this might also provide a compensating effect, in which too small a cloud area is counteracted by greater thermal emissivity, thus reducing the outgoing LW radiation more relative to thinner clouds.
 For thin clouds, the outgoing TOA LW radiation originates both from the warmer surface (partly blocked by the clouds) and the clouds, whereas for thick clouds, the outgoing TOA LW radiation originates mostly from the colder-than-surface clouds.
 
-In all of the subsets (Fig.\ \ref{fig:cloud-occurrence}b--g), the same type of bias is present as in the general case -- the outgoing SW radiation is underestimated in ICON and overestimated in MERRA-2 and ERA5, and the outgoing LW radiation is overestimated in all of the models.
+In all the subsets (Fig.\ \ref{fig:cloud-occurrence}b--g), the same type of bias is present as in the general case -- the outgoing SW radiation is underestimated in ICON and overestimated in MERRA-2 and ERA5, and the outgoing LW radiation is overestimated in all the models.
 Even though the total cloud fraction is lower by 7\% over the high-latitude SO than the low-latitude SO, the outgoing SW radiation is much greater by 41 Wm$^{-2}$, implying a much greater cloud albedo over the high-latitude SO.
@@
 The reanalyses do not show this type of contrast between the regions.
-The physical reason for this might be that the prevalence of fog or low-level clouds over the low-latitude SO and their relative lack over the high-latitude SO in obserations is not reproduced in the models (Fig.\ \ref{fig:cloud-occurrence}b--c).
+The physical reason for this might be that the prevalence of fog or low-level clouds over the low-latitude SO and their relative lack over the high-latitude SO in observations is not reproduced in the models (Fig.\ \ref{fig:cloud-occurrence}b--c).
 
@@
 When all profiles in a day are taken together, the cloud cover for the day is defined as the fraction of cloudy profiles in the total number of profiles, expressed in oktas (multiples of 1/8).
-The same calculation is done the lidar observations as for the simulated lidar profiles.
+The same calculation is done for the lidar observations as for the simulated lidar profiles.
 We use the term ``okta'' independently of its use in instantaneous synoptic observations, and here it simply means 1/8 (0.125\%) of the daily cloud cover.
@@
 The solid lines are the average calculated from the averages of every individual voyage and station.
-The bands span the 16$^\mathrm{th}$--84$^\mathrm{th}$ percentiles calculated from the distribution of the voyage and station averages.
+The bands span the 16$^\mathrm{th}$--84$^\mathrm{th}$ percentiles, calculated from the distribution of the voyage and station averages.
 Shown is also the relative frequency of occurrence and the number of profiles in each subset.
@@
 The interannual variability in cloud occurrence in ICON can be seen in Fig.\ \ref{fig:cloud-occurrence-panel}, where each year in ICON is represented by a separate line.
-The interannual variability tends to be substantially smaller than the biases, and thus is unlikely to have a stong impact on the main findings.
+The interannual variability tends to be substantially smaller than the biases, and thus is unlikely to have a strong impact on the main findings.
 
@@
 
-PK and FB, and the nextGEMS project received funding from the European Union’s Horizon 2020 research and innovation program under a grant agreement no.
+PK, FB, and the nextGEMS project received funding from the European Union’s Horizon 2020 research and innovation program under a grant agreement no.
 101003470.

### 2024-12-12 manuscript_agu.tex
Indivisible space

@@
 \item Ground-based lidar evaluation of a km-scale global climate model and reanalyses reveals substantial cloud biases over the Southern Ocean.
-\item Fog or low cloud is underestimated in the reanalyses. In all models, a cloud peak at 500 m tends to be overestimated and too high.
+\item Fog or low cloud is underestimated in the reanalyses. In all models, a cloud peak at 500\ m tends to be overestimated and too high.
 \item A ``too few, too bright'' problem of underestimated cloud fraction, compensated by overestimated cloud albedo, is present in the reanalyses.
@@
 The high resolution means that parameterizations of convection and clouds, including subgrid-scale clouds, are omitted, relying on explicit simulation but still utilizing microphysics and turbulence parameterizations.
-Standard-resolution (10--100 km) models, which use convection and cloud parameterizations, have substantial cloud biases over the Southern Ocean (SO), affecting radiation and sea surface temperature.
+Standard-resolution (10--100\ km) models, which use convection and cloud parameterizations, have substantial cloud biases over the Southern Ocean (SO), affecting radiation and sea surface temperature.
 The SO is dominated by low clouds, which cannot be observed accurately from space due to overlapping clouds, attenuation, and ground clutter.
@@
 Therefore, it represents a natural advance in climate modeling.
-Global storm-resolving models (GSRMs) are emerging as a new front in the development of high-resolution global climate models, with horizontal grid resolutions of about 2--8 km \cite{satoh2019,stevens2019}.
+Global storm-resolving models (GSRMs) are emerging as a new front in the development of high-resolution global climate models, with horizontal grid resolutions of about 2--8\ km \cite{satoh2019,stevens2019}.
 This is enough to resolve mesoscale convective storms, but smaller-scale convective plumes and cloud structure remain unresolved.
@@
 The terms global cloud-resolving models or global convection-permitting/-resolving models are also sometimes used interchangeably with GSRMs but imply that clouds or convection are resolved explicitly, which is not entirely true for GSRMs, as this would require an even higher horizontal resolution \cite{satoh2019}.
-Representative of these efforts is the DYnamics of the Atmospheric general circulation Modeled On Non-hydrostatic Domains (DYAMOND) project \cite{stevens2019,dyamond}, which is an intercomparison of nine global GSRMs over two 40-day time periods in summer (1 August -- 10 September 2016) and winter (20 January -- 1 March 2020).
+Representative of these efforts is the DYnamics of the Atmospheric general circulation Modeled On Non-hydrostatic Domains (DYAMOND) project \cite{stevens2019,dyamond}, which is an intercomparison of nine global GSRMs over two 40-day time periods in summer (1\ August--10\ September 2016) and winter (20\ January--1\ March 2020).
 A new one-year GSRM intercomparison is currently proposed by \citeA{takasuka2024}, with the hope of also evaluating the seasonal cycle and large-scale circulation.
@@
 Second-order effects on SW and LW radiation are associated with the cloud droplet size distribution, ice crystal habit, cloud lifetime, and direct radiative interaction with aerosols.
-In the 6$^\mathrm{th}$ phase of the Coupled Model Intercomparison Project [CMIP6; \citeA{eyring2016}], the cloud feedback has increased relative to CMIP5 \cite{zelinka2020}, which is one of the main reasons for the higher climate sensitivity of CMIP6 models.
+In the 6$^\mathrm{th}$\ phase of the Coupled Model Intercomparison Project [CMIP6; \citeA{eyring2016}], the cloud feedback has increased relative to CMIP5 \cite{zelinka2020}, which is one of the main reasons for the higher climate sensitivity of CMIP6 models.
 
@@
 Compensating cloud biases in the Australian Community Climate and Earth System Simulator (ACCESS) – Atmosphere-only model version 2 (AM2) over the SO were analyzed by \citeA{fiddes2022} and \citeA{fiddes2024}.
-\citeA{possner2022} showed that over the SO, the DYAMOND GSRM ICON underestimates low-level cloud fraction on the order of 30\% and overestimates net downward TOA SW radiation by approximately 10 Wm$^\mathrm{-2}$ in the highest model resolution run (2.5 km).
+\citeA{possner2022} showed that over the SO, the DYAMOND GSRM ICON underestimates low-level cloud fraction on the order of 30\% and overestimates net downward TOA SW radiation by approximately 10 Wm$^\mathrm{-2}$ in the highest model resolution run (2.5\ km).
 \citeA{zhao2022} reported a similar SW radiation bias in five analyzed CMIP6 models over high-latitude SO and the total cloud fraction underestimation on the order of 10\% over the entire 40--60°S SO.
-Recently, \citeA{ramadoss2024} analyzed 48 hours of km-scale ICON limited-area model NWP simulations over a SO region adjacent to Tasmania against the Clouds, Aerosols, Precipitation, Radiation, and atmospherIc Composition Over the southeRn oceaN (CAPRICORN) voyage cloud and precipitation observations \cite{mcfarquhar2021}.
+Recently, \citeA{ramadoss2024} analyzed 48\ hours of km-scale ICON limited-area model NWP simulations over a SO region adjacent to Tasmania against the Clouds, Aerosols, Precipitation, Radiation, and atmospherIc Composition Over the southeRn oceaN (CAPRICORN) voyage cloud and precipitation observations \cite{mcfarquhar2021}.
 They found the ICON cloud optical thickness was underestimated relative to Himawari‐8 satellite observations but also identified large differences in cloud top phase.
@@
 To achieve a like-for-like comparison with the model, we used a ground-based lidar simulator called the Automatic Lidar and Ceilometer Framework [ALCF; \citeA{kuma2021}].
-We contrasted the results with ERA5 \cite{era5} and the Modern-Era Retrospective analysis for Research and Applications, Version 2 [MERRA-2; \citeA{gelaro2017}].
+We contrasted the results with ERA5 \cite{era5} and the Modern-Era Retrospective analysis for Research and Applications, Version\ 2 [MERRA-2; \citeA{gelaro2017}].
 
@@
 \caption{
-\textbf{(a)} A map showing the tracks of 31 voyages of RV \emph{Polarstern}, RSV \emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B.
+\textbf{(a)} A map showing the tracks of 31\ voyages of RV \emph{Polarstern}, RSV \emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B.
 Palmer}, and HMNZS \emph{Wellington} and one sub-Antarctic station (Macquarie Island) analyzed here.
@@
 The dotted and dashed lines at 40°S and 55°S delineate the Southern Ocean area of our analysis and its partitioning into two subsets, respectively.
-A photo of \textbf{(b)} RV \emph{Polarstern} (© Folke Mehrtens, Alfred-Wegener-Institut), \textbf{(c)} Lufft CHM 15k installed on RV \emph{Tangaroa} (© Peter Kuma, University of Canterbury), \textbf{(d)} Vaisala CL51 (© Jeff Aquilina, Bureau of Meteorology), \textbf{(e)} Vaisala CT25K at Macquarie Island (© Simon P.\ Alexander, Australian Antarctic Division).
+A photo of \textbf{(b)} RV \emph{Polarstern} (© Folke Mehrtens, Alfred-Wegener-Institut), \textbf{(c)} Lufft CHM\ 15k installed on RV \emph{Tangaroa} (© Peter Kuma, University of Canterbury), \textbf{(d)} Vaisala CL51 (© Jeff Aquilina, Bureau of Meteorology), \textbf{(e)} Vaisala CT25K at Macquarie Island (© Simon P.\ Alexander, Australian Antarctic Division).
 }
@@
 
-Together, we analyzed data from 31 voyages of RV \emph{Polarstern}, the resupply vessel (RSV) \emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B.
+Together, we analyzed data from 31\ voyages of RV \emph{Polarstern}, the resupply vessel (RSV) \emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B.
 Palmer}, Her (now His) Majesty's New Zealand Ship (HMNZS) \emph{Wellington} and one sub-Antarctic station (Macquarie Island) in the SO south of 40°S between 2010 and 2021.
 Fig.\ \ref{fig:map} shows a map of the campaigns, Table \ref{tab:voyages} lists the campaigns, and Table \ref{tab:voyage-references} lists references where available.
-Altogether, the analyzed dataset comprised 2421 days of data south of 40°S, but the availability of ceilometer data was slightly shorter due to gaps in measurements.
+Altogether, the analyzed dataset comprised 2421\ days of data south of 40°S, but the availability of ceilometer data was slightly shorter due to gaps in measurements.
 
-The campaigns contained ceilometer observations captured by the Vaisala CL51 and CT25K, and the Lufft CHM 15k, described in detail below (Sections\ \ref{sec:cl51} and \ref{sec:chm15k}).
+The campaigns contained ceilometer observations captured by the Vaisala CL51 and CT25K, and the Lufft CHM\ 15k, described in detail below (Sections\ \ref{sec:cl51} and \ref{sec:chm15k}).
 A ceilometer is a low-power, near-infrared, vertically pointing lidar principally designed to measure cloud base, but they also measure the full vertical structure of clouds as long as the laser signal is not attenuated by thick clouds, which can be used to infer additional information such as a cloud mask and cloud occurrence by height.
@@
 CL51/31 indicates CL51 configured to emulate CL31.
-Missing days in the ceilometer data were HMNZSW16 (7 days): 24--27 November, 10 December, 16--17 December 2016; MARCUS (3 days): 8, 10 November, 10 December 2017; MICRE (9 days): 7--8, 29 June, 5, 16 July, 15 August, 17 October 2016, 11 February, 21 March 2017; TAN1502 (1 day): 24 January.
+Missing days in the ceilometer data were HMNZSW16 (7 days): 24--27 November, 10\ December, 16--17\ December 2016; MARCUS (3 days): 8, 10\ November, 10\ December 2017; MICRE (9\ days): 7--8, 29\ June, 5, 16\ July, 15\ August, 17\ October 2016, 11\ February, 21\ March 2017; TAN1502 (1\ day): 24\ January.
 }
@@
 
-The Vaisala CL51 and CT25K (photos in Fig.\ \ref{fig:map}d, e) are ceilometers operating at near-infrared wavelengths of 910 nm and 905 nm, respectively.
+The Vaisala CL51 and CT25K (photos in Fig.\ \ref{fig:map}d, e) are ceilometers operating at near-infrared wavelengths of 910\ nm and 905\ nm, respectively.
 The CL51 can also be configured to emulate the Vaisala CL31.
-The maximum range is 15.4 km (CL51), 7.7 km (CL31 emulation mode with 5 m vertical resolution), and 7.5 km (CT25K).
-The vertical resolution is 10 m (5 m configurable) in CL51 and 30 m in CT25K observations.
-The sampling (temporal) resolution is configurable, and in our datasets, it is approximately 6 s for CL51 on AA15‐16, 16 s for CT25K on MARCUS and MICRE, 36 s for CL51 on RV \emph{Polarstern}, and about 2.37 s for CL51 with CL31 emulation on TAN1502.
-The wavelengths of 905 and 910 nm are affected by water vapor absorption of about 20\% in the mid-latitudes \cite{wiegner2015,wiegner2019}, with 910 nm affected more strongly, but we do not expect this to be a significant issue as explained in \citeA{kuma2021}.
+The maximum range is 15.4\ km (CL51), 7.7\ km (CL31 emulation mode with 5\ m vertical resolution), and 7.5\ km (CT25K).
+The vertical resolution is 10\ m (5\ m configurable) in CL51 and 30\ m in CT25K observations.
+The sampling (temporal) resolution is configurable, and in our datasets, it is approximately 6\ s for CL51 on AA15‐16, 16\ s for CT25K on MARCUS and MICRE, 36\ s for CL51 on RV \emph{Polarstern}, and about 2.37\ s for CL51 with CL31 emulation on TAN1502.
+The wavelengths of 905 and 910\ nm are affected by water vapor absorption of about 20\% in the mid-latitudes \cite{wiegner2015,wiegner2019}, with 910\ nm affected more strongly, but we do not expect this to be a significant issue as explained in \citeA{kuma2021}.
 The instrument data files containing raw uncalibrated backscatter were first converted to Network Common Data Form (NetCDF) with cl2nc (\url{https://github.com/peterkuma/cl2nc}) and then processed with the ALCF (Section\ \ref{sec:alcf}) to produce absolutely calibrated attenuated volume backscattering coefficient (AVBC), cloud mask, cloud occurrence by height, and the total cloud fraction.
-Because the CT25K uses a very similar wavelength to CL51, equivalent calculations as for CL51 were done assuming a wavelength of 910 nm.
+Because the CT25K uses a very similar wavelength to CL51, equivalent calculations as for CL51 were done assuming a wavelength of 910\ nm.
 The Vaisala CL51 and CT25K instruments were used on most of the voyages and stations analyzed here.
@@
 \caption{
-An example of the attenuated volume backscattering coefficient (AVBC) \textbf{(a)} measured by CL51 during 24 hours on the PS81/3 voyage and \textbf{(b)} an equivalent AVBC simulated with the ALCF from ERA5 data during the same time period.
+An example of the attenuated volume backscattering coefficient (AVBC) \textbf{(a)} measured by CL51 during 24\ hours on the PS81/3 voyage and \textbf{(b)} an equivalent AVBC simulated with the ALCF from ERA5 data during the same time period.
 The red line identifies the cloud mask determined by the ALCF.
@@
 
-\subsection{Lufft CHM 15k}
+\subsection{Lufft CHM\ 15k}
 \label{sec:chm15k}
 
-The Lufft CHM 15k (photo in Fig.\ \ref{fig:map}c) is a ceilometer operating at a near-infrared wavelength of 1064 nm.
-The maximum range is 15.4 km; the vertical resolution is 5 m in the near range (up to 150 m) and 15 m above; the sampling (temporal) resolution is 2 s; and the number of vertical levels is 1024.
+The Lufft CHM\ 15k (photo in Fig.\ \ref{fig:map}c) is a ceilometer operating at a near-infrared wavelength of 1064\ nm.
+The maximum range is 15.4\ km; the vertical resolution is 5\ m in the near range (up to 150\ m) and 15\ m above; the sampling (temporal) resolution is 2\ s; and the number of vertical levels is 1024.
 NetCDF files containing uncalibrated backscatter produced by the instrument were processed with the ALCF (Section\ \ref{sec:alcf}) to again produce AVBC, cloud mask, cloud occurrence by height, and the total cloud fraction.
-The CHM 15k was used on four voyages (HMNZSW16, TAN1702, TAN1802, and NBP1704).
+The CHM\ 15k was used on four voyages (HMNZSW16, TAN1702, TAN1802, and NBP1704).
 
@@
 Absolute calibration of the observed backscatter was performed by comparing the measured clear-sky molecular backscatter statistically with simulated clear-sky molecular backscatter.
-AVBC was resampled to 5 min temporal resolution and 50 m vertical resolution to increase the signal-to-noise ratio while having enough resolution to detect small-scale cloud variability.
+AVBC was resampled to 5 min temporal resolution and 50\ m vertical resolution to increase the signal-to-noise ratio while having enough resolution to detect small-scale cloud variability.
 The noise standard deviation was calculated from AVBC at the highest range, where no clouds are expected.
@@
 To account for the radiative effects of subgrid-scale clouds, a cloud inhomogeneity factor is introduced in the model, which scales down the cloud liquid water for radiative calculations.
-It ranges from 0.4 at lower tropospheric stability (LTS) of 0 K to 0.8 at 30 K.
+It ranges from 0.4 at lower tropospheric stability (LTS) of 0\ K to 0.8 at 30\ K.
 In addition, vertical mixing is enhanced in unstable and humid lower-tropospheric conditions, which reduces the amount of shallow clouds.
@@
 It uses the \citeA{tiedtke1993} prognostic cloud scheme and \citeA{forbes2014} for mixed-phase clouds.
-The horizontal resolution is 0.25° in latitude and longitude, which is about 28 km in the North--South direction and 14 km in the East--West direction at 60°S.
+The horizontal resolution is 0.25° in latitude and longitude, which is about 28\ km in the North--South direction and 14\ km in the East--West direction at 60°S.
 Internally, the model uses 137 vertical levels.
@@
 We used this dataset to train a convolutional artificial neural network (ANN) to recognize profiles with precipitation from lidar backscatter (Fig.\ \ref{fig:ann}a), implemented in the TensorFlow ANN framework \cite{tensorflow}.
-Samples of short time intervals (10 min) of near-surface lidar backscatter (0–250 m) were classified as clear, rain, snow, and fog, using the synoptic observations as a training dataset (Fig.\ \ref{fig:ann}b).
+Samples of short time intervals (10\ min) of near-surface lidar backscatter (0–250 m) were classified as clear, rain, snow, and fog, using the synoptic observations as a training dataset (Fig.\ \ref{fig:ann}b).
 From these, a binary, mutually exclusive classification of profiles as precipitating (rain or snow) or dry (clear or fog) was derived.
@@
 
-In addition to the above, we partitioned our data into two mutually exclusive subsets based on LTS, which is derived as the difference between the potential temperature at 700 hPa and the surface.
-Based on a histogram of LTS in ERA5 and MERRA-2 calculated at all voyage tracks and stations (Fig.\ \ref{fig:lts}), we determined a statistically-based dividing threshold of 12 K for weak stability ($<$ 12 K) and strong stability ($\geq$ 12 K) conditions.
+In addition to the above, we partitioned our data into two mutually exclusive subsets based on LTS, which is derived as the difference between the potential temperature at 700\ hPa and the surface.
+Based on a histogram of LTS in ERA5 and MERRA-2 calculated at all voyage tracks and stations (Fig.\ \ref{fig:lts}), we determined a statistically-based dividing threshold of 12\ K for weak stability ($<$\ 12\ K) and strong stability ($\geq$\ 12\ K) conditions.
 
@@
 \caption{
-Geographical distribution of \textbf{(a, b)} cyclonic days and \textbf{(b, d)} strong stability (LTS $\geq$ 12 K) time steps in \textbf{(a, c)} ERA5 in years 2010--2013 (inclusive) and \textbf{(b, d)} ICON in model years 2021--2023 (free running).
+Geographical distribution of \textbf{(a, b)} cyclonic days and \textbf{(b, d)} strong stability (LTS\ $\geq$\ 12\ K) time steps in \textbf{(a, c)} ERA5 in years 2010--2013 (inclusive) and \textbf{(b, d)} ICON in model years 2021--2023 (free running).
 Cyclonic days are expressed as a fraction of the number of days with cyclonic activity, defined as grid points located within a double radius of any cyclone on a given day (UTC), as identified by CyTRACK.
@@
 
-For all observations considered (Fig.\ \ref{fig:cloud-occurrence}a), the data show cloud occurrence peaking nearly at the surface, whereas the models show a higher peak (at about 500 m).
+For all observations considered (Fig.\ \ref{fig:cloud-occurrence}a), the data show cloud occurrence peaking nearly at the surface, whereas the models show a higher peak (at about 500\ m).
 The models generally underestimate the total cloud fraction by 10--20\% and show a strong reduction in cloud occurrence near the surface, which is not supported by the observations.
-ICON and ERA5 overestimate cloud occurrence at their peak (between 0--1 km).
-Above 1 km, ICON and MERRA-2 underestimate cloud occurrence, but ERA5 is accurate to about 3\% or less.
-The exaggerated peak in models is partly supported by the lifting condensation level (LCL) distribution, which peaks higher by about 200 m in the models than in the observations (nearly at the surface), although this is not very pronounced.
+ICON and ERA5 overestimate cloud occurrence at their peak (between 0--1\ km).
+Above 1\ km, ICON and MERRA-2 underestimate cloud occurrence, but ERA5 is accurate to about 3\% or less.
+The exaggerated peak in models is partly supported by the lifting condensation level (LCL) distribution, which peaks higher by about 200\ m in the models than in the observations (nearly at the surface), although this is not very pronounced.
 This is indicative of near-surface relative humidity being often close to saturation in the observations but not in the models.
@@
 
-When subsetted by conditions of weak and strong stability (Fig.\ \ref{fig:cloud-occurrence}f, g), as defined in Section\ \ref{sec:cyclone-stability}, we see that in situations of strong stability, cloud occurrence peaks strongly nearly at the surface in observations, compared to situations of weak stability, where the peak is more diffuse between 0 and 1 km.
+When subsetted by conditions of weak and strong stability (Fig.\ \ref{fig:cloud-occurrence}f, g), as defined in Section\ \ref{sec:cyclone-stability}, we see that in situations of strong stability, cloud occurrence peaks strongly nearly at the surface in observations, compared to situations of weak stability, where the peak is more diffuse between 0 and 1\ km.
 It is worth mentioning that conditions of strong stability might be associated with the formation of advection fog, such as in situations of warm air advection from the north over a colder sea surface, thus inducing fog formation by cooling of the warm and humid air by the cold surface.
-In situations of strong stability, the models have smaller biases than in weak stability, with an overestimated peak by up to 12\%, underestimated cloud occurrence above 1 km by up to 5\%, and underestimated cloud occurrence near the surface by about 11\%.
-In situations of weak stability, the bias in ICON is very pronounced, with a much stronger peak at about 500 m; ERA5 underestimates cloud occurrence below 1 km (especially near the surface); and MERRA-2 underestimates cloud occurrence even more strongly.
+In situations of strong stability, the models have smaller biases than in weak stability, with an overestimated peak by up to 12\%, underestimated cloud occurrence above 1\ km by up to 5\%, and underestimated cloud occurrence near the surface by about 11\%.
+In situations of weak stability, the bias in ICON is very pronounced, with a much stronger peak at about 500\ m; ERA5 underestimates cloud occurrence below 1\ km (especially near the surface); and MERRA-2 underestimates cloud occurrence even more strongly.
 
@@
 ICON can be generally characterized as substantially overestimating cloud occurrence below 1 km and underestimating above, underestimating the total cloud fraction, and showing the greatest biases in conditions of weak stability and non-cyclonic conditions.
-It also shows a peak of cloud occurrence at higher altitudes than observations (500 m vs.
+It also shows a peak of cloud occurrence at higher altitudes than observations (500\ m vs.
 near the surface), and correspondingly, its LCL tends to be higher.
-MERRA-2 can be generally characterized as underestimating cloud occurrence at nearly all altitudes as well as the total cloud fraction, but mostly above and below 500 m (the peak at 500 m is well represented).
+MERRA-2 can be generally characterized as underestimating cloud occurrence at nearly all altitudes as well as the total cloud fraction, but mostly above and below 500\ m (the peak at 500\ m is well represented).
 MERRA-2 displays the largest errors relative to observations in the low-latitude SO zone and in situations of weak stability.
-ERA5 can be generally characterized as representing cloud occurrence correctly above about 1--1.5 km, overestimating below, but underestimating near-surface cloud occurrence (0--500 m).
+ERA5 can be generally characterized as representing cloud occurrence correctly above about 1--1.5\ km, overestimating below, but underestimating near-surface cloud occurrence (0--500\ m).
 The total cloud fraction is strongly underestimated in all situations.
@@
 In contrast, LW radiation is affected by much smaller biases than SW radiation, which is expected due to the prevailing low-level clouds having similar temperature as the surface.
-In ICON, the outgoing LW radiation is overestimated by 8\%, which could be caused by an underestimated total cloud fraction exposing a larger sea surface area to cooling to space, which is typically warmer than the atmospheric temperature at 0--2 km, where most of the clouds are located.
-In the MERRA-2 and ERA5 reanalyses, the LW biases are also slightly positive by 4 and 7 Wm$^{-2}$.
+In ICON, the outgoing LW radiation is overestimated by 8\%, which could be caused by an underestimated total cloud fraction exposing a larger sea surface area to cooling to space, which is typically warmer than the atmospheric temperature at 0--2\ km, where most of the clouds are located.
+In the MERRA-2 and ERA5 reanalyses, the LW biases are also slightly positive by 4 and 7\ Wm$^{-2}$.
 This is again in line with the underestimated total cloud fraction by about 20\%.
@@
 In all the subsets (Fig.\ \ref{fig:cloud-occurrence}b--g), the same type of bias is present as in the general case -- the outgoing SW radiation is underestimated in ICON and overestimated in MERRA-2 and ERA5, and the outgoing LW radiation is overestimated in all the models.
-Even though the total cloud fraction is lower by 7\% over the high-latitude SO than the low-latitude SO, the outgoing SW radiation is much greater by 41 Wm$^{-2}$, implying a much greater cloud albedo over the high-latitude SO.
-ICON has the same contrast between these two regions in the total cloud fraction and SW radiation, but the outgoing SW radiation difference between the regions is much smaller (16 Wm$^{-2}$).
+Even though the total cloud fraction is lower by 7\% over the high-latitude SO than the low-latitude SO, the outgoing SW radiation is much greater by 41\ Wm$^{-2}$, implying a much greater cloud albedo over the high-latitude SO.
+ICON has the same contrast between these two regions in the total cloud fraction and SW radiation, but the outgoing SW radiation difference between the regions is much smaller (16\ Wm$^{-2}$).
 The reanalyses do not show this type of contrast between the regions.
@@
 In Fig.\ \ref{fig:cloud-cover} we show the results for the same subsets of data as in Section\ \ref{sec:cloud-occurrence}.
-Observations display the highest proportion of high cloud cover values (5--8 oktas), peaking at 7 oktas.
+Observations display the highest proportion of high cloud cover values (5--8\ oktas), peaking at 7\ oktas.
 This pattern is not represented by ICON or either reanalysis.
-While ICON is closest to matching the observed distribution, it tends to be 1 okta clearer than the observations, peaking at 6 oktas, and substantially underestimating days with 8 oktas.
-Overall, the reanalyses show results similar to each other, underestimating cloud cover by about 2 oktas and strongly underestimating days with 7 and 8 oktas.
+While ICON is closest to matching the observed distribution, it tends to be 1\ okta clearer than the observations, peaking at 6\ oktas, and substantially underestimating days with 8\ oktas.
+Overall, the reanalyses show results similar to each other, underestimating cloud cover by about 2\ oktas and strongly underestimating days with 7 and 8\ oktas.
 Of the two reanalyses, MERRA-2 has slightly higher cloud cover than ERA5, by about 6\% at 6 octas, which makes it more consistent with observations.
 
-When analyzed by subsets, observations in the cyclonic subset show the highest cloud cover, with 8 oktas occurring on one half of such days (Fig.\ \ref{fig:cloud-cover}d).
+When analyzed by subsets, observations in the cyclonic subset show the highest cloud cover, with 8\ oktas occurring on one half of such days (Fig.\ \ref{fig:cloud-cover}d).
 This sensitivity to cyclonic conditions is not observed in ICON or the reanalyses.
-Interestingly, clear sky days (0 oktas) also have a local maximum peaking at about 15\% in this subset.
-When we contrast the low- and high-latitude zones, we see that the high-latitude zone tends to have greater cloud cover, peaking at 8 oktas (Fig.\ \ref{fig:cloud-cover}c).
-The high-latitude zone also has almost no clear sky or small cloud cover cases (0--4 oktas).
-ICON and the reanalyses represent this characteristic of the distribution well for 0--3 oktas, but otherwise show biases similar to the general case.
-One of the greatest biases is present in ERA5 in the subset of weak stability, in which ERA5 peaks at 3 oktas, while the observations peak at 7 oktas and show negligible cloud cover below 5 oktas.
+Interestingly, clear sky days (0\ oktas) also have a local maximum peaking at about 15\% in this subset.
+When we contrast the low- and high-latitude zones, we see that the high-latitude zone tends to have greater cloud cover, peaking at 8\ oktas (Fig.\ \ref{fig:cloud-cover}c).
+The high-latitude zone also has almost no clear sky or small cloud cover cases (0--4\ oktas).
+ICON and the reanalyses represent this characteristic of the distribution well for 0--3\ oktas, but otherwise show biases similar to the general case.
+One of the greatest biases is present in ERA5 in the subset of weak stability, in which ERA5 peaks at 3\ oktas, while the observations peak at 7\ oktas and show negligible cloud cover below 5\ oktas.
 
@@
 
-Overall, the mean $\theta_v$ is accurate to less than 0.5 K in ICON and MERRA-2, except for ICON being colder by up to 2.5 K in the mid-to-high troposphere (less stable) (Fig.\ \ref{fig:potential-temperature}a).
+Overall, the mean $\theta_v$ is accurate to less than 0.5\ K in ICON and MERRA-2, except for ICON being colder by up to 2.5\ K in the mid-to-high troposphere (less stable) (Fig.\ \ref{fig:potential-temperature}a).
 Larger differences exist, however, in the 40--55°S zone, where ICON is colder by about 5 K at higher altitudes (Fig.\ \ref{fig:potential-temperature}b).
@@
 Relative humidity displays much larger biases.
-In all subsets, ICON is too humid in the first 1 km by about 5\% but very accurate above, except for the 40--55°S zone and conditions of weak stability (Fig.\ \ref{fig:potential-temperature}b, g), where it is too dry between about 1 and 3 km.
-MERRA-2, on the other hand, is more humid than observations at all altitudes and in all subsets, by up to about 20\% at 5 km.
+In all subsets, ICON is too humid in the first 1\ km by about 5\% but very accurate above, except for the 40--55°S zone and conditions of weak stability (Fig.\ \ref{fig:potential-temperature}b, g), where it is too dry between about 1 and 3\ km.
+MERRA-2, on the other hand, is more humid than observations at all altitudes and in all subsets, by up to about 20\% at\ 5 km.
 Even though the mean near-surface relative humidity is similar to the observations (Fig.\ \ref{fig:potential-temperature}), the distribution in observation is more spread out across both high and low values, and thus observations have a greater prevalence of relative humidity close to 100\% and thus LCL located at the surface (Fig.\ \ref{fig:cloud-occurrence}a).
@@
 Ground-based lidar observations can be regarded as superior to satellite lidar observations for low-level clouds, which are predominant in this region, while mid- and high-level clouds are better sampled by satellite observations \cite{mcerlich2021}.
-Near-surface lidar retrievals (~100 m) are affected by uncertainties related to incomplete overlap, signal saturation (dead time), and after-pulse effect corrections \cite{kuma2021}.
+Near-surface lidar retrievals (~100\ m) are affected by uncertainties related to incomplete overlap, signal saturation (dead time), and after-pulse effect corrections \cite{kuma2021}.
 
@@
 The 31 voyages and a station show remarkably similar biases in cloud occurrence by height in the lidar comparison, which indicates that common underlying causes for the biases exist regardless of longitude and season.
-ICON underestimates the total cloud fraction by about 10\%, with an overestimation of clouds below 2 km and an underestimation of clouds above 2 km.
+ICON underestimates the total cloud fraction by about 10\%, with an overestimation of clouds below 2\ km and an underestimation of clouds above 2\ km.
 The reanalyses also underestimate the total cloud fraction by about 20\%.
-ERA5 overestimates cloud below 1 km but underestimates near-surface cloud or fog.
+ERA5 overestimates cloud below 1\ km but underestimates near-surface cloud or fog.
 ICON strongly overestimates the peak of cloud occurrence at about 500 m, which might be explained by the radiosonde comparison, showing that it is too moist at around this height.
-Similar to our results, \citeA{cesana2022} showed that CMIP6 models also tend to underestimate cloud occurrence above 2 km over the SO, although their analysis in this case was limited to liquid clouds.
+Similar to our results, \citeA{cesana2022} showed that CMIP6 models also tend to underestimate cloud occurrence above 2\ km over the SO, although their analysis in this case was limited to liquid clouds.
 
-Compared to lidar observations, the daily cloud cover tends to be about 1 okta lower in ICON and 2 oktas lower in the reanalyses.
+Compared to lidar observations, the daily cloud cover tends to be about 1\ okta lower in ICON and 2\ oktas lower in the reanalyses.
 Conditions of weak stability are associated with some of the greatest biases, especially in ERA5.
-The models also underestimate the cloud cover very strongly in cyclonic conditions, which are very cloudy in the observations (8 oktas), but much less so in the models.
+The models also underestimate the cloud cover very strongly in cyclonic conditions, which are very cloudy in the observations (8\ oktas), but much less so in the models.
 Similarly, \citeA{mcerlich2023} found a 40\% underestimation of cloud liquid water in cyclones over the SO in ERA5, despite total column water vapor simulated much more accurately (5\% underestimation).
@@
 The data collection by the University of Canterbury was funded by the Deep South National Science Challenge Clouds and Aerosols project.
-Data collection on the AA15-16 voyages was funded by the Australian Antarctic Science project (grant no.
-4292).
+Data collection on the AA15-16 voyages was funded by the Australian Antarctic Science project (grant no.\ 4292).
 We acknowledge the contribution of Thorsten Mauritsen to funding acquisition and project management.

### 2024-12-12 manuscript_agu.tex
Unbrekabale space

--- 2024-12-12 manuscript_agu.tex
@@
 \item Ground-based lidar evaluation of a km-scale global climate model and reanalyses reveals substantial cloud biases over the Southern Ocean.
-\item Fog or low cloud is underestimated in the reanalyses. In all models, a cloud peak at 500 m tends to be overestimated and too high.
+\item Fog or low cloud is underestimated in the reanalyses. In all models, a cloud peak at 500~m tends to be overestimated and too high.
 \item A ``too few, too bright'' problem of underestimated cloud fraction, compensated by overestimated cloud albedo, is present in the reanalyses.
@@
 The high resolution means that parameterizations of convection and clouds, including subgrid-scale clouds, are omitted, relying on explicit simulation but still utilizing microphysics and turbulence parameterizations.
-Standard-resolution (10--100 km) models, which use convection and cloud parameterizations, have substantial cloud biases over the Southern Ocean (SO), affecting radiation and sea surface temperature.
+Standard-resolution (10--100~km) models, which use convection and cloud parameterizations, have substantial cloud biases over the Southern Ocean (SO), affecting radiation and sea surface temperature.
 The SO is dominated by low clouds, which cannot be observed accurately from space due to overlapping clouds, attenuation, and ground clutter.
@@
 Therefore, it represents a natural advance in climate modeling.
-Global storm-resolving models (GSRMs) are emerging as a new front in the development of high-resolution global climate models, with horizontal grid resolutions of about 2--8 km \cite{satoh2019,stevens2019}.
+Global storm-resolving models (GSRMs) are emerging as a new front in the development of high-resolution global climate models, with horizontal grid resolutions of about 2--8~km \cite{satoh2019,stevens2019}.
 This is enough to resolve mesoscale convective storms, but smaller-scale convective plumes and cloud structure remain unresolved.
@@
 The terms global cloud-resolving models or global convection-permitting/-resolving models are also sometimes used interchangeably with GSRMs but imply that clouds or convection are resolved explicitly, which is not entirely true for GSRMs, as this would require an even higher horizontal resolution \cite{satoh2019}.
-Representative of these efforts is the DYnamics of the Atmospheric general circulation Modeled On Non-hydrostatic Domains (DYAMOND) project \cite{stevens2019,dyamond}, which is an intercomparison of nine global GSRMs over two 40-day time periods in summer (1 August -- 10 September 2016) and winter (20 January -- 1 March 2020).
+Representative of these efforts is the DYnamics of the Atmospheric general circulation Modeled On Non-hydrostatic Domains (DYAMOND) project \cite{stevens2019,dyamond}, which is an intercomparison of nine global GSRMs over two 40-day time periods in summer (1~August--10~September 2016) and winter (20~January--1~March 2020).
 A new one-year GSRM intercomparison is currently proposed by \citeA{takasuka2024}, with the hope of also evaluating the seasonal cycle and large-scale circulation.
@@
 Here, we conventionally refer to the SO as ocean regions south of 40°S, low-latitude SO as 40--55°S and high-latitude SO as south of 55°S.
-The reason for this dividing latitude is to split the SO into about two equal zones, as well as the results by \citeA{schuddeboom2021} (Fig.\ 2b), showing a contrast in CMIP model radiation biases, \citeA{schuddeboom2019} (Fig.\ 2) and \citeA{kuma2020} (Fig.\ 3) showing contrasting radiation biases in the Hadley Centre Global Environmental Model, and \citeA{cesana2022} showing contrasting cloud biases due to the 0°C isotherm reaching the surface at 55°S.
+The reason for this dividing latitude is to split the SO into about two equal zones, as well as the results by \citeA{schuddeboom2021} (Fig.~2b), showing a contrast in CMIP model radiation biases, \citeA{schuddeboom2019} (Fig.~2) and \citeA{kuma2020} (Fig.~3) showing contrasting radiation biases in the Hadley Centre Global Environmental Model, and \citeA{cesana2022} showing contrasting cloud biases due to the 0°C isotherm reaching the surface at 55°S.
 The findings of \citeA{niu2024}, however, support a different dividing line of 62°S based on cloud condensation nuclei concentration.
@@
 Compensating cloud biases in the Australian Community Climate and Earth System Simulator (ACCESS) – Atmosphere-only model version 2 (AM2) over the SO were analyzed by \citeA{fiddes2022} and \citeA{fiddes2024}.
-\citeA{possner2022} showed that over the SO, the DYAMOND GSRM ICON underestimates low-level cloud fraction on the order of 30\% and overestimates net downward TOA SW radiation by approximately 10 Wm$^\mathrm{-2}$ in the highest model resolution run (2.5 km).
+\citeA{possner2022} showed that over the SO, the DYAMOND GSRM ICON underestimates low-level cloud fraction on the order of 30\% and overestimates net downward TOA SW radiation by approximately 10 Wm$^\mathrm{-2}$ in the highest model resolution run (2.5~km).
 \citeA{zhao2022} reported a similar SW radiation bias in five analyzed CMIP6 models over high-latitude SO and the total cloud fraction underestimation on the order of 10\% over the entire 40--60°S SO.
-Recently, \citeA{ramadoss2024} analyzed 48 hours of km-scale ICON limited-area model NWP simulations over a SO region adjacent to Tasmania against the Clouds, Aerosols, Precipitation, Radiation, and atmospherIc Composition Over the southeRn oceaN (CAPRICORN) voyage cloud and precipitation observations \cite{mcfarquhar2021}.
+Recently, \citeA{ramadoss2024} analyzed 48~hours of km-scale ICON limited-area model NWP simulations over a SO region adjacent to Tasmania against the Clouds, Aerosols, Precipitation, Radiation, and atmospherIc Composition Over the southeRn oceaN (CAPRICORN) voyage cloud and precipitation observations \cite{mcfarquhar2021}.
 They found the ICON cloud optical thickness was underestimated relative to Himawari‐8 satellite observations but also identified large differences in cloud top phase.
@@
 To achieve a like-for-like comparison with the model, we used a ground-based lidar simulator called the Automatic Lidar and Ceilometer Framework [ALCF; \citeA{kuma2021}].
-We contrasted the results with ERA5 \cite{era5} and the Modern-Era Retrospective analysis for Research and Applications, Version 2 [MERRA-2; \citeA{gelaro2017}].
+We contrasted the results with ERA5 \cite{era5} and the Modern-Era Retrospective analysis for Research and Applications, Version~2 [MERRA-2; \citeA{gelaro2017}].
 
@@
 The dotted and dashed lines at 40°S and 55°S delineate the Southern Ocean area of our analysis and its partitioning into two subsets, respectively.
-A photo of \textbf{(b)} RV \emph{Polarstern} (© Folke Mehrtens, Alfred-Wegener-Institut), \textbf{(c)} Lufft CHM 15k installed on RV \emph{Tangaroa} (© Peter Kuma, University of Canterbury), \textbf{(d)} Vaisala CL51 (© Jeff Aquilina, Bureau of Meteorology), \textbf{(e)} Vaisala CT25K at Macquarie Island (© Simon P.\ Alexander, Australian Antarctic Division).
+A photo of \textbf{(b)} RV \emph{Polarstern} (© Folke Mehrtens, Alfred-Wegener-Institut), \textbf{(c)} Lufft CHM~15k installed on RV \emph{Tangaroa} (© Peter Kuma, University of Canterbury), \textbf{(d)} Vaisala CL51 (© Jeff Aquilina, Bureau of Meteorology), \textbf{(e)} Vaisala CT25K at Macquarie Island (© Simon P.\ Alexander, Australian Antarctic Division).
 }
@@
 Palmer}, Her (now His) Majesty's New Zealand Ship (HMNZS) \emph{Wellington} and one sub-Antarctic station (Macquarie Island) in the SO south of 40°S between 2010 and 2021.
-Fig.\ \ref{fig:map} shows a map of the campaigns, Table \ref{tab:voyages} lists the campaigns, and Table \ref{tab:voyage-references} lists references where available.
+Fig.~\ref{fig:map} shows a map of the campaigns, Table \ref{tab:voyages} lists the campaigns, and Table \ref{tab:voyage-references} lists references where available.
 Altogether, the analyzed dataset comprised 2421 days of data south of 40°S, but the availability of ceilometer data was slightly shorter due to gaps in measurements.
 
-The campaigns contained ceilometer observations captured by the Vaisala CL51 and CT25K, and the Lufft CHM 15k, described in detail below (Sections\ \ref{sec:cl51} and \ref{sec:chm15k}).
+The campaigns contained ceilometer observations captured by the Vaisala CL51 and CT25K, and the Lufft CHM~15k, described in detail below (Sections~\ref{sec:cl51} and \ref{sec:chm15k}).
 A ceilometer is a low-power, near-infrared, vertically pointing lidar principally designed to measure cloud base, but they also measure the full vertical structure of clouds as long as the laser signal is not attenuated by thick clouds, which can be used to infer additional information such as a cloud mask and cloud occurrence by height.
@@
 CL51/31 indicates CL51 configured to emulate CL31.
-Missing days in the ceilometer data were HMNZSW16 (7 days): 24--27 November, 10 December, 16--17 December 2016; MARCUS (3 days): 8, 10 November, 10 December 2017; MICRE (9 days): 7--8, 29 June, 5, 16 July, 15 August, 17 October 2016, 11 February, 21 March 2017; TAN1502 (1 day): 24 January.
+Missing days in the ceilometer data were HMNZSW16 (7 days): 24--27 November, 10~December, 16--17~December 2016; MARCUS (3 days): 8, 10~November, 10~December 2017; MICRE (9~days): 7--8, 29~June, 5, 16~July, 15~August, 17~October 2016, 11~February, 21~March 2017; TAN1502 (1~day): 24~January.
 }
@@
 
-The Vaisala CL51 and CT25K (photos in Fig.\ \ref{fig:map}d, e) are ceilometers operating at near-infrared wavelengths of 910 nm and 905 nm, respectively.
+The Vaisala CL51 and CT25K (photos in Fig.~\ref{fig:map}d, e) are ceilometers operating at near-infrared wavelengths of 910~nm and 905~nm, respectively.
 The CL51 can also be configured to emulate the Vaisala CL31.
-The maximum range is 15.4 km (CL51), 7.7 km (CL31 emulation mode with 5 m vertical resolution), and 7.5 km (CT25K).
-The vertical resolution is 10 m (5 m configurable) in CL51 and 30 m in CT25K observations.
-The sampling (temporal) resolution is configurable, and in our datasets, it is approximately 6 s for CL51 on AA15‐16, 16 s for CT25K on MARCUS and MICRE, 36 s for CL51 on RV \emph{Polarstern}, and about 2.37 s for CL51 with CL31 emulation on TAN1502.
-The wavelengths of 905 and 910 nm are affected by water vapor absorption of about 20\% in the mid-latitudes \cite{wiegner2015,wiegner2019}, with 910 nm affected more strongly, but we do not expect this to be a significant issue as explained in \citeA{kuma2021}.
-The instrument data files containing raw uncalibrated backscatter were first converted to Network Common Data Form (NetCDF) with cl2nc (\url{https://github.com/peterkuma/cl2nc}) and then processed with the ALCF (Section\ \ref{sec:alcf}) to produce absolutely calibrated attenuated volume backscattering coefficient (AVBC), cloud mask, cloud occurrence by height, and the total cloud fraction.
-Because the CT25K uses a very similar wavelength to CL51, equivalent calculations as for CL51 were done assuming a wavelength of 910 nm.
+The maximum range is 15.4~km (CL51), 7.7~km (CL31 emulation mode with 5~m vertical resolution), and 7.5~km (CT25K).
+The vertical resolution is 10~m (5~m configurable) in CL51 and 30~m in CT25K observations.
+The sampling (temporal) resolution is configurable, and in our datasets, it is approximately 6~s for CL51 on AA15‐16, 16~s for CT25K on MARCUS and MICRE, 36~s for CL51 on RV \emph{Polarstern}, and about 2.37~s for CL51 with CL31 emulation on TAN1502.
+The wavelengths of 905 and 910~nm are affected by water vapor absorption of about 20\% in the mid-latitudes \cite{wiegner2015,wiegner2019}, with 910~nm affected more strongly, but we do not expect this to be a significant issue as explained in \citeA{kuma2021}.
+The instrument data files containing raw uncalibrated backscatter were first converted to Network Common Data Form (NetCDF) with cl2nc (\url{https://github.com/peterkuma/cl2nc}) and then processed with the ALCF (Section~\ref{sec:alcf}) to produce absolutely calibrated attenuated volume backscattering coefficient (AVBC), cloud mask, cloud occurrence by height, and the total cloud fraction.
+Because the CT25K uses a very similar wavelength to CL51, equivalent calculations as for CL51 were done assuming a wavelength of 910~nm.
 The Vaisala CL51 and CT25K instruments were used on most of the voyages and stations analyzed here.
-Fig.\ \ref{fig:example}a shows an example of AVBC derived from the CL51 instrument data.
+Fig.~\ref{fig:example}a shows an example of AVBC derived from the CL51 instrument data.
 
@@
 \caption{
-An example of the attenuated volume backscattering coefficient (AVBC) \textbf{(a)} measured by CL51 during 24 hours on the PS81/3 voyage and \textbf{(b)} an equivalent AVBC simulated with the ALCF from ERA5 data during the same time period.
+An example of the attenuated volume backscattering coefficient (AVBC) \textbf{(a)} measured by CL51 during 24~hours on the PS81/3 voyage and \textbf{(b)} an equivalent AVBC simulated with the ALCF from ERA5 data during the same time period.
 The red line identifies the cloud mask determined by the ALCF.
@@
 
-\subsection{Lufft CHM 15k}
+\subsection{Lufft CHM~15k}
 \label{sec:chm15k}
 
-The Lufft CHM 15k (photo in Fig.\ \ref{fig:map}c) is a ceilometer operating at a near-infrared wavelength of 1064 nm.
-The maximum range is 15.4 km; the vertical resolution is 5 m in the near range (up to 150 m) and 15 m above; the sampling (temporal) resolution is 2 s; and the number of vertical levels is 1024.
-NetCDF files containing uncalibrated backscatter produced by the instrument were processed with the ALCF (Section\ \ref{sec:alcf}) to again produce AVBC, cloud mask, cloud occurrence by height, and the total cloud fraction.
-The CHM 15k was used on four voyages (HMNZSW16, TAN1702, TAN1802, and NBP1704).
+The Lufft CHM~15k (photo in Fig.~\ref{fig:map}c) is a ceilometer operating at a near-infrared wavelength of 1064~nm.
+The maximum range is 15.4~km; the vertical resolution is 5~m in the near range (up to 150~m) and 15~m above; the sampling (temporal) resolution is 2~s; and the number of vertical levels is 1024.
+NetCDF files containing uncalibrated backscatter produced by the instrument were processed with the ALCF (Section~\ref{sec:alcf}) to again produce AVBC, cloud mask, cloud occurrence by height, and the total cloud fraction.
+The CHM~15k was used on four voyages (HMNZSW16, TAN1702, TAN1802, and NBP1704).
 
@@
 Absolute calibration of the observed backscatter was performed by comparing the measured clear-sky molecular backscatter statistically with simulated clear-sky molecular backscatter.
-AVBC was resampled to 5 min temporal resolution and 50 m vertical resolution to increase the signal-to-noise ratio while having enough resolution to detect small-scale cloud variability.
+AVBC was resampled to 5 min temporal resolution and 50~m vertical resolution to increase the signal-to-noise ratio while having enough resolution to detect small-scale cloud variability.
 The noise standard deviation was calculated from AVBC at the highest range, where no clouds are expected.
 A cloud mask was calculated from AVBC using a fixed threshold of $\mathrm{2\times 10^{-6} m^{-1}sr^{-1}}$ after subtracting 5 standard deviations of range-scaled noise.
-Fig.\ \ref{fig:example}b shows an example of simulated Vaisala CL51 backscatter from ERA5 data, corresponding to a day of measurements by the instrument on the PS81/3 voyage.
+Fig.~\ref{fig:example}b shows an example of simulated Vaisala CL51 backscatter from ERA5 data, corresponding to a day of measurements by the instrument on the PS81/3 voyage.
 
@@
 To account for the radiative effects of subgrid-scale clouds, a cloud inhomogeneity factor is introduced in the model, which scales down the cloud liquid water for radiative calculations.
-It ranges from 0.4 at lower tropospheric stability (LTS) of 0 K to 0.8 at 30 K.
+It ranges from 0.4 at lower tropospheric stability (LTS) of 0~K to 0.8 at 30~K.
 In addition, vertical mixing is enhanced in unstable and humid lower-tropospheric conditions, which reduces the amount of shallow clouds.
@@
 The geographical location was kept the same.
-We discuss briefly the implications of comparing the observations with a free-running model in Section\ \ref{sec:limitations}.
+We discuss briefly the implications of comparing the observations with a free-running model in Section~\ref{sec:limitations}.
 
@@
 It uses the \citeA{tiedtke1993} prognostic cloud scheme and \citeA{forbes2014} for mixed-phase clouds.
-The horizontal resolution is 0.25° in latitude and longitude, which is about 28 km in the North--South direction and 14 km in the East--West direction at 60°S.
+The horizontal resolution is 0.25° in latitude and longitude, which is about 28~km in the North--South direction and 14~km in the East--West direction at 60°S.
 Internally, the model uses 137 vertical levels.
@@
 
-Radiation calculations presented in the results (Section\ \ref{sec:results}) were completed such that they always represent daily means in order to be consistent with the CERES SYN1deg data.
+Radiation calculations presented in the results (Section~\ref{sec:results}) were completed such that they always represent daily means in order to be consistent with the CERES SYN1deg data.
 Therefore, every instantaneous profile in the simulated lidar data was assigned a daily mean radiation value corresponding to the day (in the Coordinated Universal Time; UTC).
@@
 On the RV \emph{Polarstern} voyages, regular human-performed synoptic observations were available and included precipitation presence or absence and type.
-We used this dataset to train a convolutional artificial neural network (ANN) to recognize profiles with precipitation from lidar backscatter (Fig.\ \ref{fig:ann}a), implemented in the TensorFlow ANN framework \cite{tensorflow}.
-Samples of short time intervals (10 min) of near-surface lidar backscatter (0–250 m) were classified as clear, rain, snow, and fog, using the synoptic observations as a training dataset (Fig.\ \ref{fig:ann}b).
+We used this dataset to train a convolutional artificial neural network (ANN) to recognize profiles with precipitation from lidar backscatter (Fig.~\ref{fig:ann}a), implemented in the TensorFlow ANN framework \cite{tensorflow}.
+Samples of short time intervals (10~min) of near-surface lidar backscatter (0–250 m) were classified as clear, rain, snow, and fog, using the synoptic observations as a training dataset (Fig.~\ref{fig:ann}b).
 From these, a binary, mutually exclusive classification of profiles as precipitating (rain or snow) or dry (clear or fog) was derived.
@@
 The ANN achieved 65\% sensitivity and 87\% specificity when the true positive rate (26\%) was made to match observations.
-The receiver operating characteristic curve is shown in Fig.\ \ref{fig:ann}c.
+The receiver operating characteristic curve is shown in Fig.~\ref{fig:ann}c.
 We considered these rates satisfactory for the purpose of filtering precipitation profiles.
-Fig.\ \ref{fig:ann}d shows examples of the predicted precipitation compared to human-performed observations.
-The main ANN (`ANN` in Fig.\ \ref{fig:ann}) was trained on all data, and ancillary ANNs (`ANN2` in Fig.\ \ref{fig:ann}) were trained on all data except for each voyage.
+Fig.~\ref{fig:ann}d shows examples of the predicted precipitation compared to human-performed observations.
+The main ANN (`ANN` in Fig.~\ref{fig:ann}) was trained on all data, and ancillary ANNs (`ANN2` in Fig.~\ref{fig:ann}) were trained on all data except for each voyage.
 These were used for testing the results relative to each voyage.
@@
 
-In addition to the above, we partitioned our data into two mutually exclusive subsets based on LTS, which is derived as the difference between the potential temperature at 700 hPa and the surface.
-Based on a histogram of LTS in ERA5 and MERRA-2 calculated at all voyage tracks and stations (Fig.\ \ref{fig:lts}), we determined a statistically-based dividing threshold of 12 K for weak stability ($<$ 12 K) and strong stability ($\geq$ 12 K) conditions.
+In addition to the above, we partitioned our data into two mutually exclusive subsets based on LTS, which is derived as the difference between the potential temperature at 700~hPa and the surface.
+Based on a histogram of LTS in ERA5 and MERRA-2 calculated at all voyage tracks and stations (Fig.~\ref{fig:lts}), we determined a statistically-based dividing threshold of 12~K for weak stability ($<$~12~K) and strong stability ($\geq$~12~K) conditions.
 
@@
 \caption{
-Geographical distribution of \textbf{(a, b)} cyclonic days and \textbf{(b, d)} strong stability (LTS $\geq$ 12 K) time steps in \textbf{(a, c)} ERA5 in years 2010--2013 (inclusive) and \textbf{(b, d)} ICON in model years 2021--2023 (free running).
+Geographical distribution of \textbf{(a, b)} cyclonic days and \textbf{(b, d)} strong stability (LTS~$\geq$~12~K) time steps in \textbf{(a, c)} ERA5 in years 2010--2013 (inclusive) and \textbf{(b, d)} ICON in model years 2021--2023 (free running).
 Cyclonic days are expressed as a fraction of the number of days with cyclonic activity, defined as grid points located within a double radius of any cyclone on a given day (UTC), as identified by CyTRACK.
@@
 
-Fig.\ \ref{fig:cyclone-stability}a, b show a geographical distribution of the fraction of cyclonic days as determined by the cyclone tracking algorithm applied to the ERA5 reanalysis and ICON data (Section\ \ref{sec:cyclone-stability}).
+Fig.~\ref{fig:cyclone-stability}a, b show a geographical distribution of the fraction of cyclonic days as determined by the cyclone tracking algorithm applied to the ERA5 reanalysis and ICON data (Section~\ref{sec:cyclone-stability}).
 As expected, the strongest cyclonic activity is in the high-latitude SO zone, and it is relatively zonally symmetric at all latitudes.
@@
 
-Fig.\ \ref{fig:cyclone-stability}c, d show a geographical distribution of the conditions of weak and strong stability as determined by the LTS (Section\ \ref{sec:cyclone-stability}).
+Fig.~\ref{fig:cyclone-stability}c, d show a geographical distribution of the conditions of weak and strong stability as determined by the LTS (Section~\ref{sec:cyclone-stability}).
 Conditions of weak stability are prevalent in the mid-to-high SO (with respect to our SO partitioning; 50--65°S), which might be explained by the relatively cold near-surface air overlying the relatively warm sea surface.
@@
 We used the ALCF to derive cloud occurrence by height and the total cloud fraction from observations, ICON, ERA5, and MERRA-2.
-The results for all campaigns individually are shown in Fig.\ \ref{fig:cloud-occurrence-panel}.
-In addition, we aggregated the campaigns by calculating the averages and percentiles of all individual profiles, presented in Fig.\ \ref{fig:cloud-occurrence}.
+The results for all campaigns individually are shown in Fig.~\ref{fig:cloud-occurrence-panel}.
+In addition, we aggregated the campaigns by calculating the averages and percentiles of all individual profiles, presented in Fig.~\ref{fig:cloud-occurrence}.
 The analysis shows that the total cloud fraction (determined as the fraction of profiles with clouds at any height in the lidar cloud mask) is underestimated in ICON by about 10\% and in the reanalyses by about 20\%.
@@
 We note that fog or near-surface clouds are strongly underestimated in the reanalyses (fog and clouds are both included in the cloud occurrence).
-As shown in Fig.\ \ref{fig:cloud-occurrence-panel}, the biases are relatively consistent across the campaigns and longitudes.
+As shown in Fig.~\ref{fig:cloud-occurrence-panel}, the biases are relatively consistent across the campaigns and longitudes.
 We conclude that the ICON results the observations better than the reanalyses in this metric.
 
-For all observations considered (Fig.\ \ref{fig:cloud-occurrence}a), the data show cloud occurrence peaking nearly at the surface, whereas the models show a higher peak (at about 500 m).
+For all observations considered (Fig.~\ref{fig:cloud-occurrence}a), the data show cloud occurrence peaking nearly at the surface, whereas the models show a higher peak (at about 500~m).
 The models generally underestimate the total cloud fraction by 10--20\% and show a strong reduction in cloud occurrence near the surface, which is not supported by the observations.
-ICON and ERA5 overestimate cloud occurrence at their peak (between 0--1 km).
-Above 1 km, ICON and MERRA-2 underestimate cloud occurrence, but ERA5 is accurate to about 3\% or less.
-The exaggerated peak in models is partly supported by the lifting condensation level (LCL) distribution, which peaks higher by about 200 m in the models than in the observations (nearly at the surface), although this is not very pronounced.
+ICON and ERA5 overestimate cloud occurrence at their peak (between 0--1~km).
+Above 1~km, ICON and MERRA-2 underestimate cloud occurrence, but ERA5 is accurate to about 3\% or less.
+The exaggerated peak in models is partly supported by the lifting condensation level (LCL) distribution, which peaks higher by about 200~m in the models than in the observations (nearly at the surface), although this is not very pronounced.
 This is indicative of near-surface relative humidity being often close to saturation in the observations but not in the models.
 
-When subsetted by latitude (Fig.\ \ref{fig:cloud-occurrence}b, c), we see that the low-latitude SO zone displays a stronger peak of cloud occurrence near the surface than the high-latitude SO zone, and this could be because higher latitudes have less stable atmospheric profiles.
+When subsetted by latitude (Fig.~\ref{fig:cloud-occurrence}b, c), we see that the low-latitude SO zone displays a stronger peak of cloud occurrence near the surface than the high-latitude SO zone, and this could be because higher latitudes have less stable atmospheric profiles.
 The low- and high-latitude SO zones show similar biases in models as in the general case, but ERA5 does not overestimate the peak in the low-latitude SO zone (near-surface cloud occurrence is still strongly underestimated).
 
-When subsetted by cyclonic and non-cyclonic situations (Fig.\ \ref{fig:cloud-occurrence}d, e), we see that the cyclonic situations have a larger amount of observed cloudiness, including peak and total cloud fraction, both by about 7\%.
+When subsetted by cyclonic and non-cyclonic situations (Fig.~\ref{fig:cloud-occurrence}d, e), we see that the cyclonic situations have a larger amount of observed cloudiness, including peak and total cloud fraction, both by about 7\%.
 In the cyclonic situations, the model vertical profiles of cloud occurrence compare well with observations, but they peak higher by about 200 m and stronger by about 8\%.
@@
 
-When subsetted by conditions of weak and strong stability (Fig.\ \ref{fig:cloud-occurrence}f, g), as defined in Section\ \ref{sec:cyclone-stability}, we see that in situations of strong stability, cloud occurrence peaks strongly nearly at the surface in observations, compared to situations of weak stability, where the peak is more diffuse between 0 and 1 km.
+When subsetted by conditions of weak and strong stability (Fig.~\ref{fig:cloud-occurrence}f, g), as defined in Section~\ref{sec:cyclone-stability}, we see that in situations of strong stability, cloud occurrence peaks strongly nearly at the surface in observations, compared to situations of weak stability, where the peak is more diffuse between 0 and 1~km.
 It is worth mentioning that conditions of strong stability might be associated with the formation of advection fog, such as in situations of warm air advection from the north over a colder sea surface, thus inducing fog formation by cooling of the warm and humid air by the cold surface.
-In situations of strong stability, the models have smaller biases than in weak stability, with an overestimated peak by up to 12\%, underestimated cloud occurrence above 1 km by up to 5\%, and underestimated cloud occurrence near the surface by about 11\%.
-In situations of weak stability, the bias in ICON is very pronounced, with a much stronger peak at about 500 m; ERA5 underestimates cloud occurrence below 1 km (especially near the surface); and MERRA-2 underestimates cloud occurrence even more strongly.
+In situations of strong stability, the models have smaller biases than in weak stability, with an overestimated peak by up to 12\%, underestimated cloud occurrence above 1~km by up to 5\%, and underestimated cloud occurrence near the surface by about 11\%.
+In situations of weak stability, the bias in ICON is very pronounced, with a much stronger peak at about 500~m; ERA5 underestimates cloud occurrence below 1~km (especially near the surface); and MERRA-2 underestimates cloud occurrence even more strongly.
 
@@
 ICON can be generally characterized as substantially overestimating cloud occurrence below 1 km and underestimating above, underestimating the total cloud fraction, and showing the greatest biases in conditions of weak stability and non-cyclonic conditions.
-It also shows a peak of cloud occurrence at higher altitudes than observations (500 m vs.
+It also shows a peak of cloud occurrence at higher altitudes than observations (500~m vs.
 near the surface), and correspondingly, its LCL tends to be higher.
-MERRA-2 can be generally characterized as underestimating cloud occurrence at nearly all altitudes as well as the total cloud fraction, but mostly above and below 500 m (the peak at 500 m is well represented).
+MERRA-2 can be generally characterized as underestimating cloud occurrence at nearly all altitudes as well as the total cloud fraction, but mostly above and below 500~m (the peak at 500~m is well represented).
 MERRA-2 displays the largest errors relative to observations in the low-latitude SO zone and in situations of weak stability.
-ERA5 can be generally characterized as representing cloud occurrence correctly above about 1--1.5 km, overestimating below, but underestimating near-surface cloud occurrence (0--500 m).
+ERA5 can be generally characterized as representing cloud occurrence correctly above about 1--1.5~km, overestimating below, but underestimating near-surface cloud occurrence (0--500~m).
 The total cloud fraction is strongly underestimated in all situations.
@@
 
-In Fig.\ \ref{fig:cloud-occurrence}, we also show outgoing shortwave and longwave top of atmosphere radiation.
+In Fig.~\ref{fig:cloud-occurrence}, we also show outgoing shortwave and longwave top of atmosphere radiation.
 In observations, these come from daily mean CERES measurements averaged over the voyage tracks or a station location, whereas in the models they come from daily means of TOA radiation in the model output averaged over the same location and time periods.
-In the free-running ICON model, the time period is mapped onto the available years, as explained in Section\ \ref{sec:icon}.
+In the free-running ICON model, the time period is mapped onto the available years, as explained in Section~\ref{sec:icon}.
 
-In the general case (Fig.\ \ref{fig:cloud-occurrence}a), ICON underestimates the outgoing SW radiation by 26 Wm$^{-2}$ and the reanalyses MERRA-2 and ERA5 are much closer but overestimate it by 6 and 14 Wm$^{-2}$, respectively.
+In the general case (Fig.~\ref{fig:cloud-occurrence}a), ICON underestimates the outgoing SW radiation by 26 Wm$^{-2}$ and the reanalyses MERRA-2 and ERA5 are much closer but overestimate it by 6 and 14 Wm$^{-2}$, respectively.
 While in ICON, this is in line with the underestimated total cloud fraction by 10\%, in the reanalyses this is the opposite result as expected from the underestimated total cloud fraction by about 20\%.
@@
 In contrast, LW radiation is affected by much smaller biases than SW radiation, which is expected due to the prevailing low-level clouds having similar temperature as the surface.
-In ICON, the outgoing LW radiation is overestimated by 8\%, which could be caused by an underestimated total cloud fraction exposing a larger sea surface area to cooling to space, which is typically warmer than the atmospheric temperature at 0--2 km, where most of the clouds are located.
-In the MERRA-2 and ERA5 reanalyses, the LW biases are also slightly positive by 4 and 7 Wm$^{-2}$.
+In ICON, the outgoing LW radiation is overestimated by 8\%, which could be caused by an underestimated total cloud fraction exposing a larger sea surface area to cooling to space, which is typically warmer than the atmospheric temperature at 0--2~km, where most of the clouds are located.
+In the MERRA-2 and ERA5 reanalyses, the LW biases are also slightly positive by 4 and 7~Wm$^{-2}$.
 This is again in line with the underestimated total cloud fraction by about 20\%.
@@
 
-In all the subsets (Fig.\ \ref{fig:cloud-occurrence}b--g), the same type of bias is present as in the general case -- the outgoing SW radiation is underestimated in ICON and overestimated in MERRA-2 and ERA5, and the outgoing LW radiation is overestimated in all the models.
-Even though the total cloud fraction is lower by 7\% over the high-latitude SO than the low-latitude SO, the outgoing SW radiation is much greater by 41 Wm$^{-2}$, implying a much greater cloud albedo over the high-latitude SO.
-ICON has the same contrast between these two regions in the total cloud fraction and SW radiation, but the outgoing SW radiation difference between the regions is much smaller (16 Wm$^{-2}$).
+In all the subsets (Fig.~\ref{fig:cloud-occurrence}b--g), the same type of bias is present as in the general case -- the outgoing SW radiation is underestimated in ICON and overestimated in MERRA-2 and ERA5, and the outgoing LW radiation is overestimated in all the models.
+Even though the total cloud fraction is lower by 7\% over the high-latitude SO than the low-latitude SO, the outgoing SW radiation is much greater by 41~Wm$^{-2}$, implying a much greater cloud albedo over the high-latitude SO.
+ICON has the same contrast between these two regions in the total cloud fraction and SW radiation, but the outgoing SW radiation difference between the regions is much smaller (16~Wm$^{-2}$).
 The reanalyses do not show this type of contrast between the regions.
-The physical reason for this might be that the prevalence of fog or low-level clouds over the low-latitude SO and their relative lack over the high-latitude SO in observations is not reproduced in the models (Fig.\ \ref{fig:cloud-occurrence}b--c).
+The physical reason for this might be that the prevalence of fog or low-level clouds over the low-latitude SO and their relative lack over the high-latitude SO in observations is not reproduced in the models (Fig.~\ref{fig:cloud-occurrence}b--c).
 
@@
 
-In Fig.\ \ref{fig:cloud-cover} we show the results for the same subsets of data as in Section\ \ref{sec:cloud-occurrence}.
-Observations display the highest proportion of high cloud cover values (5--8 oktas), peaking at 7 oktas.
+In Fig.~\ref{fig:cloud-cover} we show the results for the same subsets of data as in Section~\ref{sec:cloud-occurrence}.
+Observations display the highest proportion of high cloud cover values (5--8~oktas), peaking at 7~oktas.
 This pattern is not represented by ICON or either reanalysis.
-While ICON is closest to matching the observed distribution, it tends to be 1 okta clearer than the observations, peaking at 6 oktas, and substantially underestimating days with 8 oktas.
-Overall, the reanalyses show results similar to each other, underestimating cloud cover by about 2 oktas and strongly underestimating days with 7 and 8 oktas.
+While ICON is closest to matching the observed distribution, it tends to be 1~okta clearer than the observations, peaking at 6~oktas, and substantially underestimating days with 8~oktas.
+Overall, the reanalyses show results similar to each other, underestimating cloud cover by about 2~oktas and strongly underestimating days with 7 and 8~oktas.
 Of the two reanalyses, MERRA-2 has slightly higher cloud cover than ERA5, by about 6\% at 6 octas, which makes it more consistent with observations.
 
-When analyzed by subsets, observations in the cyclonic subset show the highest cloud cover, with 8 oktas occurring on one half of such days (Fig.\ \ref{fig:cloud-cover}d).
+When analyzed by subsets, observations in the cyclonic subset show the highest cloud cover, with 8~oktas occurring on one half of such days (Fig.~\ref{fig:cloud-cover}d).
 This sensitivity to cyclonic conditions is not observed in ICON or the reanalyses.
-Interestingly, clear sky days (0 oktas) also have a local maximum peaking at about 15\% in this subset.
-When we contrast the low- and high-latitude zones, we see that the high-latitude zone tends to have greater cloud cover, peaking at 8 oktas (Fig.\ \ref{fig:cloud-cover}c).
-The high-latitude zone also has almost no clear sky or small cloud cover cases (0--4 oktas).
-ICON and the reanalyses represent this characteristic of the distribution well for 0--3 oktas, but otherwise show biases similar to the general case.
-One of the greatest biases is present in ERA5 in the subset of weak stability, in which ERA5 peaks at 3 oktas, while the observations peak at 7 oktas and show negligible cloud cover below 5 oktas.
+Interestingly, clear sky days (0~oktas) also have a local maximum peaking at about 15\% in this subset.
+When we contrast the low- and high-latitude zones, we see that the high-latitude zone tends to have greater cloud cover, peaking at 8~oktas (Fig.~\ref{fig:cloud-cover}c).
+The high-latitude zone also has almost no clear sky or small cloud cover cases (0--4~oktas).
+ICON and the reanalyses represent this characteristic of the distribution well for 0--3~oktas, but otherwise show biases similar to the general case.
+One of the greatest biases is present in ERA5 in the subset of weak stability, in which ERA5 peaks at 3~oktas, while the observations peak at 7~oktas and show negligible cloud cover below 5~oktas.
 
@@
 The total cloud fraction of a day (UTC) is calculated as a fraction of cloudy (based on the cloud mask) observed (OBS) or simulated lidar profiles.
-The models and subsets are as in Fig.\ \ref{fig:cloud-occurrence}.
+The models and subsets are as in Fig.~\ref{fig:cloud-occurrence}.
 }
@@
 \caption{
-Virtual potential temperature (virt.\ pot.\ temp.; $\theta_v$) and relative humidity (RH) determined from radiosonde launches and co-located profiles in ICON, ERA5, and MERRA-2 in subsets as in Fig.\ \ref{fig:cloud-occurrence}.
+Virtual potential temperature (virt.\ pot.\ temp.; $\theta_v$) and relative humidity (RH) determined from radiosonde launches and co-located profiles in ICON, ERA5, and MERRA-2 in subsets as in Fig.~\ref{fig:cloud-occurrence}.
 The solid lines are the average calculated from the averages of every individual voyage and station.
@@
 Consequently, we also had four virtual/model profiles (one for each year of 2021--2024) for each observed profile.
-The profiles were partitioned into the same subsets as above (Sections\ \ref{sec:cloud-occurrence} and \ref{sec:cloud-cover}).
+The profiles were partitioned into the same subsets as above (Sections~\ref{sec:cloud-occurrence} and \ref{sec:cloud-cover}).
 Apart from relative humidity, we focus on comparing virtual potential temperature ($\theta_v$) due to its role in low-level tropospheric stability, being one of the primary factors affecting shallow convection and the associated low-level cloud formation and dissipation.
-The observed and model profiles of virtual potential temperature are shown in Fig.\ \ref{fig:potential-temperature}.
+The observed and model profiles of virtual potential temperature are shown in Fig.~\ref{fig:potential-temperature}.
 
-Overall, the mean $\theta_v$ is accurate to less than 0.5 K in ICON and MERRA-2, except for ICON being colder by up to 2.5 K in the mid-to-high troposphere (less stable) (Fig.\ \ref{fig:potential-temperature}a).
-Larger differences exist, however, in the 40--55°S zone, where ICON is colder by about 5 K at higher altitudes (Fig.\ \ref{fig:potential-temperature}b).
+Overall, the mean $\theta_v$ is accurate to less than 0.5~K in ICON and MERRA-2, except for ICON being colder by up to 2.5~K in the mid-to-high troposphere (less stable) (Fig.~\ref{fig:potential-temperature}a).
+Larger differences exist, however, in the 40--55°S zone, where ICON is colder by about 5 K at higher altitudes (Fig.~\ref{fig:potential-temperature}b).
 In other subsets, the bias is relatively small.
@@
 Relative humidity displays much larger biases.
-In all subsets, ICON is too humid in the first 1 km by about 5\% but very accurate above, except for the 40--55°S zone and conditions of weak stability (Fig.\ \ref{fig:potential-temperature}b, g), where it is too dry between about 1 and 3 km.
-MERRA-2, on the other hand, is more humid than observations at all altitudes and in all subsets, by up to about 20\% at 5 km.
-Even though the mean near-surface relative humidity is similar to the observations (Fig.\ \ref{fig:potential-temperature}), the distribution in observation is more spread out across both high and low values, and thus observations have a greater prevalence of relative humidity close to 100\% and thus LCL located at the surface (Fig.\ \ref{fig:cloud-occurrence}a).
+In all subsets, ICON is too humid in the first 1~km by about 5\% but very accurate above, except for the 40--55°S zone and conditions of weak stability (Fig.~\ref{fig:potential-temperature}b, g), where it is too dry between about 1 and 3~km.
+MERRA-2, on the other hand, is more humid than observations at all altitudes and in all subsets, by up to about 20\% at~5 km.
+Even though the mean near-surface relative humidity is similar to the observations (Fig.~\ref{fig:potential-temperature}), the distribution in observation is more spread out across both high and low values, and thus observations have a greater prevalence of relative humidity close to 100\% and thus LCL located at the surface (Fig.~\ref{fig:cloud-occurrence}a).
 In our calculations, LCL is an exclusive function of near-surface temperature, near-surface relative humidity, and surface pressure.
@@
 For these reasons, one can expect the results to be slightly different due to reasons unrelated to model biases, such as different weather conditions, partially accounted for by the cyclone and stability subsetting, and the phase of climate oscillations such as the ENSO in the observations and the model.
-The interannual variability in cloud occurrence in ICON can be seen in Fig.\ \ref{fig:cloud-occurrence-panel}, where each year in ICON is represented by a separate line.
+The interannual variability in cloud occurrence in ICON can be seen in Fig.~\ref{fig:cloud-occurrence-panel}, where each year in ICON is represented by a separate line.
 The interannual variability tends to be substantially smaller than the biases, and thus is unlikely to have a strong impact on the main findings.
@@
 Ground-based lidar observations can be regarded as superior to satellite lidar observations for low-level clouds, which are predominant in this region, while mid- and high-level clouds are better sampled by satellite observations \cite{mcerlich2021}.
-Near-surface lidar retrievals (~100 m) are affected by uncertainties related to incomplete overlap, signal saturation (dead time), and after-pulse effect corrections \cite{kuma2021}.
+Near-surface lidar retrievals ($\sim$100~m) are affected by uncertainties related to incomplete overlap, signal saturation (dead time), and after-pulse effect corrections \cite{kuma2021}.
 
-We have attempted to remove lidar profiles with precipitation, which could not be properly simulated with the lidar simulator (Section\ \ref{sec:ann}).
+We have attempted to remove lidar profiles with precipitation, which could not be properly simulated with the lidar simulator (Section~\ref{sec:ann}).
 However, the approach was limited by the relatively low sensitivity of the ANN (65\%) and the fact that we had to choose a fixed threshold for surface precipitation flux in the model and reanalyses, which might not correspond to detection by the ANN applied to observations.
@@
 The 31 voyages and a station show remarkably similar biases in cloud occurrence by height in the lidar comparison, which indicates that common underlying causes for the biases exist regardless of longitude and season.
-ICON underestimates the total cloud fraction by about 10\%, with an overestimation of clouds below 2 km and an underestimation of clouds above 2 km.
+ICON underestimates the total cloud fraction by about 10\%, with an overestimation of clouds below 2~km and an underestimation of clouds above 2~km.
 The reanalyses also underestimate the total cloud fraction by about 20\%.
-ERA5 overestimates cloud below 1 km but underestimates near-surface cloud or fog.
+ERA5 overestimates cloud below 1~km but underestimates near-surface cloud or fog.
 ICON strongly overestimates the peak of cloud occurrence at about 500 m, which might be explained by the radiosonde comparison, showing that it is too moist at around this height.
-Similar to our results, \citeA{cesana2022} showed that CMIP6 models also tend to underestimate cloud occurrence above 2 km over the SO, although their analysis in this case was limited to liquid clouds.
+Similar to our results, \citeA{cesana2022} showed that CMIP6 models also tend to underestimate cloud occurrence above 2~km over the SO, although their analysis in this case was limited to liquid clouds.
 
-Compared to lidar observations, the daily cloud cover tends to be about 1 okta lower in ICON and 2 oktas lower in the reanalyses.
+Compared to lidar observations, the daily cloud cover tends to be about 1~okta lower in ICON and 2~oktas lower in the reanalyses.
 Conditions of weak stability are associated with some of the greatest biases, especially in ERA5.
-The models also underestimate the cloud cover very strongly in cyclonic conditions, which are very cloudy in the observations (8 oktas), but much less so in the models.
+The models also underestimate the cloud cover very strongly in cyclonic conditions, which are very cloudy in the observations (8~oktas), but much less so in the models.
 Similarly, \citeA{mcerlich2023} found a 40\% underestimation of cloud liquid water in cyclones over the SO in ERA5, despite total column water vapor simulated much more accurately (5\% underestimation).
@@
 The data collection by the University of Canterbury was funded by the Deep South National Science Challenge Clouds and Aerosols project.
-Data collection on the AA15-16 voyages was funded by the Australian Antarctic Science project (grant no.
-4292).
+Data collection on the AA15-16 voyages was funded by the Australian Antarctic Science project (grant no.~4292).
 We acknowledge the contribution of Thorsten Mauritsen to funding acquisition and project management.

### 2024-12-12 manuscript_agu.tex
More improvements

@@
 
-\authors{Peter Kuma\affil{1,2}\thanks{}, Frida A.-M.
+\authors{Peter Kuma\affil{1,2,3}\thanks{}, Frida A.-M.
 Bender\affil{1,2}, Adrian J.
@@
 Cassano\affil{8,9,10}, Graeme E.
-Plank\affil{3}, Sean Hartery\affil{11}, Simon Parsons\affil{12}, Sally Garrett\affil{13}, and Alex J.
+Plank\affil{3}, Sean Hartery\affil{3}\thanks{Current affiliation: Department of Physics \& Atmospheric Science, Dalhousie University, Halifax, Canada}, Simon Parsons\affil{3}\thanks{Current affiliation: New South Wales Department of Planning and Environment, Sydney, New South Wales, Australia}, Sally Garrett\affil{11}, and Alex J.
 Schuddeboom\affil{3}}
@@
 \affiliation{10}{Department of Atmospheric and Oceanic Sciences, University of Colorado, Boulder, CO, USA}
-\affiliation{11}{Department of Physics \& Atmospheric Science, Dalhousie University, Halifax, Canada}
-\affiliation{12}{New South Wales Department of Planning and Environment, Sydney, New South Wales, Australia}
-\affiliation{13}{New Zealand Defence Force, Wellington, Aotearoa/New Zealand}
+\affiliation{11}{New Zealand Defence Force, Wellington, Aotearoa/New Zealand}
 
@@
 
-The RV \emph{Polarstern} datasets are openly available on Pangaea (\url{https://pangaea.de}).
+The RV \emph{Polarstern} datasets are openly available on Pangaea (\url{https://pangaea.de}), as listed in Table~\ref{tab:voyage-references}.
 The MARCUS and MICRE datasets are openly available from ARM (\url{https://www.arm.gov}).
@@
 The CERES products are openly available from the project website (\url{https://ceres.larc.nasa.gov}) and the NASA Atmospheric Science Data Centre (\url{https://asdc.larc.nasa.gov/project/CERES}).
-The TAN1802 data are openly available on Zenodo (\url{https://doi.org/10.5281/zenodo.4060237}).
+The TAN1802 data are openly available on Zenodo \cite{kremser2020}.
 The code for performing the presented analysis and precipitation detection is open-source and available at \url{https://github.com/peterkuma/icon-so-2024} and \url{https://github.com/peterkuma/alcf-precip}, respectively.
-The remaining voyage data are openly available on Zenodo (\url{https://doi.org/}).
+The remaining voyage data (AA15-16, HMNZSW16, NBP1704, TAN1502, and TAN1702) are openly available on Zenodo (\url{https://doi.org/}).
 

### 2024-12-12 manuscript_agu.tex
Dataset reference

@@
 After AVBC is calculated, a cloud mask, cloud occurrence by height, and the total cloud fraction are determined.
-The ALCF has been used by several research teams for model and reanalysis evaluation \cite{kuma2020,kremser2021,guyot2022,pei2023,whitehead2023,mcdonald2024}.
+The ALCF has been used by several research teams for model and reanalysis evaluation \cite{kuma2020,kremser2021,guyot2022,pei2023,whitehead2023,mcdonald2024a}.
 
@@
 The code for performing the presented analysis and precipitation detection is open-source and available at \url{https://github.com/peterkuma/icon-so-2024} and \url{https://github.com/peterkuma/alcf-precip}, respectively.
-The remaining voyage data (AA15-16, HMNZSW16, NBP1704, TAN1502, and TAN1702) are openly available on Zenodo (\url{https://doi.org/}).
+The remaining voyage data (AA15-16, HMNZSW16, NBP1704, TAN1502, and TAN1702) are openly available on Zenodo \cite{mcdonald2024b}.
 

### 2024-12-13 manuscript.tex
Update on Overleaf.

@@
 Global storm-resolving models (GSRMs) are the next avenue of climate modelling.
-Among them is a 5-km version of the Icosahedral Nonhydrostatic Weather and
-Climate Model (ICON). The high resolution means that parameterizations of
-convection and clouds including subgrid-scale clouds are forgone, relying on
-explicit their simulation, but still using microphysics and turbulence
-parametrization.  Standard-resolution (10--100-km) models, which use
+Among them is a 5-km horizontal resolution version of the Icosahedral Nonhydrostatic Weather and
+Climate Model (ICON). This high resolution means that parameterizations of
+convection and clouds including subgrid-scale clouds are not required, though microphysics and turbulence
+parametrizations are still needed.  Standard-resolution (10--100-km) models, which use
 subgrid-scale convection and cloud parametrization, have substantial cloud
-biases over the Southern Ocean (SO), affecting radiation and sea surface
+biases over the Southern Ocean (SO), adversely affecting radiation and sea surface
 temperature.  We evaluated SO clouds in ICON and the ERA5 and MERRA-2
@@
 cover, ICON and the reanalyses tend to be about 1 and 2 oktas clearer,
-respectively.  Conditions of weak stability are associated with the largest
-errors in ICON and the reanalyses.  Compared to radiosondes, potential
+respectively. The largest
+errors in ICON and the reanalyses occur during periods of weak stability.  Compared to radiosondes, potential
 temperature is accurate in the reanalyses to about 0.5 K, but ICON
-underestimates stability over the low-latitude SO and too humid in the boundary
+underestimates stability over the low-latitude SO and is too humid in the boundary
 layer. MERRA-2 is too humid at all heights. SO cloud biases remain a
@@
 
-Increasing climate model resolution is one way of improving model accuracy of
-representation of the climate system \citep{mauritsen2022}. It has been
+Increasing climate model resolution is one way of improving the accuracy of
+the representation of the climate system in models \citep{mauritsen2022}. It has been
 practiced since the advent of climate modelling as more computational power,
@@
 computational availability and acceleration from general-purpose computing on
-graphics processing units (GPUs) is progressing to enable km-scale (also called
+graphics processing units (GPUs) has progressed to enable km-scale (also called
 k-scale) Earth system models (ESMs) and coupled atmosphere--ocean general
-circulation models (AOGCMs) in research conditions today and operationally in
-the forthcoming years.  Therefore, it represents a natural advance in climate
+circulation models (AOGCMs) for research today and will become operational in
+the future. Therefore, it represents a natural advance in climate
 modelling. Global storm-resolving models (GSRMs) are emerging as a new front
 in the development of high-resolution global climate models, with horizontal
-grid resolutions of about 2--8 km \citep{satoh2019,stevens2019}. This is enough
+grid resolutions of about 2--8 km \citep{satoh2019,stevens2019}. This resolution is enough
 to resolve mesoscale convective storms, but smaller-scale convective plumes and
@@
 
-nextGEMS is a project \citep{nextgems} focused on the research and development
+The nextGEMS project \citep{nextgems} focuses on the research and development
 of GSRMs at multiple modelling centres and universities in Europe. The project
@@
 \citep{rintoul2011}, such as affecting the Earth radiation balance, ocean heat
-and carbon uptake \citep{williams2023}, and the SO is an important part of the
+and carbon uptake \citep{williams2023}, and the SO is also an important part of the
 global ocean conveyor belt \citep{wang2014}. In general, marine clouds have a
@@
 
-Here, we conventionally refer to the SO as ocean regions south of 40°S,
+Here, we refer to the SO as ocean regions south of 40°S,
 low-latitude SO as 40--55°S and high-latitude SO as south of 55°S. The reason
 for this dividing latitude is to split the SO into about two equal zones, as
-well as the results by \cite{schuddeboom2021} (Fig. 2b), showing a contrast in
-CMIP model radiation biases, \cite{schuddeboom2019} (Fig. 2) and
-\cite{kuma2020} (Fig. 3) showing contrasting radiation biases in the Hadley
-Centre Global Environmental Model, and \cite{cesana2022} showing contrasting
-cloud biases due to the 0°C isotherm reaching the surface at 55°S. The findings
+well as the results by \cite{schuddeboom2021} (Fig. 2b) which show a contrast in
+CMIP model radiation biases. \cite{schuddeboom2019} (Fig. 2) and
+\cite{kuma2020} (Fig. 3) also show contrasting radiation biases in the Hadley
+Centre Global Environmental Model, which is also supported by \cite{cesana2022} which  displays contrasting cloud biases due to the 0°C isotherm reaching the surface at 55°S. The findings
 of \cite{niu2024}, however, support a different dividing line of 62°S based on
@@
 \cite{zhao2022} reported a similar SW radiation bias in five analysed CMIP6
-models over high-latitude SO and the total cloud fraction underestimation on
+models over the high-latitude SO and an underestimation of total cloud fraction on
 the order of 10\% over the entire 40--60°S SO. Recently, \cite{ramadoss2024}
@@
 \cite{zhang2023} have shown that SST biases have improved in CMIP6 compared to
-CMIP5, with SST overall increasing in the later CMIP phase. However, over the
+CMIP5, with SST overall increasing in CMIP6. However, over the
 SO this resulted in an even higher positive bias, especially in the Atlantic
@@
 The main aim of this study is to evaluate the GSRM version of ICON. ICON
-developed and maintained jointly by Deutscher Wetterdienst,
+is developed and maintained jointly by Deutscher Wetterdienst,
 Max-Planck-Institute for Meteorology, Deutsches Klimarechenzentrum (DKRZ),
@@
 model clouds over the SO, affecting sea surface temperature and the Earth’s
-albedo. Our aim is to quantify how well the GSRM ICON is simulating clouds in
+albedo. Our aim is to quantify how well the GSRM ICON simulates clouds in
 this region, particularly in light of the fact that subgrid-scale clouds and
@@
 ground clutter \citep{marchand2008}, respectively.  Specifically, the radar on
-CloudSat and lidar on CALIPSO (neither of which are nowoperational) are
-affected by the abovementioned issues, resulting in a strong underestimation of
+CloudSat and lidar on CALIPSO (neither of which are now operational) are
+affected by the above mentioned issues, resulting in a strong underestimation of
 cloud occurrence below 2 km relative to ground-based lidar observations
@@
 set of ship-based observations conducted with ceilometers and lidars on board
-of the RV \emph{Polarstern} and other voyages and stations as a reference for
-the model evaluation.
+the RV \emph{Polarstern} and other voyages and stations as a reference for model evaluation.
 
@@
 south of 40°S between 2010 and 2021. Fig. \ref{fig:map} shows a map of the
-voyages, Table \ref{tab:voyages} list the voyages, campaigns, and stations, and
+voyages, Table \ref{tab:voyages} lists the voyages, campaigns, and stations, and
 Table \ref{tab:voyage-references} lists references where available. Altogether,
@@
 about 2.37 s for CL51 with CL31 emulation on TAN1502. The wavelengths of 905
-and 910 nm are affected by water vapour absorption of about 20\% in the
+and 910 nm are both affected by water vapour absorption of about 20\% in the
 mid-latitudes \citep{wiegner2015,wiegner2019}, with 910 nm affected more
@@
 An example of attenuated volume backscattering coefficient (AVBC) \textbf{(a)}
-measured by CL51 during 24 hours on the PS81/3 voyage and \textbf{(b)} an
+measured by a CL51 during 24 hours on the PS81/3 voyage and \textbf{(b)} an
 equivalent AVBC simulated with the ALCF from ERA5 data during the same time
@@
 instruments and models \citep{kuma2021}. It performs radiative transfer
-calculations to derive equivalent lidar AVBC in an atmospheric model, which can
+calculations to derive equivalent lidar AVBC from an atmospheric model, which can
 then be compared with observed AVBC. For this purpose, it takes the cloud
@@
 A coupled (atmosphere--ocean) GSRM version of the ICON model is in development
-at the nextGEMS project \citep{hohenegger2023}. ICON is an exceptionally
+as part of the nextGEMS project \citep{hohenegger2023}. ICON is an exceptionally
 versatile model, allowing for simulations ranging from coarse-resolution ESM
@@
 
-ERA5 \citep{era5} is a reanalysis produced by the ECMWF.  It is based on a
+ERA5 \citep{era5} is a reanalysis produced by ECMWF.  It is based on a
 numerical weather prediction model IFS version CY41R2. It uses the
@@
 clouds by the threshold-based cloud detection method used in the ALCF. This is
-undesirable if equivalent precipitation backscatter is not included in the
-simulated lidar profiles. It was not possible to include precipitation
-simulation in the ALCF due to the absence of required fields in the ICON model
+undesirable as equivalent precipitation backscatter is not included in the
+simulated lidar profiles due to the absence of required fields in the ICON model
 output and the reanalysis data (the liquid and ice precipitation mass mixing
 ratios). The required radiation calculations for precipitation are also
-currently not implemented in the ALCF, even though this is a planned future
+currently not implemented in the ALCF, but are a planned future
 addition.  In order to achieve a fair comparison of observations with model
@@
 
-On the RV \emph{Polarstern} voyages, regular human-performed synoptic
+On the RV \emph{Polarstern} voyages, regular manual synoptic
 observations were available and included precipitation presence or absence and
 type. We used this dataset to train a convolutional artificial neural network
-(ANN) to recognise profiles with precipitation from lidar backscatter (Fig.
+(ANN) to recognise profiles with precipitation from lidar backscatter data (Fig.
 \ref{fig:ann}a), implemented in the TensorFlow ANN framework
@@
 relatively arbitrary due to the very large variability of ECs \citep{neu2013}.
-We used the mean sea level pressure field and horizontal wind speed fields as
-input to the CyTRACK algorithm. The algorithm uses pressure and wind speed
+The CyTRACK algorithm uses mean sea level pressure and wind speed
 thresholds as well as tracking across time steps to identify cyclone centres
@@
 large-scale pressure and wind fields in ERA5 are likely sufficiently close to
-reality. For identifying cyclones in ICON, its own pressure and wind fields
+reality \cite{mcerlich2023}. For identifying cyclones in ICON, its own pressure and wind fields
 were used as the input to CyTRACK, because the model is free-running, and thus

### 2024-12-13 manuscript_agu.tex
Update on Overleaf.

@@
 One of them is a 5-km Icosahedral Nonhydrostatic Weather and Climate Model (ICON).
-The high resolution means that parameterizations of convection and clouds, including subgrid-scale clouds, are omitted, relying on explicit simulation but still utilizing microphysics and turbulence parameterizations.
-Standard-resolution (10--100~km) models, which use convection and cloud parameterizations, have substantial cloud biases over the Southern Ocean (SO), affecting radiation and sea surface temperature.
+Its high resolution means that parameterizations of convection and clouds, including subgrid-scale clouds, are omitted, relying on explicit simulation but still utilizing microphysics and turbulence parameterizations.
+Standard-resolution (10--100~km) models, which use convection and cloud parameterizations, have substantial cloud biases over the Southern Ocean (SO), adversely affecting radiation and sea surface temperature.
 The SO is dominated by low clouds, which cannot be observed accurately from space due to overlapping clouds, attenuation, and ground clutter.
-We evaluated SO clouds in ICON and the ERA5 and MERRA-2 reanalyses using about 2400 days of lidar observations and 2300 radiosonde profiles from 31 voyages and a station during 2010--2021, compared with the models using a ground-based lidar simulator.
+We evaluated SO clouds in ICON and the ERA5 and MERRA-2 reanalyses using about 2400 days of lidar observations and 2300 radiosonde profiles from 31 voyages and Macquarie Island station during 2010--2021, compared with the models using a ground-based lidar simulator.
 We found that ICON and the reanalyses underestimate the total cloud fraction by about 10 and 20\%, respectively.
@@
 
-Increasing climate model resolution is one way of improving model accuracy of representation of the climate system \cite{mauritsen2022}.
+Increasing climate model resolution is one way of improving the accuracy of the representation of the climate system in models \cite{mauritsen2022}.
 It has been practiced since the advent of climate modeling as more computational power, memory, and storage capacity become available.
@@
 Increasing resolution is, of course, limited by the available computational power and a trade-off with increasing parameterization complexity, which is another way of improving model accuracy.
-Current computational availability and acceleration from general-purpose computing on graphics processing units (GPUs) is progressing to enable km-scale (also called k-scale) Earth system models (ESMs) and coupled atmosphere--ocean general circulation models (AOGCMs) in research conditions today and operationally in the forthcoming years.
+Current computational availability and acceleration from general-purpose computing on graphics processing units (GPUs) has progressed to enable km-scale (also called k-scale) Earth system models (ESMs) and coupled atmosphere--ocean general circulation models (AOGCMs) for research today and will become operational in the future.
 Therefore, it represents a natural advance in climate modeling.
 Global storm-resolving models (GSRMs) are emerging as a new front in the development of high-resolution global climate models, with horizontal grid resolutions of about 2--8~km \cite{satoh2019,stevens2019}.
-This is enough to resolve mesoscale convective storms, but smaller-scale convective plumes and cloud structure remain unresolved.
+This resolution is enough to resolve mesoscale convective storms, but smaller-scale convective plumes and cloud structure remain unresolved.
 At an approximately 5-km scale, non-hydrostatic processes also become important \cite{weisman1997}, and for this reason such models are generally non-hydrostatic.
@@
 
-nextGEMS is a project \cite{nextgems} focused on the research and development of GSRMs at multiple modeling centers and universities in Europe.
+The nextGEMS project \cite{nextgems} focuses on the research and development of GSRMs at multiple modeling centers and universities in Europe.
 The project also develops GSRM versions of the Icosahedral Nonhydrostatic Weather and Climate Model (ICON; \citeA{hohenegger2023}), the Integrated Forecasting System [IFS; \citeA{ifs2023}], and their ocean components at eddy-resolving resolutions: ICON-O \cite{korn2022} coupled with ICON and Finite-Element/volumE Sea ice-Ocean Model [FESOM; \citeA{wang2014a}] and Nucleus for European modeling of the Ocean [NEMO; \citeA{madec2023}] coupled with IFS.
@@
 The Southern Ocean (SO) is known to be a problematic region for climate model biases \cite{schuddeboom2021,hyder2018,cesana2022,zhao2022} due to a lack of surface and in situ observations and being a lower priority region for numerical weather prediction (NWP) and climate model development because of its distance from populated areas.
-Nevertheless, radiation biases and changes over an area of its size have a substantial influence on the global climate \cite{rintoul2011}, such as affecting the Earth radiation balance, ocean heat, and carbon uptake \cite{williams2023}, and the SO is an important part of the global ocean conveyor belt \cite{wang2014b}.
+Nevertheless, radiation biases and changes over an area of its size have a substantial influence on the global climate \cite{rintoul2011}, such as affecting the Earth radiation balance, ocean heat, and carbon uptake \cite{williams2023}, and the SO is also an important part of the global ocean conveyor belt \cite{wang2014b}.
 In general, marine clouds have a disproportionate effect on top of atmosphere (TOA) SW radiation due to the relatively low albedo of the sea surface.
@@
 
-Here, we conventionally refer to the SO as ocean regions south of 40°S, low-latitude SO as 40--55°S and high-latitude SO as south of 55°S.
-The reason for this dividing latitude is to split the SO into about two equal zones, as well as the results by \citeA{schuddeboom2021} (Fig.~2b), showing a contrast in CMIP model radiation biases, \citeA{schuddeboom2019} (Fig.~2) and \citeA{kuma2020} (Fig.~3) showing contrasting radiation biases in the Hadley Centre Global Environmental Model, and \citeA{cesana2022} showing contrasting cloud biases due to the 0°C isotherm reaching the surface at 55°S.
+Here, we refer to the SO as ocean regions south of 40°S, low-latitude SO as 40--55°S and high-latitude SO as south of 55°S.
+The reason for this dividing latitude is to split the SO into about two equal zones, as well as the results by \citeA{schuddeboom2021} (Fig.~2b) which show a contrast in CMIP model radiation biases.
+\citeA{schuddeboom2019} (Fig.~2) and \citeA{kuma2020} (Fig.~3) also show contrasting radiation biases in the Hadley Centre Global Environmental Model, which is also supported by \citeA{cesana2022} which displays contrasting cloud biases due to the 0°C isotherm reaching the surface at 55°S.
 The findings of \citeA{niu2024}, however, support a different dividing line of 62°S based on cloud condensation nuclei concentration.
@@
 \citeA{possner2022} showed that over the SO, the DYAMOND GSRM ICON underestimates low-level cloud fraction on the order of 30\% and overestimates net downward TOA SW radiation by approximately 10 Wm$^\mathrm{-2}$ in the highest model resolution run (2.5~km).
-\citeA{zhao2022} reported a similar SW radiation bias in five analyzed CMIP6 models over high-latitude SO and the total cloud fraction underestimation on the order of 10\% over the entire 40--60°S SO.
+\citeA{zhao2022} reported a similar SW radiation bias in five analyzed CMIP6 models over the high-latitude SO and an underestimation of the total cloud fraction  on the order of 10\% over the entire 40--60°S SO.
 Recently, \citeA{ramadoss2024} analyzed 48~hours of km-scale ICON limited-area model NWP simulations over a SO region adjacent to Tasmania against the Clouds, Aerosols, Precipitation, Radiation, and atmospherIc Composition Over the southeRn oceaN (CAPRICORN) voyage cloud and precipitation observations \cite{mcfarquhar2021}.
@@
 Interactions of both are also possible, for example, SST affecting clouds and clouds affecting the surface radiation.
-Using the European Centre for Medium-Range Weather Forecasts (ECMWF) Reanalysis 5 (ERA5) as a reference, \citeA{zhang2023} have shown that SST biases have improved in CMIP6 compared to CMIP5, with SST overall increasing in the later CMIP phase.
+Using the European Centre for Medium-Range Weather Forecasts (ECMWF) Reanalysis 5 (ERA5) as a reference, \citeA{zhang2023} have shown that SST biases have improved in CMIP6 compared to CMIP5, with SST overall increasing in CMIP6.
 However, over the SO this resulted in an even higher positive bias, especially in the Atlantic Ocean (AO) sector of the SO, increasing by up to 1°C.
@@
 Previous studies have identified substantial large-scale biases in climate model clouds over the SO, affecting sea surface temperature and the Earth’s albedo.
-Our aim is to quantify how well the GSRM ICON is simulating clouds in this region, particularly in light of the fact that subgrid-scale clouds and convection are not parameterized in this model.
+Our aim is to quantify how well the GSRM ICON simulates clouds in this region, particularly in light of the fact that subgrid-scale clouds and convection are not parameterized in this model.
 This region is mostly dominated by boundary layer clouds generated by shallow convection, and these are problematic to observe by spaceborne lidars and radars, which are affected by attenuation by overlapping and thick clouds \cite{mace2009,medeiros2010} and ground clutter \cite{marchand2008}, respectively.
-Specifically, the radar on CloudSat and lidar on CALIPSO (neither of which are now operational) are affected by the abovementioned issues, resulting in a strong underestimation of cloud occurrence below 2 km relative to ground-based lidar observations \cite{mcerlich2021}.
+Specifically, the radar on CloudSat and lidar on CALIPSO (neither of which are now operational) are affected by the above mentioned issues, resulting in a strong underestimation of cloud occurrence below 2 km relative to ground-based lidar observations \cite{mcerlich2021}.
 We hypothesize that this, in turn, can lead to systematic biases in low clouds in climate models, which are frequently evaluated against CloudSat--CALIPSO products.
@@
 The sampling (temporal) resolution is configurable, and in our datasets, it is approximately 6~s for CL51 on AA15‐16, 16~s for CT25K on MARCUS and MICRE, 36~s for CL51 on RV \emph{Polarstern}, and about 2.37~s for CL51 with CL31 emulation on TAN1502.
-The wavelengths of 905 and 910~nm are affected by water vapor absorption of about 20\% in the mid-latitudes \cite{wiegner2015,wiegner2019}, with 910~nm affected more strongly, but we do not expect this to be a significant issue as explained in \citeA{kuma2021}.
+The wavelengths of 905 and 910~nm are both affected by water vapor absorption of about 20\% in the mid-latitudes \cite{wiegner2015,wiegner2019}, with 910~nm affected more strongly, but we do not expect this to be a significant issue as explained in \citeA{kuma2021}.
 The instrument data files containing raw uncalibrated backscatter were first converted to Network Common Data Form (NetCDF) with cl2nc (\url{https://github.com/peterkuma/cl2nc}) and then processed with the ALCF (Section~\ref{sec:alcf}) to produce absolutely calibrated attenuated volume backscattering coefficient (AVBC), cloud mask, cloud occurrence by height, and the total cloud fraction.
@@
 \caption{
-An example of the attenuated volume backscattering coefficient (AVBC) \textbf{(a)} measured by CL51 during 24~hours on the PS81/3 voyage and \textbf{(b)} an equivalent AVBC simulated with the ALCF from ERA5 data during the same time period.
+An example of the attenuated volume backscattering coefficient (AVBC) \textbf{(a)} measured by the CL51 during 24~hours on the PS81/3 voyage and \textbf{(b)} an equivalent AVBC simulated with the ALCF from ERA5 data during the same time period.
 The red line identifies the cloud mask determined by the ALCF.
@@
 
-The Lufft CHM~15k (photo in Fig.~\ref{fig:map}c) is a ceilometer operating at a near-infrared wavelength of 1064~nm.
+The Lufft CHM~15k (photo in Fig.~\ref{fig:map}c) ceilometer operates at a near-infrared wavelength of 1064~nm.
 The maximum range is 15.4~km; the vertical resolution is 5~m in the near range (up to 150~m) and 15~m above; the sampling (temporal) resolution is 2~s; and the number of vertical levels is 1024.
@@
 The Automatic Lidar and Ceilometer Framework (ALCF) is a ground-based lidar simulator and a tool for processing observed lidar data, supporting various instruments and models \cite{kuma2021}.
-It performs radiative transfer calculations to derive equivalent lidar AVBC in an atmospheric model, which can then be compared with observed AVBC.
+It performs radiative transfer calculations to derive equivalent lidar AVBC from an atmospheric model, which can then be compared with observed AVBC.
 For this purpose, it takes the cloud fraction, liquid and ice mass mixing ratio, temperature, and pressure model fields as an input and is run offline (on the model output rather than inside the model code).
@@
 
-A coupled (atmosphere--ocean) GSRM version of the ICON model is in development at the nextGEMS project \cite{hohenegger2023}.
+A coupled (atmosphere--ocean) GSRM version of the ICON model is in development as part of the nextGEMS project \cite{hohenegger2023}.
 ICON is an exceptionally versatile model, allowing for simulations ranging from coarse-resolution ESM simulations, GSRM simulations, limited area model simulations, to large eddy simulations (LES), for both weather prediction and climate projections.
@@
 We used a Cycle 3 run \emph{ngc3028} produced in 2023 \cite{nextgems2023a,nextgems2023b} for a model time period of 20 January 2020 to 22 July 2025, of which we analyzed the period 2021--2024 (inclusive).
-While a Cycle 4 run was available, we could not use it due to a lack of availability of the necessary variables.
 The horizontal resolution of ngc3028 is about 5 km.
@@
 Artificial neural network (ANN) for prediction of precipitation in lidar backscatter.
-\textbf{(a)} Diagram showing the TensorFlow structure of the ANN, \textbf{(b)} randomly selected example samples of near-surface backscatter in four categories (clear, fog, rain, and snow), as determined by coincident human-performed weather observations, \textbf{(c)} receiver operating characteristic diagram of the ANN, \textbf{(d)} examples of 10-day time series of human-observed (``HUM'') and predicted precipitation based on an ANN trained on all voyages (``ANN'') and all voyages except for the shown voyage (``ANN2'') during three randomly selected voyages with the available data.
+\textbf{(a)} Diagram showing the TensorFlow structure of the ANN, \textbf{(b)} randomly selected example samples of near-surface backscatter in four categories (clear, fog, rain, and snow), as determined by coincident manual weather observations, \textbf{(c)} receiver operating characteristic diagram of the ANN, \textbf{(d)} examples of 10-day time series of human-observed (``HUM'') and predicted precipitation based on an ANN trained on all voyages (``ANN'') and all voyages except for the shown voyage (``ANN2'') during three randomly selected voyages with the available data.
 Here, by ``randomly selected,'' we mean selected from the top of a permutation generated by a pseudo-random number generator to prevent authors' bias in the selection.
@@
 
-On the RV \emph{Polarstern} voyages, regular human-performed synoptic observations were available and included precipitation presence or absence and type.
-We used this dataset to train a convolutional artificial neural network (ANN) to recognize profiles with precipitation from lidar backscatter (Fig.~\ref{fig:ann}a), implemented in the TensorFlow ANN framework \cite{tensorflow}.
+On the RV \emph{Polarstern} voyages, regular manual synoptic observations were available and included precipitation presence or absence and type.
+We used this dataset to train a convolutional artificial neural network (ANN) to recognize profiles with precipitation from lidar backscatter data (Fig.~\ref{fig:ann}a), implemented in the TensorFlow ANN framework \cite{tensorflow}.
 Samples of short time intervals (10~min) of near-surface lidar backscatter (0–250 m) were classified as clear, rain, snow, and fog, using the synoptic observations as a training dataset (Fig.~\ref{fig:ann}b).
@@
 Fig.~\ref{fig:ann}d shows examples of the predicted precipitation compared to human-performed observations.
-The main ANN (`ANN` in Fig.~\ref{fig:ann}) was trained on all data, and ancillary ANNs (`ANN2` in Fig.~\ref{fig:ann}) were trained on all data except for each voyage.
-These were used for testing the results relative to each voyage.
+The main ANN (`ANN` in Fig.~\ref{fig:ann}) was trained on all data, and ancillary ANNs (`ANN2` in Fig.~\ref{fig:ann}) were trained with portions of voyage data excluded to test the results for each voyage.
 
@@
 Generally, what constitutes an EC is considered relatively arbitrary due to the very large variability of ECs \cite{neu2013}.
-We used the mean sea level pressure field and horizontal wind speed fields as input to the CyTRACK algorithm.
-The algorithm uses pressure and wind speed thresholds as well as tracking across time steps to identify cyclone centers and radii in each time step.
+The CyTRACK algorithm uses mean sea level pressure and wind speed thresholds as well as tracking across time steps to identify cyclone centers and radii in each time step.
 With this information, we could classify geographical areas as either cyclonic or non-cyclonic.
-Due to a relatively small total area covered by cyclones (as identified by the cyclone center and radius), we chose a circle of a double radius (relative to one identified by CyTRACK) centered at the cyclone center as a cyclonic area for every time step and cyclone.
+Due to a relatively small total area covered by cyclones (as identified by the cyclone center and radius), we chose a circle of double the radius (relative to one identified by CyTRACK) centered at the cyclone center as a cyclonic area for every time step and cyclone.
 All other areas were identified as non-cyclonic.
@@
 Subsetting by proximity to cyclones is a relatively crude measure because it does not take into account the different sectors of cyclones, which are commonly associated with different weather situations.
-However, this was a choice made for simplicity of the analysis, given the amount of data.
+However, this was a choice made for simplicity of the analysis, given the quantity of data.
 
@@
 
-Fig.~\ref{fig:cyclone-stability}a, b show a geographical distribution of the fraction of cyclonic days as determined by the cyclone tracking algorithm applied to the ERA5 reanalysis and ICON data (Section~\ref{sec:cyclone-stability}).
-As expected, the strongest cyclonic activity is in the high-latitude SO zone, and it is relatively zonally symmetric at all latitudes.
+Fig.~\ref{fig:cyclone-stability}a, b show the geographical distribution of the fraction of cyclonic days as determined by the cyclone tracking algorithm applied to the ERA5 reanalysis and ICON data (Section~\ref{sec:cyclone-stability}).
+As expected, the strongest cyclonic activity is in the high-latitude SO zone, and is relatively zonally symmetric at all latitudes.
 The pattern matches reasonably well with \citeA{hoskins2005}.
 While both reanalysis and the model agree within about 8\% in most areas, ICON is prevailingly more cyclonic by about 4\%.
-There are clear differences, particularly in the highest occurrence rate regions, such as around Cape Adare, which is by up to 20\% more cyclonic in ICON, and the Weddell and Bellingshausen Seas, where ICON is less cyclonic by up to 10\%.
+There are clear differences, particularly in the highest occurrence rate regions, such as around Cape Adare, which is up to 20\% more cyclonic in ICON, and the Weddell and Bellingshausen Seas, where ICON is less cyclonic by up to 10\%.
 These differences might, however, stem from the relatively short time periods of comparison (4 years) and the fact that the model is free-running.
 
-Fig.~\ref{fig:cyclone-stability}c, d show a geographical distribution of the conditions of weak and strong stability as determined by the LTS (Section~\ref{sec:cyclone-stability}).
+Fig.~\ref{fig:cyclone-stability}c, d show the geographical distribution of the conditions of weak and strong stability as determined by the LTS (Section~\ref{sec:cyclone-stability}).
 Conditions of weak stability are prevalent in the mid-to-high SO (with respect to our SO partitioning; 50--65°S), which might be explained by the relatively cold near-surface air overlying the relatively warm sea surface.
@@
 In addition, we aggregated the campaigns by calculating the averages and percentiles of all individual profiles, presented in Fig.~\ref{fig:cloud-occurrence}.
-The analysis shows that the total cloud fraction (determined as the fraction of profiles with clouds at any height in the lidar cloud mask) is underestimated in ICON by about 10\% and in the reanalyses by about 20\%.
-When analyzed by height, ICON overestimates cloud occurrence below 1 km and underestimates it above; MERRA-2 underestimates cloud occurrence at all heights by up to about 10\%, especially near the surface; and ERA5 simulates cloud occurrence relatively well above 1 km but strongly underestimates it near the surface.
+The analysis shows that the total cloud fraction (defined as the fraction of profiles with clouds at any height in the lidar cloud mask) is underestimated in ICON by about 10\% and in the reanalyses by about 20\%.
+When analyzed by height, ICON overestimates cloud occurrence below 1 km and underestimates it above; MERRA-2 underestimates cloud occurrence at all heights by up to 10\%, especially near the surface; and ERA5 simulates cloud occurrence relatively well above 1 km but strongly underestimates it near the surface.
 We note that fog or near-surface clouds are strongly underestimated in the reanalyses (fog and clouds are both included in the cloud occurrence).
 As shown in Fig.~\ref{fig:cloud-occurrence-panel}, the biases are relatively consistent across the campaigns and longitudes.
-We conclude that the ICON results the observations better than the reanalyses in this metric.
+We conclude that the ICON results match the observations better than the reanalyses in this metric.
 
 For all observations considered (Fig.~\ref{fig:cloud-occurrence}a), the data show cloud occurrence peaking nearly at the surface, whereas the models show a higher peak (at about 500~m).
-The models generally underestimate the total cloud fraction by 10--20\% and show a strong reduction in cloud occurrence near the surface, which is not supported by the observations.
+The models generally underestimate the total cloud fraction by 10--20\% and show a strong reduction in cloud occurrence near the surface, which is not identified in the observations.
 ICON and ERA5 overestimate cloud occurrence at their peak (between 0--1~km).
 Above 1~km, ICON and MERRA-2 underestimate cloud occurrence, but ERA5 is accurate to about 3\% or less.
-The exaggerated peak in models is partly supported by the lifting condensation level (LCL) distribution, which peaks higher by about 200~m in the models than in the observations (nearly at the surface), although this is not very pronounced.
+The exaggerated peak in models is partly explained by the lifting condensation level (LCL) distribution, which peaks about 200~m higher in the models than in the observations (nearly at the surface), although this is not very pronounced.
 This is indicative of near-surface relative humidity being often close to saturation in the observations but not in the models.
@@
 When subsetted by cyclonic and non-cyclonic situations (Fig.~\ref{fig:cloud-occurrence}d, e), we see that the cyclonic situations have a larger amount of observed cloudiness, including peak and total cloud fraction, both by about 7\%.
-In the cyclonic situations, the model vertical profiles of cloud occurrence compare well with observations, but they peak higher by about 200 m and stronger by about 8\%.
+In the cyclonic situations, the model vertical profiles of cloud occurrence compare well with observations, but they peak higher by about 200 m and larger by about 8\%.
 The reanalyses still tend to underestimate cloud occurrence above 1 km by about 5\% and near the surface by about 14\%.
@@
 
-When subsetted by conditions of weak and strong stability (Fig.~\ref{fig:cloud-occurrence}f, g), as defined in Section~\ref{sec:cyclone-stability}, we see that in situations of strong stability, cloud occurrence peaks strongly nearly at the surface in observations, compared to situations of weak stability, where the peak is more diffuse between 0 and 1~km.
+When subsetted by conditions of weak and strong stability (Fig.~\ref{fig:cloud-occurrence}f, g), as defined in Section~\ref{sec:cyclone-stability}, we see that in situations of strong stability, cloud occurrence peaks strongly near the surface in observations, compared to situations of weak stability, where the peak is more diffuse between 0 and 1~km.
 It is worth mentioning that conditions of strong stability might be associated with the formation of advection fog, such as in situations of warm air advection from the north over a colder sea surface, thus inducing fog formation by cooling of the warm and humid air by the cold surface.
 In situations of strong stability, the models have smaller biases than in weak stability, with an overestimated peak by up to 12\%, underestimated cloud occurrence above 1~km by up to 5\%, and underestimated cloud occurrence near the surface by about 11\%.
-In situations of weak stability, the bias in ICON is very pronounced, with a much stronger peak at about 500~m; ERA5 underestimates cloud occurrence below 1~km (especially near the surface); and MERRA-2 underestimates cloud occurrence even more strongly.
+In situations of weak stability, the bias in ICON is very pronounced, with a much larger peak in cloud occurrence at about 500~m; ERA5 underestimates cloud occurrence below 1~km (especially near the surface); and MERRA-2 underestimates cloud occurrence even more strongly.
 
@@
 ICON can be generally characterized as substantially overestimating cloud occurrence below 1 km and underestimating above, underestimating the total cloud fraction, and showing the greatest biases in conditions of weak stability and non-cyclonic conditions.
-It also shows a peak of cloud occurrence at higher altitudes than observations (500~m vs.
+ICON also has a peak cloud occurrence at higher altitudes than observations (500~m vs.
 near the surface), and correspondingly, its LCL tends to be higher.
@@
 MERRA-2 displays the largest errors relative to observations in the low-latitude SO zone and in situations of weak stability.
-ERA5 can be generally characterized as representing cloud occurrence correctly above about 1--1.5~km, overestimating below, but underestimating near-surface cloud occurrence (0--500~m).
+ERA5 can be generally characterized as representing cloud occurrence correctly above about 1--1.5~km, overestimating between 500m and 1km, but underestimating near-surface cloud occurrence (0--500~m).
 The total cloud fraction is strongly underestimated in all situations.
@@
 
-In Fig.~\ref{fig:cloud-occurrence}, we also show outgoing shortwave and longwave top of atmosphere radiation.
+In Fig.~\ref{fig:cloud-occurrence}, we also display the mean outgoing shortwave and longwave top of atmosphere radiation.
 In observations, these come from daily mean CERES measurements averaged over the voyage tracks or a station location, whereas in the models they come from daily means of TOA radiation in the model output averaged over the same location and time periods.
@@
 
-In the general case (Fig.~\ref{fig:cloud-occurrence}a), ICON underestimates the outgoing SW radiation by 26 Wm$^{-2}$ and the reanalyses MERRA-2 and ERA5 are much closer but overestimate it by 6 and 14 Wm$^{-2}$, respectively.
-While in ICON, this is in line with the underestimated total cloud fraction by 10\%, in the reanalyses this is the opposite result as expected from the underestimated total cloud fraction by about 20\%.
+In the general case (Fig.~\ref{fig:cloud-occurrence}a), ICON underestimates the outgoing SW radiation by 26 Wm$^{-2}$ and the MERRA-2 and ERA5 reanalyses overestimate it by 6 and 14 Wm$^{-2}$, respectively.
+While in ICON, this is in line with the underestimated total cloud fraction of 10\%, in the reanalyses this is the opposite result to that expected from the underestimated total cloud fraction of about 20\%.
 The likely explanation is an overestimated cloud albedo, compensating for the lack of cloud area.
+We note that the the radiative transfer calculations used in the lidar simulator mean that the impact of both cloud phase and cloud fraction are convolved which may help explain this result.
 
-In contrast, LW radiation is affected by much smaller biases than SW radiation, which is expected due to the prevailing low-level clouds having similar temperature as the surface.
+In contrast, LW radiation has much smaller biases than SW radiation, which is expected due to the prevailing low-level clouds having similar temperature as the surface.
 In ICON, the outgoing LW radiation is overestimated by 8\%, which could be caused by an underestimated total cloud fraction exposing a larger sea surface area to cooling to space, which is typically warmer than the atmospheric temperature at 0--2~km, where most of the clouds are located.
-In the MERRA-2 and ERA5 reanalyses, the LW biases are also slightly positive by 4 and 7~Wm$^{-2}$.
+In the MERRA-2 and ERA5 reanalyses, the LW biases are also slightly positive 4 and 7~Wm$^{-2}$, respectively.
 This is again in line with the underestimated total cloud fraction by about 20\%.
@@
 
-In all the subsets (Fig.~\ref{fig:cloud-occurrence}b--g), the same type of bias is present as in the general case -- the outgoing SW radiation is underestimated in ICON and overestimated in MERRA-2 and ERA5, and the outgoing LW radiation is overestimated in all the models.
+In all the subsets (Fig.~\ref{fig:cloud-occurrence}b--g), the same type biases are observed, namely the outgoing SW radiation is underestimated in ICON and overestimated in MERRA-2 and ERA5, and the outgoing LW radiation is overestimated in all the models.
 Even though the total cloud fraction is lower by 7\% over the high-latitude SO than the low-latitude SO, the outgoing SW radiation is much greater by 41~Wm$^{-2}$, implying a much greater cloud albedo over the high-latitude SO.
-ICON has the same contrast between these two regions in the total cloud fraction and SW radiation, but the outgoing SW radiation difference between the regions is much smaller (16~Wm$^{-2}$).
+ICON model output displays the same contrast between these two regions in the total cloud fraction and SW radiation, but the outgoing SW radiation difference between the regions is much smaller (16~Wm$^{-2}$).
 The reanalyses do not show this type of contrast between the regions.
@@
 This is a measure of cloudiness, irrespective of height, calculated over the course of a day (UTC).
-A cloud detected at any height means that the lidar profile was classified as cloudy; otherwise, it was classified as a clear sky.
+A cloud detected at any height means that the lidar profile was classified as cloudy; otherwise, it was classified as clear sky.
 When all profiles in a day are taken together, the cloud cover for the day is defined as the fraction of cloudy profiles in the total number of profiles, expressed in oktas (multiples of 1/8).
@@
 
-In order to link the cloud biases to the local physical conditions, we analyzed about 2300 radiosonde profiles south of 40°S from the 24 RV \emph{Polarstern} voyages, MARCUS, NBP1704, TAN1702, and TAN1802.
+In order to examine the potential link in the cloud biases to the local physical conditions, we analyzed about 2300 radiosonde profiles south of 40°S from the 24 RV \emph{Polarstern} voyages, MARCUS, NBP1704, TAN1702, and TAN1802.
 Spatially and temporally colocated profiles were taken from ICON and the reanalyses.
@@
 The profiles were partitioned into the same subsets as above (Sections~\ref{sec:cloud-occurrence} and \ref{sec:cloud-cover}).
-Apart from relative humidity, we focus on comparing virtual potential temperature ($\theta_v$) due to its role in low-level tropospheric stability, being one of the primary factors affecting shallow convection and the associated low-level cloud formation and dissipation.
+We focus on comparing virtual potential temperature ($\theta_v$) due to its role in low-level tropospheric stability, being one of the primary factors affecting shallow convection and the associated low-level cloud formation and dissipation.
 The observed and model profiles of virtual potential temperature are shown in Fig.~\ref{fig:potential-temperature}.
 
-Overall, the mean $\theta_v$ is accurate to less than 0.5~K in ICON and MERRA-2, except for ICON being colder by up to 2.5~K in the mid-to-high troposphere (less stable) (Fig.~\ref{fig:potential-temperature}a).
+Overall, the mean $\theta_v$ is accurate to within 0.5~K in ICON and MERRA-2, except for ICON being colder by up to 2.5~K in the mid-to-high troposphere (less stable) (Fig.~\ref{fig:potential-temperature}a).
 Larger differences exist, however, in the 40--55°S zone, where ICON is colder by about 5 K at higher altitudes (Fig.~\ref{fig:potential-temperature}b).
 In other subsets, the bias is relatively small.
-MERRA-2 is very close to the observations, possibly due to a high accuracy of assimilation of this quantity.
+MERRA-2 and ERA5 are very close to the observations, possibly due to a high accuracy of assimilation of this quantity.
 Notably, the variability of virtual potential temperature (as represented by the percentiles) is much smaller in ICON than in the observations.
@@
 Ground-based lidar observations are affected by attenuation by thick cloud layers, and for this reason the results are most representative of boundary layer clouds, while higher-level clouds are only occasionally visible to the lidar when boundary layer clouds are not present.
-Ground-based lidar observations can be regarded as superior to satellite lidar observations for low-level clouds, which are predominant in this region, while mid- and high-level clouds are better sampled by satellite observations \cite{mcerlich2021}.
+Ground-based lidar observations can be regarded as superior to satellite lidar observations for low-level clouds, which are predominant in this region, while mid- and high-level clouds are likely better sampled by satellite observations \cite{mcerlich2021}.
 Near-surface lidar retrievals ($\sim$100~m) are affected by uncertainties related to incomplete overlap, signal saturation (dead time), and after-pulse effect corrections \cite{kuma2021}.
@@
 However, the approach was limited by the relatively low sensitivity of the ANN (65\%) and the fact that we had to choose a fixed threshold for surface precipitation flux in the model and reanalyses, which might not correspond to detection by the ANN applied to observations.
-Also, we made no attempt to remove profiles with precipitation not reaching the surface.
-The above reasons may result in an artificial bias in the comparison, even though we expect this to be much smaller than the identified model biases.
+We also made no attempt to remove profiles with precipitation which did not reach the surface.
+The above reasons may result in an artificial bias in the comparison, though we expect this to be much smaller than the identified model biases.
 
@@
 
-We analyzed a total of about 2400 days of lidar and 2300 radiosonde observations from 31 voyages/campaigns and a subantarctic station, covering the Atlantic, Australian, and New Zealand sectors of the SO over the span of 10 years.
+We analyzed a total of about 2400 days of lidar and 2300 radiosonde observations from 31 voyages/campaigns and the Macquarie Island subantarctic station, covering the Atlantic, Australian, and New Zealand sectors of the SO over the span of 10 years.
 This dataset, together with the use of a ground-based lidar simulator, provided a comprehensive basis for evaluating SO cloud and thermodynamic profile biases in the GSRM ICON and the ERA5 and MERRA-2 reanalyses.
@@
 Our main finding corroborates previous findings of large boundary layer cloud biases in models and their subsequent effect on the radiative transfer.
-This also applies to the new GSRM ICON, but the biases are generally lower than in the reanalyses, despite the reanalyses having the advantage of assimilation of the observed meteorological conditions.
+For example, low- and mid-level clouds in the cold-air sector of cyclones were identified as being responsible for most of the SW bias in \cite{Bodas-Salcedoetal2012}.
+This understanding was refined in \cite{Bodas-Salcedoetal2014} which highlighted that the SW bias was associated with an incorrectly simulated mid-level cloud regime, which occurred in regions where cloud with tops at mid-level and low-levels occurred.
+Our results align less well with more recent work by \cite{ramadoss2024} which shows persistent shortwave radiative bias over the Southern Ocean are associated with incorrect cloud phase representation.
+While \cite{fiddes2024} suggest biases in the liquid water path are the largest contributor to the cloud radiative bias over the Southern Ocean.
+Our general finding applies to the new GSRM ICON, but the biases are generally lower than in the reanalyses, despite the reanalyses having the advantage of assimilation of the observed meteorological conditions.
 The GSRM has, on the other hand, the advantage of a much higher spatial resolution and, to a limited extent, explicit calculation of traditionally subgrid-scale processes such as convection.
@@
 The radiosonde observations indicate that the LCL is too high in ICON and reanalyses, which is probably responsible for the higher peak of clouds in the models and the lack of near-surface clouds or fog.
-The radiosonde comparison, however, does not seem to explain cloud biases at higher altitudes.
+The radiosonde comparison, however, does not seem to explain cloud biases at higher altitudes which is perhaps suggestive of biases in the influence of the liquid water path in teh models relative to the reality observed by the models.
 MERRA-2 is too moist at all heights.
@@
 The results imply that SO cloud biases are still a substantial issue even in the km-scale resolution ICON model, even though an improvement over the lower-resolution reanalyses is notable.
-More effort is needed to improve the model cloud simulations in this understudied region.
+More effort is therefore needed to improve the model cloud simulations in this understudied region.
 However, this analysis suggests that the transition from models with parameterized convection and clouds to storm-resolving models might not solve these biases without additional effort.

### 2024-12-13 manuscript_agu.tex
Update on Overleaf.

@@
 \subsection{CERES}
+\label{sec:ceres}
 
@@
 MERRA-2 displays the largest errors relative to observations in the low-latitude SO zone and in situations of weak stability.
-ERA5 can be generally characterized as representing cloud occurrence correctly above about 1--1.5~km, overestimating between 500m and 1km, but underestimating near-surface cloud occurrence (0--500~m).
+ERA5 can be generally characterized as representing cloud occurrence correctly above about 1.5~km, overestimating between 500~m and 1~km, but underestimating near-surface cloud occurrence (0--500~m).
 The total cloud fraction is strongly underestimated in all situations.
@@
 
-In Fig.~\ref{fig:cloud-occurrence}, we also display the mean outgoing shortwave and longwave top of atmosphere radiation.
+In Fig.~\ref{fig:cloud-occurrence}, we also display the mean outgoing shortwave and longwave top of atmosphere radiation, whose calculation is described in Section~\ref{sec:ceres}.
 In observations, these come from daily mean CERES measurements averaged over the voyage tracks or a station location, whereas in the models they come from daily means of TOA radiation in the model output averaged over the same location and time periods.
@@
 The likely explanation is an overestimated cloud albedo, compensating for the lack of cloud area.
-We note that the the radiative transfer calculations used in the lidar simulator mean that the impact of both cloud phase and cloud fraction are convolved which may help explain this result.
+
+We note that the the radiative transfer calculations used in the lidar simulator mean that the impact of both cloud phase and cloud fraction are convolved to produce the cloud mask.
+Therefore, the cloud occurrence is not affected by any cloud phase biases as long as the cloud is optically thick enough to be detected and the laser signal is not too attenuated.
+However, a combination of underestimated total cloud fraction and overestimated outgoing SW at TOA is indicative of an overestimated cloud albedo due to either cloud liquid and ice water content, cloud phase, droplet or ice crystal size distribution, shape or orientation of ice crystals, or cloud overlap.
 
@@
 Our main finding corroborates previous findings of large boundary layer cloud biases in models and their subsequent effect on the radiative transfer.
-For example, low- and mid-level clouds in the cold-air sector of cyclones were identified as being responsible for most of the SW bias in \cite{Bodas-Salcedoetal2012}.
-This understanding was refined in \cite{Bodas-Salcedoetal2014} which highlighted that the SW bias was associated with an incorrectly simulated mid-level cloud regime, which occurred in regions where cloud with tops at mid-level and low-levels occurred.
+For example, low- and mid-level clouds in the cold-air sector of cyclones were identified as being responsible for most of the SW bias in \cite{bodas-salcedo2012}.
+This understanding was refined in \cite{bodas-salcedo2014}, which highlighted that the SW bias was associated with an incorrectly simulated mid-level cloud regime, which occurred in regions where cloud with tops at mid-level and low-levels occurred.
 Our results align less well with more recent work by \cite{ramadoss2024} which shows persistent shortwave radiative bias over the Southern Ocean are associated with incorrect cloud phase representation.
@@
 The radiosonde observations indicate that the LCL is too high in ICON and reanalyses, which is probably responsible for the higher peak of clouds in the models and the lack of near-surface clouds or fog.
-The radiosonde comparison, however, does not seem to explain cloud biases at higher altitudes which is perhaps suggestive of biases in the influence of the liquid water path in teh models relative to the reality observed by the models.
+The radiosonde comparison, however, does not seem to explain cloud biases at higher altitudes, which is perhaps suggestive of biases in the influence of the liquid water path in the models relative to the reality.
 MERRA-2 is too moist at all heights.

### 2024-12-13 manuscript_agu.tex
Fix citations

@@
 Our main finding corroborates previous findings of large boundary layer cloud biases in models and their subsequent effect on the radiative transfer.
-For example, low- and mid-level clouds in the cold-air sector of cyclones were identified as being responsible for most of the SW bias in \cite{bodas-salcedo2012}.
-This understanding was refined in \cite{bodas-salcedo2014}, which highlighted that the SW bias was associated with an incorrectly simulated mid-level cloud regime, which occurred in regions where cloud with tops at mid-level and low-levels occurred.
-Our results align less well with more recent work by \cite{ramadoss2024} which shows persistent shortwave radiative bias over the Southern Ocean are associated with incorrect cloud phase representation.
-While \cite{fiddes2024} suggest biases in the liquid water path are the largest contributor to the cloud radiative bias over the Southern Ocean.
+For example, low- and mid-level clouds in the cold-air sector of cyclones were identified as being responsible for most of the SW bias in \citeA{bodas-salcedo2012}.
+This understanding was refined in \citeA{bodas-salcedo2014}, which highlighted that the SW bias was associated with an incorrectly simulated mid-level cloud regime, which occurred in regions where cloud with tops at mid-level and low-levels occurred.
+Our results align less well with more recent work by \citeA{ramadoss2024} which shows persistent shortwave radiative bias over the Southern Ocean are associated with incorrect cloud phase representation.
+While \citeA{fiddes2024} suggest biases in the liquid water path are the largest contributor to the cloud radiative bias over the Southern Ocean.
 Our general finding applies to the new GSRM ICON, but the biases are generally lower than in the reanalyses, despite the reanalyses having the advantage of assimilation of the observed meteorological conditions.

### 2024-12-13 manuscript_agu.tex
Link to custom ALCF

@@
 The TAN1802 data are openly available on Zenodo \cite{kremser2020}.
-The code for performing the presented analysis and precipitation detection is open-source and available at \url{https://github.com/peterkuma/icon-so-2024} and \url{https://github.com/peterkuma/alcf-precip}, respectively.
+The code for performing the presented analysis, precipitation detection, and a custom version of the ALCF using for our analysis are open-source and available at \url{https://github.com/peterkuma/icon-so-2024}, \url{https://github.com/peterkuma/alcf-precip}, and \url{https://github.com/peterkuma/icon-so-2024-alcf}, respectively.
 The remaining voyage data (AA15-16, HMNZSW16, NBP1704, TAN1502, and TAN1702) are openly available on Zenodo \cite{mcdonald2024b}.
+The Natural Earth dataset is openly available from \url{https://www.naturalearthdata.com}.
 

### 2024-12-13 manuscript_agu.tex
Fixing grammar

@@
 Outgoing shortwave radiation is overestimated in the reanalyses, implying a ``too few, too bright'' cloud problem.
-Thermodynamic conditions are relatively well represented, but ICON is less stable than observations and MERRA-2 is too humid.
+Thermodynamic conditions are relatively well represented, but ICON is less stable than observations, and MERRA-2 is too humid.
 SO cloud biases are a substantial issue in the GSRM, but it matches the observations better than the lower-resolution reanalyses.
@@
 Nevertheless, radiation biases and changes over an area of its size have a substantial influence on the global climate \cite{rintoul2011}, such as affecting the Earth radiation balance, ocean heat, and carbon uptake \cite{williams2023}, and the SO is also an important part of the global ocean conveyor belt \cite{wang2014b}.
-In general, marine clouds have a disproportionate effect on top of atmosphere (TOA) SW radiation due to the relatively low albedo of the sea surface.
+In general, marine clouds have a disproportionate effect on top-of-atmosphere (TOA) SW radiation due to the relatively low albedo of the sea surface.
 The relative longitudinal symmetry of the SO means that model cloud biases tend to be similar across longitudes.
@@
 This region is mostly dominated by boundary layer clouds generated by shallow convection, and these are problematic to observe by spaceborne lidars and radars, which are affected by attenuation by overlapping and thick clouds \cite{mace2009,medeiros2010} and ground clutter \cite{marchand2008}, respectively.
-Specifically, the radar on CloudSat and lidar on CALIPSO (neither of which are now operational) are affected by the above mentioned issues, resulting in a strong underestimation of cloud occurrence below 2 km relative to ground-based lidar observations \cite{mcerlich2021}.
+Specifically, the radar on CloudSat and lidar on CALIPSO (neither of which are now operational) are affected by the above-mentioned issues, resulting in a strong underestimation of cloud occurrence below 2 km relative to ground-based lidar observations \cite{mcerlich2021}.
 We hypothesize that this, in turn, can lead to systematic biases in low clouds in climate models, which are frequently evaluated against CloudSat--CALIPSO products.
@@
 
-The campaigns contained ceilometer observations captured by the Vaisala CL51 and CT25K, and the Lufft CHM~15k, described in detail below (Sections~\ref{sec:cl51} and \ref{sec:chm15k}).
+The campaigns contained ceilometer observations captured by the Vaisala CL51, CT25K, and the Lufft CHM~15k, described in detail below (Sections~\ref{sec:cl51} and \ref{sec:chm15k}).
 A ceilometer is a low-power, near-infrared, vertically pointing lidar principally designed to measure cloud base, but they also measure the full vertical structure of clouds as long as the laser signal is not attenuated by thick clouds, which can be used to infer additional information such as a cloud mask and cloud occurrence by height.
@@
 Fig.~\ref{fig:cyclone-stability}a, b show the geographical distribution of the fraction of cyclonic days as determined by the cyclone tracking algorithm applied to the ERA5 reanalysis and ICON data (Section~\ref{sec:cyclone-stability}).
-As expected, the strongest cyclonic activity is in the high-latitude SO zone, and is relatively zonally symmetric at all latitudes.
+As expected, the strongest cyclonic activity is in the high-latitude SO zone and is relatively zonally symmetric at all latitudes.
 The pattern matches reasonably well with \citeA{hoskins2005}.
@@
 The models generally underestimate the total cloud fraction by 10--20\% and show a strong reduction in cloud occurrence near the surface, which is not identified in the observations.
-ICON and ERA5 overestimate cloud occurrence at their peak (between 0--1~km).
+ICON and ERA5 overestimate cloud occurrence at their peak (between 0 and 1~km).
 Above 1~km, ICON and MERRA-2 underestimate cloud occurrence, but ERA5 is accurate to about 3\% or less.
@@
 
-In Fig.~\ref{fig:cloud-occurrence}, we also display the mean outgoing shortwave and longwave top of atmosphere radiation, whose calculation is described in Section~\ref{sec:ceres}.
+In Fig.~\ref{fig:cloud-occurrence}, we also display the mean outgoing shortwave and longwave top-of-atmosphere radiation, whose calculation is described in Section~\ref{sec:ceres}.
 In observations, these come from daily mean CERES measurements averaged over the voyage tracks or a station location, whereas in the models they come from daily means of TOA radiation in the model output averaged over the same location and time periods.
@@
 
-In the general case (Fig.~\ref{fig:cloud-occurrence}a), ICON underestimates the outgoing SW radiation by 26 Wm$^{-2}$ and the MERRA-2 and ERA5 reanalyses overestimate it by 6 and 14 Wm$^{-2}$, respectively.
+In the general case (Fig.~\ref{fig:cloud-occurrence}a), ICON underestimates the outgoing SW radiation by 26 Wm$^{-2}$, and the MERRA-2 and ERA5 reanalyses overestimate it by 6 and 14 Wm$^{-2}$, respectively.
 While in ICON, this is in line with the underestimated total cloud fraction of 10\%, in the reanalyses this is the opposite result to that expected from the underestimated total cloud fraction of about 20\%.
@@
 
-We note that the the radiative transfer calculations used in the lidar simulator mean that the impact of both cloud phase and cloud fraction are convolved to produce the cloud mask.
-Therefore, the cloud occurrence is not affected by any cloud phase biases as long as the cloud is optically thick enough to be detected and the laser signal is not too attenuated.
+We note that the radiative transfer calculations used in the lidar simulator mean that the impact of both cloud phase and cloud fraction are convolved to produce the cloud mask.
+Therefore, the cloud occurrence is not affected by any cloud phase biases as long as the cloud is optically thick enough to be detected, and the laser signal is not too attenuated.
 However, a combination of underestimated total cloud fraction and overestimated outgoing SW at TOA is indicative of an overestimated cloud albedo due to either cloud liquid and ice water content, cloud phase, droplet or ice crystal size distribution, shape or orientation of ice crystals, or cloud overlap.
@@
 In ICON, the outgoing LW radiation is overestimated by 8\%, which could be caused by an underestimated total cloud fraction exposing a larger sea surface area to cooling to space, which is typically warmer than the atmospheric temperature at 0--2~km, where most of the clouds are located.
-In the MERRA-2 and ERA5 reanalyses, the LW biases are also slightly positive 4 and 7~Wm$^{-2}$, respectively.
+In the MERRA-2 and ERA5 reanalyses, the LW biases are also slightly positive, 4 and 7~Wm$^{-2}$, respectively.
 This is again in line with the underestimated total cloud fraction by about 20\%.
@@
 
-In all the subsets (Fig.~\ref{fig:cloud-occurrence}b--g), the same type biases are observed, namely the outgoing SW radiation is underestimated in ICON and overestimated in MERRA-2 and ERA5, and the outgoing LW radiation is overestimated in all the models.
+In all the subsets (Fig.~\ref{fig:cloud-occurrence}b--g), the same type of biases are observed, namely the outgoing SW radiation is underestimated in ICON and overestimated in MERRA-2 and ERA5, and the outgoing LW radiation is overestimated in all the models.
 Even though the total cloud fraction is lower by 7\% over the high-latitude SO than the low-latitude SO, the outgoing SW radiation is much greater by 41~Wm$^{-2}$, implying a much greater cloud albedo over the high-latitude SO.
-ICON model output displays the same contrast between these two regions in the total cloud fraction and SW radiation, but the outgoing SW radiation difference between the regions is much smaller (16~Wm$^{-2}$).
+The ICON model output displays the same contrast between these two regions in the total cloud fraction and SW radiation, but the outgoing SW radiation difference between the regions is much smaller (16~Wm$^{-2}$).
 The reanalyses do not show this type of contrast between the regions.
@@
 This is a measure of cloudiness, irrespective of height, calculated over the course of a day (UTC).
-A cloud detected at any height means that the lidar profile was classified as cloudy; otherwise, it was classified as clear sky.
+A cloud detected at any height means that the lidar profile was classified as cloudy; otherwise, it was classified as a clear sky.
 When all profiles in a day are taken together, the cloud cover for the day is defined as the fraction of cloudy profiles in the total number of profiles, expressed in oktas (multiples of 1/8).
@@
 The interannual variability in cloud occurrence in ICON can be seen in Fig.~\ref{fig:cloud-occurrence-panel}, where each year in ICON is represented by a separate line.
-The interannual variability tends to be substantially smaller than the biases, and thus is unlikely to have a strong impact on the main findings.
+The interannual variability tends to be substantially smaller than the biases and thus is unlikely to have a strong impact on the main findings.
 
@@
 However, the approach was limited by the relatively low sensitivity of the ANN (65\%) and the fact that we had to choose a fixed threshold for surface precipitation flux in the model and reanalyses, which might not correspond to detection by the ANN applied to observations.
-We also made no attempt to remove profiles with precipitation which did not reach the surface.
+We also made no attempt to remove profiles with precipitation that did not reach the surface.
 The above reasons may result in an artificial bias in the comparison, though we expect this to be much smaller than the identified model biases.
@@
 For example, low- and mid-level clouds in the cold-air sector of cyclones were identified as being responsible for most of the SW bias in \citeA{bodas-salcedo2012}.
-This understanding was refined in \citeA{bodas-salcedo2014}, which highlighted that the SW bias was associated with an incorrectly simulated mid-level cloud regime, which occurred in regions where cloud with tops at mid-level and low-levels occurred.
-Our results align less well with more recent work by \citeA{ramadoss2024} which shows persistent shortwave radiative bias over the Southern Ocean are associated with incorrect cloud phase representation.
+This understanding was refined in \citeA{bodas-salcedo2014}, which highlighted that the SW bias was associated with an incorrectly simulated mid-level cloud regime, which occurred in regions where clouds with tops at mid-level and low-levels occurred.
+Our results align less well with more recent work by \citeA{ramadoss2024}, which shows persistent shortwave radiative biases over the Southern Ocean are associated with incorrect cloud phase representation.
 While \citeA{fiddes2024} suggest biases in the liquid water path are the largest contributor to the cloud radiative bias over the Southern Ocean.
@@
 The radiosonde observations indicate that the LCL is too high in ICON and reanalyses, which is probably responsible for the higher peak of clouds in the models and the lack of near-surface clouds or fog.
-The radiosonde comparison, however, does not seem to explain cloud biases at higher altitudes, which is perhaps suggestive of biases in the influence of the liquid water path in the models relative to the reality.
+The radiosonde comparison, however, does not seem to explain cloud biases at higher altitudes, which is perhaps suggestive of biases in the influence of the liquid water path in the models relative to reality.
 MERRA-2 is too moist at all heights.

### 2025-06-26 manuscript_agu_rev1.tex
Revised version

--- 2024-12-13 manuscript_agu.tex
@@
 
+\usepackage{xr}
+\externaldocument{si_rev1}
+
 \draftfalse
@@
 
-\title{Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON, and the ERA5 and MERRA-2 reanalyses}
+\title{Ship-based lidar evaluation of Southern Ocean low clouds in the storm-resolving general circulation model ICON and the ERA5 and MERRA-2 reanalyses}
 
-\authors{Peter Kuma\affil{1,2,3}\thanks{}, Frida A.-M.
+\authors{Peter Kuma\affil{1,2,3,4}, Frida A.-M.
 Bender\affil{1,2}, Adrian J.
 McDonald\affil{3}, Simon P.
-Alexander\affil{4,5}, Greg M.
-McFarquhar\affil{6,7}, John J.
-Cassano\affil{8,9,10}, Graeme E.
-Plank\affil{3}, Sean Hartery\affil{3}\thanks{Current affiliation: Department of Physics \& Atmospheric Science, Dalhousie University, Halifax, Canada}, Simon Parsons\affil{3}\thanks{Current affiliation: New South Wales Department of Planning and Environment, Sydney, New South Wales, Australia}, Sally Garrett\affil{11}, and Alex J.
-Schuddeboom\affil{3}}
+Alexander\affil{5,6}, Greg M.
+McFarquhar\affil{7,8}, John J.
+Cassano\affil{9,10,11}, Graeme E.
+Plank\affil{3}, Sean Hartery\affil{3}\thanks{Current affiliation: Department of Physics \& Atmospheric Science, Dalhousie University, Halifax, Canada}, Simon Parsons\affil{3}\thanks{Current affiliation: New South Wales Department of Planning and Environment, Sydney, New South Wales, Australia}, Sally Garrett\affil{12}, Alex J.
+Schuddeboom\affil{3}, and Anna Possner\affil{4}}
 
@@
 \affiliation{3}{School of Physical and Chemical Sciences, University of Canterbury, Christchurch, Aotearoa/New Zealand}
-\affiliation{4}{Australian Antarctic Division, Kingston, Tasmania, Australia}
-\affiliation{5}{Australian Antarctic Program Partnership, Institute for Marine and Antarctic Studies, University of Tasmania, Hobart, Tasmania, Australia}
-\affiliation{6}{Cooperative Institute of Severe and High Impact Weather Research and Operations, University of Oklahoma, Norman, OK, USA}
-\affiliation{7}{School of Meteorology, University of Oklahoma, Norman, OK, USA}
-\affiliation{8}{Cooperative Institute for Research in Environmental Sciences, University of Colorado, Boulder, CO, USA}
-\affiliation{9}{National Snow and Ice Data Center, University of Colorado, Boulder, CO, USA}
-\affiliation{10}{Department of Atmospheric and Oceanic Sciences, University of Colorado, Boulder, CO, USA}
-\affiliation{11}{New Zealand Defence Force, Wellington, Aotearoa/New Zealand}
+\affiliation{4}{Institute for Atmospheric and Environmental Sciences, Goethe University Frankfurt, Frankfurt am Main, Hesse, Germany}
+\affiliation{5}{Australian Antarctic Division, Kingston, Tasmania, Australia}
+\affiliation{6}{Australian Antarctic Program Partnership, Institute for Marine and Antarctic Studies, University of Tasmania, Hobart, Tasmania, Australia}
+\affiliation{7}{Cooperative Institute of Severe and High Impact Weather Research and Operations, University of Oklahoma, Norman, OK, USA}
+\affiliation{8}{School of Meteorology, University of Oklahoma, Norman, OK, USA}
+\affiliation{9}{Cooperative Institute for Research in Environmental Sciences, University of Colorado, Boulder, CO, USA}
+\affiliation{10}{National Snow and Ice Data Center, University of Colorado, Boulder, CO, USA}
+\affiliation{11}{Department of Atmospheric and Oceanic Sciences, University of Colorado, Boulder, CO, USA}
+\affiliation{12}{New Zealand Defence Force, Wellington, Aotearoa/New Zealand}
 
@@
 \item Ground-based lidar evaluation of a km-scale global climate model and reanalyses reveals substantial cloud biases over the Southern Ocean.
-\item Fog or low cloud is underestimated in the reanalyses. In all models, a cloud peak at 500~m tends to be overestimated and too high.
-\item A ``too few, too bright'' problem of underestimated cloud fraction, compensated by overestimated cloud albedo, is present in the reanalyses.
+\item Total cloud fraction and fog are underestimated in the reanalyses. In all models, a cloud peak at 500~m is overestimated and too high.
+\item A ``too few, too bright'' problem of underestimated cloud fraction, compensated by overestimated cloud albedo, is present in MERRA-2.
 \end{keypoints}
@@
 \begin{abstract}
-Global storm-resolving models (GSRMs) are the upcoming global climate models.
+Global storm resolving models (GSRMs) represent the next generation of global climate models.
 One of them is a 5-km Icosahedral Nonhydrostatic Weather and Climate Model (ICON).
-Its high resolution means that parameterizations of convection and clouds, including subgrid-scale clouds, are omitted, relying on explicit simulation but still utilizing microphysics and turbulence parameterizations.
+Its high resolution means that parameterizations of convection and clouds, including subgrid-scale clouds, are omitted, relying on explicit simulation but necessarily utilizing microphysics and turbulence parameterizations.
 Standard-resolution (10--100~km) models, which use convection and cloud parameterizations, have substantial cloud biases over the Southern Ocean (SO), adversely affecting radiation and sea surface temperature.
 The SO is dominated by low clouds, which cannot be observed accurately from space due to overlapping clouds, attenuation, and ground clutter.
-We evaluated SO clouds in ICON and the ERA5 and MERRA-2 reanalyses using about 2400 days of lidar observations and 2300 radiosonde profiles from 31 voyages and Macquarie Island station during 2010--2021, compared with the models using a ground-based lidar simulator.
+We evaluated SO clouds in ICON and the ERA5 and MERRA-2 reanalyses using approximately 2400 days of lidar observations and 2300 radiosonde profiles from 31 voyages and Macquarie Island station during 2010--2021, compared with the models using a ground-based lidar simulator.
 We found that ICON and the reanalyses underestimate the total cloud fraction by about 10 and 20\%, respectively.
-ICON and ERA5 overestimate the cloud occurrence peak at about 500 m, potentially explained by their lifting condensation levels being too high.
-The reanalyses strongly underestimate fog or near-surface clouds, and MERRA-2 underestimates cloud occurrence at almost all heights.
-Outgoing shortwave radiation is overestimated in the reanalyses, implying a ``too few, too bright'' cloud problem.
-Thermodynamic conditions are relatively well represented, but ICON is less stable than observations, and MERRA-2 is too humid.
-SO cloud biases are a substantial issue in the GSRM, but it matches the observations better than the lower-resolution reanalyses.
+ICON and ERA5 overestimate the cloud occurrence peak at about 500~m, associated with underestimated lower tropospheric stability and overestimated lifting condensation level.
+The reanalyses strongly underestimate fog and near-surface clouds, and MERRA-2 underestimates cloud occurrence at almost all heights.
+Outgoing shortwave radiation is overestimated in MERRA-2, implying a ``too few, too bright'' cloud problem.
+SO cloud and fog biases are a substantial issue in the analyzed models and result in shortwave and longwave radiation biases.
 \end{abstract}
@@
 Reanalyses are the best estimates of past meteorological conditions based on an underlying global model and observations.
-We evaluated clouds and thermodynamic profiles over the Southern Ocean in one such model, as well as two reanalyses, based on 2400 days of ship and station observations.
-Thanks to the high resolution, the model relies entirely on explicit simulation of clouds, instead of subgrid-scale parameterizations.
+We evaluated clouds, temperature, and humidity profiles over the Southern Ocean in one such model, as well as two reanalyses, based on 2400 days of ship and station observations.
+Thanks to the high resolution, the model relies entirely on explicit simulation of clouds instead of subgrid-scale parameterizations.
 For the evaluation, we used ceilometer and radiosonde observations and a lidar simulator, which enables a fair comparison with the model and reanalyses.
 We subsetted our results by cyclonic activity and stability.
-We found that the model and reanalyses underestimate a lidar-derived cloud fraction, and the reanalyses do so more strongly.
+We found that the model and reanalyses underestimate lidar-derived cloud fraction, and the reanalyses do so more strongly.
 Fog or near-surface clouds are especially underestimated in the reanalyses.
 However, the model and one of the reanalyses also tend to overestimate the peak of cloud occurrence at 500 m above the ground, and it tends to be higher.
-This is linked to thermodynamic profiles, which show a higher lifting condensation level.
-Southern Ocean biases are still an important problem in the model, but an improvement over the reanalyses is notable.
+This is linked to thermodynamic profiles, which show a higher lifting condensation level and lower stability.
+Southern Ocean cloud and fog biases are an important problem in the analyzed models and result in radiation balance biases.
 
@@
 
-Increasing climate model resolution is one way of improving the accuracy of the representation of the climate system in models \cite{mauritsen2022}.
+Increasing climate model spatial resolution is one way of improving the accuracy of the representation of the climate system in models \cite{mauritsen2022}.
 It has been practiced since the advent of climate modeling as more computational power, memory, and storage capacity become available.
@@
 
-The nextGEMS project \cite{nextgems} focuses on the research and development of GSRMs at multiple modeling centers and universities in Europe.
+The main aim of this study is to evaluate the GSRM version of ICON developed by the nextGEMS project \cite{nextgems,segura2025}.
+ICON is developed and maintained jointly by Deutscher Wetterdienst, the Max-Planck-Institute for Meteorology, Deutsches Klimarechenzentrum (DKRZ), Karlsruhe Institute of Technology, and the Center for Climate Systems Modeling.
+Our aim is to quantify how well the GSRM ICON simulates clouds in this region, particularly in light of the fact that subgrid-scale clouds and convection are not parameterized in this model.
+This region is mostly dominated by boundary layer clouds generated by shallow convection, and these are problematic to observe by spaceborne lidars and radars, which are affected by attenuation by overlapping and thick clouds \cite{mace2009,medeiros2010} and ground clutter \cite{marchand2008}, respectively.
+Specifically, the radar on CloudSat and lidar on the Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observation (CALIPSO), neither of which are now operational, are affected by the above-mentioned issues, resulting in a strong underestimation of cloud occurrence below 2 km in a merged CloudSat--CALIPSO product relative to ground-based lidar observations at McMurdo Station \cite{mcerlich2021}.
+However, removing situations with higher overlapping clouds could enable a less biased comparison of low clouds.
+We hypothesize that this, in turn, can lead to systematic biases in low clouds in climate models, which are frequently evaluated against CloudSat--CALIPSO products.
+Reanalyses can also suffer from cloud biases, as these are usually parameterized in their atmospheric component and also in regions where input observations are sparse.
+This makes them a problematic reference for clouds over the SO, and any biases relative to a reanalysis should be interpreted with caution.
+Instead, we chose to use a large set of ship-based observations conducted with ceilometers and lidars on board the RV \emph{Polarstern} and other voyages and a station as a reference for the model evaluation.
+Altogether, we analyzed approximately 2400 days of data from 31 voyages and one sub-Antarctic station covering diverse longitudes and latitudes of the SO.
+To achieve a like-for-like comparison with the model, we used a ground-based lidar simulator called the Automatic Lidar and Ceilometer Framework [ALCF; \citeA{kuma2021}].
+We contrasted the results with ERA5 \cite{era5} and the Modern-Era Retrospective analysis for Research and Applications, Version~2 [MERRA-2; \citeA{gelaro2017}].
+
+The nextGEMS project focuses on the research and development of GSRMs at multiple modeling centers and universities in Europe.
 The project also develops GSRM versions of the Icosahedral Nonhydrostatic Weather and Climate Model (ICON; \citeA{hohenegger2023}), the Integrated Forecasting System [IFS; \citeA{ifs2023}], and their ocean components at eddy-resolving resolutions: ICON-O \cite{korn2022} coupled with ICON and Finite-Element/volumE Sea ice-Ocean Model [FESOM; \citeA{wang2014a}] and Nucleus for European modeling of the Ocean [NEMO; \citeA{madec2023}] coupled with IFS.
 The project has so far produced ICON and IFS simulations with three development versions called Cycle 1--3 and a pre-final version, with a final production version planned by the end of the project.
-nextGEMS is not the only project developing GSRMs; other GSRMs (or GSRM versions of climate models) currently in development include: Convection-Permitting Simulations With the E3SM Global Atmosphere Model [SCREAM; \citeA{caldwell2021}], Atmospheric Model [NICAM; \citeA{satoh2008}], Unified Model (UM), eXperimental System for High-resolution modeling for Earth-to-Local Domain [X-SHiELD; \citeA{shield}], Action de Recherche Petite Echelle Grande Echelle-NonHydrostatic version [ARPEGE-NH; \citeA{bubnova1995,voldoire2017}], Finite-Volume Dynamical Core on the Cubed Sphere [FV3, \citeA{lin2004}], the National Aeronautics and Space Administration (NASA) Goddard Earth Observing System global atmospheric model version 5 [GEOS5; \citeA{putman2011}], Model for Prediction Across Scales [MPAS; \citeA{skamarock2012}], and System for Atmospheric Modeling [SAM; \citeA{khairoutdinov2003}].
+nextGEMS is not the only project developing GSRMs; other GSRMs (or GSRM versions of climate models) currently in development include: Convection-Permitting Simulations With the E3SM Global Atmosphere Model [SCREAM; \citeA{caldwell2021}], Non-hydrostatic Icosahedral Atmospheric Model [NICAM; \citeA{satoh2008}], Unified Model (UM), eXperimental System for High-resolution modeling for Earth-to-Local Domain [X-SHiELD; \citeA{shield}], Action de Recherche Petite Echelle Grande Echelle-NonHydrostatic version [ARPEGE-NH; \citeA{bubnova1995,voldoire2017}], Finite-Volume Dynamical Core on the Cubed Sphere [FV3, \citeA{lin2004}], the National Aeronautics and Space Administration (NASA) Goddard Earth Observing System global atmospheric model version 5 [GEOS5; \citeA{putman2011}], Model for Prediction Across Scales [MPAS; \citeA{skamarock2012}], and System for Atmospheric Modeling [SAM; \citeA{khairoutdinov2003}].
 
@@
 Second-order effects on SW and LW radiation are associated with the cloud droplet size distribution, ice crystal habit, cloud lifetime, and direct radiative interaction with aerosols.
-In the 6$^\mathrm{th}$ phase of the Coupled Model Intercomparison Project [CMIP6; \citeA{eyring2016}], the cloud feedback has increased relative to CMIP5 \cite{zelinka2020}, which is one of the main reasons for the higher climate sensitivity of CMIP6 models.
+In the 6$^\mathrm{th}$ phase of the Coupled Model Intercomparison Project [CMIP6; \citeA{eyring2016}], the cloud feedback has increased relative to CMIP5 \cite{zelinka2020}, especially in the Southern Hemisphere mid-to-high latitudes, which is one of the main reasons for the higher climate sensitivity of CMIP6 models.
 
 The Southern Ocean (SO) is known to be a problematic region for climate model biases \cite{schuddeboom2021,hyder2018,cesana2022,zhao2022} due to a lack of surface and in situ observations and being a lower priority region for numerical weather prediction (NWP) and climate model development because of its distance from populated areas.
-Nevertheless, radiation biases and changes over an area of its size have a substantial influence on the global climate \cite{rintoul2011}, such as affecting the Earth radiation balance, ocean heat, and carbon uptake \cite{williams2023}, and the SO is also an important part of the global ocean conveyor belt \cite{wang2014b}.
+Nevertheless, radiation biases and changes over an area of its size have a substantial influence on the global climate \cite{rintoul2011}, such as affecting the Earth's radiation balance, ocean heat, and carbon uptake \cite{williams2023}, and the SO is also an important part of the global ocean conveyor belt \cite{wang2014b}.
 In general, marine clouds have a disproportionate effect on top-of-atmosphere (TOA) SW radiation due to the relatively low albedo of the sea surface.
@@
 
-Here, we refer to the SO as ocean regions south of 40°S, low-latitude SO as 40--55°S and high-latitude SO as south of 55°S.
+In the following text, we refer to the SO as ocean regions south of 40°S, low-latitude SO as 40--55°S, and high-latitude SO as south of 55°S, all the way to the Antarctic coast.
 The reason for this dividing latitude is to split the SO into about two equal zones, as well as the results by \citeA{schuddeboom2021} (Fig.~2b) which show a contrast in CMIP model radiation biases.
-\citeA{schuddeboom2019} (Fig.~2) and \citeA{kuma2020} (Fig.~3) also show contrasting radiation biases in the Hadley Centre Global Environmental Model, which is also supported by \citeA{cesana2022} which displays contrasting cloud biases due to the 0°C isotherm reaching the surface at 55°S.
+\citeA{schuddeboom2019} (Fig.~2) and \citeA{kuma2020} (Fig.~3) also show contrasting radiation biases in the Hadley Centre Global Environmental Model, which is also supported by \citeA{cesana2022}, displaying contrasting cloud biases due to the 0°C isotherm reaching the surface at 55°S.
 The findings of \citeA{niu2024}, however, support a different dividing line of 62°S based on cloud condensation nuclei concentration.
 
-SO radiation biases have been relatively large and systematic compared to the rest of the globe since at least CMIP3 \cite{trenberth2010}, and the SO SW cloud radiative effect (CRE) bias is still positive in eight analyzed CMIP6 models analyzed by \citeA{schuddeboom2021} over the high-latitude SO, whereas over the low-latitude SO it tends to be more neutral or negative in some models.
+SO radiation biases have been relatively large and systematic compared to the rest of the globe since at least CMIP3 \cite{trenberth2010}, and the SO SW cloud radiative effect (CRE) bias is still positive in eight CMIP6 models analyzed by \citeA{schuddeboom2021} over the high-latitude SO, whereas over the low-latitude SO it tends to be more neutral or negative in some models.
 Too much absorbed SW radiation over the SO was also identified in the GSRM SCREAM \cite{caldwell2021}.
-Compensating biases are possible, such as the ``too few too bright'' cloud bias, characterized by too small cloud fraction and too large cloud albedo \cite{wall2017,kuma2020}, previously described by \citeA{webb2001}, \citeA{weare2004}, \citeA{zhang2005}, \citeA{karlsson2008}, \citeA{nam2012}, \citeA{klein2013}, and \citeA{bender2017} in other regions and models, which means that a model can maintain a reasonable SW radiation balance by reflecting too much SW radiation from clouds, but these cover too small an area.
-A study by \citeA{konsta2022} showed that this type of bias is still present in six analyzed CMIP6 models in tropical marine clouds, using the GCM-Oriented Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observation (CALIPSO) Cloud Product [CALIPSO--GOCCP; \citeA{chepfer2010}] and Polarization \& Anisotropy of Reflectances for Atmospheric Sciences coupled with Observations from a Lidar [PARASOL; \citeA{lier2008}] as a reference.
+Compensating biases are possible, such as the ``too few too bright'' cloud bias, characterized by too small a cloud fraction and too large a cloud albedo \cite{wall2017,kuma2020}, previously described by \citeA{webb2001}, \citeA{weare2004}, \citeA{zhang2005}, \citeA{karlsson2008}, \citeA{nam2012}, \citeA{klein2013}, and \citeA{bender2017} in other regions and models, which means that a model can maintain a reasonable SW radiation balance by reflecting too much SW radiation from clouds, but these cover too small an area.
+A study by \citeA{konsta2022} showed that this type of bias is still present in six analyzed CMIP6 models in tropical marine clouds, using the GCM-Oriented CALIPSO Cloud Product [CALIPSO--GOCCP; \citeA{chepfer2010}] and Polarization \& Anisotropy of Reflectances for Atmospheric Sciences coupled with Observations from a Lidar [PARASOL; \citeA{lier2008}] as a reference.
 They suggest improper simulation of subgrid-scale cloud heterogeneity as a cause.
@@
 \citeA{zhao2022} reported a similar SW radiation bias in five analyzed CMIP6 models over the high-latitude SO and an underestimation of the total cloud fraction on the order of 10\% over the entire 40--60°S SO.
-Recently, \citeA{ramadoss2024} analyzed 48~hours of km-scale ICON limited-area model NWP simulations over a SO region adjacent to Tasmania against the Clouds, Aerosols, Precipitation, Radiation, and atmospherIc Composition Over the southeRn oceaN (CAPRICORN) voyage cloud and precipitation observations \cite{mcfarquhar2021}.
+Recently, \citeA{ramadoss2024} analyzed 48~hours of km-scale ICON limited-area model NWP simulations over an SO region adjacent to Tasmania against the Clouds, Aerosols, Precipitation, Radiation, and atmospherIc Composition Over the southeRn oceaN (CAPRICORN) voyage cloud and precipitation observations \cite{mcfarquhar2021}.
 They found the ICON cloud optical thickness was underestimated relative to Himawari‐8 satellite observations but also identified large differences in cloud top phase.
 
-In general, sea surface temperature (SST) biases in the SO can originate either in the atmosphere \cite{hyder2018}, caused by too much shortwave heating of the surface, too little longwave cooling of the surface, or in the ocean circulation.
-Interactions of both are also possible, for example, SST affecting clouds and clouds affecting the surface radiation.
+In general, sea surface temperature (SST) biases in the SO can originate either in the atmosphere \cite{hyder2018}, caused by too much shortwave heating of the surface or too little longwave cooling of the surface, such as in situations of too much cloud cover or cloud optical thickness, or in the ocean circulation.
+Interactions of both are also possible; for example, SST affecting clouds and clouds affecting the surface radiation.
 Using the European Centre for Medium-Range Weather Forecasts (ECMWF) Reanalysis 5 (ERA5) as a reference, \citeA{zhang2023} have shown that SST biases have improved in CMIP6 compared to CMIP5, with SST overall increasing in CMIP6.
-However, over the SO this resulted in an even higher positive bias, especially in the Atlantic Ocean (AO) sector of the SO, increasing by up to 1°C.
-\citeA{luo2023} identified that the SO SST bias in an ensemble of 18 CMIP6 models originates not from the surface heat and radiation fluxes (using reanalyses as a reference), but from a warm bias in the Northern Atlantic Deep Water.
-
-The main aim of this study is to evaluate the GSRM version of ICON.
-ICON is developed and maintained jointly by Deutscher Wetterdienst, Max-Planck-Institute for Meteorology, Deutsches Klimarechenzentrum (DKRZ), Karlsruhe Institute of Technology, and the Center for Climate Systems Modeling.
-Previous studies have identified substantial large-scale biases in climate model clouds over the SO, affecting sea surface temperature and the Earth’s albedo.
-Our aim is to quantify how well the GSRM ICON simulates clouds in this region, particularly in light of the fact that subgrid-scale clouds and convection are not parameterized in this model.
-This region is mostly dominated by boundary layer clouds generated by shallow convection, and these are problematic to observe by spaceborne lidars and radars, which are affected by attenuation by overlapping and thick clouds \cite{mace2009,medeiros2010} and ground clutter \cite{marchand2008}, respectively.
-Specifically, the radar on CloudSat and lidar on CALIPSO (neither of which are now operational) are affected by the above-mentioned issues, resulting in a strong underestimation of cloud occurrence below 2 km relative to ground-based lidar observations \cite{mcerlich2021}.
-We hypothesize that this, in turn, can lead to systematic biases in low clouds in climate models, which are frequently evaluated against CloudSat--CALIPSO products.
-Reanalyses can also suffer from cloud biases, as these are usually parameterized in their atmospheric component and also in regions where input observations are sparse.
-This makes them a problematic reference for clouds over the SO, and any biases relative to a reanalysis should be interpreted with caution.
-Instead, we chose to use a large set of ship-based observations conducted with ceilometers and lidars on board the RV \emph{Polarstern} and other voyages and stations as a reference for the model evaluation.
-
-Altogether, we analyzed about 2400 days of data from 31 voyages and one sub-Antarctic station covering diverse longitudes and latitudes of the SO.
-To achieve a like-for-like comparison with the model, we used a ground-based lidar simulator called the Automatic Lidar and Ceilometer Framework [ALCF; \citeA{kuma2021}].
-We contrasted the results with ERA5 \cite{era5} and the Modern-Era Retrospective analysis for Research and Applications, Version~2 [MERRA-2; \citeA{gelaro2017}].
+However, over the SO, this resulted in an even higher positive bias, especially in the Atlantic Ocean (AO) sector of the SO, increasing by up to 1°C.
+\citeA{luo2023} identified that the SO SST bias in an ensemble of 18 CMIP6 models originates not from the surface heat and radiation fluxes (using reanalyses as a reference) but from a warm bias in the Northern Atlantic Deep Water.
 
@@
 Together, we analyzed data from 31 voyages of RV \emph{Polarstern}, the resupply vessel (RSV) \emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B.
-Palmer}, Her (now His) Majesty's New Zealand Ship (HMNZS) \emph{Wellington} and one sub-Antarctic station (Macquarie Island) in the SO south of 40°S between 2010 and 2021.
+Palmer}, Her (now His) Majesty's New Zealand Ship (HMNZS) \emph{Wellington}, and one sub-Antarctic station (Macquarie Island) in the SO south of 40°S between 2010 and 2021.
 Fig.~\ref{fig:map} shows a map of the campaigns, Table \ref{tab:voyages} lists the campaigns, and Table \ref{tab:voyage-references} lists references where available.
-Altogether, the analyzed dataset comprised 2421 days of data south of 40°S, but the availability of ceilometer data was slightly shorter due to gaps in measurements.
+The analyzed dataset comprised 2421 days of data south of 40°S, but the availability of ceilometer data was slightly shorter due to gaps in measurements.
 
@@
 Apart from lidar observations, radiosondes were launched on weather balloons at regular synoptic times on the RV \emph{Polarstern}, MARCUS, NBP17024, TAN1702, and TAN1802 campaigns, measuring pressure, temperature, relative humidity, and the global navigation satellite system coordinates.
-Derived thermodynamic (virtual potential temperature, lifting condensation level, etc.) and dynamic physical quantities (wind speed and direction) for the measured vertical profiles were calculated with rstool \cite{rstool}.
+Derived thermodynamic (virtual potential temperature, relative humidity, lifting condensation level, etc.) and dynamic physical quantities (wind speed and direction) for the measured vertical profiles were calculated with the program radiosonde tool [rstool; \citeA{rstool}].
 Surface meteorological quantities were measured continuously by an onboard automatic weather station or individual instruments.
@@
 The sampling (temporal) resolution is configurable, and in our datasets, it is approximately 6~s for CL51 on AA15‐16, 16~s for CT25K on MARCUS and MICRE, 36~s for CL51 on RV \emph{Polarstern}, and about 2.37~s for CL51 with CL31 emulation on TAN1502.
-The wavelengths of 905 and 910~nm are both affected by water vapor absorption of about 20\% in the mid-latitudes \cite{wiegner2015,wiegner2019}, with 910~nm affected more strongly, but we do not expect this to be a significant issue as explained in \citeA{kuma2021}.
-The instrument data files containing raw uncalibrated backscatter were first converted to Network Common Data Form (NetCDF) with cl2nc (\url{https://github.com/peterkuma/cl2nc}) and then processed with the ALCF (Section~\ref{sec:alcf}) to produce absolutely calibrated attenuated volume backscattering coefficient (AVBC), cloud mask, cloud occurrence by height, and the total cloud fraction.
-Because the CT25K uses a very similar wavelength to CL51, equivalent calculations as for CL51 were done assuming a wavelength of 910~nm.
+The wavelengths of 905 and 910~nm are both affected by water vapor absorption of about 20\% in the mid-latitudes \cite{wiegner2015,wiegner2019}, with 910~nm affected more strongly, but we do not expect this to be a significant issue, as explained in \citeA{kuma2021}.
+The instrument data files containing raw uncalibrated backscatter were first converted to Network Common Data Form (NetCDF) with cl2nc \cite{kuma2024a} and then processed with the ALCF (Section~\ref{sec:alcf}) to produce absolutely calibrated attenuated volume backscattering coefficient (AVBC), cloud mask, cloud occurrence by height, and the total cloud fraction.
+Because the CT25K uses a very similar wavelength to the CL51, equivalent calculations as for the CL51 were done assuming a wavelength of 910~nm.
 The Vaisala CL51 and CT25K instruments were used on most of the voyages and stations analyzed here.
@@
 After AVBC is calculated, a cloud mask, cloud occurrence by height, and the total cloud fraction are determined.
+The total cloud fraction is defined as the fraction of profiles with clouds at any height in the lidar cloud mask.
 The ALCF has been used by several research teams for model and reanalysis evaluation \cite{kuma2020,kremser2021,guyot2022,pei2023,whitehead2023,mcdonald2024a}.
@@
 
+How attenuation of the lidar signal affects cloud detection is dependent on factors such as the optical thickness of the measured cloud and its backscattering phase function, as well as the range-dependent noise standard deviation.
+A rough estimate can be made under an assumption of a relatively strongly backscattering cloud of $\beta = \mathrm{100\times 10^{-6} m^{-1}sr^{-1}}$ at a height of $r_1$ = 2 km, range-dependent noise $\beta_n$ at $r_2$ = 8 km of about $\mathrm{5\times 10^{-6} m^{-1}sr^{-1}}$, and cloud detection threshold $\beta_t = \mathrm{2\times 10^{-6} m^{-1}sr^{-1}}$, noise multiplication factor $f$ = 5, at full attenuation the two-way attenuation factor $A$ satisfies $A\beta = \beta_t + f\times \beta_n\left(\frac{r_1}{r_2}\right)^2$, which is equivalent to exponential decay ($A = e^{-2\delta}$) with optical depth $\delta$ (at the lidar wavelength) of about 1.7.
+
 \subsection{ICON}
@@
 A coupled (atmosphere--ocean) GSRM version of the ICON model is in development as part of the nextGEMS project \cite{hohenegger2023}.
-ICON is an exceptionally versatile model, allowing for simulations ranging from coarse-resolution ESM simulations, GSRM simulations, limited area model simulations, to large eddy simulations (LES), for both weather prediction and climate projections.
+ICON is a very flexible model, allowing for simulations ranging from coarse-resolution ESM simulations, GSRM simulations, limited area model simulations, and large eddy simulations (LES) for both weather prediction and climate projections.
 ICON uses the atmospheric component ICON-A \cite{giorgetta2018}, whose physics is derived from ECHAM6 \cite{stevens2013}, and the ocean component ICON-O \cite{korn2022}.
@@
 
-Here, we use a free-running (i.e., the weather situation in the model does not correspond to reality) coupled GSRM simulation made for the purpose of climate projection.
+Here, we use a free-running (i.e., the weather conditions in the model do not correspond to reality) coupled GSRM simulation made for the purpose of climate projection.
 nextGEMS has so far produced four cycles of model runs.
@@
 While this makes the code development simpler without having to rely on uncertain parameterizations, it can miss smaller-scale clouds below the grid resolution.
-Turbulence and cloud microphysics are still parameterized in this model, and aerosols are taken from a climatology.
+Turbulence and cloud microphysics have to be parameterized in this model as in other models, and aerosols are derived from a climatology.
 To account for the radiative effects of subgrid-scale clouds, a cloud inhomogeneity factor is introduced in the model, which scales down the cloud liquid water for radiative calculations.
 It ranges from 0.4 at lower tropospheric stability (LTS) of 0~K to 0.8 at 30~K.
-In addition, vertical mixing is enhanced in unstable and humid lower-tropospheric conditions, which reduces the amount of shallow clouds.
+In addition, turbulent mixing in the Smagorinsky scheme was adjusted to allow mixing or entrainment in situations of no mixing under the traditional scheme, affecting stratocumulus clouds but not trade wind clouds \cite{segura2025}.
 
-Because the analyzed ICON simulation was free-running (years 2021--2024, inclusive), weather and climate oscillations (such as the El Niño--Southern Oscillation) are not expected to be equivalent to reality at the same time and place.
+Because the analyzed ICON simulation was free-running (years 2021--2024, inclusive), weather and climate oscillations (such as the El Niño--Southern Oscillation phase) are not expected to be equivalent to reality at the same time and place.
 To compare with the observations collected during a different time period (years 2010--2021, inclusive), we compared the model output with observations at the same time of year and geographical location, as determined for each data point, such as a lidar profile or a radiosonde launch.
 In the ALCF, this was done using the \emph{override\_year} option (\url{https://alcf.peterkuma.net/documentation/cli/cmd_model.html}).
-For radiosonde profiles, the same mapping of time from was done.
+For radiosonde profiles, the same mapping of time was done.
 That is, when selecting an equivalent profile from the model, the time of the profile was changed so that the time relative to the start of the year was preserved, but the year was changed to one of the four years available in the model data.
@@
 The geographical location was kept the same.
-We discuss briefly the implications of comparing the observations with a free-running model in Section~\ref{sec:limitations}.
+
+Due to our comparison being long-term and large-scale, it is expected that a comparison between the free-running model and observations is statistically robust, despite weather-related differences between the two.
+Furthermore, the results from multiple campaigns are combined in a way that equal statistical weight is given to each campaign, eliminating an outsize influence of longer campaigns, allowing us to estimate uncertainty ranges under the assumption of independence of weather conditions between the campaigns, and ensuring that the results are statistically representative over the whole area covered by the campaigns.
+Different approaches to a comparison would be possible.
+For example, one could use only the first several days of a free-running simulation initialized from observations (or a reanalysis) for a comparison, as done in the Transpose-AMIP experiments \cite{williams2013}, thus being able to compare clouds and the physical drivers under the same weather conditions.
+Another possibility is the use of a model nudged to a reanalysis \cite{kuma2020}, but this was not available for our ICON simulations.
+We discuss further the implications of comparing the observations with a free-running model in Section~\ref{sec:limitations}.
 
@@
 Here, we use the following products: 1-hourly instantaneous 2D single-level diagnostics (M2I1NXASM) for 2-m temperature and humidity; 3-hourly instantaneous 3D assimilated meteorological fields (M2I3NVASM) for cloud quantities, pressure, and temperature; 1-hourly average 2D surface flux diagnostics (M2T1NXFLX) for precipitation; and 1-hourly average 2D radiation diagnostics (M2T1NXRAD) for radiation quantities \cite{merra2}.
+Vertically resolved fields in M2I3NVASM start at a height of about 60 m, which limits our analysis of fog and near-surface clouds in this reanalysis.
 
@@
 TOA radiation quantities are taken from the CERES instruments onboard the Terra and Aqua satellites \cite{wielicki1996,loeb2018}.
-In our analysis, we used the adjusted all-sky SW and LW upwelling fluxes at TOA from the synoptic TOA and surface fluxes and clouds 1-degree daily edition 4A product (CER\_SYN1deg-Day\_Terra-Aqua-MODIS\_Edition4A) \cite{doelling2013,doelling2016}.
+In our analysis, we used adjusted all-sky SW and LW upwelling fluxes at TOA, adjusted cloud liquid and ice water paths, and adjusted cloud amount from the synoptic TOA and surface fluxes and clouds 1-degree daily edition 4A product (CER\_SYN1deg-Day\_Terra-Aqua-MODIS\_Edition4A) \cite{doelling2013,doelling2016}.
+The water paths in the product are computed from optical depth and particle size from geostationary satellites and the Moderate Resolution Imaging Spectroradiometer [MODIS, \citeA{pagano1993}] \cite{ceres2025}.
+The water paths were multiplied by the cloud amount to get the water path relative to the whole grid cell area, equivalent to the definition used in the models.
 
-Radiation calculations presented in the results (Section~\ref{sec:results}) were completed such that they always represent daily means in order to be consistent with the CERES SYN1deg data.
-Therefore, every instantaneous profile in the simulated lidar data was assigned a daily mean radiation value corresponding to the day (in the Coordinated Universal Time; UTC).
-In turn, the average radiation during the entire voyage or station observation period was calculated as the average of the profile values.
-In the observed lidar data, the daily mean radiation value was taken from the spatially and temporally co-located CERES SYN1deg data for the day (in UTC).
+Radiation and water path calculations presented in the results (Section~\ref{sec:results}) were completed such that they always represent daily means in order to be consistent with the CERES SYN1deg data.
+Therefore, every instantaneous profile in the simulated lidar data was assigned a daily mean radiation and water path value corresponding to the day (in the Coordinated Universal Time; UTC).
+In turn, the average radiation and water paths during the entire voyage or station observation period were calculated as averages of the profile values.
+In the observed lidar data, the daily mean values were taken from the spatially and temporally co-located CERES SYN1deg data for the day (in UTC).
 The voyage or station average was calculated in the same way.
@@
 This is undesirable if equivalent precipitation backscatter is not included in the simulated lidar profiles.
-It was not possible to include precipitation simulation in the ALCF due to the absence of required fields in the ICON model output and the reanalysis data (the liquid and ice precipitation mass mixing ratios).
+It was not possible to include precipitation simulation in the ALCF due to the absence of required fields of liquid and ice precipitation mass mixing ratios in the model output.
+While the fields could in principle be calculated from surface fluxes, such a calculation would be highly uncertain.
 The required radiation calculations for precipitation are also currently not implemented in the ALCF, even though this is a planned future addition.
 In order to achieve a fair comparison of observations with model output, we exclude observed and simulated lidar profiles with precipitation, either manually or using an automated method.
-It is relatively difficult to distinguish precipitation backscatter from cloud backscatter in lidar observations, especially when only one wavelength channel and no polarized channel are available.
+It is relatively difficult to distinguish precipitation backscatter from cloud backscatter in lidar observations, especially when only one wavelength channel and no polarized channel are available \cite{kim2020}.
 In models, the same can be accomplished relatively easily by excluding profiles exceeding a certain surface precipitation flux.
@@
 
+In our analysis we partitioned our dataset by cyclonic activity and stability into multiple subsets in order to evaluate cloud biases in the context of the main physical controlling processes.
+The SO is a region of occurrence of both extratropical and polar cyclones.
+Cyclonic activity results in cloud formation at the air mass boundaries along the cold and warm fronts, as well as inside the cold sector, after a passing cold sector destabilizes the atmosphere relative to the surface temperature.
+In the cold front and cold sector, clouds are convectively driven, including deep convection, and the advection of colder air masses over warmer ocean surfaces can trigger convection and subsequent cloud formation.
+Conversely, warm advection can trigger fog or cloud formation by boundary layer air cooled by the ocean surface until it reaches saturation.
+More quiescent areas outside of cyclones can also be associated with clouds.
+These can be, for example, associated with clouds formed by warm or cold advection outside of cyclones, persistent clouds, clouds formed due to diurnal heating or cooling, or due to ocean currents.
+Boundary layer stability can be expected to be associated with clouds by either allowing convection and turbulence under weak stability, inhibiting convection turbulence under strong stability, and by capping inversion controlling the cloud top height or trapping moist air near the surface and preventing fog dispersion.
+Therefore, dividing our dataset by these subsets allows us to quantify model biases associated with some of the main physical processes controlling cloud formation, persistence, and dissipation.
+Other methods of subsetting, such as using the ISCCP pressure--optical thickness diagram \cite{rossow1991,rossow1999,hahn2001} to separate profiles by cloud regimes and other cloud regime classifications \cite{oreopoulos2016,schuddeboom2018}, would be feasible.
+
 We partitioned our data into two mutually exclusive subsets by cyclonic activity.
@@
 The CyTRACK algorithm uses mean sea level pressure and wind speed thresholds as well as tracking across time steps to identify cyclone centers and radii in each time step.
-With this information, we could classify geographical areas as either cyclonic or non-cyclonic.
+With this information, we could classify every location at a given time as either cyclonic or non-cyclonic.
 Due to a relatively small total area covered by cyclones (as identified by the cyclone center and radius), we chose a circle of double the radius (relative to one identified by CyTRACK) centered at the cyclone center as a cyclonic area for every time step and cyclone.
@@
 \citeA{mcerlich2023} have shown that wind is simulated well in ERA5 relative to the WindSat polarimetric microwave radiometer measurements \cite{meissner2009}.
-For identifying cyclones in ICON, its own pressure and wind fields were used as the input to CyTRACK, because the model is free-running, and thus the pressure and wind fields are different from reality.
+For identifying cyclones in ICON, its own pressure and wind fields were used as the input to CyTRACK because the model is free-running, and thus the pressure and wind fields are different from reality.
 Subsetting by proximity to cyclones is a relatively crude measure because it does not take into account the different sectors of cyclones, which are commonly associated with different weather situations.
 However, this was a choice made for simplicity of the analysis, given the quantity of data.
+\citeA{konstali2024} performed a more complex attribution of precipitation to individual cyclone features.
 
 In addition to the above, we partitioned our data into two mutually exclusive subsets based on LTS, which is derived as the difference between the potential temperature at 700~hPa and the surface.
-Based on a histogram of LTS in ERA5 and MERRA-2 calculated at all voyage tracks and stations (Fig.~\ref{fig:lts}), we determined a statistically-based dividing threshold of 12~K for weak stability ($<$~12~K) and strong stability ($\geq$~12~K) conditions.
+Based on a histogram of LTS in ERA5 and MERRA-2 calculated at all voyage tracks and stations (Fig.~\ref{fig:lts}), we determined a statistically based dividing threshold of 12~K for weak stability ($<$~12~K) and strong stability ($\geq$~12~K) conditions.
 
@@
 \centering
-\includegraphics[width=\textwidth]{img/cyc_stab_dist.pdf}
+\includegraphics[width=\textwidth]{img/cyc_stab_dist_rev1.pdf}
 \caption{
@@
 Cyclonic days are expressed as a fraction of the number of days with cyclonic activity, defined as grid points located within a double radius of any cyclone on a given day (UTC), as identified by CyTRACK.
+The voyage tracks and the point of the MICRE campaign are also shown.
 }
@@
 Fig.~\ref{fig:cyclone-stability}c, d show the geographical distribution of the conditions of weak and strong stability as determined by the LTS (Section~\ref{sec:cyclone-stability}).
-Conditions of weak stability are prevalent in the mid-to-high SO (with respect to our SO partitioning; 50--65°S), which might be explained by the relatively cold near-surface air overlying the relatively warm sea surface.
-Conditions of strong stability are prevalent elsewhere over the SO.
+Conditions of weak stability are prevalent in the mid-to-high SO (50--65°S), which might be explained by the relatively cold near-surface air overlying the relatively warm sea surface.
+Conditions of strong stability are common elsewhere over the SO.
 The distribution is also less zonally symmetric than the cyclonic activity.
 In the high-latitude SO, the presence of sea ice might have a substantial stabilizing effect \cite{knight2024}.
-The ERA5 reanalysis is also substantially more stable than ICON across the whole region.
-
-\begin{figure}[p!]
-\centerline{
-\includegraphics[width=1.06\textwidth]{img/cloud_occurrence_panel.pdf}
-}
-\caption{
-Cloud occurrence by height for the 31 voyages and one sub-Antarctic station (MICRE) in observations (O) and simulated by the ALCF from the ICON model (I), MERRA‐2 (M), and ERA5 reanalysis data (E).
-The numbers in the legend indicate the total cloud fraction and the number of days of data.
-Multiple lines of ICON profiles are for each of the four years of model data available.
-}
-\label{fig:cloud-occurrence-panel}
-\end{figure}
+ICON is also substantially less stable than ERA5 across the whole region.
+In Section~\ref{sec:thermodynamic-profiles} we show that based on radiosonde observations, the bias is in ICON and not ERA5, and it is the result of underestimated temperature at heights corresponding to 700 hPa, as well as overestimated near-surface air temperature, characterized by a higher frequency of occurrence in the 1--7°C range compared to observations at radiosonde launch locations (Fig.~\ref{fig:stats-hist-surf}a).
+This may be related to large-scale circulation in the model or radiative transfer biases.
 
@@
 The results for all campaigns individually are shown in Fig.~\ref{fig:cloud-occurrence-panel}.
+As shown in this figure, the biases are relatively consistent across the campaigns and longitudes.
 In addition, we aggregated the campaigns by calculating the averages and percentiles of all individual profiles, presented in Fig.~\ref{fig:cloud-occurrence}.
-The analysis shows that the total cloud fraction (defined as the fraction of profiles with clouds at any height in the lidar cloud mask) is underestimated in ICON by about 10\% and in the reanalyses by about 20\%.
+The analysis shows that the total cloud fraction is underestimated in ICON by about 10\% and in the reanalyses by about 20\%.
 When analyzed by height, ICON overestimates cloud occurrence below 1 km and underestimates it above; MERRA-2 underestimates cloud occurrence at all heights by up to 10\%, especially near the surface; and ERA5 simulates cloud occurrence relatively well above 1 km but strongly underestimates it near the surface.
 We note that fog or near-surface clouds are strongly underestimated in the reanalyses (fog and clouds are both included in the cloud occurrence).
-As shown in Fig.~\ref{fig:cloud-occurrence-panel}, the biases are relatively consistent across the campaigns and longitudes.
 We conclude that the ICON results match the observations better than the reanalyses in this metric.
 
-For all observations considered (Fig.~\ref{fig:cloud-occurrence}a), the data show cloud occurrence peaking nearly at the surface, whereas the models show a higher peak (at about 500~m).
-The models generally underestimate the total cloud fraction by 10--20\% and show a strong reduction in cloud occurrence near the surface, which is not identified in the observations.
+For all observations considered (Fig.~\ref{fig:cloud-occurrence}a), the data show cloud occurrence peaking near the surface, whereas the models show a higher peak (at about 500~m).
+The models generally underestimate the total cloud fraction by 10--30\% and show a strong drop in cloud occurrence near the surface, which is not identified in the observations.
 ICON and ERA5 overestimate cloud occurrence at their peak (between 0 and 1~km).
 Above 1~km, ICON and MERRA-2 underestimate cloud occurrence, but ERA5 is accurate to about 3\% or less.
-The exaggerated peak in models is partly explained by the lifting condensation level (LCL) distribution, which peaks about 200~m higher in the models than in the observations (nearly at the surface), although this is not very pronounced.
-This is indicative of near-surface relative humidity being often close to saturation in the observations but not in the models.
+The exaggerated peak in models is partly explained by the lifting condensation level (LCL) distribution, which peaks about 300~m higher in the models than in the observations (near the surface), although this is not very pronounced.
+This is indicative of near-surface relative humidity often being close to saturation in the observations but not in the models (Fig.~\ref{fig:stats-hist-surf}b).
+There are multiple possible reasons for this bias, such as how the statistical distribution of RH within a grid cell is represented in the models, the air--sea moisture flux parameterization, or weaker stability in the models can cause more boundary mixing across heights and thus lower near-surface RH.
 
-When subsetted by latitude (Fig.~\ref{fig:cloud-occurrence}b, c), we see that the low-latitude SO zone displays a stronger peak of cloud occurrence near the surface than the high-latitude SO zone, and this could be because higher latitudes have less stable atmospheric profiles.
+When subsetted by latitude (Fig.~\ref{fig:cloud-occurrence}b, c), we see that the low-latitude SO zone (40--55°S) displays a stronger peak of cloud occurrence near the surface than the high-latitude SO zone (between 55°S and the Antarctic coast), and this could be because higher latitudes have greater prevalence of weakly stable profiles (Fig.~\ref{fig:cyclone-stability}c, d), although more stable profiles populate regions south of 65°S close to the Antarctic coast.
+Cyclonic activity is also stronger in high-latitude SO, which is typically associated with shallow or deep convection rather than very stable stratification necessary for fog formation.
 The low- and high-latitude SO zones show similar biases in models as in the general case, but ERA5 does not overestimate the peak in the low-latitude SO zone (near-surface cloud occurrence is still strongly underestimated).
 
-When subsetted by cyclonic and non-cyclonic situations (Fig.~\ref{fig:cloud-occurrence}d, e), we see that the cyclonic situations have a larger amount of observed cloudiness, including peak and total cloud fraction, both by about 7\%.
-In the cyclonic situations, the model vertical profiles of cloud occurrence compare well with observations, but they peak higher by about 200 m and larger by about 8\%.
-The reanalyses still tend to underestimate cloud occurrence above 1 km by about 5\% and near the surface by about 14\%.
-Non-cyclonic situations are similar to the general case, partially also because they form the majority of cases.
+When subsetted by cyclonic and non-cyclonic situations (Fig.~\ref{fig:cloud-occurrence}d, e), we see that the cyclonic situations have a larger amount of observed cloudiness, including peak and total cloud fraction, by about 10\%.
+In the cyclonic situations, the model vertical profiles of cloud occurrence compare well with observations, but they peak higher by about 200 m and are larger by about 8\%.
+The reanalyses tend to underestimate cloud occurrence above 1 km by about 5\% and near the surface by about 15\%.
+Non-cyclonic situations are similar to the general case, also because they form the majority of analyzed profiles (83\%).
 
-When subsetted by conditions of weak and strong stability (Fig.~\ref{fig:cloud-occurrence}f, g), as defined in Section~\ref{sec:cyclone-stability}, we see that in situations of strong stability, cloud occurrence peaks strongly near the surface in observations, compared to situations of weak stability, where the peak is more diffuse between 0 and 1~km.
-It is worth mentioning that conditions of strong stability might be associated with the formation of advection fog, such as in situations of warm air advection from the north over a colder sea surface, thus inducing fog formation by cooling of the warm and humid air by the cold surface.
-In situations of strong stability, the models have smaller biases than in weak stability, with an overestimated peak by up to 12\%, underestimated cloud occurrence above 1~km by up to 5\%, and underestimated cloud occurrence near the surface by about 11\%.
-In situations of weak stability, the bias in ICON is very pronounced, with a much larger peak in cloud occurrence at about 500~m; ERA5 underestimates cloud occurrence below 1~km (especially near the surface); and MERRA-2 underestimates cloud occurrence even more strongly.
+When subsetted by conditions of strong and weak stability (Fig.~\ref{fig:cloud-occurrence}f, g), as defined in Section~\ref{sec:cyclone-stability}, we see that in situations of strong stability, cloud occurrence peaks strongly near the surface in observations, compared to situations of weak stability, where the peak is more diffuse between 0 and 1~km.
+Physically, conditions of strong stability are associated with the formation of advection fog, such as in situations of warm air advection from the north over a colder sea surface, thus inducing fog formation by cooling of the warm and humid air by the cold surface.
+In situations of strong stability, the models have smaller biases than in weak stability, with an overestimated peak up to 12\%, underestimated cloud occurrence above 1~km by up to 5\%, and underestimated cloud occurrence near the surface by about 10\% in the reanalyses but not ICON.
+In situations of weak stability, the bias in ICON is very pronounced, with a much larger peak in cloud occurrence at about 500~m; the reanalyses underestimate cloud occurrence below 1~km, especially near the surface; and MERRA-2 underestimates cloud occurrence more strongly at almost all heights.
 
-In all situations, even when the models overestimate cloud occurrence at some altitudes, they always substantially underestimate the total cloud fraction.
-ICON can be generally characterized as substantially overestimating cloud occurrence below 1 km and underestimating above, underestimating the total cloud fraction, and showing the greatest biases in conditions of weak stability and non-cyclonic conditions.
+In all subsets, even when the models overestimate cloud occurrence at some altitudes, they always substantially underestimate the total cloud fraction.
+ICON can be generally characterized as substantially overestimating cloud occurrence below 1~km and underestimating above, underestimating the total cloud fraction, and showing the greatest biases in conditions of weak stability and non-cyclonic conditions.
 ICON also has a peak cloud occurrence at higher altitudes than observations (500~m vs.
@@
 MERRA-2 can be generally characterized as underestimating cloud occurrence at nearly all altitudes as well as the total cloud fraction, but mostly above and below 500~m (the peak at 500~m is well represented).
-MERRA-2 displays the largest errors relative to observations in the low-latitude SO zone and in situations of weak stability.
+MERRA-2 displays the largest errors relative to observations in the low-latitude SO zone and under weak stability.
 ERA5 can be generally characterized as representing cloud occurrence correctly above about 1.5~km, overestimating between 500~m and 1~km, but underestimating near-surface cloud occurrence (0--500~m).
-The total cloud fraction is strongly underestimated in all situations.
-ERA5 has a tendency towards underestimation in the low-latitude SO zone and situations of weak stability; conversely, it overestimates in the high-latitude SO zone and conditions of strong stability.
+The total cloud fraction is strongly underestimated in all subsets.
+ERA5 has a tendency towards greater cloud underestimation in the low-latitude SO zone and under weak stability; conversely, it overestimates the peak of cloud occurrence at 500~m in the high-latitude SO zone and under strong stability.
 
@@
 \centering
-\includegraphics[width=\textwidth]{img/cl_agg.pdf}
+\includegraphics[width=\textwidth]{img/cl_agg_rev1.pdf}
 \caption{
@@
 
-\subsection{Top of Atmosphere Radiation}
-
-In Fig.~\ref{fig:cloud-occurrence}, we also display the mean outgoing shortwave and longwave top-of-atmosphere radiation, whose calculation is described in Section~\ref{sec:ceres}.
-In observations, these come from daily mean CERES measurements averaged over the voyage tracks or a station location, whereas in the models they come from daily means of TOA radiation in the model output averaged over the same location and time periods.
-In the free-running ICON model, the time period is mapped onto the available years, as explained in Section~\ref{sec:icon}.
-
-In the general case (Fig.~\ref{fig:cloud-occurrence}a), ICON underestimates the outgoing SW radiation by 26 Wm$^{-2}$, and the MERRA-2 and ERA5 reanalyses overestimate it by 6 and 14 Wm$^{-2}$, respectively.
-While in ICON, this is in line with the underestimated total cloud fraction of 10\%, in the reanalyses this is the opposite result to that expected from the underestimated total cloud fraction of about 20\%.
-The likely explanation is an overestimated cloud albedo, compensating for the lack of cloud area.
-
-We note that the radiative transfer calculations used in the lidar simulator mean that the impact of both cloud phase and cloud fraction are convolved to produce the cloud mask.
-Therefore, the cloud occurrence is not affected by any cloud phase biases as long as the cloud is optically thick enough to be detected, and the laser signal is not too attenuated.
-However, a combination of underestimated total cloud fraction and overestimated outgoing SW at TOA is indicative of an overestimated cloud albedo due to either cloud liquid and ice water content, cloud phase, droplet or ice crystal size distribution, shape or orientation of ice crystals, or cloud overlap.
-
-In contrast, LW radiation has much smaller biases than SW radiation, which is expected due to the prevailing low-level clouds having similar temperature as the surface.
-In ICON, the outgoing LW radiation is overestimated by 8\%, which could be caused by an underestimated total cloud fraction exposing a larger sea surface area to cooling to space, which is typically warmer than the atmospheric temperature at 0--2~km, where most of the clouds are located.
-In the MERRA-2 and ERA5 reanalyses, the LW biases are also slightly positive, 4 and 7~Wm$^{-2}$, respectively.
-This is again in line with the underestimated total cloud fraction by about 20\%.
-However, if the clouds are too thick, as expected from the SW results, this might also provide a compensating effect, in which too small a cloud area is counteracted by greater thermal emissivity, thus reducing the outgoing LW radiation more relative to thinner clouds.
-For thin clouds, the outgoing TOA LW radiation originates both from the warmer surface (partly blocked by the clouds) and the clouds, whereas for thick clouds, the outgoing TOA LW radiation originates mostly from the colder-than-surface clouds.
-
-In all the subsets (Fig.~\ref{fig:cloud-occurrence}b--g), the same type of biases are observed, namely the outgoing SW radiation is underestimated in ICON and overestimated in MERRA-2 and ERA5, and the outgoing LW radiation is overestimated in all the models.
-Even though the total cloud fraction is lower by 7\% over the high-latitude SO than the low-latitude SO, the outgoing SW radiation is much greater by 41~Wm$^{-2}$, implying a much greater cloud albedo over the high-latitude SO.
-The ICON model output displays the same contrast between these two regions in the total cloud fraction and SW radiation, but the outgoing SW radiation difference between the regions is much smaller (16~Wm$^{-2}$).
-The reanalyses do not show this type of contrast between the regions.
-The physical reason for this might be that the prevalence of fog or low-level clouds over the low-latitude SO and their relative lack over the high-latitude SO in observations is not reproduced in the models (Fig.~\ref{fig:cloud-occurrence}b--c).
-
-\subsection{Cloud Cover}
+\subsection{Daily Cloud Cover}
 \label{sec:cloud-cover}
@@
 The same calculation is done for the lidar observations as for the simulated lidar profiles.
-We use the term ``okta'' independently of its use in instantaneous synoptic observations, and here it simply means 1/8 (0.125\%) of the daily cloud cover.
+We use the term ``okta'' independently of its use in instantaneous synoptic observations, and here it simply means 1/8 (0.125) of the daily cloud cover.
 
@@
 \centering
-\includegraphics[width=\textwidth]{img/clt_hist.pdf}
+\includegraphics[width=\textwidth]{img/clt_hist_rev1.pdf}
 \caption{
@@
 
+\subsection{Top of Atmosphere Radiation, Liquid and Ice Water Path}
+
+In Fig.~\ref{fig:cloud-occurrence}, we also show the mean outgoing shortwave and longwave top-of-atmosphere radiation, whose calculation is described in Section~\ref{sec:ceres}.
+In observations, these come from daily mean CERES measurements averaged over the voyage tracks or a station location, whereas in the models they come from daily means of TOA radiation in the model output averaged over the same location and time periods.
+
+In the general case (Fig.~\ref{fig:cloud-occurrence}a), ICON and ERA5 underestimate the outgoing SW radiation by 22 and 20 Wm$^{-2}$ (respectively), and MERRA-2 overestimates it by 6 Wm$^{-2}$.
+While in ICON and ERA5, this is in line with the underestimated total cloud fraction of 10\% and 22\% (respectively); in MERRA-2, the opposite result is expected from the underestimated total cloud fraction of about 20\%.
+Neglecting the direct radiative effects of sea and aerosol, this is only possible if the albedo of cloudy areas is overestimated, compensating for the lack of cloudy areas.
+
+We note that the radiative transfer calculations used in the lidar simulator mean that the impact of both cloud phase and cloud fraction are convolved to produce the cloud mask.
+Therefore, the cloud occurrence is not affected by any cloud phase biases as long as the cloud is optically thick enough to be detected and the laser signal is not too attenuated.
+A combination of underestimated total cloud fraction and overestimated outgoing SW at TOA is indicative of an overestimated cloud albedo (in cloudy areas) due to either cloud liquid and ice water content, cloud phase, droplet or ice crystal size distribution, shape or orientation of ice crystals, cloud overlap, or their combination.
+The influence of cold clouds is likely second-order due to the much larger typical effective radius of ice crystals than cloud droplets.
+
+In contrast to SW radiation, the models have much smaller LW radiation biases, which is expected due to the prevailing low-level clouds having similar temperatures as the surface.
+\citeA{roh2021} also found LW biases to be much lower than SW biases in DYAMOND models over the tropical Atlantic Ocean.
+In ICON, the outgoing LW radiation is overestimated by 5\% (Fig.~\ref{fig:cloud-occurrence}a).
+This is likely caused by an underestimated total cloud fraction exposing a larger sea surface area to cooling to space, which is typically warmer than the atmospheric temperature at 0--2~km, where most of the clouds are located.
+In the MERRA-2 and ERA5 reanalyses, the LW biases are also slightly positive, 4 and 5~Wm$^{-2}$, respectively.
+This is again in line with the underestimated total cloud fraction by about 20\%.
+However, if the clouds are too thick, as expected from the SW results, this might also provide a compensating effect, in which too small a cloud area is counteracted by greater optical thickness in the LW spectrum, thus reducing the outgoing LW radiation more relative to thinner clouds.
+For thin clouds, the outgoing TOA LW radiation originates both from the warmer surface (partly blocked by the clouds) and the clouds, whereas for thick clouds, the outgoing TOA LW radiation originates mostly from the colder-than-surface clouds.
+
+In all the subsets (Fig.~\ref{fig:cloud-occurrence}b--g), the same type of biases are observed, namely the outgoing SW radiation is underestimated in ICON and ERA5 and overestimated in MERRA-2, and the outgoing LW radiation is overestimated in all the models.
+Even though the total cloud fraction is higher by 6\% over the high-latitude SO than the low-latitude SO, the outgoing SW radiation is much greater by 41~Wm$^{-2}$, implying a much greater cloud albedo (of cloudy areas) over the high-latitude SO.
+ICON has little difference in the total cloud fraction between low- and high-latitude SO, but greater outgoing SW radiation by 14~Wm$^{-2}$ over the high-latitude SO, likely due to thicker clouds under deeper convection in less stable and more cyclonic conditions relative to the low-latitude SO.
+In contrast, the reanalyses showed both greater total cloud fraction and outgoing SW radiation over the high-latitude SO compared to the low-latitude SO.
+
+Fig.~\ref{fig:stats-hist} shows the SW and LW radiation, liquid water path (LWP), and ice water path (IWP) distributions as histograms and their corresponding averages.
+LWP and IWP are calculated from the mass of water in the column divided by the area of the column, i.e.
+not just the area of the cloudy portion of the column, as in some definitions.
+ERA5 and ICON overestimate outgoing SW near 80 Wm$^{-2}$ (Fig.~\ref{fig:stats-hist}a), which probably relates to clear sky situations, as expected from the underestimated cloud fraction.
+They also underestimate the highly reflective situations above 200 Wm$^{-2}$.
+MERRA-2 exhibits the too few, too bright problem in terms of overestimating SW reflectivity around 290 Wm$^{-2}$, given that the total cloud fraction in MERRA-2 is strongly underestimated.
+The LW distribution shows that all of the models overestimate outgoing LW (Fig.~\ref{fig:stats-hist}b), which is expected from the underestimated cloud fraction, exposing more of the warmer ocean surface relative to colder clouds.
+The LWP distribution shows that all models overestimate cases with near-zero LWP (Fig.~\ref{fig:stats-hist}c), which relates to the underestimated total cloud fraction.
+MERRA-2 shows quite overestimated high-LWP situations, which is most likely related to the too few, too bright problem of simulating lower total cloud fraction but clouds with higher LWP to compensate.
+IWP (Fig.~\ref{fig:stats-hist}d) is somewhat less important radiatively than LWP because of the typically larger and less numerous hydrometeors.
+Similarly to LWP, the models overestimate situations with near-zero IWP.
+ERA5 is otherwise simulating the IWP distribution well, but ICON and MERRA-2 underestimate IWP.
+Fig.~\ref{fig:stats-hist-cloudy} shows the same as Fig.~\ref{fig:stats-hist}, but for cloudy profiles only.
+This figure shows more distinctly that in cloudy situations, MERRA-2 overestimates moderate (0.05--0.15 kg m$^{-2}$) and high LWP (over 0.15 kg m$^{-2}$), and ERA5 and ICON underestimate moderate LWP.
+ICON also overestimates high LWP, resulting in overestimated average LWP.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=\textwidth]{img/stats_hist.pdf}
+\caption{
+Histograms and averages of outgoing \textbf{(a)} SW and \textbf{(b)} LW radiation at TOA, \textbf{(c)} liquid water path, and \textbf{(d)} ice water path in CERES SYN1deg observations (OBS), ICON, MERRA-2, and ERA5 along the voyage tracks.
+All voyages are weighted equally.
+The statistics are calculated from daily mean values corresponding to each time step and geographical location of the voyage tracks.
+}
+\label{fig:stats-hist}
+\end{figure}
+
 \begin{figure}[p!]
 \centering
-\includegraphics[width=0.72\textwidth]{img/theta_hur.pdf}
+\includegraphics[width=0.85\textwidth]{img/rs_agg_rev1.pdf}
 \caption{
@@
 
-\subsection{Thermodynamic Profiles}
+\subsection{Relative humidity and potential temperature profiles}
+\label{sec:thermodynamic-profiles}
 
-In order to examine the potential link in the cloud biases to the local physical conditions, we analyzed about 2300 radiosonde profiles south of 40°S from the 24 RV \emph{Polarstern} voyages, MARCUS, NBP1704, TAN1702, and TAN1802.
+In order to examine the potential link in the cloud biases to the local physical conditions, we analyzed about 2300 radiosonde profiles south of 40°S available from the 24 RV \emph{Polarstern} voyages and the MARCUS, NBP1704, TAN1702, and TAN1802 campaigns.
 Spatially and temporally colocated profiles were taken from ICON and the reanalyses.
 Because the time period covered by the ICON model output (2021--2024) was different from the time period covered by the observations (2010--2021), when comparing with the model, we first had to remap the observation time to model time by taking the same time relative to the start of the year.
-Consequently, we also had four virtual/model profiles (one for each year of 2021--2024) for each observed profile.
+Consequently, we also had four virtual/model profiles (one for each year from 2021 to 2024) for each observed profile.
 The profiles were partitioned into the same subsets as above (Sections~\ref{sec:cloud-occurrence} and \ref{sec:cloud-cover}).
-We focus on comparing virtual potential temperature ($\theta_v$) due to its role in low-level tropospheric stability, being one of the primary factors affecting shallow convection and the associated low-level cloud formation and dissipation.
-The observed and model profiles of virtual potential temperature are shown in Fig.~\ref{fig:potential-temperature}.
+We focus on comparing virtual potential temperature ($\theta_v$) and relative humidity, being one of the primary factors affecting shallow convection and the associated low-level cloud formation and dissipation.
+The observed and model profiles of virtual potential temperature and relative humidity are shown in Fig.~\ref{fig:potential-temperature}.
 
@@
 Relative humidity displays much larger biases.
-In all subsets, ICON is too humid in the first 1~km by about 5\% but very accurate above, except for the 40--55°S zone and conditions of weak stability (Fig.~\ref{fig:potential-temperature}b, g), where it is too dry between about 1 and 3~km.
-MERRA-2, on the other hand, is more humid than observations at all altitudes and in all subsets, by up to about 20\% at~5 km.
-Even though the mean near-surface relative humidity is similar to the observations (Fig.~\ref{fig:potential-temperature}), the distribution in observation is more spread out across both high and low values, and thus observations have a greater prevalence of relative humidity close to 100\% and thus LCL located at the surface (Fig.~\ref{fig:cloud-occurrence}a).
-In our calculations, LCL is an exclusive function of near-surface temperature, near-surface relative humidity, and surface pressure.
+In all subsets, ICON is too humid in the first 1~km by about 5\%, but very accurate above, except for the 40--55°S zone and conditions of weak stability (Fig.~\ref{fig:potential-temperature}b, g), where it is too dry between about 1 and 3~km.
+Even though relative humidity measured by radiosondes in the first 100~m is not very different between the observations and the models (Fig.~\ref{fig:potential-temperature}a), near-surface (2-m) relative humidity at the radiosonde launch locations is much greater in the observations, most often close to 100\%, unlike in the models, where 85\% tends to be the most common (Fig.~\ref{fig:stats-hist-surf}b).
+This also explains why LCL is much more frequently located at the surface in the observations than in the models (Fig.~\ref{fig:cloud-occurrence}a).
+LCL is fully determined by near-surface temperature, near-surface relative humidity, and surface pressure.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.6\textwidth]{img/rs_lts_hist.pdf}
+\caption{
+Histogram of lower tropospheric stability calculated from the observed radiosonde profiles and the corresponding model profiles. All campaigns are weighted equally.
+}
+\label{fig:rs-lts-hist}
+\end{figure}
+
+\begin{figure}[t]
+\centering
+\makebox[\textwidth][c]{\includegraphics[width=1.3\textwidth]{img/rs_hur_hist.png}}
+\caption{
+Relative humidity histograms calculated from the observed radiosonde profiles and the equivalent model profiles for \textbf{(a)} all bins, \textbf{(b)} clear bins, and \textbf{(c)} cloudy bins, determined from the lidar cloud mask.
+Model histogram values are relative to observations.
+The histogram values are normalized to 100\% for each level separately.
+All campaigns are weighted equally.
+}
+\label{fig:rs-hur-hist}
+\end{figure}
+
+Fig.~\ref{fig:rs-thetav-hur-cloud} shows virtual potential temperature and RH profiles for profiles containing fog, cloud at 500 m, and cloud at 1.5 km.
+These situations are characterized by particular cloud biases as identified in the lidar cloud occurrence analysis.
+The rationale is to examine $\theta_v$ and RH associated with these situations.
+Foggy situations are characterized by a rapid increase of $\theta_v$ with height and an observed average RH of about 90\% near the surface (Fig.~\ref{fig:rs-thetav-hur-cloud}a).
+In contrast, the models simulate higher RH in the first 100~m under foggy conditions by several percentage points.
+In situations with clouds occurring at 500 m, $\theta_v$ is relatively flat between the surface and 500 m (Fig.~\ref{fig:rs-thetav-hur-cloud}b), as expected for convectively driven clouds.
+The observed RH peaks at 500 m at about 90\%.
+The models, however, simulated higher RH between the surface and 500 m under these conditions.
+ICON and ERA5 show a stronger decrease of RH above this height than observations, and ERA5 shows more strongly stable stratification.
+Unlike the foggy and 500-m cloud situations, situations with clouds at 1.5 km do not have a flat $\theta_v$ with height.
+This indicates that unlike the former, clouds at 1.5 km are not (or not as strongly) convectively driven.
+As expected, RH in these situations peaks at 1.5 km at about 85\% in observations.
+In the models, this peak is much less pronounced.
+
+Fig.~\ref{fig:rs-lts-hist} shows the histogram of LTS calculated from all radiosonde profiles and the corresponding profiles in the models.
+It can be seen that ICON substantially underestimates the occurrence of cases of strong stability above 16 K while overestimating the cases of moderate stability (8 to 16 K).
+When considered together with the cloud occurrence results presented in Fig.~\ref{fig:cloud-occurrence}, we see that since the model is biased towards weak stability, it overrepresents cloud profiles strongly peaking at 500 m (Fig.~\ref{fig:cloud-occurrence}g) over cloud profiles with fog or near-surface cloud (Fig.~\ref{fig:cloud-occurrence}f).
+This can be a physical reason for its overall positive bias in cloud at 500 m (Fig.~\ref{fig:cloud-occurrence}a) instead of the observed cloud occurrence profile peaking near the surface.
+The reanalyses simulate the LTS distribution well except for a slight underestimation of LTS.
+
+Fig.~\ref{fig:rs-hur-hist} shows RH histograms calculated from the radiosonde observations and equivalent profiles in the models (shown as anomalies relative to the observations), calculated for all, clear, and cloudy bins, based on the lidar observations and the simulated lidar backscatter in the models.
+Here, we show only the first 2 km to concentrate on the identified cloud biases seen at these heights.
+We can see several notable features.
+The models simulate progressively fewer high-RH (\textgreater 90\%) bins above the ground (Fig.~\ref{fig:rs-hur-hist}b--d).
+This can be related to either ice nucleation happening in the models, which requires smaller RH for saturation, or the grid cell size in the models, which requires lower grid cell average RH than 100\% for saturation to occur in a fraction of the grid cell.
+The models also tend to simulate more clear bins than observations for RH between 80 and 100\% between the ground and about 1 km (Fig.~\ref{fig:rs-hur-hist}f--h).
+In observations, these values of RH are associated with cloudy bins (Fig.~\ref{fig:rs-hur-hist}i).
+Conversely, the models predominantly associate only RH very close to 100\% with cloudy bins at these heights (Fig.~\ref{fig:rs-hur-hist}j--l).
+This may be one of the main reasons for the identified cloud or fog biases near the ground.
+A possible explanation is that cloud droplets are able to form or persist at RH between 90 and 100\% at these heights over the SO.
+This could be due to abundant sea salt or biogenic aerosol or droplet generation from sea spray in the common high swell and high wind speed conditions over the SO.
+Stratus fractus or other broken clouds could also lead to less than 100\% RH when averaged over the size of the vertical bins (up to 30 m in some of the radiosonde profiles).
+
+Fig.~\ref{fig:rs-thetav-hist} shows histograms the same as the previous figure, but for virtual potential temperature.
+They show a more complex picture, characterized by a central peak at about 0°C near the surface, increasing to about 5°C at 2 km (Fig.~\ref{fig:rs-thetav-hist}a).
+For cloudy bins, the central peak is generally flatter with height and even shows a minimum in $\theta_v$ at about 500 m (Fig.~\ref{fig:rs-thetav-hist}i).
+This is indicative of convection being associated with clouds at these heights, which results in flat virtual potential temperature profiles.
+In the reanalyses, in the first 200 m, values slightly above 0°C are associated with more clear bins than in observations, and values slightly below 0°C with fewer (Fig.~\ref{fig:rs-thetav-hist}g--h).
+Conversely, the opposite is true for cloudy bins (Fig.~\ref{fig:rs-thetav-hist}k--l).
+Situations with 0°C near-surface air temperature might occur predominantly when open ocean surface keeps the near-surface air temperature close to 0°C under otherwise colder air mass conditions, such as under cold advection.
+ICON displays a notable bias above about 1 km, where the central peak is strongly underestimated (Fig.~\ref{fig:rs-thetav-hist}j).
+Instead, these heights and values of $\theta_v$ are more associated with clear bins (Fig.~\ref{fig:rs-thetav-hist}f).
+This might be related to the strong underestimation of cloud occurrence at these heights.
 
@@
 Therefore, our results are likely representative of summer and, to a lesser extent, spring and autumn conditions.
+Cloud regimes and phase in the region are seasonally variable \cite{danker2022}.
 
@@
 The interannual variability in cloud occurrence in ICON can be seen in Fig.~\ref{fig:cloud-occurrence-panel}, where each year in ICON is represented by a separate line.
-The interannual variability tends to be substantially smaller than the biases and thus is unlikely to have a strong impact on the main findings.
+As could be expected, the interannual variability tends to be substantially smaller than the biases and thus is unlikely to have a strong impact on the main findings.
+
+It would be possible to use short-term ICON simulations for almost one-to-one comparison to observations.
+However, here we focus on long-term biases, which are statistically more robust.
+Our analysis is, therefore, complementary to shorter process-level studies.
+The reanalyses pose the difficulty of determining how much assimilated observations impact the results.
+While one might expect temperature and RH profiles to be well represented in the reanalyses due to assimilation of satellite data, we see that this is not always the case in comparison with the radiosonde profiles and near-surface meteorological observations.
+This could be due to the limited vertical accuracy of satellite sounding measurements and obscuration by clouds.
+Despite the assimilation, the cloud and radiation biases are often comparable to or greater than in the free-running model.
 
 Ground-based lidar observations are affected by attenuation by thick cloud layers, and for this reason the results are most representative of boundary layer clouds, while higher-level clouds are only occasionally visible to the lidar when boundary layer clouds are not present.
-Ground-based lidar observations can be regarded as superior to satellite lidar observations for low-level clouds, which are predominant in this region, while mid- and high-level clouds are likely better sampled by satellite observations \cite{mcerlich2021}.
+Ground-based lidar observations can be regarded as complementary to satellite lidar observations for the evaluation of low-level clouds, which are predominant in this region, while mid- and high-level clouds are likely better sampled by satellite observations \cite{mcerlich2021}.
+Ground-based observations are, however, complicated by precipitation, and satellite observations can also be used if the effect of overlapping clouds is carefully eliminated.
 Near-surface lidar retrievals ($\sim$100~m) are affected by uncertainties related to incomplete overlap, signal saturation (dead time), and after-pulse effect corrections \cite{kuma2021}.
 
-We have attempted to remove lidar profiles with precipitation, which could not be properly simulated with the lidar simulator (Section~\ref{sec:ann}).
+Supercooled liquid clouds (liquid clouds under subzero temperature) commonly occur over the SO.
+In our analysis of LWP and IWP, we see that both phases are abundant.
+Because liquid water droplets are typically smaller and more numerous than ice crystals in cold clouds, they attenuate a greater amount of the lidar radiation.
+Clouds with a relatively modest optical thickness of 1.7 can attenuate the lidar signal for a detection at 2 km using an instrument with noise properties like the Vaisala CL31 (Section 2.4).
+While supercooled liquid clouds and their attenuation are accounted for by the lidar simulator, they can strongly attenuate the signal and cause artifically low values of cloud occurrence at higher altitudes.
+For example, we found that cloud occurrence at 1.5 km is underestimated in ICON and underlying clouds are overestimated.
+However, this can also mean that clouds at 1.5 km are present in the model but the signal is too attenuated by the lower clouds in the model but not in the observations, where the underlying clouds are not as pronounced.
+
+We have attempted to remove lidar profiles with precipitation (about 26\% of all profiles), which could not be properly simulated with the lidar simulator (Section~\ref{sec:ann}).
 However, the approach was limited by the relatively low sensitivity of the ANN (65\%) and the fact that we had to choose a fixed threshold for surface precipitation flux in the model and reanalyses, which might not correspond to detection by the ANN applied to observations.
@@
 
+Subsetting by cyclonic activity and stability is done based on the ERA5 data.
+As we have shown, the reanalyses also suffer from biases in near-surface and upper-level quantities.
+Therefore, the subsetting is limited by the accuracy of the ERA5 pressure field, near-surface temperature, and temperature at 700~hPa.
+Near-surface ship observations are affected by the ship structures as well as the variable height above sea level at which the measurements are taken.
+The accuracy of radiosonde measurements in the first tens of meters from the surface is also likely affected by the ship environment, such as turbulence generated by ship structures and the ship exhaust.
+Vertical averaging of the radiosonde data can result in lower RH near saturation due to averaging of drier and moister layers together.
+For example, some of the RV \textit{Polarstern} radiosondes are available in vertical resolution of about 20--30 m.
+The satellite retrieval of LWP is affected by large biases, especially over high latitudes \cite{khanal2020}, which limits our comparison with the models.
+
 \section{Discussion and Conclusions}
 
-We analyzed a total of about 2400 days of lidar and 2300 radiosonde observations from 31 voyages/campaigns and the Macquarie Island subantarctic station, covering the Atlantic, Australian, and New Zealand sectors of the SO over the span of 10 years.
+\begin{table}[t]
+\caption{Summary of the main biases.
+Values are relative to observations and rounded to the nearest 5, except for daily cloud cover and RH, which are rounded to the nearest integer.
+The best-performing value is marked in \textbf{bold}.
+Abbreviations: boundary layer (BL), relative humidity (RH), shortwave (SW), longwave (LW), liquid water path (LWP), ice water path (IWP), and lifting condensation level (LCL).}
+\label{tab:summary}
+\centering
+\begin{tabular}{llll}
+& ICON & MERRA-2 & ERA5\\
+\hline
+Total cloud fraction (\%) & \textbf{-10} & -20 & -20\\
+Daily cloud cover (okta) & \textbf{-1} & -2 & -2\\
+Fog (\%) & \textbf{0} & -10 & -10\\
+BL clouds (at $\sim$500 m) & 15 & \textbf{0} & 5\\
+Mid-lev. clouds (at $\sim$1.5 km) & -5 & -5 & \textbf{0}\\
+RH at 500 m & 2 & 2 & \textbf{0}\\
+SW (W m$^{-2}$) & -25 & \textbf{5} & -20\\
+LW (W m$^{-2}$) & 5 & 5 & 5\\
+LWP (g m$^{-2}$) & \textbf{10} & 20 & -15\\
+IWP (g m$^{-2}$) & -30 & -30 & \textbf{-15}\\
+LCL distribution peak (m) & 300 & 300 & 300\\
+\hline
+\end{tabular}
+\end{table}
+
+We analyzed a total of about 2400 days of lidar and 2300 radiosonde observations from 31 campaigns and the Macquarie Island subantarctic station, covering the Atlantic, Australian, and New Zealand sectors of the SO over 10 years.
 This dataset, together with the use of a ground-based lidar simulator, provided a comprehensive basis for evaluating SO cloud and thermodynamic profile biases in the GSRM ICON and the ERA5 and MERRA-2 reanalyses.
-Our analysis provides a unique evaluation perspective different from satellite observations -- one that we argue is more suitable for evaluating boundary layer clouds, which are predominant in this region.
-Furthermore, we subsetted our dataset by low and high latitude bands, cyclonic activity, and stability in order to identify how these conditions influence the biases.
+Our analysis provides a unique evaluation perspective, complementary to satellite observations for evaluating boundary layer clouds and fog, which are predominant in this region.
+We did not, however, analyze the cloud phase based on ground-based observations.
+Cloud phase can have a strong impact on the SW radiative transfer due to larger and therefore less numerous hydrometeors (for the same amount of water) scatter much less SW radiation.
+Especially underestimation of fog or near-surface clouds is very strong in the reanalyses, and we showed that this relates to cloud formation or persistence at RH between 80 and 100\% in the boundary layer in the observations, while in models RH values less than 100\% are associated with clear bins.
+We subsetted the dataset by low and high latitude SO bands, cyclonic activity, and stability in order to identify how these conditions influence the biases.
+The main identified biases are summarized in Table~\ref{tab:summary} and discussed below.
 
 Our main finding corroborates previous findings of large boundary layer cloud biases in models and their subsequent effect on the radiative transfer.
-For example, low- and mid-level clouds in the cold-air sector of cyclones were identified as being responsible for most of the SW bias in \citeA{bodas-salcedo2012}.
-This understanding was refined in \citeA{bodas-salcedo2014}, which highlighted that the SW bias was associated with an incorrectly simulated mid-level cloud regime, which occurred in regions where clouds with tops at mid-level and low-levels occurred.
-Our results align less well with more recent work by \citeA{ramadoss2024}, which shows persistent shortwave radiative biases over the Southern Ocean are associated with incorrect cloud phase representation.
-While \citeA{fiddes2024} suggest biases in the liquid water path are the largest contributor to the cloud radiative bias over the Southern Ocean.
-Our general finding applies to the new GSRM ICON, but the biases are generally lower than in the reanalyses, despite the reanalyses having the advantage of assimilation of the observed meteorological conditions.
-The GSRM has, on the other hand, the advantage of a much higher spatial resolution and, to a limited extent, explicit calculation of traditionally subgrid-scale processes such as convection.
+For example, low- and mid-level clouds in the cold-air sector of cyclones were identified as being responsible for most of the SW bias by \citeA{bodas-salcedo2012}.
+Precipitation in intense extratropical oceanic cyclones is projected to increase with future warming \cite{kodama2019}.
+The understanding of radiation biases was refined by \citeA{bodas-salcedo2014}, who highlighted that the SW bias was associated with an incorrectly simulated mid-level cloud regime, which occurred in regions where clouds with tops at mid-level and low-levels occurred.
+\citeA{ramadoss2024} have shown that in precipitating conditions, km-scale ICON has SW radiative biases associated with the overrepresentation of liquid phase at the cloud top in low stratocumuli clouds in a short (48-h) simulation over the SO.
+\citeA{fiddes2024} suggested that biases in the liquid water path are the largest contributor to the cloud radiative bias over the SO.
+Our general finding applies to the new GSRM ICON, but the biases are lower than in the reanalyses in several aspects, namely the total cloud fraction, daily cloud cover, fog, and LWP (Table~\ref{tab:summary}), despite the reanalyses having the advantage of assimilation of the observed meteorological conditions.
+ICON, on the other hand, performs worse than the reanalyses in clouds and RH at 500 m, mid-level clouds (here defined as 1.5 km), outgoing SW radiation, and IWP.
+ICON has the advantage of a much higher spatial resolution and, to a limited extent, explicit calculation of traditionally subgrid-scale processes such as convection.
+These are incomplete due to the lack of sub-grid scale convection parameterization below the km scale.
+The lack of parameterized subgrid-scale convection in ICON was a pragmatic choice in the model development, but it can be a source of substantial cloud biases even at the 5-km resolution.
 
 We show that relative to ERA5, the distribution and strength of cyclonic activity over the SO is well represented in ICON, but it displays lower values of LTS.
-The latter is also manifested in the radiosonde profile comparison, showing that the virtual potential temperature profiles in ICON are less stable than in the observations over low-latitude SO.
+The latter is also manifested in the radiosonde profile comparison (Fig.~\ref{fig:rs-lts-hist}), showing that the virtual potential temperature profiles in ICON are less stable than in the observations over low-latitude SO.
+It is also manifested in near-surface air temperature, which is overestimated in the 1--7°C range at the radiosonde launch locations (Fig.~\ref{fig:stats-hist-surf}a).
+The underestimated LTS is linked to the overestimated cloud peak at 500 m in the lidar cloud occurrence comparison (Fig~\ref{fig:cloud-occurrence}f--g).
+It might also be interacting with the cloud inhomogeneity factor employed in ICON (Section~\ref{sec:icon}), resulting in lower cloud liquid water used in radiative calculations, hence decreased outgoing SW radiation.
+Based on the virtual potential temperature profiles analysis, clouds at 500 m are predominantly convectively driven, and it is therefore expected that a model bias towards weak stability results in an increased cloud formation at this level.
+The underestimation of clouds above 1 km in ICON does not have a clear physical reason in our analysis and is likely partially or fully caused by stronger obscuration of the simulated lidar signal by the underlying and overestimated clouds in the model at around 500 m.
 
-The 31 voyages and a station show remarkably similar biases in cloud occurrence by height in the lidar comparison, which indicates that common underlying causes for the biases exist regardless of longitude and season.
+The campaigns show remarkably similar biases in cloud occurrence by height in the lidar comparison (Fig.~\ref{fig:cloud-occurrence-panel}), which indicates that common underlying causes for the biases exist regardless of longitude and season.
 ICON underestimates the total cloud fraction by about 10\%, with an overestimation of clouds below 2~km and an underestimation of clouds above 2~km.
-The reanalyses also underestimate the total cloud fraction by about 20\%.
-ERA5 overestimates cloud below 1~km but underestimates near-surface cloud or fog.
-ICON strongly overestimates the peak of cloud occurrence at about 500 m, which might be explained by the radiosonde comparison, showing that it is too moist at around this height.
-Similar to our results, \citeA{cesana2022} showed that CMIP6 models also tend to underestimate cloud occurrence above 2~km over the SO, although their analysis in this case was limited to liquid clouds.
+The reanalyses underestimate the total cloud fraction by about 20\%.
+ERA5 overestimates cloud below 1~km but underestimates near-surface cloud and fog.
+ICON strongly overestimates the peak of cloud occurrence at about 500 m.
+This can be explained by the radiosonde comparison, showing that it is too moist at around this height (Fig.~\ref{fig:potential-temperature}a); has underestimated LTS (Fig.~\ref{fig:cyclone-stability} and \ref{fig:rs-lts-hist}), permitting shallow convection to this height; and has underestimated near-surface RH (Fig.~\ref{fig:stats-hist-surf}), resulting in higher LCL (Fig.~\ref{fig:cloud-occurrence}).
+Similar to our results for mid-level clouds, \citeA{cesana2022} showed that CMIP6 models also tend to underestimate cloud occurrence above 2~km over the SO, although their analysis in this case was limited to liquid clouds.
+
+The inability of the models to simulate fog can be linked to various biases identified in our analysis.
+Near-surface RH is too low in the models (Fig.~\ref{fig:stats-hist-surf}), potentially due to low moisture flux from the surface and too large mixing in the boundary layer.
+Near-surface temperature is also too high in ICON, and it can be expected that fog formation occurs in low near-surface temperature conditions when a warm and moist air mass is cooled by the surface to the saturation point.
+Fig.~\ref{fig:rs-thetav-hur-cloud} shows that fog occurs under highly stratified conditions.
+The underestimated LTS in ICON (and to a lesser extent in the reanalyses; Fig.~\ref{fig:rs-lts-hist}) indicates that the models are biased to weaker stability, thus having less favorable conditions for fog formation and persistence.
+The RH distribution in cloudy bins (Fig.~\ref{fig:rs-hur-hist}) also suggests that in observations, near-surface hydrometeors can occur under lower RH in observations than in the models.
+This could be due to high availability of cloud condensation nuclei (CCN) or ice nucleating particles (INPs) or due to hydrometeors and aerosols formed via sea spray under high swell and wind conditions.
+These parametrizations are likely very uncertain in the models in the SO due to the sparsity of reference data.
+\citeA{kawai2016} have shown that marine fog has some of the highest concentrations globally over the SO, and SO marine fog has a greater occurrence in winter.
+They conclude that marine fog is related to large-scale circulation and warm advection, and this is expected to change in a warming climate.
 
@@
 Conditions of weak stability are associated with some of the greatest biases, especially in ERA5.
-The models also underestimate the cloud cover very strongly in cyclonic conditions, which are very cloudy in the observations (8~oktas), but much less so in the models.
-Similarly, \citeA{mcerlich2023} found a 40\% underestimation of cloud liquid water in cyclones over the SO in ERA5, despite total column water vapor simulated much more accurately (5\% underestimation).
+The models also underestimate the cloud cover very strongly in cyclonic conditions, which are very cloudy in the observations (8~oktas) but much less so in the models.
+Similarly, \citeA{mcerlich2023} found a 40\% underestimation of cloud liquid water in cyclones over the SO in ERA5, despite total column water vapor being simulated much more accurately (5\% underestimation).
 
-The radiosonde observations indicate that the LCL is too high in ICON and reanalyses, which is probably responsible for the higher peak of clouds in the models and the lack of near-surface clouds or fog.
-The radiosonde comparison, however, does not seem to explain cloud biases at higher altitudes, which is perhaps suggestive of biases in the influence of the liquid water path in the models relative to reality.
-MERRA-2 is too moist at all heights.
-ICON also exhibits smaller internal variability than the radiosonde observations.
-Overall, the radiosonde comparison only partially explains the identified cloud biases, and other physical causes are likely contributing.
-This warrants further investigation, especially of ocean--atmosphere fluxes, shallow convection, and boundary layer turbulence.
-The lack of parameterized subgrid-scale convection in ICON could be a substantial issue even at the 5-km resolution.
+The radiosonde observations indicate that the LCL is too high in ICON and reanalyses, which is probably responsible for the higher peak of clouds in the models and the lack of near-surface clouds and fog.
+Notably, ICON exhibits smaller internal variability in $\theta_v$ than the radiosonde observations.
+The analysis of cloud liquid and ice water path (Fig.~\ref{fig:stats-hist} and \ref{fig:stats-hist-cloudy}) shows that both phases are present in observations in about equal amounts.
+The models show diverse biases, the most pronounced being overestimation of high-LWP values in MERRA-2 and overestimation of cases with near-zero LWP and IWP in all models.
+All models tend to compensate for the overestimated cases of near-zero LWP with more high-LWP values to get a mean LWP that is either less (but close) to the observations (ERA5) or higher than the observations (ICON and MERRA-2).
+IWP is underestimated in all of the models.
+In the case of ICON and MERRA-2, the mean IWP was underestimated and LWP overestimated, indicating that the models produce too much liquid and not enough ice phase.
+This is in contrast with previous findings of the lack of supercooled liquid over the SO in other models.
+If the liquid phase is overestimated relative to the ice phase, one would expect underestimated cloud SW reflectivity due to a larger number of smaller hydrometeors for the same amount of water.
+Cloudy areas would then appear brighter in the SW spectrum.
+This can contribute to the too few, too bright bias, i.e., the the overestimated brightness of cloudy areas compensates for the lower total cloud fraction in the models.
 
 The relationship between cloud biases and radiation has a number of notable features.
-Perhaps unsurprisingly, the reanalyses exhibit the too few, too bright bias previously identified in models.
-In our results, this is characterized by outgoing TOA SW radiation similar to or higher than in the satellite observations, while at the same time total cloud fraction is substantially underestimated relative to the ground-based lidar observations.
-This feature seems to be much more pronounced in ERA5 than in MERRA-2.
-On the other hand, this relationship is not present in ICON.
-This model generally predicts smaller outgoing TOA SW radiation and smaller total cloud fraction than observations, and the deficit of outgoing TOA SW radiation is approximately proportional to the deficit of the total cloud fraction.
+MERRA-2 exhibits the too few, too bright bias previously identified in models.
+In our results, this is characterized by overestimated outgoing TOA SW radiation, while at the same time total cloud fraction is underestimated based on the ground-based lidar observations.
+On the other hand, this relationship is not present in ICON or ERA5.
+ICON predicts smaller outgoing TOA SW radiation and smaller total cloud fraction than observations, and the deficit of outgoing TOA SW radiation is approximately proportional to the deficit of the total cloud fraction.
 While this might be a welcome feature and an improvement over previous models, it does mean that the outgoing TOA SW radiation is overall underestimated instead of being compensated by a higher cloud albedo.
 This can, of course, lead to undesirable secondary effects such as overestimated solar heating of the sea surface, among other factors responsible for SO SST biases in climate models \cite{zhang2023,luo2023,hyder2018}.
-To some extent, the cloud albedo might be reduced in the model artificially by the application of an inhomogeneity factor to lower cloud liquid water in the radiative transfer calculations (Sec.
-\ref{sec:icon}).
+In contrast with our results, \citeA{schuddeboom2021} showed that CMIP6 models tend to overestimate a stratocumulus cloud regime over the SO.
 
-The results imply that SO cloud biases are still a substantial issue even in the km-scale resolution ICON model, even though an improvement over the lower-resolution reanalyses is notable.
+Our results imply that SO cloud biases are a substantial issue even in the km-scale resolution ICON and the reanalyses.
 More effort is therefore needed to improve the model cloud simulations in this understudied region.
-However, this analysis suggests that the transition from models with parameterized convection and clouds to storm-resolving models might not solve these biases without additional effort.
-Evaluation of ocean--atmosphere heat, moisture, and momentum fluxes against in-situ observations over the SO and comparison of GSRM simulations against large-eddy simulations are two potential avenues for future research that could elucidate the physical mechanisms behind the biases, in addition to the more common efforts in SO cloud microphysics and precipitation evaluation.
+We see that while the ICON is superior to the coarser reanalyses in some aspects (Table~\ref{tab:summary}), it is affected by cloud biases large enough to cause important radiative biases.
+Parts of the GSRM relevant to low clouds, however, do not benefit from the higher resolution, such as cloud microphysics, unresolved clouds smaller than the grid cell, and turbulence.
+Cloud biases have also been shown to be a persistent issue in other GSRM models \cite{seiki2022}.
+
+We suggest the following avenues for future research.
+Evaluation of ocean--atmosphere heat, moisture, and momentum fluxes with in-situ observations over the SO and comparison of GSRM simulations with large-eddy simulations in process-oriented studies; evaluation of the DYAMOND project simulations in a similar manner as performed here (for models which provide the necessary fields); and combining active satellite sensors such as the Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observations (CALIOP) on CALIPSO and Atmospheric Lidar [ATLID; \citeA{heliere2017}] on the Earth Clouds, Aerosols and Radiation Explorer [EarthCARE; \citeA{illingworth2015}] satellite with ground-based remote sensing could provide a more complete underestanding of the cloud biases across the whole troposphere.
+Cloud phase could be analyzed in more detail using the CALIPSO data, as was done by \citeA{roh2020} in a cloud-resolving model, or using ground-based observations with a dual-polarization Mini Micro Pulse Lidar [MiniMPL; \citeA{spinhirne1993,campbell2002,flynn2007}] data available from the TAN1802 voyage.
+\citeA{guyot2022} and \citeA{whitehead2024} have developed a machine learning method for identifying cloud phase from ceilometer data, and this could be used with our ground-based lidar dataset to analyze the cloud phase.
+However, their method would require a careful calibration with reference data coming from this region.
 
@@
 The TAN1802 data are openly available on Zenodo \cite{kremser2020}.
-The code for performing the presented analysis, precipitation detection, and a custom version of the ALCF using for our analysis are open-source and available at \url{https://github.com/peterkuma/icon-so-2024}, \url{https://github.com/peterkuma/alcf-precip}, and \url{https://github.com/peterkuma/icon-so-2024-alcf}, respectively.
 The remaining voyage data (AA15-16, HMNZSW16, NBP1704, TAN1502, and TAN1702) are openly available on Zenodo \cite{mcdonald2024b}.
 The Natural Earth dataset is openly available from \url{https://www.naturalearthdata.com}.
+The code used in our analysis is open-source and available on Zenodo: the code for performing the presented analysis \cite{kuma2024a}, precipitation detection \cite{kuma2024b}, cl2nc \cite{kuma2024c}, and a custom version of the ALCF used in our analysis \cite{kuma2024d}.
 
@@
 
-PK, FB, and the nextGEMS project received funding from the European Union’s Horizon 2020 research and innovation program under a grant agreement no.
-101003470.
-FB received funding from the Wenner-Gren Foundation and the Swedish e-Science Research Centre.
+This research was supported by the European Union’s Horizon 2020 research and innovation program projects nextGEMS (grant number 101003470) and CleanCloud (grant number 101137639), the Hans Ertel Centre for Weather Research (grant number 4823DWDP7), and the Swedish e-Science Research Centre (SeRC).
+FB received funding from the Wenner-Gren Foundation.
 The work of GM was supported by the United States (U.S.) Department of Energy Award DE-SC0021159.
@@
 We acknowledge the contribution of Thorsten Mauritsen to funding acquisition and project management.
-We acknowledge the RV \emph{Polarstern} datasets provided by the Alfred Wegener Institute and Pangaea, the AA15-16 dataset provided by the Australian Antarctic Division (AAD) and University of Canterbury (UC), the RV \emph{Tangaroa} datasets provided by the National Institute of Water and Atmospheric Research and UC, the NBP1704 dataset provided by the National Science Foundation, Cooperative Institute for Research in Environmental Sciences, University of Colorado and UC, the HMNZSW16 dataset provided by the Royal New Zealand Navy and UC, the MARCUS dataset provided by ARM and AAD, and the MICRE dataset provided by ARM, the Australian Bureau of Meteorology, and AAD.
+We acknowledge the RV \emph{Polarstern} datasets provided by the Alfred Wegener Institute and Pangaea, the AA15-16 dataset provided by the Australian Antarctic Division (AAD) and University of Canterbury (UC), the RV \emph{Tangaroa} datasets provided by the National Institute of Water and Atmospheric Research and UC, the NBP1704 dataset provided by the National Science Foundation, Cooperative Institute for Research in Environmental Sciences, University of Colorado, and UC, the HMNZSW16 dataset provided by the Royal New Zealand Navy and UC, the MARCUS dataset provided by ARM and AAD, and the MICRE dataset provided by ARM, the Australian Bureau of Meteorology, and AAD.
 Technical, logistical, and ship support for MARCUS and MICRE were provided by the AAD through Australian Antarctic Science projects 4292 and 4387, and we thank Steven Whiteside, Lloyd Symonds, Rick van den Enden, Peter de Vries, Chris Young, Chris Richards, Andrew Klekociuk, John French, Terry Egan, Nick Cartwright, and Ken Barrett for all of their assistance.
@@
 
-\bibliography{manuscript}
+\bibliography{manuscript_agu_rev1}
 

### 2025-06-26 si_rev1.tex
Revised version

\documentclass[draft,jgrga]{agutexSI2019}

\usepackage{xr}
\externaldocument{manuscript_agu_rev1}

\makeatletter
\def\@makecol{\setbox\@outputbox
     \vbox{\boxmaxdepth \maxdepth
\ifdim\ht\dbltopins<1pt\else\unvbox\dbltopins\fi
     \unvbox\@cclv
\ifdim\ht\dblbotins<1pt\else\unvbox\dblbotins\fi%
\ifvoid\footins\else\vskip\skip\footins\footnoterule\unvbox\footins\fi
%\vss
\vskip 0pt plus 1fil minus \maxdimen
}%
%\global\savefigandtabnumber\figandtabnumber
%\global\advance\savefigandtabnumber by 1 %% Because loop stops one short
                                         %% of the total number of figs
\global\savedblfigandtabnumber\dblfigandtabnumber
   \xdef\@freelist{\@freelist\@midlist}\gdef\@midlist{}\@combinefloats
   \setbox\@outputbox\vbox to\@colht{\boxmaxdepth\maxdepth
   \@texttop\dimen128=\dp\@outputbox\unvbox\@outputbox
   \vskip-\dimen128\@textbottom}%
   \global\maxdepth\@maxdepth}
\makeatother

 \usepackage{graphicx}

%  Uncomment the following command to allow illustrations to print
%   when using Draft:
 \setkeys{Gin}{draft=false}

\authorrunninghead{KUMA ET AL.}

\titlerunninghead{SHIP-BASED LIDAR EVALUATION OF SO LOW CLOUDS}

\authoraddr{Corresponding author: P. Kuma, Institute for Atmospheric and Environmental Sciences, Goethe University Frankfurt, Altenhöferallee 1, Frankfurt am Main, 60438, Hesse, Germany. (peter@peterkuma.net)}

\begin{document}

%\includegraphics{agu_pubart-white_reduced.eps}

\title{Supporting Information for "Ship-based lidar evaluation of Southern Ocean low clouds in the storm-resolving general circulation model ICON, and the ERA5 and MERRA-2 reanalyses"}

\authors{Peter Kuma\affil{1,2,3,4}, Frida A.-M. Bender\affil{1,2}, Adrian J. McDonald\affil{3}, Simon P. Alexander\affil{5,6}, Greg M. McFarquhar\affil{7,8}, John J. Cassano\affil{9,10,11}, Graeme E. Plank\affil{3}, Sean Hartery\affil{3}\thanks{Current affiliation: Department of Physics \& Atmospheric Science, Dalhousie University, Halifax, Canada}, Simon Parsons\affil{3}\thanks{Current affiliation: New South Wales Department of Planning and Environment, Sydney, New South Wales, Australia}, Sally Garrett\affil{12}, Alex J. Schuddeboom\affil{3}, and Anna Possner\affil{4}}

\affiliation{1}{Department of Meteorology (MISU), Stockholm University, Stockholm, Sweden}
\affiliation{2}{Bolin Centre for Climate Research, Stockholm University, Stockholm, Sweden}
\affiliation{3}{School of Physical and Chemical Sciences, University of Canterbury, Christchurch, Aotearoa/New Zealand}
\affiliation{4}{Institute for Atmospheric and Environmental Sciences, Goethe University Frankfurt, Frankfurt am Main, Hesse, Germany}
\affiliation{5}{Australian Antarctic Division, Kingston, Tasmania, Australia}
\affiliation{6}{Australian Antarctic Program Partnership, Institute for Marine and Antarctic Studies, University of Tasmania, Hobart, Tasmania, Australia}
\affiliation{7}{Cooperative Institute of Severe and High Impact Weather Research and Operations, University of Oklahoma, Norman, OK, USA}
\affiliation{8}{School of Meteorology, University of Oklahoma, Norman, OK, USA}
\affiliation{9}{Cooperative Institute for Research in Environmental Sciences, University of Colorado, Boulder, CO, USA}
\affiliation{10}{National Snow and Ice Data Center, University of Colorado, Boulder, CO, USA}
\affiliation{11}{Department of Atmospheric and Oceanic Sciences, University of Colorado, Boulder, CO, USA}
\affiliation{12}{New Zealand Defence Force, Wellington, Aotearoa/New Zealand}

\begin{article}

\noindent\textbf{Contents of this file}
\begin{enumerate}
\item Figure S1
\item Figure S2
\item Figure S3
\item Figure S4
\item Figure S5
\end{enumerate}

\end{article}
\clearpage

\begin{figure}[p!]
\centerline{
\includegraphics[width=0.95\textwidth]{img/cl.pdf}
}
\caption{
Cloud occurrence by height for the 31 voyages and one sub-Antarctic station (MICRE) in observations (O) and simulated by the ALCF from the ICON model (I), MERRA‐2 (M), and ERA5 reanalysis data (E). The numbers in the legend indicate the total cloud fraction and the number of days of data. Multiple lines of ICON profiles are for each of the four years of model data available.
}
\label{fig:cloud-occurrence-panel}
\end{figure}

\begin{figure}[p!]
\includegraphics[width=\textwidth]{img/stats_hist_surf.pdf}
\caption{
Histograms of near-surface \textbf{(a)} air temperature and \textbf{(b)} relative humidity at radiosonde launch locations in the observations and the corresponding locations and times in the models. Only locations south of 40°S are included.
}
\label{fig:stats-hist-surf}
\end{figure}

\begin{figure}[p!]
\includegraphics[width=\textwidth]{img/stats_hist_cloudy.pdf}
\caption{
The same as Fig.~\ref{fig:stats-hist} but for cloudy profiles only, as identified by the lidar cloud mask.
}
\label{fig:stats-hist-cloudy}
\end{figure}

\begin{figure}[t]
\centerline{
\includegraphics[width=1.2\textwidth]{img/rs_thetav_hur_cloud.pdf}
}
\caption{
The same as Fig.~\ref{fig:potential-temperature}, but only for profiles that contain \textbf{(a)} fog, \textbf{(b)} cloud at 500~m, and \textbf{(c)} cloud at 1.5~km.
}
\label{fig:rs-thetav-hur-cloud}
\end{figure}

\begin{figure}[t]
\centerline{
\includegraphics[width=1.2\textwidth]{img/rs_thetav_hist.png}
}
\caption{
The same as Fig.~\ref{fig:rs-hur-hist}, but for virtual potential temperature.
}
\label{fig:rs-thetav-hist}
\end{figure}

\end{document}

### 2025-06-30 manuscript_agu_rev1.tex
Update on Overleaf.

@@
 Specifically, the radar on CloudSat and lidar on the Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observation (CALIPSO), neither of which are now operational, are affected by the above-mentioned issues, resulting in a strong underestimation of cloud occurrence below 2 km in a merged CloudSat--CALIPSO product relative to ground-based lidar observations at McMurdo Station \cite{mcerlich2021}.
-However, removing situations with higher overlapping clouds could enable a less biased comparison of low clouds.
+Removing situations with higher overlapping clouds could enable a less biased comparison of low clouds.
 We hypothesize that this, in turn, can lead to systematic biases in low clouds in climate models, which are frequently evaluated against CloudSat--CALIPSO products.
@@
 
-Because the analyzed ICON simulation was free-running (years 2021--2024, inclusive), weather and climate oscillations (such as the El Niño--Southern Oscillation phase) are not expected to be equivalent to reality at the same time and place.
+Because the analyzed ICON simulation was free-running (years 2021--2024, inclusive), weather and climate oscillations (such as the El Niño--Southern Oscillation phase) are not expected to be equivalent to reality.
 To compare with the observations collected during a different time period (years 2010--2021, inclusive), we compared the model output with observations at the same time of year and geographical location, as determined for each data point, such as a lidar profile or a radiosonde launch.
@@
 
-In our analysis we partitioned our dataset by cyclonic activity and stability into multiple subsets in order to evaluate cloud biases in the context of the main physical controlling processes.
-The SO is a region of occurrence of both extratropical and polar cyclones.
+In our analysis, we partitioned our dataset by cyclonic activity and stability into multiple subsets to evaluate cloud biases in the context of the main physical controlling processes.
+The SO is a region of the occurrence of both extratropical and polar cyclones.
 Cyclonic activity results in cloud formation at the air mass boundaries along the cold and warm fronts, as well as inside the cold sector, after a passing cold sector destabilizes the atmosphere relative to the surface temperature.
 In the cold front and cold sector, clouds are convectively driven, including deep convection, and the advection of colder air masses over warmer ocean surfaces can trigger convection and subsequent cloud formation.
-Conversely, warm advection can trigger fog or cloud formation by boundary layer air cooled by the ocean surface until it reaches saturation.
+In contrast, warm advection can trigger fog or cloud formation by boundary layer air cooled by the ocean surface until it reaches saturation.
 More quiescent areas outside of cyclones can also be associated with clouds.
@@
 In contrast, the models simulate higher RH in the first 100~m under foggy conditions by several percentage points.
-In situations with clouds occurring at 500 m, $\theta_v$ is relatively flat between the surface and 500 m (Fig.~\ref{fig:rs-thetav-hur-cloud}b), as expected for convectively driven clouds.
+In situations with clouds occurring at 500 m, $\theta_v$ is relatively constant between the surface and 500 m (Fig.~\ref{fig:rs-thetav-hur-cloud}b), as expected for convectively driven clouds.
 The observed RH peaks at 500 m at about 90\%.
@@
 They show a more complex picture, characterized by a central peak at about 0°C near the surface, increasing to about 5°C at 2 km (Fig.~\ref{fig:rs-thetav-hist}a).
-For cloudy bins, the central peak is generally flatter with height and even shows a minimum in $\theta_v$ at about 500 m (Fig.~\ref{fig:rs-thetav-hist}i).
+For cloudy bins, the central peak is generally more constant with height and even shows a minimum in $\theta_v$ at about 500 m (Fig.~\ref{fig:rs-thetav-hist}i).
 This is indicative of convection being associated with clouds at these heights, which results in flat virtual potential temperature profiles.
@@
 The campaigns show remarkably similar biases in cloud occurrence by height in the lidar comparison (Fig.~\ref{fig:cloud-occurrence-panel}), which indicates that common underlying causes for the biases exist regardless of longitude and season.
-ICON underestimates the total cloud fraction by about 10\%, with an overestimation of clouds below 2~km and an underestimation of clouds above 2~km.
+ICON underestimates the total cloud fraction by about 10\%, with an overestimation of clouds below 1~km and an underestimation of clouds above 1~km.
 The reanalyses underestimate the total cloud fraction by about 20\%.

### 2025-06-30 manuscript_agu.tex
Final edits before the initial submission

@@
 The wavelengths of 905 and 910~nm are both affected by water vapor absorption of about 20\% in the mid-latitudes \cite{wiegner2015,wiegner2019}, with 910~nm affected more strongly, but we do not expect this to be a significant issue as explained in \citeA{kuma2021}.
-The instrument data files containing raw uncalibrated backscatter were first converted to Network Common Data Form (NetCDF) with cl2nc (\url{https://github.com/peterkuma/cl2nc}) and then processed with the ALCF (Section~\ref{sec:alcf}) to produce absolutely calibrated attenuated volume backscattering coefficient (AVBC), cloud mask, cloud occurrence by height, and the total cloud fraction.
+The instrument data files containing raw uncalibrated backscatter were first converted to Network Common Data Form (NetCDF) with cl2nc \cite{kuma2024a} and then processed with the ALCF (Section~\ref{sec:alcf}) to produce absolutely calibrated attenuated volume backscattering coefficient (AVBC), cloud mask, cloud occurrence by height, and the total cloud fraction.
 Because the CT25K uses a very similar wavelength to CL51, equivalent calculations as for CL51 were done assuming a wavelength of 910~nm.

### 2025-06-30 manuscript_agu_rev1.tex
Addressing author comments

--- 2025-06-26 manuscript_agu_rev1.tex
@@
 \begin{keypoints}
-\item Ground-based lidar evaluation of a km-scale global climate model and reanalyses reveals substantial cloud biases over the Southern Ocean.
-\item Total cloud fraction and fog are underestimated in the reanalyses. In all models, a cloud peak at 500~m is overestimated and too high.
+\item Large cloud biases are present in the global storm-resolving model, but are lower in several key aspects than in the reanalyses.
+\item The models tend to underestimate total cloud fraction, near-surface cloud and fog, while overestimating cloud occurrence peak at 500 m.
 \item A ``too few, too bright'' problem of underestimated cloud fraction, compensated by overestimated cloud albedo, is present in MERRA-2.
@@
 Surface meteorological quantities were measured continuously by an onboard automatic weather station or individual instruments.
+
+Some of the observatial data were likely used in reanalysis assimilation.
+The Macquarie Island station surface measurements and radiosonde profiles (not used in our analysis), were sent to the World Meteorological Organization Global Telecommunication System (GTS).
+The lidar measurements and radiosonde profiles on the RSV \textit{Aurora Australis} were not sent for assimilation.
 
@@
 Generally, what constitutes an EC is considered relatively arbitrary due to the very large variability of ECs \cite{neu2013}.
-The CyTRACK algorithm uses mean sea level pressure and wind speed thresholds as well as tracking across time steps to identify cyclone centers and radii in each time step.
+The CyTRACK algorithm uses mean sea level pressure and wind speed thresholds as well as tracking across time steps to identify cyclone centers and their radii in each time step.
 With this information, we could classify every location at a given time as either cyclonic or non-cyclonic.
-Due to a relatively small total area covered by cyclones (as identified by the cyclone center and radius), we chose a circle of double the radius (relative to one identified by CyTRACK) centered at the cyclone center as a cyclonic area for every time step and cyclone.
-All other areas were identified as non-cyclonic.
+Due to a relatively small total area covered by cyclones, as identified by the cyclone center and radius, for every time step and cyclone we defined a cyclonic area as a circle of double the radius identified by CyTRACK centered at the cyclone center.
+All other areas were defined as non-cyclonic.
 For identifying cyclones in the observations and the reanalyses, ERA5 pressure and wind fields were used as the input to CyTRACK.

### 2025-07-17 manuscript_agu_rev1.tex
Update on Overleaf.

@@
 We evaluated clouds, temperature, and humidity profiles over the Southern Ocean in one such model, as well as two reanalyses, based on 2400 days of ship and station observations.
-Thanks to the high resolution, the model relies entirely on explicit simulation of clouds instead of subgrid-scale parameterizations.
+Thanks to the high resolution, the model relies entirely on explicit simulation of cloud dynamics instead of subgrid-scale parameterizations.
 For the evaluation, we used ceilometer and radiosonde observations and a lidar simulator, which enables a fair comparison with the model and reanalyses.
@@
 ICON is developed and maintained jointly by Deutscher Wetterdienst, the Max-Planck-Institute for Meteorology, Deutsches Klimarechenzentrum (DKRZ), Karlsruhe Institute of Technology, and the Center for Climate Systems Modeling.
-Our aim is to quantify how well the GSRM ICON simulates clouds in this region, particularly in light of the fact that subgrid-scale clouds and convection are not parameterized in this model.
+Our aim is to quantify how well the GSRM ICON simulates clouds over the Southern Ocean (SO), particularly in light of the fact that subgrid-scale clouds and convection are not parameterized in this model.
 This region is mostly dominated by boundary layer clouds generated by shallow convection, and these are problematic to observe by spaceborne lidars and radars, which are affected by attenuation by overlapping and thick clouds \cite{mace2009,medeiros2010} and ground clutter \cite{marchand2008}, respectively.
@@
 
-The Southern Ocean (SO) is known to be a problematic region for climate model biases \cite{schuddeboom2021,hyder2018,cesana2022,zhao2022} due to a lack of surface and in situ observations and being a lower priority region for numerical weather prediction (NWP) and climate model development because of its distance from populated areas.
+The SO is known to be a problematic region for climate model biases \cite{schuddeboom2021,hyder2018,cesana2022,zhao2022} due to a lack of surface and in situ observations.
+This region has also long been a lower priority region for numerical weather prediction (NWP) and climate model development because of its distance from populated areas.
 Nevertheless, radiation biases and changes over an area of its size have a substantial influence on the global climate \cite{rintoul2011}, such as affecting the Earth's radiation balance, ocean heat, and carbon uptake \cite{williams2023}, and the SO is also an important part of the global ocean conveyor belt \cite{wang2014b}.
@@
 
-SO radiation biases have been relatively large and systematic compared to the rest of the globe since at least CMIP3 \cite{trenberth2010}, and the SO SW cloud radiative effect (CRE) bias is still positive in eight CMIP6 models analyzed by \citeA{schuddeboom2021} over the high-latitude SO, whereas over the low-latitude SO it tends to be more neutral or negative in some models.
+SO radiation biases have been relatively large and systematic compared to the rest of the globe since at least CMIP3 \cite{trenberth2010,bodas-salcedo2012}, and the SO SW cloud radiative effect (CRE) bias is still positive in eight CMIP6 models analyzed by \citeA{schuddeboom2021} over the high-latitude SO, whereas over the low-latitude SO it tends to be more neutral or negative in some models.
 Too much absorbed SW radiation over the SO was also identified in the GSRM SCREAM \cite{caldwell2021}.
@@
 
-How attenuation of the lidar signal affects cloud detection is dependent on factors such as the optical thickness of the measured cloud and its backscattering phase function, as well as the range-dependent noise standard deviation.
+How attenuation of the lidar signal affects cloud detection is dependent on factors such as the optical thickness of the measured cloud and its backscattering phase function, as well as the range-dependent noise standard deviation \cite{kuma2021}.
 A rough estimate can be made under an assumption of a relatively strongly backscattering cloud of $\beta = \mathrm{100\times 10^{-6} m^{-1}sr^{-1}}$ at a height of $r_1$ = 2 km, range-dependent noise $\beta_n$ at $r_2$ = 8 km of about $\mathrm{5\times 10^{-6} m^{-1}sr^{-1}}$, and cloud detection threshold $\beta_t = \mathrm{2\times 10^{-6} m^{-1}sr^{-1}}$, noise multiplication factor $f$ = 5, at full attenuation the two-way attenuation factor $A$ satisfies $A\beta = \beta_t + f\times \beta_n\left(\frac{r_1}{r_2}\right)^2$, which is equivalent to exponential decay ($A = e^{-2\delta}$) with optical depth $\delta$ (at the lidar wavelength) of about 1.7.
@@
 
-When subsetted by latitude (Fig.~\ref{fig:cloud-occurrence}b, c), we see that the low-latitude SO zone (40--55°S) displays a stronger peak of cloud occurrence near the surface than the high-latitude SO zone (between 55°S and the Antarctic coast), and this could be because higher latitudes have greater prevalence of weakly stable profiles (Fig.~\ref{fig:cyclone-stability}c, d), although more stable profiles populate regions south of 65°S close to the Antarctic coast.
+When the data are subset by latitude (Fig.~\ref{fig:cloud-occurrence}b, c), we see that the low-latitude SO zone (40--55°S) displays a stronger peak of cloud occurrence near the surface than the high-latitude SO zone (between 55°S and the Antarctic coast), and this could be because higher latitudes have greater prevalence of weakly stable profiles (Fig.~\ref{fig:cyclone-stability}c, d), although more stable profiles populate regions south of 65°S close to the Antarctic coast.
 Cyclonic activity is also stronger in high-latitude SO, which is typically associated with shallow or deep convection rather than very stable stratification necessary for fog formation.
@@
 
-When subsetted by conditions of strong and weak stability (Fig.~\ref{fig:cloud-occurrence}f, g), as defined in Section~\ref{sec:cyclone-stability}, we see that in situations of strong stability, cloud occurrence peaks strongly near the surface in observations, compared to situations of weak stability, where the peak is more diffuse between 0 and 1~km.
+When the data are subset by stability (Fig.~\ref{fig:cloud-occurrence}f, g), as defined in Section~\ref{sec:cyclone-stability}, we see that in situations of strong stability, cloud occurrence peaks strongly near the surface in observations, compared to situations of weak stability, where the peak is more diffuse between 0 and 1~km.
 Physically, conditions of strong stability are associated with the formation of advection fog, such as in situations of warm air advection from the north over a colder sea surface, thus inducing fog formation by cooling of the warm and humid air by the cold surface.
@@
 A cloud detected at any height means that the lidar profile was classified as cloudy; otherwise, it was classified as a clear sky.
-When all profiles in a day are taken together, the cloud cover for the day is defined as the fraction of cloudy profiles in the total number of profiles, expressed in oktas (multiples of 1/8).
+When all profiles in a day are taken together, the cloud cover for the day is defined as the fraction of cloudy profiles in the total number of profiles.
+It is expressed in oktas (multiples of 1/8), reflecting the 3-hourly model output of MERRA-2 and ICON, i.e.
+8 times per day.
 The same calculation is done for the lidar observations as for the simulated lidar profiles.
@@
 Therefore, the cloud occurrence is not affected by any cloud phase biases as long as the cloud is optically thick enough to be detected and the laser signal is not too attenuated.
-A combination of underestimated total cloud fraction and overestimated outgoing SW at TOA is indicative of an overestimated cloud albedo (in cloudy areas) due to either cloud liquid and ice water content, cloud phase, droplet or ice crystal size distribution, shape or orientation of ice crystals, cloud overlap, or their combination.
+An overestimated cloud albedo (in cloudy areas) can be due to either cloud liquid and ice water content, cloud phase, droplet or ice crystal size distribution, shape or orientation of ice crystals, cloud overlap, or their combination.
 The influence of cold clouds is likely second-order due to the much larger typical effective radius of ice crystals than cloud droplets.
@@
 This is again in line with the underestimated total cloud fraction by about 20\%.
-However, if the clouds are too thick, as expected from the SW results, this might also provide a compensating effect, in which too small a cloud area is counteracted by greater optical thickness in the LW spectrum, thus reducing the outgoing LW radiation more relative to thinner clouds.
+However, if the clouds are too thick, as expected from the SW results, this might also provide a compensating effect, in which too small a cloud area is counteracted by greater optical thickness in the LW spectrum, thus reducing the outgoing LW radiation more in thick relative to thinner clouds.
 For thin clouds, the outgoing TOA LW radiation originates both from the warmer surface (partly blocked by the clouds) and the clouds, whereas for thick clouds, the outgoing TOA LW radiation originates mostly from the colder-than-surface clouds.
@@
 In all the subsets (Fig.~\ref{fig:cloud-occurrence}b--g), the same type of biases are observed, namely the outgoing SW radiation is underestimated in ICON and ERA5 and overestimated in MERRA-2, and the outgoing LW radiation is overestimated in all the models.
-Even though the total cloud fraction is higher by 6\% over the high-latitude SO than the low-latitude SO, the outgoing SW radiation is much greater by 41~Wm$^{-2}$, implying a much greater cloud albedo (of cloudy areas) over the high-latitude SO.
-ICON has little difference in the total cloud fraction between low- and high-latitude SO, but greater outgoing SW radiation by 14~Wm$^{-2}$ over the high-latitude SO, likely due to thicker clouds under deeper convection in less stable and more cyclonic conditions relative to the low-latitude SO.
+The total cloud fraction is higher by 6\% over the high-latitude SO than the low-latitude SO, and the outgoing SW radiation is much greater by 41~Wm$^{-2}$.
+ICON has little difference in the total cloud fraction between low- and high-latitude SO, but greater outgoing SW radiation by 14~Wm$^{-2}$ over the high-latitude SO, likely due to thicker clouds and deeper convection in less stable and more cyclonic conditions relative to the low-latitude SO.
 In contrast, the reanalyses showed both greater total cloud fraction and outgoing SW radiation over the high-latitude SO compared to the low-latitude SO.
@@
 Spatially and temporally colocated profiles were taken from ICON and the reanalyses.
-Because the time period covered by the ICON model output (2021--2024) was different from the time period covered by the observations (2010--2021), when comparing with the model, we first had to remap the observation time to model time by taking the same time relative to the start of the year.
+Because the time period covered by the ICON model output (2021--2024) was different from the time period covered by the observations (2010--2021), we first remap the observation time to model time by taking the same time relative to the start of the year.
 Consequently, we also had four virtual/model profiles (one for each year from 2021 to 2024) for each observed profile.
 The profiles were partitioned into the same subsets as above (Sections~\ref{sec:cloud-occurrence} and \ref{sec:cloud-cover}).
-We focus on comparing virtual potential temperature ($\theta_v$) and relative humidity, being one of the primary factors affecting shallow convection and the associated low-level cloud formation and dissipation.
+We focus on comparing virtual potential temperature ($\theta_v$) and relative humidity, being one of the primary factors affecting shallow convection,the associated low-level cloud formation, and cloud dissipation.
 The observed and model profiles of virtual potential temperature and relative humidity are shown in Fig.~\ref{fig:potential-temperature}.
@@
 Overall, the mean $\theta_v$ is accurate to within 0.5~K in ICON and MERRA-2, except for ICON being colder by up to 2.5~K in the mid-to-high troposphere (less stable) (Fig.~\ref{fig:potential-temperature}a).
-Larger differences exist, however, in the 40--55°S zone, where ICON is colder by about 5 K at higher altitudes (Fig.~\ref{fig:potential-temperature}b).
+Larger differences exist, however, in the 40--55°S zone, where ICON is colder by about 5 K at 5~km (Fig.~\ref{fig:potential-temperature}b).
 In other subsets, the bias is relatively small.
@@
 The models simulate progressively fewer high-RH (\textgreater 90\%) bins above the ground (Fig.~\ref{fig:rs-hur-hist}b--d).
-This can be related to either ice nucleation happening in the models, which requires smaller RH for saturation, or the grid cell size in the models, which requires lower grid cell average RH than 100\% for saturation to occur in a fraction of the grid cell.
+This can be related to either ice nucleation happening in the models, which can occur below liquid water saturation, or the grid cell size in the models, which requires lower grid cell average RH than 100\% for saturation to occur in a fraction of the grid cell.
 The models also tend to simulate more clear bins than observations for RH between 80 and 100\% between the ground and about 1 km (Fig.~\ref{fig:rs-hur-hist}f--h).
-In observations, these values of RH are associated with cloudy bins (Fig.~\ref{fig:rs-hur-hist}i).
+In the observations, these values of RH are associated with cloudy bins (Fig.~\ref{fig:rs-hur-hist}i).
 Conversely, the models predominantly associate only RH very close to 100\% with cloudy bins at these heights (Fig.~\ref{fig:rs-hur-hist}j--l).
@@
 Therefore, our results are likely representative of summer and, to a lesser extent, spring and autumn conditions.
+Ship access to sea ice covered areas of the SO is also limited.
 Cloud regimes and phase in the region are seasonally variable \cite{danker2022}.
@@
 Clouds with a relatively modest optical thickness of 1.7 can attenuate the lidar signal for a detection at 2 km using an instrument with noise properties like the Vaisala CL31 (Section 2.4).
-While supercooled liquid clouds and their attenuation are accounted for by the lidar simulator, they can strongly attenuate the signal and cause artifically low values of cloud occurrence at higher altitudes.
+While supercooled liquid clouds and their attenuation are accounted for by the lidar simulator, they can strongly attenuate the signal and cause artificially low values of cloud occurrence at higher altitudes.
 For example, we found that cloud occurrence at 1.5 km is underestimated in ICON and underlying clouds are overestimated.
@@
 Cloud phase can have a strong impact on the SW radiative transfer due to larger and therefore less numerous hydrometeors (for the same amount of water) scatter much less SW radiation.
-Especially underestimation of fog or near-surface clouds is very strong in the reanalyses, and we showed that this relates to cloud formation or persistence at RH between 80 and 100\% in the boundary layer in the observations, while in models RH values less than 100\% are associated with clear bins.
+Especially, the underestimation of fog or near-surface clouds is very substantial in the reanalyses, and we showed that this relates to cloud formation or persistence at RH between 80 and 100\% in the boundary layer in the observations, while in models RH values less than 100\% are associated with clear bins.
 We subsetted the dataset by low and high latitude SO bands, cyclonic activity, and stability in order to identify how these conditions influence the biases.
@@
 The inability of the models to simulate fog can be linked to various biases identified in our analysis.
-Near-surface RH is too low in the models (Fig.~\ref{fig:stats-hist-surf}), potentially due to low moisture flux from the surface and too large mixing in the boundary layer.
+Near-surface RH is too low in the models (Fig.~\ref{fig:stats-hist-surf}), potentially due to low moisture flux from the surface and too effective boundary layer mixing.
 Near-surface temperature is also too high in ICON, and it can be expected that fog formation occurs in low near-surface temperature conditions when a warm and moist air mass is cooled by the surface to the saturation point.
@@
 We suggest the following avenues for future research.
-Evaluation of ocean--atmosphere heat, moisture, and momentum fluxes with in-situ observations over the SO and comparison of GSRM simulations with large-eddy simulations in process-oriented studies; evaluation of the DYAMOND project simulations in a similar manner as performed here (for models which provide the necessary fields); and combining active satellite sensors such as the Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observations (CALIOP) on CALIPSO and Atmospheric Lidar [ATLID; \citeA{heliere2017}] on the Earth Clouds, Aerosols and Radiation Explorer [EarthCARE; \citeA{illingworth2015}] satellite with ground-based remote sensing could provide a more complete underestanding of the cloud biases across the whole troposphere.
+Evaluation of ocean--atmosphere heat, moisture, and momentum fluxes with in-situ observations over the SO and comparison of GSRM simulations with large-eddy simulations in process-oriented studies; evaluation of the DYAMOND project simulations in a similar manner as performed here (for models which provide the necessary fields); and combining active satellite sensors such as the Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observations (CALIOP) on CALIPSO and Atmospheric Lidar [ATLID; \citeA{heliere2017}] on the Earth Clouds, Aerosols and Radiation Explorer [EarthCARE; \citeA{illingworth2015}] satellite with ground-based remote sensing could provide a more complete understanding of the cloud biases across the whole troposphere.
 Cloud phase could be analyzed in more detail using the CALIPSO data, as was done by \citeA{roh2020} in a cloud-resolving model, or using ground-based observations with a dual-polarization Mini Micro Pulse Lidar [MiniMPL; \citeA{spinhirne1993,campbell2002,flynn2007}] data available from the TAN1802 voyage.

### 2025-07-17 manuscript_agu_rev1.tex
Merge

@@
 \item Large cloud biases are present in the global storm-resolving model, but are lower in several key aspects than in the reanalyses.
-\item The models tend to underestimate total cloud fraction, near-surface cloud and fog, while overestimating cloud occurrence peak at 500 m.
+\item The models tend to underestimate total cloud fraction, very low-level ($<$~250~m) cloud and fog, while overestimating cloud occurrence peak at 500 m.
 \item A ``too few, too bright'' problem of underestimated cloud fraction, compensated by overestimated cloud albedo, is present in MERRA-2.
@@
 ICON and ERA5 overestimate the cloud occurrence peak at about 500~m, associated with underestimated lower tropospheric stability and overestimated lifting condensation level.
-The reanalyses strongly underestimate fog and near-surface clouds, and MERRA-2 underestimates cloud occurrence at almost all heights.
+The reanalyses strongly underestimate fog and very low-level clouds, and MERRA-2 underestimates cloud occurrence at almost all heights.
 Outgoing shortwave radiation is overestimated in MERRA-2, implying a ``too few, too bright'' cloud problem.
@@
 Reanalyses are the best estimates of past meteorological conditions based on an underlying global model and observations.
-We evaluated clouds, temperature, and humidity profiles over the Southern Ocean in one such model, as well as two reanalyses, based on 2400 days of ship and station observations.
-Thanks to the high resolution, the model relies entirely on explicit simulation of cloud dynamics instead of subgrid-scale parameterizations.
-For the evaluation, we used ceilometer and radiosonde observations and a lidar simulator, which enables a fair comparison with the model and reanalyses.
+We evaluated clouds, temperature, and humidity profiles over the Southern Ocean in one such model, ICON, as well as two reanalyses, based on 2400 days of ship and station observations.
+Thanks to the high resolution, ICON relies entirely on explicit simulation of clouds instead of subgrid-scale parameterizations.
+For the evaluation, we used ceilometer and radiosonde observations and a lidar simulator, which enables a fair comparison with ICON and reanalyses.
 We subsetted our results by cyclonic activity and stability.
-We found that the model and reanalyses underestimate lidar-derived cloud fraction, and the reanalyses do so more strongly.
-Fog or near-surface clouds are especially underestimated in the reanalyses.
-However, the model and one of the reanalyses also tend to overestimate the peak of cloud occurrence at 500 m above the ground, and it tends to be higher.
+We found that ICON and reanalyses underestimate lidar-derived cloud fraction, and the reanalyses do so more strongly.
+Fog or very low-level clouds are especially underestimated in the reanalyses.
+However, ICON and one of the reanalyses also tend to overestimate the peak of cloud occurrence at 500 m above the ground, and it tends to be higher.
 This is linked to thermodynamic profiles, which show a higher lifting condensation level and lower stability.
@@
 Altogether, we analyzed approximately 2400 days of data from 31 voyages and one sub-Antarctic station covering diverse longitudes and latitudes of the SO.
-To achieve a like-for-like comparison with the model, we used a ground-based lidar simulator called the Automatic Lidar and Ceilometer Framework [ALCF; \citeA{kuma2021}].
+To achieve a like-for-like comparison with the models (ICON, MERRA-2, and ERA5), we used a ground-based lidar simulator called the Automatic Lidar and Ceilometer Framework [ALCF; \citeA{kuma2021}].
 We contrasted the results with ERA5 \cite{era5} and the Modern-Era Retrospective analysis for Research and Applications, Version~2 [MERRA-2; \citeA{gelaro2017}].
@@
 
-Apart from lidar observations, radiosondes were launched on weather balloons at regular synoptic times on the RV \emph{Polarstern}, MARCUS, NBP17024, TAN1702, and TAN1802 campaigns, measuring pressure, temperature, relative humidity, and the global navigation satellite system coordinates.
-Derived thermodynamic (virtual potential temperature, relative humidity, lifting condensation level, etc.) and dynamic physical quantities (wind speed and direction) for the measured vertical profiles were calculated with the program radiosonde tool [rstool; \citeA{rstool}].
+Apart from lidar observations, radiosondes were launched on weather balloons at regular synoptic times on the RV \emph{Polarstern}, MARCUS, NBP17024, TAN1702, and TAN1802 campaigns, measuring pressure, temperature, relative humidity (RH), and the global navigation satellite system coordinates.
+Derived thermodynamic [virtual potential temperature ($theta_v$), RH, lifting condensation level, etc.] and dynamic physical quantities (wind speed and direction) for the measured vertical profiles were calculated with the program radiosonde tool [rstool; \citeA{rstool}].
 Surface meteorological quantities were measured continuously by an onboard automatic weather station or individual instruments.
@@
 Some of the observatial data were likely used in reanalysis assimilation.
-The Macquarie Island station surface measurements and radiosonde profiles (not used in our analysis), were sent to the World Meteorological Organization Global Telecommunication System (GTS).
-The lidar measurements and radiosonde profiles on the RSV \textit{Aurora Australis} were not sent for assimilation.
+The Macquarie Island station surface measurements and radiosonde profiles (not used in our analysis) were sent to the World Meteorological Organization Global Telecommunication System (GTS).
+The surface-level, lidar and radiosonde measurements on the RSV \textit{Aurora Australis} were not used outside of research purposes.
 
@@
 It uses version 5.12.4 of the Goddard Earth Observing System (GEOS) atmospheric model \cite{rienecker2008,molod2015}.
-Non-convective clouds (condensation, autoconversion, and evaporation) are parameterized using a prognostic scheme \cite{bacmeister2006}, and sub-grid cloud fraction is determined using total water distribution and a critical relative humidity threshold.
+Non-convective clouds (condensation, autoconversion, and evaporation) are parameterized using a prognostic scheme \cite{bacmeister2006}, and sub-grid cloud fraction is determined using total water distribution and a critical RH threshold.
 The reanalysis output analyzed here is available at a spatial resolution of 0.5° of latitude and 0.625° of longitude, which is about 56 km in the North--South direction and 35 km in the East--West direction at 60°S.
@@
 Here, we use the following products: 1-hourly instantaneous 2D single-level diagnostics (M2I1NXASM) for 2-m temperature and humidity; 3-hourly instantaneous 3D assimilated meteorological fields (M2I3NVASM) for cloud quantities, pressure, and temperature; 1-hourly average 2D surface flux diagnostics (M2T1NXFLX) for precipitation; and 1-hourly average 2D radiation diagnostics (M2T1NXRAD) for radiation quantities \cite{merra2}.
-Vertically resolved fields in M2I3NVASM start at a height of about 60 m, which limits our analysis of fog and near-surface clouds in this reanalysis.
+Vertically resolved fields in M2I3NVASM start at a height of about 60 m, which limits our analysis of fog and very low-level ($<$~250~m) clouds in this reanalysis.
 
@@
 Artificial neural network (ANN) for prediction of precipitation in lidar backscatter.
-\textbf{(a)} Diagram showing the TensorFlow structure of the ANN, \textbf{(b)} randomly selected example samples of near-surface backscatter in four categories (clear, fog, rain, and snow), as determined by coincident manual weather observations, \textbf{(c)} receiver operating characteristic diagram of the ANN, \textbf{(d)} examples of 10-day time series of human-observed (``HUM'') and predicted precipitation based on an ANN trained on all voyages (``ANN'') and all voyages except for the shown voyage (``ANN2'') during three randomly selected voyages with the available data.
+\textbf{(a)} Diagram showing the TensorFlow structure of the ANN, \textbf{(b)} randomly selected example samples of very low-level (0–250~m) backscatter in four categories (clear, fog, rain, and snow), as determined by coincident manual weather observations, \textbf{(c)} receiver operating characteristic diagram of the ANN, \textbf{(d)} examples of 10-day time series of human-observed (``HUM'') and predicted precipitation based on an ANN trained on all voyages (``ANN'') and all voyages except for the shown voyage (``ANN2'') during three randomly selected voyages with the available data.
 Here, by ``randomly selected,'' we mean selected from the top of a permutation generated by a pseudo-random number generator to prevent authors' bias in the selection.
@@
 We used this dataset to train a convolutional artificial neural network (ANN) to recognize profiles with precipitation from lidar backscatter data (Fig.~\ref{fig:ann}a), implemented in the TensorFlow ANN framework \cite{tensorflow}.
-Samples of short time intervals (10~min) of near-surface lidar backscatter (0–250 m) were classified as clear, rain, snow, and fog, using the synoptic observations as a training dataset (Fig.~\ref{fig:ann}b).
+Samples of short time intervals (10~min) of very low-level lidar backscatter (0–250 m) were classified as clear, rain, snow, and fog, using the synoptic observations as a training dataset (Fig.~\ref{fig:ann}b).
 From these, a binary, mutually exclusive classification of profiles as precipitating (rain or snow) or dry (clear or fog) was derived.
@@
 \citeA{mcerlich2023} have shown that wind is simulated well in ERA5 relative to the WindSat polarimetric microwave radiometer measurements \cite{meissner2009}.
-For identifying cyclones in ICON, its own pressure and wind fields were used as the input to CyTRACK because the model is free-running, and thus the pressure and wind fields are different from reality.
+For identifying cyclones in ICON, its own pressure and wind fields were used as the input to CyTRACK because ICON is free-running, and thus the pressure and wind fields are different from reality.
 Subsetting by proximity to cyclones is a relatively crude measure because it does not take into account the different sectors of cyclones, which are commonly associated with different weather situations.
@@
 The pattern matches reasonably well with \citeA{hoskins2005}.
-While both reanalysis and the model agree within about 8\% in most areas, ICON is prevailingly more cyclonic by about 4\%.
+While both reanalysis and ICON agree within about 8\% in most areas, ICON is prevailingly more cyclonic by about 4\%.
 There are clear differences, particularly in the highest occurrence rate regions, such as around Cape Adare, which is up to 20\% more cyclonic in ICON, and the Weddell and Bellingshausen Seas, where ICON is less cyclonic by up to 10\%.
-These differences might, however, stem from the relatively short time periods of comparison (4 years) and the fact that the model is free-running.
+These differences might, however, stem from the relatively short time periods of comparison (4 years) and the fact that ICON is free-running.
 
@@
 ICON is also substantially less stable than ERA5 across the whole region.
-In Section~\ref{sec:thermodynamic-profiles} we show that based on radiosonde observations, the bias is in ICON and not ERA5, and it is the result of underestimated temperature at heights corresponding to 700 hPa, as well as overestimated near-surface air temperature, characterized by a higher frequency of occurrence in the 1--7°C range compared to observations at radiosonde launch locations (Fig.~\ref{fig:stats-hist-surf}a).
-This may be related to large-scale circulation in the model or radiative transfer biases.
+In Section~\ref{sec:thermodynamic-profiles} we show that based on radiosonde observations, the bias is in ICON and not ERA5, and it is the result of underestimated temperature at heights corresponding to 700 hPa, as well as overestimated near-surface (2~m) air temperature, characterized by a higher frequency of occurrence in the 1--7°C range compared to observations at radiosonde launch locations (Fig.~\ref{fig:stats-hist-surf}a).
+This may be related to large-scale circulation in ICON or radiative transfer biases.
 
@@
 When analyzed by height, ICON overestimates cloud occurrence below 1 km and underestimates it above; MERRA-2 underestimates cloud occurrence at all heights by up to 10\%, especially near the surface; and ERA5 simulates cloud occurrence relatively well above 1 km but strongly underestimates it near the surface.
-We note that fog or near-surface clouds are strongly underestimated in the reanalyses (fog and clouds are both included in the cloud occurrence).
+We note that fog or very low-level clouds are strongly underestimated in the reanalyses (fog and clouds are both included in the cloud occurrence).
 We conclude that the ICON results match the observations better than the reanalyses in this metric.
@@
 The exaggerated peak in models is partly explained by the lifting condensation level (LCL) distribution, which peaks about 300~m higher in the models than in the observations (near the surface), although this is not very pronounced.
-This is indicative of near-surface relative humidity often being close to saturation in the observations but not in the models (Fig.~\ref{fig:stats-hist-surf}b).
+This is indicative of near-surface RH often being close to saturation in the observations but not in the models (Fig.~\ref{fig:stats-hist-surf}b).
 There are multiple possible reasons for this bias, such as how the statistical distribution of RH within a grid cell is represented in the models, the air--sea moisture flux parameterization, or weaker stability in the models can cause more boundary mixing across heights and thus lower near-surface RH.
@@
 Cyclonic activity is also stronger in high-latitude SO, which is typically associated with shallow or deep convection rather than very stable stratification necessary for fog formation.
-The low- and high-latitude SO zones show similar biases in models as in the general case, but ERA5 does not overestimate the peak in the low-latitude SO zone (near-surface cloud occurrence is still strongly underestimated).
+The low- and high-latitude SO zones show similar biases in models as in the general case, but ERA5 does not overestimate the peak in the low-latitude SO zone (very low-level cloud occurrence is still strongly underestimated).
 
@@
 MERRA-2 displays the largest errors relative to observations in the low-latitude SO zone and under weak stability.
-ERA5 can be generally characterized as representing cloud occurrence correctly above about 1.5~km, overestimating between 500~m and 1~km, but underestimating near-surface cloud occurrence (0--500~m).
+ERA5 can be generally characterized as representing cloud occurrence correctly above about 1.5~km, overestimating between 500~m and 1~km, but underestimating very low-level cloud occurrence.
 The total cloud fraction is strongly underestimated in all subsets.
@@
 Therefore, the cloud occurrence is not affected by any cloud phase biases as long as the cloud is optically thick enough to be detected and the laser signal is not too attenuated.
-An overestimated cloud albedo (in cloudy areas) can be due to either cloud liquid and ice water content, cloud phase, droplet or ice crystal size distribution, shape or orientation of ice crystals, cloud overlap, or their combination.
+A combination of underestimated total cloud fraction and overestimated outgoing SW at TOA is indicative of an overestimated cloud albedo (in cloudy areas) due to either cloud liquid and ice water content, cloud phase, droplet or ice crystal size distribution, shape or orientation of ice crystals, cloud overlap, or their combination.
 The influence of cold clouds is likely second-order due to the much larger typical effective radius of ice crystals than cloud droplets.
@@
 In all the subsets (Fig.~\ref{fig:cloud-occurrence}b--g), the same type of biases are observed, namely the outgoing SW radiation is underestimated in ICON and ERA5 and overestimated in MERRA-2, and the outgoing LW radiation is overestimated in all the models.
-The total cloud fraction is higher by 6\% over the high-latitude SO than the low-latitude SO, and the outgoing SW radiation is much greater by 41~Wm$^{-2}$.
-ICON has little difference in the total cloud fraction between low- and high-latitude SO, but greater outgoing SW radiation by 14~Wm$^{-2}$ over the high-latitude SO, likely due to thicker clouds and deeper convection in less stable and more cyclonic conditions relative to the low-latitude SO.
+Even though the total cloud fraction is higher by 6\% over the high-latitude SO than the low-latitude SO, the outgoing SW radiation is much greater by 41~Wm$^{-2}$, implying a much greater cloud albedo (of cloudy areas) over the high-latitude SO.
+ICON has little difference in the total cloud fraction between low- and high-latitude SO, but greater outgoing SW radiation by 14~Wm$^{-2}$ over the high-latitude SO, likely due to thicker clouds under deeper convection in less stable and more cyclonic conditions relative to the low-latitude SO.
 In contrast, the reanalyses showed both greater total cloud fraction and outgoing SW radiation over the high-latitude SO compared to the low-latitude SO.
@@
 \caption{
-Virtual potential temperature (virt.\ pot.\ temp.; $\theta_v$) and relative humidity (RH) determined from radiosonde launches and co-located profiles in ICON, ERA5, and MERRA-2 in subsets as in Fig.~\ref{fig:cloud-occurrence}.
+Virtual potential temperature ($\theta_v$) and relative humidity (RH) determined from radiosonde launches and co-located profiles in ICON, ERA5, and MERRA-2 in subsets as in Fig.~\ref{fig:cloud-occurrence}.
 The solid lines are the average calculated from the averages of every individual voyage and station.
@@
 Spatially and temporally colocated profiles were taken from ICON and the reanalyses.
-Because the time period covered by the ICON model output (2021--2024) was different from the time period covered by the observations (2010--2021), we first remap the observation time to model time by taking the same time relative to the start of the year.
+Because the time period covered by the ICON model output (2021--2024) was different from the time period covered by the observations (2010--2021), when comparing with ICON, we first had to remap the observation time to model time by taking the same time relative to the start of the year.
 Consequently, we also had four virtual/model profiles (one for each year from 2021 to 2024) for each observed profile.
 The profiles were partitioned into the same subsets as above (Sections~\ref{sec:cloud-occurrence} and \ref{sec:cloud-cover}).
-We focus on comparing virtual potential temperature ($\theta_v$) and relative humidity, being one of the primary factors affecting shallow convection,the associated low-level cloud formation, and cloud dissipation.
-The observed and model profiles of virtual potential temperature and relative humidity are shown in Fig.~\ref{fig:potential-temperature}.
+We focus on comparing $\theta_v$ and RH, being one of the primary factors affecting shallow convection and the associated low-level cloud formation and dissipation.
+The observed and model profiles of $\theta_v$ and RH are shown in Fig.~\ref{fig:potential-temperature}.
 
@@
 MERRA-2 and ERA5 are very close to the observations, possibly due to a high accuracy of assimilation of this quantity.
-Notably, the variability of virtual potential temperature (as represented by the percentiles) is much smaller in ICON than in the observations.
-This indicates that the model's internal variability in the lower-tropospheric thermodynamic conditions in the SO is smaller than in reality.
+Notably, the variability of $\theta_v$ (as represented by the percentiles) is much smaller in ICON than in the observations.
+This indicates that this model's internal variability in the lower-tropospheric thermodynamic conditions in the SO is smaller than in reality.
 
-Relative humidity displays much larger biases.
+RH displays much larger biases.
 In all subsets, ICON is too humid in the first 1~km by about 5\%, but very accurate above, except for the 40--55°S zone and conditions of weak stability (Fig.~\ref{fig:potential-temperature}b, g), where it is too dry between about 1 and 3~km.
-Even though relative humidity measured by radiosondes in the first 100~m is not very different between the observations and the models (Fig.~\ref{fig:potential-temperature}a), near-surface (2-m) relative humidity at the radiosonde launch locations is much greater in the observations, most often close to 100\%, unlike in the models, where 85\% tends to be the most common (Fig.~\ref{fig:stats-hist-surf}b).
+Even though RH measured by radiosondes in the first 100~m is not very different between the observations and the models (Fig.~\ref{fig:potential-temperature}a), near-surface (2-m) RH at the radiosonde launch locations is much greater in the observations, most often close to 100\%, unlike in the models, where 85\% tends to be the most common (Fig.~\ref{fig:stats-hist-surf}b).
 This also explains why LCL is much more frequently located at the surface in the observations than in the models (Fig.~\ref{fig:cloud-occurrence}a).
-LCL is fully determined by near-surface temperature, near-surface relative humidity, and surface pressure.
+LCL is fully determined by near-surface temperature, near-surface RH, and surface pressure.
 
@@
 
-Fig.~\ref{fig:rs-thetav-hur-cloud} shows virtual potential temperature and RH profiles for profiles containing fog, cloud at 500 m, and cloud at 1.5 km.
+Fig.~\ref{fig:rs-thetav-hur-cloud} shows $\theta_v$ and RH profiles for profiles containing fog, cloud at 500 m, and cloud at 1.5 km.
 These situations are characterized by particular cloud biases as identified in the lidar cloud occurrence analysis.
@@
 It can be seen that ICON substantially underestimates the occurrence of cases of strong stability above 16 K while overestimating the cases of moderate stability (8 to 16 K).
-When considered together with the cloud occurrence results presented in Fig.~\ref{fig:cloud-occurrence}, we see that since the model is biased towards weak stability, it overrepresents cloud profiles strongly peaking at 500 m (Fig.~\ref{fig:cloud-occurrence}g) over cloud profiles with fog or near-surface cloud (Fig.~\ref{fig:cloud-occurrence}f).
+When considered together with the cloud occurrence results presented in Fig.~\ref{fig:cloud-occurrence}, we see that since ICON is biased towards weak stability, it overrepresents cloud profiles strongly peaking at 500 m (Fig.~\ref{fig:cloud-occurrence}g) over cloud profiles with fog or very low-level cloud (Fig.~\ref{fig:cloud-occurrence}f).
 This can be a physical reason for its overall positive bias in cloud at 500 m (Fig.~\ref{fig:cloud-occurrence}a) instead of the observed cloud occurrence profile peaking near the surface.
@@
 The models simulate progressively fewer high-RH (\textgreater 90\%) bins above the ground (Fig.~\ref{fig:rs-hur-hist}b--d).
-This can be related to either ice nucleation happening in the models, which can occur below liquid water saturation, or the grid cell size in the models, which requires lower grid cell average RH than 100\% for saturation to occur in a fraction of the grid cell.
+This can be related to either ice nucleation happening in the models, which requires smaller RH for saturation, or the grid cell size in the models, which requires lower grid cell average RH than 100\% for saturation to occur in a fraction of the grid cell.
 The models also tend to simulate more clear bins than observations for RH between 80 and 100\% between the ground and about 1 km (Fig.~\ref{fig:rs-hur-hist}f--h).
@@
 
-Fig.~\ref{fig:rs-thetav-hist} shows histograms the same as the previous figure, but for virtual potential temperature.
+Fig.~\ref{fig:rs-thetav-hist} shows histograms the same as the previous figure, but for $\theta_v$.
 They show a more complex picture, characterized by a central peak at about 0°C near the surface, increasing to about 5°C at 2 km (Fig.~\ref{fig:rs-thetav-hist}a).
 For cloudy bins, the central peak is generally more constant with height and even shows a minimum in $\theta_v$ at about 500 m (Fig.~\ref{fig:rs-thetav-hist}i).
-This is indicative of convection being associated with clouds at these heights, which results in flat virtual potential temperature profiles.
+This is indicative of convection being associated with clouds at these heights, which results in flat $\theta_v$ profiles.
 In the reanalyses, in the first 200 m, values slightly above 0°C are associated with more clear bins than in observations, and values slightly below 0°C with fewer (Fig.~\ref{fig:rs-thetav-hist}g--h).
@@
 Moreover, the simulation is free-running and ocean-coupled, which means that observations had to be temporally mapped to this time period (at the same time relative to the start of the year) for the comparison.
-For these reasons, one can expect the results to be slightly different due to reasons unrelated to model biases, such as different weather conditions, partially accounted for by the cyclone and stability subsetting, and the phase of climate oscillations such as the ENSO in the observations and the model.
+For these reasons, one can expect the results to be slightly different due to reasons unrelated to model biases, such as different weather conditions, partially accounted for by the cyclone and stability subsetting, and the phase of climate oscillations such as the ENSO in the observations and ICON.
 The interannual variability in cloud occurrence in ICON can be seen in Fig.~\ref{fig:cloud-occurrence-panel}, where each year in ICON is represented by a separate line.
@@
 Ground-based observations are, however, complicated by precipitation, and satellite observations can also be used if the effect of overlapping clouds is carefully eliminated.
-Near-surface lidar retrievals ($\sim$100~m) are affected by uncertainties related to incomplete overlap, signal saturation (dead time), and after-pulse effect corrections \cite{kuma2021}.
+Lidar retrievals close to the surface ($\sim$100~m) are affected by uncertainties related to incomplete overlap, signal saturation (dead time), and after-pulse effect corrections \cite{kuma2021}.
 
@@
 We have attempted to remove lidar profiles with precipitation (about 26\% of all profiles), which could not be properly simulated with the lidar simulator (Section~\ref{sec:ann}).
-However, the approach was limited by the relatively low sensitivity of the ANN (65\%) and the fact that we had to choose a fixed threshold for surface precipitation flux in the model and reanalyses, which might not correspond to detection by the ANN applied to observations.
+However, the approach was limited by the relatively low sensitivity of the ANN (65\%) and the fact that we had to choose a fixed threshold for surface precipitation flux in the models, which might not correspond to detection by the ANN applied to observations.
 We also made no attempt to remove profiles with precipitation that did not reach the surface.
@@
 Cloud phase can have a strong impact on the SW radiative transfer due to larger and therefore less numerous hydrometeors (for the same amount of water) scatter much less SW radiation.
-Especially, the underestimation of fog or near-surface clouds is very substantial in the reanalyses, and we showed that this relates to cloud formation or persistence at RH between 80 and 100\% in the boundary layer in the observations, while in models RH values less than 100\% are associated with clear bins.
+Especially, the underestimation of fog or very low-level clouds is very substantial in the reanalyses, and we showed that this relates to cloud formation or persistence at RH between 80 and 100\% in the boundary layer in the observations, while in models RH values less than 100\% are associated with clear bins.
 We subsetted the dataset by low and high latitude SO bands, cyclonic activity, and stability in order to identify how these conditions influence the biases.
@@
 We show that relative to ERA5, the distribution and strength of cyclonic activity over the SO is well represented in ICON, but it displays lower values of LTS.
-The latter is also manifested in the radiosonde profile comparison (Fig.~\ref{fig:rs-lts-hist}), showing that the virtual potential temperature profiles in ICON are less stable than in the observations over low-latitude SO.
+The latter is also manifested in the radiosonde profile comparison (Fig.~\ref{fig:rs-lts-hist}), showing that the $\theta_v$ profiles in ICON are less stable than in the observations over low-latitude SO.
 It is also manifested in near-surface air temperature, which is overestimated in the 1--7°C range at the radiosonde launch locations (Fig.~\ref{fig:stats-hist-surf}a).
@@
 It might also be interacting with the cloud inhomogeneity factor employed in ICON (Section~\ref{sec:icon}), resulting in lower cloud liquid water used in radiative calculations, hence decreased outgoing SW radiation.
-Based on the virtual potential temperature profiles analysis, clouds at 500 m are predominantly convectively driven, and it is therefore expected that a model bias towards weak stability results in an increased cloud formation at this level.
-The underestimation of clouds above 1 km in ICON does not have a clear physical reason in our analysis and is likely partially or fully caused by stronger obscuration of the simulated lidar signal by the underlying and overestimated clouds in the model at around 500 m.
+Based on the $\theta_v$ profiles analysis, clouds at 500 m are predominantly convectively driven, and it is therefore expected that a model bias towards weak stability results in an increased cloud formation at this level.
+The underestimation of clouds above 1 km in ICON does not have a clear physical reason in our analysis and is likely partially or fully caused by stronger obscuration of the simulated lidar signal by the underlying and overestimated clouds in ICON at around 500 m.
 
@@
 The reanalyses underestimate the total cloud fraction by about 20\%.
-ERA5 overestimates cloud below 1~km but underestimates near-surface cloud and fog.
+ERA5 overestimates cloud below 1~km but underestimates very low-level cloud and fog.
 ICON strongly overestimates the peak of cloud occurrence at about 500 m.
@@
 The underestimated LTS in ICON (and to a lesser extent in the reanalyses; Fig.~\ref{fig:rs-lts-hist}) indicates that the models are biased to weaker stability, thus having less favorable conditions for fog formation and persistence.
-The RH distribution in cloudy bins (Fig.~\ref{fig:rs-hur-hist}) also suggests that in observations, near-surface hydrometeors can occur under lower RH in observations than in the models.
+The RH distribution in cloudy bins (Fig.~\ref{fig:rs-hur-hist}) also suggests that in observations, very low-level hydrometeors can occur under lower RH in observations than in the models.
 This could be due to high availability of cloud condensation nuclei (CCN) or ice nucleating particles (INPs) or due to hydrometeors and aerosols formed via sea spray under high swell and wind conditions.
@@
 
-The radiosonde observations indicate that the LCL is too high in ICON and reanalyses, which is probably responsible for the higher peak of clouds in the models and the lack of near-surface clouds and fog.
+The radiosonde observations indicate that the LCL is too high in ICON and reanalyses, which is probably responsible for the higher peak of clouds in the models and the lack of very low-level clouds and fog.
 Notably, ICON exhibits smaller internal variability in $\theta_v$ than the radiosonde observations.

### 2025-07-18 manuscript_agu_rev1.tex
Update on Overleaf.

@@
 These properties are in turn influenced by the atmospheric thermodynamics, convection and circulation, and both the indirect and direct effects of aerosols.
-Second-order effects on SW and LW radiation are associated with the cloud droplet size distribution, ice crystal habit, cloud lifetime, and direct radiative interaction with aerosols.
+Second-order effects on SW and LW radiation are associated with the cloud droplet size distribution, ice crystal habit, cloud lifetime, and direct radiative interaction with aerosols \cite{boucher2013}.
 In the 6$^\mathrm{th}$ phase of the Coupled Model Intercomparison Project [CMIP6; \citeA{eyring2016}], the cloud feedback has increased relative to CMIP5 \cite{zelinka2020}, especially in the Southern Hemisphere mid-to-high latitudes, which is one of the main reasons for the higher climate sensitivity of CMIP6 models.
@@
 This region has also long been a lower priority region for numerical weather prediction (NWP) and climate model development because of its distance from populated areas.
-Nevertheless, radiation biases and changes over an area of its size have a substantial influence on the global climate \cite{rintoul2011}, such as affecting the Earth's radiation balance, ocean heat, and carbon uptake \cite{williams2023}, and the SO is also an important part of the global ocean conveyor belt \cite{wang2014b}.
+Nevertheless, radiation biases and changes over an area of its size have a substantial influence on the global climate \cite{rintoul2011,bodas-salcedo2012}, such as affecting the Earth's radiation balance, ocean heat, and carbon uptake \cite{williams2023}, and the SO is also an important part of the global ocean conveyor belt \cite{wang2014b}.
 In general, marine clouds have a disproportionate effect on top-of-atmosphere (TOA) SW radiation due to the relatively low albedo of the sea surface.
@@
 
-When subsetted by cyclonic and non-cyclonic situations (Fig.~\ref{fig:cloud-occurrence}d, e), we see that the cyclonic situations have a larger amount of observed cloudiness, including peak and total cloud fraction, by about 10\%.
+When the data are subset as either cyclonic and non-cyclonic situations (Fig.~\ref{fig:cloud-occurrence}d, e), we see that the cyclonic situations have a larger amount of observed cloudiness, including peak and total cloud fraction, by about 10\%.
 In the cyclonic situations, the model vertical profiles of cloud occurrence compare well with observations, but they peak higher by about 200 m and are larger by about 8\%.

### 2025-07-18 manuscript_agu_rev1.tex
Move rs info to methods

@@
 \subsection{Voyage and Station Data}
+\label{sec:voyage-and-station-data}
 
@@
 Apart from lidar observations, radiosondes were launched on weather balloons at regular synoptic times on the RV \emph{Polarstern}, MARCUS, NBP17024, TAN1702, and TAN1802 campaigns, measuring pressure, temperature, relative humidity (RH), and the global navigation satellite system coordinates.
-Derived thermodynamic [virtual potential temperature ($theta_v$), RH, lifting condensation level, etc.] and dynamic physical quantities (wind speed and direction) for the measured vertical profiles were calculated with the program radiosonde tool [rstool; \citeA{rstool}].
+In total, about 2300 radiosonde profiles south of 40°S were available.
+Spatially and temporally colocated profiles were taken from the models.
+Because the time period covered by the ICON model output (2021--2024) was different from the time period covered by the observations (2010--2021), when comparing with ICON, we first had to remap the observation time to model time by taking the same time relative to the start of the year.
+Consequently, we also had four virtual/model profiles (one for each year from 2021 to 2024) for each observed profile.
+Derived thermodynamic [virtual potential temperature ($\theta_v$), lifting condensation level (LCL), etc.] and dynamic physical quantities (wind speed and direction) for the measured vertical profiles were calculated with the program radiosonde tool [rstool; \citeA{rstool}].
 Surface meteorological quantities were measured continuously by an onboard automatic weather station or individual instruments.
@@
 Above 1~km, ICON and MERRA-2 underestimate cloud occurrence, but ERA5 is accurate to about 3\% or less.
-The exaggerated peak in models is partly explained by the lifting condensation level (LCL) distribution, which peaks about 300~m higher in the models than in the observations (near the surface), although this is not very pronounced.
+The exaggerated peak in models is partly explained by the LCL distribution, which peaks about 300~m higher in the models than in the observations (near the surface), although this is not very pronounced.
 This is indicative of near-surface RH often being close to saturation in the observations but not in the models (Fig.~\ref{fig:stats-hist-surf}b).
@@
 
-In order to examine the potential link in the cloud biases to the local physical conditions, we analyzed about 2300 radiosonde profiles south of 40°S available from the 24 RV \emph{Polarstern} voyages and the MARCUS, NBP1704, TAN1702, and TAN1802 campaigns.
-Spatially and temporally colocated profiles were taken from ICON and the reanalyses.
-Because the time period covered by the ICON model output (2021--2024) was different from the time period covered by the observations (2010--2021), when comparing with ICON, we first had to remap the observation time to model time by taking the same time relative to the start of the year.
-Consequently, we also had four virtual/model profiles (one for each year from 2021 to 2024) for each observed profile.
+In order to examine the potential link in the cloud biases to the local physical conditions, we analyzed the radiosonde profiles available from the campaigns (Section~\ref{sec:voyage-and-station-data}).
 The profiles were partitioned into the same subsets as above (Sections~\ref{sec:cloud-occurrence} and \ref{sec:cloud-cover}).

### 2025-07-18 manuscript_agu_rev1.tex
Various

@@
 \subsection{Top of Atmosphere Radiation, Liquid and Ice Water Path}
+\label{sec:rad-lwp-iwp}
 
@@
 
-Fig.~\ref{fig:stats-hist} shows the SW and LW radiation, liquid water path (LWP), and ice water path (IWP) distributions as histograms and their corresponding averages.
+Fig.~\ref{fig:stats-hist-rad} shows the SW and LW radiation as histograms and their corresponding averages.
+ERA5 and ICON overestimate outgoing SW near 80 Wm$^{-2}$ (Fig.~\ref{fig:stats-hist-rad}a), which probably relates to clear sky situations, as expected from the underestimated cloud fraction.
+They also underestimate the highly reflective situations above 200 Wm$^{-2}$.
+MERRA-2 exhibits the too few, too bright problem in terms of overestimating SW reflectivity around 290 Wm$^{-2}$, given that the total cloud fraction in MERRA-2 is strongly underestimated.
+The LW distribution shows that all of the models overestimate outgoing LW (Fig.~\ref{fig:stats-hist-rad}b), which is expected from the underestimated cloud fraction, exposing more of the warmer ocean surface relative to colder clouds.
+
+Fig.~\ref{fig:stats-hist-si} shows liquid water path (LWP), and ice water path (IWP) distributions as histograms and their corresponding averages.
 LWP and IWP are calculated from the mass of water in the column divided by the area of the column, i.e.
 not just the area of the cloudy portion of the column, as in some definitions.
-ERA5 and ICON overestimate outgoing SW near 80 Wm$^{-2}$ (Fig.~\ref{fig:stats-hist}a), which probably relates to clear sky situations, as expected from the underestimated cloud fraction.
-They also underestimate the highly reflective situations above 200 Wm$^{-2}$.
-MERRA-2 exhibits the too few, too bright problem in terms of overestimating SW reflectivity around 290 Wm$^{-2}$, given that the total cloud fraction in MERRA-2 is strongly underestimated.
-The LW distribution shows that all of the models overestimate outgoing LW (Fig.~\ref{fig:stats-hist}b), which is expected from the underestimated cloud fraction, exposing more of the warmer ocean surface relative to colder clouds.
-The LWP distribution shows that all models overestimate cases with near-zero LWP (Fig.~\ref{fig:stats-hist}c), which relates to the underestimated total cloud fraction.
+The available observational satellite reference for LWP and IWP over high latitudes is unfortunately very uncertain due to a high solar zenith angle and inability of passive visible and infrared retrievals to detect phase below the cloud top of mixed-phase clouds \cite{huang2006,greenwald2009,seethala2010,eliasson2011,duncan2018,khanal2020}, and this limits our comparison.
+The LWP distribution shows that all models overestimate cases with near-zero LWP (Fig.~\ref{fig:stats-hist-si}a), which relates to the underestimated total cloud fraction.
 MERRA-2 shows quite overestimated high-LWP situations, which is most likely related to the too few, too bright problem of simulating lower total cloud fraction but clouds with higher LWP to compensate.
-IWP (Fig.~\ref{fig:stats-hist}d) is somewhat less important radiatively than LWP because of the typically larger and less numerous hydrometeors.
+IWP (Fig.~\ref{fig:stats-hist-si}b) is somewhat less important radiatively than LWP because of the typically larger and less numerous hydrometeors.
 Similarly to LWP, the models overestimate situations with near-zero IWP.
 ERA5 is otherwise simulating the IWP distribution well, but ICON and MERRA-2 underestimate IWP.
-Fig.~\ref{fig:stats-hist-cloudy} shows the same as Fig.~\ref{fig:stats-hist}, but for cloudy profiles only.
-This figure shows more distinctly that in cloudy situations, MERRA-2 overestimates moderate (0.05--0.15 kg m$^{-2}$) and high LWP (over 0.15 kg m$^{-2}$), and ERA5 and ICON underestimate moderate LWP.
+In the cloudy situations (Fig.~\ref{fig:stats-hist-si}c, d), it can be seen more distinctly that MERRA-2 overestimates moderate (0.05--0.15 kg m$^{-2}$) and high LWP (over 0.15 kg m$^{-2}$), and ERA5 and ICON underestimate moderate LWP.
 ICON also overestimates high LWP, resulting in overestimated average LWP.
@@
 \centering
-\includegraphics[width=\textwidth]{img/stats_hist.pdf}
+\includegraphics[width=\textwidth]{img/stats_hist_rad.pdf}
 \caption{
-Histograms and averages of outgoing \textbf{(a)} SW and \textbf{(b)} LW radiation at TOA, \textbf{(c)} liquid water path, and \textbf{(d)} ice water path in CERES SYN1deg observations (OBS), ICON, MERRA-2, and ERA5 along the voyage tracks.
-All voyages are weighted equally.
-The statistics are calculated from daily mean values corresponding to each time step and geographical location of the voyage tracks.
+Histograms and averages of outgoing \textbf{(a)} SW and \textbf{(b)} LW radiation at TOA in CERES SYN1deg observations (OBS), ICON, MERRA-2, and ERA5.
+All campaigns are weighted equally.
+The statistics are calculated from daily mean values corresponding to each time step and geographical location of the voyage tracks and stations.
 }
-\label{fig:stats-hist}
+\label{fig:stats-hist-rad}
 \end{figure}
@@
 Notably, ICON exhibits smaller internal variability in $\theta_v$ than the radiosonde observations.
-The analysis of cloud liquid and ice water path (Fig.~\ref{fig:stats-hist} and \ref{fig:stats-hist-cloudy}) shows that both phases are present in observations in about equal amounts.
+The analysis of LWP and IWP (Fig.~\ref{fig:stats-hist-si}) shows that both phases are present in observations in about equal amounts.
 The models show diverse biases, the most pronounced being overestimation of high-LWP values in MERRA-2 and overestimation of cases with near-zero LWP and IWP in all models.
@@
 This can contribute to the too few, too bright bias, i.e., the the overestimated brightness of cloudy areas compensates for the lower total cloud fraction in the models.
+As mentioned in Section~\ref{sec:rad-lwp-iwp}, the LWP and IWP are, however, affected by high uncertainty of the satellite retrievals.
 

### 2025-07-18 si_rev1.tex
Various

@@
 \begin{figure}[p!]
-\includegraphics[width=\textwidth]{img/stats_hist_cloudy.pdf}
+\includegraphics[width=\textwidth]{img/stats_hist_si.pdf}
 \caption{
-The same as Fig.~\ref{fig:stats-hist} but for cloudy profiles only, as identified by the lidar cloud mask.
+Histograms and averages of \textbf{(a, c)} liquid water path, and \textbf{(b, d)} ice water path in CERES SYN1deg observations (OBS), ICON,
+MERRA-2, and ERA5 for \textbf{(a, b)} all and \textbf{(c, d)} cloudy profiles.
+All campaigns are weighted equally.
+The statistics are calculated from daily mean values corresponding to each time step and geographical location of the voyage tracks and stations.
 }
-\label{fig:stats-hist-cloudy}
+\label{fig:stats-hist-si}
 \end{figure}

### 2025-07-18 manuscript_agu_rev1.tex
Add citations for condensation below RH 100%

@@
 A possible explanation is that cloud droplets are able to form or persist at RH between 90 and 100\% at these heights over the SO.
-This could be due to abundant sea salt or biogenic aerosol or droplet generation from sea spray in the common high swell and high wind speed conditions over the SO.
+This could be due to abundant hygroscopic nuclei such as sea salt \cite{zieger2017,kong2018} or droplet generation from sea spray in the common high swell and high wind speed conditions over the SO \cite{revell2019,hartery2020}.
 Stratus fractus or other broken clouds could also lead to less than 100\% RH when averaged over the size of the vertical bins (up to 30 m in some of the radiosonde profiles).

### 2025-07-18 manuscript_agu_rev1.tex
Various

@@
 \item Large cloud biases are present in the global storm-resolving model, but are lower in several key aspects than in the reanalyses.
-\item The models tend to underestimate total cloud fraction, very low-level ($<$~250~m) cloud and fog, while overestimating cloud occurrence peak at 500 m.
+\item The models tend to underestimate total cloud fraction and very low-level ($<$~250~m) cloud and fog, while overestimating cloud occurrence peak at 500 m.
 \item A ``too few, too bright'' problem of underestimated cloud fraction, compensated by overestimated cloud albedo, is present in MERRA-2.
@@
 For the evaluation, we used ceilometer and radiosonde observations and a lidar simulator, which enables a fair comparison with ICON and reanalyses.
-We subsetted our results by cyclonic activity and stability.
+We subset our results by cyclonic activity and stability.
 We found that ICON and reanalyses underestimate lidar-derived cloud fraction, and the reanalyses do so more strongly.
@@
 The Macquarie Island station surface measurements and radiosonde profiles (not used in our analysis) were sent to the World Meteorological Organization Global Telecommunication System (GTS).
-The surface-level, lidar and radiosonde measurements on the RSV \textit{Aurora Australis} were not used outside of research purposes.
+The measurements on the RSV \textit{Aurora Australis} and HMNZS \textit{Wellington} were not used outside of research purposes.
+The AWS measurements but not lidar or radiosonde measurements on the RV \textit{Tangaroa} voyages were collected by the New Zealand MetService and communicated to the GTS.
+The ceilometer measurements on NBP1704 were not used outside of research purposes.
 
@@
 This is indicative of near-surface RH often being close to saturation in the observations but not in the models (Fig.~\ref{fig:stats-hist-surf}b).
-There are multiple possible reasons for this bias, such as how the statistical distribution of RH within a grid cell is represented in the models, the air--sea moisture flux parameterization, or weaker stability in the models can cause more boundary mixing across heights and thus lower near-surface RH.
+There are multiple possible reasons for this bias, such as how the statistical distribution of RH within a grid cell is represented in the models, the air--sea moisture flux parameterization, or weaker stability in the models, which can cause more boundary mixing across heights and thus lower near-surface RH.
 
@@
 Especially, the underestimation of fog or very low-level clouds is very substantial in the reanalyses, and we showed that this relates to cloud formation or persistence at RH between 80 and 100\% in the boundary layer in the observations, while in models RH values less than 100\% are associated with clear bins.
-We subsetted the dataset by low and high latitude SO bands, cyclonic activity, and stability in order to identify how these conditions influence the biases.
+We subset the dataset by low and high latitude SO bands, cyclonic activity, and stability in order to identify how these conditions influence the biases.
 The main identified biases are summarized in Table~\ref{tab:summary} and discussed below.

### 2025-07-18 manuscript_agu_rev1.tex
Various

@@
 
-Some of the observatial data were likely used in reanalysis assimilation.
+Some of the observational data were likely used in reanalysis assimilation.
 The Macquarie Island station surface measurements and radiosonde profiles (not used in our analysis) were sent to the World Meteorological Organization Global Telecommunication System (GTS).
 The measurements on the RSV \textit{Aurora Australis} and HMNZS \textit{Wellington} were not used outside of research purposes.
-The AWS measurements but not lidar or radiosonde measurements on the RV \textit{Tangaroa} voyages were collected by the New Zealand MetService and communicated to the GTS.
+The AWS measurements, but not lidar or radiosonde measurements on the RV \textit{Tangaroa} voyages, were collected by the New Zealand MetService and communicated to the GTS.
 The ceilometer measurements on NBP1704 were not used outside of research purposes.
@@
 
-When the data are subset by latitude (Fig.~\ref{fig:cloud-occurrence}b, c), we see that the low-latitude SO zone (40--55°S) displays a stronger peak of cloud occurrence near the surface than the high-latitude SO zone (between 55°S and the Antarctic coast), and this could be because higher latitudes have greater prevalence of weakly stable profiles (Fig.~\ref{fig:cyclone-stability}c, d), although more stable profiles populate regions south of 65°S close to the Antarctic coast.
+When the data are subset by latitude (Fig.~\ref{fig:cloud-occurrence}b, c), we see that the low-latitude SO zone (40--55°S) displays a stronger peak of cloud occurrence near the surface than the high-latitude SO zone (between 55°S and the Antarctic coast), and this could be because higher latitudes have a greater prevalence of weakly stable profiles (Fig.~\ref{fig:cyclone-stability}c, d), although more stable profiles populate regions south of 65°S close to the Antarctic coast.
 Cyclonic activity is also stronger in high-latitude SO, which is typically associated with shallow or deep convection rather than very stable stratification necessary for fog formation.
@@
 For example, we found that cloud occurrence at 1.5 km is underestimated in ICON and underlying clouds are overestimated.
-However, this can also mean that clouds at 1.5 km are present in the model but the signal is too attenuated by the lower clouds in the model but not in the observations, where the underlying clouds are not as pronounced.
+However, this can also mean that clouds at 1.5 km are present in the model but the signal is too attenuated by the lower clouds in the model, but not in the observations, where the underlying clouds are not as pronounced.
 
@@
 For example, some of the RV \textit{Polarstern} radiosondes are available in vertical resolution of about 20--30 m.
-The satellite retrieval of LWP is affected by large biases, especially over high latitudes \cite{khanal2020}, which limits our comparison with the models.
+As mentioned in Section~\ref{sec:rad-lwp-iwp}, the satellite retrieval of LWP and IWP is affected by large biases, especially over high latitudes, which limits our comparison with the models.
 
@@
 We suggest the following avenues for future research.
-Evaluation of ocean--atmosphere heat, moisture, and momentum fluxes with in-situ observations over the SO and comparison of GSRM simulations with large-eddy simulations in process-oriented studies; evaluation of the DYAMOND project simulations in a similar manner as performed here (for models which provide the necessary fields); and combining active satellite sensors such as the Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observations (CALIOP) on CALIPSO and Atmospheric Lidar [ATLID; \citeA{heliere2017}] on the Earth Clouds, Aerosols and Radiation Explorer [EarthCARE; \citeA{illingworth2015}] satellite with ground-based remote sensing could provide a more complete understanding of the cloud biases across the whole troposphere.
+Evaluation of ocean--atmosphere heat, moisture, and momentum fluxes with in-situ observations over the SO and comparison of GSRM simulations with large-eddy simulations in process-oriented studies; evaluation of the DYAMOND project simulations in a similar manner as performed here (for models that provide the necessary fields); and combining active satellite sensors such as the Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observations (CALIOP) on CALIPSO and Atmospheric Lidar [ATLID; \citeA{heliere2017}] on the Earth Clouds, Aerosols and Radiation Explorer [EarthCARE; \citeA{illingworth2015}] satellite with ground-based remote sensing could provide a more complete understanding of the cloud biases across the whole troposphere.
 Cloud phase could be analyzed in more detail using the CALIPSO data, as was done by \citeA{roh2020} in a cloud-resolving model, or using ground-based observations with a dual-polarization Mini Micro Pulse Lidar [MiniMPL; \citeA{spinhirne1993,campbell2002,flynn2007}] data available from the TAN1802 voyage.

### 2025-07-21 manuscript_agu_rev1.tex
Fix grammar

@@
 \begin{keypoints}
-\item Large cloud biases are present in the global storm-resolving model, but are lower in several key aspects than in the reanalyses.
+\item Large cloud biases are present in the global storm-resolving model but are lower in several key aspects than in the reanalyses.
 \item The models tend to underestimate total cloud fraction and very low-level ($<$~250~m) cloud and fog, while overestimating cloud occurrence peak at 500 m.
@@
 In total, about 2300 radiosonde profiles south of 40°S were available.
-Spatially and temporally colocated profiles were taken from the models.
+Spatially and temporally collocated profiles were taken from the models.
 Because the time period covered by the ICON model output (2021--2024) was different from the time period covered by the observations (2010--2021), when comparing with ICON, we first had to remap the observation time to model time by taking the same time relative to the start of the year.
@@
 CL51/31 indicates CL51 configured to emulate CL31.
-Missing days in the ceilometer data were HMNZSW16 (7 days): 24--27 November, 10~December, 16--17~December 2016; MARCUS (3 days): 8, 10~November, 10~December 2017; MICRE (9~days): 7--8, 29~June, 5, 16~July, 15~August, 17~October 2016, 11~February, 21~March 2017; TAN1502 (1~day): 24~January.
+Missing days in the ceilometer data were HMNZSW16 (7 days): 24--27 November, 10~December, and 16--17~December 2016; MARCUS (3 days): 8, 10~November, and 10~December 2017; MICRE (9~days): 7--8, 29~June, 5, 16~July, 15~August, 17~October 2016, 11~February, and 21~March 2017; and TAN1502 (1~day): 24~January.
 }
@@
 Non-convective clouds (condensation, autoconversion, and evaporation) are parameterized using a prognostic scheme \cite{bacmeister2006}, and sub-grid cloud fraction is determined using total water distribution and a critical RH threshold.
-The reanalysis output analyzed here is available at a spatial resolution of 0.5° of latitude and 0.625° of longitude, which is about 56 km in the North--South direction and 35 km in the East--West direction at 60°S.
+The reanalysis output analyzed here is available at a spatial resolution of 0.5° of latitude and 0.625° of longitude, which is about 56 km in the north--south direction and 35 km in the east--west direction at 60°S.
 The number of vertical model levels is 72.
@@
 It uses the \citeA{tiedtke1993} prognostic cloud scheme and \citeA{forbes2014} for mixed-phase clouds.
-The horizontal resolution is 0.25° in latitude and longitude, which is about 28~km in the North--South direction and 14~km in the East--West direction at 60°S.
+The horizontal resolution is 0.25° in latitude and longitude, which is about 28~km in the north--south direction and 14~km in the east--west direction at 60°S.
 Internally, the model uses 137 vertical levels.
@@
 More quiescent areas outside of cyclones can also be associated with clouds.
-These can be, for example, associated with clouds formed by warm or cold advection outside of cyclones, persistent clouds, clouds formed due to diurnal heating or cooling, or due to ocean currents.
+These can be, for example, associated with clouds formed by warm or cold advection outside of cyclones, persistent clouds, clouds formed due to diurnal heating or cooling, or clouds formed due to ocean currents.
 Boundary layer stability can be expected to be associated with clouds by either allowing convection and turbulence under weak stability, inhibiting convection turbulence under strong stability, and by capping inversion controlling the cloud top height or trapping moist air near the surface and preventing fog dispersion.
@@
 With this information, we could classify every location at a given time as either cyclonic or non-cyclonic.
-Due to a relatively small total area covered by cyclones, as identified by the cyclone center and radius, for every time step and cyclone we defined a cyclonic area as a circle of double the radius identified by CyTRACK centered at the cyclone center.
+Due to a relatively small total area covered by cyclones, as identified by the cyclone center and radius, for every time step and cyclone, we defined a cyclonic area as a circle of double the radius identified by CyTRACK centered at the cyclone center.
 All other areas were defined as non-cyclonic.
@@
 
-Fig.~\ref{fig:cyclone-stability}a, b show the geographical distribution of the fraction of cyclonic days as determined by the cyclone tracking algorithm applied to the ERA5 reanalysis and ICON data (Section~\ref{sec:cyclone-stability}).
+Fig.~\ref{fig:cyclone-stability}a and b show the geographical distribution of the fraction of cyclonic days as determined by the cyclone tracking algorithm applied to the ERA5 reanalysis and ICON data (Section~\ref{sec:cyclone-stability}).
 As expected, the strongest cyclonic activity is in the high-latitude SO zone and is relatively zonally symmetric at all latitudes.
@@
 When the data are subset by latitude (Fig.~\ref{fig:cloud-occurrence}b, c), we see that the low-latitude SO zone (40--55°S) displays a stronger peak of cloud occurrence near the surface than the high-latitude SO zone (between 55°S and the Antarctic coast), and this could be because higher latitudes have a greater prevalence of weakly stable profiles (Fig.~\ref{fig:cyclone-stability}c, d), although more stable profiles populate regions south of 65°S close to the Antarctic coast.
-Cyclonic activity is also stronger in high-latitude SO, which is typically associated with shallow or deep convection rather than very stable stratification necessary for fog formation.
+Cyclonic activity is also stronger in high-latitude SO, which is typically associated with shallow or deep convection rather than the very stable stratification necessary for fog formation.
 The low- and high-latitude SO zones show similar biases in models as in the general case, but ERA5 does not overestimate the peak in the low-latitude SO zone (very low-level cloud occurrence is still strongly underestimated).
 
-When the data are subset as either cyclonic and non-cyclonic situations (Fig.~\ref{fig:cloud-occurrence}d, e), we see that the cyclonic situations have a larger amount of observed cloudiness, including peak and total cloud fraction, by about 10\%.
+When the data are subset as either cyclonic or non-cyclonic situations (Fig.~\ref{fig:cloud-occurrence}d, e), we see that the cyclonic situations have a larger amount of observed cloudiness, including peak and total cloud fraction, by about 10\%.
 In the cyclonic situations, the model vertical profiles of cloud occurrence compare well with observations, but they peak higher by about 200 m and are larger by about 8\%.
@@
 Physically, conditions of strong stability are associated with the formation of advection fog, such as in situations of warm air advection from the north over a colder sea surface, thus inducing fog formation by cooling of the warm and humid air by the cold surface.
-In situations of strong stability, the models have smaller biases than in weak stability, with an overestimated peak up to 12\%, underestimated cloud occurrence above 1~km by up to 5\%, and underestimated cloud occurrence near the surface by about 10\% in the reanalyses but not ICON.
+In situations of strong stability, the models have smaller biases than in weak stability, with an overestimated peak of up to 12\%, underestimated cloud occurrence above 1~km by up to 5\%, and underestimated cloud occurrence near the surface by about 10\% in the reanalyses but not ICON.
 In situations of weak stability, the bias in ICON is very pronounced, with a much larger peak in cloud occurrence at about 500~m; the reanalyses underestimate cloud occurrence below 1~km, especially near the surface; and MERRA-2 underestimates cloud occurrence more strongly at almost all heights.
@@
 The LCL is derived from radiosonde profiles and equivalent model profiles, which were not available for all voyages and times.
-The total cloud fraction (CF), average shortwave (SW), and longwave (LW) and the relative frequency of occurrence (RFO) are shown.
+The total cloud fraction (CF), average outgoing shortwave (SW) and longwave (LW) radiation, and the relative frequency of occurrence (RFO) are shown.
 The bands are the 16$^\mathrm{th}$--84$^\mathrm{th}$ percentile, calculated from the set of all voyages and stations.
@@
 When all profiles in a day are taken together, the cloud cover for the day is defined as the fraction of cloudy profiles in the total number of profiles.
-It is expressed in oktas (multiples of 1/8), reflecting the 3-hourly model output of MERRA-2 and ICON, i.e.
-8 times per day.
+It is expressed in oktas (multiples of 1/8), reflecting the 3-hourly model output of MERRA-2 and ICON, i.e., 8 times per day.
 The same calculation is done for the lidar observations as for the simulated lidar profiles.
@@
 
-Fig.~\ref{fig:stats-hist-si} shows liquid water path (LWP), and ice water path (IWP) distributions as histograms and their corresponding averages.
-LWP and IWP are calculated from the mass of water in the column divided by the area of the column, i.e.
-not just the area of the cloudy portion of the column, as in some definitions.
-The available observational satellite reference for LWP and IWP over high latitudes is unfortunately very uncertain due to a high solar zenith angle and inability of passive visible and infrared retrievals to detect phase below the cloud top of mixed-phase clouds \cite{huang2006,greenwald2009,seethala2010,eliasson2011,duncan2018,khanal2020}, and this limits our comparison.
+Fig.~\ref{fig:stats-hist-si} shows liquid water path (LWP) and ice water path (IWP) distributions as histograms and their corresponding averages.
+LWP and IWP are calculated from the mass of water in the column divided by the area of the column, i.e., not just the area of the cloudy portion of the column, as in some definitions.
+The available observational satellite reference for LWP and IWP over high latitudes is unfortunately very uncertain due to a high solar zenith angle and the inability of passive visible and infrared retrievals to detect phase below the cloud top of mixed-phase clouds \cite{huang2006,greenwald2009,seethala2010,eliasson2011,duncan2018,khanal2020}, and this limits our comparison.
 The LWP distribution shows that all models overestimate cases with near-zero LWP (Fig.~\ref{fig:stats-hist-si}a), which relates to the underestimated total cloud fraction.
@@
 Unlike the foggy and 500-m cloud situations, situations with clouds at 1.5 km do not have a flat $\theta_v$ with height.
-This indicates that unlike the former, clouds at 1.5 km are not (or not as strongly) convectively driven.
+This indicates that, unlike the former, clouds at 1.5 km are not (or not as strongly) convectively driven.
 As expected, RH in these situations peaks at 1.5 km at about 85\% in observations.
@@
 Conversely, the opposite is true for cloudy bins (Fig.~\ref{fig:rs-thetav-hist}k--l).
-Situations with 0°C near-surface air temperature might occur predominantly when open ocean surface keeps the near-surface air temperature close to 0°C under otherwise colder air mass conditions, such as under cold advection.
+Situations with 0°C near-surface air temperature might occur predominantly when an open ocean surface keeps the near-surface air temperature close to 0°C under otherwise colder air mass conditions, such as under cold advection.
 ICON displays a notable bias above about 1 km, where the central peak is strongly underestimated (Fig.~\ref{fig:rs-thetav-hist}j).
@@
 Therefore, our results are likely representative of summer and, to a lesser extent, spring and autumn conditions.
-Ship access to sea ice covered areas of the SO is also limited.
-Cloud regimes and phase in the region are seasonally variable \cite{danker2022}.
+Ship access to sea-ice-covered areas of the SO is also limited.
+Cloud regimes and phases in the region are seasonally variable \cite{danker2022}.
 
@@
 Moreover, the simulation is free-running and ocean-coupled, which means that observations had to be temporally mapped to this time period (at the same time relative to the start of the year) for the comparison.
-For these reasons, one can expect the results to be slightly different due to reasons unrelated to model biases, such as different weather conditions, partially accounted for by the cyclone and stability subsetting, and the phase of climate oscillations such as the ENSO in the observations and ICON.
+For these reasons, one can expect the results to be slightly different due to reasons unrelated to model biases, such as different weather conditions, partially accounted for by the cyclone and stability subsetting, and the phase of climate oscillations, such as the ENSO in the observations and ICON.
 The interannual variability in cloud occurrence in ICON can be seen in Fig.~\ref{fig:cloud-occurrence-panel}, where each year in ICON is represented by a separate line.
@@
 For example, we found that cloud occurrence at 1.5 km is underestimated in ICON and underlying clouds are overestimated.
-However, this can also mean that clouds at 1.5 km are present in the model but the signal is too attenuated by the lower clouds in the model, but not in the observations, where the underlying clouds are not as pronounced.
+However, this can also mean that clouds at 1.5 km are present in the model, but the signal is too attenuated by the lower clouds in the model, but not in the observations, where the underlying clouds are not as pronounced.
 
@@
 We did not, however, analyze the cloud phase based on ground-based observations.
-Cloud phase can have a strong impact on the SW radiative transfer due to larger and therefore less numerous hydrometeors (for the same amount of water) scatter much less SW radiation.
+Cloud phase can have a strong impact on the SW radiative transfer due to larger and therefore less numerous hydrometeors (for the same amount of water) scattering much less SW radiation.
 Especially, the underestimation of fog or very low-level clouds is very substantial in the reanalyses, and we showed that this relates to cloud formation or persistence at RH between 80 and 100\% in the boundary layer in the observations, while in models RH values less than 100\% are associated with clear bins.
@@
 Precipitation in intense extratropical oceanic cyclones is projected to increase with future warming \cite{kodama2019}.
-The understanding of radiation biases was refined by \citeA{bodas-salcedo2014}, who highlighted that the SW bias was associated with an incorrectly simulated mid-level cloud regime, which occurred in regions where clouds with tops at mid-level and low-levels occurred.
-\citeA{ramadoss2024} have shown that in precipitating conditions, km-scale ICON has SW radiative biases associated with the overrepresentation of liquid phase at the cloud top in low stratocumuli clouds in a short (48-h) simulation over the SO.
+The understanding of radiation biases was refined by \citeA{bodas-salcedo2014}, who highlighted that the SW bias was associated with an incorrectly simulated mid-level cloud regime, which occurred in regions where clouds with tops at mid-level and low levels occurred.
+\citeA{ramadoss2024} have shown that in precipitating conditions, km-scale ICON has SW radiative biases associated with the overrepresentation of the liquid phase at the cloud top in low stratocumulus clouds in a short (48-h) simulation over the SO.
 \citeA{fiddes2024} suggested that biases in the liquid water path are the largest contributor to the cloud radiative bias over the SO.
@@
 It might also be interacting with the cloud inhomogeneity factor employed in ICON (Section~\ref{sec:icon}), resulting in lower cloud liquid water used in radiative calculations, hence decreased outgoing SW radiation.
-Based on the $\theta_v$ profiles analysis, clouds at 500 m are predominantly convectively driven, and it is therefore expected that a model bias towards weak stability results in an increased cloud formation at this level.
+Based on the $\theta_v$ profile analysis, clouds at 500 m are predominantly convectively driven, and it is therefore expected that a model bias towards weak stability results in an increased cloud formation at this level.
 The underestimation of clouds above 1 km in ICON does not have a clear physical reason in our analysis and is likely partially or fully caused by stronger obscuration of the simulated lidar signal by the underlying and overestimated clouds in ICON at around 500 m.
@@
 The reanalyses underestimate the total cloud fraction by about 20\%.
-ERA5 overestimates cloud below 1~km but underestimates very low-level cloud and fog.
+ERA5 overestimates clouds below 1~km but underestimates very low-level clouds and fog.
 ICON strongly overestimates the peak of cloud occurrence at about 500 m.
@@
 Cloudy areas would then appear brighter in the SW spectrum.
-This can contribute to the too few, too bright bias, i.e., the the overestimated brightness of cloudy areas compensates for the lower total cloud fraction in the models.
-As mentioned in Section~\ref{sec:rad-lwp-iwp}, the LWP and IWP are, however, affected by high uncertainty of the satellite retrievals.
+This can contribute to the too few, too bright bias, i.e., the overestimated brightness of cloudy areas compensates for the lower total cloud fraction in the models.
+As mentioned in Section~\ref{sec:rad-lwp-iwp}, the LWP and IWP are, however, affected by the high uncertainty of the satellite retrievals.
 
 The relationship between cloud biases and radiation has a number of notable features.
-MERRA-2 exhibits the too few, too bright bias previously identified in models.
+MERRA-2 exhibits the too-few-too-bright bias previously identified in models.
 In our results, this is characterized by overestimated outgoing TOA SW radiation, while at the same time total cloud fraction is underestimated based on the ground-based lidar observations.
@@
 Evaluation of ocean--atmosphere heat, moisture, and momentum fluxes with in-situ observations over the SO and comparison of GSRM simulations with large-eddy simulations in process-oriented studies; evaluation of the DYAMOND project simulations in a similar manner as performed here (for models that provide the necessary fields); and combining active satellite sensors such as the Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observations (CALIOP) on CALIPSO and Atmospheric Lidar [ATLID; \citeA{heliere2017}] on the Earth Clouds, Aerosols and Radiation Explorer [EarthCARE; \citeA{illingworth2015}] satellite with ground-based remote sensing could provide a more complete understanding of the cloud biases across the whole troposphere.
-Cloud phase could be analyzed in more detail using the CALIPSO data, as was done by \citeA{roh2020} in a cloud-resolving model, or using ground-based observations with a dual-polarization Mini Micro Pulse Lidar [MiniMPL; \citeA{spinhirne1993,campbell2002,flynn2007}] data available from the TAN1802 voyage.
+Cloud phase could be analyzed in more detail using the CALIPSO data, as was done by \citeA{roh2020} in a cloud-resolving model, or using ground-based observations with the dual-polarization Mini Micro Pulse Lidar [MiniMPL; \citeA{spinhirne1993,campbell2002,flynn2007}] data available from the TAN1802 voyage.
 \citeA{guyot2022} and \citeA{whitehead2024} have developed a machine learning method for identifying cloud phase from ceilometer data, and this could be used with our ground-based lidar dataset to analyze the cloud phase.
@@
 We acknowledge the contribution of Thorsten Mauritsen to funding acquisition and project management.
-We acknowledge the RV \emph{Polarstern} datasets provided by the Alfred Wegener Institute and Pangaea, the AA15-16 dataset provided by the Australian Antarctic Division (AAD) and University of Canterbury (UC), the RV \emph{Tangaroa} datasets provided by the National Institute of Water and Atmospheric Research and UC, the NBP1704 dataset provided by the National Science Foundation, Cooperative Institute for Research in Environmental Sciences, University of Colorado, and UC, the HMNZSW16 dataset provided by the Royal New Zealand Navy and UC, the MARCUS dataset provided by ARM and AAD, and the MICRE dataset provided by ARM, the Australian Bureau of Meteorology, and AAD.
+We acknowledge the RV \emph{Polarstern} datasets provided by the Alfred Wegener Institute and Pangaea; the AA15-16 dataset provided by the Australian Antarctic Division (AAD) and University of Canterbury (UC); the RV \emph{Tangaroa} datasets provided by the National Institute of Water and Atmospheric Research and UC; the NBP1704 dataset provided by the National Science Foundation, Cooperative Institute for Research in Environmental Sciences, University of Colorado, and UC; the HMNZSW16 dataset provided by the Royal New Zealand Navy and UC; the MARCUS dataset provided by ARM and AAD; and the MICRE dataset provided by ARM, the Australian Bureau of Meteorology, and AAD.
 Technical, logistical, and ship support for MARCUS and MICRE were provided by the AAD through Australian Antarctic Science projects 4292 and 4387, and we thank Steven Whiteside, Lloyd Symonds, Rick van den Enden, Peter de Vries, Chris Young, Chris Richards, Andrew Klekociuk, John French, Terry Egan, Nick Cartwright, and Ken Barrett for all of their assistance.

### 2025-07-21 si_rev1.tex
Fix grammar

@@
 \caption{
-Histograms and averages of \textbf{(a, c)} liquid water path, and \textbf{(b, d)} ice water path in CERES SYN1deg observations (OBS), ICON,
-MERRA-2, and ERA5 for \textbf{(a, b)} all and \textbf{(c, d)} cloudy profiles.
+Histograms and averages of \textbf{(a, c)} liquid water path and \textbf{(b, d)} ice water path in CERES SYN1deg observations (OBS), ICON, MERRA-2, and ERA5 for \textbf{(a, b)} all and \textbf{(c, d)} cloudy profiles.
 All campaigns are weighted equally.

### 2025-07-21 manuscript_agu_rev1.tex
Fix grammar

@@
 Its high resolution means that parameterizations of convection and clouds, including subgrid-scale clouds, are omitted, relying on explicit simulation but necessarily utilizing microphysics and turbulence parameterizations.
-Standard-resolution (10--100~km) models, which use convection and cloud parameterizations, have substantial cloud biases over the Southern Ocean (SO), adversely affecting radiation and sea surface temperature.
+Standard-resolution (10–100~km) models, which use convection and cloud parameterizations, have substantial cloud biases over the Southern Ocean (SO), adversely affecting radiation and sea surface temperature.
 The SO is dominated by low clouds, which cannot be observed accurately from space due to overlapping clouds, attenuation, and ground clutter.
-We evaluated SO clouds in ICON and the ERA5 and MERRA-2 reanalyses using approximately 2400 days of lidar observations and 2300 radiosonde profiles from 31 voyages and Macquarie Island station during 2010--2021, compared with the models using a ground-based lidar simulator.
+We evaluated SO clouds in ICON and the ERA5 and MERRA-2 reanalyses using approximately 2400 days of lidar observations and 2300 radiosonde profiles from 31 voyages and Macquarie Island station during 2010–2021, compared with the models using a ground-based lidar simulator.
 We found that ICON and the reanalyses underestimate the total cloud fraction by about 10 and 20\%, respectively.
@@
 Increasing resolution is, of course, limited by the available computational power and a trade-off with increasing parameterization complexity, which is another way of improving model accuracy.
-Current computational availability and acceleration from general-purpose computing on graphics processing units (GPUs) has progressed to enable km-scale (also called k-scale) Earth system models (ESMs) and coupled atmosphere--ocean general circulation models (AOGCMs) for research today and will become operational in the future.
+Current computational availability and acceleration from general-purpose computing on graphics processing units has progressed to enable km-scale (also called k-scale) Earth system models (ESMs) and coupled atmosphere–ocean general circulation models for research today and will become operational in the future.
 Therefore, it represents a natural advance in climate modeling.
-Global storm-resolving models (GSRMs) are emerging as a new front in the development of high-resolution global climate models, with horizontal grid resolutions of about 2--8~km \cite{satoh2019,stevens2019}.
+Global storm-resolving models (GSRMs) are emerging as a new front in the development of high-resolution global climate models, with horizontal grid resolutions of about 2–8~km \cite{satoh2019,stevens2019}.
 This resolution is enough to resolve mesoscale convective storms, but smaller-scale convective plumes and cloud structure remain unresolved.
@@
 The terms global cloud-resolving models or global convection-permitting/-resolving models are also sometimes used interchangeably with GSRMs but imply that clouds or convection are resolved explicitly, which is not entirely true for GSRMs, as this would require an even higher horizontal resolution \cite{satoh2019}.
-Representative of these efforts is the DYnamics of the Atmospheric general circulation Modeled On Non-hydrostatic Domains (DYAMOND) project \cite{stevens2019,dyamond}, which is an intercomparison of nine global GSRMs over two 40-day time periods in summer (1~August--10~September 2016) and winter (20~January--1~March 2020).
+Representative of these efforts is the DYnamics of the Atmospheric general circulation Modeled On Non-hydrostatic Domains (DYAMOND) project \cite{stevens2019,dyamond}, which is an intercomparison of nine global GSRMs over two 40-day time periods in summer (1~August–10~September 2016) and winter (20~January–1~March 2020).
 A new one-year GSRM intercomparison is currently proposed by \citeA{takasuka2024}, with the hope of also evaluating the seasonal cycle and large-scale circulation.
@@
 This region is mostly dominated by boundary layer clouds generated by shallow convection, and these are problematic to observe by spaceborne lidars and radars, which are affected by attenuation by overlapping and thick clouds \cite{mace2009,medeiros2010} and ground clutter \cite{marchand2008}, respectively.
-Specifically, the radar on CloudSat and lidar on the Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observation (CALIPSO), neither of which are now operational, are affected by the above-mentioned issues, resulting in a strong underestimation of cloud occurrence below 2 km in a merged CloudSat--CALIPSO product relative to ground-based lidar observations at McMurdo Station \cite{mcerlich2021}.
+Specifically, the radar on CloudSat and lidar on the Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observation (CALIPSO), neither of which are now operational, are affected by the above-mentioned issues, resulting in a strong underestimation of cloud occurrence below 2 km in a merged CloudSat–CALIPSO product relative to ground-based lidar observations at McMurdo Station \cite{mcerlich2021}.
 Removing situations with higher overlapping clouds could enable a less biased comparison of low clouds.
-We hypothesize that this, in turn, can lead to systematic biases in low clouds in climate models, which are frequently evaluated against CloudSat--CALIPSO products.
+We hypothesize that this, in turn, can lead to systematic biases in low clouds in climate models, which are frequently evaluated against CloudSat–CALIPSO products.
 Reanalyses can also suffer from cloud biases, as these are usually parameterized in their atmospheric component and also in regions where input observations are sparse.
 This makes them a problematic reference for clouds over the SO, and any biases relative to a reanalysis should be interpreted with caution.
-Instead, we chose to use a large set of ship-based observations conducted with ceilometers and lidars on board the RV \emph{Polarstern} and other voyages and a station as a reference for the model evaluation.
+Instead, we chose to use a large set of ship-based observations conducted with ceilometers and lidars on board the research vessel (RV) \emph{Polarstern} and other voyages and a station as a reference for the model evaluation.
 Altogether, we analyzed approximately 2400 days of data from 31 voyages and one sub-Antarctic station covering diverse longitudes and latitudes of the SO.
 To achieve a like-for-like comparison with the models (ICON, MERRA-2, and ERA5), we used a ground-based lidar simulator called the Automatic Lidar and Ceilometer Framework [ALCF; \citeA{kuma2021}].
-We contrasted the results with ERA5 \cite{era5} and the Modern-Era Retrospective analysis for Research and Applications, Version~2 [MERRA-2; \citeA{gelaro2017}].
+We contrasted the results with the European Centre for Medium-Range Weather Forecasts (ECMWF) Reanalysis 5 [ERA5; \citeA{era5}] and the Modern-Era Retrospective analysis for Research and Applications, Version~2 [MERRA-2; \citeA{gelaro2017}].
 
@@
 The project also develops GSRM versions of the Icosahedral Nonhydrostatic Weather and Climate Model (ICON; \citeA{hohenegger2023}), the Integrated Forecasting System [IFS; \citeA{ifs2023}], and their ocean components at eddy-resolving resolutions: ICON-O \cite{korn2022} coupled with ICON and Finite-Element/volumE Sea ice-Ocean Model [FESOM; \citeA{wang2014a}] and Nucleus for European modeling of the Ocean [NEMO; \citeA{madec2023}] coupled with IFS.
-The project has so far produced ICON and IFS simulations with three development versions called Cycle 1--3 and a pre-final version, with a final production version planned by the end of the project.
+The project has so far produced ICON and IFS simulations with three development versions called Cycle 1–3 and a pre-final version, with a final production version planned by the end of the project.
 nextGEMS is not the only project developing GSRMs; other GSRMs (or GSRM versions of climate models) currently in development include: Convection-Permitting Simulations With the E3SM Global Atmosphere Model [SCREAM; \citeA{caldwell2021}], Non-hydrostatic Icosahedral Atmospheric Model [NICAM; \citeA{satoh2008}], Unified Model (UM), eXperimental System for High-resolution modeling for Earth-to-Local Domain [X-SHiELD; \citeA{shield}], Action de Recherche Petite Echelle Grande Echelle-NonHydrostatic version [ARPEGE-NH; \citeA{bubnova1995,voldoire2017}], Finite-Volume Dynamical Core on the Cubed Sphere [FV3, \citeA{lin2004}], the National Aeronautics and Space Administration (NASA) Goddard Earth Observing System global atmospheric model version 5 [GEOS5; \citeA{putman2011}], Model for Prediction Across Scales [MPAS; \citeA{skamarock2012}], and System for Atmospheric Modeling [SAM; \citeA{khairoutdinov2003}].
@@
 Multiple cloud properties have an effect on shortwave (SW) and longwave (LW) radiation.
-To first order, the total cloud fraction, cloud phase, and the liquid and ice water path are the most important cloud properties influencing SW and LW radiation.
+To first order, the total cloud fraction, cloud phase, and the liquid and ice water path (LWP and IWP) are the most important cloud properties influencing SW and LW radiation.
 These properties are in turn influenced by the atmospheric thermodynamics, convection and circulation, and both the indirect and direct effects of aerosols.
@@
 
-In the following text, we refer to the SO as ocean regions south of 40°S, low-latitude SO as 40--55°S, and high-latitude SO as south of 55°S, all the way to the Antarctic coast.
+In the following text, we refer to the SO as ocean regions south of 40°S, low-latitude SO as 40–55°S, and high-latitude SO as south of 55°S, all the way to the Antarctic coast.
 The reason for this dividing latitude is to split the SO into about two equal zones, as well as the results by \citeA{schuddeboom2021} (Fig.~2b) which show a contrast in CMIP model radiation biases.
@@
 
-SO radiation biases have been relatively large and systematic compared to the rest of the globe since at least CMIP3 \cite{trenberth2010,bodas-salcedo2012}, and the SO SW cloud radiative effect (CRE) bias is still positive in eight CMIP6 models analyzed by \citeA{schuddeboom2021} over the high-latitude SO, whereas over the low-latitude SO it tends to be more neutral or negative in some models.
+SO radiation biases have been relatively large and systematic compared to the rest of the globe since at least CMIP3 \cite{trenberth2010,bodas-salcedo2012}, and the SO SW cloud radiative effect bias is still positive in eight CMIP6 models analyzed by \citeA{schuddeboom2021} over the high-latitude SO, whereas over the low-latitude SO it tends to be more neutral or negative in some models.
 Too much absorbed SW radiation over the SO was also identified in the GSRM SCREAM \cite{caldwell2021}.
 Compensating biases are possible, such as the ``too few too bright'' cloud bias, characterized by too small a cloud fraction and too large a cloud albedo \cite{wall2017,kuma2020}, previously described by \citeA{webb2001}, \citeA{weare2004}, \citeA{zhang2005}, \citeA{karlsson2008}, \citeA{nam2012}, \citeA{klein2013}, and \citeA{bender2017} in other regions and models, which means that a model can maintain a reasonable SW radiation balance by reflecting too much SW radiation from clouds, but these cover too small an area.
-A study by \citeA{konsta2022} showed that this type of bias is still present in six analyzed CMIP6 models in tropical marine clouds, using the GCM-Oriented CALIPSO Cloud Product [CALIPSO--GOCCP; \citeA{chepfer2010}] and Polarization \& Anisotropy of Reflectances for Atmospheric Sciences coupled with Observations from a Lidar [PARASOL; \citeA{lier2008}] as a reference.
+A study by \citeA{konsta2022} showed that this type of bias is still present in six analyzed CMIP6 models in tropical marine clouds, using the General-circulation-model-Oriented CALIPSO Cloud Product [CALIPSO–GOCCP; \citeA{chepfer2010}] and Polarization \& Anisotropy of Reflectances for Atmospheric Sciences coupled with Observations from a Lidar [PARASOL; \citeA{lier2008}] as a reference.
 They suggest improper simulation of subgrid-scale cloud heterogeneity as a cause.
@@
 \citeA{possner2022} showed that over the SO, the DYAMOND GSRM ICON underestimates low-level cloud fraction on the order of 30\% and overestimates net downward TOA SW radiation by approximately 10 Wm$^\mathrm{-2}$ in the highest model resolution run (2.5~km).
-\citeA{zhao2022} reported a similar SW radiation bias in five analyzed CMIP6 models over the high-latitude SO and an underestimation of the total cloud fraction on the order of 10\% over the entire 40--60°S SO.
+\citeA{zhao2022} reported a similar SW radiation bias in five analyzed CMIP6 models over the high-latitude SO and an underestimation of the total cloud fraction on the order of 10\% over the entire 40–60°S SO.
 Recently, \citeA{ramadoss2024} analyzed 48~hours of km-scale ICON limited-area model NWP simulations over an SO region adjacent to Tasmania against the Clouds, Aerosols, Precipitation, Radiation, and atmospherIc Composition Over the southeRn oceaN (CAPRICORN) voyage cloud and precipitation observations \cite{mcfarquhar2021}.
@@
 
-In general, sea surface temperature (SST) biases in the SO can originate either in the atmosphere \cite{hyder2018}, caused by too much shortwave heating of the surface or too little longwave cooling of the surface, such as in situations of too much cloud cover or cloud optical thickness, or in the ocean circulation.
+In general, sea surface temperature (SST) biases in the SO can originate either in the atmosphere \cite{hyder2018}, caused by too much SW heating of the surface or too little LW cooling of the surface, such as in situations of too much cloud cover or cloud optical thickness, or in the ocean circulation.
 Interactions of both are also possible; for example, SST affecting clouds and clouds affecting the surface radiation.
-Using the European Centre for Medium-Range Weather Forecasts (ECMWF) Reanalysis 5 (ERA5) as a reference, \citeA{zhang2023} have shown that SST biases have improved in CMIP6 compared to CMIP5, with SST overall increasing in CMIP6.
+Using ERA5 as a reference, \citeA{zhang2023} have shown that SST biases have improved in CMIP6 compared to CMIP5, with SST overall increasing in CMIP6.
 However, over the SO, this resulted in an even higher positive bias, especially in the Atlantic Ocean (AO) sector of the SO, increasing by up to 1°C.
@@
 Palmer}, and HMNZS \emph{Wellington} and one sub-Antarctic station (Macquarie Island) analyzed here.
-The tracks cover Antarctic sectors south of South America, the Atlantic Ocean, Africa, Australia, and New Zealand in the years 2010--2021 (inclusive).
+The tracks cover Antarctic sectors south of South America, the Atlantic Ocean, Africa, Australia, and New Zealand in the years 2010–2021 (inclusive).
 The dotted and dashed lines at 40°S and 55°S delineate the Southern Ocean area of our analysis and its partitioning into two subsets, respectively.
@@
 Spatially and temporally collocated profiles were taken from the models.
-Because the time period covered by the ICON model output (2021--2024) was different from the time period covered by the observations (2010--2021), when comparing with ICON, we first had to remap the observation time to model time by taking the same time relative to the start of the year.
+Because the time period covered by the ICON model output (2021–2024) was different from the time period covered by the observations (2010–2021), when comparing with ICON, we first had to remap the observation time to model time by taking the same time relative to the start of the year.
 Consequently, we also had four virtual/model profiles (one for each year from 2021 to 2024) for each observed profile.
@@
 CL51/31 indicates CL51 configured to emulate CL31.
-Missing days in the ceilometer data were HMNZSW16 (7 days): 24--27 November, 10~December, and 16--17~December 2016; MARCUS (3 days): 8, 10~November, and 10~December 2017; MICRE (9~days): 7--8, 29~June, 5, 16~July, 15~August, 17~October 2016, 11~February, and 21~March 2017; and TAN1502 (1~day): 24~January.
+Missing days in the ceilometer data were HMNZSW16 (7 days): 24–27 November, 10~December, and 16–17~December 2016; MARCUS (3 days): 8, 10~November, and 10~December 2017; MICRE (9~days): 7–8, 29~June, 5, 16~July, 15~August, 17~October 2016, 11~February, and 21~March 2017; and TAN1502 (1~day): 24~January.
 }
@@
 
-A coupled (atmosphere--ocean) GSRM version of the ICON model is in development as part of the nextGEMS project \cite{hohenegger2023}.
+A coupled (atmosphere–ocean) GSRM version of the ICON model is in development as part of the nextGEMS project \cite{hohenegger2023}.
 ICON is a very flexible model, allowing for simulations ranging from coarse-resolution ESM simulations, GSRM simulations, limited area model simulations, and large eddy simulations (LES) for both weather prediction and climate projections.
@@
 nextGEMS has so far produced four cycles of model runs.
-We used a Cycle 3 run \emph{ngc3028} produced in 2023 \cite{nextgems2023a,nextgems2023b} for a model time period of 20 January 2020 to 22 July 2025, of which we analyzed the period 2021--2024 (inclusive).
+We used a Cycle 3 run \emph{ngc3028} produced in 2023 \cite{nextgems2023a,nextgems2023b} for a model time period of 20 January 2020 to 22 July 2025, of which we analyzed the period 2021–2024 (inclusive).
 The horizontal resolution of ngc3028 is about 5 km.
@@
 
-Unlike current general circulation models (GCMs), the storm-resolving version of ICON does not use convective and cloud parameterization but relies on explicit simulation of convection and clouds on the model grid.
+Unlike current general circulation models, the storm-resolving version of ICON does not use convective and cloud parameterization but relies on explicit simulation of convection and clouds on the model grid.
 Subgrid-scale clouds are not resolved, and the grid cell cloud fraction is always either 0 or 100\%.
@@
 
-Because the analyzed ICON simulation was free-running (years 2021--2024, inclusive), weather and climate oscillations (such as the El Niño--Southern Oscillation phase) are not expected to be equivalent to reality.
-To compare with the observations collected during a different time period (years 2010--2021, inclusive), we compared the model output with observations at the same time of year and geographical location, as determined for each data point, such as a lidar profile or a radiosonde launch.
+Because the analyzed ICON simulation was free-running (years 2021–2024, inclusive), weather and climate oscillations [such as the El Niño–Southern Oscillation (ENSO) phase] are not expected to be equivalent to reality.
+To compare with the observations collected during a different time period (years 2010–2021, inclusive), we compared the model output with observations at the same time of year and geographical location, as determined for each data point, such as a lidar profile or a radiosonde launch.
 In the ALCF, this was done using the \emph{override\_year} option (\url{https://alcf.peterkuma.net/documentation/cli/cmd_model.html}).
@@
 Non-convective clouds (condensation, autoconversion, and evaporation) are parameterized using a prognostic scheme \cite{bacmeister2006}, and sub-grid cloud fraction is determined using total water distribution and a critical RH threshold.
-The reanalysis output analyzed here is available at a spatial resolution of 0.5° of latitude and 0.625° of longitude, which is about 56 km in the north--south direction and 35 km in the east--west direction at 60°S.
+The reanalysis output analyzed here is available at a spatial resolution of 0.5° of latitude and 0.625° of longitude, which is about 56 km in the north–south direction and 35 km in the east–west direction at 60°S.
 The number of vertical model levels is 72.
@@
 ERA5 \cite{era5} is a reanalysis produced by the ECMWF.
-It is based on a numerical weather prediction model IFS version CY41R2.
+It is based on an NWP model IFS version CY41R2.
 It uses the \citeA{tiedtke1993} prognostic cloud scheme and \citeA{forbes2014} for mixed-phase clouds.
-The horizontal resolution is 0.25° in latitude and longitude, which is about 28~km in the north--south direction and 14~km in the east--west direction at 60°S.
+The horizontal resolution is 0.25° in latitude and longitude, which is about 28~km in the north–south direction and 14~km in the east–west direction at 60°S.
 Internally, the model uses 137 vertical levels.
@@
 
-TOA radiation quantities are taken from the CERES instruments onboard the Terra and Aqua satellites \cite{wielicki1996,loeb2018}.
-In our analysis, we used adjusted all-sky SW and LW upwelling fluxes at TOA, adjusted cloud liquid and ice water paths, and adjusted cloud amount from the synoptic TOA and surface fluxes and clouds 1-degree daily edition 4A product (CER\_SYN1deg-Day\_Terra-Aqua-MODIS\_Edition4A) \cite{doelling2013,doelling2016}.
+TOA radiation quantities are taken from the Clouds and the Earth’s Radiant Energy System (CERES) instruments onboard the Terra and Aqua satellites \cite{wielicki1996,loeb2018}.
+In our analysis, we used the adjusted all-sky SW and LW upwelling fluxes at TOA, adjusted cloud LWP and IWP, and adjusted cloud amount from the synoptic TOA and surface fluxes and clouds 1-degree daily edition 4A product (CER\_SYN1deg-Day\_Terra-Aqua-MODIS\_Edition4A) \cite{doelling2013,doelling2016}.
 The water paths in the product are computed from optical depth and particle size from geostationary satellites and the Moderate Resolution Imaging Spectroradiometer [MODIS, \citeA{pagano1993}] \cite{ceres2025}.
@@
 Therefore, dividing our dataset by these subsets allows us to quantify model biases associated with some of the main physical processes controlling cloud formation, persistence, and dissipation.
-Other methods of subsetting, such as using the ISCCP pressure--optical thickness diagram \cite{rossow1991,rossow1999,hahn2001} to separate profiles by cloud regimes and other cloud regime classifications \cite{oreopoulos2016,schuddeboom2018}, would be feasible.
+Other methods of subsetting, such as using the International Satellite Cloud Climatology Project (ISCCP) pressure–optical thickness diagram \cite{rossow1991,rossow1999,hahn2001} to separate profiles by cloud regimes and other cloud regime classifications \cite{oreopoulos2016,schuddeboom2018}, would be feasible.
 
 We partitioned our data into two mutually exclusive subsets by cyclonic activity.
-For this purpose, we used a cyclone tracking algorithm to identify extratropical and polar cyclones (ECs and PCs) over the SO in the reanalysis and ICON data.
+For this purpose, we used a cyclone tracking algorithm to identify extratropical cyclones and polar cyclones over the SO in the reanalysis and ICON data.
 We used the open-source cyclone tracking package CyTRACK \cite{perez-alarcon2024}.
-Generally, what constitutes an EC is considered relatively arbitrary due to the very large variability of ECs \cite{neu2013}.
+Generally, what constitutes an extratropical cyclone is considered relatively arbitrary due to the very large variability of the cyclones \cite{neu2013}.
 The CyTRACK algorithm uses mean sea level pressure and wind speed thresholds as well as tracking across time steps to identify cyclone centers and their radii in each time step.
@@
 \caption{
-Geographical distribution of \textbf{(a, b)} cyclonic days and \textbf{(b, d)} strong stability (LTS~$\geq$~12~K) time steps in \textbf{(a, c)} ERA5 in years 2010--2013 (inclusive) and \textbf{(b, d)} ICON in model years 2021--2023 (free running).
+Geographical distribution of \textbf{(a, b)} cyclonic days and \textbf{(b, d)} strong stability (LTS~$\geq$~12~K) time steps in \textbf{(a, c)} ERA5 in years 2010–2013 (inclusive) and \textbf{(b, d)} ICON in model years 2021–2023 (free running).
 Cyclonic days are expressed as a fraction of the number of days with cyclonic activity, defined as grid points located within a double radius of any cyclone on a given day (UTC), as identified by CyTRACK.
@@
 Fig.~\ref{fig:cyclone-stability}c, d show the geographical distribution of the conditions of weak and strong stability as determined by the LTS (Section~\ref{sec:cyclone-stability}).
-Conditions of weak stability are prevalent in the mid-to-high SO (50--65°S), which might be explained by the relatively cold near-surface air overlying the relatively warm sea surface.
+Conditions of weak stability are prevalent in the mid-to-high SO (50–65°S), which might be explained by the relatively cold near-surface air overlying the relatively warm sea surface.
 Conditions of strong stability are common elsewhere over the SO.
@@
 ICON is also substantially less stable than ERA5 across the whole region.
-In Section~\ref{sec:thermodynamic-profiles} we show that based on radiosonde observations, the bias is in ICON and not ERA5, and it is the result of underestimated temperature at heights corresponding to 700 hPa, as well as overestimated near-surface (2~m) air temperature, characterized by a higher frequency of occurrence in the 1--7°C range compared to observations at radiosonde launch locations (Fig.~\ref{fig:stats-hist-surf}a).
+In Section~\ref{sec:thermodynamic-profiles} we show that based on radiosonde observations, the bias is in ICON and not ERA5, and it is the result of underestimated temperature at heights corresponding to 700 hPa, as well as overestimated near-surface (2~m) air temperature, characterized by a higher frequency of occurrence in the 1–7°C range compared to observations at radiosonde launch locations (Fig.~\ref{fig:stats-hist-surf}a).
 This may be related to large-scale circulation in ICON or radiative transfer biases.
@@
 For all observations considered (Fig.~\ref{fig:cloud-occurrence}a), the data show cloud occurrence peaking near the surface, whereas the models show a higher peak (at about 500~m).
-The models generally underestimate the total cloud fraction by 10--30\% and show a strong drop in cloud occurrence near the surface, which is not identified in the observations.
+The models generally underestimate the total cloud fraction by 10–30\% and show a strong drop in cloud occurrence near the surface, which is not identified in the observations.
 ICON and ERA5 overestimate cloud occurrence at their peak (between 0 and 1~km).
@@
 This is indicative of near-surface RH often being close to saturation in the observations but not in the models (Fig.~\ref{fig:stats-hist-surf}b).
-There are multiple possible reasons for this bias, such as how the statistical distribution of RH within a grid cell is represented in the models, the air--sea moisture flux parameterization, or weaker stability in the models, which can cause more boundary mixing across heights and thus lower near-surface RH.
+There are multiple possible reasons for this bias, such as how the statistical distribution of RH within a grid cell is represented in the models, the air–sea moisture flux parameterization, or weaker stability in the models, which can cause more boundary mixing across heights and thus lower near-surface RH.
 
-When the data are subset by latitude (Fig.~\ref{fig:cloud-occurrence}b, c), we see that the low-latitude SO zone (40--55°S) displays a stronger peak of cloud occurrence near the surface than the high-latitude SO zone (between 55°S and the Antarctic coast), and this could be because higher latitudes have a greater prevalence of weakly stable profiles (Fig.~\ref{fig:cyclone-stability}c, d), although more stable profiles populate regions south of 65°S close to the Antarctic coast.
+When the data are subset by latitude (Fig.~\ref{fig:cloud-occurrence}b, c), we see that the low-latitude SO zone (40–55°S) displays a stronger peak of cloud occurrence near the surface than the high-latitude SO zone (between 55°S and the Antarctic coast), and this could be because higher latitudes have a greater prevalence of weakly stable profiles (Fig.~\ref{fig:cyclone-stability}c, d), although more stable profiles populate regions south of 65°S close to the Antarctic coast.
 Cyclonic activity is also stronger in high-latitude SO, which is typically associated with shallow or deep convection rather than the very stable stratification necessary for fog formation.
@@
 The total cloud fraction (CF), average outgoing shortwave (SW) and longwave (LW) radiation, and the relative frequency of occurrence (RFO) are shown.
-The bands are the 16$^\mathrm{th}$--84$^\mathrm{th}$ percentile, calculated from the set of all voyages and stations.
+The bands are the 16$^\mathrm{th}$–84$^\mathrm{th}$ percentile, calculated from the set of all voyages and stations.
 }
@@
 In Fig.~\ref{fig:cloud-cover} we show the results for the same subsets of data as in Section~\ref{sec:cloud-occurrence}.
-Observations display the highest proportion of high cloud cover values (5--8~oktas), peaking at 7~oktas.
+Observations display the highest proportion of high cloud cover values (5–8~oktas), peaking at 7~oktas.
 This pattern is not represented by ICON or either reanalysis.
@@
 When we contrast the low- and high-latitude zones, we see that the high-latitude zone tends to have greater cloud cover, peaking at 8~oktas (Fig.~\ref{fig:cloud-cover}c).
-The high-latitude zone also has almost no clear sky or small cloud cover cases (0--4~oktas).
-ICON and the reanalyses represent this characteristic of the distribution well for 0--3~oktas, but otherwise show biases similar to the general case.
+The high-latitude zone also has almost no clear sky or small cloud cover cases (0–4~oktas).
+ICON and the reanalyses represent this characteristic of the distribution well for 0–3~oktas, but otherwise show biases similar to the general case.
 One of the greatest biases is present in ERA5 in the subset of weak stability, in which ERA5 peaks at 3~oktas, while the observations peak at 7~oktas and show negligible cloud cover below 5~oktas.
@@
 
-In Fig.~\ref{fig:cloud-occurrence}, we also show the mean outgoing shortwave and longwave top-of-atmosphere radiation, whose calculation is described in Section~\ref{sec:ceres}.
+In Fig.~\ref{fig:cloud-occurrence}, we also show the mean outgoing SW and LW TOA radiation, whose calculation is described in Section~\ref{sec:ceres}.
 In observations, these come from daily mean CERES measurements averaged over the voyage tracks or a station location, whereas in the models they come from daily means of TOA radiation in the model output averaged over the same location and time periods.
@@
 In ICON, the outgoing LW radiation is overestimated by 5\% (Fig.~\ref{fig:cloud-occurrence}a).
-This is likely caused by an underestimated total cloud fraction exposing a larger sea surface area to cooling to space, which is typically warmer than the atmospheric temperature at 0--2~km, where most of the clouds are located.
+This is likely caused by an underestimated total cloud fraction exposing a larger sea surface area to cooling to space, which is typically warmer than the atmospheric temperature at 0–2~km, where most of the clouds are located.
 In the MERRA-2 and ERA5 reanalyses, the LW biases are also slightly positive, 4 and 5~Wm$^{-2}$, respectively.
@@
 
-In all the subsets (Fig.~\ref{fig:cloud-occurrence}b--g), the same type of biases are observed, namely the outgoing SW radiation is underestimated in ICON and ERA5 and overestimated in MERRA-2, and the outgoing LW radiation is overestimated in all the models.
+In all the subsets (Fig.~\ref{fig:cloud-occurrence}b–g), the same type of biases are observed, namely the outgoing SW radiation is underestimated in ICON and ERA5 and overestimated in MERRA-2, and the outgoing LW radiation is overestimated in all the models.
 Even though the total cloud fraction is higher by 6\% over the high-latitude SO than the low-latitude SO, the outgoing SW radiation is much greater by 41~Wm$^{-2}$, implying a much greater cloud albedo (of cloudy areas) over the high-latitude SO.
@@
 They also underestimate the highly reflective situations above 200 Wm$^{-2}$.
-MERRA-2 exhibits the too few, too bright problem in terms of overestimating SW reflectivity around 290 Wm$^{-2}$, given that the total cloud fraction in MERRA-2 is strongly underestimated.
+MERRA-2 exhibits the too-few-too-bright problem in terms of overestimating SW reflectivity around 290 Wm$^{-2}$, given that the total cloud fraction in MERRA-2 is strongly underestimated.
 The LW distribution shows that all of the models overestimate outgoing LW (Fig.~\ref{fig:stats-hist-rad}b), which is expected from the underestimated cloud fraction, exposing more of the warmer ocean surface relative to colder clouds.
 
-Fig.~\ref{fig:stats-hist-si} shows liquid water path (LWP) and ice water path (IWP) distributions as histograms and their corresponding averages.
-LWP and IWP are calculated from the mass of water in the column divided by the area of the column, i.e., not just the area of the cloudy portion of the column, as in some definitions.
-The available observational satellite reference for LWP and IWP over high latitudes is unfortunately very uncertain due to a high solar zenith angle and the inability of passive visible and infrared retrievals to detect phase below the cloud top of mixed-phase clouds \cite{huang2006,greenwald2009,seethala2010,eliasson2011,duncan2018,khanal2020}, and this limits our comparison.
-The LWP distribution shows that all models overestimate cases with near-zero LWP (Fig.~\ref{fig:stats-hist-si}a), which relates to the underestimated total cloud fraction.
-MERRA-2 shows quite overestimated high-LWP situations, which is most likely related to the too few, too bright problem of simulating lower total cloud fraction but clouds with higher LWP to compensate.
-IWP (Fig.~\ref{fig:stats-hist-si}b) is somewhat less important radiatively than LWP because of the typically larger and less numerous hydrometeors.
-Similarly to LWP, the models overestimate situations with near-zero IWP.
-ERA5 is otherwise simulating the IWP distribution well, but ICON and MERRA-2 underestimate IWP.
-In the cloudy situations (Fig.~\ref{fig:stats-hist-si}c, d), it can be seen more distinctly that MERRA-2 overestimates moderate (0.05--0.15 kg m$^{-2}$) and high LWP (over 0.15 kg m$^{-2}$), and ERA5 and ICON underestimate moderate LWP.
+Fig.~\ref{fig:stats-hist-si} shows the LWP and IWP distributions as histograms and their corresponding averages.
+The LWP and IWP are calculated from the mass of water in the column divided by the area of the column, i.e., not just the area of the cloudy portion of the column, as in some definitions.
+The available observational satellite reference for the LWP and IWP over high latitudes is unfortunately very uncertain due to a high solar zenith angle and the inability of passive visible and infrared retrievals to detect phase below the cloud top of mixed-phase clouds \cite{huang2006,greenwald2009,seethala2010,eliasson2011,duncan2018,khanal2020}, and this limits our comparison.
+The LWP distribution shows that all models overestimate cases with a near-zero LWP (Fig.~\ref{fig:stats-hist-si}a), which relates to the underestimated total cloud fraction.
+MERRA-2 shows quite overestimated high-LWP situations, which is most likely related to the too-few-too-bright problem of simulating lower total cloud fraction but clouds with a higher LWP to compensate.
+The IWP (Fig.~\ref{fig:stats-hist-si}b) is somewhat less important radiatively than LWP because of the typically larger and less numerous hydrometeors.
+Similarly to the LWP, the models overestimate situations with a near-zero IWP.
+ERA5 is otherwise simulating the IWP distribution well, but ICON and MERRA-2 underestimate the IWP.
+In the cloudy situations (Fig.~\ref{fig:stats-hist-si}c, d), it can be seen more distinctly that MERRA-2 overestimates moderate (0.05–0.15 kg m$^{-2}$) and high LWP (over 0.15 kg m$^{-2}$), and ERA5 and ICON underestimate moderate LWP.
 ICON also overestimates high LWP, resulting in overestimated average LWP.
@@
 The solid lines are the average calculated from the averages of every individual voyage and station.
-The bands span the 16$^\mathrm{th}$--84$^\mathrm{th}$ percentiles, calculated from the distribution of the voyage and station averages.
+The bands span the 16$^\mathrm{th}$–84$^\mathrm{th}$ percentiles, calculated from the distribution of the voyage and station averages.
 Shown is also the relative frequency of occurrence and the number of profiles in each subset.
@@
 Overall, the mean $\theta_v$ is accurate to within 0.5~K in ICON and MERRA-2, except for ICON being colder by up to 2.5~K in the mid-to-high troposphere (less stable) (Fig.~\ref{fig:potential-temperature}a).
-Larger differences exist, however, in the 40--55°S zone, where ICON is colder by about 5 K at 5~km (Fig.~\ref{fig:potential-temperature}b).
+Larger differences exist, however, in the 40–55°S zone, where ICON is colder by about 5 K at 5~km (Fig.~\ref{fig:potential-temperature}b).
 In other subsets, the bias is relatively small.
@@
 RH displays much larger biases.
-In all subsets, ICON is too humid in the first 1~km by about 5\%, but very accurate above, except for the 40--55°S zone and conditions of weak stability (Fig.~\ref{fig:potential-temperature}b, g), where it is too dry between about 1 and 3~km.
+In all subsets, ICON is too humid in the first 1~km by about 5\%, but very accurate above, except for the 40–55°S zone and conditions of weak stability (Fig.~\ref{fig:potential-temperature}b, g), where it is too dry between about 1 and 3~km.
 Even though RH measured by radiosondes in the first 100~m is not very different between the observations and the models (Fig.~\ref{fig:potential-temperature}a), near-surface (2-m) RH at the radiosonde launch locations is much greater in the observations, most often close to 100\%, unlike in the models, where 85\% tends to be the most common (Fig.~\ref{fig:stats-hist-surf}b).
@@
 We can see several notable features.
-The models simulate progressively fewer high-RH (\textgreater 90\%) bins above the ground (Fig.~\ref{fig:rs-hur-hist}b--d).
+The models simulate progressively fewer high-RH (\textgreater 90\%) bins above the ground (Fig.~\ref{fig:rs-hur-hist}b–d).
 This can be related to either ice nucleation happening in the models, which requires smaller RH for saturation, or the grid cell size in the models, which requires lower grid cell average RH than 100\% for saturation to occur in a fraction of the grid cell.
-The models also tend to simulate more clear bins than observations for RH between 80 and 100\% between the ground and about 1 km (Fig.~\ref{fig:rs-hur-hist}f--h).
+The models also tend to simulate more clear bins than observations for RH between 80 and 100\% between the ground and about 1 km (Fig.~\ref{fig:rs-hur-hist}f–h).
 In the observations, these values of RH are associated with cloudy bins (Fig.~\ref{fig:rs-hur-hist}i).
-Conversely, the models predominantly associate only RH very close to 100\% with cloudy bins at these heights (Fig.~\ref{fig:rs-hur-hist}j--l).
+Conversely, the models predominantly associate only RH very close to 100\% with cloudy bins at these heights (Fig.~\ref{fig:rs-hur-hist}j–l).
 This may be one of the main reasons for the identified cloud or fog biases near the ground.
@@
 This is indicative of convection being associated with clouds at these heights, which results in flat $\theta_v$ profiles.
-In the reanalyses, in the first 200 m, values slightly above 0°C are associated with more clear bins than in observations, and values slightly below 0°C with fewer (Fig.~\ref{fig:rs-thetav-hist}g--h).
-Conversely, the opposite is true for cloudy bins (Fig.~\ref{fig:rs-thetav-hist}k--l).
+In the reanalyses, in the first 200 m, values slightly above 0°C are associated with more clear bins than in observations, and values slightly below 0°C with fewer (Fig.~\ref{fig:rs-thetav-hist}g–h).
+Conversely, the opposite is true for cloudy bins (Fig.~\ref{fig:rs-thetav-hist}k–l).
 Situations with 0°C near-surface air temperature might occur predominantly when an open ocean surface keeps the near-surface air temperature close to 0°C under otherwise colder air mass conditions, such as under cold advection.
@@
 Supercooled liquid clouds (liquid clouds under subzero temperature) commonly occur over the SO.
-In our analysis of LWP and IWP, we see that both phases are abundant.
+In our analysis of the LWP and IWP, we see that both phases are abundant.
 Because liquid water droplets are typically smaller and more numerous than ice crystals in cold clouds, they attenuate a greater amount of the lidar radiation.
@@
 Vertical averaging of the radiosonde data can result in lower RH near saturation due to averaging of drier and moister layers together.
-For example, some of the RV \textit{Polarstern} radiosondes are available in vertical resolution of about 20--30 m.
-As mentioned in Section~\ref{sec:rad-lwp-iwp}, the satellite retrieval of LWP and IWP is affected by large biases, especially over high latitudes, which limits our comparison with the models.
+For example, some of the RV \textit{Polarstern} radiosondes are available in vertical resolution of about 20–30 m.
+As mentioned in Section~\ref{sec:rad-lwp-iwp}, the satellite retrieval of the LWP and IWP is affected by large biases, especially over high latitudes, which limits our comparison with the models.
 
@@
 \citeA{ramadoss2024} have shown that in precipitating conditions, km-scale ICON has SW radiative biases associated with the overrepresentation of the liquid phase at the cloud top in low stratocumulus clouds in a short (48-h) simulation over the SO.
-\citeA{fiddes2024} suggested that biases in the liquid water path are the largest contributor to the cloud radiative bias over the SO.
-Our general finding applies to the new GSRM ICON, but the biases are lower than in the reanalyses in several aspects, namely the total cloud fraction, daily cloud cover, fog, and LWP (Table~\ref{tab:summary}), despite the reanalyses having the advantage of assimilation of the observed meteorological conditions.
-ICON, on the other hand, performs worse than the reanalyses in clouds and RH at 500 m, mid-level clouds (here defined as 1.5 km), outgoing SW radiation, and IWP.
+\citeA{fiddes2024} suggested that biases in the LWP are the largest contributor to the cloud radiative bias over the SO.
+Our general finding applies to the new GSRM ICON, but the biases are lower than in the reanalyses in several aspects, namely the total cloud fraction, daily cloud cover, fog, and the LWP (Table~\ref{tab:summary}), despite the reanalyses having the advantage of assimilation of the observed meteorological conditions.
+ICON, on the other hand, performs worse than the reanalyses in clouds and RH at 500 m, mid-level clouds (here defined as 1.5 km), outgoing SW radiation, and the IWP.
 ICON has the advantage of a much higher spatial resolution and, to a limited extent, explicit calculation of traditionally subgrid-scale processes such as convection.
@@
 The latter is also manifested in the radiosonde profile comparison (Fig.~\ref{fig:rs-lts-hist}), showing that the $\theta_v$ profiles in ICON are less stable than in the observations over low-latitude SO.
-It is also manifested in near-surface air temperature, which is overestimated in the 1--7°C range at the radiosonde launch locations (Fig.~\ref{fig:stats-hist-surf}a).
-The underestimated LTS is linked to the overestimated cloud peak at 500 m in the lidar cloud occurrence comparison (Fig~\ref{fig:cloud-occurrence}f--g).
+It is also manifested in near-surface air temperature, which is overestimated in the 1–7°C range at the radiosonde launch locations (Fig.~\ref{fig:stats-hist-surf}a).
+The underestimated LTS is linked to the overestimated cloud peak at 500 m in the lidar cloud occurrence comparison (Fig~\ref{fig:cloud-occurrence}f–g).
 It might also be interacting with the cloud inhomogeneity factor employed in ICON (Section~\ref{sec:icon}), resulting in lower cloud liquid water used in radiative calculations, hence decreased outgoing SW radiation.
@@
 Notably, ICON exhibits smaller internal variability in $\theta_v$ than the radiosonde observations.
-The analysis of LWP and IWP (Fig.~\ref{fig:stats-hist-si}) shows that both phases are present in observations in about equal amounts.
-The models show diverse biases, the most pronounced being overestimation of high-LWP values in MERRA-2 and overestimation of cases with near-zero LWP and IWP in all models.
-All models tend to compensate for the overestimated cases of near-zero LWP with more high-LWP values to get a mean LWP that is either less (but close) to the observations (ERA5) or higher than the observations (ICON and MERRA-2).
-IWP is underestimated in all of the models.
+The analysis of the LWP and IWP (Fig.~\ref{fig:stats-hist-si}) shows that both phases are present in observations in about equal amounts.
+The models show diverse biases, the most pronounced being overestimation of high-LWP values in MERRA-2 and overestimation of cases with a near-zero LWP and IWP in all models.
+All models tend to compensate for the overestimated cases of a near-zero LWP with more high-LWP values to get a mean LWP that is either less (but close) to the observations (ERA5) or higher than the observations (ICON and MERRA-2).
+The IWP is underestimated in all of the models.
 In the case of ICON and MERRA-2, the mean IWP was underestimated and LWP overestimated, indicating that the models produce too much liquid and not enough ice phase.
@@
 We suggest the following avenues for future research.
-Evaluation of ocean--atmosphere heat, moisture, and momentum fluxes with in-situ observations over the SO and comparison of GSRM simulations with large-eddy simulations in process-oriented studies; evaluation of the DYAMOND project simulations in a similar manner as performed here (for models that provide the necessary fields); and combining active satellite sensors such as the Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observations (CALIOP) on CALIPSO and Atmospheric Lidar [ATLID; \citeA{heliere2017}] on the Earth Clouds, Aerosols and Radiation Explorer [EarthCARE; \citeA{illingworth2015}] satellite with ground-based remote sensing could provide a more complete understanding of the cloud biases across the whole troposphere.
+Evaluation of ocean–atmosphere heat, moisture, and momentum fluxes with in-situ observations over the SO and comparison of GSRM simulations with large-eddy simulations in process-oriented studies; evaluation of the DYAMOND project simulations in a similar manner as performed here (for models that provide the necessary fields); and combining active satellite sensors such as the Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observations (CALIOP) on CALIPSO and Atmospheric Lidar [ATLID; \citeA{heliere2017}] on the Earth Clouds, Aerosols and Radiation Explorer [EarthCARE; \citeA{illingworth2015}] satellite with ground-based remote sensing could provide a more complete understanding of the cloud biases across the whole troposphere.
 Cloud phase could be analyzed in more detail using the CALIPSO data, as was done by \citeA{roh2020} in a cloud-resolving model, or using ground-based observations with the dual-polarization Mini Micro Pulse Lidar [MiniMPL; \citeA{spinhirne1993,campbell2002,flynn2007}] data available from the TAN1802 voyage.

### 2025-07-21 manuscript_agu_rev1.tex
Fix grammar

@@
 The SO is dominated by low clouds, which cannot be observed accurately from space due to overlapping clouds, attenuation, and ground clutter.
-We evaluated SO clouds in ICON and the ERA5 and MERRA-2 reanalyses using approximately 2400 days of lidar observations and 2300 radiosonde profiles from 31 voyages and Macquarie Island station during 2010–2021, compared with the models using a ground-based lidar simulator.
+We evaluated SO clouds in ICON and the ERA5 and MERRA-2 reanalyses using approximately 2400 days of lidar observations and 2300 radiosonde profiles from 31 voyages and a Macquarie Island station during 2010–2021, compared to the models using a ground-based lidar simulator.
 We found that ICON and the reanalyses underestimate the total cloud fraction by about 10 and 20\%, respectively.
@@
 We found that ICON and reanalyses underestimate lidar-derived cloud fraction, and the reanalyses do so more strongly.
-Fog or very low-level clouds are especially underestimated in the reanalyses.
+Fog and very low-level clouds are especially underestimated in the reanalyses.
 However, ICON and one of the reanalyses also tend to overestimate the peak of cloud occurrence at 500 m above the ground, and it tends to be higher.
@@
 This region is mostly dominated by boundary layer clouds generated by shallow convection, and these are problematic to observe by spaceborne lidars and radars, which are affected by attenuation by overlapping and thick clouds \cite{mace2009,medeiros2010} and ground clutter \cite{marchand2008}, respectively.
-Specifically, the radar on CloudSat and lidar on the Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observation (CALIPSO), neither of which are now operational, are affected by the above-mentioned issues, resulting in a strong underestimation of cloud occurrence below 2 km in a merged CloudSat–CALIPSO product relative to ground-based lidar observations at McMurdo Station \cite{mcerlich2021}.
+Specifically, the radar on CloudSat and lidar on the Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observation (CALIPSO), neither of which are operational any more, are affected by the above-mentioned issues, resulting in a strong underestimation of cloud occurrence below 2 km in a merged CloudSat–CALIPSO product relative to ground-based lidar observations at McMurdo Station \cite{mcerlich2021}.
 Removing situations with higher overlapping clouds could enable a less biased comparison of low clouds.
@@
 This makes them a problematic reference for clouds over the SO, and any biases relative to a reanalysis should be interpreted with caution.
-Instead, we chose to use a large set of ship-based observations conducted with ceilometers and lidars on board the research vessel (RV) \emph{Polarstern} and other voyages and a station as a reference for the model evaluation.
-Altogether, we analyzed approximately 2400 days of data from 31 voyages and one sub-Antarctic station covering diverse longitudes and latitudes of the SO.
+Instead, we chose to use a large set of ship-based observations conducted with ceilometers and lidars on board the research vessel (RV) \emph{Polarstern} and other ships and a station as a reference for the model evaluation.
+Altogether, we analyzed approximately 2400 days of data from 31 voyages and a sub-Antarctic station covering diverse longitudes and latitudes of the SO.
 To achieve a like-for-like comparison with the models (ICON, MERRA-2, and ERA5), we used a ground-based lidar simulator called the Automatic Lidar and Ceilometer Framework [ALCF; \citeA{kuma2021}].
@@
 
-Some of the observational data were likely used in reanalysis assimilation.
+Some of the observational data were likely used in the assimilation of the reanalyses.
 The Macquarie Island station surface measurements and radiosonde profiles (not used in our analysis) were sent to the World Meteorological Organization Global Telecommunication System (GTS).
@@
 The wavelengths of 905 and 910~nm are both affected by water vapor absorption of about 20\% in the mid-latitudes \cite{wiegner2015,wiegner2019}, with 910~nm affected more strongly, but we do not expect this to be a significant issue, as explained in \citeA{kuma2021}.
-The instrument data files containing raw uncalibrated backscatter were first converted to Network Common Data Form (NetCDF) with cl2nc \cite{kuma2024a} and then processed with the ALCF (Section~\ref{sec:alcf}) to produce absolutely calibrated attenuated volume backscattering coefficient (AVBC), cloud mask, cloud occurrence by height, and the total cloud fraction.
+The instrument data files containing raw uncalibrated backscatter were first converted to the Network Common Data Form (NetCDF) with cl2nc \cite{kuma2024a} and then processed with the ALCF (Section~\ref{sec:alcf}) to produce absolutely calibrated attenuated volume backscattering coefficient (AVBC), cloud mask, cloud occurrence by height, and the total cloud fraction.
 Because the CT25K uses a very similar wavelength to the CL51, equivalent calculations as for the CL51 were done assuming a wavelength of 910~nm.
@@
 The maximum range is 15.4~km; the vertical resolution is 5~m in the near range (up to 150~m) and 15~m above; the sampling (temporal) resolution is 2~s; and the number of vertical levels is 1024.
-NetCDF files containing uncalibrated backscatter produced by the instrument were processed with the ALCF (Section~\ref{sec:alcf}) to again produce AVBC, cloud mask, cloud occurrence by height, and the total cloud fraction.
+NetCDF files containing uncalibrated backscatter produced by the instrument were processed with the ALCF (Section~\ref{sec:alcf}) to produce AVBC, cloud mask, cloud occurrence by height, and the total cloud fraction.
 The CHM~15k was used on four voyages (HMNZSW16, TAN1702, TAN1802, and NBP1704).
@@
 The total cloud fraction is defined as the fraction of profiles with clouds at any height in the lidar cloud mask.
-The ALCF has been used by several research teams for model and reanalysis evaluation \cite{kuma2020,kremser2021,guyot2022,pei2023,whitehead2023,mcdonald2024a}.
+The ALCF has in the past been used by several research teams for model and reanalysis evaluation \cite{kuma2020,kremser2021,guyot2022,pei2023,whitehead2023,mcdonald2024a}.
 
@@
 How attenuation of the lidar signal affects cloud detection is dependent on factors such as the optical thickness of the measured cloud and its backscattering phase function, as well as the range-dependent noise standard deviation \cite{kuma2021}.
-A rough estimate can be made under an assumption of a relatively strongly backscattering cloud of $\beta = \mathrm{100\times 10^{-6} m^{-1}sr^{-1}}$ at a height of $r_1$ = 2 km, range-dependent noise $\beta_n$ at $r_2$ = 8 km of about $\mathrm{5\times 10^{-6} m^{-1}sr^{-1}}$, and cloud detection threshold $\beta_t = \mathrm{2\times 10^{-6} m^{-1}sr^{-1}}$, noise multiplication factor $f$ = 5, at full attenuation the two-way attenuation factor $A$ satisfies $A\beta = \beta_t + f\times \beta_n\left(\frac{r_1}{r_2}\right)^2$, which is equivalent to exponential decay ($A = e^{-2\delta}$) with optical depth $\delta$ (at the lidar wavelength) of about 1.7.
+A rough estimate can be made under an assumption of a relatively strongly backscattering cloud of $\beta = \mathrm{100\times 10^{-6} m^{-1}sr^{-1}}$ at a height of $r_1$ = 2 km, range-dependent noise $\beta_n$ at $r_2$ = 8 km of about $\mathrm{5\times 10^{-6} m^{-1}sr^{-1}}$, and cloud detection threshold $\beta_t = \mathrm{2\times 10^{-6} m^{-1}sr^{-1}}$, noise multiplication factor $f$ = 5.
+At full attenuation (relative to the detection threshold), the two-way attenuation factor $A$ satisfies $A\beta = \beta_t + f\times \beta_n\left(\frac{r_1}{r_2}\right)^2$.
+This is equivalent to exponential decay ($A = e^{-2\delta}$) with optical depth $\delta$ (at the lidar wavelength) of about 1.7.
 
@@
 
-We analyzed a total of about 2400 days of lidar and 2300 radiosonde observations from 31 campaigns and the Macquarie Island subantarctic station, covering the Atlantic, Australian, and New Zealand sectors of the SO over 10 years.
+We analyzed a total of about 2400 days of lidar and 2300 radiosonde observations from 31 campaigns and the Macquarie Island sub-Antarctic station, covering the Atlantic, Australian, and New Zealand sectors of the SO over 10 years.
 This dataset, together with the use of a ground-based lidar simulator, provided a comprehensive basis for evaluating SO cloud and thermodynamic profile biases in the GSRM ICON and the ERA5 and MERRA-2 reanalyses.

### 2025-07-21 manuscript_agu_rev1.tex
Small fixes

@@
 To compare with the observations collected during a different time period (years 2010–2021, inclusive), we compared the model output with observations at the same time of year and geographical location, as determined for each data point, such as a lidar profile or a radiosonde launch.
-In the ALCF, this was done using the \emph{override\_year} option (\url{https://alcf.peterkuma.net/documentation/cli/cmd_model.html}).
-For radiosonde profiles, the same mapping of time was done.
-That is, when selecting an equivalent profile from the model, the time of the profile was changed so that the time relative to the start of the year was preserved, but the year was changed to one of the four years available in the model data.
-Thus, for every radiosonde launch, there were four equivalent model profiles.
-The geographical location was kept the same.
+In the ALCF, this was done using the \emph{override\_year} option.
 
@@
 It is based on an NWP model IFS version CY41R2.
-It uses the \citeA{tiedtke1993} prognostic cloud scheme and \citeA{forbes2014} for mixed-phase clouds.
+It uses the \citeA{tiedtke1993} prognostic cloud scheme and the \citeA{forbes2014} scheme for mixed-phase clouds.
 The horizontal resolution is 0.25° in latitude and longitude, which is about 28~km in the north–south direction and 14~km in the east–west direction at 60°S.
@@
 Here, we use output at 1-hourly instantaneous time intervals, except for radiation quantities, which are accumulations (from these we calculate daily means).
-Vertically resolved quantities are made available on 37 pressure levels.
+Vertically resolved quantities are available on 37 pressure levels.
 
@@
 In the observed lidar data, the daily mean values were taken from the spatially and temporally co-located CERES SYN1deg data for the day (in UTC).
-The voyage or station average was calculated in the same way.
+The voyage and station averages were calculated in the same way.
 
@@
 \caption{Summary of the main biases.
-Values are relative to observations and rounded to the nearest 5, except for daily cloud cover and RH, which are rounded to the nearest integer.
+Values are relative to observations and rounded to the nearest multiple of 5, except for daily cloud cover and RH, which are rounded to the nearest integer.
 The best-performing value is marked in \textbf{bold}.
@@
 We did not, however, analyze the cloud phase based on ground-based observations.
-Cloud phase can have a strong impact on the SW radiative transfer due to larger and therefore less numerous hydrometeors (for the same amount of water) scattering much less SW radiation.
-Especially, the underestimation of fog or very low-level clouds is very substantial in the reanalyses, and we showed that this relates to cloud formation or persistence at RH between 80 and 100\% in the boundary layer in the observations, while in models RH values less than 100\% are associated with clear bins.
+Cloud phase can have a strong impact on the SW radiative transfer due to larger and therefore less numerous hydrometeors in cold and mixed-phase clouds (for the same amount of water), scattering much less SW radiation.
+Especially, the underestimation of fog or very low-level clouds is very substantial in the reanalyses, and we showed that this relates to cloud and fog formation or persistence at RH between 80 and 100\% in the boundary layer in the observations, while in models RH values less than 100\% are associated with clear bins.
 We subset the dataset by low and high latitude SO bands, cyclonic activity, and stability in order to identify how these conditions influence the biases.
@@
 We show that relative to ERA5, the distribution and strength of cyclonic activity over the SO is well represented in ICON, but it displays lower values of LTS.
-The latter is also manifested in the radiosonde profile comparison (Fig.~\ref{fig:rs-lts-hist}), showing that the $\theta_v$ profiles in ICON are less stable than in the observations over low-latitude SO.
+The latter is also manifested in the radiosonde profile comparison (Fig.~\ref{fig:rs-lts-hist}), showing that the $\theta_v$ profiles in ICON are less stable than in the observations.
 It is also manifested in near-surface air temperature, which is overestimated in the 1–7°C range at the radiosonde launch locations (Fig.~\ref{fig:stats-hist-surf}a).

### 2025-07-21 si_rev1.tex
Small fixes
Various submission-related changes

@@
 \documentclass[draft,jgrga]{agutexSI2019}
-
-\usepackage{xr}
-\externaldocument{manuscript_agu_rev1}
 
@@
 
-\title{Supporting Information for "Ship-based lidar evaluation of Southern Ocean low clouds in the storm-resolving general circulation model ICON, and the ERA5 and MERRA-2 reanalyses"}
+\title{Supporting Information for "Ship-based lidar evaluation of Southern Ocean low clouds in the storm-resolving general circulation model ICON and the ERA5 and MERRA-2 reanalyses"}
 
@@
 \begin{figure}[p!]
+\includegraphics[width=\textwidth]{img/stats_hist_surf.pdf}
+\caption{
+Histograms of near-surface \textbf{(a)} air temperature and \textbf{(b)} relative humidity at radiosonde launch locations in the observations and the corresponding locations and times in the models.
+Only locations south of 40°S are included.
+}
+\label{fig:stats-hist-surf}
+\end{figure}
+
+\begin{figure}[p!]
 \centerline{
@@
 \label{fig:cloud-occurrence-panel}
-\end{figure}
-
-\begin{figure}[p!]
-\includegraphics[width=\textwidth]{img/stats_hist_surf.pdf}
-\caption{
-Histograms of near-surface \textbf{(a)} air temperature and \textbf{(b)} relative humidity at radiosonde launch locations in the observations and the corresponding locations and times in the models.
-Only locations south of 40°S are included.
-}
-\label{fig:stats-hist-surf}
 \end{figure}
@@
 \caption{
-The same as Fig.~\ref{fig:potential-temperature}, but only for profiles that contain \textbf{(a)} fog, \textbf{(b)} cloud at 500~m, and \textbf{(c)} cloud at 1.5~km.
+The same as Fig.~9, but only for profiles that contain \textbf{(a)} fog, \textbf{(b)} cloud at 500~m, and \textbf{(c)} cloud at 1.5~km.
 }
@@
 \caption{
-The same as Fig.~\ref{fig:rs-hur-hist}, but for virtual potential temperature.
+The same as Fig.~11, but for virtual potential temperature.
 }

### 2025-07-23 manuscript.tex
Rename manuscript

@@
-% Related publications:
-%
-% Takasuka et al. (2024), A protocol and analysis of year-long simulations of global storm-resolving models and beyond
-% Knight et al. (2024), Cloud properties and boundary layer stability above Southern Ocean sea ice and coastal Antarctica
-% Zheng et al. (2024), Using Satellite and ARM Observations to Evaluate Cold Air Outbreak Cloud Transitions in E3SM Global Storm-Resolving Simulations
-% Schmidt et al. (2024), Effects of vertical grid spacing on the climate simulated in the ICON-Sapphire global storm-resolving model
-% Fons et al. (2024), Investigating the sign of stratocumulus adjustments to aerosols in the global storm-resolving model ICON
-% Fiddes et al. (2024), A machine learning approach for evaluating Southern Ocean cloud radiative biases in a global atmosphere model
-% Mooers et al. (2023), Comparing storm resolving models and climates via unsupervised machine learning
-% Zhang et al. (2023), Understanding models' global sea surface temperature bias in mean state: from CMIP5 to CMIP6
-% Grundner (2023), Data-Driven Cloud Cover Parameterizations for the ICON Earth System Model Using Deep Learning and Symbolic Regression [thesis]
-% Luo et al. (2023), Origins of Southern Ocean warm sea surface temperature bias in CMIP6 models
-% Sherriff-Tadano et al. (2023), Southern Ocean Surface Temperatures and Cloud Biases in Climate Models Connected to the Representation of Glacial Deep Ocean Circulation
-% Danker et al. (2022), Exploring relations between cloud morphology, cloud phase, and cloud radiative properties in Southern Ocean's stratocumulus clouds
-% Possner et al. (2022), Resolution Dependence of Southern Ocean Mixed-Phase Clouds in ICON
-% Mauritsen et al. (2022), Early Development and Tuning of a Global Coupled Cloud Resolving Model, and its Fast Response to Increasing CO2
-% Wall et al. (2022), Observational Constraints on Southern Ocean Cloud-Phase Feedback
-% Grundner et al. (2022), Deep learning based cloud cover parameterization for ICON
-% Cesana et al. (2022), Southern Ocean Solar Reflection Biases in CMIP6 Models Linked to Cloud Phase and Vertical Structure Representations
-% Fiddes et al. (2022), Southern Ocean cloud and shortwave radiation biases in a nudged climate model simulation: does the model ever get it right?
-% Zhao et al. (2022), Compensating Errors in Cloud Radiative and Physical Properties over the Southern Ocean in the CMIP6 Climate Models
-% Konsta et al. (2022), Low-Level Marine Tropical Clouds in Six CMIP6 Models Are Too Few, Too Bright but Also Too Compact and Too Homogeneous
-% Lin and Yu (2022), The potential impact of model horizontal resolution on the simulation of atmospheric cloud radiative effect in CMIP6 models
-% Ramadoss et al. (2021), An evaluation of kilometre scale ICON simulations of mixed-phase stratocumulus over the Southern Ocean durin CAPRICORN [poster]
-% Miao et al. (2021), A Regime-based Investigation into the Errors of CMIP6 Simulated Cloud Radiative Effects Using Satellite Observations
-% Roh et al. (2021), Intercomparison of cloud properties in DYAMOND simulations over the Atlantic Ocean
-% Caldwell et al. (2021), Convection-Permitting Simulations With the E3SM Global Atmosphere Model
-% Schuddeboom and McDonald (2021), The Southern Ocean Radiative Bias, Cloud Compensating Errors, and Equilibrium Climate Sensitivity in CMIP6 Models
-% Ramadoss et al. (2020), Simulating mixed-phase cloud properties with ICON around the CAPRICORN field campaign at the kilometre scale [poster]
-% Heim et al. (2021), Inter-model Variability in Convection-Resolving Simulations of Subtropical Marine Low Clouds
-% Seiki and Roh (2020), Improvements in Supercooled Liquid Water Simulations of Low-Level Mixed-Phase Clouds over the Southern Ocean Using a Single-Column Model
-% Stevens et al. (2020), The added value of large-eddy and storm-resolving models for simulating clouds and precipitation
-% Atlas et al. (2020), How well do large‐eddy simulations and global climate models represent observed boundary layer structures and low clouds over the summertime Southern Ocean?
-% Korn et al. (2020), ICON‐O: The Ocean Component of the ICON Earth System Model—Global Simulation Characteristics and Local Telescoping Capability
-% Vignesh et al. (2020), Assessment of CMIP6 Cloud Fraction and Comparison with Satellite Observations
-% Chen et al. (2022), Evaluation of Simulated Cloud Diurnal Variation in CMIP6 Climate Models
-% Jian et al. (2020), Evaluation of the CMIP6 planetary albedo climatology using satellite observations
-% Satoh et al. (2019), Global Cloud-Resolving Models
-% Hyder et al. (2018), Critical Southern Ocean climate model biases traced to atmospheric model cloud errors
+\documentclass[draft]{agujournal2019}
+\usepackage{url} %this package should fix any errors with URLs in refs.
+\usepackage{lineno}
+%\usepackage[inline]{trackchanges} %for better track changes. finalnew option will compile document with changes incorporated.
+\usepackage{soul}
+\linenumbers
 
-\documentclass[12pt,a4paper]{article}
-\usepackage{fontspec}
-\usepackage{microtype}
-\usepackage[margin=2cm]{geometry}
-\usepackage[citecolor=black]{hyperref}
-\usepackage[authoryear,round]{natbib}
-\usepackage{doi}
-\usepackage{titlesec}
-\usepackage{caption}
-\DeclareCaptionLabelSeparator{pipe}{ | }
-\captionsetup{labelfont={bf,sf},labelsep=pipe}
-\usepackage{graphicx}
-\usepackage{lineno}
-\linenumbers
-\setsansfont{Source Sans Pro}
-\setmainfont{EB Garamond}
-\setmonofont[Scale=0.8]{SpaceMono}[
-	Path=./fonts/,
-	Extension=.ttf,
-	UprightFont=*-Regular,
-	BoldFont=*-Bold,
-	ItalicFont=*-Italic,
-	BoldItalicFont=*-BoldItalic
-]
-\hypersetup{
-	colorlinks=true,
-	urlcolor=blue,
-	pdftitle={Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON, and the ERA5 and MERRA-2 reanalyses},
-	pdfauthor={Peter Kuma, Frida A.-M.
-Bender, Adrian J.
-McDonald, Simon P.
-Alexander, Greg M.
-McFarquhar, John J.
-Cassano, Graeme E.
-Plank, Sean Hartery, Simon Parsons, Sally Garrett, and Alex J.
-Schuddeboom}
-}
-\bibliographystyle{abbrvnat}
-\titleformat*{\section}{\large\bfseries\sffamily}
-\titleformat*{\subsection}{\normalsize\bfseries\sffamily}
-\titlespacing*{\section}{0pt}{14pt}{6pt}
-\titlespacing*{\subsection}{0pt}{13pt}{4pt}
-\parskip=6pt
-\parindent=0pt
+\draftfalse
+
+\journalname{JGR: Atmospheres}
 
@@
 
-\fontsize{13pt}{15pt}\selectfont
+\title{Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON, and the ERA5 and MERRA-2 reanalyses}
 
-\begin{center} \Large \sffamily\textbf{Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON and the ERA5 and MERRA-2 reanalyses}\\[0.4cm]
-\normalsize Peter Kuma$^\mathsf{1,2,\star}$, Frida A.-M.
-Bender$^\mathsf{1,2}$, Adrian J.
-McDonald$^\mathsf{3}$, Simon P.
-Alexander$^\mathsf{4,5}$, Greg M.
-McFarquhar$^\mathsf{6,7}$, John J.
-Cassano$^\mathsf{8,9,10}$, Graeme E.
-Plank$^\mathsf{3}$, Sean Hartery$^\mathsf{11}$, Simon Parsons$^\mathsf{12}$, Sally Garrett$^\mathsf{13}$, and Alex J.
-Schuddeboom$^\mathsf{3}$\\[0.4cm]
-\footnotesize
-$^\mathsf{1}$Department of Meteorology (MISU), Stockholm University, Stockholm, Sweden\\
-$^\mathsf{2}$Bolin Centre for Climate Research, Stockholm University, Stockholm, Sweden\\
-$^\mathsf{3}$School of Physical and Chemical Sciences, University of Canterbury, Christchurch, Aotearoa/New Zealand\\
-$^\mathsf{4}$Australian Antarctic Division, Kingston, Tasmania, Australia\\
-$^\mathsf{5}$Australian Antarctic Program Partnership, Institute for Marine and Antarctic Studies, University of Tasmania, Hobart, Tasmania, Australia\\
-$^\mathsf{6}$Cooperative Institute of Severe and High Impact Weather Research and Operations, University of Oklahoma, Norman, OK, USA\\
-$^\mathsf{7}$School of Meteorology, University of Oklahoma, Norman, OK, USA\\
-$^\mathsf{8}$Cooperative Institute for Research in Environmental Sciences, University of Colorado, Boulder, CO, USA\\
-$^\mathsf{9}$National Snow and Ice Data Center, University of Colorado, Boulder, CO, USA\\
-$^\mathsf{10}$Department of Atmospheric and Oceanic Sciences, University of Colorado, Boulder, CO, USA\\[0.2cm]
-$^\mathsf{11}$Department of Physics \& Atmospheric Science, Dalhousie University, Halifax, Canada\\
-$^\mathsf{12}$New South Wales Department of Planning and Environment, Sydney, New South Wales, Australia\\
-$^\mathsf{13}$New Zealand Defence Force, Wellington, New Zealand\\
-$^\star$Corresponding author: Peter Kuma (\href{mailto:peter.kuma@misu.su.se}{peter.kuma@misu.su.se})\\[0.4cm]
-\normalsize \today\\[0.4cm]
+\authors{Peter Kuma\affil{1,2,3}\thanks{}, Frida A.-M.
+Bender\affil{1,2}, Adrian J.
+McDonald\affil{3}, Simon P.
+Alexander\affil{4,5}, Greg M.
+McFarquhar\affil{6,7}, John J.
+Cassano\affil{8,9,10}, Graeme E.
+Plank\affil{3}, Sean Hartery\affil{3}\thanks{Current affiliation: Department of Physics \& Atmospheric Science, Dalhousie University, Halifax, Canada}, Simon Parsons\affil{3}\thanks{Current affiliation: New South Wales Department of Planning and Environment, Sydney, New South Wales, Australia}, Sally Garrett\affil{11}, and Alex J.
+Schuddeboom\affil{3}}
 
-\end{center}
+\affiliation{1}{Department of Meteorology (MISU), Stockholm University, Stockholm, Sweden}
+\affiliation{2}{Bolin Centre for Climate Research, Stockholm University, Stockholm, Sweden}
+\affiliation{3}{School of Physical and Chemical Sciences, University of Canterbury, Christchurch, Aotearoa/New Zealand}
+\affiliation{4}{Australian Antarctic Division, Kingston, Tasmania, Australia}
+\affiliation{5}{Australian Antarctic Program Partnership, Institute for Marine and Antarctic Studies, University of Tasmania, Hobart, Tasmania, Australia}
+\affiliation{6}{Cooperative Institute of Severe and High Impact Weather Research and Operations, University of Oklahoma, Norman, OK, USA}
+\affiliation{7}{School of Meteorology, University of Oklahoma, Norman, OK, USA}
+\affiliation{8}{Cooperative Institute for Research in Environmental Sciences, University of Colorado, Boulder, CO, USA}
+\affiliation{9}{National Snow and Ice Data Center, University of Colorado, Boulder, CO, USA}
+\affiliation{10}{Department of Atmospheric and Oceanic Sciences, University of Colorado, Boulder, CO, USA}
+\affiliation{11}{New Zealand Defence Force, Wellington, Aotearoa/New Zealand}
 
-\section*{Abstract}
+\correspondingauthor{Peter Kuma}{peter@peterkuma.net}
 
-Global storm-resolving models (GSRMs) are the next avenue of climate modelling.
-Among them is a 5-km horizontal resolution version of the Icosahedral Nonhydrostatic Weather and
-Climate Model (ICON). This high resolution means that parameterizations of
-convection and clouds including subgrid-scale clouds are not required, though microphysics and turbulence
-parametrizations are still needed.  Standard-resolution (10--100-km) models, which use
-subgrid-scale convection and cloud parametrization, have substantial cloud
-biases over the Southern Ocean (SO), adversely affecting radiation and sea surface
-temperature.  We evaluated SO clouds in ICON and the ERA5 and MERRA-2
-reanalyses.  The SO is dominated by low clouds, which cannot be observed
-accurately from space due to overlapping clouds, attenuation, and ground
-clutter.  Instead, we analysed about 2400 days of lidar observations from 31
-voyages and a station during 2010--2021 using a ground-based lidar simulator.
-ICON and the reanalyses underestimate the total cloud fraction by about 10 and
-20\%, respectively. ICON and ERA5 overestimate the cloud occurrence peak at
-about 500 m, potentially explained by their lifting condensation levels being
-too high.  The reanalyses strongly underestimate near-surface clouds or fog.
-MERRA-2 tends to underestimate cloud occurrence at all heights.  In daily cloud
-cover, ICON and the reanalyses tend to be about 1 and 2 oktas clearer,
-respectively. The largest
-errors in ICON and the reanalyses occur during periods of weak stability.  Compared to radiosondes, potential
-temperature is accurate in the reanalyses to about 0.5 K, but ICON
-underestimates stability over the low-latitude SO and is too humid in the boundary
-layer. MERRA-2 is too humid at all heights. SO cloud biases remain a
-substantial issue in the GSRM, but are an improvement over the lower-resolution
-reanalyses. Explicitly resolved convection and cloud processes (except
-microphysics) were not enough to address the model cloud biases.
+\begin{keypoints}
+\item Ground-based lidar evaluation of a km-scale global climate model and reanalyses reveals substantial cloud biases over the Southern Ocean.
+\item Fog or low cloud is underestimated in the reanalyses. In all models, a cloud peak at 500~m tends to be overestimated and too high.
+\item A ``too few, too bright'' problem of underestimated cloud fraction, compensated by overestimated cloud albedo, is present in the reanalyses.
+\end{keypoints}
+
+\begin{abstract}
+Global storm-resolving models (GSRMs) are the latest generation of global climate models.
+One of them is a 5-km Icosahedral Nonhydrostatic Weather and Climate Model (ICON).
+Its high resolution means that parameterizations of convection and clouds, including subgrid-scale clouds, are omitted, relying on explicit simulation but still utilizing microphysics and turbulence parameterizations.
+Standard-resolution (10--100~km) models, which use convection and cloud parameterizations, have substantial cloud biases over the Southern Ocean (SO), adversely affecting radiation and sea surface temperature.
+The SO is dominated by low clouds, which cannot be observed accurately from space due to overlapping clouds, attenuation, and ground clutter.
+We evaluated SO clouds in ICON and the ERA5 and MERRA-2 reanalyses using about 2400 days of lidar observations and 2300 radiosonde profiles from 31 voyages and Macquarie Island station during 2010--2021, compared with the models using a ground-based lidar simulator.
+We found that ICON and the reanalyses underestimate the total cloud fraction by about 10 and 20\%, respectively.
+ICON and ERA5 overestimate the cloud occurrence peak at about 500 m, potentially explained by their lifting condensation levels being too high.
+The reanalyses strongly underestimate fog or near-surface clouds, and MERRA-2 underestimates cloud occurrence at almost all heights.
+Outgoing shortwave radiation is overestimated in the reanalyses, implying a ``too few, too bright'' cloud problem.
+Thermodynamic conditions are relatively well represented, but ICON is less stable than observations, and MERRA-2 is too humid.
+SO cloud biases are a substantial issue in the GSRM, but it matches the observations better than the lower-resolution reanalyses.
+\end{abstract}
+
+\section*{Plain Language Summary}
+
+Global storm-resolving models are climate models with km-scale horizontal resolution, which are currently in development.
+Reanalyses are the best estimates of past meteorological conditions based on an underlying global model and observations.
+We evaluated clouds and thermodynamic profiles over the Southern Ocean in one such model, as well as two reanalyses, based on 2400 days of ship and station observations.
+Thanks to the high resolution, the model relies entirely on explicit simulation of clouds, instead of subgrid-scale parameterizations.
+For the evaluation, we used ceilometer and radiosonde observations and a lidar simulator, which enables a fair comparison with the model and reanalyses.
+We subsetted our results by cyclonic activity and stability.
+We found that the model and reanalyses underestimate a lidar-derived cloud fraction, and the reanalyses do so more strongly.
+Fog or near-surface clouds are especially underestimated in the reanalyses.
+However, the model and one of the reanalyses also tend to overestimate the peak of cloud occurrence at 500 m above the ground, and it tends to be higher.
+This is linked to thermodynamic profiles, which show a higher lifting condensation level.
+Southern Ocean biases are still an important problem in the model, but an improvement over the reanalyses is notable.
 
@@
 
-Increasing climate model resolution is one way of improving the accuracy of
-the representation of the climate system in models \citep{mauritsen2022}. It has been
-practiced since the advent of climate modelling as more computational power,
-memory, and storage capacity become available. It is, however, often not as
-easy as changing the grid size because of the complex interplay between model
-dynamics and physics, which necessitates adjusting and tuning all components
-together. Increasing resolution is of course limited by the available
-computational power and a trade-off with increasing parameterization
-complexity, which is another way of improving model accuracy. Current
-computational availability and acceleration from general-purpose computing on
-graphics processing units (GPUs) has progressed to enable km-scale (also called
-k-scale) Earth system models (ESMs) and coupled atmosphere--ocean general
-circulation models (AOGCMs) for research today and will become operational in
-the future. Therefore, it represents a natural advance in climate
-modelling. Global storm-resolving models (GSRMs) are emerging as a new front
-in the development of high-resolution global climate models, with horizontal
-grid resolutions of about 2--8 km \citep{satoh2019,stevens2019}. This resolution is enough
-to resolve mesoscale convective storms, but smaller-scale convective plumes and
-cloud structure remain unresolved. At an approximately 5-km scale,
-non-hydrostatic processes also become important \citep{weisman1997}, and for
-this reason such models are generally non-hydrostatic. The terms global
-cloud-resolving models or global convection-permitting/-resolving models are
-also sometimes used interchangeably with GSRMs but imply that clouds or
-convection are resolved explicitly, which is not entirely true for GSRMs, as
-this would require an even higher horizontal resolution \citep{satoh2019}.
-Representative of these efforts is the DYnamics of the Atmospheric general
-circulation Modeled On Non-hydrostatic Domains (DYAMOND) project
-\citep{stevens2019,dyamond}, which is an intercomparison of nine global GSRMs
-over two 40-day time periods in summer (1 August -- 10 September 2016) and
-winter (20 January -- 1 March 2020). A new one-year GSRM intercomparison is
-currently proposed by \cite{takasuka2024}, with the hope of also evaluating the
-seasonal cycle and large-scale circulation.  An alternative to using a
-computationally costly GSRM is to train an artificial neural network on GSRM
-output and use it for subgrid-scale clouds, as done with the GSRM ICON by
-\cite{grundner2022} and \cite{grundner2023}.
+Increasing climate model resolution is one way of improving the accuracy of the representation of the climate system in models \cite{mauritsen2022}.
+It has been practiced since the advent of climate modeling as more computational power, memory, and storage capacity become available.
+It is, however, often not as easy as changing the grid size because of the complex interplay between model dynamics and physics, which necessitates adjusting and tuning all components together.
+Increasing resolution is, of course, limited by the available computational power and a trade-off with increasing parameterization complexity, which is another way of improving model accuracy.
+Current computational availability and acceleration from general-purpose computing on graphics processing units (GPUs) has progressed to enable km-scale (also called k-scale) Earth system models (ESMs) and coupled atmosphere--ocean general circulation models (AOGCMs) for research today and will become operational in the future.
+Therefore, it represents a natural advance in climate modeling.
+Global storm-resolving models (GSRMs) are emerging as a new front in the development of high-resolution global climate models, with horizontal grid resolutions of about 2--8~km \cite{satoh2019,stevens2019}.
+This resolution is enough to resolve mesoscale convective storms, but smaller-scale convective plumes and cloud structure remain unresolved.
+At an approximately 5-km scale, non-hydrostatic processes also become important \cite{weisman1997}, and for this reason such models are generally non-hydrostatic.
+The terms global cloud-resolving models or global convection-permitting/-resolving models are also sometimes used interchangeably with GSRMs but imply that clouds or convection are resolved explicitly, which is not entirely true for GSRMs, as this would require an even higher horizontal resolution \cite{satoh2019}.
+Representative of these efforts is the DYnamics of the Atmospheric general circulation Modeled On Non-hydrostatic Domains (DYAMOND) project \cite{stevens2019,dyamond}, which is an intercomparison of nine global GSRMs over two 40-day time periods in summer (1~August--10~September 2016) and winter (20~January--1~March 2020).
+A new one-year GSRM intercomparison is currently proposed by \citeA{takasuka2024}, with the hope of also evaluating the seasonal cycle and large-scale circulation.
+An alternative to using a computationally costly GSRM is to train an artificial neural network on GSRM output and use it for subgrid-scale clouds, as done with the GSRM ICON by \citeA{grundner2022} and \citeA{grundner2023}.
 
-The nextGEMS project \citep{nextgems} focuses on the research and development
-of GSRMs at multiple modelling centres and universities in Europe. The project
-also develops GSRM versions of the Icosahedral Nonhydrostatic Weather and
-Climate Model (ICON; \cite{hohenegger2023}), the Integrated Forecasting System
-[IFS; \cite{ifs2023}], and their ocean components at eddy-resolving
-resolutions: ICON-O \citep{korn2022} coupled with ICON and
-Finite-Element/volumE Sea ice-Ocean Model [FESOM; \cite{wang2014}] and Nucleus
-for European Modelling of the Ocean [NEMO; \cite{madec2023}] coupled with IFS.
-The project has so far produced ICON and IFS simulations with three development
-versions called Cycle 1--3 and a pre-final version, with a final production
-version planned by the end of the project. nextGEMS is not the only project
-developing GSRMs; other GSRMs (or GSRM versions of climate models) currently in
-development include: Convection-Permitting Simulations With the E3SM Global
-Atmosphere Model [SCREAM; \cite{caldwell2021}], Atmospheric Model [NICAM;
-\cite{satoh2008}], Unified Model (UM), eXperimental System for High-resolution
-modeling for Earth-to-Local Domain [X-SHiELD; \cite{shield}], Action de
-Recherche Petite Echelle Grande Echelle-NonHydrostatic version [ARPEGE-NH;
-\cite{bubnova1995,voldoire2017}], Finite-Volume Dynamical Core on the Cubed
-Sphere [FV3, \cite{lin2004}], the National Aeronautics and Space Administration
-(NASA) Goddard Earth Observing System global atmospheric model version 5
-[GEOS5; \cite{putman2011}], Model for Prediction Across Scales [MPAS;
-\cite{skamarock2012}], and System for Atmospheric Modeling [SAM;
-\cite{khairoutdinov2003}].
+The nextGEMS project \cite{nextgems} focuses on the research and development of GSRMs at multiple modeling centers and universities in Europe.
+The project also develops GSRM versions of the Icosahedral Nonhydrostatic Weather and Climate Model (ICON; \citeA{hohenegger2023}), the Integrated Forecasting System [IFS; \citeA{ifs2023}], and their ocean components at eddy-resolving resolutions: ICON-O \cite{korn2022} coupled with ICON and Finite-Element/volumE Sea ice-Ocean Model [FESOM; \citeA{wang2014a}] and Nucleus for European modeling of the Ocean [NEMO; \citeA{madec2023}] coupled with IFS.
+The project has so far produced ICON and IFS simulations with three development versions called Cycle 1--3 and a pre-final version, with a final production version planned by the end of the project.
+nextGEMS is not the only project developing GSRMs; other GSRMs (or GSRM versions of climate models) currently in development include: Convection-Permitting Simulations With the E3SM Global Atmosphere Model [SCREAM; \citeA{caldwell2021}], Atmospheric Model [NICAM; \citeA{satoh2008}], Unified Model (UM), eXperimental System for High-resolution modeling for Earth-to-Local Domain [X-SHiELD; \citeA{shield}], Action de Recherche Petite Echelle Grande Echelle-NonHydrostatic version [ARPEGE-NH; \citeA{bubnova1995,voldoire2017}], Finite-Volume Dynamical Core on the Cubed Sphere [FV3, \citeA{lin2004}], the National Aeronautics and Space Administration (NASA) Goddard Earth Observing System global atmospheric model version 5 [GEOS5; \citeA{putman2011}], Model for Prediction Across Scales [MPAS; \citeA{skamarock2012}], and System for Atmospheric Modeling [SAM; \citeA{khairoutdinov2003}].
 
-Multiple cloud properties have an effect on shortwave (SW) and longwave (LW)
-radiation. To first order, the total cloud fraction, cloud phase, and the
-liquid and ice water path are the most important cloud properties influencing
-SW and LW radiation. These properties are in turn influenced by the
-atmospheric thermodynamics, convection and circulation, and both the indirect
-and direct effects of aerosols. Second order effects on SW and LW radiation are
-associated with the cloud droplet size distribution, ice crystal habit, cloud
-lifetime, and direct radiative interaction with aerosols.  In the
-6$^\mathrm{th}$ phase of the Coupled Model Intercomparison Project [CMIP6;
-\cite{eyring2016}], the cloud feedback has increased relative to CMIP5
-\citep{zelinka2020}, which is one of the main reasons for the higher climate
-sensitivity of CMIP6 models.
+Multiple cloud properties have an effect on shortwave (SW) and longwave (LW) radiation.
+To first order, the total cloud fraction, cloud phase, and the liquid and ice water path are the most important cloud properties influencing SW and LW radiation.
+These properties are in turn influenced by the atmospheric thermodynamics, convection and circulation, and both the indirect and direct effects of aerosols.
+Second-order effects on SW and LW radiation are associated with the cloud droplet size distribution, ice crystal habit, cloud lifetime, and direct radiative interaction with aerosols.
+In the 6$^\mathrm{th}$ phase of the Coupled Model Intercomparison Project [CMIP6; \citeA{eyring2016}], the cloud feedback has increased relative to CMIP5 \cite{zelinka2020}, which is one of the main reasons for the higher climate sensitivity of CMIP6 models.
 
-The Southern Ocean (SO) is known to be a problematic region for climate model
-biases \citep{schuddeboom2021,hyder2018,cesana2022,zhao2022} due to a lack of
-surface and in situ observations and being a lower priority region for
-numerical weather prediction (NWP) and climate model development because of its
-distance from populated areas. Nevertheless, radiation biases and changes over
-an area of its size have a substantial influence on the global climate
-\citep{rintoul2011}, such as affecting the Earth radiation balance, ocean heat
-and carbon uptake \citep{williams2023}, and the SO is also an important part of the
-global ocean conveyor belt \citep{wang2014}. In general, marine clouds have a
-disproportionate effect on top of atmosphere (TOA) SW radiation due to the
-relatively low albedo of the sea surface.  The relative longitudinal symmetry
-of the SO means that model cloud biases tend to be similar across longitudes.
+The Southern Ocean (SO) is known to be a problematic region for climate model biases \cite{schuddeboom2021,hyder2018,cesana2022,zhao2022} due to a lack of surface and in situ observations and being a lower priority region for numerical weather prediction (NWP) and climate model development because of its distance from populated areas.
+Nevertheless, radiation biases and changes over an area of its size have a substantial influence on the global climate \cite{rintoul2011}, such as affecting the Earth radiation balance, ocean heat, and carbon uptake \cite{williams2023}, and the SO is also an important part of the global ocean conveyor belt \cite{wang2014b}.
+In general, marine clouds have a disproportionate effect on top-of-atmosphere (TOA) SW radiation due to the relatively low albedo of the sea surface.
+The approximate longitudinal symmetry of the SO means that model cloud biases tend to be similar across longitudes.
 
-Here, we refer to the SO as ocean regions south of 40°S,
-low-latitude SO as 40--55°S and high-latitude SO as south of 55°S. The reason
-for this dividing latitude is to split the SO into about two equal zones, as
-well as the results by \cite{schuddeboom2021} (Fig. 2b) which show a contrast in
-CMIP model radiation biases. \cite{schuddeboom2019} (Fig. 2) and
-\cite{kuma2020} (Fig. 3) also show contrasting radiation biases in the Hadley
-Centre Global Environmental Model, which is also supported by \cite{cesana2022} which  displays contrasting cloud biases due to the 0°C isotherm reaching the surface at 55°S. The findings
-of \cite{niu2024}, however, support a different dividing line of 62°S based on
-cloud condensation nuclei concentration.
+Here, we refer to the SO as ocean regions south of 40°S, low-latitude SO as 40--55°S and high-latitude SO as south of 55°S.
+The reason for this dividing latitude is to split the SO into about two equal zones, as well as the results by \citeA{schuddeboom2021} (Fig.~2b) which show a contrast in CMIP model radiation biases.
+\citeA{schuddeboom2019} (Fig.~2) and \citeA{kuma2020} (Fig.~3) also show contrasting radiation biases in the Hadley Centre Global Environmental Model, which is also supported by \citeA{cesana2022} which displays contrasting cloud biases due to the 0°C isotherm reaching the surface at 55°S.
+The findings of \citeA{niu2024}, however, support a different dividing line of 62°S based on cloud condensation nuclei concentration.
 
-SO radiation biases have been relatively large and systematic compared to the
-rest of the globe since at least CMIP3 \citep{trenberth2010}, and the SO SW
-cloud radiative effect (CRE) bias is still positive in eight analysed CMIP6
-models analysed by \cite{schuddeboom2021} over the high-latitude SO, whereas
-over the low-latitude SO it tends to be more neutral or negative in some
-models. Too much absorbed SW radiation over the SO was also identified in the
-GSRM SCREAM \cite{caldwell2021}. Compensating biases are possible, such as the
-`too few too bright' cloud bias, characterised by too small cloud fraction and
-too large cloud albedo \citep{wall2017,kuma2020}, previously described by
-\cite{webb2001}, \cite{weare2004}, \cite{zhang2005}, \cite{karlsson2008},
-\cite{nam2012}, \cite{klein2013}, and \cite{bender2017} in other regions and
-models, which means that a model can maintain a reasonable SW radiation balance
-by reflecting too much SW radiation from clouds, but these cover too small
-area. A study by \cite{konsta2022} showed that this type of bias is still
-present in six analysed CMIP6 models in tropical marine clouds, using the
-GCM-Oriented Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observation
-(CALIPSO) Cloud Product [CALIPSO--GOCCP; \cite{chepfer2010}] and Polarization
-\& Anisotropy of Reflectances for Atmospheric Sciences coupled with
-Observations from a Lidar [PARASOL; \cite{lier2008}] as a reference. They
-suggest improper simulation of subgrid-scale cloud heterogeneity as a cause.
-Compensating cloud biases in the Australian Community Climate and Earth System
-Simulator (ACCESS) – Atmosphere-only model version 2 (AM2) over the SO were
-analysed by \cite{fiddes2022} and \cite{fiddes2024}.  \cite{possner2022} showed
-that over the SO, the DYAMOND GSRM ICON underestimates low-level cloud fraction
-on the order of 30\% [relative to Moderate Resolution Imaging Spectroradiometer
-(MODIS) data] and overestimates downwelling TOA SW radiation by approximately
-10 Wm$^\mathrm{-2}$ [relative to the Clouds and the Earth’s Radiant Energy
-System (CERES) data] in the highest model resolution run (2.5 km).
-\cite{zhao2022} reported a similar SW radiation bias in five analysed CMIP6
-models over the high-latitude SO and an underestimation of total cloud fraction on
-the order of 10\% over the entire 40--60°S SO. Recently, \cite{ramadoss2024}
-analysed 48 hours of km-scale ICON limited area model NWP simulations over a SO
-region adjacent to Tasmania against the Clouds, Aerosols, Precipitation,
-Radiation, and atmospherIc Composition Over the southeRn oceaN (CAPRICORN)
-voyage cloud and precipitation observations \cite{mcfarquhar2021}. They found
-the ICON cloud optical thickness was underestimated relative to Himawari‐8
-satellite observations, but also identified large differences in cloud top
-phase.
+SO radiation biases have been relatively large and systematic compared to the rest of the globe since at least CMIP3 \cite{trenberth2010}, and the SO SW cloud radiative effect (CRE) bias is still positive in eight analyzed CMIP6 models analyzed by \citeA{schuddeboom2021} over the high-latitude SO, whereas over the low-latitude SO it tends to be more neutral or negative in some models.
+Too much absorbed SW radiation over the SO was also identified in the GSRM SCREAM \cite{caldwell2021}.
+Compensating biases are possible, such as the ``too few too bright'' cloud bias, characterized by too small cloud fraction and too large cloud albedo \cite{wall2017,kuma2020}, previously described by \citeA{webb2001}, \citeA{weare2004}, \citeA{zhang2005}, \citeA{karlsson2008}, \citeA{nam2012}, \citeA{klein2013}, and \citeA{bender2017} in other regions and models, which means that a model can maintain a reasonable SW radiation balance by reflecting too much SW radiation from clouds, but these cover too small an area.
+A study by \citeA{konsta2022} showed that this type of bias is still present in six analyzed CMIP6 models in tropical marine clouds, using the GCM-Oriented Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observation (CALIPSO) Cloud Product [CALIPSO--GOCCP; \citeA{chepfer2010}] and Polarization \& Anisotropy of Reflectances for Atmospheric Sciences coupled with Observations from a Lidar [PARASOL; \citeA{lier2008}] as a reference.
+They suggest improper simulation of subgrid-scale cloud heterogeneity as a cause.
+Compensating cloud biases in the Australian Community Climate and Earth System Simulator (ACCESS) – Atmosphere-only model version 2 (AM2) over the SO were analyzed by \citeA{fiddes2022} and \citeA{fiddes2024}.
+\citeA{possner2022} showed that over the SO, the DYAMOND GSRM ICON underestimates low-level cloud fraction on the order of 30\% and overestimates net downward TOA SW radiation by approximately 10 Wm$^\mathrm{-2}$ in the highest model resolution run (2.5~km).
+\citeA{zhao2022} reported a similar SW radiation bias in five analyzed CMIP6 models over the high-latitude SO and an underestimation of the total cloud fraction on the order of 10\% over the entire 40--60°S SO.
+Recently, \citeA{ramadoss2024} analyzed 48~hours of km-scale ICON limited-area model NWP simulations over a SO region adjacent to Tasmania against the Clouds, Aerosols, Precipitation, Radiation, and atmospherIc Composition Over the southeRn oceaN (CAPRICORN) voyage cloud and precipitation observations \cite{mcfarquhar2021}.
+They found the ICON cloud optical thickness was underestimated relative to Himawari‐8 satellite observations but also identified large differences in cloud top phase.
 
-In general, sea surface temperature (SST) biases in the SO can originate either
-in the atmosphere \citep{hyder2018}, caused by too much shortwave heating of
-the surface, too little longwave cooling of the surface, or in the ocean
-circulation. Interactions of both are also possible, for example SST affecting
-clouds and clouds affecting the surface radiation. Using the European Centre
-for Medium-Range Weather Forecasts (ECMWF) Reanalysis 5 (ERA5) as a reference,
-\cite{zhang2023} have shown that SST biases have improved in CMIP6 compared to
-CMIP5, with SST overall increasing in CMIP6. However, over the
-SO this resulted in an even higher positive bias, especially in the Atlantic
-Ocean (AO) sector of the SO, increasing by up to 1°C.  \cite{luo2023}
-identified that the SO SST bias in an ensemble of 18 CMIP6 models originates
-not from the surface heat and radiation fluxes (using reanalyses as a
-reference), but from a warm bias in the Northern Atlantic Deep Water.
+In general, sea surface temperature (SST) biases in the SO can originate either in the atmosphere \cite{hyder2018}, caused by too much shortwave heating the surface, too little longwave cooling the surface, or in the ocean circulation.
+Interactions of both are also possible, for example, SST affecting clouds and clouds affecting the surface radiation.
+Using the European Centre for Medium-Range Weather Forecasts (ECMWF) Reanalysis 5 (ERA5) as a reference, \citeA{zhang2023} have shown that SST biases have improved in CMIP6 compared to CMIP5, with SST overall increasing in CMIP6.
+However, over the SO this resulted in an even higher positive bias, especially in the Atlantic Ocean (AO) sector of the SO, increasing by up to 1°C.
+\citeA{luo2023} identified that the SO SST bias in an ensemble of 18 CMIP6 models originates not from the surface heat and radiation fluxes (using reanalyses as a reference), but from a warm bias in the Northern Atlantic Deep Water.
 
-The main aim of this study is to evaluate the GSRM version of ICON. ICON
-is developed and maintained jointly by Deutscher Wetterdienst,
-Max-Planck-Institute for Meteorology, Deutsches Klimarechenzentrum (DKRZ),
-Karlsruhe Institute of Technology, and the Center for Climate Systems Modeling.
-Previous studies have identified substantial large-scale biases in climate
-model clouds over the SO, affecting sea surface temperature and the Earth’s
-albedo. Our aim is to quantify how well the GSRM ICON simulates clouds in
-this region, particularly in light of the fact that subgrid-scale clouds and
-convection are not parameterized in this model. This region is mostly dominated
-by boundary layer clouds generated by shallow convection, and these are
-problematic to observe by spaceborne lidars and radars, which are affected by
-attenuation by overlapping and thick clouds \citep{mace2009,medeiros2010} and
-ground clutter \citep{marchand2008}, respectively.  Specifically, the radar on
-CloudSat and lidar on CALIPSO (neither of which are now operational) are
-affected by the above mentioned issues, resulting in a strong underestimation of
-cloud occurrence below 2 km relative to ground-based lidar observations
-\citep{mcerlich2021}.  We hypothesise that this, in turn, can lead to
-systematic biases in low clouds in climate models, which are frequently
-evaluated against CloudSat--CALIPSO products. Reanalyses can also suffer from
-cloud biases, as these are usually parametrised in their atmospheric component,
-and also in regions where input observations are sparse. This makes them a
-problematic reference for clouds over the SO, and any biases relative to a
-reanalysis should be interpreted with caution. Instead, we chose to use a large
-set of ship-based observations conducted with ceilometers and lidars on board
-the RV \emph{Polarstern} and other voyages and stations as a reference for model evaluation.
+The main aim of this study is to evaluate the GSRM version of ICON.
+ICON is developed and maintained jointly by Deutscher Wetterdienst, Max-Planck-Institute for Meteorology, Deutsches Klimarechenzentrum (DKRZ), Karlsruhe Institute of Technology, and the Center for Climate Systems Modeling.
+Previous studies have identified substantial large-scale biases in climate model clouds over the SO, affecting sea surface temperature and the Earth’s albedo.
+Our aim is to quantify how well the GSRM ICON simulates clouds in this region, particularly in light of the fact that subgrid-scale clouds and convection are not parameterized in this model.
+This region is mostly dominated by boundary layer clouds generated by shallow convection, and these are problematic to observe by spaceborne lidars and radars, which are affected by attenuation by overlapping and thick clouds \cite{mace2009,medeiros2010} and ground clutter \cite{marchand2008}, respectively.
+Specifically, the radar on CloudSat and lidar on CALIPSO (neither of which are now operational) are affected by the above-mentioned issues, resulting in a strong underestimation of cloud occurrence below 2 km relative to ground-based lidar observations \cite{mcerlich2021}.
+We hypothesize that this, in turn, can lead to systematic biases in low clouds in climate models, which are frequently evaluated against CloudSat--CALIPSO products.
+Reanalyses can also suffer from cloud biases, as these are usually parameterized in their atmospheric component and also in regions where input observations are sparse.
+This makes them a problematic reference for clouds over the SO, and any biases relative to a reanalysis should be interpreted with caution.
+Instead, we chose to use a large set of ship-based observations conducted with ceilometers and lidars on board the RV \emph{Polarstern} and other voyages and stations as a reference for the model evaluation.
 
-Altogether, we analysed about 2400 days of data from 31 voyages, and one
-sub-Antarctic station covering diverse longitudes and latitudes of the SO. To
-achieve a like-for-like comparison with the model, we used a ground-based lidar
-simulator called the Automatic Lidar and Ceilometer Framework [ALCF;
-\cite{kuma2021}]. We contrasted the results with ERA5 \citep{era5} and the
-Modern-Era Retrospective analysis for Research and Applications, Version 2
-[MERRA-2; \cite{gelaro2017}].
+Altogether, we analyzed about 2400 days of data from 31 voyages and one sub-Antarctic station covering diverse longitudes and latitudes of the SO.
+To achieve a like-for-like comparison with the model, we used a ground-based lidar simulator called the Automatic Lidar and Ceilometer Framework [ALCF; \citeA{kuma2021}].
+We contrasted the results with ERA5 \cite{era5} and the Modern-Era Retrospective analysis for Research and Applications, Version~2 [MERRA-2; \citeA{gelaro2017}].
 
@@
 \caption{
-\textbf{(a)} A map showing the tracks of 31 voyages of RV \emph{Polarstern},
-RSV \emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B. Palmer},
-and HMNZS \emph{Wellington} and one sub-Antarctic station (Macquarie Island)
-analysed here. The tracks cover Antarctic sectors south of South America, the
-Atlantic Ocean, Africa, Australia, and New Zealand in the years 2010--2021
-(inclusive).  The dotted and dashed lines at 40°S and 55°S delineate the
-Southern Ocean area of our analysis and its partitioning into two subsets,
-respectively.  A photo of \textbf{(b)} RV \emph{Polarstern} (© Folke Mehrtens,
-Alfred-Wegener-Institut), \textbf{(c)} Lufft CHM 15k installed on RV
-\emph{Tangaroa} (© Peter Kuma, University of Canterbury), \textbf{(d)} Vaisala
-CL51 (© Jeff Aquilina, Bureau of Meteorology), \textbf{(e)} Vaisala CT25K at
-Macquarie Island (© Simon P.\ Alexander, Australian Antarctic Division).
+\textbf{(a)} A map showing the tracks of 31 voyages of RV \emph{Polarstern}, RSV \emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B.
+Palmer}, and HMNZS \emph{Wellington} and one sub-Antarctic station (Macquarie Island) analyzed here.
+The tracks cover Antarctic sectors south of South America, the Atlantic Ocean, Africa, Australia, and New Zealand in the years 2010--2021 (inclusive).
+The dotted and dashed lines at 40°S and 55°S delineate the Southern Ocean area of our analysis and its partitioning into two subsets, respectively.
+A photo of \textbf{(b)} RV \emph{Polarstern} (© Folke Mehrtens, Alfred-Wegener-Institut), \textbf{(c)} Lufft CHM~15k installed on RV \emph{Tangaroa} (© Peter Kuma, University of Canterbury), \textbf{(d)} Vaisala CL51 (© Jeff Aquilina, Bureau of Meteorology), \textbf{(e)} Vaisala CT25K at Macquarie Island (© Simon P.\ Alexander, Australian Antarctic Division).
 }
@@
 
-\subsection{Voyage and station data}
+\subsection{Voyage and Station Data}
 
-Together, we analysed data from 31 voyages of RV \emph{Polarstern}, the
-resupply vessel (RSV) \emph{Aurora Australis}, RV \emph{Tangaroa}, RV
-\emph{Nathaniel B.  Palmer}, Her (now His) Majesty's New Zealand Ship (HMNZS)
-\emph{Wellington} and one sub-Antarctic station (Macquarie Island) in the SO
-south of 40°S between 2010 and 2021. Fig. \ref{fig:map} shows a map of the
-voyages, Table \ref{tab:voyages} lists the voyages, campaigns, and stations, and
-Table \ref{tab:voyage-references} lists references where available. Altogether,
-the voyages and station dataset comprised 2421 days of data south of 40°S, but
-the availability of ceilometer data was slightly shorter due to gaps in
-measurements.
+Together, we analyzed data from 31 voyages of RV \emph{Polarstern}, the resupply vessel (RSV) \emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B.
+Palmer}, Her (now His) Majesty's New Zealand Ship (HMNZS) \emph{Wellington} and one sub-Antarctic station (Macquarie Island) in the SO south of 40°S between 2010 and 2021.
+Fig.~\ref{fig:map} shows a map of the campaigns, Table \ref{tab:voyages} lists the campaigns, and Table \ref{tab:voyage-references} lists references where available.
+Altogether, the analyzed dataset comprised 2421 days of data south of 40°S, but the availability of ceilometer data was slightly lower due to gaps in measurements.
 
-Missing days in the ceilometer data were HMNZSW16 (7 days): 24--27 November, 10
-December, 16--17 December 2016; Measurements of Aerosols, Radiation, and CloUds
-over the Southern Ocean (MARCUS;  3 days): 8, 10 November, 10 December 2017;
-Macquarie Island Cloud Radiation Experiment (MICRE; 9 days): 7--8, 29 June, 5,
-16 July, 15 August, 17 October 2016, 11 February, 21 March 2017; TAN1502 (1
-day): 24 January.
+The campaigns contained ceilometer observations captured by the Vaisala CL51, CT25K, and the Lufft CHM~15k, described in detail below (Sections~\ref{sec:cl51} and \ref{sec:chm15k}).
+A ceilometer is a low-power, near-infrared, vertically pointing lidar principally designed to measure cloud base, but they also measure the full vertical structure of clouds as long as the laser signal is not attenuated by thick clouds, which can be used to infer additional information such as a cloud mask and cloud occurrence by height.
+We note that during the MICRE campaign, the ceilometers Vaisala CT25K and CL51 were installed at the Macquarie Island station concurrently, but in our analysis we only used the CT25K data obtained from the Atmospheric Radiation Measurement (ARM) data archive.
 
-The data sources contained ceilometer observations captured by the Vaisala CL51
-and CT25K, and the Lufft CHM 15k, described in detail below (Sections
-\ref{sec:cl51} and \ref{sec:chm15k}). A ceilometer is a low-power near-infrared
-vertically pointing lidar principally designed to measure cloud base, but they
-also measure the full vertical structure of clouds as long as the laser signal
-is not attenuated by thick clouds, which can be used to infer additional
-information such as a cloud mask and cloud occurrence by height.  We note that
-during the MICRE campaign, the ceilometers Vaisala CT25K and CL51 were
-installed at the Macquarie Island station concurrently, but in our analysis we
-only used the CT25K data obtained from the Atmospheric Radiation Measurement
-(ARM) data archive.
-
-Apart from lidar observations, radiosondes were launched on weather balloons at
-regular synoptic times on the RV \emph{Polarstern}, MARCUS, NBP17024, TAN1702,
-and TAN1802 voyages and campaigns, measuring pressure, temperature, relative
-humidity, and the global navigation satellite system coordinates. Derived
-thermodynamic (virtual potential temperature, lifting condensation level, etc.)
-and dynamic physical quantities (wind speed and direction) for the measured
-vertical profiles were calculated with rstool \citep{rstool}. Surface
-meteorological quantities were measured continuously by an onboard automatic
-weather station or individual instruments.
+Apart from lidar observations, radiosondes were launched on weather balloons at regular synoptic times on the RV \emph{Polarstern}, MARCUS, NBP17024, TAN1702, and TAN1802 campaigns, measuring pressure, temperature, relative humidity, and the global navigation satellite system coordinates.
+Derived thermodynamic (virtual potential temperature, lifting condensation level, etc.) and dynamic physical quantities (wind speed and direction) for the measured vertical profiles were calculated with rstool \cite{rstool}.
+Surface meteorological quantities were measured continuously by an onboard automatic weather station or individual instruments.
 
@@
 \caption{
-An overview of the analysed voyages, campaigns, and stations. Start, end, and
-the number of days (UTC; inclusive) refer to the time period when the vessel
-was south of 40°S.  Abbreviations: ceilometer (ceil.), Australia (AU), New
-Zealand (NZ), South America (SA), Atlantic Ocean (AO), and Africa (AF). The
-number of days is rounded to the nearest integer. CL51/31 indicates CL51
-configured to emulate CL31.
+An overview of the analyzed campaigns (voyages and stations).
+Start, end, and the number of days (UTC; inclusive) refer to the time period when the vessel was south of 40°S.
+Abbreviations: ceilometer (ceil.), Australia (AU), New Zealand (NZ), South America (SA), Atlantic Ocean (AO), and Africa (AF).
+The number of days is rounded to the nearest integer.
+CL51/31 indicates CL51 configured to emulate CL31.
+Missing days in the ceilometer data were HMNZSW16 (7 days): 24--27 November, 10~December, 16--17~December 2016; MARCUS (3 days): 8, 10~November, 10~December 2017; MICRE (9~days): 7--8, 29~June, 5, 16~July, 15~August, 17~October 2016, 11~February, 21~March 2017; TAN1502 (1~day): 24~January.
 }
 \label{tab:voyages}
+\centering
 \small
@@
 \begin{table}[t!]
-\caption{Voyage, campaign and station publication references.}
+\caption{Campaign publication references.}
 \label{tab:voyage-references}
+\centering
 \small
@@
 \hline
-AA15-16  & \cite{klekociuk2020} \\
-MARCUS   & \cite{mcfarquhar2021,xia2024,niu2024} \\
-MICRE    & \cite{mcfarquhar2021} \\
-NBP1704  & \cite{ackley2020} \\
-PS77/2   & \cite{kniglanglo2011a,kniglanglo2011b,kniglanglo2011c,kniglanglo2014a,fahrbach2011} \\
-PS77/3   & \cite{kniglanglo2011d,kniglanglo2011e,kniglanglo2012a,kniglanglo2014b,knust2011} \\
-PS79/2   & \cite{kniglanglo2012b,kniglanglo2012c,kniglanglo2012d,kniglanglo2014c,kattner2012} \\
-PS79/3   & \cite{kniglanglo2012e,kniglanglo2012f,kniglanglo2012g,kniglanglo2014d,wolfgladrow2012} \\
-PS79/4   & \cite{kniglanglo2012h,kniglanglo2012i,kniglanglo2012j,kniglanglo2014e,lucassen2012} \\
-PS81/2   & \cite{kniglanglo2013a,kniglanglo2013b,kniglanglo2013c,kniglanglo2014f,boebel2013} \\
-PS81/3   & \cite{kniglanglo2013d,kniglanglo2013e,kniglanglo2013f,kniglanglo2014g,gutt2013} \\
-PS81/4   & \cite{kniglanglo2013g,kniglanglo2013h,kniglanglo2013i,kniglanglo2014f,bohrmann2013} \\
-PS81/5   & \cite{kniglanglo2013j,kniglanglo2013k,kniglanglo2013l,kniglanglo2014g,jokat2013} \\
-PS81/6   & \cite{kniglanglo2013m,kniglanglo2013n,kniglanglo2013o,kniglanglo2014h,lemke2013} \\
-PS81/7   & \cite{kniglanglo2013p,kniglanglo2013q,kniglanglo2014i,kniglanglo2016a,meyer2013} \\
-PS81/8   & \cite{kniglanglo2013r,kniglanglo2014j,kniglanglo2014k,kniglanglo2014l,schlindwein2014} \\
-PS81/9   & \cite{kniglanglo2014m,kniglanglo2014n,kniglanglo2014o,kniglanglo2014p,knust2014} \\
-PS89     & \cite{kniglanglo2015a,kniglanglo2015b,kniglanglo2015c,kniglanglo2015d,boebel2016}\\
-PS96     & \cite{kniglanglo2016b,kniglanglo2016c,kniglanglo2016d,kniglanglo2016e,schrder2017} \\
-PS97     & \cite{kniglanglo2016f,kniglanglo2016g,kniglanglo2016h,kniglanglo2016i,lamy2017} \\
-PS103    & \cite{kniglanglo2017a,kniglanglo2017b,kniglanglo2017c,kniglanglo2017d,boebel2018} \\
-PS104    & \cite{kniglanglo2017e,kniglanglo2017f,kniglanglo2017g,gohl2018,schmithsen2021a} \\
-PS111    & \cite{schmithsen2019a,schmithsen2020a,schmithsen2021b,schmithsen2021c,schrder2018} \\
-PS112    & \cite{schmithsen2019b,schmithsen2020b,schmithsen2021d,schmithsen2021e,meyer2018} \\
-PS117    & \cite{schmithsen2019c,schmithsen2020c,schmithsen2021f,schmithsen2021g,boebel2019} \\
-PS118    & \cite{schmithsen2019d,schmithsen2020d,schmithsen2021h,schmithsen2021i,dorschel2019} \\
-PS123    & \cite{schmithsen2021j,schmithsen2021m,schmithsen2021n,schmithsen2021k,hoppmann2023} \\
-PS124    & \cite{schmithsen2021o,schmithsen2021q,schmithsen2021p,hoppmann2023} \\
-TAN1802  & \cite{kremser2020,kremser2021} \\
+AA15-16  & \citeA{klekociuk2020} \\
+MARCUS   & \citeA{mcfarquhar2021,xia2024,niu2024} \\
+MICRE    & \citeA{mcfarquhar2021} \\
+NBP1704  & \citeA{ackley2020} \\
+PS77/2   & \citeA{kniglanglo2011a,kniglanglo2011b,kniglanglo2011c,kniglanglo2014a,fahrbach2011} \\
+PS77/3   & \citeA{kniglanglo2011d,kniglanglo2011e,kniglanglo2012a,kniglanglo2014b,knust2011} \\
+PS79/2   & \citeA{kniglanglo2012b,kniglanglo2012c,kniglanglo2012d,kniglanglo2014c,kattner2012} \\
+PS79/3   & \citeA{kniglanglo2012e,kniglanglo2012f,kniglanglo2012g,kniglanglo2014d,wolfgladrow2012} \\
+PS79/4   & \citeA{kniglanglo2012h,kniglanglo2012i,kniglanglo2012j,kniglanglo2014e,lucassen2012} \\
+PS81/2   & \citeA{kniglanglo2013a,kniglanglo2013b,kniglanglo2013c,kniglanglo2014f,boebel2013} \\
+PS81/3   & \citeA{kniglanglo2013d,kniglanglo2013e,kniglanglo2013f,kniglanglo2014g,gutt2013} \\
+PS81/4   & \citeA{kniglanglo2013g,kniglanglo2013h,kniglanglo2013i,kniglanglo2014q,bohrmann2013} \\
+PS81/5   & \citeA{kniglanglo2013j,kniglanglo2013k,kniglanglo2013l,kniglanglo2014r,jokat2013} \\
+PS81/6   & \citeA{kniglanglo2013m,kniglanglo2013n,kniglanglo2013o,kniglanglo2014h,lemke2013} \\
+PS81/7   & \citeA{kniglanglo2013p,kniglanglo2013q,kniglanglo2014i,kniglanglo2016a,meyer2013} \\
+PS81/8   & \citeA{kniglanglo2013r,kniglanglo2014j,kniglanglo2014k,kniglanglo2014l,schlindwein2014} \\
+PS81/9   & \citeA{kniglanglo2014m,kniglanglo2014n,kniglanglo2014o,kniglanglo2014p,knust2014} \\
+PS89     & \citeA{kniglanglo2015a,kniglanglo2015b,kniglanglo2015c,kniglanglo2015d,boebel2016}\\
+PS96     & \citeA{kniglanglo2016b,kniglanglo2016c,kniglanglo2016d,kniglanglo2016e,schrder2017} \\
+PS97     & \citeA{kniglanglo2016f,kniglanglo2016g,kniglanglo2016h,kniglanglo2016i,lamy2017} \\
+PS103    & \citeA{kniglanglo2017a,kniglanglo2017b,kniglanglo2017c,kniglanglo2017d,boebel2018} \\
+PS104    & \citeA{kniglanglo2017e,kniglanglo2017f,kniglanglo2017g,gohl2018,schmithsen2021a} \\
+PS111    & \citeA{schmithsen2019a,schmithsen2020a,schmithsen2021b,schmithsen2021c,schrder2018} \\
+PS112    & \citeA{schmithsen2019b,schmithsen2020b,schmithsen2021d,schmithsen2021e,meyer2018} \\
+PS117    & \citeA{schmithsen2019c,schmithsen2020c,schmithsen2021f,schmithsen2021g,boebel2019} \\
+PS118    & \citeA{schmithsen2019d,schmithsen2020d,schmithsen2021h,schmithsen2021i,dorschel2019} \\
+PS123    & \citeA{schmithsen2021j,schmithsen2021m,schmithsen2021n,schmithsen2021k,hoppmann2023a} \\
+PS124    & \citeA{schmithsen2021o,schmithsen2021q,schmithsen2021p,hoppmann2023b} \\
+TAN1802  & \citeA{kremser2020,kremser2021} \\
+\hline
 \end{tabular}
@@
 
-The Vaisala CL51 and CT25K (photos in Fig. \ref{fig:map}d, e) are ceilometers
-operating at a near-infrared wavelength of 910 nm and 905 nm, respectively.
-The CL51 can also be configured to emulate the Vaisala CL31. The maximum range
-is 15.4 km (CL51), 7.7 km (CL31 emulation mode with 5 m vertical resolution),
-and 7.5 km (CT25K). The vertical resolution is 10 m (5 m configurable) in CL51
-and 30 m in CT25K observations. The sampling (temporal) resolution is
-configurable, and in our datasets is approximately 6 s for CL51 on AA15‐16, 16
-s for CT25K on MARCUS and MICRE, 36 s for CL51 on RV \emph{Polarstern}, and
-about 2.37 s for CL51 with CL31 emulation on TAN1502. The wavelengths of 905
-and 910 nm are both affected by water vapour absorption of about 20\% in the
-mid-latitudes \citep{wiegner2015,wiegner2019}, with 910 nm affected more
-strongly, but we do not expect this to be a significant issue as explained in
-\cite{kuma2021}.  The instrument data files containing raw uncalibrated
-backscatter were first converted to Network Common Data Form (NetCDF) with
-cl2nc (\url{https://github.com/peterkuma/cl2nc}) and then processed with the
-ALCF (Section \ref{sec:alcf}) to produce absolutely calibrated attenuated
-volume backscattering coefficient (AVBC), cloud mask, cloud occurrence by
-height, and the total cloud fraction. Because the CT25K uses a very similar
-wavelength to CL51, equivalent calculations as for CL51 were done assuming a
-wavelength of 910 nm. The Vaisala CL51 and CT25K instruments were used on most
-of the voyages and stations analysed here. Fig.  \ref{fig:example}a shows an
-example of AVBC derived from the CL51 instrument data.
+The Vaisala CL51 and CT25K (photos in Fig.~\ref{fig:map}d, e) are ceilometers operating at near-infrared wavelengths of 910~nm and 905~nm, respectively.
+The CL51 can also be configured to emulate the Vaisala CL31.
+The maximum range is 15.4~km (CL51), 7.7~km (CL31 emulation mode with 5~m vertical resolution), and 7.5~km (CT25K).
+The vertical resolution is 10~m (5~m configurable) in CL51 and 30~m in CT25K observations.
+The sampling (temporal) resolution is configurable, and in our datasets, it is approximately 6~s for CL51 on AA15‐16, 16~s for CT25K on MARCUS and MICRE, 36~s for CL51 on RV \emph{Polarstern}, and about 2.37~s for CL51 with CL31 emulation on TAN1502.
+The wavelengths of 905 and 910~nm are both affected by water vapor absorption of about 20\% in the mid-latitudes \cite{wiegner2015,wiegner2019}, with 910~nm affected more strongly, but we do not expect this to be a significant issue as explained in \citeA{kuma2021}.
+The instrument data files containing raw uncalibrated backscatter were first converted to Network Common Data Form (NetCDF) with cl2nc \cite{kuma2024a} and then processed with the ALCF (Section~\ref{sec:alcf}) to produce absolutely calibrated attenuated volume backscattering coefficient (AVBC), cloud mask, cloud occurrence by height, and the total cloud fraction.
+Because the CT25K uses a very similar wavelength to CL51, equivalent calculations as for CL51 were done assuming a wavelength of 910~nm.
+The Vaisala CL51 and CT25K instruments were used on most of the voyages and stations analyzed here.
+Fig.~\ref{fig:example}a shows an example of AVBC derived from the CL51 instrument data.
 
@@
 \caption{
-An example of attenuated volume backscattering coefficient (AVBC) \textbf{(a)}
-measured by a CL51 during 24 hours on the PS81/3 voyage and \textbf{(b)} an
-equivalent AVBC simulated with the ALCF from ERA5 data during the same time
-period. The red line identifies the cloud mask determined by the ALCF.
+An example of the attenuated volume backscattering coefficient (AVBC) \textbf{(a)} measured by the CL51 during 24~hours on the PS81/3 voyage and \textbf{(b)} an equivalent AVBC simulated with the ALCF from ERA5 data during the same time period.
+The red line identifies the cloud mask determined by the ALCF.
 }
@@
 
-\subsection{Lufft CHM 15k}
+\subsection{Lufft CHM~15k}
 \label{sec:chm15k}
 
-The Lufft CHM 15k (photo in Fig. \ref{fig:map}c) is a ceilometer operating at a
-near-infrared wavelength of 1064 nm. The maximum range is 15.4 km, the vertical
-resolution is 5 m in the near range (up to 150 m) and 15 m above, the sampling
-(temporal) resolution is 2 s, and the number of vertical levels is 1024.
-NetCDF files containing uncalibrated backscatter produced by the instrument
-were processed with the ALCF (Section \ref{sec:alcf}) to again produce AVBC,
-cloud mask, cloud occurrence by height, and the total cloud fraction. The CHM
-15k was used on four voyages (HMNZSW16, TAN1702, TAN1802, and NBP1704).
+The Lufft CHM~15k (photo in Fig.~\ref{fig:map}c) ceilometer operates at a near-infrared wavelength of 1064~nm.
+The maximum range is 15.4~km; the vertical resolution is 5~m in the near range (up to 150~m) and 15~m above; the sampling (temporal) resolution is 2~s; and the number of vertical levels is 1024.
+NetCDF files containing uncalibrated backscatter produced by the instrument were processed with the ALCF (Section~\ref{sec:alcf}) to again produce AVBC, cloud mask, cloud occurrence by height, and the total cloud fraction.
+The CHM~15k was used on four voyages (HMNZSW16, TAN1702, TAN1802, and NBP1704).
 
@@
 
-The Automatic Lidar and Ceilometer Framework (ALCF) is a ground-based lidar
-simulator and a tool for processing observed lidar data, supporting various
-instruments and models \citep{kuma2021}. It performs radiative transfer
-calculations to derive equivalent lidar AVBC from an atmospheric model, which can
-then be compared with observed AVBC. For this purpose, it takes the cloud
-fraction, liquid and ice mass mixing ratio, temperature, and pressure model
-fields as an input and is run offline (on the model output rather than inside
-the model code). The lidar simulator in the ALCF is based on the instrument
-simulator Cloud Feedback Model Intercomparison Project (CFMIP) Observation
-Simulator Package (COSP) \citep{bodas-salcedo2011}.  After AVBC is calculated,
-a cloud mask, cloud occurrence by height, and the total cloud fraction are
-determined. The ALCF has been used by several research teams for model and
-reanalysis evaluation
-\citep{kuma2020,kremser2021,guyot2022,pei2023,whitehead2023,mcdonald2024}.
+The Automatic Lidar and Ceilometer Framework (ALCF) is a ground-based lidar simulator and a tool for processing observed lidar data, supporting various instruments and models \cite{kuma2021}.
+It performs radiative transfer calculations to derive equivalent lidar AVBC from an atmospheric model, which can then be compared with observed AVBC.
+For this purpose, it takes the cloud fraction, liquid and ice mass mixing ratio, temperature, and pressure model fields as an input and is run offline (on the model output rather than inside the model code).
+The lidar simulator in the ALCF is based on the instrument simulator Cloud Feedback Model Intercomparison Project (CFMIP) Observation Simulator Package (COSP) \cite{bodas-salcedo2011}.
+After AVBC is calculated, a cloud mask, cloud occurrence by height, and the total cloud fraction are determined.
+The ALCF has been used by several research teams for model and reanalysis evaluation \cite{kuma2020,kremser2021,guyot2022,pei2023,whitehead2023,mcdonald2024a}.
 
-Absolute calibration of the observed backscatter was performed by comparing the
-measured clear-sky molecular backscatter statistically with simulated clear-sky
-molecular backscatter. AVBC was resampled to 5 min temporal resolution and 50 m
-vertical resolution to increase signal-to-noise ratio while having enough
-resolution to detect small-scale cloud variability. The noise standard
-deviation was calculated from AVBC at the highest range, where no clouds are
-expected.  A cloud mask was calculated from AVBC using a fixed threshold of
-$\mathrm{2\times 10^{-6} m^{-1}sr^{-1}}$ after subtracting 5 standard
-deviations of range-scaled noise. Fig. \ref{fig:example}b shows an example of
-simulated Vaisala CL51 backscatter from ERA5 data, corresponding to a day of
-measurements by the instrument on the PS81/3 voyage.
+Absolute calibration of the observed backscatter was performed by comparing the measured clear-sky molecular backscatter statistically with simulated clear-sky molecular backscatter.
+AVBC was resampled to 5 min temporal resolution and 50~m vertical resolution to increase the signal-to-noise ratio while having enough resolution to detect small-scale cloud variability.
+The noise standard deviation was calculated from AVBC at the highest range, where no clouds are expected.
+A cloud mask was calculated from AVBC using a fixed threshold of $\mathrm{2\times 10^{-6} m^{-1}sr^{-1}}$ after subtracting 5 standard deviations of range-scaled noise.
+Fig.~\ref{fig:example}b shows an example of simulated Vaisala CL51 backscatter from ERA5 data, corresponding to a day of measurements by the instrument on the PS81/3 voyage.
 
@@
 
-A coupled (atmosphere--ocean) GSRM version of the ICON model is in development
-as part of the nextGEMS project \citep{hohenegger2023}. ICON is an exceptionally
-versatile model, allowing for simulations ranging from coarse-resolution ESM
-simulations, GSRM simulations, limited area model simulations, to large eddy
-simulations (LES), for both weather prediction and climate projections. ICON
-uses the atmospheric component ICON-A \citep{giorgetta2018}, whose physics is
-derived from ECHAM6 \citep{stevens2013}, and the ocean component ICON-O
-\citep{korn2022}. Earlier runs of the GSRM ICON from DYAMOND were evaluated by
-\cite{mauritsen2022}.
+A coupled (atmosphere--ocean) GSRM version of the ICON model is in development as part of the nextGEMS project \cite{hohenegger2023}.
+ICON is an exceptionally versatile model, allowing for simulations ranging from coarse-resolution ESM simulations, GSRM simulations, limited area model simulations, to large eddy simulations (LES), for both weather prediction and climate projections.
+ICON uses the atmospheric component ICON-A \cite{giorgetta2018}, whose physics is derived from ECHAM6 \cite{stevens2013}, and the ocean component ICON-O \cite{korn2022}.
+Earlier runs of the GSRM ICON from DYAMOND were evaluated by \citeA{mauritsen2022}.
 
-Here, we use a free-running (i.e., the weather situation in the model does not
-correspond to reality) coupled GSRM simulation made for the purpose of climate
-projection.  nextGEMS has so far produced four cycles of model runs. We used a
-Cycle 3 run \emph{ngc3028} produced in 2023 \citep{nextgems2023a,nextgems2023b}
-for a model time period of 20 January 2020 to 22 July 2025, of which we
-analysed the period 2021--2024 (inclusive). While a Cycle 4 run was available,
-we could not use it due to a lack of availability of the necessary variables.
-The horizontal resolution of ngc3028 is about 5 km.  The model output is
-available on 90 vertical levels and 3-hourly instantaneous temporal resolution.
+Here, we use a free-running (i.e., the weather situation in the model does not correspond to reality) coupled GSRM simulation made for the purpose of climate projection.
+nextGEMS has so far produced four cycles of model runs.
+We used a Cycle 3 run \emph{ngc3028} produced in 2023 \cite{nextgems2023a,nextgems2023b} for a model time period of 20 January 2020 to 22 July 2025, of which we analyzed the period 2021--2024 (inclusive).
+The horizontal resolution of \emph{ngc3028} is about 5 km.
+The model output is available on 90 vertical levels and 3-hourly instantaneous temporal resolution.
 
-Unlike current general circulation models (GCMs), the storm-resolving version
-of ICON does not use convective and cloud parameterization but relies on
-explicit simulation of convection and clouds on the model grid. Subgrid-scale
-clouds are not resolved, and the grid cell cloud fraction is always either 0 or
-100\%. While this makes the code development simpler without having to rely on
-uncertain parameterizations, it can miss smaller-scale clouds below the grid
-resolution.  Turbulence and cloud microphysics are still parameterized in this
-model. To account for the radiative effects of subgrid-scale clouds, a cloud
-inhomogeneity factor is introduced in the model which scales down the cloud
-liquid water for radiative calculations. It ranges from 0.4 at lower
-tropospheric stability (LTS) of 0 K to 0.8 at 30 K. In addition, vertical
-mixing is enhanced in unstable and humid lower-tropospheric conditions, which
-reduces the amount of shallow clouds.
+Unlike current general circulation models (GCMs), the storm-resolving version of ICON does not use convective and cloud parameterization but relies on explicit simulation of convection and clouds on the model grid.
+Subgrid-scale clouds are not resolved, and the grid cell cloud fraction is always either 0 or 100\%.
+While this makes the code development simpler without having to rely on uncertain parameterizations, it can miss smaller-scale clouds below the grid resolution.
+Turbulence and cloud microphysics are still parameterized in this model, and aerosols are taken from a climatology.
+To account for the radiative effects of subgrid-scale clouds, a cloud inhomogeneity factor is introduced in the model, which scales down the cloud liquid water for radiative calculations.
+It ranges from 0.4 at lower tropospheric stability (LTS) of 0~K to 0.8 at 30~K.
+In addition, vertical mixing is enhanced in unstable and humid lower-tropospheric conditions, which reduces the amount of shallow clouds.
 
-Because the model is free-running, weather and climate oscillations (such as
-the El Niño--Southern Oscillation) are not expected to be equivalent to reality
-at the same time and place. To compare with the observations collected in
-different years (2010--2021, inclusive), we compared the model output with
-observations at the same time of year and geographical location, as determined
-for each data point such as a lidar profile or a radiosonde launch.
+Because the analyzed ICON simulation was free-running (years 2021--2024, inclusive), weather and climate oscillations (such as the El Niño--Southern Oscillation) are not expected to be equivalent to reality at the same time and place.
+To compare with the observations collected during a different time period (years 2010--2021, inclusive), we compared the model output with observations at the same time of year and geographical location, as determined for each data point, such as a lidar profile or a radiosonde launch.
+In the ALCF, this was done using the \emph{override\_year} option (\url{https://alcf.peterkuma.net/documentation/cli/cmd_model.html}).
+For radiosonde profiles, the same mapping of time was done.
+That is, when selecting an equivalent profile from the model, the time of the profile was changed so that the time relative to the start of the year was preserved, but the year was changed to one of the four years available in the model data.
+Thus, for every radiosonde launch, there were four equivalent model profiles.
+The geographical location was kept the same.
+We discuss briefly the implications of comparing the observations with a free-running model in Section~\ref{sec:limitations}.
 
@@
 
-The Modern-Era Retrospective analysis for Research and Applications, Version 2
-(MERRA-2) is a reanalysis produced by the Global Modeling and Assimilation
-Office at the NASA Goddard Space Flight Center \citep{gelaro2017}.  It uses
-version 5.12.4 of the Goddard Earth Observing System (GEOS) atmospheric model
-\citep{rienecker2008,molod2015}. Non-convective clouds (condensation,
-autoconversion, and evaporation) are parametrised using a prognostic scheme
-\citep{bacmeister2006}, and sub-grid cloud fraction is determined using total
-water distribution and a critical relative humidity threshold. The reanalysis
-output analysed here is available at a spatial resolution of 0.5° of latitude
-and 0.625° of longitude, which is about 56 km in the North--South direction and
-35 km in the East--West direction at 60°S. The number of vertical model levels
-is 72. Here, we use the following products: 1-hourly instantaneous 2D
-single-level diagnostics (M2I1NXASM) for 2-m temperature and humidity; 3-hourly
-instantaneous 3D assimilated meteorological fields (M2I3NVASM) for cloud
-quantities, pressure, and temperature; 1-hourly average 2D surface flux
-diagnostics (M2T1NXFLX) for precipitation; and 1-hourly average 2D radiation
-diagnostics (M2T1NXRAD) for radiation quantities \citep{merra2}.
+The Modern-Era Retrospective analysis for Research and Applications, Version 2 (MERRA-2) is a reanalysis produced by the Global Modeling and Assimilation Office at the NASA Goddard Space Flight Center \cite{gelaro2017}.
+It uses version 5.12.4 of the Goddard Earth Observing System (GEOS) atmospheric model \cite{rienecker2008,molod2015}.
+Non-convective clouds (condensation, autoconversion, and evaporation) are parameterized using a prognostic scheme \cite{bacmeister2006}, and sub-grid cloud fraction is determined using total water distribution and a critical relative humidity threshold.
+The reanalysis output analyzed here is available at a spatial resolution of 0.5° of latitude and 0.625° of longitude, which is about 56 km in the North--South direction and 35 km in the East--West direction at 60°S.
+The number of vertical model levels is 72.
+Here, we use the following products: 1-hourly instantaneous 2D single-level diagnostics (M2I1NXASM) for 2-m temperature and humidity; 3-hourly instantaneous 3D assimilated meteorological fields (M2I3NVASM) for cloud quantities, pressure, and temperature; 1-hourly average 2D surface flux diagnostics (M2T1NXFLX) for precipitation; and 1-hourly average 2D radiation diagnostics (M2T1NXRAD) for radiation quantities \cite{merra2}.
 
@@
 
-ERA5 \citep{era5} is a reanalysis produced by ECMWF.  It is based on a
-numerical weather prediction model IFS version CY41R2. It uses the
-\cite{tiedtke1993} prognostic cloud scheme and \cite{forbes2014} for
-mixed-phase clouds. The horizontal resolution is 0.25° in latitude and
-longitude, which is about 28 km in the North--South direction and 14 km in the
-East--West direction at 60°S.  Internally, the model uses 137 vertical levels.
-Here, we use output at 1-hourly instantaneous time intervals, except for
-radiation quantities, which are accumulations (from these we calculate daily
-means).  Vertically resolved quantities are made available on 37 pressure
-levels.
+ERA5 \cite{era5} is a reanalysis produced by the ECMWF.
+It is based on a numerical weather prediction model IFS version CY41R2.
+It uses the \citeA{tiedtke1993} prognostic cloud scheme and \citeA{forbes2014} for mixed-phase clouds.
+The horizontal resolution is 0.25° in latitude and longitude, which is about 28~km in the North--South direction and 14~km in the East--West direction at 60°S.
+Internally, the model uses 137 vertical levels.
+Here, we use output at 1-hourly instantaneous time intervals, except for radiation quantities, which are accumulations (from these we calculate daily means).
+Vertically resolved quantities are made available on 37 pressure levels.
 
 \subsection{CERES}
+\label{sec:ceres}
 
-TOA radiation quantities are taken from the CERES instruments onboard the Terra
-and Aqua satellites \citep{wielicki1996,loeb2018}. In our analysis we used the
-adjusted all sky SW and LW upwelling fluxes at TOA from the synoptic TOA and
-surface fluxes and clouds 1 degree daily edition 4A product
-(CER\_SYN1deg-Day\_Terra-Aqua-MODIS\_Edition4A)
-\citep{doelling2013,doelling2016}.
+TOA radiation quantities are taken from the CERES instruments onboard the Terra and Aqua satellites \cite{wielicki1996,loeb2018}.
+In our analysis, we used the adjusted all-sky SW and LW upwelling fluxes at TOA from the synoptic TOA and surface fluxes and clouds 1-degree daily edition 4A product (CER\_SYN1deg-Day\_Terra-Aqua-MODIS\_Edition4A) \cite{doelling2013,doelling2016}.
 
-Radiation calculations presented in the results (Section \ref{sec:results})
-were completed such that they always represent daily means in order to be
-consistent with the CERES SYN1deg data. Therefore, every instantaneous profile
-in the simulated lidar data was assigned a daily mean radiation value
-corresponding to the day (in the Coordinated Universal Time; UTC). In turn, the
-average radiation during the entire voyage or station observation period were
-calculated as the average of the profile values. In the observed lidar data,
-the daily mean radiation value was taken from the spatially and temporally
-co-located CERES SYN1deg data for the day (in UTC). The voyage or station
-average was calculated in the same way.
+Radiation calculations presented in the results (Section~\ref{sec:results}) were completed such that they always represent daily means in order to be consistent with the CERES SYN1deg data.
+Therefore, every instantaneous profile in the simulated lidar data was assigned a daily mean radiation value corresponding to the day (in the Coordinated Universal Time; UTC).
+In turn, the average radiation during the entire voyage or station observation period was calculated as the average of the profile values.
+In the observed lidar data, the daily mean radiation value was taken from the spatially and temporally co-located CERES SYN1deg data for the day (in UTC).
+The voyage or station average was calculated in the same way.
 
@@
 \caption{
-Artificial neural network (ANN) for prediction of precipitation in lidar
-backscatter. \textbf{(a)} Diagram showing the TensorFlow structure of the ANN,
-\textbf{(b)} randomly selected example samples of near-surface backscatter in
-four categories (clear, fog, rain, and snow), as determined by coincident
-human-performed weather observations, \textbf{(c)} receiver operating
-characteristic diagram of the ANN, \textbf{(d)} examples of 10-day time series
-of human-observed (`HUM') and predicted precipitation based on an ANN trained
-on all voyages (`ANN') and all voyages except for the shown voyage (`ANN2')
-during three randomly selected voyages with the available data. Here, by
-`randomly selected' we mean selected from the top of a permutation generated by
-a pseudo-random number generator to prevent authors' bias in the selection.
+Artificial neural network (ANN) for prediction of precipitation in lidar backscatter.
+\textbf{(a)} Diagram showing the TensorFlow structure of the ANN, \textbf{(b)} randomly selected example samples of near-surface backscatter in four categories (clear, fog, rain, and snow), as determined by coincident manual weather observations, \textbf{(c)} receiver operating characteristic diagram of the ANN, \textbf{(d)} examples of 10-day time series of human-observed (``HUM'') and predicted precipitation based on an ANN trained on all voyages (``ANN'') and all voyages except for the shown voyage (``ANN2'') during three randomly selected voyages with the available data.
+Here, by ``randomly selected,'' we mean selected from the top of a permutation generated by a pseudo-random number generator to prevent authors' bias in the selection.
 }
@@
 
-\subsection{Precipitation identification using machine learning}
+\subsection{Precipitation Identification Using Machine Learning}
 \label{sec:ann}
 
-Precipitation can cause strong enough lidar backscattering to be recognised as
-clouds by the threshold-based cloud detection method used in the ALCF. This is
-undesirable as equivalent precipitation backscatter is not included in the
-simulated lidar profiles due to the absence of required fields in the ICON model
-output and the reanalysis data (the liquid and ice precipitation mass mixing
-ratios). The required radiation calculations for precipitation are also
-currently not implemented in the ALCF, but are a planned future
-addition.  In order to achieve a fair comparison of observations with model
-output, we exclude observed and simulated lidar profiles with precipitation
-either manually or using an automated method. It is relatively difficult to
-distinguish precipitation backscatter from cloud backscatter in lidar
-observations, especially when only one wavelength channel and no polarised
-channel are available. In models, the same can be accomplished relatively
-easily by excluding profiles exceeding a certain surface precipitation flux. In
-the observations, using precipitation flux measurements from rain gauges can be
-very unreliable on ships due to ship movement, turbulence caused by nearby ship
-structures, and sea spray. Our analysis of rain gauge data from the RV
-\emph{Tangaroa} showed large discrepancies between the rain gauge time series
-and human-performed synoptic observations, as well as large inconsistencies in
-the rain gauge time series. Human-performed observations of precipitation
-presence or absence are expected to be reliable but only cover a limited set of
-times. Therefore, it was desirable to implement a method of detecting
-precipitation from observed backscatter profiles alone.
+Precipitation can cause strong enough lidar backscattering to be recognized as clouds by the threshold-based cloud detection method used in the ALCF.
+This is undesirable if equivalent precipitation backscatter is not included in the simulated lidar profiles.
+It was not possible to include precipitation simulation in the ALCF due to the absence of required fields in the ICON model output and the reanalysis data (the liquid and ice precipitation mass mixing ratios).
+The required radiation calculations for precipitation are also currently not implemented in the ALCF, even though this is a planned future addition.
+In order to achieve a fair comparison of observations with model output, we exclude observed and simulated lidar profiles with precipitation, either manually or using an automated method.
+It is relatively difficult to distinguish precipitation backscatter from cloud backscatter in lidar observations, especially when only one wavelength channel and no polarized channel are available.
+In models, the same can be accomplished relatively easily by excluding profiles exceeding a certain surface precipitation flux.
+In the observations, using precipitation flux measurements from rain gauges can be very unreliable on ships due to ship movement, turbulence caused by nearby ship structures, and sea spray.
+Our analysis of rain gauge data from the RV \emph{Tangaroa} showed large discrepancies between the rain gauge time series and human-performed synoptic observations, as well as large inconsistencies in the rain gauge time series.
+Human-performed observations of precipitation presence or absence are expected to be reliable but only cover a limited set of times.
+Therefore, it was desirable to implement a method of detecting precipitation from observed backscatter profiles alone.
 
-On the RV \emph{Polarstern} voyages, regular manual synoptic
-observations were available and included precipitation presence or absence and
-type. We used this dataset to train a convolutional artificial neural network
-(ANN) to recognise profiles with precipitation from lidar backscatter data (Fig.
-\ref{fig:ann}a), implemented in the TensorFlow ANN framework
-\citep{tensorflow}. Samples of short time intervals (10 min) of near-surface
-lidar backscatter (0–250 m) were classified as clear, rain, snow, and fog,
-using the synoptic observations as a training dataset (Fig.  \ref{fig:ann}b).
-From these, a binary, mutually exclusive classification of profiles as
-precipitating (rain or snow) or dry (clear or fog) was derived. For detecting
-model and reanalysis precipitation, we used a fixed threshold for surface
-precipitation flux of 0.1 mm h$^{-1}$ (the ANN was not used).
+On the RV \emph{Polarstern} voyages, regular manual synoptic observations were available and included precipitation presence or absence and type.
+We used this dataset to train a convolutional artificial neural network (ANN) to recognize profiles with precipitation from lidar backscatter data (Fig.~\ref{fig:ann}a), implemented in the TensorFlow ANN framework \cite{tensorflow}.
+Samples of short time intervals (10~min) of near-surface lidar backscatter (0–250 m) were classified as clear, rain, snow, and fog, using the synoptic observations as a training dataset (Fig.~\ref{fig:ann}b).
+From these, a binary, mutually exclusive classification of profiles as precipitating (rain or snow) or dry (clear or fog) was derived.
+For detecting model and reanalysis precipitation, we used a fixed threshold for surface precipitation flux of 0.1 mm h$^{-1}$ (the ANN was not used).
 
-The ANN achieved 65\% sensitivity and 87\% specificity when the true positive
-rate (26\%) was made to match observations. The receiver operating
-characteristic curve is shown in Fig. \ref{fig:ann}c. We considered these rates
-satisfactory for the purpose of filtering precipitation profiles. Fig.
-\ref{fig:ann}d shows examples of the predicted precipitation compared to
-human-performed observations. The main ANN (`ANN` in Fig. \ref{fig:ann}) was
-trained on all data, and ancillary ANNs (`ANN2` in Fig \ref{fig:ann}) were
-trained on all data except for each voyage. These were used for testing the
-results relative to each voyage.
+The ANN achieved 65\% sensitivity and 87\% specificity when the true positive rate (26\%) was made to match observations.
+The receiver operating characteristic curve is shown in Fig.~\ref{fig:ann}c.
+We considered these rates satisfactory for the purpose of filtering precipitation profiles.
+Fig.~\ref{fig:ann}d shows examples of the predicted precipitation compared to human-performed observations.
+The main ANN (`ANN` in Fig.~\ref{fig:ann}) was trained on all data, and ancillary ANNs (`ANN2` in Fig.~\ref{fig:ann}) were trained with portions of voyage data excluded to test the results for each voyage.
 
@@
 \caption{
-Lower tropospheric stability (LTS) distribution in \textbf{(a)} ERA5 and
-\textbf{(b)} MERRA-2 calculated for the 31 voyage tracks and one station from
-the highest instantaneous temporal resolution data available. Shown is also the
-chosen dividing threshold of 12 K for conditions weak and strong stability.
+Lower tropospheric stability (LTS) distribution in \textbf{(a)} ERA5 and \textbf{(b)} MERRA-2 calculated for the 31 voyage tracks and one station from the highest instantaneous temporal resolution data available.
+Shown is also the chosen dividing threshold of 12 K for conditions of weak and strong stability.
 }
@@
 
-\subsection{Partitioning by cyclonic activity and stability}
+\subsection{Partitioning by Cyclonic Activity and Stability}
 \label{sec:cyclone-stability}
 
-We partitioned our data into two mutually exclusive subsets by cyclonic
-activity. For this purpose, we used a cyclone tracking algorithm to identify
-extratropical and polar cyclones (ECs and PCs) over the SO in the reanalysis
-and ICON data. We used the open source cyclone tracking package CyTRACK
-\citep{perez-alarcon2024}.  Generally, what constitutes an EC is considered
-relatively arbitrary due to the very large variability of ECs \citep{neu2013}.
-The CyTRACK algorithm uses mean sea level pressure and wind speed
-thresholds as well as tracking across time steps to identify cyclone centres
-and radii in each time step. With this information, we could classify
-geographical areas as either cyclonic or non-cyclonic. Due to a relatively
-small total area covered by cyclones (as identified by the cyclone centre and
-radius), we chose a circle of a double radius (relative to one identified by
-CyTRACK) centred at the cyclone centre as a cyclonic area for every time step
-and cyclone. All other areas were identified as non-cyclonic. For identifying
-cyclones in the observations and the reanalyses, ERA5 pressure and wind fields
-were used as the input to CyTRACK.  This is justified by the fact that the
-large-scale pressure and wind fields in ERA5 are likely sufficiently close to
-reality \cite{mcerlich2023}. For identifying cyclones in ICON, its own pressure and wind fields
-were used as the input to CyTRACK, because the model is free-running, and thus
-the pressure and wind fields are different from reality. Subsetting by
-proximity to cyclones is a relatively crude measure because it does not take
-into account the different sectors of cyclones, which are commonly associated
-with different weather situations. However, this was a choice made for
-simplicity of the analysis, given the amount of data.
+We partitioned our data into two mutually exclusive subsets by cyclonic activity.
+For this purpose, we used a cyclone tracking algorithm to identify extratropical and polar cyclones (ECs and PCs) over the SO in the reanalysis and ICON data.
+We used the open-source cyclone tracking package CyTRACK \cite{perez-alarcon2024}.
+Generally, what constitutes an EC is considered relatively arbitrary due to the very large variability of ECs \cite{neu2013}.
+The CyTRACK algorithm uses mean sea level pressure and wind speed thresholds as well as tracking across time steps to identify cyclone centers and radii in each time step.
+With this information, we could classify geographical areas as either cyclonic or non-cyclonic.
+Due to a relatively small total area covered by cyclones (as identified by the cyclone center and radius), we chose a circle of double the radius (relative to the one identified by CyTRACK) centered at the cyclone center as a cyclonic area for every time step and cyclone.
+All other areas were identified as non-cyclonic.
+For identifying cyclones in the observations and the reanalyses, ERA5 pressure and wind fields were used as the input to CyTRACK.
+This is justified by the fact that the large-scale pressure and wind fields in ERA5 are likely sufficiently close to reality.
+\citeA{mcerlich2023} have shown that wind is simulated well in ERA5 relative to the WindSat polarimetric microwave radiometer measurements \cite{meissner2009}.
+For identifying cyclones in ICON, its own pressure and wind fields were used as the input to CyTRACK, because the model is free-running, and thus the pressure and wind fields are different from reality.
+Subsetting by proximity to cyclones is a relatively crude measure because it does not take into account the different sectors of cyclones, which are commonly associated with different weather situations.
+However, this was a choice made for simplicity of the analysis, given the quantity of data.
 
-In addition to the above, we partitioned our data into two mutually exclusive
-subsets based on LTS, which is derived as the difference between the potential
-temperature at 700 hPa and the surface.  Based on a histogram of LTS in ERA5
-and MERRA-2 calculated at all voyage tracks and stations (Fig.  \ref{fig:lts}),
-we determined a statistically-based dividing threshold of 12 K for weak
-stability (< 12 K) and strong stability (>= 12 K) conditions.
+In addition to the above, we partitioned our data into two mutually exclusive subsets based on LTS, which is derived as the difference between the potential temperature at 700~hPa and the surface.
+Based on a histogram of LTS in ERA5 and MERRA-2 calculated at all voyage tracks and stations (Fig.~\ref{fig:lts}), we determined a statistically-based dividing threshold of 12~K for weak stability ($<$~12~K) and strong stability ($\geq$~12~K) conditions.
 
@@
 \caption{
-Geographical distribution of \textbf{(a, b)} cyclonic days and \textbf{(b, d)}
-strong stability (LTS > 12 K) time steps in \textbf{(a, c)} ERA5 in years
-2010--2013 (inclusive) and \textbf{(b, d)} ICON in model years 2021--2023 (free
-running). Cyclonic days are expressed as a fraction of the number of days with
-cyclonic activity, defined as grid points located within a double radius of any
-cyclone on a given day (UTC), as identified by CyTRACK.
+Geographical distribution of \textbf{(a, b)} cyclonic days and \textbf{(b, d)} strong stability (LTS~$\geq$~12~K) time steps in \textbf{(a, c)} ERA5 in years 2010--2013 (inclusive) and \textbf{(b, d)} ICON in model years 2021--2023 (free running).
+Cyclonic days are expressed as a fraction of the number of days with cyclonic activity, defined as grid points located within a double radius of any cyclone on a given day (UTC), as identified by CyTRACK.
 }
@@
 
-\subsection{Cyclonic activity and stability}
+\subsection{Cyclonic Activity and Stability}
 
-Fig. \ref{fig:cyclone-stability}a, b show a geographical distribution of the
-fraction of cyclonic days as determined by the cyclone tracking algorithm
-applied to the ERA5 reanalysis and ICON data (Section
-\ref{sec:cyclone-stability}). As expected, the strongest cyclonic activity is
-in the high-latitude SO zone, and it is relatively zonally symmetric at all
-latitudes.  The pattern matches reasonably well with \cite{hoskins2005}. While
-both reanalysis and the model agree relatively well, there are clear
-differences particularly in the highest occurrence rate regions -- over the
-Amundsen Sea, where the Amundsen Sea low is located \cite{turner2013} and which
-is more cyclonic in the reanalysis, and around Cape Adare, which is more
-cyclonic in ICON. These differences might, however, stem from the relatively
-short time periods of comparison (4 years) and the fact that the model is
-free-running.
+Fig.~\ref{fig:cyclone-stability}a, b show the geographical distribution of the fraction of cyclonic days as determined by the cyclone tracking algorithm applied to the ERA5 reanalysis and ICON data (Section~\ref{sec:cyclone-stability}).
+As expected, the strongest cyclonic activity is in the high-latitude SO zone and is relatively zonally symmetric at all latitudes.
+The pattern matches reasonably well with \citeA{hoskins2005}.
+While both reanalysis and the model agree within about 8\% in most areas, ICON is prevailingly more cyclonic by about 4\%.
+There are clear differences, particularly in the highest occurrence rate regions, such as around Cape Adare, which is up to 20\% more cyclonic in ICON, and the Weddell and Bellingshausen Seas, where ICON is less cyclonic by up to 10\%.
+These differences could, however, stem from the relatively short time periods of the comparison (4 years) and the fact that the model is free-running.
 
-Fig. \ref{fig:cyclone-stability}c, d show a geographical distribution of the
-conditions of weak and strong stability as determined by the LTS (Section
-\ref{sec:cyclone-stability}). Conditions of weak stability are prevalent in the
-mid-to-high SO (with respect to our SO partitioning; 50--65°S), which might be
-explained by the relatively cold near-surface air overlying the relatively warm
-sea surface. Conditions of strong stability are prevalent elsewhere over the
-SO. The distribution is also less zonally symmetric than the cyclonic activity.
-In the high-latitude SO, the presence of sea ice might have substantial
-stabilising effect \citep{knight2024}. The ERA5 reanalysis is also
-substantially more stable than ICON across the whole region.
+Fig.~\ref{fig:cyclone-stability}c, d show the geographical distribution of the conditions of weak and strong stability as quantified by the LTS (Section~\ref{sec:cyclone-stability}).
+Conditions of weak stability are prevalent in the mid-to-high SO (with respect to our SO partitioning; 50--65°S), which might be explained by the relatively cold near-surface air overlying the relatively warm sea surface.
+Conditions of strong stability are prevalent elsewhere over the SO.
+The distribution is also less zonally symmetric than the cyclonic activity.
+In the high-latitude SO, the presence of sea ice might have a substantial stabilizing effect \cite{knight2024}.
+The ERA5 reanalysis is also substantially more stable than ICON across the whole region.
 
@@
 
-\subsection{Cloud occurrence by height}
+\subsection{Cloud Occurrence by Height}
 \label{sec:cloud-occurrence}
 
-We used the ALCF to derive cloud occurrence by height and the total cloud
-fraction from observations, ICON, ERA5 and MERRA-2 (Fig.
-\ref{fig:cloud-occurrence-panel}). In addition, we aggregated the data sources
-(voyages and stations) by calculating the averages and percentiles of all
-individual profiles, presented in Fig. \ref{fig:cloud-occurrence}. The analysis
-shows that the total cloud fraction (determined as the fraction of profiles
-with clouds at any height in the lidar cloud mask) is underestimated in ICON by
-about 10\% and in the reanalyses by about 20\%. When analysed by height, ICON
-overestimates cloud occurrence below 1 km and underestimates it above, MERRA-2
-underestimates cloud occurrence at all heights by up to about 10\%, especially
-near the surface, and ERA5 simulates cloud occurrence relatively well above 1
-km, but strongly underestimates it near the surface.  We note that fog or
-near-surface clouds are strongly underestimated in the reanalyses (fog and
-clouds are both included in the cloud occurrence).  As shown in Fig.
-\ref{fig:cloud-occurrence-panel}, the biases are relatively consistent across
-the data sources and longitudes. We conclude that the ICON results  the
-observations better than the reanalyses in this metric.
+We used the ALCF to derive cloud occurrence by height and the total cloud fraction from observations, ICON, ERA5, and MERRA-2.
+The results for all campaigns individually are shown in Fig.~\ref{fig:cloud-occurrence-panel}.
+In addition, we aggregated the campaigns by calculating the averages and percentiles of all individual profiles, presented in Fig.~\ref{fig:cloud-occurrence}.
+The analysis in Fig.~\ref{fig:cloud-occurrence} shows that the total cloud fraction (defined as the fraction of profiles with clouds at any height in the lidar cloud mask) is underestimated in ICON by about 10\% and in the reanalyses by about 20\%.
+When analyzed by height, ICON overestimates cloud occurrence below 1 km and underestimates it above; MERRA-2 underestimates cloud occurrence at all heights by up to 10\%, especially near the surface; and ERA5 simulates cloud occurrence relatively well above 1 km but strongly underestimates it near the surface.
+We note that fog or near-surface clouds are strongly underestimated in the reanalyses (fog and clouds are both included in the cloud occurrence).
+Though, as shown in Fig.~\ref{fig:cloud-occurrence-panel}, the biases are relatively consistent across the campaigns and longitudes.
+We therefore conclude that the ICON results match the observations better than the reanalyses in this metric.
 
-For all observations considered (Fig. \ref{fig:cloud-occurrence}a), the data
-show cloud occurrence peaking at the surface, whereas the models show a higher
-peak (at about 500 m). The models generally underestimate the total cloud
-fraction by 10--20\% and show a strong reduction in cloud occurrence near the
-surface, which is not supported by the observations. ICON and ERA5 overestimate
-cloud occurrence at their peak (between 0--1 km). Above 1 km, ICON and MERRA-2
-underestimate cloud occurrence, but ERA5 is accurate to about 3\% or less. The
-exaggerated peak in models is partly supported by the lifting condensation
-level (LCL) distribution, which peaks higher by about 200 m in the models than
-in the observations (at the surface), although this is not very pronounced.
-This is indicative of near-surface relatively humidity being often close to
-saturation in the observations but not in the models.
+For all observations considered (Fig.~\ref{fig:cloud-occurrence} a), the data show cloud occurrence peaking nearly at the surface, whereas the models show a higher peak (at about 500~m).
+The models generally underestimate the total cloud fraction by 10--20\% and show a strong reduction in cloud occurrence near the surface, which is not identified in the observations.
+ICON and ERA5 overestimate cloud occurrence at their peak (between 0 and 1~km).
+Above 1~km, ICON and MERRA-2 underestimate cloud occurrence, but ERA5 is more accurate within 3\%.
+The exaggerated peak in models is partly explained by the lifting condensation level (LCL) distribution, which peaks about 200~m higher in the models than in the observations (nearly at the surface), although this is not very pronounced.
+This is indicative of near-surface relative humidity being often close to saturation in the observations but not in the models.
 
-When subsetted by latitude (Fig.  \ref{fig:cloud-occurrence}b, c), we see that
-the low-latitude SO zone displays a stronger peak of cloud occurrence near the
-surface than the high-latitude SO zone, and this could be because higher
-latitudes have less stable atmospheric profiles. The low- and high-latitude SO
-zones show similar biases in models as in the general case, but ERA5 does not
-overestimate the peak in the low-latitude SO zone (near-surface cloud
-occurrence is still strongly underestimated).
+When subsetted by latitude (Fig.~\ref{fig:cloud-occurrence} b, c), we see that the low-latitude SO zone displays a stronger peak of cloud occurrence near the surface than the high-latitude SO zone, and this could be because higher latitudes have less stable atmospheric profiles.
+The low- and high-latitude SO zones show similar biases in models as in the general case, but ERA5 does not overestimate the peak in the low-latitude SO zone (near-surface cloud occurrence is still strongly underestimated).
 
-When subsetted by cyclonic and non-cyclonic situations (Fig.
-\ref{fig:cloud-occurrence}d, e), we see that the cyclonic situations have a
-larger amount of observed cloudiness, including peak and total cloud fraction,
-both by about 7\%.  In the cyclonic situations, the model vertical profiles of
-cloud occurrence compare well with observations, but they peak higher by about
-200 m and stronger by about 8\%. The reanalyses still tend to underestimate
-cloud occurrence above 1 km by about 5\% and near the surface by about 14\%.
-Non-cyclonic situations are similar to the general case, partially also because
-they form the majority of cases.
+When subsetted by cyclonic and non-cyclonic situations (Fig.~\ref{fig:cloud-occurrence} d, e), we see that the cyclonic situations have a larger amount of observed cloudiness, including peak and total cloud fraction, both by about 7\%.
+In the cyclonic situations, the model vertical profiles of cloud occurrence compare well with observations, but their peak occurs higher by about 200 m and larger by about 8\%.
+The reanalyses still tend to underestimate cloud occurrence above 1 km by about 5\% and near the surface by about 14\%.
+Non-cyclonic situations are similar to the general case, partially because they form the majority of cases.
 
-When subsetted by conditions of weak and strong stability (Fig.
-\ref{fig:cloud-occurrence}f, g), as defined in Section
-\ref{sec:cyclone-stability}, we see that in situations of strong stability
-cloud occurrence peaks strongly at the surface in observations, compared to
-situations of weak stability, where the peak is more diffuse between 0 and 1
-km.  It is work mentioning that conditions of strong stability might be
-associated with the formation of advection fog, such as in situation of warm
-air advection from the north over colder sea surface, thus inducing fog
-formation by cooling of the warm and humid air by the cold surface.  In
-situations of strong stability, the models have smaller biases than in weak
-stability, with overestimated peak by up to 12\%, underestimated cloud
-occurrence above 1 km by up to 5\% and underestimated cloud occurrence near the
-surface by about 11\%.  In situations of weak stability, the bias in ICON is
-very pronounced, with a much stronger peak at about 500 m, ERA5 underestimates
-cloud occurrence below 1 km (especially near the surface), and MERRA-2
-underestimates cloud occurrence even more strongly.
+When subsetted by conditions of weak and strong stability (Fig.~\ref{fig:cloud-occurrence} f, g), as defined in Section~\ref{sec:cyclone-stability}, we see that in situations of strong stability, cloud occurrence peaks strongly near the surface in observations, compared to situations of weak stability, where the peak is spread more uniformly between 0 and 1~km.
+It is worth mentioning that conditions of strong stability might be associated with the formation of advection fog, such as in situations of warm air advection from the north over a colder sea surface, thus inducing fog formation by cooling of the warm and humid air by the cold surface.
+In situations of strong stability, the models have smaller biases than in weak stability, with an overestimated peak by up to 12\%, underestimated cloud occurrence above 1~km by up to 5\%, and underestimated cloud occurrence near the surface by about 11\%.
+In situations of weak stability, the bias in ICON is very pronounced, with a much larger peak in cloud occurrence at about 500~m; ERA5 underestimates cloud occurrence below 1~km (especially near the surface); and MERRA-2 underestimates cloud occurrence even more strongly.
 
-In all situations, even when the models overestimate cloud occurrence at some
-altitudes, they always substantially underestimate the total cloud fraction.
-ICON can be generally characterised as substantially overestimating cloud
-occurrence below 1 km and underestimating above, underestimating the total
-cloud fraction, and showing greatest biases in conditions of weak stability and
-non-cyclonic conditions. It also shows a peak of cloud occurrence at higher
-altitude than observations (500 m vs. near the surface), and correspondingly,
-its LCL tends to be higher. MERRA-2 can be generally characterised as
-underestimating cloud occurrence at nearly all altitudes as well as the total
-cloud fraction, but mostly above and below 500 m (the peak at 500 m is
-well-represented). MERRA-2 displays the largest errors relative to observations
-in the low-latitude SO zone and in situations of weak stability. ERA5 can be
-generally characterised as representing cloud occurrence correctly above about
-1--1.5 km, overestimating below, but underestimating near-surface cloud
-occurrence (0--500 m). The total cloud fraction is strongly underestimated in
-all situations. ERA5 has a tendency towards underestimation in the low-latitude
-SO zone and situations of weak stability; conversely, overestimating in the
-high-latitude SO zone and conditions of strong stability.
+In all situations, even in cases where the models overestimate cloud occurrence at some altitudes, they always substantially underestimate the total cloud fraction.
+ICON can be generally characterized as substantially overestimating cloud occurrence below 1 km and underestimating above, underestimating the total cloud fraction, and showing the greatest biases in conditions of weak stability and non-cyclonic conditions.
+ICON also has a peak cloud occurrence at higher altitudes than observations (500~m vs.
+near the surface), and correspondingly, its LCL tends to be higher.
+MERRA-2 can be generally characterized as underestimating cloud occurrence at nearly all altitudes as well as the total cloud fraction, but mostly above and below 500~m (the peak at 500~m is well represented).
+MERRA-2 displays the largest errors relative to observations in the low-latitude SO zone and in situations of weak stability.
+ERA5 can be generally characterized as representing cloud occurrence correctly above about 1.5~km, overestimating between 500~m and 1~km, but underestimating near-surface cloud occurrence (0--500~m).
+The total cloud fraction is strongly underestimated in all situations.
+ERA5 has a tendency towards underestimation in the low-latitude SO zone and situations of weak stability; conversely, it overestimates in the high-latitude SO zone and conditions of strong stability.
 
@@
 \caption{
-Cloud occurrence by height calculated as the average of all voyages and
-stations and lifting condensation level (LCL) distribution. The LCL is derived
-from radiosonde profiles and equivalent model profiles, which were not
-available for all voyages and times. The total cloud fraction (CF), average
-shortwave (SW), and longwave (LW) and the relative frequency of occurrence
-(RFO) are shown. The bands are the 16$^\mathrm{th}$--84$^\mathrm{th}$
-percentile calculated from the set of all voyages and stations.
+Cloud occurrence by height calculated as the average of all voyages and stations and lifting condensation level (LCL) distribution.
+The LCL is derived from radiosonde profiles and equivalent model profiles, which were not available for all voyages and times.
+The total cloud fraction (CF), average shortwave (SW), and longwave (LW) and the relative frequency of occurrence (RFO) are shown.
+The bands are the 16$^\mathrm{th}$--84$^\mathrm{th}$ percentile, calculated from the set of all voyages and stations.
 }
@@
 
-\subsection{Cloud cover}
+\subsection{Top of Atmosphere Radiation}
+
+In Fig.~\ref{fig:cloud-occurrence}, we also display the mean outgoing shortwave and longwave top-of-atmosphere radiation, whose calculation is described in Section~\ref{sec:ceres}.
+In observations, these come from daily mean CERES measurements averaged over the voyage tracks or a station location, whereas in the models they come from daily means of TOA radiation in the model output averaged over the same location and time periods.
+In the free-running ICON model, the time period is mapped onto the available years, as explained in Section~\ref{sec:icon}.
+
+In the general case (Fig.~\ref{fig:cloud-occurrence}a), ICON underestimates the outgoing SW radiation by 26 Wm$^{-2}$, and the MERRA-2 and ERA5 reanalyses overestimate it by 6 and 14 Wm$^{-2}$, respectively.
+While in ICON, this is in line with the underestimated total cloud fraction of 10\%, in the reanalyses this result can not be explained by the underestimated total cloud fraction of about 20\%.
+The likely explanation is an overestimated cloud albedo, compensating for the lack of cloud area.
+
+We note that the radiative transfer calculations used in the lidar simulator mean that the impact of both cloud phase and cloud fraction are convolved to produce the cloud mask.
+Therefore, the cloud occurrence is not affected by any cloud phase biases as long as the cloud is optically thick enough to be detected, and the laser signal is not too attenuated.
+However, a combination of underestimated total cloud fraction and overestimated outgoing SW at TOA is indicative of an overestimated cloud albedo due to either cloud liquid and ice water content, cloud phase, droplet or ice crystal size distribution, shape or orientation of ice crystals, or cloud overlap.
+
+In contrast, LW radiation has much smaller biases than SW radiation, which is expected due to the prevailing low-level clouds having similar temperatures to the surface.
+In ICON, the outgoing LW radiation is overestimated by 8\%, which could be caused by an underestimated total cloud fraction exposing a larger sea surface area to cooling to space, which is typically warmer than the atmospheric temperature at 0--2~km, where most of the clouds are located.
+In the MERRA-2 and ERA5 reanalyses, the LW biases are also slightly positive, 4 and 7~Wm$^{-2}$, respectively.
+This is again in line with the underestimated total cloud fraction by about 20\%.
+However, if the clouds are too optically thick, as expected from the SW results, this might also provide a compensating effect, in which too small a cloud area is counteracted by greater thermal emissivity, thus reducing the outgoing LW radiation more relative to thinner clouds.
+For thin clouds, the outgoing TOA LW radiation originates both from the warmer surface (partly blocked by the clouds) and the clouds, whereas for thick clouds, the outgoing TOA LW radiation originates mostly from the colder-than-surface cloud tops.
+
+In all the subsets (Fig.~\ref{fig:cloud-occurrence}b--g), the same type of biases are observed, namely the outgoing SW radiation is underestimated in ICON and overestimated in MERRA-2 and ERA5, and the outgoing LW radiation is overestimated in all the models.
+Even though the total cloud fraction is lower by 7\% over the high-latitude SO than the low-latitude SO, the outgoing SW radiation is much greater by 41~Wm$^{-2}$, implying a much greater cloud albedo over the high-latitude SO.
+The ICON model output displays the same contrast between these two regions in the total cloud fraction and SW radiation, but the outgoing SW radiation difference between the regions is much smaller (16~Wm$^{-2}$).
+The reanalyses do not display this contrast between the regions.
+The physical reason for this might be that the prevalence of fog or low-level clouds over the low-latitude SO and their relative lack over the high-latitude SO in observations is not reproduced in the models (Fig.~\ref{fig:cloud-occurrence}b--c).
+
+\subsection{Cloud Cover}
 \label{sec:cloud-cover}
 
-We also analysed the daily cloud cover (total cloud fraction) distribution.
-This is a measure of cloudiness, irrespective of height, calculated over the
-course of a day (UTC). A cloud detected at any height means that the lidar
-profile was classified as cloudy; otherwise, it was classified as clear sky.
-When all profiles in a day are taken together, the cloud cover for the day is
-defined as the fraction of cloudy profiles in the total number of profiles,
-expressed in oktas (multiples of 1/8).
+We also analyzed the daily cloud cover (total cloud fraction) distribution.
+This is a measure of cloudiness, irrespective of height, calculated over the course of a day (UTC).
+A cloud detected at any height means that the lidar profile was classified as cloudy; otherwise, it was classified as a clear sky.
+When all profiles in a day are taken together, the cloud cover for the day is defined as the fraction of cloudy profiles in the total number of profiles, expressed in oktas (multiples of 1/8).
+The same calculation is done for the lidar observations as for the simulated lidar profiles.
+We use the term ``okta'' independently of its use in instantaneous synoptic observations, and here it simply means 1/8 (12.5\%) of the daily cloud cover.
 
-In Fig.  \ref{fig:cloud-cover} we show the results for the same subsets of data
-as in Section \ref{sec:cloud-occurrence}. Observations display the highest
-proportion of high cloud cover values (5--8 oktas), peaking at 7 oktas. This
-pattern is not represented by ICON or either reanalyses.  While ICON is closest
-to matching the observed distribution, it tends to be 1 okta clearer than the
-observations, peaking at 6 oktas, and substantially underestimating days with 8
-oktas.  Overall, the reanalyses show results similar to each other,
-underestimating cloud cover by about 2 oktas and strongly underestimating days
-with 7 and 8 oktas. Of the two reanalyses, MERRA-2 has slightly higher cloud
-cover then ERA5, by about 6\% at 6 octas, which makes it more consistent with
-observations.
+In Fig.~\ref{fig:cloud-cover} we show the results for the same subsets of data as in Section~\ref{sec:cloud-occurrence}.
+Observations display the highest proportion of high cloud cover values (5--8~oktas), peaking at 7~oktas.
+This pattern is not represented by ICON or either reanalysis.
+While ICON is closest to matching the observed distribution, it tends to be 1~okta clearer than the observations, peaking at 6~oktas, and substantially underestimating days with 8~oktas.
+Overall, the reanalyses show results similar to each other, underestimating cloud cover by about 2~oktas and strongly underestimating days with 7 and 8~oktas.
+Of the two reanalyses, MERRA-2 has slightly higher cloud cover than ERA5, by about 6\% at 6 octas, which makes it more consistent with observations.
 
-When analysed by subsets, observations in the cyclonic subset show the highest
-cloud cover, with 8 oktas occurring on one half of such days (Fig.
-\ref{fig:cloud-cover}d).  This sensitivity to cyclonic conditions is not
-observed in ICON or the reanalyses. Interestingly, clear sky days (0 oktas)
-also have a local maximum peaking at about 15\% in this subset.  When we
-contrast the low- and high-latitude zones, we see that the high-latitude zone
-tends to have greater cloud cover, peaking at 8 oktas (Fig.
-\ref{fig:cloud-cover}c). The high-latitude zone also has almost no clear sky or
-small cloud cover cases (0--4 oktas). ICON and the reanalyses represent this
-characteristic of the distribution well for 0--3 oktas, but otherwise show
-biases similar to the general case. One of the greatest biases is present in
-ERA5 in the subset of weak stability, in which ERA5 peaks at 3 oktas, while the
-observations peak at 7 oktas and show negligible cloud cover below 5 oktas.
+When analyzed by subsets, observations in the cyclonic subset show the highest cloud cover, with 8~oktas occurring on one half of such days (Fig.~\ref{fig:cloud-cover}d).
+This sensitivity to cyclonic conditions is not observed in ICON or the reanalyses.
+Interestingly, clear sky days (0~oktas) also have a local maximum peaking at about 15\% in this subset.
+When we contrast the low- and high-latitude zones, we see that the high-latitude zone tends to have greater cloud cover, peaking at 8~oktas (Fig.~\ref{fig:cloud-cover}c).
+The high-latitude zone also has almost no clear sky or small cloud cover cases (0--4~oktas).
+ICON and the reanalyses represent this characteristic of the distribution well for 0--3~oktas, but otherwise show biases similar to the general case.
+One of the greatest biases is present in ERA5 in the subset of weak stability, in which ERA5 peaks at 3~oktas, while the observations peak at 7~oktas and show negligible cloud cover below 5~oktas.
 
@@
 \caption{
-Daily total cloud fraction histograms calculated as the average of all voyage
-and station histograms. The total cloud fraction of a day (UTC) is calculated
-as a fraction of cloudy (based on the cloud mask) observed (OBS) or simulated
-lidar profiles. The models and subsets are as in Fig.
-\ref{fig:cloud-occurrence}.
+Daily total cloud fraction histograms calculated as the average of all voyage and station histograms.
+The total cloud fraction of a day (UTC) is calculated as a fraction of cloudy (based on the cloud mask) observed (OBS) or simulated lidar profiles.
+The models and subsets are as in Fig.~\ref{fig:cloud-occurrence}.
 }
@@
 \caption{
-Virtual potential temperature ($\theta_v$) and relative humidity (RH)
-determined from radiosonde launches and co-located profiles in ICON, ERA5, and
-MERRA-2 in subsets as in Fig. \ref{fig:cloud-occurrence}.  The solid lines are
-the average calculated from the averages of every individual voyage and
-station. The bands span the 16$^\mathrm{th}$--84$^\mathrm{th}$ percentiles
-calculated from the distribution of the voyage and station averages. Shown is
-also the relative frequency of occurrence and the number of profiles in each
-subset.
+Virtual potential temperature (virt.\ pot.\ temp.; $\theta_v$) and relative humidity (RH) determined from radiosonde launches and co-located profiles in ICON, ERA5, and MERRA-2 in subsets as in Fig.~\ref{fig:cloud-occurrence}.
+The solid lines are the average calculated from the averages of every individual voyage and station.
+The bands span the 16$^\mathrm{th}$--84$^\mathrm{th}$ percentiles, calculated from the distribution of the voyage and station averages.
+Shown is also the relative frequency of occurrence and the number of profiles in each subset.
 }
@@
 
-\subsection{Thermodynamic profiles}
+\subsection{Thermodynamic Profiles}
 
-In order to link the cloud biases to the local physical conditions, we analysed
-about 2300 radiosonde profiles south of 40°S from the 24 RV \emph{Polarstern}
-voyages, MARCUS, NBP1704, TAN1702, and TAN1802. Spatially and temporally
-colocated profiles were taken from ICON and the reanalyses.  Because the time
-period covered by the ICON model output (2021--2024) was different from the
-time period covered by the observations (2010--2021), when comparing with the
-model, we first had to remap the observation time to model time by taking the
-same time relative to the start of the year. Consequently, we also had four
-virtual/model profiles (one for each year of 2021--2024) for each observed
-profile.  The profiles were partitioned into the same subsets as above
-(Sections \ref{sec:cloud-occurrence} and \ref{sec:cloud-cover}).  Apart from
-relative humidity, we focus on comparing virtual potential temperature
-($\theta_v$) due to its role in low-level tropospheric stability, being one of
-the primary factors affecting shallow convection and the associated low-level
-cloud formation and dissipation. The observed and model profiles of virtual
-potential temperature are shown in Fig. \ref{fig:potential-temperature}.
+In order to examine the potential link in the cloud biases to the local physical conditions, we analyzed about 2300 radiosonde profiles south of 40°S from the 24 RV \emph{Polarstern} voyages, MARCUS, NBP1704, TAN1702, and TAN1802.
+Spatially and temporally colocated profiles were taken from ICON and the reanalyses.
+Because the time period covered by the ICON model output (2021--2024) was different from the time period covered by the observations (2010--2021), when comparing with the model, we first had to remap the observation time to model time by taking the same time relative to the start of the year.
+Consequently, we also had four virtual/model profiles (one for each year of 2021--2024) for each observed profile.
+The profiles were partitioned into the same subsets as above (Sections~\ref{sec:cloud-occurrence} and \ref{sec:cloud-cover}).
+We focus on comparing virtual potential temperature ($\theta_v$) due to its role in low-level tropospheric stability, being one of the primary factors affecting shallow convection and the associated low-level cloud formation and dissipation.
+The observed and model profiles of virtual potential temperature are shown in Fig.~\ref{fig:potential-temperature}.
 
-Overall, the mean $\theta_v$ is accurate less than 0.5 K in ICON and MERRA-2,
-being only colder by up to 2 K in the mid-to-high troposphere (less stable) in
-ICON than in observations (Fig. \ref{fig:potential-temperature}a).  Larger
-differences exist, however, in the 40--55°S zone, where ICON is colder by about
-5 K at higher altitudes (Fig.  \ref{fig:potential-temperature}b). In other
-subsets, the bias is relatively small. MERRA-2 is very close to the
-observations, possibly due to a high accuracy of assimilation of this quantity.
-Notably, the variability of virtual potential temperature (as represented by
-the percentiles) is much smaller in ICON than in the observations. This
-indicates that the model's internal variability in the lower-tropospheric
-thermodynamic conditions in the SO is smaller than in reality.
+Overall, the mean $\theta_v$ is accurate to within 0.5~K in ICON and MERRA-2, except for ICON being colder by up to 2.5~K in the mid-to-high troposphere (less stable) (Fig.~\ref{fig:potential-temperature}a).
+Larger differences exist, however, in the 40--55°S zone, where ICON is colder by about 5 K at higher altitudes (Fig.~\ref{fig:potential-temperature}b).
+In other subsets, the bias is relatively small.
+MERRA-2 and ERA5 are very close to the observations, possibly due to data assimilation.
+Notably, the variability of virtual potential temperature (as represented by the percentiles) is much smaller in ICON than in the observations.
+This indicates that the model's internal variability in the lower-tropospheric thermodynamic conditions in the SO is smaller than in reality.
 
-Relative humidity displays much larger biases. In all subsets, ICON is too
-humid in the first 1 km by about 5\% but very accurate above, except for the
-40--55°S zone and conditions of weak stability (Fig.
-\ref{fig:potential-temperature}b, g),  where it is too dry between about 1 and
-3 km. MERRA-2, on the other hand, is more humid than observations at all
-altitudes and in all subsets, by up to about 20\% at 5 km. Even though the mean
-near-surface relative humidity is similar to the observations (Fig.
-\ref{potential-temperature}), the distribution in observation is more spread
-out across both high and low values, and thus observations have a greater
-prevalence of relative humidity close to 100\% and thus LCL located at the
-surface (Fig. \ref{cloud-occurrence}a). In our calculations, LCL is a exclusive
-function of near-surface temperature, near-surface relative humidity and
-surface pressure.
+Relative humidity displays much larger biases.
+In all subsets, ICON is too humid in the first 1~km by about 5\% but very accurate above, except for the 40--55°S zone and conditions of weak stability (Fig.~\ref{fig:potential-temperature}b, g), where it is too dry between about 1 and 3~km.
+MERRA-2, on the other hand, is more humid than observations at all altitudes and in all subsets, by up to about 20\% at~5 km.
+Even though the mean near-surface relative humidity is similar to the observations (Fig.~\ref{fig:potential-temperature}), the distribution in observation is more spread out across both high and low values, and thus observations have a greater prevalence of relative humidity close to 100\% and thus LCL located at the surface (Fig.~\ref{fig:cloud-occurrence}a).
+In our calculations, LCL is an exclusive function of near-surface temperature, near-surface relative humidity, and surface pressure.
 
-\section{Limitations of this study}
+\section{Limitations of this Study}
+\label{sec:limitations}
 
-Let us consider the main limitations of the presented results. The spatial
-coverage of our dataset does not include most parts of the Indian Ocean and
-Pacific Ocean sectors of the SO. Even though climatological features of the SO
-are typically relatively uniform zonally, variations exist, such as those
-related to the Antarctic Peninsula and the southern tip of South America. The
-voyages were mostly undertaken in the Austral summer months and only rarely in
-the winter months, due to the poor accessibility of this region during winter.
-Therefore, our results are likely representative of summer and to a lesser
-extent, spring and autumn conditions.
+Let us consider the main limitations of the presented results.
+The spatial coverage of our dataset does not include most parts of the Indian Ocean and Pacific Ocean sectors of the SO.
+Even though climatological features of the SO are typically relatively uniform zonally, variations exist, such as those related to the Antarctic Peninsula and the southern tip of South America.
+The voyages were mostly undertaken in the Austral summer months and only rarely in the winter months, due to the poor accessibility of this region during winter.
+Therefore, our results are likely representative of summer and, to a lesser extent, spring and autumn conditions.
 
-The time period of ICON is relatively short, with only four full years of
-simulation available. Moreover, the simulation is free-running and
-ocean-coupled, which means that observations had to be temporally mapped to
-this time period (at the same time relative to the start of the year) for the
-comparison. For these reasons, one can expect the results to be slightly
-different due to reasons unrelated to model biases, such as different weather
-conditions, partially accounted for by the cyclone and stability subsetting,
-and the phase of climate oscillations such as the ENSO in the observations and
-the model.
+The time period of ICON is relatively short, with only four full years of simulations available.
+Moreover, the simulation is free-running and ocean-coupled, which means that observations had to be temporally mapped to this time period (at the same time relative to the start of the year) for the comparison.
+For these reasons, one can expect the results to be slightly different due to reasons unrelated to model biases, such as different weather conditions, partially accounted for by the cyclone and stability subsetting, and the phase of climate oscillations such as the ENSO in the observations and the model.
+The interannual variability in cloud occurrence in ICON can be seen in Fig.~\ref{fig:cloud-occurrence-panel}, where each year in ICON is represented by a separate line.
+The interannual variability tends to be substantially smaller than the biases and thus is unlikely to have a strong impact on the main findings.
 
-Ground-based lidar observations are affected by attenuation by thick cloud
-layers, and for this reason the results are most representative of boundary
-layer clouds, while higher-level clouds are only occasionally visible to the
-lidar when boundary layer clouds are not present. Ground-based lidar
-observations can be regarded as superior to satellite lidar observations for
-low-level clouds, which are predominant in this region, while mid- and
-high-level clouds are better sampled by satellite observations
-\citep{mcerlich2021}.
+Ground-based lidar observations are affected by attenuation by thick cloud layers, and for this reason the results are most representative of boundary layer clouds, while higher-level clouds are only occasionally visible to the lidar when boundary layer clouds are not present.
+Ground-based lidar observations can be regarded as superior to satellite lidar observations for low-level clouds, which are predominant in this region, while mid- and high-level clouds are likely better sampled by satellite observations \cite{mcerlich2021}.
+Near-surface lidar retrievals ($\sim$100~m) are affected by uncertainties related to incomplete overlap, signal saturation (dead time), and after-pulse effect corrections \cite{kuma2021}.
 
-We have attempted to remove lidar profiles with precipitation, which could not
-be properly simulated with the lidar simulator (Section \ref{sec:ann}).
-However, the approach was limited by the relatively low sensitivity of the ANN
-(65\%) and the fact that we had to choose a fixed threshold for surface
-precipitation flux in the model and reanalyses, which might not correspond to
-detection by the ANN applied to observations. Also, we made no attempt to
-remove profiles with precipitation not reaching the surface. The above reasons
-may result in an artificial bias in the comparison, even though we expect this
-to be much smaller than the identified model biases.
+We have attempted to remove lidar profiles with precipitation, which could not be properly simulated with the lidar simulator (Section~\ref{sec:ann}).
+However, the approach was limited by the relatively low sensitivity of the ANN (65\%) and the fact that we had to choose a fixed threshold for surface precipitation flux in the model and reanalyses, which might not correspond to detection by the ANN applied to observations.
+We also made no attempt to remove profiles with precipitation that did not reach the surface.
+The above reasons may result in an artificial bias in the comparison, though we expect this to be much smaller than the identified model biases.
 
-\section{Discussion and conclusions}
+\section{Discussion and Conclusions}
 
-We analysed a total of about 2400 days of lidar and 2300 radiosonde
-observations from 31 voyages/campaigns and a subantarctic station, covering the
-Atlantic, Australian, and New Zealand sectors of the SO over the span of 10
-years. This dataset, together with the use of a ground-based lidar simulator,
-provided a comprehensive basis for evaluating SO cloud and thermodynamic
-profile biases in the GSRM ICON and the ERA5 and MERRA-2 reanalyses. Our
-analysis provides a unique evaluation perspective different from satellite
-observations -- one that we argue is more suitable for evaluating boundary
-layer clouds, which are predominant in this region. Furthermore, we subsetted
-our dataset by low and high latitude bands, cyclonic activity, and stability in
-order to identify how these conditions influence the biases.
+We analyzed a total of about 2400 days of lidar and 2300 radiosonde observations from 31 voyages/campaigns and the Macquarie Island subantarctic station, covering the Atlantic, Australian, and New Zealand sectors of the SO over the span of 10 years.
+This dataset, together with the use of a ground-based lidar simulator, provided a comprehensive basis for evaluating SO cloud and thermodynamic profile biases in the GSRM ICON and the ERA5 and MERRA-2 reanalyses.
+Our analysis provides a unique evaluation perspective different from satellite observations -- one that we argue is more suitable for evaluating boundary layer clouds, which are predominant in this region.
+Furthermore, we subsetted our dataset by low and high latitude bands, cyclonic activity, and stability in order to identify how these conditions influence the biases.
 
-Our main finding corroborates previous findings of large boundary layer cloud
-biases in models and their subsequent effect on the radiative transfer. This
-also applies to the new GSRM ICON, but the biases are generally lower than in
-the reanalyses, despite the reanalyses having the advantage of assimilation of
-the observed meteorological conditions.  The GSRM has, on the other hand, the
-advantage of a much higher spatial resolution and, to a limited extent,
-explicit calculation of traditionally subgrid-scale processes such as
-convection.
+Our main finding corroborates previous findings of large boundary layer cloud biases in models and their subsequent effect on the radiative transfer.
+For example, low- and mid-level clouds in the cold-air sector of cyclones were identified as being responsible for most of the SW bias in \citeA{bodas-salcedo2012}.
+This understanding was refined in \citeA{bodas-salcedo2014}, which highlighted that the SW bias was associated with an incorrectly simulated mid-level cloud regime, which occurred in regions where clouds with tops at mid-level and low-levels occurred.
+Our results align less well with more recent work by \citeA{ramadoss2024}, which shows persistent shortwave radiative biases over the Southern Ocean are associated with incorrect cloud phase representation.
+While \citeA{fiddes2024} suggest biases in the liquid water path are the largest contributor to the cloud radiative bias over the Southern Ocean.
+Our general finding applies to the new GSRM ICON, but the biases are generally lower than in the reanalyses, despite the reanalyses having the advantage of assimilation of the observed meteorological conditions.
+The GSRM has, on the other hand, the advantage of a much higher spatial resolution and, to a limited extent, explicit calculation of traditionally subgrid-scale processes, such as convection.
 
-We show that relative to ERA5, the distribution and strength of cyclonic
-activity over the SO is well represented in ICON, but it displays lower values
-of LTS. The latter is also manifested in the radiosonde profile comparison,
-showing that the virtual potential temperature profiles in ICON are less stable
-than in the observations over low-latitude SO.
+We show that relative to ERA5, the distribution and strength of cyclonic activity over the SO is well represented in ICON, but it displays lower values of LTS.
+The latter is also manifested in the radiosonde profile comparison, showing that the virtual potential temperature profiles in ICON are less stable than in the observations over low-latitude SO.
 
-The 31 voyages and a station show remarkably similar biases in cloud occurrence
-by height in the lidar comparison, which indicates that common underlying
-causes for the biases exist regardless of longitude and season. ICON
-underestimates the total cloud fraction by about 10\%, with an overestimation
-of clouds below 2 km and an underestimation of clouds above 2 km. The
-reanalyses also underestimate the total cloud fraction by about 20\%.  ERA5
-overestimates cloud below 1 km but underestimates near-surface cloud or fog.
-ICON strongly overestimates the peak of cloud occurrence at about 500 m, which
-might be explained by the radiosonde comparison, showing that it is too moist
-at around this height.  Similar to our results, \cite{cesana2022} showed that
-CMIP6 models also tend to underestimate cloud occurrence above 2 km over the
-SO, although their analysis in this case was limited to liquid clouds.
+The 31 voyages and the station show remarkably similar biases in cloud occurrence by height in the lidar comparison, which indicates that common underlying causes for the biases exist regardless of longitude and season.
+ICON underestimates the total cloud fraction by about 10\%, with an overestimation of clouds below 2~km and an underestimation of clouds above 2~km.
+The reanalyses also underestimate the total cloud fraction by about 20\%.
+ERA5 overestimates cloud below 1~km but underestimates near-surface cloud or fog.
+ICON strongly overestimates the peak of cloud occurrence at about 500 m, which might be explained by the radiosonde comparison, showing that it is too moist at around this height.
+Similar to our results, \citeA{cesana2022} showed that CMIP6 models also tend to underestimate cloud occurrence above 2~km over the SO, although their analysis in this case was limited to liquid clouds.
 
-Compared to lidar observations, the daily cloud cover tends to be about 1 okta
-lower in ICON and 2 oktas lower in the reanalyses.  Conditions of weak
-stability are associated with some of the greatest biases, especially in ERA5.
-The models also underestimate the cloud cover very strongly in cyclonic
-conditions, which are very cloudy in the observations (8 oktas), but much less
-so in the models.
+Compared to lidar observations, the daily cloud cover tends to be about 1~okta lower in ICON and 2~oktas lower in the reanalyses.
+Conditions of weak stability are associated with some of the greatest biases, especially in ERA5.
+The models also underestimate the cloud cover very strongly in cyclonic conditions, which are very cloudy in the observations (8~oktas), but much less so in the models.
+Similarly, \citeA{mcerlich2023} found a 40\% underestimation of cloud liquid water in cyclones over the SO in ERA5, despite total column water vapor simulated much more accurately (5\% underestimation).
 
-The radiosonde observations indicate that the LCL is too high in ICON and
-reanalyses, which is probably responsible for the higher peak of clouds in the
-models and the lack of near-surface clouds or fog. The radiosonde comparison,
-however, does not seem to explain cloud biases at higher altitudes.  MERRA-2 is
-too moist at all heights.  ICON also exhibits smaller internal variability than
-the radiosonde observations. Overall, the radiosonde comparison only partially
-explains the identified cloud biases, and other physical causes are likely
-contributing.  This warrants further investigation, especially of
-ocean--atmosphere fluxes, shallow convection, and boundary layer turbulence.
-The lack of parametrised subgrid-scale convection in ICON could be a
-substantial issue even at the 5-km resolution.
+The radiosonde observations indicate that the LCL is too high in ICON and reanalyses, which is probably responsible for the higher peak of clouds in the models and the lack of near-surface clouds or fog.
+The radiosonde comparison, however, does not seem to explain cloud biases at higher altitudes, which is perhaps suggestive of biases in the influence of the liquid water path in the models relative to reality.
+MERRA-2 is too moist at all heights.
+ICON also exhibits smaller internal variability than the radiosonde observations.
+Overall, the radiosonde comparison only partially explains the identified cloud biases, and other physical causes are likely contributing.
+This warrants further investigation, especially of ocean--atmosphere fluxes, shallow convection, and boundary layer turbulence.
+The lack of parameterized subgrid-scale convection in ICON could be a substantial issue even at the 5-km resolution.
 
-The relationship between cloud biases and radiation has a number of notable
-features. Perhaps unsurprisingly, the reanalyses exhibit the too few, too
-bright bias previously identified in models. In our results, this is
-characterised by outgoing TOA SW radiation similar to or higher than in the
-satellite observations, while at the same time total cloud fraction is
-substantially underestimated relative to the ground-based lidar observations.
-This feature seems to be much more pronounced in ERA5 than in MERRA-2. On the
-other hand, this relationship is not present in ICON. This model generally
-predicts smaller outgoing TOA SW radiation and smaller total cloud fraction
-than observations, and the deficit of outgoing TOA SW radiation is
-approximately proportional to the deficit of the total cloud fraction. While
-this might be a welcome feature and an improvement over previous models, it
-does mean that the outgoing TOA SW radiation is overall underestimated instead
-of being compensated by a higher cloud albedo.  This can, of course, lead to
-undesirable secondary effects such as overestimated solar heating of the sea
-surface, among other factors responsible for SO SST biases in climate models
-\citep{zhang2023,luo2023,hyder2018}.  To some extent, the cloud albedo might be
-reduced in the model artifically by the application of an inhomogeneity factor
-to lower cloud liquid water in the radiative transfer calculations (Sec.
+The relationship between cloud biases and radiation has a number of notable features.
+Perhaps unsurprisingly, the reanalyses exhibit the too few, too bright bias previously identified in models.
+In our results, this is characterized by outgoing TOA SW radiation similar to or higher than in the satellite observations, while at the same time total cloud fraction is substantially underestimated relative to the ground-based lidar observations.
+This feature seems to be much more pronounced in ERA5 than in MERRA-2.
+On the other hand, this relationship is not present in ICON.
+This model generally predicts smaller outgoing TOA SW radiation and smaller total cloud fraction than observations, and the deficit of outgoing TOA SW radiation is approximately proportional to the deficit of the total cloud fraction.
+While this might be a welcome feature and an improvement over previous models, it does mean that the outgoing TOA SW radiation is overall underestimated instead of being compensated by a higher cloud albedo.
+This can, of course, lead to undesirable secondary effects such as overestimated solar heating of the sea surface, among other factors responsible for SO SST biases in climate models \cite{zhang2023,luo2023,hyder2018}.
+To some extent, the cloud albedo might be reduced in the model artificially by the application of an inhomogeneity factor to lower cloud liquid water in the radiative transfer calculations (Sec.
 \ref{sec:icon}).
 
-The results imply that SO cloud biases are still a substantial issue even in
-the km-scale resolution ICON model, even though an improvement over the
-lower-resolution reanalyses is notable. More effort is needed to improve the
-model cloud simulations in this understudied region. However, this analysis
-suggests that the transition from models with parametrised convection and
-clouds to storm-resolving models might not solve these biases without
-additional effort.  Evaluation of ocean--atmosphere heat, moisture, and
-momentum fluxes against in-situ observations over the SO and comparison of GSRM
-simulations against large-eddy simulations are two potential avenues for future
-research that could elucidate the physical mechanisms behind the biases, in
-addition to the more common efforts in SO cloud microphysics and precipitation
-evaluation.
+The results imply that SO cloud biases are still a substantial issue even in the km-scale resolution ICON model, even though an improvement over the lower-resolution reanalyses is notable.
+More effort is therefore needed to improve the model cloud simulations in this understudied region.
+However, this analysis suggests that the transition from models with parameterized convection and clouds to storm-resolving models might not solve these biases without additional effort.
+Evaluation of ocean--atmosphere heat, moisture, and momentum fluxes against in-situ observations over the SO and comparison of GSRM simulations against large-eddy simulations are two potential avenues for future research that could elucidate the physical mechanisms behind the biases, in addition to the more common efforts in SO cloud microphysics and precipitation evaluation.
 
-\fontsize{12pt}{14pt}\selectfont
-\section*{Acknowledgements}
+\section*{Open Research Section}
 
-PK and FB, and the nextGEMS project received funding from the European Union’s
-Horizon 2020 research and innovation program under a grant agreement no.
-101003470. FB received funding from the Wenner-Gren Foundation and the Swedish
-e-Science Research Centre.  The work of GM was supported by the United States
-(U.S.) Department of Energy Award DE-SC0021159.  Supercomputing resources were
-provided by the DKRZ (project 1125 ICON-development) and the National Academic
-Infrastructure for Supercomputing in Sweden (allocation 2023/22-202). The data
-collection by the University of Canterbury was funded by the Deep South
-National Science Challenge Clouds and Aerosols project.  Data collection on the
-AA15-16 voyages was funded by the Australian Antarctic Science project (grant
-no.  4292).  We acknowledge the contribution of Thorsten Mauritsen to funding
-acquisition and project management.  We acknowledge the RV \emph{Polarstern}
-datasets provided by the Alfred Wegener Institute and Pangaea, the AA15-16
-dataset provided by the Australian Antarctic Division (AAD) and University of
-Canterbury (UC), the RV \emph{Tangaroa} datasets provided by the National
-Institute of Water and Atmospheric Research and UC, the NBP1704 dataset
-provided by the National Science Foundation, Cooperative Institute for Research
-in Environmental Sciences, University of Colorado and UC, the HMNZSW16 dataset
-provided by the Royal New Zealand Navy and UC, the MARCUS dataset provided by
-ARM and AAD, and the MICRE dataset provided by ARM, the Australian Bureau of
-Meteorology, and AAD.  Technical, logistical, and ship support for MARCUS and
-MICRE were provided by the AAD through Australian Antarctic Science projects
-4292 and 4387, and we thank Steven Whiteside, Lloyd Symonds, Rick van den
-Enden, Peter de Vries, Chris Young, Chris Richards, Andrew Klekociuk, John
-French, Terry Egan, Nick Cartwright, and Ken Barrett for all of their
-assistance.  We thank the scientific staff, the crew, and everyone involved in
-collecting data on the voyages and stations, especially Gert König-Langlo,
-Holger Schmithüsen, Roger Marchand, Peter Guest, Kelly Schick, Jamie Halla, and
-Mike J.  Harvey (†). We thank Loretta Preis for providing additional RV
-\emph{Polarstern} data.  We acknowledge the ICON model output provided by the
-nextGEMS project, Deutscher Wetterdienst, Max-Planck-Institute for Meteorology,
-DKRZ, Karlsruhe Institute of Technology, and Center for Climate Systems
-Modeling; reanalysis dataset ERA5 provided by the Copernicus Climate Change
-Service; MERRA-2 provided by the Global Modeling and Assimilation Office; CERES
-datasets provided by the NASA Langley Atmospheric Science Data Center
-Distributed Active Archive Center; and the Natural Earth dataset provided by
-naturalearthdata.com.  Last but not least, we acknowledge the use of open
-source software Python, Cython \citep{behnel2011}, TensorFlow
-\citep{abadi2016}, Devuan GNU+Linux, parallel \citep{tange2011}, NumPy
-\citep{harris2020}, SciPy \citep{virtanen2020}, Matplotlib \citep{hunter2007},
-cartopy \citep{cartopy}, pyproj, Inkscape, Bash, GNU Fortran, HDF
-\citep{folk1999}, and NetCDF \citep{rew1990}.  We dedicate this study to the
-memory of Mike J.  Harvey, who very substantially contributed to obtaining the
-atmospheric observations on the RV \emph{Tangaroa} voyages used in this study.
+The RV \emph{Polarstern} datasets are openly available on Pangaea (\url{https://pangaea.de}), as listed in Table~\ref{tab:voyage-references}.
+The MARCUS and MICRE datasets are openly available from ARM (\url{https://www.arm.gov}).
+The MERRA-2 data are openly available from the NASA Goddard Earth Sciences (GES) Data and Information Services Center (DISC) (\url{https://disc.gsfc.nasa.gov/datasets?project=MERRA-2}).
+The ERA5 data are openly available from the Copernicus Climate Data Store (CDS) (\url{https://cds.climate.copernicus.eu}).
+The ICON data are available on the Levante cluster of the DKRZ (\url{https://www.dkrz.de/en/systems/hpc/hlre-4-levante}) after registration at \url{https://luv.dkrz.de/register/}.
+The CERES products are openly available from the project website (\url{https://ceres.larc.nasa.gov}) and the NASA Atmospheric Science Data Centre (\url{https://asdc.larc.nasa.gov/project/CERES}).
+The TAN1802 data are openly available on Zenodo \cite{kremser2020}.
+The remaining voyage data (AA15-16, HMNZSW16, NBP1704, TAN1502, and TAN1702) are openly available on Zenodo \cite{mcdonald2024b}.
+The Natural Earth dataset is openly available from \url{https://www.naturalearthdata.com}.
+The code used in our analysis is open-source and available on Zenodo: the code for performing the presented analysis \cite{kuma2024a}, precipitation detection \cite{kuma2024b}, cl2nc \cite{kuma2024c}, and a custom version of the ALCF used in our analysis \cite{kuma2024d}.
 
-\section*{Code availability}
+\acknowledgments
 
-The ALCF, cl2nc, rstool, lidar precipitation detection code, and our data
-processing and plotting code are open source and available at
-\url{https://alcf.peterkuma.net}, \url{https://github.com/peterkuma/cl2nc},
-\url{https://github.com/peterkuma/rstool}, and
-\url{https://github.com/peterkuma/alcf-precip},
-\url{https://github.com/peterkuma/icon-so-2024}, respectively. CyTRACK is
-available at \url{https://github.com/apalarcon/CyTRACK}. The ICON model is
-available at \url{https://gitlab.dkrz.de/icon/icon-mpim}.
+PK, FB, and the nextGEMS project received funding from the European Union’s Horizon 2020 research and innovation program under a grant agreement no.
+101003470.
+FB received funding from the Wenner-Gren Foundation and the Swedish e-Science Research Centre.
+The work of GM was supported by the United States (U.S.) Department of Energy Award DE-SC0021159.
+Supercomputing resources were provided by the DKRZ (project 1125 ICON-development) and the National Academic Infrastructure for Supercomputing in Sweden (allocation 2023/22-202).
+The data collection by the University of Canterbury was funded by the Deep South National Science Challenge Clouds and Aerosols project.
+Data collection on the AA15-16 voyages was funded by the Australian Antarctic Science project (grant no.~4292).
+We acknowledge the contribution of Thorsten Mauritsen to funding acquisition and project management.
+We acknowledge the RV \emph{Polarstern} datasets provided by the Alfred Wegener Institute and Pangaea, the AA15-16 dataset provided by the Australian Antarctic Division (AAD) and University of Canterbury (UC), the RV \emph{Tangaroa} datasets provided by the National Institute of Water and Atmospheric Research and UC, the NBP1704 dataset provided by the National Science Foundation, Cooperative Institute for Research in Environmental Sciences, University of Colorado and UC, the HMNZSW16 dataset provided by the Royal New Zealand Navy and UC, the MARCUS dataset provided by ARM and AAD, and the MICRE dataset provided by ARM, the Australian Bureau of Meteorology, and AAD.
+Technical, logistical, and ship support for MARCUS and MICRE were provided by the AAD through Australian Antarctic Science projects 4292 and 4387, and we thank Steven Whiteside, Lloyd Symonds, Rick van den Enden, Peter de Vries, Chris Young, Chris Richards, Andrew Klekociuk, John French, Terry Egan, Nick Cartwright, and Ken Barrett for all of their assistance.
+We thank the scientific staff, the crew, and everyone involved in collecting data on the voyages and stations, especially Gert König-Langlo, Holger Schmithüsen, Roger Marchand, Peter Guest, Kelly Schick, Jamie Halla, and Mike J.
+Harvey (†).
+We thank Loretta Preis for providing additional RV \emph{Polarstern} data.
+We acknowledge the ICON model output provided by the nextGEMS project, Deutscher Wetterdienst, Max-Planck-Institute for Meteorology, DKRZ, Karlsruhe Institute of Technology, and Center for Climate Systems Modeling; the reanalysis dataset ERA5 provided by the Copernicus Climate Change Service; MERRA-2 provided by the Global Modeling and Assimilation Office; CERES datasets provided by the NASA Langley Atmospheric Science Data Center Distributed Active Archive Center; and the Natural Earth dataset provided by naturalearthdata.com.
+Last but not least, we acknowledge the use of open-source software: Python, Cython \cite{behnel2011}, TensorFlow \cite{abadi2016}, Devuan GNU+Linux, parallel \cite{tange2011}, NumPy \cite{harris2020}, SciPy \cite{virtanen2020}, Matplotlib \cite{hunter2007}, cartopy \cite{cartopy}, pyproj, Inkscape, Bash, GNU Fortran, HDF \cite{folk1999}, and NetCDF \cite{rew1990}.
+We dedicate this study to the memory of Mike J.
+Harvey, who very substantially contributed to obtaining the atmospheric observations on the RV \emph{Tangaroa} voyages used in this study.
 
-\section*{Data availability}
-
-The RV \emph{Polarstern} datasets are openly available on Pangaea
-(\url{https://pangaea.de}). The MARCUS and MICRE datasets are openly available
-from ARM (\url{https://www.arm.gov}). The MERRA-2 data are openly available
-from the NASA Goddard Earth Sciences (GES) Data and Information Services Center
-(DISC) (\url{https://disc.gsfc.nasa.gov/datasets?project=MERRA-2}).  The ERA5
-data are openly available from the Copernicus Climate Data Store (CDS)
-(\url{https://cds.climate.copernicus.eu}). The ICON data are available on the
-Levante cluster of the DKRZ
-(\url{https://www.dkrz.de/en/systems/hpc/hlre-4-levante}) after registration at
-\url{https://luv.dkrz.de/register/}. The CERES products are available from the
-project website (\url{https://ceres.larc.nasa.gov}) and the NASA Atmospheric
-Science Data Centre (\url{https://asdc.larc.nasa.gov/project/CERES}).  The
-TAN1802 data are available on Zenodo
-(\url{https://doi.org/10.5281/zenodo.4060237}).
-
-% TODO: The other voyage and station data are openly available on Zenodo ().
-% Subsetted model and reanalysis data for the voyage tracks and the station and
-% data processed with the ALCF are openly available on Zenodo ().
-
-\section*{Author contributions}
-
-The authors have made the following contributions based on the CRediT taxonomy
-(\url{https://credit.niso.org}).  PK: conceptualization, data curation, formal
-analysis, investigation, methodology, software, writing – original draft; FAMB:
-conceptualization, funding acquisition, project administration, supervision,
-and writing – review \& editing; AJM, SPA, GMM, JJC, GEP, SH, SP, SG, and AJS:
-data curation, investigation, resources, writing – review \& editing.
-
-%\footnotesize
-\fontsize{11pt}{13pt}\selectfont
-\setlength{\bibsep}{0.0pt}
 \bibliography{manuscript}

### 2025-07-23 manuscript_rev1.tex
Rename manuscript

--- 2025-07-21 manuscript_agu_rev1.tex
@@
 \linenumbers
-
-\usepackage{xr}
-\externaldocument{si_rev1}
 
@@
 \item Large cloud biases are present in the global storm-resolving model but are lower in several key aspects than in the reanalyses.
-\item The models tend to underestimate total cloud fraction and very low-level ($<$~250~m) cloud and fog, while overestimating cloud occurrence peak at 500 m.
+\item The models tend to underestimate total cloud fraction and very low-level cloud and fog, while overestimating cloud occurrence peak at 500 m.
 \item A ``too few, too bright'' problem of underestimated cloud fraction, compensated by overestimated cloud albedo, is present in MERRA-2.
@@
 Reanalyses are the best estimates of past meteorological conditions based on an underlying global model and observations.
-We evaluated clouds, temperature, and humidity profiles over the Southern Ocean in one such model, ICON, as well as two reanalyses, based on 2400 days of ship and station observations.
+We evaluated clouds, temperature, and humidity profiles over the Southern Ocean in one such model, ICON and two reanalyses, based on 2400 days of ship and station observations.
 Thanks to the high resolution, ICON relies entirely on explicit simulation of clouds instead of subgrid-scale parameterizations.
@@
 ICON is also substantially less stable than ERA5 across the whole region.
-In Section~\ref{sec:thermodynamic-profiles} we show that based on radiosonde observations, the bias is in ICON and not ERA5, and it is the result of underestimated temperature at heights corresponding to 700 hPa, as well as overestimated near-surface (2~m) air temperature, characterized by a higher frequency of occurrence in the 1–7°C range compared to observations at radiosonde launch locations (Fig.~\ref{fig:stats-hist-surf}a).
+In Section~\ref{sec:thermodynamic-profiles} we show that based on radiosonde observations, the bias is in ICON and not ERA5, and it is the result of underestimated temperature at heights corresponding to 700 hPa, as well as overestimated near-surface (2~m) air temperature, characterized by a higher frequency of occurrence in the 1–7°C range compared to observations at radiosonde launch locations (Fig.~S1a).
 This may be related to large-scale circulation in ICON or radiative transfer biases.
@@
 We used the ALCF to derive cloud occurrence by height and the total cloud fraction from observations, ICON, ERA5, and MERRA-2.
-The results for all campaigns individually are shown in Fig.~\ref{fig:cloud-occurrence-panel}.
+The results for all campaigns individually are shown in Fig.~S2.
 As shown in this figure, the biases are relatively consistent across the campaigns and longitudes.
@@
 The exaggerated peak in models is partly explained by the LCL distribution, which peaks about 300~m higher in the models than in the observations (near the surface), although this is not very pronounced.
-This is indicative of near-surface RH often being close to saturation in the observations but not in the models (Fig.~\ref{fig:stats-hist-surf}b).
+This is indicative of near-surface RH often being close to saturation in the observations but not in the models (Fig.~S1b).
 There are multiple possible reasons for this bias, such as how the statistical distribution of RH within a grid cell is represented in the models, the air–sea moisture flux parameterization, or weaker stability in the models, which can cause more boundary mixing across heights and thus lower near-surface RH.
@@
 
-Fig.~\ref{fig:stats-hist-si} shows the LWP and IWP distributions as histograms and their corresponding averages.
+Fig.~S3 shows the LWP and IWP distributions as histograms and their corresponding averages.
 The LWP and IWP are calculated from the mass of water in the column divided by the area of the column, i.e., not just the area of the cloudy portion of the column, as in some definitions.
 The available observational satellite reference for the LWP and IWP over high latitudes is unfortunately very uncertain due to a high solar zenith angle and the inability of passive visible and infrared retrievals to detect phase below the cloud top of mixed-phase clouds \cite{huang2006,greenwald2009,seethala2010,eliasson2011,duncan2018,khanal2020}, and this limits our comparison.
-The LWP distribution shows that all models overestimate cases with a near-zero LWP (Fig.~\ref{fig:stats-hist-si}a), which relates to the underestimated total cloud fraction.
+The LWP distribution shows that all models overestimate cases with a near-zero LWP (Fig.~S3a), which relates to the underestimated total cloud fraction.
 MERRA-2 shows quite overestimated high-LWP situations, which is most likely related to the too-few-too-bright problem of simulating lower total cloud fraction but clouds with a higher LWP to compensate.
-The IWP (Fig.~\ref{fig:stats-hist-si}b) is somewhat less important radiatively than LWP because of the typically larger and less numerous hydrometeors.
+The IWP (Fig.~S3b) is somewhat less important radiatively than LWP because of the typically larger and less numerous hydrometeors.
 Similarly to the LWP, the models overestimate situations with a near-zero IWP.
 ERA5 is otherwise simulating the IWP distribution well, but ICON and MERRA-2 underestimate the IWP.
-In the cloudy situations (Fig.~\ref{fig:stats-hist-si}c, d), it can be seen more distinctly that MERRA-2 overestimates moderate (0.05–0.15 kg m$^{-2}$) and high LWP (over 0.15 kg m$^{-2}$), and ERA5 and ICON underestimate moderate LWP.
+In the cloudy situations (Fig.~S3c, d), it can be seen more distinctly that MERRA-2 overestimates moderate (0.05–0.15 kg m$^{-2}$) and high LWP (over 0.15 kg m$^{-2}$), and ERA5 and ICON underestimate moderate LWP.
 ICON also overestimates high LWP, resulting in overestimated average LWP.
@@
 In all subsets, ICON is too humid in the first 1~km by about 5\%, but very accurate above, except for the 40–55°S zone and conditions of weak stability (Fig.~\ref{fig:potential-temperature}b, g), where it is too dry between about 1 and 3~km.
-Even though RH measured by radiosondes in the first 100~m is not very different between the observations and the models (Fig.~\ref{fig:potential-temperature}a), near-surface (2-m) RH at the radiosonde launch locations is much greater in the observations, most often close to 100\%, unlike in the models, where 85\% tends to be the most common (Fig.~\ref{fig:stats-hist-surf}b).
+Even though RH measured by radiosondes in the first 100~m is not very different between the observations and the models (Fig.~\ref{fig:potential-temperature}a), near-surface (2-m) RH at the radiosonde launch locations is much greater in the observations, most often close to 100\%, unlike in the models, where 85\% tends to be the most common (Fig.~S1b).
 This also explains why LCL is much more frequently located at the surface in the observations than in the models (Fig.~\ref{fig:cloud-occurrence}a).
@@
 
-Fig.~\ref{fig:rs-thetav-hur-cloud} shows $\theta_v$ and RH profiles for profiles containing fog, cloud at 500 m, and cloud at 1.5 km.
+Fig.~S4 shows $\theta_v$ and RH profiles for profiles containing fog, cloud at 500 m, and cloud at 1.5 km.
 These situations are characterized by particular cloud biases as identified in the lidar cloud occurrence analysis.
 The rationale is to examine $\theta_v$ and RH associated with these situations.
-Foggy situations are characterized by a rapid increase of $\theta_v$ with height and an observed average RH of about 90\% near the surface (Fig.~\ref{fig:rs-thetav-hur-cloud}a).
+Foggy situations are characterized by a rapid increase of $\theta_v$ with height and an observed average RH of about 90\% near the surface (Fig.~S4a).
 In contrast, the models simulate higher RH in the first 100~m under foggy conditions by several percentage points.
-In situations with clouds occurring at 500 m, $\theta_v$ is relatively constant between the surface and 500 m (Fig.~\ref{fig:rs-thetav-hur-cloud}b), as expected for convectively driven clouds.
+In situations with clouds occurring at 500 m, $\theta_v$ is relatively constant between the surface and 500 m (Fig.~S4b), as expected for convectively driven clouds.
 The observed RH peaks at 500 m at about 90\%.
@@
 
-Fig.~\ref{fig:rs-thetav-hist} shows histograms the same as the previous figure, but for $\theta_v$.
-They show a more complex picture, characterized by a central peak at about 0°C near the surface, increasing to about 5°C at 2 km (Fig.~\ref{fig:rs-thetav-hist}a).
-For cloudy bins, the central peak is generally more constant with height and even shows a minimum in $\theta_v$ at about 500 m (Fig.~\ref{fig:rs-thetav-hist}i).
+Fig.~S5 shows histograms the same as the previous figure, but for $\theta_v$.
+They show a more complex picture, characterized by a central peak at about 0°C near the surface, increasing to about 5°C at 2 km (Fig.~S5a).
+For cloudy bins, the central peak is generally more constant with height and even shows a minimum in $\theta_v$ at about 500 m (Fig.~S5i).
 This is indicative of convection being associated with clouds at these heights, which results in flat $\theta_v$ profiles.
-In the reanalyses, in the first 200 m, values slightly above 0°C are associated with more clear bins than in observations, and values slightly below 0°C with fewer (Fig.~\ref{fig:rs-thetav-hist}g–h).
-Conversely, the opposite is true for cloudy bins (Fig.~\ref{fig:rs-thetav-hist}k–l).
+In the reanalyses, in the first 200 m, values slightly above 0°C are associated with more clear bins than in observations, and values slightly below 0°C with fewer (Fig.~S5g–h).
+Conversely, the opposite is true for cloudy bins (Fig.~S5k–l).
 Situations with 0°C near-surface air temperature might occur predominantly when an open ocean surface keeps the near-surface air temperature close to 0°C under otherwise colder air mass conditions, such as under cold advection.
-ICON displays a notable bias above about 1 km, where the central peak is strongly underestimated (Fig.~\ref{fig:rs-thetav-hist}j).
-Instead, these heights and values of $\theta_v$ are more associated with clear bins (Fig.~\ref{fig:rs-thetav-hist}f).
+ICON displays a notable bias above about 1 km, where the central peak is strongly underestimated (Fig.~S5j).
+Instead, these heights and values of $\theta_v$ are more associated with clear bins (Fig.~S5f).
 This might be related to the strong underestimation of cloud occurrence at these heights.
@@
 For these reasons, one can expect the results to be slightly different due to reasons unrelated to model biases, such as different weather conditions, partially accounted for by the cyclone and stability subsetting, and the phase of climate oscillations, such as the ENSO in the observations and ICON.
-The interannual variability in cloud occurrence in ICON can be seen in Fig.~\ref{fig:cloud-occurrence-panel}, where each year in ICON is represented by a separate line.
+The interannual variability in cloud occurrence in ICON can be seen in Fig.~S2, where each year in ICON is represented by a separate line.
 As could be expected, the interannual variability tends to be substantially smaller than the biases and thus is unlikely to have a strong impact on the main findings.
@@
 The latter is also manifested in the radiosonde profile comparison (Fig.~\ref{fig:rs-lts-hist}), showing that the $\theta_v$ profiles in ICON are less stable than in the observations.
-It is also manifested in near-surface air temperature, which is overestimated in the 1–7°C range at the radiosonde launch locations (Fig.~\ref{fig:stats-hist-surf}a).
+It is also manifested in near-surface air temperature, which is overestimated in the 1–7°C range at the radiosonde launch locations (Fig.~S1a).
 The underestimated LTS is linked to the overestimated cloud peak at 500 m in the lidar cloud occurrence comparison (Fig~\ref{fig:cloud-occurrence}f–g).
@@
 
-The campaigns show remarkably similar biases in cloud occurrence by height in the lidar comparison (Fig.~\ref{fig:cloud-occurrence-panel}), which indicates that common underlying causes for the biases exist regardless of longitude and season.
+The campaigns show remarkably similar biases in cloud occurrence by height in the lidar comparison (Fig.~S2), which indicates that common underlying causes for the biases exist regardless of longitude and season.
 ICON underestimates the total cloud fraction by about 10\%, with an overestimation of clouds below 1~km and an underestimation of clouds above 1~km.
@@
 ICON strongly overestimates the peak of cloud occurrence at about 500 m.
-This can be explained by the radiosonde comparison, showing that it is too moist at around this height (Fig.~\ref{fig:potential-temperature}a); has underestimated LTS (Fig.~\ref{fig:cyclone-stability} and \ref{fig:rs-lts-hist}), permitting shallow convection to this height; and has underestimated near-surface RH (Fig.~\ref{fig:stats-hist-surf}), resulting in higher LCL (Fig.~\ref{fig:cloud-occurrence}).
+This can be explained by the radiosonde comparison, showing that it is too moist at around this height (Fig.~\ref{fig:potential-temperature}a); has underestimated LTS (Fig.~\ref{fig:cyclone-stability} and \ref{fig:rs-lts-hist}), permitting shallow convection to this height; and has underestimated near-surface RH (Fig.~S1), resulting in higher LCL (Fig.~\ref{fig:cloud-occurrence}).
 Similar to our results for mid-level clouds, \citeA{cesana2022} showed that CMIP6 models also tend to underestimate cloud occurrence above 2~km over the SO, although their analysis in this case was limited to liquid clouds.
@@
 The inability of the models to simulate fog can be linked to various biases identified in our analysis.
-Near-surface RH is too low in the models (Fig.~\ref{fig:stats-hist-surf}), potentially due to low moisture flux from the surface and too effective boundary layer mixing.
+Near-surface RH is too low in the models (Fig.~S1), potentially due to low moisture flux from the surface and too effective boundary layer mixing.
 Near-surface temperature is also too high in ICON, and it can be expected that fog formation occurs in low near-surface temperature conditions when a warm and moist air mass is cooled by the surface to the saturation point.
-Fig.~\ref{fig:rs-thetav-hur-cloud} shows that fog occurs under highly stratified conditions.
+Fig.~S4 shows that fog occurs under highly stratified conditions.
 The underestimated LTS in ICON (and to a lesser extent in the reanalyses; Fig.~\ref{fig:rs-lts-hist}) indicates that the models are biased to weaker stability, thus having less favorable conditions for fog formation and persistence.
@@
 Notably, ICON exhibits smaller internal variability in $\theta_v$ than the radiosonde observations.
-The analysis of the LWP and IWP (Fig.~\ref{fig:stats-hist-si}) shows that both phases are present in observations in about equal amounts.
+The analysis of the LWP and IWP (Fig.~S3) shows that both phases are present in observations in about equal amounts.
 The models show diverse biases, the most pronounced being overestimation of high-LWP values in MERRA-2 and overestimation of cases with a near-zero LWP and IWP in all models.
